### 2021-01-09 Drafts and notes/draft_01.tex
add folder with notes

\documentclass[12pt,reqno]{amsart}

\setlength{\columnseprule}{0.4pt}
\setlength{\topmargin}{0cm}
\setlength{\oddsidemargin}{.25cm}
\setlength{\evensidemargin}{.25cm}
\setlength{\textheight}{22.5cm}
\setlength{\textwidth}{15.5cm}
\renewcommand{\baselinestretch}{1.05}

\usepackage{amsfonts,amsmath,amsthm}
\usepackage{amssymb,epsfig}
\usepackage{enumerate} 
%\usepackage{amscd}  
%{enumerate} 
%\usepackage{amscd}  
%\usepackage{cas%\usepackage{cases}
%\usepackage[notcite,notref]{showkeys}
%\geometry{verbose,tmargin=3cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2.5cm,headheight=2.5cm}

\usepackage[utf8]{inputenc}
\usepackage[euler-digits]{eulervm}
%\usepackage[bitstream-charter]{mathdesign}
\usepackage{eucal}
\usepackage[unicode=true]{hyperref}
\hypersetup{colorlinks = true,pdftex}
%\hypersetup{hidelinks=true}
\hypersetup{
     colorlinks,
     linkcolor={black!50!black},
	% linkcolor={red!50!black},
%    linkbordercolor = {blue},
%    <your other options...>,
     citecolor={blue}
}

%graphic
%\usepackage[text={425pt,650pt},centering]{geometry}

\usepackage{pdfsync}

\usepackage{geometry}
\geometry{verbose,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2.5cm,headheight=2.5cm}

\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{tikz}
\usepackage{caption}
\usepackage{color} %color
\definecolor{vert}{rgb}{0,0.6,0}

\usepackage{comment}
\numberwithin{figure}{section}
%\pagestyle{plain}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{ass}{Assumption}
\renewcommand{\theass}{}
\newtheorem{defn}{Definition}
\newtheorem{quest}{Question}
\newtheorem{com}{Comment}
\newtheorem{ex}{Example}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{prop}[thm]{Proposition}
\theoremstyle{remark}
\newtheorem{rem}{\bf{Remark}}
\numberwithin{equation}{section}

%\renewcommand{\thefootnote}{\fnsymbol{footnote}}

%Characters -- Shortcuts
\newcommand{\E}{\mathbb{E}}
\newcommand{\M}{\mathbb{M}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\bP}{\mathbb{P}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\bS}{\mathbb{S}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\bfS}{\mathbf{S}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cF}{\mathcal{F}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cL}{\mathcal{L}}
\newcommand{\cM}{\mathcal{M}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\cT}{\mathcal{T}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\I}{\mathrm{I}}

%Functional spaces
\newcommand{\AC}{{\rm AC\,}}
\newcommand{\ACl}{{\rm AC}_{{\rm loc}}}
\newcommand{\BUC}{{\rm BUC\,}}
\newcommand{\USC}{{\rm USC\,}}
\newcommand{\LSC}{{\rm LSC\,}}
\newcommand{\Li}{L^{\infty}}
\newcommand{\Lip}{{\rm Lip\,}}
\newcommand{\W}{W^{1,\infty}}
\newcommand{\Wx}{W_x^{1,\infty}}

%Domains
\newcommand{\bO}{\partial\Omega}
\newcommand{\cO}{\overline\Omega}
\newcommand{\Q}{\mathbb{T}^{n}\times(0,\infty)}
\newcommand{\iQ}{\mathbb{T}^{n}\times\{0\}}
\newcommand{\cQ}{\mathbb{T}^{n}\times[0,\infty)}

%Greek alphabets -- Shortcuts
\newcommand{\al}{\alpha}
\newcommand{\gam}{\gamma}
\newcommand{\del}{\delta}
\newcommand{\ep}{\varepsilon}
\newcommand{\kap}{\kappa}
\newcommand{\lam}{\lambda}
\newcommand{\sig}{\sigma}
\newcommand{\om}{\omega}
\newcommand{\Del}{\Delta}
\newcommand{\Gam}{\Gamma}
\newcommand{\Lam}{\Lambda}
\newcommand{\Om}{\Omega}
\newcommand{\Sig}{\Sigma}

%Overlines, Underlines -- Shortcuts
\newcommand{\ol}{\overline}
\newcommand{\ul}{\underline}
\newcommand{\pl}{\partial}
\newcommand{\supp}{{\rm supp}\,}
\newcommand{\inter}{{\rm int}\,}
\newcommand{\loc}{{\rm loc}\,}
\newcommand{\co}{{\rm co}\,}
\newcommand{\diam}{{\rm diam}\,}
\newcommand{\diag}{{\rm diag}\,}
\newcommand{\dist}{{\rm dist}\,}
\newcommand{\Div}{{\rm div}\,}
\newcommand{\sgn}{{\rm sgn}\,}
\newcommand{\tr}{{\rm tr}\,}
\newcommand{\Per}{{\rm Per}\,}

\renewcommand{\subjclassname}{%
\textup{2010} Mathematics Subject Classification}

%Hyperlink in PDF file
%\usepackage[dvipdfm,
%  colorlinks=false,
%  bookmarks=true,
%  bookmarksnumbered=false,
%  bookmarkstype=toc]{hyperref}
%\makeatletter
%\def\@pdfm@dest#1{%
%  \Hy@SaveLastskip
%  \@pdfm@mark{dest (#1) [@thispage /\@pdfview\space @xpos @ypos null]}%
%  \Hy@RestoreLastskip
%}

%BibLatex
%\usepackage[
%backend=biber,
%style=alphabetic,
%sorting=ynt
%]{biblatex}
%\addbibresource{rate.bib}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title[Rate of convergence]
{Second-order state-constraint Hamilton-Jacobi equations}

\thanks{The authors are supported in part by NSF grant DMS-1664424.}

\begin{abstract}

\end{abstract}

\author{Yuxi Han}
\address[Y. Han]
{
Department of Mathematics, 
University of Wisconsin Madison, 480 Lincoln  Drive, Madison, WI 53706, USA}
\email{yuxi.han@wisc.edu}

\author{Son N. T. Tu}
\address[S. N.T. Tu]
{
Department of Mathematics, 
University of Wisconsin Madison, 480 Lincoln  Drive, Madison, WI 53706, USA}
\email{thaison@math.wisc.edu}

%\date{\today}
\keywords{first-order Hamilton--Jacobi equations; state-constraint problems; optimal control theory; rate of convergence; viscosity solutions.}
\subjclass[2010]{
35B40, %Asymptotic behavior of solutions, 
35D40, %Viscosity solutions
49J20, %Optimal control problems involving partial differential equations
49L25, %Viscosity solutions
70H20 %Hamilton-Jacobi equations
}

\maketitle

%\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}\label{sec:intro}

%\nocite{*}

%\section*{Acknowledgement}

\bibliography{zzzzlibrary}{}
%\bibliographystyle{ieeetr}
\bibliographystyle{acm}

\end{document}

### 2021-01-09 Drafts and notes/draft_01.tex
Updating the tex file, xing all warnings and errors.
change font to mathpazo

@@
 \usepackage[utf8]{inputenc}
+\usepackage{mathpazo}
 \usepackage[euler-digits]{eulervm}
@@
 \usepackage[unicode=true]{hyperref}
-\hypersetup{colorlinks = true,pdftex}
+\hypersetup{colorlinks = true}
 %\hypersetup{hidelinks=true}
@@
 \usepackage{geometry}
-\geometry{verbose,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2.5cm,headheight=2.5cm}
+%\geometry{verbose,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2.5cm,headheight=2.5cm}
 
@@
 \title[Rate of convergence]
-{Second-order state-constraint Hamilton-Jacobi equations}
+{\textsc{Second-order state-constraint Hamilton-Jacobi equations}}
 
@@
 \section{Introduction}\label{sec:intro}
+Paper to read \cite{Ishii2017a}.
 

### 2021-01-15 Drafts and notes/draft_01.tex
Added the question on distance function.
Added some thoughts on differentiability with respect to the parameter

@@
-\documentclass[12pt,reqno]{amsart}
-
-\setlength{\columnseprule}{0.4pt}
-\setlength{\topmargin}{0cm}
-\setlength{\oddsidemargin}{.25cm}
-\setlength{\evensidemargin}{.25cm}
-\setlength{\textheight}{22.5cm}
-\setlength{\textwidth}{15.5cm}
+\documentclass[11pt,reqno]{amsart}
+%============%============%============%============%
+\usepackage{marktext}
+%============%============%============%============%
+%\setlength{\columnseprule}{0.4pt}
+%\setlength{\topmargin}{0cm}
+%\setlength{\oddsidemargin}{.25cm}
+%\setlength{\evensidemargin}{.25cm}
+%\setlength{\textheight}{22.5cm}
+%\setlength{\textwidth}{15.5cm}
 \renewcommand{\baselinestretch}{1.05}
-
+%============%============%============%============%
+\usepackage[toc,page]{appendix}
+%============%============%============%============%
+\usepackage{xcolor}
+\usepackage{placeins}
 \usepackage{amsfonts,amsmath,amsthm}
@@
 \usepackage{enumerate} 
-%\usepackage{amscd}  
-%{enumerate} 
-%\usepackage{amscd}  
-%\usepackage{cas%\usepackage{cases}
-%\usepackage[notcite,notref]{showkeys}
-%\geometry{verbose,tmargin=3cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2.5cm,headheight=2.5cm}
-
+\usepackage[notcite,notref]{showkeys}
+\usepackage{fullpage}
+%============%============%============%============%
 \usepackage[utf8]{inputenc}
 \usepackage{mathpazo}
-\usepackage[euler-digits]{eulervm}
-%\usepackage[bitstream-charter]{mathdesign}
+%\usepackage[euler-digits]{eulervm}
+
 \usepackage{eucal}
@@
      colorlinks,
-     linkcolor={black!50!black},
-	% linkcolor={red!50!black},
-%    linkbordercolor = {blue},
+     linkcolor={black!10!red},
+     linkbordercolor = {black!100!red},
 %    <your other options...>,
@@
 \usepackage{geometry}
-%\geometry{verbose,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2.5cm,headheight=2.5cm}
+\geometry{verbose,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2.5cm,headheight=3.5cm}
 
@@
 
+\newcommand{\rmC}{\mathrm{C}}
+
 \renewcommand{\subjclassname}{%
@@
 
+\usepackage{import}
+\usepackage{xifthen}
+\usepackage{pdfpages}
+\usepackage{transparent}
+\newcommand{\incfig}[1]{%
+    \def\svgwidth{\columnwidth}
+    \import{./figs/}{#1.pdf_tex}
+}
+
 \begin{document}
@@
 
-%\date{\today}
+\date{\today}
 \keywords{first-order Hamilton--Jacobi equations; state-constraint problems; optimal control theory; rate of convergence; viscosity solutions.}
@@
 \section{Introduction}\label{sec:intro}
-Paper to read \cite{Ishii2017a}.
+Paper to read \cite{Ishii2017a} and \cite{Lasry1989}.
+
+\section{Preliminaries}\label{sec:prelim}
+
+\subsection{Convergence result}
+\begin{thm}[Qualitative result] Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$.
+Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$.
+Let $u^\varepsilon$ be the solution to
+\begin{equation}\label{eq:PDE}
+    \begin{cases}
+    \lambda u^\varepsilon(x) + |Du^\varepsilon(x)|^p - f(x) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
+    \text{in}\;\Omega, \vspace{0cm}\\
+    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u(x) = +\infty.
+    \end{cases} \tag{PDE$_\varepsilon$}
+\end{equation}
+Then $u^\varepsilon \rightarrow u$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$ and $u$ solves
+\begin{equation*}
+    \begin{cases}
+    \lambda u(x) + |Du(x)|^p - f(x) \leq 0 \qquad\text{in}\;\Omega,\\
+    \lambda u(x) + |Du(x)|^p - f(x) \geq 0 \qquad\text{on}\;\overline{\Omega}.
+    \end{cases}   
+\end{equation*}
+\end{thm}
+
+\begin{proof}
+
+\end{proof}
 
 %\nocite{*}
+
+\section{Questions}
+\begin{quest} [Jan 12, 2021.] Why do we use the distance functions to get boundary estimates? 
+\end{quest}
+
+\begin{quest} [Jan 13, 2021.] Maximum principle for sub-quadratic case.
+\end{quest}
+
+\begin{appendices}
+\section{Construction of solution for sub-quadratic case}
+In this section, with the specific form of the Hamiltonian $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$, we show the existence and uniqueness of solutions to \eqref{eq:PDE}.
+\begin{thm} If $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ then there exists a unique solution $u\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDE}.
+\end{thm}
+
+\begin{proof} For $\delta>0$, let us define $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) < \delta\}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$.
+\begin{figure}[ht]
+    \centering
+    %\incfig{Domains}
+    \def\svgwidth{0.5\columnwidth}
+    \import{./figs/}{Domains.pdf_tex}
+    \caption{The domain $\Omega$ variations $\Omega_\delta, \Omega^\delta$.}
+    \label{fig:Domains}
+\end{figure}
+We consider $\delta$ small enough so that the distance function $x\mapsto \mathrm{dist}(x,\partial \Omega)$ is $\mathrm{C}^2$ in the strip $\Omega^\delta\backslash \overline{\Omega}_\delta$, we recall that $|D d(x)| = 1$ in that region.
+We extend the signed distance function into a $\mathrm{C}^2(\mathbb{R}^n)$ function, denoted by $d(x)$ such that
+\begin{equation*}
+    \begin{cases}
+    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_\delta,\\
+    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^\delta\backslash \Omega.
+    \end{cases}
+\end{equation*}
+We can choose $d(\cdot)$ so that $\Omega_\delta = \{x\in \mathbb{R}^n: d(x)-\delta >0 \}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: d(x) +\delta>0\}$.
+
+To find candidate for subsolution and supersolution to \eqref{eq:PDE}, we use the ansatz
+\begin{equation}\label{eq:ansatz}
+    u(x) = C_0 d(x)^{-\alpha}, \qquad x\in \Omega
+\end{equation}
+as we expect it blows up near the boundary like some thing proportionate to inverse of the distance function, due to the structure of $H(x,\varrho) = |\varrho|^p - f(x)$.
+Let us plug \eqref{eq:ansatz} into \eqref{eq:PDE} we obtain that the highest order terms are
+\begin{equation*}
+        -C_0 \alpha(\alpha+1)d^{-(\alpha+2)} + C_0^p \alpha^p d^{-(\alpha+1)p}.
+\end{equation*}
+Setting them to zero, we deduce that
+\begin{equation*}
+    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_0 = \frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}.
+\end{equation*}
+We can obtain the following families of subsolution on $\Omega^\delta$ and supersolution on $\Omega^\delta$ as follow.
+\begin{equation*}
+        \overline{w}_{\eta,\delta}(x) = \frac{C_0+\eta}{(d(x)-\delta)^\alpha} +\frac{C_\eta}{\lambda} \quad\text{for}\;x\in \Omega_\delta \qquad\text{and}\qquad \underline{w}_{\eta,\delta}(x) = \frac{C_0-\eta}{(d(x)+\delta)^\alpha} -\frac{C_\eta}{\lambda} \quad\text{for}\;x\in \Omega^\delta.
+\end{equation*}
+We divide the rest of the proof into 3 steps.
+\begin{itemize}
+    \item Step 1. Building a maximal solution to \eqref{eq:PDE}. 
+\end{itemize}
+\end{proof}
+
+\section{Gradient bounds}
+\subsection{Local interior gradient bound for elliptic equation}
+Let $\Omega\subset \R^n$ be an open, bounded, connected set with $\rmC^2$ boundary and $H(x,p):\overline{\Omega}\times \R^n\rightarrow \mathbb{R}$ be a continuously differentiable Hamiltonian satisfying
+\begin{equation}\label{eq:grow}
+\lim_{|p\rightarrow \infty} \left(\frac{1}{2}H(x,p)^2 + D_xH(x,p)\cdot p\right) = +\infty \qquad\text{uniformly in}\;x\in \overline{\Omega}. \tag{H1}
+\end{equation}
+We consider the following equation
+\begin{equation}\label{eq:C_eps}
+    \lambda u^\varepsilon(x) + H(x,Du^\varepsilon(x)) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad\text{in}\;\Omega.
+\end{equation}
+Let $u^\varepsilon\in \rmC^2(\Omega)\cap \mathrm{C}^1(\overline{\Omega})$ be a bounded solution to \eqref{eq:C_eps}, say $|\lambda u^\varepsilon(x)| \leq C_1$ for all $x\in \overline{\Omega}$.
+In this section we show that an interior gradient bound also holds, i.e., if $x\mapsto|Du^\varepsilon(x)|$ has a maximum over $\overline{\Omega}$ at $x_0\in \Omega$ then $|Du^\varepsilon(x_0)| \leq C_2$ for all $x\in \Omega$.
+Here $C_1,C_2$ are independent of $\varepsilon>0$.\\
+
+\noindent We will use the classical Bernstein's argument.
+Let $\varphi(x) = \frac{1}{2}|Du^\varepsilon(x)|^2$ for $x\in \Omega$.
+Differentiate \eqref{eq:C_eps} in $x_i$ then multiply the resulting equation with $u^\varepsilon_{x_i}$ and then sum over $i=1,2,\ldots, n$ we obtain
+\begin{equation*}
+    2\lambda \varphi(x) + D_pH(x,Du^\varepsilon(x))\cdot D\varphi(x) - \varepsilon \Delta \varphi(x) + \Big(\varepsilon |D^2u^\varepsilon(x)| + D_xH(x,Du^\varepsilon(x))\cdot Du^\varepsilon(x)\Big) = 0.
+\end{equation*}
+If $\varphi(x)$ achieves its maximum over $\overline{\Omega}$ at $x_0\in \Omega$, then $D\varphi(x_0) = 0$ and $\Delta \varphi(x_0)\leq 0$, together with $\varepsilon |D^2u^\varepsilon(x)|^2\geq \frac{1}{n\varepsilon}(\varepsilon\Delta u^\varepsilon(x))^2\geq (\varepsilon\Delta u^\varepsilon(x))^2$ if $n\varepsilon < 1$ we deduce that
+\begin{equation*}
+    \lambda |D u^\varepsilon(x_0)|^2 + \Big(\lambda u^\varepsilon(x_0)+H(x_0,Du^\varepsilon(x_0))\Big)^2 + D_xH(x_0,Du^\varepsilon(x_0))\cdot Du^\varepsilon(x_0) \leq 0.
+\end{equation*}
+Assume $|\lambda u^\varepsilon(x_0)|\leq C_1$, using \eqref{eq:grow} we deduce that
+\begin{equation*}
+    \frac{1}{2}H(x_0,Du^\varepsilon(x_0))^2 + D_xH(x_0,Du^\varepsilon(x_0))\cdot Du^\varepsilon(x_0) + \left(\frac{1}{\sqrt{2}}H(x_0,Du^\varepsilon(x_0) - \sqrt{2}C_1\right)^2 - \left(C_1\right)^2\leq 0
+\end{equation*}
+which gives us $|Du^\varepsilon(x_0)|\leq C_2$ for some $C_2$ independent of $\varepsilon$. 
+\begin{rem} Assumption \eqref{eq:grow} is weaker than the combination of $p\mapsto H(x,p)$ is superlinear and $|D_xH(x,p)|\leq C(1+|p|)$.
+\end{rem}
+
+\section{Differentiability with respect to the parameter}
+For the vanishing viscosity problem with the Dirichlet boundary condition,
+\begin{equation}
+\label{dir}
+\left\{
+  \begin{aligned}
+    H(x, Du^\epsilon(x)) &= \epsilon \Delta u^\epsilon \quad \, \text{in } U, \\
+              u^\epsilon &= 0 \quad \qquad \text{on } \partial U,
+  \end{aligned}
+\right.
+\end{equation}
+we want to show the smooth dependence of $u^\epsilon$ on $\epsilon$.
+Formally, if we differentiate \eqref{dir} with respect to $\epsilon$, we get
+\begin{equation}
+\label{dir_dif}
+\left\{
+  \begin{aligned}
+    D_pH(x, Du^\epsilon(x))\cdot Du^\epsilon_\epsilon &= \epsilon \Delta u^\epsilon_\epsilon +\Delta u^\epsilon \quad \, \text{in } U, \\
+              u^\epsilon_\epsilon &= 0 \quad \qquad  \qquad  \text{on } \partial U.
+  \end{aligned}
+\right.
+\end{equation}
+By Schaefer's fixed point theorem and the maximal principle, $u^\epsilon_\epsilon$ is the unique solution in $C^2(\overline{U})$ of \eqref{dir_dif} \textcolor{orange}{(needs double check)}.
+The main idea is, we look at the difference quotients $\displaystyle \frac{u^{\epsilon+h}-u^\epsilon}{h}$and prove that as $h \to 0^+$, they converge to a limiting function $w^{\ast}$ in the uniform norm \textcolor{orange}{(maybe weaker convergence is fine)} such that $w^{\ast}$ solves \eqref{dir_dif}.
+Since \eqref{dir_dif} has a unique solution, we have $$u^\epsilon_\epsilon=\lim_{h \to 0^+}\frac{u^{\epsilon+h}-u^\epsilon}{h}.$$
+
+Fix $\epsilon >0$. Let $$w^h(x):=\frac{u^{\epsilon+h}(x)-u^\epsilon(x)}{h} \in C^2(\overline{U}).$$
+
+A little computation will show that $w^h$ solves
+
+\begin{equation}
+\label{dir_quo}
+\left\{
+  \begin{aligned}
+   \epsilon \Delta w^h(x) + \frac{\epsilon}{\epsilon + h}\Delta u^\epsilon &= \frac{\epsilon}{\epsilon +h} \int_0^1 D_pH(x, Du^\epsilon+\theta (Du^{\epsilon+h}-Du^\epsilon)) d\theta \cdot Dw^h \quad \, \text{in } U, \\
+              w^h &= 0 \quad \qquad \text{on } \partial U.
+  \end{aligned}
+\right.
+\end{equation}
+Heuristically, we see as $h \to 0^+$, \eqref{dir_quo} "converges" to \eqref{dir_dif}.
+
+\textcolor{orange}{Still thinking about how to show $w^h$ converges uniformly as $h \to 0^+$.
+I am tring to show $\| w^h-w^\ast\|_\infty \to 0$ by looking at the equation solved by $v^h:=w^h-w^\ast$.
+More to fill in...}
+
+\end{appendices}
 

### 2021-01-17 Drafts and notes/Draft.tex
Added many appendices

--- 2021-01-15 Drafts and notes/draft_01.tex
@@
 \section{Introduction}\label{sec:intro}
-Paper to read \cite{Ishii2017a} and \cite{Lasry1989}.
 
-\section{Preliminaries}\label{sec:prelim}
-
-\subsection{Convergence result}
-\begin{thm}[Qualitative result] Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$.
+Let $\Omega$ be an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$.
 Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$.
@@
     \text{in}\;\Omega, \vspace{0cm}\\
-    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u(x) = +\infty.
+    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^\varepsilon(x) = +\infty.
     \end{cases} \tag{PDE$_\varepsilon$}
 \end{equation}
-Then $u^\varepsilon \rightarrow u$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$ and $u$ solves
-\begin{equation*}
+We are interested in studying the asymptotic behavior of $\{u^\varepsilon\}_{\varepsilon>0}$ as the vanishing viscosity happens: $\varepsilon\rightarrow 0$.
+
+Paper to read \cite{Ishii2017a} and \cite{Lasry1989}.
+
+\section{Preliminaries}\label{sec:prelim}
+
+\subsection{Convergence result}
+Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$. Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$.
+
+Let $u^\varepsilon$ be the solution to \eqref{eq:PDE}, we observe that if$u^\varepsilon\rightarrow u^0$ uniformly on compact subsets of $\Omega$, we see that $u(x)\rightarrow +\infty$ as $\mathrm{dist}(x,\partial \Omega)\to 0$ as well, therefore the limiting solution is not the state-constraint solution to a limiting first order equation.
+
+\begin{lem}\label{lem:max} Let $u\in \rmC(\overline{\Omega})$ be a viscosity subsolution of 
+\begin{equation}\label{S_0}
+ \lambda u(x) + H(x,Du(x)) = 0\;\qquad\text{in}\;\Omega
+\end{equation}
+such that, for all viscosity subsolution $v\in \rmC(\overline{\Omega})$ of \eqref{S_0} one has $v\leq u\in \overline{\Omega}$, then $u$ is a viscosity supersolution of \eqref{S_0} on $\overline{\Omega}$.
+\end{lem}
+
+\begin{thm}[Qualitative result] Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$.
+Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$.
+Let $u^\varepsilon$ be the solution to \eqref{eq:PDE}, then $u^\varepsilon \rightarrow u$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$ and $u$ solves
+\begin{equation}\label{eq:PDE0}
     \begin{cases}
@@
     \lambda u(x) + |Du(x)|^p - f(x) \geq 0 \qquad\text{on}\;\overline{\Omega}.
-    \end{cases}   
-\end{equation*}
+    \end{cases}\tag{PDE$_0$}   
+\end{equation}
 \end{thm}
 
-\begin{proof}
-
+\color{blue}
+\begin{proof} (\textit{Added on Jan 16, 2021 - Heuristic idea}) Assume that we can get some sort of equi-continuity of the family $\{u^\varepsilon\}_{\varepsilon>0}$ in a local way, that is, for any compact sub-domain $\Omega'\subset\subset \Omega$ there is a constant $C(\Omega')$ such that
+\begin{equation}\label{eq:bound}
+    \Vert u^\varepsilon\Vert_{L^\infty(\Omega')} +\Vert Du^\varepsilon\Vert_{L^\infty(\Omega')} \leq C(\Omega').
+\end{equation}
+This should be done using Berstein's method (fill in later, and as $u$ blows up on $\partial \Omega$, this bound \eqref{eq:bound} may not be improved).
+Now let us assume via some subsequence $\varepsilon_j\to 0$ we have $u^{\varepsilon_j}\rightarrow u^0$ uniformly on compact subsets of $\Omega$, the interior stability of viscosity solution should yield us that
+\begin{equation*}
+    \lambda u^0(x) + |Du^0(x)|^p - f(x) = 0 \qquad\text{in}\;\Omega.
+\end{equation*}
+The real difficulty is describing what is the behavior of $u^0$ on the boundary. As we expect it to solves \eqref{eq:PDE0}, it should be the maximal subsolution (hence, solution) to 
+\begin{equation}\label{eq:S_lambda}
+    \lambda u(x) + |Du(x)|^p - f(x) = 0 \qquad\text{in}\;\Omega.
+\end{equation}
+Let $v^\varepsilon\in \rmC^2(\Omega)\cap \rmC(\overline{\Omega})$ be the unique solution to the Dirichlet problem
+\begin{equation}\label{eq:v_eps}
+\begin{cases}
+    \lambda v^\varepsilon(x) + |Dv^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v^\varepsilon(x) &\qquad\text{in}\;\Omega,\\
+    \;\;\,\quad\quad\qquad\qquad\qquad\qquad v^\varepsilon = u &\qquad \text{on}\;\partial\Omega.
+\end{cases}
+\end{equation}
+where $u\in \rmC(\overline{\Omega})$ is the unique solution of \eqref{eq:PDE0}. Note that $v^\varepsilon\rightarrow v^0$ solves the corresponding Dirichlet problem
+\begin{equation}\label{eq:v_0}
+\begin{cases}
+    \lambda v^0(x) + |Dv^0(x)|^p - f(x) = 0 &\qquad\text{in}\;\Omega,\\
+    \;\;\,\quad\quad\qquad\qquad\qquad\qquad v^0 = u &\qquad \text{on}\;\partial\Omega.
+\end{cases}
+\end{equation}
+\begin{lem} $v^0\equiv u$ as the unique solution to \eqref{eq:PDE0}.
+\end{lem}
+\begin{proof} We observe that $u$ solves \eqref{eq:PDE0} is the unique solution to the Dirichlet problem \eqref{eq:v_0} as well, thus $v^0 \equiv u$ by comparison principle.
 \end{proof}
+\noindent By comparison principle, we see that
+\begin{equation*}
+    v^\varepsilon(x)\leq u^\varepsilon(x) \qquad\text{for}\;x\in \Omega.
+\end{equation*}
+Let $\varepsilon\to 0$, we deduce that
+\begin{equation*}
+    u(x)\leq u^0(x) \qquad\text{for}\;x\in \Omega.
+\end{equation*}
+\end{proof}
+\color{black}
 

### 2021-01-17 Drafts and notes/Old_draft_01.tex
Added many appendices

--- 2021-01-17 Drafts and notes/Draft.tex
@@
 \section{Introduction}\label{sec:intro}
+Paper to read \cite{Ishii2017a} and \cite{Lasry1989}.
 
-Let $\Omega$ be an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$.
+\section{Preliminaries}\label{sec:prelim}
+
+\subsection{Convergence result}
+\begin{thm}[Qualitative result] Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$.
 Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$.
@@
 \end{equation}
-We are interested in studying the asymptotic behavior of $\{u^\varepsilon\}_{\varepsilon>0}$ as the vanishing viscosity happens: $\varepsilon\rightarrow 0$.
-
-Paper to read \cite{Ishii2017a} and \cite{Lasry1989}.
-
-\section{Preliminaries}\label{sec:prelim}
-
-\subsection{Convergence result}
-Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$. Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$.
-
-Let $u^\varepsilon$ be the solution to \eqref{eq:PDE}, we observe that if$u^\varepsilon\rightarrow u^0$ uniformly on compact subsets of $\Omega$, we see that $u(x)\rightarrow +\infty$ as $\mathrm{dist}(x,\partial \Omega)\to 0$ as well, therefore the limiting solution is not the state-constraint solution to a limiting first order equation.
-
-\begin{lem}\label{lem:max} Let $u\in \rmC(\overline{\Omega})$ be a viscosity subsolution of 
-\begin{equation}\label{S_0}
- \lambda u(x) + H(x,Du(x)) = 0\;\qquad\text{in}\;\Omega
-\end{equation}
-such that, for all viscosity subsolution $v\in \rmC(\overline{\Omega})$ of \eqref{S_0} one has $v\leq u\in \overline{\Omega}$, then $u$ is a viscosity supersolution of \eqref{S_0} on $\overline{\Omega}$.
-\end{lem}
-
-\begin{thm}[Qualitative result] Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$.
-Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$.
-Let $u^\varepsilon$ be the solution to \eqref{eq:PDE}, then $u^\varepsilon \rightarrow u$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$ and $u$ solves
+Then $u^\varepsilon \rightarrow u$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$ and $u$ solves
 \begin{equation}\label{eq:PDE0}

### 2021-01-27 Drafts and notes/Draft.tex
Added Construction

--- 2021-01-15 Drafts and notes/draft_01.tex
@@
 %============%============%============%============%
-\usepackage{marktext}
+
 %============%============%============%============%
@@
 \usepackage[utf8]{inputenc}
-\usepackage{mathpazo}
+%\usepackage{mathpazo}
 %\usepackage[euler-digits]{eulervm}
-
+\usepackage[libertine,cmintegrals,cmbraces,vvarbb]{newtxmath}
 \usepackage{eucal}
@@
 \newcommand{\rmC}{\mathrm{C}}
+\newcommand{\rup}{\rightharpoonup}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \usepackage{import}
@@
 }
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
-
 \title[Rate of convergence]
 {\textsc{Second-order state-constraint Hamilton-Jacobi equations}}
-
 \thanks{The authors are supported in part by NSF grant DMS-1664424.}
-
 \begin{abstract}
-
+We investigate qualitatively the convergence of large, or state-constraint solution to nonlinear elliptic equation as the viscosity vanish.
 \end{abstract}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \author{Yuxi Han}
@@
 \email{yuxi.han@wisc.edu}
-
 \author{Son N. T. Tu}
@@
 \email{thaison@math.wisc.edu}
-
 \date{\today}
@@
 }
+\maketitle
+\setcounter{tocdepth}{1}
+\tableofcontents
 
-\maketitle
-
-%\tableofcontents
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}\label{sec:intro}
-Paper to read \cite{Ishii2017a} and \cite{Lasry1989}.
+\subsection{Motivation} Let $\Omega$ be an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$.
+Let us consider the following Hamiltonian $ H(x,\varrho) = |\varrho|^p-f(x)$ for $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$, $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
+Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ (see \cite{Lasry1989}) be the solution to
+\begin{equation}\label{eq:PDEeps}
+    \begin{cases}
+    \lambda u^\varepsilon(x) + H(x,Du^\varepsilon(x)) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
+    \text{in}\;\Omega, \vspace{0cm}\\
+    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^\varepsilon(x) = +\infty.
+    \end{cases} \tag{PDE$_\varepsilon$}
+\end{equation}
+When $1<p\leq 2$, equation \eqref{eq:PDEeps} describes the (expectation) value function associated with a minimization of a stochastic optimal control problem with state-constraint.
+We are interested in studying the asymptotic behavior of $\{u^\varepsilon\}_{\varepsilon>0}$ as $\varepsilon\rightarrow 0$.
+Heuristically, the state-constraint second-order problem converges to the state-constraint first-order, which is associated with deterministic optimal control, which is described in the framework of viscosity solution as follows:
+\begin{equation}\label{eq:PDE0}
+    \begin{cases}
+     \lambda u(x) + H(x,Du(x)) \leq 0\;\qquad\text{in}\;\Omega,\\
+     \lambda u(x) + H(x,Du(x)) \geq 0\;\qquad\text{on}\;\overline{\Omega}.
+    \end{cases} \tag{PDE$_0$}
+\end{equation}
+Equation \eqref{eq:PDE0} admits a unique viscosity solution in the space $\rmC(\overline{\Omega})$, which is also the maximal viscosity subsolution among all viscosity subsolution $v\in\rmC(\overline{\Omega})$.
+The problem is interesting since in the limit we no longer have blowing up behavior.
+In this paper, we are interested in the rate of convergence of $u^\varepsilon \to u$ as $\varepsilon\to 0$.
+A boundary layer is expected to describe the behavior of convergence near the boundary.
+\subsection{Assumptions} We will always assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary in $\mathbb{R}^n$ and $H:\mathbb{R}^n\times \mathbb{R}^n$ is a continuous Hamiltonian.
+\begin{itemize}
+    \item[$\mathrm{(A1)}$] $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
+\end{itemize}
+We list the assumptions on a general Hamiltonian as follow.
+\begin{itemize}
+    \item[$\mathrm{(H1)}$] There exists $C_1 > 0$ such that $H(x,p) \geq -C_1$ for all $(x,p)\in \overline{\Omega}\times\mathbb{R}^n$.
+    \item[$\mathrm{(H2)}$] There exists $C_2>0$ such that $|H(x,0)|\,\leq \,C_2$ for all $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$.
+    \item[$\mathrm{(H3)}$] For each $R>0$ there exists a modulus $\omega_{R}[0,\infty)\to [0,\infty)$ such that $\omega_R(0^+) = 0$ and 
+    \begin{equation*}
+        \begin{cases}
+        |H(x,p) - H(y,p)| \leq \omega_R(|x-y|),\\
+        |H(x,p) - H(x,q)| \leq \omega_R(|p-q|),
+        \end{cases} \qquad\text{for all}\;x,y\in \overline{\Omega}, p,q \in \mathbb{R}^n\;\text{with}\;|p|,|q|\leq R.
+    \end{equation*}
+    \item[$\mathrm{(H4)}$] $H(x,p)\rightarrow \infty$ as $|p|\to \infty$ uniformly in $x\in \overline{\Omega}$.
+\end{itemize}
 
 \section{Preliminaries}\label{sec:prelim}
+\subsection{Gradient estimate}
 
-\subsection{Convergence result}
-\begin{thm}[Qualitative result] Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$.
-Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$.
-Let $u^\varepsilon$ be the solution to
-\begin{equation}\label{eq:PDE}
-    \begin{cases}
-    \lambda u^\varepsilon(x) + |Du^\varepsilon(x)|^p - f(x) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
-    \text{in}\;\Omega, \vspace{0cm}\\
-    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u(x) = +\infty.
-    \end{cases} \tag{PDE$_\varepsilon$}
-\end{equation}
-Then $u^\varepsilon \rightarrow u$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$ and $u$ solves
-\begin{equation*}
-    \begin{cases}
-    \lambda u(x) + |Du(x)|^p - f(x) \leq 0 \qquad\text{in}\;\Omega,\\
-    \lambda u(x) + |Du(x)|^p - f(x) \geq 0 \qquad\text{on}\;\overline{\Omega}.
-    \end{cases}   
-\end{equation*}
-\end{thm}
+\subsection{Well-posedness of large solution for subquaratic case}
 
-\begin{proof}
+In this section, with the specific form of the Hamiltonian $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$, we show the existence and uniqueness of solutions to \eqref{eq:PDEeps}.
+We note that the assumption of $f$ can be relaxed to $f\in L^\infty(\Omega)$ only, but for the clarity of the proof we will assume $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
 
-\end{proof}
-
-%\nocite{*}
-
-\section{Questions}
-\begin{quest} [Jan 12, 2021.] Why do we use the distance functions to get boundary estimates? 
-\end{quest}
-
-\begin{quest} [Jan 13, 2021.] Maximum principle for sub-quadratic case.
-\end{quest}
-
-\begin{appendices}
-\section{Construction of solution for sub-quadratic case}
-In this section, with the specific form of the Hamiltonian $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$, we show the existence and uniqueness of solutions to \eqref{eq:PDE}.
-\begin{thm} If $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ then there exists a unique solution $u\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDE}.
+\begin{thm} If $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ then there exists a unique solution $u\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps}.
 \end{thm}
@@
     %\incfig{Domains}
-    \def\svgwidth{0.5\columnwidth}
+    \def\svgwidth{0.47\columnwidth}
     \import{./figs/}{Domains.pdf_tex}
@@
 
-To find candidate for subsolution and supersolution to \eqref{eq:PDE}, we use the ansatz
+\noindent To find candidate for subsolution and supersolution to \eqref{eq:PDEeps}, we use the ansatz
 \begin{equation}\label{eq:ansatz}
@@
 as we expect it blows up near the boundary like some thing proportionate to inverse of the distance function, due to the structure of $H(x,\varrho) = |\varrho|^p - f(x)$.
-Let us plug \eqref{eq:ansatz} into \eqref{eq:PDE} we obtain that the highest order terms are
+Let us plug \eqref{eq:ansatz} into \eqref{eq:PDEeps} we obtain that the highest order terms are
 \begin{equation*}
@@
 \end{equation*}
-We can obtain the following families of subsolution on $\Omega^\delta$ and supersolution on $\Omega^\delta$ as follow.
+We can obtain the following families of supersolution on $\Omega_\delta$ and subsolution on $\Omega^\delta$ as follow.
 \begin{equation*}
@@
 We divide the rest of the proof into 3 steps.
-\begin{itemize}
-    \item Step 1. Building a maximal solution to \eqref{eq:PDE}. 
-\end{itemize}
+We first construct a minimal solution, then a maximal solution to \eqref{eq:PDEeps}, and finally show that they are equal to conclude the existence and uniqueness of solution to \eqref{eq:PDEeps}.
+
+\begin{prop}\label{pro:minimalsol} There exists a minimal solution $\underline{u}\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that $v\geq \underline{u}$ for any other solution $v\in \mathrm{C}^2(\Omega)$ solving \eqref{eq:PDEeps}.
+\end{prop}
+\begin{proof} Let $w_{\eta,\delta}\in \mathrm{C}^2(\Omega)$ solves
+    \begin{equation}\label{e:w_def}
+    \begin{cases}
+        \mathcal{L}\left[w_{\eta,\delta}\right] = 0 &\qquad\text{in}\;\Omega,\\
+        \qquad w_{\eta,\delta} = \underline{w}_{\eta,\delta} &\qquad\text{on}\;\partial\Omega.
+    \end{cases}
+    \end{equation}
+    Fix $\eta>0$, as $\delta\to 0$ the value of $\underline{w}_{\eta,\delta}$ blows up on the boundary, therefore by comparison principle we have $\delta_1 \leq  \delta_2$ implies $w_{\eta,\delta_1}\leq  w_{\eta,\delta_2}$ on $\overline{\Omega}$.
+
+    \noindent Since $\underline{w}_{\eta,\delta'}$ is a subsolution in $\overline{\Omega}$ with finite boundary, we obtain that
+    \begin{equation}\label{e:cp_delta1}
+        0<\delta \leq \delta'\qquad\Longrightarrow\qquad \underline{w}_{\eta,\delta'} \leq w_{\eta_,\delta'}\leq w_{\eta,\delta} \qquad\text{on}\;\overline{\Omega}.
+    \end{equation}
+    For $\delta' > 0$, since $\overline{w}_{\eta,\delta}$ is a supersolution on $\Omega_{\delta'}$ with infinity value on the boundary $\partial\Omega_{\delta'}$, by comparison principle
+    \begin{equation}\label{e:cp_delta2}
+        w_{\eta,\delta} \leq \overline{w}_{\eta, \delta'} \qquad\text{in}\;\Omega_{\delta'} \qquad\Longrightarrow\qquad w_{\eta,\delta} \leq \overline{w}_{\eta,0} \qquad\text{in}\;\Omega.
+    \end{equation}
+    From \eqref{e:cp_delta1} and \eqref{e:cp_delta2} we have
+    \begin{equation}\label{e:cp_delta3}
+        0<\delta \leq \delta'\qquad\Longrightarrow\qquad \underline{w}_{\eta,\delta'} \leq w_{\eta_,\delta'}\leq w_{\eta,\delta} \leq \overline{w}_{\eta,0} \qquad\text{in}\;\Omega.
+    \end{equation}
+    Thus $\{w_{\eta,\delta}\}_{\delta>0}$ is locally bounded in $L^{\infty}_{\mathrm{loc}}(\Omega)$.
+Using the gradient estimate for $w_{\eta,\delta}$ solving \eqref{e:w_def} we deduce that $\{w_{\eta,\delta}\}_{\delta>0}$ is locally bounded in $W^{1,\infty}_{\mathrm{loc}}(\Omega)$.
+Plug it back into the defining equation \eqref{e:w_def} to bound the Laplacian and the second derivative terms, we deduce that $\{w_{\eta,\delta}\}_{\delta>0}$ is locally bounded in $W^{2,r}_{\mathrm{loc}}(\Omega)$ for all $r<\infty$.
+
+    \noindent Local boundedness of $\{u_{\eta,\delta}\}_{\delta>0}$ in $W^{2,r}_{\mathrm{loc}}(\Omega)$ implies weak$^*$ compactnes, that is there exists a function $u\in W^{2,r}(\Omega)$ such that (via subsequence and monotonicity)
+    \begin{equation*}
+    \begin{cases}
+        w_{\eta,\delta} \rup u \qquad\text{weakly in}\;W^{2,r}_{\mathrm{loc}}(\Omega),\vspace{0.2cm}\\
+        w_{\eta,\delta} \to u \qquad\text{strongly in}\;W^{1,r}_{\mathrm{loc}}(\Omega).
+    \end{cases}
+    \end{equation*}
+    In particular, $w_{\eta,\delta}\to u$ in $\mathrm{C}^1_{\mathrm{loc}}(\Omega)$ thanks to compact embedding.
+Let us rewrite the equation $\mathcal{L}\left[u_{\eta,\delta}\right] = 0$ as $\varepsilon\Delta w_{\eta,\delta}(x) = F[w_{\eta,\delta}](x)$ in $U$ for $U\subset\subset \Omega$ where
+    \begin{equation*}
+        F[w_{\eta,\delta}](x) =  \lambda w_{\eta,\delta}(x) + H(x,Dw_{\eta,\delta}(x)).
+    \end{equation*}
+    As $u_{\eta,\delta}\to u$ in $\mathrm{C}^1(U)$ as $\delta\to 0$, we have $F[w_{\eta,\delta}](x) \to F(x)$ uniformly in $U$ where 
+    \begin{equation*}
+        F(x) = \lambda u(x) + H(x,Du(x)).
+    \end{equation*}
+    In the limit we see that $u\in L^2$ is a weak solution of $\varepsilon\Delta u = F$ in $U$ where $F$ is continuous, thus $u\in \mathrm{C}^2(\Omega)$ as well and by stability we see that $u$ solves $\mathcal{L}[u] = 0$ in $\Omega$.
+From \eqref{e:cp_delta3} we also have
+    \begin{equation*}
+        \underline{w}_{\eta,0} \leq u \leq \overline{w}_{\eta,0} \qquad\text{in}\;\Omega.
+    \end{equation*}
+    It is clear that $u(x)\to \infty$ as $\mathrm{dist}(x,\partial\Omega)\to 0$ with the precise rate like \eqref{eq:ansatz}.
+We note that at this point, by construction, $u$ may depend on $\eta$.
+We show that $u$ is the maximal solution of $\mathcal{L}[u] = 0$ in $\Omega$ such that $u = +\infty$ on $\partial\Omega$, and thus consequently showing that $u$ is independent of $\eta$.
+
+    \noindent Let $v\in W^{2,r}(\Omega)$ for all $r<\infty$ solving \eqref{eq:PDEeps}.
+Fix $\delta>0$, then for all $\vartheta>0$ small we see that on $\partial\overline{\Omega}_\vartheta$ the value of $v$ blows up as $\vartheta\to 0$, while $w_{\eta,\delta}$ remains bounded (we fixed $\delta>0$).
+Comparison principle gives us that $v\geq w_{\eta,\delta}$ on $\Omega_{\vartheta}$, thus as $\vartheta\to 0$ we obtain $v\geq w_{\eta,\delta}$ on $\Omega$.
+Let $\delta\to 0$ we deduce that $v\geq u$ on $\Omega$.
+This concludes that $u$ is the minimal solution in $W^{2,r}(\Omega)(\forall\,r<\infty)$ and thus independent of $\eta>0$.
 \end{proof}
+
+\begin{prop} There exists a maximal solution $\overline{u}\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that $v\leq \overline{u}$ for any other solution $v\in \mathrm{C}^2(\Omega)$ solving \eqref{eq:PDEeps}.
+\end{prop}
+
+\begin{proof} For each $\delta>0$, let us denote $u_\delta\in \mathrm{C}^2(\Omega_\delta)$ be the minimal solution to $\mathcal{L}[u_\delta] = 0$ in $\Omega$ and $u_\delta = +\infty$ on $\partial\Omega_\delta$ according to Proposition \ref{pro:minimalsol}.
+By comparison principle, for every $\eta>0$ there holds
+\begin{equation*}
+    \underline{w}_{\eta,\delta} \leq u_\delta \leq \overline{w}_{\eta,\delta} \qquad\text{in}\;\Omega_\delta,
+\end{equation*}
+and
+\begin{equation*}
+    0<\delta<\delta' \qquad \Longrightarrow\qquad u_\delta \leq u_\delta' \qquad\text{in}\;\Omega_{\delta'}.
+\end{equation*}
+We have the local boundedness of $\{u_\delta\}_{\delta>0}$ in $W^{2,r}(\Omega)$ as well, thus together with monotonicity there exists $u\in W^{2,r}(\Omega)$ for all $r<\infty$ such that $u_\delta\to u$ strongly in $\rmC^1_{\mathrm{loc}}(\Omega)$, therefore using the equation $\mathcal{L}[u_\delta] = 0$ in $\Omega_\delta$ and the regularity of Laplace equation we deduce that $u\in \mathrm{C}^2(\Omega)$ solving \eqref{eq:PDEeps} and
+\begin{equation*}
+    \underline{w}_{\eta,0} \leq u\leq \overline{w}_{\eta,0} \qquad\text{in}\;\Omega
+\end{equation*}
+for all $\eta>0$.
+From the construction, as $u_\delta$ is independent of $\eta$, it is clear that $u$ is also independent of $\eta$.
+We now show that $u$ is the maximal solution of \eqref{eq:PDEeps}.
+Let $v\in\rmC^2(\Omega)$ solves \eqref{eq:PDEeps}, then clearly $v\leq u_\delta$ on $\Omega_\delta$ and therefore as $\delta \to 0$ we have $v\leq u$.
+\end{proof}
+\noindent In conclusion we have found a minimal solution $\underline{u}$ and a maximal solution $\overline{u}$ in $\rmC^2(\Omega)$ such that
+\begin{equation}\label{e:chain}
+    \underline{w}_{\eta,0} \leq \underline{u}\leq \overline{u}\leq \overline{w}_{\eta,0} \qquad\text{in}\;\Omega
+\end{equation}
+for any $\eta>0$. This extra parameter $\eta$ now enables us to show that $\overline{u} = \underline{u}$ in $\Omega$.
+
+\begin{prop}[Uniqueness] We have $\overline{u}\equiv \underline{u}$ in $\Omega$ and therefore solution to \eqref{eq:PDEeps} in $\mathrm{C}^2(\Omega)$ is unique.
+\end{prop}
+\begin{proof} Let $\theta\in (0,1)$, we cook up a subsolution by convex combination $w_\theta = \theta \overline{u} + (1-\theta)\lambda^{-1}\left(\inf_{\Omega} f\right)$, which if we can use comparison principle then
+\begin{equation*}
+    w_\theta = \theta \overline{u} + (1-\theta)\lambda^{-1}\left(\inf_{\Omega} f\right) \leq \underline{u} \qquad\text{in}\;\Omega.
+\end{equation*}
+If that is the case, let $\theta\to 1$ we conclude that $\overline{u} \leq \underline{u}$.
+There is a problem here, as they are both explosive solutions, to use comparison principle we need to show that $w_\theta \leq \underline{u}$ in a neighborhood of $\partial\Omega$.
+From \eqref{e:chain} we see that
+\begin{equation*}
+    1\leq \frac{\overline{u}(x)}{\underline{u}(x)} \leq \frac{\overline{w}_{\eta,0}(x)}{\underline{w}_{\eta,0}(x)} = \frac{(C_0+\eta)+\lambda^{-1}C_\eta d(x)^\alpha}{(C_0-\eta)-\lambda^{-1}C_\eta d(x)^\alpha} \qquad\text{for}\;x\in \Omega
+\end{equation*}
+and therefore
+\begin{equation*}
+   1\leq  \lim_{d(x)\to 0} \left(\frac{\overline{u}(x)}{\underline{u}(x)}\right) \leq \frac{C_0+\eta}{C_0-\eta} \qquad\Longrightarrow\qquad  \lim_{d(x)\to 0} \left(\frac{\overline{u}(x)}{\underline{u}(x)}\right) = 1
+\end{equation*}
+since $\eta>0$ is chosen arbitrary. This means for any $\varsigma\in(0,1)$ we can find $\delta(\varsigma)>0$ small such that on $\Omega\backslash \Omega_\delta$ one has
+\begin{equation*}
+\frac{\overline{u}(x)}{\underline{u}(x)}\leq (1+\varsigma)     \qquad\Longrightarrow\qquad \frac{1}{1+\varsigma} \overline{u}(x) \leq \underline{u}(x) \qquad\text{in}\; \Omega\backslash \Omega_\delta
+\end{equation*}
+For given $\theta\in (0,1)$, we can always choose $\varsigma$ small enough such that $(1+\varsigma)^{-1} > \theta$ which renders $\underline{u}(x) \geq \theta \overline{u}(x) + (1-\theta)\lambda^{-1}\left(\inf_\Omega f\right)$ for $0< d(x) < \delta' < \delta$.
+\end{proof}
+\noindent A final remark is that, we can also repeat the proof for $p=2$.
+\end{proof}
+\subsection{Convergence result} We show the convergence (qualitatively) of \eqref{eq:PDEeps} to \eqref{eq:PDE0}.
+We first state the following Lemma (\cite{Capuzzo-Dolcetta1990}), which characterizes the state-constraint of first-order equation
+\begin{equation}\label{S_0}
+ \lambda u(x) + H(x,Du(x)) = 0\;\qquad\text{in}\;\Omega. \tag{$S_0$}
+\end{equation}
+
+\begin{lem}\label{lem:max} Let $u\in \rmC(\overline{\Omega})$ be a viscosity subsolution of \eqref{S_0} such that, for all viscosity subsolution $v\in \rmC(\overline{\Omega})$ of \eqref{S_0} one has $v\leq u$ in $\overline{\Omega}$, then $u$ is a viscosity supersolution of \eqref{S_0} on $\overline{\Omega}$.
+\end{lem}
+\noindent Lemma \ref{lem:max} is a variation of Perron's method.
+We give a proof in Appendix for the sake of completeness.
+Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ be a solution to \eqref{eq:PDEeps}, we claim that $\{\lambda u^\varepsilon\}_{\varepsilon>0}$ is uniformly bounded from below by a constant independent of $\varepsilon$ and $\lambda$.
+We have
+\begin{equation*}
+    u^\varepsilon(x) = \lim_{m\to \infty} u^{\varepsilon}_m(x), \qquad x\in \Omega,
+\end{equation*}
+where $u^{\varepsilon,m}\in \mathrm{C}^2(\Omega)\cap \rmC(\overline{\Omega})$ solves the Drichlet problem
+\begin{equation}\label{e:uepsm}
+    \begin{cases}
+    \lambda u(x) + H(x,Du(x)) - \varepsilon \Delta u(x) = 0 &\qquad
+    \text{in}\;\Omega, \vspace{0cm}\\
+    \;\;\quad\quad\qquad\qquad\qquad\qquad u(x) = m &\qquad
+    \text{on}\;\partial\Omega.
+    \end{cases} \tag{PDE$_{\varepsilon,m}$}
+\end{equation}
+If we assume $\mathrm{(H2)}$ then we can take $C_2 = \Vert f\Vert_{L^\infty(\Omega)}$ and take $\varphi(x) \equiv -\lambda^{-1}C_2$ for $x\in \overline{\Omega}$ as a subsolution to \eqref{e:uepsm}, hence by comparison principle for \eqref{e:uepsm} we have $u^{\varepsilon}_m(x)\geq -\lambda^{-1}C_2$ for all $x\in \overline{\Omega}$, thus as $m\to \infty$ we obtain $u^\varepsilon(x) \geq -\lambda^{-1}C_2$ for all $x\in \Omega$.
+
+\begin{thm}[Qualitative result]\label{thm:qual} Assume $\mathrm{(A1)}$.
+Let $u^\varepsilon$ be the solution to \eqref{eq:PDEeps}, then there exists $u^0 \in \mathrm{C}(\overline{\Omega})$ such that $u^\varepsilon \rightarrow u^0$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$ and $u^0$ solves \eqref{eq:PDE0}.
+Furthermore
+\begin{equation*}
+    u^0 \leq u^\varepsilon \qquad\text{in}\;\Omega.
+\end{equation*}
+\end{thm}
+
+\begin{proof}[Proof of Theorem \ref{thm:qual}] By the priori estimate
+\begin{equation*}
+    |u^\varepsilon(x)| + |Du^\varepsilon(x)| \leq C_\delta \qquad\text{for}\;x\in \overline{\Omega}_\delta
+\end{equation*}
+we deduce from the Arzel\'a--Ascoli theorem that there exists a subsequence $\varepsilon_j\to 0$ and a function $u^0\in \rmC(\Omega)$ such that $u^{\varepsilon_j}\to u^0$ locally uniformly in $\Omega$.
+By the stability of viscosity solution we easily deduce that
+\begin{equation}\label{eq:u0int}
+   \lambda u^0(x) + H(x,Du^0(x)) = 0 \qquad\text{in}\;\Omega.
+\end{equation}
+Since $u^\varepsilon(x)\geq -C_2$ for all $x\in \Omega$ we also have $u^0(x)\geq -C_2$ for all $x\in \Omega$, thus together with \eqref{eq:u0int} we obtain $H(x,\xi) \leq C_2$ for all $\xi\in D^+u^0(x)$ and $x\in \Omega$.
+The coercivity $\mathrm{(H4)}$ implies that there exists $K>0$ such that
+\begin{equation*}
+    |u^0(x) - u^0(y)| \leq K \qquad\text{for all}\;x,y\in \Omega.
+\end{equation*}
+Thus we can extend $u^0$ uniquely to $u^0\in \rmC(\overline{\Omega})$.
+We will use Lemma \ref{lem:max} to show that $u^0$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$.
+It suffices to to show that $u^0\geq w$ on $\overline{\Omega}$ where $w\in \rmC(\overline{\Omega})$ is the unique solution to \eqref{eq:PDE0}.
+
+For $\delta>0$, let $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) < \delta\}$ and $v_\delta\in\rmC(\overline{\Omega}_\delta)$ be the state-constraint viscosity subsolution to the problem $\lambda u(x) + H(x,Du(x)) = 0$ in $\Omega_\delta$.
+As $v_\delta\rightarrow w$ locally uniformly as $\delta\rightarrow 0^+$ (see \cite{kim_state-constraint_2020}) and $w$ is bounded, therefore $\{v_\delta\}_{\delta>0}$ is uniformly bounded.
+Let $v^\varepsilon_\delta\in \rmC^2(\Omega_\delta)\cap \rmC(\overline{\Omega}_\delta)$ be the unique solution to the Dirichlet problem
+\begin{equation}\label{eq:vv_eps}
+\begin{cases}
+    \lambda v_\delta^\varepsilon(x) + |Dv_\delta^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v_\delta^\varepsilon(x) &\qquad\text{in}\;\Omega_\delta,\\
+    \;\;\;\,\quad\qquad\qquad\qquad\qquad v_\delta^\varepsilon = v_\delta &\qquad \text{on}\;\partial\Omega_\delta.
+\end{cases}
+\end{equation}
+For all $\delta$ small enough $v_\delta\leq u^\varepsilon$ on $\partial \Omega_\delta$, thus by maximum principle $v^\varepsilon_\delta \leq u^\varepsilon$ on $\overline{\Omega}_\delta$.
+Let $\varepsilon\to 0$ we have $v_\delta \leq u^0$ on $\overline{\Omega}_\delta$.
+Let $\delta\rightarrow 0$ we obtain $w\leq u^0$ in $\Omega$, which implies $w\leq u^0$ on $\overline{\Omega}$ since both $w,u^0$ belong to $\rmC(\overline{\Omega})$.
+\end{proof}
+
+\section{Rate of convergence via Doubling variables}
+\noindent Let $\Omega = B(0,1)$. Fix $\theta \in (0,1)$ to be chosen later, let us define
+\begin{align*}
+    \Psi^{\sigma}(x,y) = \theta u^\varepsilon(x) - u^0(y) - \frac{|x-y|^2}{\sigma}- \frac{C_0}{d(x)^\alpha}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega} 
+\end{align*}
+where $\sigma>0$ to be chosen later.
+
+\section{Rate of convergence via a simple idea}
+\noindent Let $\Omega = B(0,1)$, the scaling and distance near boundary are the same, i.e., $(1-\delta)\Omega = \Omega_\delta$.
+
+\noindent Let $u_\delta\in \rmC(\overline{\Omega}_\delta)$ be the state-constraint solution of the first-order equation, still $H(x,\varrho) = |\varrho|^p - f(x)$,
+\begin{equation*}
+    \begin{cases}
+    \lambda u_\delta(x) + H(x,Du_\delta(x)) \leq 0 &\qquad\text{in}\;(1-\delta)\Omega,\\
+    \lambda u_\delta(x) + H(x,Du_\delta(x)) \geq 0 &\qquad\text{on}\;(1-\delta)\overline{\Omega}.
+    \end{cases}
+\end{equation*}
+We know that the optimal rate of convergence of $u_\delta$ to $u^0$ is given by (\cite{kim_state-constraint_2020})
+\begin{equation*}
+    0\leq u_\delta - u^0 \leq C\delta
+\end{equation*}
+where $C$ depends on $H$ only (\textcolor{red}{check this}).
+
+\noindent Let $g_{\varepsilon,\delta}(x) = u^\varepsilon(x)$ for $x\in \partial\Omega_\delta$ which is finite.
+We have $u_\delta\leq g_{\varepsilon,\delta}$ for all $\varepsilon$ and also for each fixed $\delta>0$ then
+\begin{equation*}
+    \lim_{\varepsilon\to 0} g_{\varepsilon,\delta}(x) = u_\delta(x).
+\end{equation*}
+On the domain $\Omega_\delta$, we consider the problem
+\begin{equation*}
+    \begin{cases}
+    \mathcal{L}[v^\varepsilon] = 0 &\qquad\text{in}\;\Omega_\delta,\\
+    v^\varepsilon = g_{\delta,\varepsilon} &\qquad\text{on}\;\partial\Omega_\delta.
+    \end{cases}
+\end{equation*}
+Question: can we quantify $\Vert v^\varepsilon - u_\delta\Vert_{L^\infty}$ in term of $\varepsilon$?
+
+\section{Rate of convergence via nonlinear adjoint method}
+
+%\nocite{*}
+
+\section{Questions and Ideas}
+\begin{quest} [Jan 12, 2021] Why do we use the distance functions to get boundary estimates? 
+\end{quest}
+
+\begin{quest} [Jan 13, 2021] Maximum principle for sub-quadratic case.
+\end{quest}
+
+\begin{quest}[Jan 20, 2021] Here is an idea to estimate $\Vert u^\varepsilon - u^0\Vert_{L^\infty_{loc}(\Omega)}$. We start first by assuming star-shaped and consider
+\begin{equation}\label{e:S_eta}
+    \begin{cases}
+    \lambda u_\eta^\varepsilon(x) + H(x,Du_\eta^\varepsilon(x)) - \varepsilon \Delta u_\eta^\varepsilon(x) = 0 &\qquad
+    \text{in}\;(1-\eta)\Omega, \vspace{0cm}\\
+    \qquad\qquad\qquad\qquad\qquad\qquad\;\, u^\varepsilon_\eta(x) = +\infty &\qquad
+    \text{on}\;(1-\eta)\partial\Omega.
+    \end{cases} \tag{$S_\eta$}
+\end{equation}
+Can we estimate $0\leq u^\varepsilon_\eta - u^\varepsilon \leq \omega(\varepsilon,\eta)$ and then chose $\eta = \omega'(\varepsilon)$ to conclude?
+One way is to approximate infinity boundary by finite boundary first, it may be too naive, but whatever!
+\begin{equation}\label{e:S_eta_m}
+    \begin{cases}
+    \lambda v_\eta^\varepsilon(x) + H(x,Dv_\eta^\varepsilon(x)) - \varepsilon \Delta v_\eta^\varepsilon(x) = 0 &\qquad
+    \text{in}\;(1-\eta)\Omega, \vspace{0cm}\\
+    \qquad\qquad\qquad\qquad\qquad\qquad\;\, v^\varepsilon_\eta(x) = m &\qquad
+    \text{on}\;(1-\eta)\partial\Omega.
+    \end{cases} \tag{$S_{\eta}^m$}
+\end{equation}
+In contrast, let us consider
+\begin{equation}\label{e:S_0}
+    \begin{cases}
+    \lambda v^\varepsilon(x) + H(x,Dv^\varepsilon(x)) - \varepsilon \Delta v^\varepsilon(x) = 0 &\qquad
+    \text{in}\;\Omega, \vspace{0cm}\\
+    \qquad\qquad\qquad\qquad\qquad\qquad\;\, v^\varepsilon(x) = m &\qquad
+    \text{on}\;\partial\Omega.
+    \end{cases} \tag{$S^m$}
+\end{equation}
+How can we compare $v^\varepsilon$ and $v^\varepsilon_\eta$?
+\end{quest}
+
+\begin{appendices}
 
@@
 \end{equation}
-we want to show the smooth dependence of $u^\epsilon$ on $\epsilon$.
+where  $H(x,p)$ is $C^\infty(\overline{U}\times \mathbb{R}^n)$, $\displaystyle \frac{H(x,p)}{|p|} \to \infty$ uniformly in $x$ as $|p| \to \infty$ and $\displaystyle \sup_{x\in U}|D_xH(x,p)|\leq C(1+|p|)$, we want to show the smooth dependence of $u^\epsilon$ on $\epsilon$.
 Formally, if we differentiate \eqref{dir} with respect to $\epsilon$, we get
@@
 \end{equation}
-By Schaefer's fixed point theorem and the maximal principle, $u^\epsilon_\epsilon$ is the unique solution in $C^2(\overline{U})$ of \eqref{dir_dif} \textcolor{orange}{(needs double check)}.
-The main idea is, we look at the difference quotients $\displaystyle \frac{u^{\epsilon+h}-u^\epsilon}{h}$and prove that as $h \to 0^+$, they converge to a limiting function $w^{\ast}$ in the uniform norm \textcolor{orange}{(maybe weaker convergence is fine)} such that $w^{\ast}$ solves \eqref{dir_dif}.
+By Schaefer's fixed point theorem and the maximal principle, $u^\epsilon_\epsilon$ is the unique solution in $C^{2,\alpha}(\overline{U})$ of \eqref{dir_dif}.
+
+\noindent The main idea is, we look at the difference quotients $\displaystyle \frac{u^{\epsilon+h}-u^\epsilon}{h}$and prove that as $h \to 0^+$, they converge to a limiting function $w^{\ast}$ in the uniform norm  such that $w^{\ast}$ solves \eqref{dir_dif}.
 Since \eqref{dir_dif} has a unique solution, we have $$u^\epsilon_\epsilon=\lim_{h \to 0^+}\frac{u^{\epsilon+h}-u^\epsilon}{h}.$$
 
-Fix $\epsilon >0$. Let $$w^h(x):=\frac{u^{\epsilon+h}(x)-u^\epsilon(x)}{h} \in C^2(\overline{U}).$$
+\subsection{Solution $u^\epsilon \in C^{2,\alpha}(\overline{U})$ exists} We use Schaufer's fixed point theorem as follows.
 
-A little computation will show that $w^h$ solves
+\begin{thm} Suppose $X$ is a Banach space.
+Let $A:X \to X$ be continuous and compact.
+Assume the set $\{u\in X : u=\lambda A[u]$ for some $0 \leq  \lambda \leq 1\}$ is bounded.
+Then $A$ has a fixed point $u =A[u]$.
+\end{thm}
+\noindent Fix $0<\alpha<1$. Let $X=C^{1,\alpha}(\overline{U})$. Given $u \in X=C^{1,\alpha}(\overline{U})$, we look at the linear PDE
+\begin{equation}
+\label{fix}
+\left\{
+  \begin{aligned}
+   \epsilon \Delta v &= H(x, Du) \quad \, \text{in } U, \\
+              v &= 0 \qquad \qquad \text{on } \partial U.
+  \end{aligned}
+\right.
+\end{equation}
+\noindent
+Estimate the Holder norm of RHS
+$$\|H(x, Du)\|_{C^{0, \alpha}(\overline{U})}:=\sup_{x\in\overline{U}} |H(x,Du(x))| + \sup_{x, y \in \overline{U}}\frac{|H(x, Du(x))-H(y, Du(y))|}{|x-y|^\alpha}.$$
+Since $Du$ is bounded and H is smooth,
+\begin{equation}
+    \sup_{x\in\overline{U}} |H(x,Du(x))| \leq C.
+\end{equation}
+
+\begin{equation}
+    \begin{aligned}
+  &\sup_{x, y \in \overline{U}}\frac{|H(x, Du(x))-H(y, Du(y))|}{|x-y|^\alpha}\\
+  \leq &  \sup_{x, y \in \overline{U}}\frac{|H(x, Du(x))-H(y, Du(x))|}{|x-y|^\alpha} + \sup_{x, y \in \overline{U}}\frac{|H(y, Du(x))-H(y, Du(y))|}{|x-y|^\alpha} \\
+  =&    \sup_{x, y \in \overline{U}}\frac{|\int_0^1D_xH(y+\theta (x-y), Du(x))d\theta \cdot (x-y)|}{|x-y|^\alpha}\\& +
+     \sup_{x, y \in \overline{U}}\frac{|\int_0^1D_pH(y, Du(y)+\theta (Du(x)-Du(y)))d\theta \cdot (Du(x)-Du(y))|}{|x-y|^\alpha}\\
+  \leq &  C\sup_{x, y \in \overline{U}} (1+|Du(x)|)|x-y|^{1-\alpha} +  C \sup_{x, y \in \overline{U}}\frac{| (Du(x)-Du(y))|}{|x-y|^\alpha}\\
+ \leq & C(1 + \|u\|_{C^{1,\alpha}(\overline{U})})
+    \end{aligned}
+\end{equation}
+since $Du$ is bounded on $\overline{U}$, $D_pH \in C^\infty (\overline{U} \times \mathbb{R}^n)$ and
+$\displaystyle \sup_{x\in U}|D_xH(x,p)|\leq C(1+|p|)$. Therefore,
+\begin{equation}
+ \|H(x, Du)\|_{C^{0, \alpha}(\overline{U})} \leq C(1 + \|u\|_{C^{1,\alpha}(\overline{U})}).
+\end{equation}
+By Schauder estimates, there exists a unique solution $v \in C^{2,\alpha }(\overline{U})$ such that
+\begin{equation}
+\label{schauder}
+    \|v\|_{C^{2, \alpha}(\overline{U})} \leq C  \|H(x, Du)\|_{C^{0, \alpha}(\overline{U})}. 
+\end{equation}
+\noindent Define operator $A$ on $X := C^{1, \alpha} (\overline{U}) $ by $A[u]=v$. So 
+\begin{equation}
+     \|A[u]\|_{C^{2, \alpha}(\overline{U})} \leq C(1 + \|u\|_{C^{1,\alpha}(\overline{U})}),
+\end{equation}
+\noindent
+ and thus $A$ is continuous and compact.
+(i.e., if $\{u_k\}_{k=1}^\infty$ is bounded in $X=C^{1, \alpha}(\overline{U})$, then $\{A[u_k]\}_{k=1}\infty$ is bounded in $C^{2,\alpha} (\overline{U})$, thus precompact in $C^{1, \alpha}(\overline{U})$.
+Lemma 6.36 in Gilbarg and Trudinger.
+)
+
+ Next we try to bound $\{u\in X : u=\lambda A[u]$ for some $0 \leq  \lambda \leq 1\}$.
+ If $u=\lambda A[u]$, the PDE becomes
+
+\begin{equation}
+\label{lamb}
+\left\{
+  \begin{aligned}
+   \epsilon \Delta u &= \lambda H(x, Du) \quad \, \text{in } U, \\
+              u &= 0 \qquad \qquad \text{on } \partial U.
+  \end{aligned}
+\right.
+\end{equation}
+
+Calderon-Zygmund estimates tell us that if we have
+\begin{equation}
+\label{cald}
+\left\{
+  \begin{aligned}
+  - \Delta v &=\Tilde{f}   \qquad \, \text{in } U, \\
+              v &= 0 \qquad \text{on } \partial U.
+  \end{aligned}
+\right.
+\end{equation}
+
+and $\Tilde{f} \in {L^p(U)}$ for some $p\in (1, \infty)$, then $v \in W^{2,p}(U)$ and $$\|v\|_{w^{2,p}(U)} \leq C\|\Tilde{f}\|_{L^p(U)}.$$
+
+Apply to \eqref{lamb} and we get
+
+\begin{equation}
+    \|u\|_{w^{2,p}(U)} \leq C\|H(x, Du)\|_{L^p(U)}
+\end{equation}
+
+(We want RHS to be bounded by some constant so that later we can choose $p$ larger than $n$ to  conclude $ \|u\|_{C^{1, \alpha}(U)} \leq   C\|u\|_{w^{2,p}(U)} \leq C$ by Morrey's estimate.) By a priori estimate, if we assume the solution of \eqref{dir} $u$ exists, then $\| Du\|_{L^\infty} \leq C_0$ where $C_0$ is independent of $\epsilon$.
+We can modify $H$ to get a new $\Tilde{H}$ so that it is smooth, $\Tilde{H} = H$ for $|p|<C_1$ and $H(x,p)=C_1+1$ for $|p|>C_1+1$ for some constant $C_1$ ($C_1$ is definitely larger than $C^0$).
+Moreover, the same prior estimate is correct for $\Tilde{H}$.
+Namely, if the solution $\Tilde{u}$ to \eqref{dir} with $H$ replaced by $\Tilde{H}$ exists, then $\| D\Tilde{u}\|_{L^\infty} \leq C_0$.
+(The way we choose this $C_1$ is that we work back from the beginning of the proof of a priori estimate for $u$, on both the boundary and interior of $\Omega$, and modify $H$ so that all the proofs go through and the same a priori estimate holds for the equation with $\Tilde{H}$.) Now with $\Tilde{H}$, we go through the same argument of Schaufer's fixed point theorem from the very beginning, and \eqref{cald} reads
+\begin{equation}
+       \|\Tilde{u}\|_{w^{2,p}(U)} \leq C\|\Tilde{H}(x, D\Tilde{u})\|_{L^p(U)} \leq C(1+\|D\Tilde{u}\|_{L^\infty}) \leq C.
+\end{equation}
+
+Choose $p=2n$ and $\displaystyle \alpha =\frac{1}{2}$. We have $\{\Tilde{u}\in X : \Tilde{u}=\lambda A[\Tilde{u}]$ for some $0 \leq  \lambda \leq 1\}$ is bounded in $X= C^{1, \frac{1}{2}}(
+\overline{U})$.
+Thus Schaefer's fixed point theorem implies the equation \eqref{dir} with $H$ replaced by $\Tilde{H}$ has a solution $\Tilde{u} \in C^{2,\alpha} (\overline{\Omega})$.
+Since $\| D\Tilde{u}\|_{L^\infty} \leq C_0$, $\Tilde{u}$ also solves the original equation \eqref{dir}.
+
+\subsection{Uniqueness}
+Let $u$ and $v$ be two solutions to \eqref{dir} and $w := u-v$. Then we have
+\begin{equation}
+\begin{aligned}
+    &-\epsilon \Delta (u-v) = H(x, Dv)-H(x, Du)\\
+    \Rightarrow &-\epsilon \Delta w   =\int_0^1 D_pH(x, tDv+(1-t)Du) \cdot (Dv-Du)dt\\
+    \Rightarrow &-\epsilon \Delta w  +\int_0^1 D_pH(x, tDv+(1-t)Du)dt \cdot Dw = 0.
+\end{aligned}
+\end{equation}
+By the strong maximum principle, $w \equiv 0$.
+
+\subsection{Smooth dependence on $\epsilon$}
+Fix $\epsilon >0$. Let  $$w^h(x):=\frac{u^{\epsilon+h}(x)-u^\epsilon(x)}{h} \in C^{2,\alpha}(\overline{U}).$$
+
+A little computation shows that $w^h$ solves
 
@@
 \end{equation}
-Heuristically, we see as $h \to 0^+$, \eqref{dir_quo} "converges" to \eqref{dir_dif}.
 
-\textcolor{orange}{Still thinking about how to show $w^h$ converges uniformly as $h \to 0^+$.
-I am tring to show $\| w^h-w^\ast\|_\infty \to 0$ by looking at the equation solved by $v^h:=w^h-w^\ast$.
-More to fill in...}
+From the existence proof, we know $\|u^\epsilon\|_{C^{2,\alpha}(\overline{U})} \leq C$ uniformly in $\epsilon$.
+So $\|Du^{\epsilon+h}-Du^\epsilon\|_{C^{0,\alpha}(\overline{U})}$and $\|\Delta u\|_{C^{0,\alpha}(\overline{U})}
+$ is uniformly bounded in $h$.
+
+By Schauder estimates, $\{w^h\}_{h>0} \subset C^{2, \alpha}(\overline{U})$ are bounded, hence is precompact in $ C^{2, \beta}(\overline{U})$ for any $\beta < \alpha$.
+Therefore, there exits a subsequence $\{w^{h_j}\}_{j=1}^\infty$ such that $w^{h_j} \to w^\ast$ for some $w^\ast \in  C^{2, \beta}(\overline{U}) $ and $w^\ast$ solves \eqref{dir_dif}.
+This implies $w^h \to w^\ast$ in $C^{2, \beta}(\overline{U})$.
+
+\section{Proofs of some Lemmas and Propositions}
+\begin{proof}[Proof of Lemma \ref{lem:max}] The proof is a variation of Perron's method (see \cite{Capuzzo-Dolcetta1990}).
+Let $\varphi\in \rmC(\overline{\Omega})$ and $x_0\in \overline{\Omega}$ such that $u(x_0) = \varphi(x_0)$ and $u-\varphi$ has a global strict minimum over $\overline{\Omega}$ at $x_0$ and that
+\begin{equation}\label{eq:max_a1}
+    \lambda \varphi(x_0) + H(x_0,D\varphi(x_0)) < 0.
+\end{equation}
+Let $\varphi^\varepsilon(x) = \varphi(x) - |x-x_0|^2 + \varepsilon$ for $x\in \overline{\Omega}$. Let $\delta > 0$, we see that for $x\in \partial B(x_0,\delta)\cap \overline{\Omega}$ then
+\begin{equation*}
+    \varphi^\varepsilon(x) = \varphi(x) - \delta^2 +\varepsilon \leq \varphi(x) - \varepsilon
+\end{equation*}
+if $2\varepsilon \leq \delta^2$. We observe that
+\begin{equation*}
+    \begin{split}
+    \varphi^\varepsilon(x) - \varphi(x_0)  &= \varphi(x)-\varphi(x_0) + \varepsilon - |x-x_0|^2 \\
+    D\phi^\varepsilon(x) - D\phi(x_0) &= D\varphi(x) - D\varphi(x_0) - 2(x-x_0)
+    \end{split}
+\end{equation*}
+for $x\in B(x,\delta)\cap \overline{\Omega}$.
+We deduce from \eqref{eq:max_a1}, the continuity of $H(x,p)$ near $(x_0,D\varphi(x_0))$ and the fact that $\varphi\in \rmC^1(\overline{\Omega})$ that if $\delta$ is small enough and $0<2\varepsilon < \delta^2$ then
+\begin{equation}\label{eq:max_a2}
+    \lambda \varphi^\varepsilon(x)+H(x,D\varphi^\varepsilon(x)) < 0 \qquad\text{for}\;x\in B(x_0,\delta)\cap \overline{\Omega}.
+\end{equation}
+We have found $\phi^\varepsilon\in \mathrm{C}^1(\overline{\Omega})$ such that $\varphi^\varepsilon(x_0)>u(x_0)$, $\varphi^\varepsilon<u$ on $\partial B(x_0,\delta)\cap \overline{\Omega}$ and \eqref{eq:max_a2}.
+Let
+\begin{equation*}
+    \tilde{u}(x) = \begin{cases}
+    \max \big\lbrace u(x),\phi^\varepsilon(x) \big\rbrace &x\in B(x_0,\delta)\cap \overline{\Omega},\\
+    u(x)&x\notin B(x_0,\delta)\cap \overline{\Omega},\\
+    \end{cases}
+\end{equation*}
+We see that $\tilde{u}\in \rmC(\overline{\Omega})$ is a subsolution of \eqref{S_0} in $\Omega$ with $\tilde{u}(x_0) > u(x_0)$, which is a contradiction, thus $u$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$.
+\end{proof}
 

### 2021-01-27 Drafts and notes/Old_draft_02.tex
Added Construction

--- 2021-01-17 Drafts and notes/Draft.tex
@@
 
-Let $\Omega$ be an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$.
-Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$.
-Let $u^\varepsilon$ be the solution to
+Let $\Omega$ be an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$. Let us consider the following Hamiltonian
+\begin{equation*}
+    H(x,\varrho) = |\varrho|^p-f(x), \qquad (x,p)\in \overline{\Omega}\times \mathbb{R}^n
+\end{equation*}
+where $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$. Let $u^\varepsilon$ be the solution to 
 \begin{equation}\label{eq:PDE}
     \begin{cases}
-    \lambda u^\varepsilon(x) + |Du^\varepsilon(x)|^p - f(x) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
+    \lambda u^\varepsilon(x) + H(x,Du^\varepsilon(x)) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
     \text{in}\;\Omega, \vspace{0cm}\\
@@
 We are interested in studying the asymptotic behavior of $\{u^\varepsilon\}_{\varepsilon>0}$ as the vanishing viscosity happens: $\varepsilon\rightarrow 0$.
+The viscosity formulation of the corresponding state-constraint first order is
+\begin{equation}\label{eq:1st}
+    \begin{cases}
+     \lambda u(x) + H(x,Du(x)) \leq 0\;\qquad\text{in}\;\Omega,\\
+     \lambda u(x) + H(x,Du(x)) \geq 0\;\qquad\text{on}\;\overline{\Omega}.
+    \end{cases}
+\end{equation}
+Equation \eqref{eq:1st} admits a unique viscosity solution in the space $\rmC(\overline{\Omega})$, which is also the maximal viscosity subsolution among all viscosity subsolution $v\in\rmC(\overline{\Omega})$.
+However, with unbounded solutions the situation is unclear.
 
@@
 
-Let $u^\varepsilon$ be the solution to \eqref{eq:PDE}, we observe that if$u^\varepsilon\rightarrow u^0$ uniformly on compact subsets of $\Omega$, we see that $u(x)\rightarrow +\infty$ as $\mathrm{dist}(x,\partial \Omega)\to 0$ as well, therefore the limiting solution is not the state-constraint solution to a limiting first order equation.
+Let $u^\varepsilon$ be the solution to \eqref{eq:PDE}, we observe that if $u^\varepsilon\rightarrow u^0$ uniformly on compact subsets of $\Omega$, we see that $u(x)\rightarrow +\infty$ as $\mathrm{dist}(x,\partial \Omega)\to 0$ as well, therefore the limiting solution is not the state-constraint solution to a limiting first order equation.
 
@@
 \end{equation}
-such that, for all viscosity subsolution $v\in \rmC(\overline{\Omega})$ of \eqref{S_0} one has $v\leq u\in \overline{\Omega}$, then $u$ is a viscosity supersolution of \eqref{S_0} on $\overline{\Omega}$.
+such that, for all viscosity subsolution $v\in \rmC(\overline{\Omega})$ of \eqref{S_0} one has $v\leq u$ in $\overline{\Omega}$, then $u$ is a viscosity supersolution of \eqref{S_0} on $\overline{\Omega}$.
 \end{lem}
+\begin{proof} We review the proof using Perron's method (see \cite{Capuzzo-Dolcetta1990}).
+Let $\varphi\in \rmC(\overline{\Omega})$ and $x_0\in \overline{\Omega}$ such that $u(x_0) = \varphi(x_0)$ and $u-\varphi$ has a global strict minimum over $\overline{\Omega}$ at $x_0$ and that
+\begin{equation}\label{eq:max_a1}
+    \lambda \varphi(x_0) + H(x_0,D\varphi(x_0)) < 0.
+\end{equation}
+Let $\varphi^\varepsilon(x) = \varphi(x) - |x-x_0|^2 + \varepsilon$ for $x\in \overline{\Omega}$. Let $\delta > 0$, we see that for $x\in \partial B(x_0,\delta)\cap \overline{\Omega}$ then
+\begin{equation*}
+    \varphi^\varepsilon(x) = \varphi(x) - \delta^2 +\varepsilon \leq \varphi(x) - \varepsilon
+\end{equation*}
+if $2\varepsilon \leq \delta^2$. We observe that
+\begin{equation*}
+    \begin{split}
+    \varphi^\varepsilon(x) - \varphi(x_0)  &= \varphi(x)-\varphi(x_0) + \varepsilon - |x-x_0|^2 \\
+    D\phi^\varepsilon(x) - D\phi(x_0) &= D\varphi(x) - D\varphi(x_0) - 2(x-x_0)
+    \end{split}
+\end{equation*}
+for $x\in B(x,\delta)\cap \overline{\Omega}$.
+We deduce from \eqref{eq:max_a1}, the continuity of $H(x,p)$ near $(x_0,D\varphi(x_0))$ and the fact that $\varphi\in \rmC^1(\overline{\Omega})$ that if $\delta$ is small enough and $0<2\varepsilon < \delta^2$ then
+\begin{equation}\label{eq:max_a2}
+    \lambda \varphi^\varepsilon(x)+H(x,D\varphi^\varepsilon(x)) < 0 \qquad\text{for}\;x\in B(x_0,\delta)\cap \overline{\Omega}.
+\end{equation}
+We have found $\phi^\varepsilon\in \mathrm{C}^1(\overline{\Omega})$ such that $\varphi^\varepsilon(x_0)>u(x_0)$, $\varphi^\varepsilon<u$ on $\partial B(x_0,\delta)\cap \overline{\Omega}$ and \eqref{eq:max_a2}.
+Let
+\begin{equation*}
+    \tilde{u}(x) = \begin{cases}
+    \max \big\lbrace u(x),\phi^\varepsilon(x) \big\rbrace &x\in B(x_0,\delta)\cap \overline{\Omega},\\
+    u(x)&x\notin B(x_0,\delta)\cap \overline{\Omega},\\
+    \end{cases}
+\end{equation*}
+We see that $\tilde{u}\in \rmC(\overline{\Omega})$ is a subsolution of \eqref{S_0} in $\Omega$ with $\tilde{u}(x_0) > u(x_0)$, which is a contradiction, thus $u$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$.
+\end{proof}
 
@@
 Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$.
-Let $u^\varepsilon$ be the solution to \eqref{eq:PDE}, then $u^\varepsilon \rightarrow u$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$ and $u$ solves
+Let $u^\varepsilon$ be the solution to \eqref{eq:PDE}, then $u^\varepsilon \rightarrow u^0$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$ and $u^0$ solves
 \begin{equation}\label{eq:PDE0}
     \begin{cases}
-    \lambda u(x) + |Du(x)|^p - f(x) \leq 0 \qquad\text{in}\;\Omega,\\
-    \lambda u(x) + |Du(x)|^p - f(x) \geq 0 \qquad\text{on}\;\overline{\Omega}.
-    \end{cases}\tag{PDE$_0$}   
+    \lambda u(x) + |Du(x)|^p - f(x)=  0 \qquad\text{in}\;\Omega, \vspace{0cm}\\
+    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^0(x) = +\infty.
+    \end{cases} \tag{PDE$_0$}
 \end{equation}
@@
 \end{equation*}
-The real difficulty is describing what is the behavior of $u^0$ on the boundary. As we expect it to solves \eqref{eq:PDE0}, it should be the maximal subsolution (hence, solution) to 
+The real difficulty is describing what is the behavior of $u^0$ on the boundary. It is clear that
+\begin{equation*}
+    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^0(x) = +\infty.
+\end{equation*}
+
+In fact, for each $x_0\in \partial \Omega$, let $\Vec{\mathfrak{n}}(x_0)$ be the unit outward normal vector, consider $x_s = x_0 - s\Vec{\mathfrak{n}}(x_0)$ for $s>0$.
+For each $j\in \mathbb{N}$ there holds $\lim_{s\to 0} u^\varepsilon(x_s) = +\infty$, therefore we can find a subsequence $s_j \to 0$ such that
+\begin{equation*}
+    u^\varepsilon(x_{s_j}) \geq \tfrac{1}{\varepsilon_j}.
+\end{equation*}
+\vspace{2cm}
+
+As we expect it to solves \eqref{eq:PDE0}, it should be the maximal subsolution (hence, solution) to 
 \begin{equation}\label{eq:S_lambda}
@@
 \color{black}
+
+\begin{lem} If $\delta$ is small enough then $u^0$ is a supersolution of \eqref{S_0} on $\overline{\Omega}_\delta$.
+\end{lem}
+\begin{proof} For $\delta>0$, let us denote $v_\delta\in\rmC(\overline{\Omega}_\delta)$ be the state-constraint viscosity subsolution to the problem $\lambda u(x) + H(x,Du(x)) = 0$ in $\Omega_\delta$, then by Lemma  \ref{lem:max} we have
+\begin{equation}\label{eq:les1}
+   u^0(x) \leq v_\delta(x) \qquad\text{for}\;x\in \overline{\Omega}_\delta
+\end{equation}
+since $u^0 \in \rmC(\overline{\Omega}_\delta)$ is a viscosity (sub)solution to $\lambda u(x) + H(x,Du(x)) = 0$ in $\Omega_\delta$.
+Let us denote $v^\varepsilon\in \rmC^2(\Omega_\delta)\cap \rmC(\overline{\Omega}_\delta)$ as the unique solution to the Dirichlet problem
+\begin{equation}\label{eq:vv_eps}
+\begin{cases}
+    \lambda v^\varepsilon(x) + |Dv^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v^\varepsilon(x) &\qquad\text{in}\;\Omega_\delta,\\
+    \;\;\,\quad\quad\qquad\qquad\qquad\qquad v^\varepsilon = v_\delta &\qquad \text{on}\;\partial\Omega_\delta.
+\end{cases}
+\end{equation}
+Comparing $u^\varepsilon$ and $v^\varepsilon$ on $\overline{\Omega}_\delta$, for $\delta$ small enough we have $v_\delta\leq u^\varepsilon$ on $\partial \Omega_\delta$, thus by comparison principle for \eqref{eq:vv_eps} we obtain that $v^\varepsilon \leq u^\varepsilon$ on $\overline{\Omega}_\delta$, thus as $\varepsilon\to 0$ we have
+\begin{equation}\label{eq:les2}
+    v_\delta(x) \leq u^0(x)  \qquad\text{for}\;x\in \overline{\Omega}_\delta.
+\end{equation}
+From \eqref{eq:les1} and \eqref{eq:les2} we deduce that $v_\delta = u^0$ on $\overline{\Omega}_\delta$.
+\end{proof}
 

### 2021-01-27 Drafts and notes/Old_draft_03.tex
Added Construction

--- 2021-01-27 Drafts and notes/Old_draft_02.tex
@@
 \subsection{Convergence result}
-Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$. Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$.
+Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$.
+Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$.
+\vspace{0.2cm}
 
-Let $u^\varepsilon$ be the solution to \eqref{eq:PDE}, we observe that if $u^\varepsilon\rightarrow u^0$ uniformly on compact subsets of $\Omega$, we see that $u(x)\rightarrow +\infty$ as $\mathrm{dist}(x,\partial \Omega)\to 0$ as well, therefore the limiting solution is not the state-constraint solution to a limiting first order equation.
+\color{blue} 
+\paragraph{\underline{\textbf{Double check!
+Contradiction appears!}}} Let $u^\varepsilon$ be the solution to \eqref{eq:PDE}, we observe that if $u^\varepsilon\rightarrow u^0$ uniformly on compact subsets of $\Omega$, we see that $u(x)\rightarrow +\infty$ as $\mathrm{dist}(x,\partial \Omega)\to 0$ as well, therefore the limiting solution is not the state-constraint solution to a limiting first order equation.
+\color{black}
 
@@
 
-\begin{thm}[Qualitative result] Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$.
-Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$.
-Let $u^\varepsilon$ be the solution to \eqref{eq:PDE}, then $u^\varepsilon \rightarrow u^0$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$ and $u^0$ solves
-\begin{equation}\label{eq:PDE0}
+\begin{lem} Assume $u^{\varepsilon_j}\rightarrow u^0$ locally uniformly and let $w\in \rmC(\overline{\Omega})$ be the unique solution to 
+\begin{equation*}
     \begin{cases}
-    \lambda u(x) + |Du(x)|^p - f(x)=  0 \qquad\text{in}\;\Omega, \vspace{0cm}\\
-    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^0(x) = +\infty.
-    \end{cases} \tag{PDE$_0$}
-\end{equation}
-\end{thm}
+    \lambda w(x)  + H(x,Dw(x)) \leq 0 \qquad\text{in}\;\Omega,\\
+    \lambda w(x)  + H(x,Dw(x)) \geq 0 \qquad\text{on}\;\overline{\Omega}.
+    \end{cases}
+\end{equation*}
+We have $u^0(x)\geq u(x)$ for $x\in \Omega$.
+\end{lem}
+\begin{proof} For $\delta>0$, let $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) < \delta\}$ and $v_\delta\in\rmC(\overline{\Omega}_\delta)$ be the state-constraint viscosity subsolution to the problem $\lambda u(x) + H(x,Du(x)) = 0$ in $\Omega_\delta$.% If $\delta$ is small enough then $u^0$ is a supersolution of \eqref{S_0} on $\overline{\Omega}_\delta$.
 
-\color{blue}
-\begin{proof} (\textit{Added on Jan 16, 2021 - Heuristic idea}) Assume that we can get some sort of equi-continuity of the family $\{u^\varepsilon\}_{\varepsilon>0}$ in a local way, that is, for any compact sub-domain $\Omega'\subset\subset \Omega$ there is a constant $C(\Omega')$ such that
-\begin{equation}\label{eq:bound}
-    \Vert u^\varepsilon\Vert_{L^\infty(\Omega')} +\Vert Du^\varepsilon\Vert_{L^\infty(\Omega')} \leq C(\Omega').
-\end{equation}
-This should be done using Berstein's method (fill in later, and as $u$ blows up on $\partial \Omega$, this bound \eqref{eq:bound} may not be improved).
-Now let us assume via some subsequence $\varepsilon_j\to 0$ we have $u^{\varepsilon_j}\rightarrow u^0$ uniformly on compact subsets of $\Omega$, the interior stability of viscosity solution should yield us that
-\begin{equation*}
-    \lambda u^0(x) + |Du^0(x)|^p - f(x) = 0 \qquad\text{in}\;\Omega.
-\end{equation*}
-The real difficulty is describing what is the behavior of $u^0$ on the boundary. It is clear that
-\begin{equation*}
-    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^0(x) = +\infty.
-\end{equation*}
-
-In fact, for each $x_0\in \partial \Omega$, let $\Vec{\mathfrak{n}}(x_0)$ be the unit outward normal vector, consider $x_s = x_0 - s\Vec{\mathfrak{n}}(x_0)$ for $s>0$.
-For each $j\in \mathbb{N}$ there holds $\lim_{s\to 0} u^\varepsilon(x_s) = +\infty$, therefore we can find a subsequence $s_j \to 0$ such that
-\begin{equation*}
-    u^\varepsilon(x_{s_j}) \geq \tfrac{1}{\varepsilon_j}.
-\end{equation*}
-\vspace{2cm}
-
-As we expect it to solves \eqref{eq:PDE0}, it should be the maximal subsolution (hence, solution) to 
-\begin{equation}\label{eq:S_lambda}
-    \lambda u(x) + |Du(x)|^p - f(x) = 0 \qquad\text{in}\;\Omega.
-\end{equation}
-Let $v^\varepsilon\in \rmC^2(\Omega)\cap \rmC(\overline{\Omega})$ be the unique solution to the Dirichlet problem
-\begin{equation}\label{eq:v_eps}
-\begin{cases}
-    \lambda v^\varepsilon(x) + |Dv^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v^\varepsilon(x) &\qquad\text{in}\;\Omega,\\
-    \;\;\,\quad\quad\qquad\qquad\qquad\qquad v^\varepsilon = u &\qquad \text{on}\;\partial\Omega.
-\end{cases}
-\end{equation}
-where $u\in \rmC(\overline{\Omega})$ is the unique solution of \eqref{eq:PDE0}. Note that $v^\varepsilon\rightarrow v^0$ solves the corresponding Dirichlet problem
-\begin{equation}\label{eq:v_0}
-\begin{cases}
-    \lambda v^0(x) + |Dv^0(x)|^p - f(x) = 0 &\qquad\text{in}\;\Omega,\\
-    \;\;\,\quad\quad\qquad\qquad\qquad\qquad v^0 = u &\qquad \text{on}\;\partial\Omega.
-\end{cases}
-\end{equation}
-\begin{lem} $v^0\equiv u$ as the unique solution to \eqref{eq:PDE0}.
-\end{lem}
-\begin{proof} We observe that $u$ solves \eqref{eq:PDE0} is the unique solution to the Dirichlet problem \eqref{eq:v_0} as well, thus $v^0 \equiv u$ by comparison principle.
-\end{proof}
-\noindent By comparison principle, we see that
-\begin{equation*}
-    v^\varepsilon(x)\leq u^\varepsilon(x) \qquad\text{for}\;x\in \Omega.
-\end{equation*}
-Let $\varepsilon\to 0$, we deduce that
-\begin{equation*}
-    u(x)\leq u^0(x) \qquad\text{for}\;x\in \Omega.
-\end{equation*}
-\end{proof}
-\color{black}
-
-\begin{lem} If $\delta$ is small enough then $u^0$ is a supersolution of \eqref{S_0} on $\overline{\Omega}_\delta$.
-\end{lem}
-\begin{proof} For $\delta>0$, let us denote $v_\delta\in\rmC(\overline{\Omega}_\delta)$ be the state-constraint viscosity subsolution to the problem $\lambda u(x) + H(x,Du(x)) = 0$ in $\Omega_\delta$, then by Lemma  \ref{lem:max} we have
-\begin{equation}\label{eq:les1}
-   u^0(x) \leq v_\delta(x) \qquad\text{for}\;x\in \overline{\Omega}_\delta
-\end{equation}
-since $u^0 \in \rmC(\overline{\Omega}_\delta)$ is a viscosity (sub)solution to $\lambda u(x) + H(x,Du(x)) = 0$ in $\Omega_\delta$.
-Let us denote $v^\varepsilon\in \rmC^2(\Omega_\delta)\cap \rmC(\overline{\Omega}_\delta)$ as the unique solution to the Dirichlet problem
+As $v_\delta\rightarrow w$ locally uniformly as $\delta\rightarrow 0^+$ and $w$ is bounded, we see that $v_\delta$ is uniformly bounded.
+Let $v^\varepsilon\in \rmC^2(\Omega_\delta)\cap \rmC(\overline{\Omega}_\delta)$ be the unique solution to the Dirichlet problem
 \begin{equation}\label{eq:vv_eps}
@@
 \end{equation}
-Comparing $u^\varepsilon$ and $v^\varepsilon$ on $\overline{\Omega}_\delta$, for $\delta$ small enough we have $v_\delta\leq u^\varepsilon$ on $\partial \Omega_\delta$, thus by comparison principle for \eqref{eq:vv_eps} we obtain that $v^\varepsilon \leq u^\varepsilon$ on $\overline{\Omega}_\delta$, thus as $\varepsilon\to 0$ we have
+Since $v_\delta$ is bounded, for all $\delta$ small enough $v_\delta\leq u^\varepsilon$ on $\partial \Omega_\delta$, thus by maximum principle $v^\varepsilon \leq u^\varepsilon$ on $\overline{\Omega}_\delta$, hence as $\varepsilon\to 0$ we have
 \begin{equation}\label{eq:les2}
@@
 \end{equation}
-From \eqref{eq:les1} and \eqref{eq:les2} we deduce that $v_\delta = u^0$ on $\overline{\Omega}_\delta$.
+Let $\delta\rightarrow 0$ we obtain the conclusion $w(x)\leq u^0(x)$ for $x\in \Omega$.
 \end{proof}
+
+\begin{thm}[Qualitative result] Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$.
+Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$.
+Let $u^\varepsilon$ be the solution to \eqref{eq:PDE}, then $u^\varepsilon \rightarrow u^0$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$ and $u^0$ solves
+\begin{equation}\label{eq:PDE0}
+    \begin{cases}
+    \lambda u^0(x) + |Du^0(x)|^p - f(x)\leq  0 \qquad\text{in}\;\Omega, \\
+    \lambda u^0(x) + |Du^0(x)|^p - f(x)\geq  0 \qquad\text{on}\;\overline{\Omega}.
+    \end{cases}
+\end{equation}
+\end{thm}
 
@@
 
-To find candidate for subsolution and supersolution to \eqref{eq:PDE}, we use the ansatz
+\noindent To find candidate for subsolution and supersolution to \eqref{eq:PDE}, we use the ansatz
 \begin{equation}\label{eq:ansatz}
@@
 \end{equation}
-By Schaefer's fixed point theorem and the maximal principle, $u^\epsilon_\epsilon$ is the unique solution in $C^2(\overline{U})$ of \eqref{dir_dif} \textcolor{orange}{(needs double check)}.
-The main idea is, we look at the difference quotients $\displaystyle \frac{u^{\epsilon+h}-u^\epsilon}{h}$and prove that as $h \to 0^+$, they converge to a limiting function $w^{\ast}$ in the uniform norm \textcolor{orange}{(maybe weaker convergence is fine)} such that $w^{\ast}$ solves \eqref{dir_dif}.
+By Schaefer's fixed point theorem and the maximal principle, $u^\epsilon_\epsilon$ is the unique solution in $C^{2,\alpha}(\overline{U})$ of \eqref{dir_dif}.
+
+The main idea is, we look at the difference quotients $\displaystyle \frac{u^{\epsilon+h}-u^\epsilon}{h}$and prove that as $h \to 0^+$, they converge to a limiting function $w^{\ast}$ in the uniform norm  such that $w^{\ast}$ solves \eqref{dir_dif}.
 Since \eqref{dir_dif} has a unique solution, we have $$u^\epsilon_\epsilon=\lim_{h \to 0^+}\frac{u^{\epsilon+h}-u^\epsilon}{h}.$$
 
-Fix $\epsilon >0$. Let $$w^h(x):=\frac{u^{\epsilon+h}(x)-u^\epsilon(x)}{h} \in C^2(\overline{U}).$$
+\subsection{Solution $u^\epsilon \in C^{2,\alpha}(\overline{U})$ exists}
+We use Schaufer's fixed point theorem as follows.
 
-A little computation will show that $w^h$ solves
+\begin{thm}
+Suppose $X$ is a Banach space.
+Let $A:X \to X$ be continuous and compact.
+Assume the set $\{u\in X : u=\lambda A[u]$ for some $0 \leq  \lambda \leq 1\}$ is bounded.
+Then $A$ has a fixed point $u =A[u]$.
+\end{thm}
+
+Fix $0<\alpha<1$. Let $X=C^{1,\alpha}(\overline{U})$. Given $u \in X=C^{1,\alpha}(\overline{U})$, we look at the linear PDE
+\begin{equation}
+\label{fix}
+\left\{
+  \begin{aligned}
+   \epsilon \Delta v &= H(x, Du) \quad \, \text{in } U, \\
+              v &= 0 \qquad \qquad \text{on } \partial U.
+  \end{aligned}
+\right.
+\end{equation}
+
+Estimate the Holder norm of RHS
+$$\|H(x, Du)\|_{C^{0, \alpha}(\overline{U})}:=\sup_{x\in\overline{U}} |H(x,Du(x))| + \sup_{x, y \in \overline{U}}\frac{|H(x, Du(x))-H(y, Du(y))|}{|x-y|^\alpha}.$$
+Since $Du$ is bounded and H is smooth,
+\begin{equation}
+    \sup_{x\in\overline{U}} |H(x,Du(x))| \leq C.
+\end{equation}
+
+\begin{equation}
+    \begin{aligned}
+  &\sup_{x, y \in \overline{U}}\frac{|H(x, Du(x))-H(y, Du(y))|}{|x-y|^\alpha}\\
+  \leq &  \sup_{x, y \in \overline{U}}\frac{|H(x, Du(x))-H(y, Du(x))|}{|x-y|^\alpha} + \sup_{x, y \in \overline{U}}\frac{|H(y, Du(x))-H(y, Du(y))|}{|x-y|^\alpha} \\
+  =&    \sup_{x, y \in \overline{U}}\frac{|\int_0^1D_xH(y+\theta (x-y), Du(x))d\theta \cdot (x-y)|}{|x-y|^\alpha}\\& +
+     \sup_{x, y \in \overline{U}}\frac{|\int_0^1D_pH(y, Du(y)+\theta (Du(x)-Du(y)))d\theta \cdot (Du(x)-Du(y))|}{|x-y|^\alpha}\\
+  \leq &  C\sup_{x, y \in \overline{U}} (1+|Du(x)|)|x-y|^{1-\alpha} +  C \sup_{x, y \in \overline{U}}\frac{| (Du(x)-Du(y))|}{|x-y|^\alpha}\\
+ \leq & C(1 + \|u\|_{C^{1,\alpha}(\overline{U})})
+    \end{aligned}
+\end{equation}
+since $Du$ is bounded on $\overline{U}$, $D_pH \in C^\infty (\overline{U} \times \mathbb{R}^n)$ and
+$\displaystyle \sup_{x\in U}|D_xH(x,p)|\leq C(1+|p|)$.
+
+Therefore,
+\begin{equation}
+ \|H(x, Du)\|_{C^{0, \alpha}(\overline{U})} \leq C(1 + \|u\|_{C^{1,\alpha}(\overline{U})}).
+\end{equation}
+By Schauder estimates, there exists a unique solution $v \in C^{2,\alpha }(\overline{U})$ such that
+
+\begin{equation}
+\label{schauder}
+    \|v\|_{C^{2, \alpha}(\overline{U})} \leq C  \|H(x, Du)\|_{C^{0, \alpha}(\overline{U})}. 
+\end{equation}
+
+Define operator $A$ on $X := C^{1, \alpha} (\overline{U}) $ by $A[u]=v$.
+
+So 
+\begin{equation}
+     \|A[u]\|_{C^{2, \alpha}(\overline{U})} \leq C(1 + \|u\|_{C^{1,\alpha}(\overline{U})}),
+\end{equation}
+
+ and thus $A$ is continuous and compact.
+(i.e., if $\{u_k\}_{k=1}^\infty$ is bounded in $X=C^{1, \alpha}(\overline{U})$, then $\{A[u_k]\}_{k=1}\infty$ is bounded in $C^{2,\alpha} (\overline{U})$, thus precompact in $C^{1, \alpha}(\overline{U})$.
+Lemma 6.33 in Gilbarg and Trudinger.
+)
+
+ Next we try to bound $\{u\in X : u=\lambda A[u]$ for some $0 \leq  \lambda \leq 1\}$.
+ If $u=\lambda A[u]$, the PDE becomes
+
+\begin{equation}
+\label{lamb}
+\left\{
+  \begin{aligned}
+   \epsilon \Delta u &= \lambda H(x, Du) \quad \, \text{in } U, \\
+              u &= 0 \qquad \qquad \text{on } \partial U.
+  \end{aligned}
+\right.
+\end{equation}
+
+Calderon-Zygmund estimates tell us that if we have
+\begin{equation}
+\label{cald}
+\left\{
+  \begin{aligned}
+  - \Delta v &=\Tilde{f}   \qquad \, \text{in } U, \\
+              v &= 0 \qquad \text{on } \partial U.
+  \end{aligned}
+\right.
+\end{equation}
+
+and $\Tilde{f} \in {L^p(U)}$ for some $p\in (1, \infty)$, then $v \in W^{2,p}(U)$ and $$\|v\|_{w^{2,p}(U)} \leq C\|\Tilde{f}\|_{L^p(U)}.$$
+
+Apply to \eqref{lamb} and we get
+
+\begin{equation}
+    \|u\|_{w^{2,p}(U)} \leq C\|H(x, Du)\|_{L^p(U)}
+\end{equation}
+\textcolor{red}{(I want RHS to be bounded by some constant so that I can choose $p$ larger than $n$ to  conclude $ \|u\|_{C^{1, \alpha}(U)} \leq   C\|u\|_{w^{2,p}(U)} \leq C$ by Morrey's estimate.
+But with the assumption on $H$, I don't really know how to bound RHS.)}
+
+Choose $p=2n$ and $\displaystyle \alpha =\frac{1}{2}$. We have $\{u\in X : u=\lambda A[u]$ for some $0 \leq  \lambda \leq 1\}$ is bounded in $X= C^{1, \frac{1}{2}}(
+\overline{U})$.
+Thus Schaefer's fixed point theorem implies there exists a solution $u \in C^{2, \alpha}$ that solves \eqref{dir}.
+
+\subsection{Smooth dependence on $\epsilon$}
+Fix $\epsilon >0$. Let  $$w^h(x):=\frac{u^{\epsilon+h}(x)-u^\epsilon(x)}{h} \in C^{2,\alpha}(\overline{U}).$$
+
+A little computation shows that $w^h$ solves
 
@@
 \end{equation}
-Heuristically, we see as $h \to 0^+$, \eqref{dir_quo} "converges" to \eqref{dir_dif}.
+We want to bound $\{w^h\}_{h>0}$ in $C^{2, \alpha}(\overline{U})$ uniformly in $h$.
+(Then $\{w^h\}_{h>0}$ is precompact in  $C^{2, \gamma}(\overline{U})$ for $\gamma < \alpha$ and we can pass to limit.) Since the coefficients depend on $Du^{\epsilon+h}-Du^\epsilon$, in order to use Schauder/Calderon-Zygmond estimates, we need to bound the Holder norm of $Du^{\epsilon+h}-Du^\epsilon$ uniformly in h.
 
-\textcolor{orange}{Still thinking about how to show $w^h$ converges uniformly as $h \to 0^+$.
-I am tring to show $\| w^h-w^\ast\|_\infty \to 0$ by looking at the equation solved by $v^h:=w^h-w^\ast$.
-More to fill in...}
+If we look at the equation $u^{\epsilon +h} -u^\epsilon$ solves, i.e.,
+\begin{equation}
+\label{diff}
+\left\{
+  \begin{aligned}
+   \epsilon (\Delta u^{\epsilon+h}(x) -\Delta u^\epsilon(x) )+ h \Delta u^{\epsilon+h}&= \int_0^1 D_pH(x, Du^\epsilon+\theta (Du^{\epsilon+h}-Du^\epsilon)) d\theta \cdot D( u^{\epsilon+h}(x) - u^\epsilon(x)) \quad \, \text{in } U, \\
+              w^h &= 0 \quad \qquad \text{on } \partial U.
+  \end{aligned}
+\right.
+\end{equation}
+
+\textcolor{red}{(Again the coeffients depend on $Du^{\epsilon+h}-Du^\epsilon$.I don't know how to use Schauder/Calderon-Zygmond estimates at this point...)}
 

### 2021-02-04 Drafts and notes/Old_draft_05.tex
Added proof of rate of convergence for the simple case

--- 2021-01-27 Drafts and notes/Draft.tex
@@
 %\usepackage{mathpazo}
-%\usepackage[euler-digits]{eulervm}
-\usepackage[libertine,cmintegrals,cmbraces,vvarbb]{newtxmath}
+
+%\usepackage[libertine,cmintegrals,cmbraces,vvarbb]{newtxmath}
 \usepackage{eucal}
+\usepackage[euler-digits]{eulervm}
 \usepackage[unicode=true]{hyperref}
@@
 \section{Preliminaries}\label{sec:prelim} 
+\subsection{Setting and simplifications} Let $\delta_0>0$ be a fixed number such that $\mathrm{dist}(x,\partial\Omega)$ is $\mathrm{C}^2$ on $\Omega\backslash \Omega_{\delta_0}$, i.e., in the region where $0<\mathrm{dist}(x,\partial\Omega) < \delta_0$.
+We then extend $\mathrm{dist}(x,\partial\Omega)$ to a function $d(x)\in \mathrm{C}^2(\mathbb{R}^n)$ such that
+\begin{equation*}
+    \begin{cases}
+    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_{\delta_0},\\
+    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^{\delta_0}\backslash \Omega.
+    \end{cases}
+\end{equation*}
+Let us denote
+\begin{equation*}
+    K := \max_{x\in \overline{\Omega}} |\Delta d(x)|.
+\end{equation*}
+\noindent Let us denote by $\mathcal{L}^\varepsilon:\rmC^2(\Omega)\to \rmC^2(\Omega)$ the operator
+\begin{equation*}
+    \mathcal{L}^\varepsilon[u](x) := \lambda u(x) + |Du(x)|^p - f(x) - \varepsilon \Delta u(x), \qquad x\in \Omega.
+\end{equation*}
 \subsection{Gradient estimate}
@@
 
-\begin{thm} If $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ then there exists a unique solution $u\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps}.
+\begin{thm} If $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ then there exists a unique solution $u^\varepsilon\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that
+\begin{equation*}
+    %\frac{C_\varepsilon-\eta}{d(x)^\alpha}-\frac{M_\eta}{\lambda} \leq u(x)\leq \frac{C_\varepsilon+\eta}{d(x)^\alpha}+\frac{M_\eta}{\lambda} 
+    \lim_{d(x)\to 0} u^\varepsilon(x) \,d(x)^\alpha = C_\varepsilon 
+\end{equation*}
+where
+\begin{equation*}
+    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}\right) \varepsilon^{\frac{1}{p-1}}.
+\end{equation*}
 \end{thm}
 
-\begin{proof} For $\delta>0$, let us define $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) < \delta\}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$.
+\begin{proof} For $\delta>0$, let us define $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) < \delta\}$ $\textcolor{orange}{(\mathrm{dist}(x,\partial \Omega) > \delta)}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$.
 \begin{figure}[ht]
@@
 
-\noindent To find candidate for subsolution and supersolution to \eqref{eq:PDEeps}, we use the ansatz
+\noindent To find a candidate for subsolution and supersolution to \eqref{eq:PDEeps}, we use the \emph{ansatz}
 \begin{equation}\label{eq:ansatz}
-    u(x) = C_0 d(x)^{-\alpha}, \qquad x\in \Omega
+    u(x) = C_\varepsilon d(x)^{-\alpha}, \qquad x\in \Omega
 \end{equation}
 as we expect it blows up near the boundary like some thing proportionate to inverse of the distance function, due to the structure of $H(x,\varrho) = |\varrho|^p - f(x)$.
-Let us plug \eqref{eq:ansatz} into \eqref{eq:PDEeps} we obtain that the highest order terms are
+Let us plug \eqref{eq:ansatz} into \eqref{eq:PDEeps} we obtain that
+\begin{align*}
+    \lambda u(x) &\approx C_\varepsilon d(x)^{-\alpha},\\
+    \frac{\partial u}{\partial x_i}(x) &\approx -\alpha C_\varepsilon d(x)^{-(\alpha+1)} \frac{\partial d}{\partial x_i}(x) \qquad\qquad\qquad \Longrightarrow\qquad |Du (x)|^p \approx \alpha^p C_\varepsilon^p d(x)^{-p(\alpha+1)}|\nabla d(x)|^p,\\
+    %\frac{\partial^2 u}{\partial x_i^2}(x) &\approx \alpha(\alpha+1)C_0 d(x)^{-(\alpha+2)}\left|\frac{\partial d}{\partial x_i}(x)\right|^2 -\alpha C_0 d(x)^{-(\alpha+1)}\frac{\partial ^2 d}{\partial x_i^2}(x),\\
+    \varepsilon\Delta u(x) &\approx \frac{\varepsilon C_\varepsilon\alpha(\alpha+1)}{d(x)^{\alpha+2}}|\nabla d(x)|^2 - \frac{\varepsilon C_\varepsilon\alpha}{d(x)^{\alpha+1}}\Delta d(x).
+\end{align*}
+As $|\nabla d(x)| = 1$ for $x$ near $\partial\Omega$, we see that as $x\to \partial \Omega$, the highest explosive order terms are
 \begin{equation*}
-        -C_0 \alpha(\alpha+1)d^{-(\alpha+2)} + C_0^p \alpha^p d^{-(\alpha+1)p}.
+        -\varepsilon C_\varepsilon \alpha(\alpha+1)d^{-(\alpha+2)} + C_\varepsilon^p \alpha^p d^{-(\alpha+1)p}.
 \end{equation*}
@@
 \begin{equation*}
-    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_0 = \frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}.
+    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}\right) \varepsilon^{\frac{1}{p-1}}.
 \end{equation*}
-We can obtain the following families of supersolution on $\Omega_\delta$ and subsolution on $\Omega^\delta$ as follow.
+We can obtain the following families of supersolution on $\Omega_\delta$ and subsolution on $\Omega^\delta$ as follow. Let us denote
 \begin{equation*}
-        \overline{w}_{\eta,\delta}(x) = \frac{C_0+\eta}{(d(x)-\delta)^\alpha} +\frac{C_\eta}{\lambda} \quad\text{for}\;x\in \Omega_\delta \qquad\text{and}\qquad \underline{w}_{\eta,\delta}(x) = \frac{C_0-\eta}{(d(x)+\delta)^\alpha} -\frac{C_\eta}{\lambda} \quad\text{for}\;x\in \Omega^\delta.
+    G = \left[\left(K\delta_0+(\alpha+1)\right)^\frac{1}{p-1} - (\alpha+1)^{\frac{1}{p-1}}\right]\alpha.
 \end{equation*}
+
+\begin{lem}\label{lem:subsln} For each $<\delta < \frac{1}{2}\delta_0$, if $\color{red}\eta\geq G\varepsilon^{\frac{1}{p-1}}$,\color{black} we have
+\begin{equation*}
+    \overline{w}_{\eta,\delta}(x) = \frac{C_\varepsilon+\eta}{(d(x)-\delta)^\alpha} +\frac{M}{\lambda},\qquad x\in \Omega_\delta
+\end{equation*}
+is a supersolution of \eqref{eq:PDEeps} in $\Omega_\delta$ where
+\begin{equation*}
+    M = \max_{\overline{\Omega}} f(x) + 2^{\alpha+1}K\alpha\varepsilon\delta_0^{-(\alpha+1)}.
+\end{equation*}
+\end{lem}
+\begin{proof} We compute
+\begin{align*}
+    \mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) &= \frac{\lambda(C_\varepsilon + \eta)}{(d(x)-\delta)^\alpha} + M_\eta + \frac{(C_\varepsilon+\eta)^p \alpha^p}{(d(x)-\delta)^{p(\alpha+1)}}|\nabla d(x)|^p - f(x) \\
+    &\qquad\qquad\qquad\qquad\quad\;\,  - \frac{\varepsilon(C_\varepsilon+\eta)\alpha(\alpha+1)}{(d(x)-\delta)^{\alpha+2}}|\nabla d(x)|^2 + \frac{\varepsilon(C_\varepsilon+\eta)\alpha}{(d(x)-\delta)^{\alpha+1}}\Delta d(x).
+\end{align*}
+\textcolor{red}{to be filled in...}
+\end{proof}
+
+\begin{lem}\label{lem:supersln} For each $\eta>0$ there exists $M_\eta > 0$ such that 
+\begin{equation*}
+    \overline{w}_{\eta,\delta}(x) \textcolor{orange}{(\underline{w}_{\eta, \delta})} = \frac{C_\varepsilon-\eta}{(d(x)+\delta)^\alpha} -\frac{M_\eta}{\lambda}, \qquad x\in \Omega^\delta 
+\end{equation*}
+is a supersolution $\textcolor{orange}{(subsolution)}$ of \eqref{eq:PDEeps} in $\Omega^\delta$.
+\end{lem}
+
 We divide the rest of the proof into 3 steps.
@@
     \end{equation}
-    Fix $\eta>0$, as $\delta\to 0$ the value of $\underline{w}_{\eta,\delta}$ blows up on the boundary, therefore by comparison principle we have $\delta_1 \leq  \delta_2$ implies $w_{\eta,\delta_1}\leq  w_{\eta,\delta_2}$ on $\overline{\Omega}$.
+    Fix $\eta>0$, as $\delta\to 0$ the value of $\underline{w}_{\eta,\delta}$ blows up on the boundary, therefore by comparison principle we have $\delta_1 \leq  \delta_2$ implies $w_{\eta,\delta_1}\geq  w_{\eta,\delta_2}$ on $\overline{\Omega}$.
 
@@
 
-\section{Rate of convergence via Doubling variables}
-\noindent Let $\Omega = B(0,1)$. Fix $\theta \in (0,1)$ to be chosen later, let us define
+\section{Rate of convergence via Doubling variables - a toy case}
+\noindent Let $\Omega = B(0,1)$. Let $\beta,\sigma,\delta \in (0,1)$ to be chosen later, let us define
 \begin{align*}
-    \Psi^{\sigma}(x,y) = \theta u^\varepsilon(x) - u^0(y) - \frac{|x-y|^2}{\sigma}- \frac{C_0}{d(x)^\alpha}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega} 
+    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u_\delta(y) - \frac{L_0|x-y|^2}{\sigma}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}_\delta
 \end{align*}
-where $\sigma>0$ to be chosen later.
+where $L_0$ is the Lipschitz constant of $u^0$ and $u_\delta\in \mathrm{C}(\overline{\Omega}_\delta)$ is the state-constraint solution to
+\begin{equation*}
+    \begin{cases}  
+    \lambda u_\delta(x) + H(x,Du_\delta(x)) \leq 0 \qquad\text{in}\; \Omega_\delta\\
+    \lambda u_\delta(x) + H(x,Du_\delta(x)) \geq 0 \qquad\text{on}\; \overline{\Omega}_\delta.
+    \end{cases}
+\end{equation*}
+As we are working with the ball, note that $\Omega_\delta = (1-\delta)\Omega$. Let $\mathfrak{F}$ be the Lipschitz constant of $f$.
+\paragraph{\textcolor{blue}{\textbf{Step 1.}}} Since $u^\varepsilon (x)d(x)^\alpha \to C_\varepsilon$ as $d(x)\to 0$, we see that $\Phi^\sigma(x,y)\to -\infty$ as $d(x)\to 0$, therefore for a fixed $\varepsilon>0$, there is $(x_{\sigma},y_\sigma)\in \Omega\times\overline{\Omega}_\delta$ such that
+\begin{equation*}
+    \max_{\overline{\Omega}\times \overline{\Omega}_\delta} \Phi^\sigma = \Phi^\sigma(x_\sigma,y_\sigma).
+\end{equation*}
+\paragraph{\textcolor{blue}{\textbf{Step 2.}}} $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(x_\sigma,x_\sigma)$ gives us that
+    \begin{equation}\label{e:est_sigma2}
+        \mathfrak{C}\frac{|x_\sigma-y_\sigma|^2}{\sigma} \leq u_\delta(x_\sigma) - u_\delta(y_\sigma) \leq \mathfrak{C}|x_\sigma-y_\sigma| \qquad\Longrightarrow\qquad |x_\sigma -y _\sigma|\leq \sigma.
+    \end{equation}
+    This gives us that
+    \begin{equation}\label{e:est_sigma3}
+        |x_\sigma|\leq |y_\sigma|+\sigma \qquad\Longrightarrow\qquad d(x_\sigma) \geq d(y_\sigma) - \sigma\geq \delta-\sigma.
+    \end{equation}
+Let 
+\begin{equation*}
+   \fbox{$\displaystyle \delta = 2\sigma$.}
+\end{equation*}
+then 
+\begin{equation*}
+    \fbox{$d(x_\sigma) \geq \sigma$.}
+\end{equation*}
+\paragraph{\textcolor{blue}{\textbf{Step 3.}}} $x\mapsto \Phi^\sigma(x,y_\sigma)$ has a maximum at $x_\sigma\in \Omega$, thus 
+\begin{align*}
+    &\lambda u^\varepsilon(x_\sigma) + \left|\frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma} - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\nabla d(x_\sigma )\right|^p - f(x_\sigma)\\
+    &\qquad\qquad\qquad -\varepsilon\left(\frac{2n}{\sigma} + \frac{C_\varepsilon(\alpha+\beta)(\alpha+\beta+1)|\nabla d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+\beta+2}}-\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\Delta d(x_\sigma)\right)  \leq 0.
+\end{align*}
+\paragraph{\textcolor{blue}{\textbf{Step 4.}}} $y\mapsto \Phi^\sigma(x_\sigma,y)$ has a maximum at $y_\sigma\in \overline{\Omega}$, thus 
+\begin{equation*}
+    \lambda u_\delta(y_\sigma) + \left|\frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma}\right|^p - f(y_\sigma) \geq 0
+\end{equation*}
+\paragraph{\textcolor{blue}{\textbf{Step 5.}}} Gradient estimate, let
+\begin{equation*}
+    \xi_\sigma = \frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma} \qquad\text{and}\qquad \zeta_\sigma = - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\nabla d(x_\sigma)
+\end{equation*}
+then $|\xi_\sigma|\leq 2\mathfrak{C}$ already and furthermore
+\begin{equation*}
+   \xi_\sigma+\zeta_\sigma \in D^-u^\varepsilon(x_\sigma),
+\end{equation*}
+which, by the local gradient estimate, as $x_\sigma\in \Omega_{\sigma}$, this is bounded in terms of $\sigma$ and will blow up as $\sigma\to 0$. Nevertheless, we can do better as following.
+\begin{equation*}
+ |\zeta_\sigma|=   \left|\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\nabla d(x_\sigma )\right| \leq \frac{C_\varepsilon(\alpha+\beta)}{\sigma^{\alpha+\beta+1}}\leq \frac{\alpha+\beta}{\alpha} (\alpha+1)^\frac{1}{p-1}\frac{\varepsilon^\frac{1}{p-1}}{\sigma^{\alpha+\beta+1}}.
+\end{equation*}
+Thus by choosing $\sigma = \varepsilon^\gamma$ appropriately, we can make this tends to zero as $\varepsilon \to 0$. Indeed, we have
+\begin{equation*}
+    |\zeta_\sigma| \leq \frac{(\alpha+1)^\frac{1}{p-1}}{\alpha} \varepsilon^{\frac{1}{p-1} - \gamma(\alpha+\beta+1)} = \frac{\alpha+\beta}{\alpha}(\alpha+1)^{\alpha+1}\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)},
+\end{equation*}
+where we made use of the fact that $\alpha+1 = \frac{1}{p-1}$. We see that the first condition we want to impose is
+\begin{equation}\label{e:condition_gamma_1}
+    \fbox{\qquad\qquad\qquad$\displaystyle 0 < \gamma < \frac{\alpha+1}{\alpha+1+\beta}$\qquad\qquad\qquad.}
+\end{equation}
+As long as \eqref{e:condition_gamma_1} holds then
+\begin{equation}\label{e:bddp_sigmaq_sigma}
+    |\zeta_\sigma|\leq \mathfrak{C}_\alpha \qquad\text{where}\qquad \mathfrak{C}_\alpha = \frac{\alpha+\beta}{\alpha}(\alpha+1)^{\alpha+1}.
+\end{equation}
+\paragraph{\textcolor{blue}{\textbf{Step 6.}}} Recall $|\nabla d(x_\sigma)| = 1$, we have
+\begin{align}
+    \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) &\leq \underbrace{\left|\frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma}\right|^p}_{|\xi_\sigma|^p} - \underbrace{ \left|\frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma} - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\nabla d(x_\sigma )\right|^p}_{|\xi_\sigma+\zeta_\sigma|^p} \nonumber\\
+    &+ \underbrace{f(y_\sigma) - f(x_\sigma)}_{\mathfrak{F}|x_\sigma - y_\sigma|} + \varepsilon\left(\frac{2n}{\sigma} + \underbrace{\frac{C_\varepsilon(\alpha+\beta)(\alpha+\beta+1)}{d(x_\sigma)^{\alpha+\beta+2}}}_{\frac{C_\varepsilon (\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta + 1}}.\frac{\alpha+\beta+1}{d(x_\sigma)}}-\underbrace{\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\Delta d(x_\sigma)}_{\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}.\Delta d(x_\sigma)}\right)\nonumber\\
+    &\leq |\xi_\sigma|^p - |\xi_\sigma+\zeta_\sigma|^p + \mathfrak{F}\sigma + \frac{2n\varepsilon}{\sigma} + (\alpha+\beta+1)|\zeta_\sigma|\frac{\varepsilon}{\sigma} + K|\zeta_\sigma|\varepsilon \label{e:est3}
+\end{align}
+where we recall that $K = \max_{x\in \overline{\Omega}}\Delta d(x)$. Let's recall a simple estimate, let $f(t) = (x+ty)^p$ then
+\begin{align*}
+    f(1) - f(0) = \int_ 0^1 f'(s)\;ds = p\int_0^1 (x+sy)^{p-1}y\;ds,
+\end{align*}
+therefore
+\begin{align*}
+    \left||x+y|^p - |x|^p \right| &\leq p \left(\int_0^1 |x+sy|^{p-1}ds\right)|y|\\
+    &\leq p\left(\int_0^1\Big(|x|+s|y|\Big)^{p-1}\;ds\right)|y| \leq  p\Big(|x|+|y|\Big)^{p-1}|y|.
+\end{align*}
+Using this for $x = \xi_\sigma$ and $y = \zeta_\sigma$ we deduce that
+\begin{align}
+    \Big||\xi_\sigma+\zeta_\sigma|^p - |\xi|^p\Big| &\leq p\Big(|\xi_\sigma|+|\zeta_\sigma|\Big)^{p-1}|\zeta_\sigma|\nonumber\\
+    &\leq p\left(2\mathfrak{C} + \frac{(\alpha+1)^{\alpha+1}}{\alpha}\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)}\right)^{p-1}\frac{(\alpha+1)^{\alpha+1}}{\alpha}\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)}\nonumber\\
+    &\leq \underbrace{\left(p\big(2\mathfrak{C} + \mathfrak{C}_\alpha\big)^{p-1} \mathfrak{C}_\alpha \right)}_{\mathfrak{B}}\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)} \label{e:est2}
+\end{align}
+where we make use of \eqref{e:bddp_sigmaq_sigma}.
+\paragraph{\textcolor{blue}{\textbf{Step 7. Combining stuffs.}}} From \eqref{e:est2} and \eqref{e:est3} and $\sigma = \varepsilon^\gamma$ we deduce that
+\begin{align*}
+    \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) &\leq   \mathfrak{B}\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)}+ \mathfrak{F}\varepsilon^\gamma + 2n \varepsilon^{1-\gamma}\\
+    & + (\alpha+\beta + 1)\mathfrak{C}_\alpha \varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)} \varepsilon^{1-\gamma} + K\mathfrak{C}_\alpha\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)} \varepsilon.
+\end{align*}
+Let us denote
+\begin{equation*}
+    \mathfrak{X}:= \max\Big\lbrace \mathfrak{B}, \mathfrak{F},2n, (\alpha+\beta+1)\mathfrak{C}_\alpha, K\mathfrak{C}_\alpha \Big\rbrace
+\end{equation*}
+then
+\begin{equation*}
+    \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) \leq \mathfrak{X}\Big(\varepsilon^{\alpha+1-\gamma(\alpha+1+\beta)}+\varepsilon^\gamma+\varepsilon^{1-\gamma} + \varepsilon^{\alpha+2-\gamma(\alpha+2+\beta)}+\varepsilon^{\alpha+2-\gamma(\alpha+1+\beta)}\Big).
+\end{equation*}
+Take $\gamma = \frac{1}{2}$ to balance $\varepsilon^\gamma \approx \varepsilon^{1-\gamma}$ (\textcolor{blue}{which normally gives the rate $\sqrt{\varepsilon}$ for zero Dirichlet boundary problem}), we have
+\begin{equation*}
+    \begin{cases}
+    \alpha+1 - \frac{1}{2}(\alpha+1+\beta) > \frac{1}{2}\vspace{3pt}\\
+    \alpha+2 - \frac{1}{2}(\alpha+2+\beta) > \frac{1}{2}\vspace{3pt}\\
+    \alpha+2 - \frac{1}{2}(\alpha+1+\beta) > \frac{1}{2}
+    \end{cases} \qquad\Longleftrightarrow\qquad \begin{cases}
+    \alpha+1-\beta > 1\\
+    \alpha+2-\beta > 1\\
+    \alpha+3-\beta > 1
+    \end{cases}
+\end{equation*}
+which is always correct as long as $0 < \beta < \alpha$. We note that as $1<p<2$, we have $\alpha\in (0,\infty)$ and therefore such a choice of $\beta$ is always possible. We conclude that
+\begin{equation}\label{e:crucial}
+    \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) \leq \mathfrak{X}\varepsilon^\frac{1}{2}
+\end{equation}
+where $\sigma = \varepsilon^\frac{1}{2}$. 
+\paragraph{\textcolor{blue}{\textbf{Step 8.
+Deriving the conclusion}.}} Using $\Phi^\sigma(x_\sigma,y_\sigma)\geq \Phi^\sigma(x,x)$ for \textcolor{red}{all} $x\in \overline{\Omega}_\delta =  \overline{\Omega}_{2\sigma}$, we have
+\begin{equation*}
+    \lambda u^\varepsilon(x) - \lambda u_\delta(x) - \frac{C_\varepsilon}{d(x)^{\alpha+\beta}} \leq \Phi^\sigma(x_\sigma,y_\sigma) \leq \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) \leq \mathfrak{X}\varepsilon^\frac{1}{2}.
+\end{equation*}
+Using $d(x)\geq 2\sigma = 2\varepsilon^{\frac{1}{2}}$ we deduce that
+\begin{equation}\label{e:almost}
+    \lambda u^\varepsilon(x) - \lambda u_\delta(x) \leq \mathfrak{X}\varepsilon^\frac{1}{2} + \frac{(\alpha+1)^{\alpha+1}}{2^{\alpha+\beta}\alpha}\varepsilon^{\alpha+1 - \frac{\alpha+\beta}{2}} \leq \tilde{\mathfrak{X}}\varepsilon^\frac{1}{2} \qquad \text{for all}\;x\in \overline{\Omega}_{2\sigma}
+\end{equation}
+where (we see that $\alpha+1 - \frac{\alpha+\beta}{2} = 1+ \frac{\alpha-\beta}{2} > 1$)
+\begin{equation*}
+    \tilde{\mathfrak{X}} = \max \left\lbrace\mathfrak{X}, \frac{(\alpha+1)^{\alpha+1}}{2^{\alpha+\beta}\alpha} \right\rbrace.
+\end{equation*}
+Finally, in the case of the ball, $\Omega_\delta = (1-\delta)\Omega$, by \cite[Theorem 1.5]{kim_state-constraint_2020} we know that, optimally,
+\begin{equation}\label{e:citepaper}
+    0\leq \lambda u_\delta(x) - \lambda u^0(x)\leq C_H\delta \qquad\text{for all}\; x\in \overline{\Omega}_\delta.
+\end{equation}
+From \eqref{e:almost} and \eqref{e:citepaper} and $\delta =2\sigma= 2\varepsilon^\frac{1}{2}$, and $u^\varepsilon \geq u^0$ from Theorem \ref{thm:qual} we deduce that
+\begin{align*}
+    \fbox{ $\displaystyle 0 \leq \lambda u^\varepsilon(x) - \lambda u^0(x) \leq \left(\tilde{\mathfrak{X}} + 2C_H\right)\sqrt{\varepsilon} \qquad\text{for all}\; x\in \overline{\Omega}_{2\sqrt{\varepsilon}}$.}
+\end{align*}
+It appears that the boundary layer is the strip
+\begin{equation*}
+    \Gamma_\varepsilon = \{x\in \Omega: 0<\mathrm\dist(x,\partial\Omega)< 2\sqrt{\varepsilon}\}.
+\end{equation*}
+\color{blue}
+\textcolor{blue}{\textbf{The next questions and tasks:}}
+\begin{enumerate}
+    \item Check all the constants, make sure things are correct!
+    \item It seems that $\sqrt{\varepsilon}$ is the best using this method. Now we can improve this by either:
+    \begin{itemize}
+        \item[(a)] Make the boundary layer to $\sqrt{\varepsilon}$ only, instead of $2\sqrt{\varepsilon}$.
+        \item[(b)] \textcolor{red}{\textbf{Important.}} Generalize this to more general domain, possibly star-shaped domains where we can do scaling is fine (just my guess).
+    \end{itemize}
+    \item Other formulations of the doubling variable method here, for example, in the first step, it seems that making $\Phi^\sigma(x,y)\to  -\infty$ as $x\to \partial\Omega$ is "\emph{too wasteful}".
+One may need only to do something like
+    \begin{equation*}
+        \Phi^\sigma(x,y) < \Phi^\sigma(0,0) \qquad\text{if}\qquad d(x) < \;\text{something close to the boundary}.
+    \end{equation*}
+    Can we improve that to get a better rate?
+My guess is not even if we can improve this, since the dominating term coming from $\varepsilon^\gamma$ and $\varepsilon^{1-\gamma}$ later.
+Nevertheless, it maybe still interesting to see why and how the \emph{wasteful} formulation here can be improved.
+    \item \textcolor{red}{\textbf{Important.}} Using nonlinear adjoint method.
+    \item Now once we have some rate, can we do bootstrap to improve it as we discussed earlier (the simple ideas, ...)?
+    \item \textcolor{red}{\textbf{Important.}} Can we find an example where $|u^\varepsilon - u^0| = \mathcal{O}(1)$ in the strip where $0<\mathrm{dist}(x,\partial\Omega)<2\sqrt{\varepsilon}$?
+Or can we even make more layers inside with more scales, as $|u^\varepsilon - u^0| = \mathcal{O}(1)$ is not possible near the boundary $\partial\Omega$.
+\end{enumerate}
+\color{black}
 
+\newpage
 \section{Rate of convergence via a simple idea}

### 2021-02-04 Drafts and notes/Draft.tex
editing

@@
 %\usepackage{mathpazo}
-%\usepackage[euler-digits]{eulervm}
-\usepackage[libertine,cmintegrals,cmbraces,vvarbb]{newtxmath}
+
+%\usepackage[libertine,cmintegrals,cmbraceFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfs,vvarbb]{newtxmath}
 \usepackage{eucal}
+\usepackage[euler-digits]{eulervm}
 \usepackage[unicode=true]{hyperref}
@@
 \section{Preliminaries}\label{sec:prelim} 
-\subsection{Gradient estimate}
-
-\subsection{Well-posedness of large solution for subquaratic case}
-
-In this section, with the specific form of the Hamiltonian $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$, we show the existence and uniqueness of solutions to \eqref{eq:PDEeps}.
-We note that the assumption of $f$ can be relaxed to $f\in L^\infty(\Omega)$ only, but for the clarity of the proof we will assume $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
-
-\begin{thm} If $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ then there exists a unique solution $u\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps}.
-\end{thm}
-
-\begin{proof} For $\delta>0$, let us define $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) < \delta\}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$.
+\subsection{Setting and simplifications} Let $\Omega$ be an open, bounded and connected subset of $\mathbb{R}^n$ with boundary $\partial$ is of class $C^2$.
+For $\delta>0$, let us define $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) > \delta\}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$.
 \begin{figure}[ht]
@@
 
-\noindent To find candidate for subsolution and supersolution to \eqref{eq:PDEeps}, we use the ansatz
+Let $\delta_0>0$ be a fixed number such that $x\mapsto \mathrm{dist}(x,\partial\Omega)$ is of class $\mathrm{C}^2$ on $\Omega\backslash \Omega_{\delta_0}$, i.e., in the region where $0<\mathrm{dist}(x,\partial\Omega) \leq \delta_0$.
+We then extend $\mathrm{dist}(x,\partial\Omega)$ to a function $d(x)\in \mathrm{C}^2(\mathbb{R}^n)$ such that
+\begin{equation*}
+    \begin{cases}
+    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_{\delta_0},\\
+    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^{\delta_0}\backslash \Omega.
+    \end{cases}
+\end{equation*}
+Let us denote
+\begin{equation*}
+    K := \max_{x\in \overline{\Omega}} |\Delta d(x)|.
+\end{equation*}
+\noindent Let us denote by $\mathcal{L}^\varepsilon:\rmC^2(\Omega)\to \rmC^2(\Omega)$ the operator
+\begin{equation*}
+    \mathcal{L}^\varepsilon[u](x) := \lambda u(x) + H(x,Du(x)) - \varepsilon \Delta u(x), \qquad x\in \Omega.
+\end{equation*}
+\subsection{Gradient estimate}
+
+\subsection{Well-posedness of large solution for subquaratic case}
+
+In this section, with the specific form of the Hamiltonian $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$, we show the existence and uniqueness of solutions to \eqref{eq:PDEeps}.
+We note that the assumption of $f$ can be relaxed to $f\in L^\infty(\Omega)$ only, but for the clarity of the proof we will assume $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
+
+\begin{thm} If $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ then there exists a unique solution $u^\varepsilon\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that
+\begin{equation*}
+    %\frac{C_\varepsilon-\eta}{d(x)^\alpha}-\frac{M_\eta}{\lambda} \leq u(x)\leq \frac{C_\varepsilon+\eta}{d(x)^\alpha}+\frac{M_\eta}{\lambda} 
+    \lim_{d(x)\to 0} u^\varepsilon(x) \,d(x)^\alpha = C_\varepsilon 
+\end{equation*}
+where
+\begin{equation*}
+    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}\right) \varepsilon^{\frac{1}{p-1}}.
+\end{equation*}
+\end{thm}
+
+\begin{proof}
+
+\noindent To find a candidate for subsolution and supersolution to \eqref{eq:PDEeps}, we use the \emph{ansatz}
 \begin{equation}\label{eq:ansatz}
-    u(x) = C_0 d(x)^{-\alpha}, \qquad x\in \Omega
+    u(x) = C_\varepsilon d(x)^{-\alpha}, \qquad x\in \Omega
 \end{equation}
 as we expect it blows up near the boundary like some thing proportionate to inverse of the distance function, due to the structure of $H(x,\varrho) = |\varrho|^p - f(x)$.
-Let us plug \eqref{eq:ansatz} into \eqref{eq:PDEeps} we obtain that the highest order terms are
+Let us plug \eqref{eq:ansatz} into \eqref{eq:PDEeps} we obtain that
+\begin{align*}
+    \lambda u(x) &\approx C_\varepsilon d(x)^{-\alpha},\\
+    \frac{\partial u}{\partial x_i}(x) &\approx -\alpha C_\varepsilon d(x)^{-(\alpha+1)} \frac{\partial d}{\partial x_i}(x) \qquad\qquad\qquad \Longrightarrow\qquad |Du (x)|^p \approx \alpha^p C_\varepsilon^p d(x)^{-p(\alpha+1)}|\nabla d(x)|^p,\\
+    %\frac{\partial^2 u}{\partial x_i^2}(x) &\approx \alpha(\alpha+1)C_0 d(x)^{-(\alpha+2)}\left|\frac{\partial d}{\partial x_i}(x)\right|^2 -\alpha C_0 d(x)^{-(\alpha+1)}\frac{\partial ^2 d}{\partial x_i^2}(x),\\
+    \varepsilon\Delta u(x) &\approx \frac{\varepsilon C_\varepsilon\alpha(\alpha+1)}{d(x)^{\alpha+2}}|\nabla d(x)|^2 - \frac{\varepsilon C_\varepsilon\alpha}{d(x)^{\alpha+1}}\Delta d(x).
+\end{align*}
+As $|\nabla d(x)| = 1$ for $x$ near $\partial\Omega$, we see that as $x\to \partial \Omega$, the highest explosive order terms are
 \begin{equation*}
-        -C_0 \alpha(\alpha+1)d^{-(\alpha+2)} + C_0^p \alpha^p d^{-(\alpha+1)p}.
+        -\varepsilon C_\varepsilon \alpha(\alpha+1)d^{-(\alpha+2)} + C_\varepsilon^p \alpha^p d^{-(\alpha+1)p}.
 \end{equation*}

### 2021-04-06 Drafts and notes/Attempts/Old_draft_04.tex
Major change

--- 2021-02-04 Drafts and notes/Old_draft_05.tex
@@
 
-\begin{proof} For $\delta>0$, let us define $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) < \delta\}$ $\textcolor{orange}{(\mathrm{dist}(x,\partial \Omega) > \delta)}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$.
+\begin{proof} For $\delta>0$, let us define $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) < \delta\}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$.
 \begin{figure}[ht]
@@
 \begin{equation*}
-    \overline{w}_{\eta,\delta}(x) \textcolor{orange}{(\underline{w}_{\eta, \delta})} = \frac{C_\varepsilon-\eta}{(d(x)+\delta)^\alpha} -\frac{M_\eta}{\lambda}, \qquad x\in \Omega^\delta 
-\end{equation*}
-is a supersolution $\textcolor{orange}{(subsolution)}$ of \eqref{eq:PDEeps} in $\Omega^\delta$.
+    \overline{w}_{\eta,\delta}(x) = \frac{C_\varepsilon-\eta}{(d(x)+\delta)^\alpha} -\frac{M_\eta}{\lambda}, \qquad x\in \Omega^\delta
+\end{equation*}
+is a supersolution of \eqref{eq:PDEeps} in $\Omega^\delta$.
 \end{lem}
@@
     \end{equation}
-    Fix $\eta>0$, as $\delta\to 0$ the value of $\underline{w}_{\eta,\delta}$ blows up on the boundary, therefore by comparison principle we have $\delta_1 \leq  \delta_2$ implies $w_{\eta,\delta_1}\geq  w_{\eta,\delta_2}$ on $\overline{\Omega}$.
+    Fix $\eta>0$, as $\delta\to 0$ the value of $\underline{w}_{\eta,\delta}$ blows up on the boundary, therefore by comparison principle we have $\delta_1 \leq  \delta_2$ implies $w_{\eta,\delta_1}\leq  w_{\eta,\delta_2}$ on $\overline{\Omega}$.
 
@@
 
-\section{Rate of convergence via Doubling variables - a toy case}
+\section{Rate of convergence via Doubling variables}
+\noindent Let $\Omega = B(0,1)$. Let $\sigma \in (0,1)$ and $\beta \in (0,1)$ to be chosen later, let us define
+\begin{align*}
+    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u^0(y) - \frac{|x-y|^2}{\sigma}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}.
+\end{align*}
+\paragraph{\textcolor{blue}{\textbf{Step 1.}}} Since $u^\varepsilon d(x)^\alpha \to C_\varepsilon$ as $d(x)\to 0$, we see that $\Phi^\sigma(x,y)\to -\infty$ as $d(x)\to 0$, therefore for a fixed $\varepsilon>0$, there is $(x_{\sigma},y_\sigma)\in \Omega\times\overline{\Omega}$ such that
+\begin{equation*}
+    \max_{\overline{\Omega}\times \overline{\Omega}} \Phi^\sigma = \Phi^\sigma(x_\sigma,y_\sigma).
+\end{equation*}
+\paragraph{\textcolor{blue}{\textbf{Step 2.}}} Preliminaries estimates.
+\begin{itemize} 
+    \item[(a)] $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(x_\sigma,x_\sigma)$ gives us that
+    \begin{align*}
+        u^\varepsilon(x_\sigma) - u^0(y_\sigma) - \frac{|x_\sigma-y_\sigma|^2}{\sigma}- \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+\beta}} \geq u^\varepsilon(x_\sigma) - u^0(x_\sigma) -  \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+\beta}}
+    \end{align*}
+    which imlies that
+    \begin{equation}\label{e:est_sigma}
+        \frac{|x_\sigma-y_\sigma|^2}{\sigma} \leq u^0(x_\sigma) - u^0(y_\sigma) \leq \mathfrak{C}|x_\sigma-y_\sigma| \qquad\Longrightarrow\qquad |x_\sigma -y _\sigma|\leq \mathfrak{C}\sigma.
+    \end{equation}
+    \item[(b)] $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(y_\sigma,y_\sigma)$ gives us that
+    \begin{align*}
+        u^\varepsilon(x_\sigma) - u^0(y_\sigma) - \frac{|x_\sigma-y_\sigma|^2}{\sigma}- \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+\beta}} \geq u^\varepsilon(y_\sigma) - u^0(y_\sigma) -  \frac{C_\varepsilon}{d(y_\sigma)^{\alpha+\beta}}
+    \end{align*}
+    which implies that
+    \begin{equation*}
+        \frac{|x_\sigma-y_\sigma|^2}{\sigma} + C_\varepsilon\left(\frac{1}{d(x_\sigma)^{\alpha+\beta}} - \frac{1}{d(y_\sigma)^{\alpha+\beta}}\right) \leq u^\varepsilon(x_\sigma) - u^\varepsilon(y_\sigma) .
+    \end{equation*}
+    \item[(c)] $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(0,0)$ gives us that
+    \begin{align*}
+        u^\varepsilon(x_\sigma) - u^0(y_\sigma) - \frac{|x_\sigma-y_\sigma|^2}{\sigma}- \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+\beta}} \geq u^\varepsilon(0) - u^0(0) -  C_\varepsilon
+    \end{align*}
+    and thus 
+    \begin{equation*}
+         \frac{|x_\sigma-y_\sigma|^2}{\sigma}+ \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+\beta}}  \leq u^\varepsilon(x_\sigma) - u^\varepsilon(0) + u^0(0) - u^0(y_\sigma) + C_\varepsilon.
+    \end{equation*}
+\end{itemize}
+
+\newpage
+\section{New try}
 \noindent Let $\Omega = B(0,1)$. Let $\beta,\sigma,\delta \in (0,1)$ to be chosen later, let us define
 \begin{align*}
-    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u_\delta(y) - \frac{L_0|x-y|^2}{\sigma}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}_\delta
-\end{align*}
-where $L_0$ is the Lipschitz constant of $u^0$ and $u_\delta\in \mathrm{C}(\overline{\Omega}_\delta)$ is the state-constraint solution to
+    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u_\delta(y) - \mathfrak{C}\frac{|x-y|^2}{\sigma}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}_\delta
+\end{align*}
+where $\mathfrak{C}$ is the Lipschitz constant of $u^0$, $u_\delta\in \mathrm{C}(\overline{\Omega}_\delta)$ is the state-constraint solution to
 \begin{equation*}
@@
 \end{equation*}
-\color{blue}
-\textcolor{blue}{\textbf{The next questions and tasks:}}
-\begin{enumerate}
-    \item Check all the constants, make sure things are correct!
-    \item It seems that $\sqrt{\varepsilon}$ is the best using this method. Now we can improve this by either:
-    \begin{itemize}
-        \item[(a)] Make the boundary layer to $\sqrt{\varepsilon}$ only, instead of $2\sqrt{\varepsilon}$.
-        \item[(b)] \textcolor{red}{\textbf{Important.}} Generalize this to more general domain, possibly star-shaped domains where we can do scaling is fine (just my guess).
-    \end{itemize}
-    \item Other formulations of the doubling variable method here, for example, in the first step, it seems that making $\Phi^\sigma(x,y)\to  -\infty$ as $x\to \partial\Omega$ is "\emph{too wasteful}".
-One may need only to do something like
-    \begin{equation*}
-        \Phi^\sigma(x,y) < \Phi^\sigma(0,0) \qquad\text{if}\qquad d(x) < \;\text{something close to the boundary}.
-    \end{equation*}
-    Can we improve that to get a better rate?
-My guess is not even if we can improve this, since the dominating term coming from $\varepsilon^\gamma$ and $\varepsilon^{1-\gamma}$ later.
-Nevertheless, it maybe still interesting to see why and how the \emph{wasteful} formulation here can be improved.
-    \item \textcolor{red}{\textbf{Important.}} Using nonlinear adjoint method.
-    \item Now once we have some rate, can we do bootstrap to improve it as we discussed earlier (the simple ideas, ...)?
-    \item \textcolor{red}{\textbf{Important.}} Can we find an example where $|u^\varepsilon - u^0| = \mathcal{O}(1)$ in the strip where $0<\mathrm{dist}(x,\partial\Omega)<2\sqrt{\varepsilon}$?
-Or can we even make more layers inside with more scales, as $|u^\varepsilon - u^0| = \mathcal{O}(1)$ is not possible near the boundary $\partial\Omega$.
-\end{enumerate}
-\color{black}
+The next questions and tasks:
 

### 2021-04-06 Drafts and notes/Attempts/Old_draft_06.tex
Major change

--- 2021-02-04 Drafts and notes/Draft.tex
@@
 %============%============%============%============%
+%\usepackage{romannum}
 \usepackage{xcolor}
@@
 In this paper, we are interested in the rate of convergence of $u^\varepsilon \to u$ as $\varepsilon\to 0$.
-A boundary layer is expected to describe the behavior of convergence near the boundary.
+A boundary layer is expected to describe the behavior of this convergence near the boundary.
 \subsection{Assumptions} We will always assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary in $\mathbb{R}^n$ and $H:\mathbb{R}^n\times \mathbb{R}^n$ is a continuous Hamiltonian.
@@
 \section{Preliminaries}\label{sec:prelim} 
-\subsection{Setting and simplifications} Let $\Omega$ be an open, bounded and connected subset of $\mathbb{R}^n$ with boundary $\partial$ is of class $C^2$.
-For $\delta>0$, let us define $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) > \delta\}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$.
+\subsection{Setting and simplifications} Let $\Omega$ be an open, bounded and connected subset of $\mathbb{R}^n$ with boundary $\partial\Omega$ is of class $C^2$.
+For small $\delta>0$, we denote $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) > \delta\}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$.
 \begin{figure}[ht]
@@
 \end{figure}
-We consider $\delta$ small enough so that the distance function $x\mapsto \mathrm{dist}(x,\partial \Omega)$ is $\mathrm{C}^2$ in the strip $\Omega^\delta\backslash \overline{\Omega}_\delta$, we recall that $|D d(x)| = 1$ in that region.
-We extend the signed distance function into a $\mathrm{C}^2(\mathbb{R}^n)$ function, denoted by $d(x)$ such that
-\begin{equation*}
-    \begin{cases}
-    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_\delta,\\
-    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^\delta\backslash \Omega.
-    \end{cases}
-\end{equation*}
-We can choose $d(\cdot)$ so that $\Omega_\delta = \{x\in \mathbb{R}^n: d(x)-\delta >0 \}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: d(x) +\delta>0\}$.
-
-Let $\delta_0>0$ be a fixed number such that $x\mapsto \mathrm{dist}(x,\partial\Omega)$ is of class $\mathrm{C}^2$ on $\Omega\backslash \Omega_{\delta_0}$, i.e., in the region where $0<\mathrm{dist}(x,\partial\Omega) \leq \delta_0$.
+
+\noindent Let $\delta_0>0$ be a fixed number such that $x\mapsto \mathrm{dist}(x,\partial\Omega)$ is of class $\mathrm{C}^2$ on $\Omega\backslash \Omega_{\delta_0}$ (see \cite{gilbarg_elliptic_2001}), i.e., in the region where $0<\mathrm{dist}(x,\partial\Omega) \leq \delta_0$.
 We then extend $\mathrm{dist}(x,\partial\Omega)$ to a function $d(x)\in \mathrm{C}^2(\mathbb{R}^n)$ such that
-\begin{equation*}
+\begin{equation}\label{e:distance_def}
     \begin{cases}
@@
     \end{cases}
-\end{equation*}
-Let us denote
-\begin{equation*}
-    K := \max_{x\in \overline{\Omega}} |\Delta d(x)|.
-\end{equation*}
-\noindent Let us denote by $\mathcal{L}^\varepsilon:\rmC^2(\Omega)\to \rmC^2(\Omega)$ the operator
+\end{equation}
+We recall that $|D d(x)| = 1$ in the viscosity sense (and thus in classical sense) in $\Omega^{\delta_0}\backslash \Omega_{\delta_0}$.
+Since $x\mapsto \mathrm{dist}(x,\partial \Omega)$ is a viscosity solution to $|Du(x)|=1$ in $\Omega$.
+%we can assume that the extension $d(x)$ as also satisfies $|Dd(x)|\leq 1$ in $\Omega$.
+Let 
+\begin{equation*}
+    K_1 := \max_{x\in \overline{\Omega}} |\Delta d(x)| \qquad\text{and}\qquad K_2 := \max_{x\in \overline{\Omega}} |D d(x)|.
+\end{equation*}
+\noindent We denote by $\mathcal{L}^\varepsilon:\rmC^2(\Omega)\to \rmC^2(\Omega)$ the elliptic operator
 \begin{equation*}
@@
 \end{equation*}
-\subsection{Gradient estimate}
-
-\subsection{Well-posedness of large solution for subquaratic case}
-
-In this section, with the specific form of the Hamiltonian $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$, we show the existence and uniqueness of solutions to \eqref{eq:PDEeps}.
-We note that the assumption of $f$ can be relaxed to $f\in L^\infty(\Omega)$ only, but for the clarity of the proof we will assume $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
+
+\subsection{Local gradient estimate} 
+We recall the local gradient bound following \cite[Appendix]{Lasry1989}.
+The technique being used is the classical Bernstein's method.
+Let $\Omega$ be an open, bounded subset of $\R^n$, $\varepsilon \in (0,1)$ and $\lambda \in [0,1)$.
+We consider the Hamiltonian $H(x,\rho) = |\rho|^p - f(x)$ where $1<p < \infty$.
+
+\begin{thm}\label{thm:grad_1} Let $f\in \rmC(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $u\in \mathrm{C}^2(\Omega)$ be a solution to $\mathcal{L}^\varepsilon[u] = 0$ in $\Omega$.
+Assume that $\lambda u(x)-f(x)\geq -K_0$ in $\Omega$, then for $\delta>0$ there exists $C_\delta = C(K_0,p,\delta, \Vert D f\Vert_{L^\infty(\Omega)})$ such that
+\begin{equation*}
+    \sup_{x\in \overline{\Omega}_\delta} \Big(|u(x)|+|Du(x)|\Big) \leq C_\delta.
+\end{equation*}
+\end{thm}
+
+\begin{proof} Let $\theta\in (0,1)$ be chosen later, $\varphi\in \mathrm{C}_c^\infty(\Omega)$, $0\leq \varphi\leq 1$, $\mathrm{supp}\;\varphi\subset \Omega$ and $\varphi = 1$ on $\Omega_\delta$ such that
+\begin{equation}\label{e:ass_power}
+    |\Delta \varphi(x)| \leq C|\varphi(x)|^\theta \qquad\text{and}\qquad |D \varphi(x)|^2 \leq C\varphi^{1+\theta}
+\end{equation}
+for $x\in \Omega$ and $C = C(\delta,\theta)$.
+Let $w(x) = |Du(x)|^2$ for $x\in \Omega$, the goal is to derive an equation for $\varphi w$. The equation for $w$ is given by
+\begin{equation*}
+    -\varepsilon \Delta w + p|D u|^{p-2}D u \cdot D w + 2\lambda w - D f\cdot D u + \varepsilon |D^2u|^2 = 0 \qquad\text{in}\;\Omega.
+\end{equation*}
+Using that, we can derive an equation for $(\varphi w)$ as follows.
+\begin{align*}
+    &-\varepsilon \Delta (\varphi w) + p|D u|^{p-2}D u \cdot D (\varphi w) + 2\lambda (\varphi w) + \varepsilon \varphi|D^2u|^2 + 2\varepsilon \frac{D \varphi}{\varphi}\cdot D (\varphi w) \\
+    &\qquad\qquad\qquad\qquad = \varphi(D f\cdot D u) + p|D u|^{p-2}(D u\cdot D \varphi)w -\varepsilon w \Delta \varphi + 2\varepsilon \frac{|D \varphi|^2}{\varphi}w
+    \qquad\text{in}\;\mathrm{supp}\;\varphi.
+\end{align*}
+Assume that $\varphi w$ achieves its maximum over $\overline{\Omega}$ at $x_0\in \Omega$ then we can assume that $x_0\in \mathrm{supp}\;\varphi$, since otherwise the maximum of $\varphi w$ over $\overline{\Omega}$ is zero.
+By the classical maximum principle
+\begin{equation*}
+    -\varepsilon \Delta(\varphi w)(x_0)\geq 0 \qquad\text{and}\qquad |D(\varphi w)(x_0)| = 0.
+\end{equation*}
+Using that in the equation of $\varphi w$ above, we obtain that
+\begin{equation*}
+    \varepsilon \varphi|D^2u|^2 \leq  \varphi (Df\cdot Du)+ p|Du|^{p-1} |D\varphi|w + \varepsilon w |\Delta\varphi|  + 2\varepsilon  w\frac{|D\varphi|^2}{\varphi},
+\end{equation*}
+where all terms are evaluated at $x_0$. Using \eqref{e:ass_power} we have
+\begin{equation}\label{e:est_for_D^2u}
+    \varepsilon \varphi|D^2u|^2 \leq  \varphi |Df|w^{\frac{1}{2}}+ Cp w^{\frac{p-1}{2}+1} \varphi^{\frac{1+\theta}{2}} + C\varepsilon w \varphi^{\theta} + 2C\varepsilon  w\varphi^\theta.
+\end{equation}
+By Cauchy-Schwartz inquality, we have $n|D^2u|^2\geq (\Delta u)^2$, thus if $n\varepsilon < 1$ then
+\begin{equation}\label{e:est_for_D^2u_2}
+    \varepsilon |D^2u|^2 \geq \frac{(\varepsilon \Delta u)^2}{n\varepsilon} \geq (\varepsilon \Delta u)^2 = \left(\lambda u + |Du|^p - f\right)^2 \geq |Du|^{2p} - 2C_0|Du|^p \geq \frac{|Du|^{2p}}{2} - 2K_0.
+\end{equation}
+Using \eqref{e:est_for_D^2u_2} in \eqref{e:est_for_D^2u} we obtain that
+\begin{equation*}
+    \varphi\left(\frac{1}{2}w^p - 2K_0\right) \leq \varphi |Df|w^{\frac{1}{2}}+ Cp w^{\frac{p-1}{2}+1} \varphi^{\frac{1+\theta}{2}} + 3C\varepsilon w \varphi^{\theta}.
+\end{equation*}
+Multiply both sides by $\varphi^{p-1}$ we deduce that
+\begin{align*}
+    (\varphi w)^p \leq 4K_0\varphi^{p-1} + 2\Vert Df\Vert_{L^\infty}\varphi^p w^{\frac{1}{2}} + 2Cp \varphi^{\frac{2p+\theta - 1}{2}}w^{\frac{p+1}{2}} + 6C\varepsilon \varphi^{p+\theta - 1}w.
+\end{align*}
+Choose $2p+\theta -1 \geq p+1$, i.e., $p+\theta\geq 2$. This is always possible with the requirement $\theta \in (0,1)$, as $1<p <\infty$. We deduce that 
+\begin{equation}\label{e:est_for_D^2u_3}
+    (\varphi w)^p \leq C\left(1+ (\varphi w)^\frac{1}{2} + (\varphi w)^\frac{p+1}{2} +(\varphi w)\right)
+\end{equation}
+As a polynomial in $z = (\varphi w)(x_0)$, this implies that $(\varphi w)(x_0)\leq C$ where $C$ depends on coefficients of the right hand side of \eqref{e:est_for_D^2u_3}, which implies our desired gradient bound since $\overline{\Omega}_\delta\subset \mathrm{supp}\;\varphi$.
+\end{proof}
+
+\subsection{Well-posedness of large solution for subquaratic case} In this section, with the specific form of the Hamiltonian $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$, we show the existence and uniqueness of solutions to \eqref{eq:PDEeps}.
+We note that the assumption of $f$ can be relaxed to $f\in L^\infty(\Omega)$, but for the clarity of the proof we will assume $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
 
@@
     \lambda u(x) &\approx C_\varepsilon d(x)^{-\alpha},\\
-    \frac{\partial u}{\partial x_i}(x) &\approx -\alpha C_\varepsilon d(x)^{-(\alpha+1)} \frac{\partial d}{\partial x_i}(x) \qquad\qquad\qquad \Longrightarrow\qquad |Du (x)|^p \approx \alpha^p C_\varepsilon^p d(x)^{-p(\alpha+1)}|\nabla d(x)|^p,\\
+    \frac{\partial u}{\partial x_i}(x) &\approx -\alpha C_\varepsilon d(x)^{-(\alpha+1)} \frac{\partial d}{\partial x_i}(x) \qquad\qquad\qquad \Longrightarrow\qquad |Du (x)|^p \approx \alpha^p C_\varepsilon^p d(x)^{-p(\alpha+1)}|D d(x)|^p,\\
     %\frac{\partial^2 u}{\partial x_i^2}(x) &\approx \alpha(\alpha+1)C_0 d(x)^{-(\alpha+2)}\left|\frac{\partial d}{\partial x_i}(x)\right|^2 -\alpha C_0 d(x)^{-(\alpha+1)}\frac{\partial ^2 d}{\partial x_i^2}(x),\\
-    \varepsilon\Delta u(x) &\approx \frac{\varepsilon C_\varepsilon\alpha(\alpha+1)}{d(x)^{\alpha+2}}|\nabla d(x)|^2 - \frac{\varepsilon C_\varepsilon\alpha}{d(x)^{\alpha+1}}\Delta d(x).
-\end{align*}
-As $|\nabla d(x)| = 1$ for $x$ near $\partial\Omega$, we see that as $x\to \partial \Omega$, the highest explosive order terms are
+    \varepsilon\Delta u(x) &\approx \frac{\varepsilon C_\varepsilon\alpha(\alpha+1)}{d(x)^{\alpha+2}}|D d(x)|^2 - \frac{\varepsilon C_\varepsilon\alpha}{d(x)^{\alpha+1}}\Delta d(x).
+\end{align*}
+As $|D d(x)| = 1$ for $x$ near $\partial\Omega$, we see that as $x\to \partial \Omega$, the highest explosive order terms are
 \begin{equation*}
@@
 Setting them to zero, we deduce that
-\begin{equation*}
-    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}\right) \varepsilon^{\frac{1}{p-1}}.
-\end{equation*}
-We can obtain the following families of supersolution on $\Omega_\delta$ and subsolution on $\Omega^\delta$ as follow. Let us denote
-\begin{equation*}
-    G = \left[\left(K\delta_0+(\alpha+1)\right)^\frac{1}{p-1} - (\alpha+1)^{\frac{1}{p-1}}\right]\alpha.
-\end{equation*}
-
-\begin{lem}\label{lem:subsln} For each $<\delta < \frac{1}{2}\delta_0$, if $\color{red}\eta\geq G\varepsilon^{\frac{1}{p-1}}$,\color{black} we have
-\begin{equation*}
-    \overline{w}_{\eta,\delta}(x) = \frac{C_\varepsilon+\eta}{(d(x)-\delta)^\alpha} +\frac{M}{\lambda},\qquad x\in \Omega_\delta
+\begin{equation}\label{e:relation}
+    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}\right) \varepsilon^{\frac{1}{p-1}} = \frac{1}{\alpha}(\alpha+1)^{\alpha+1}\varepsilon^{\alpha+1}.
+\end{equation}
+We note that $\alpha+1 = \frac{1}{p-1}$ for convenience later. Recall that $_1 = \max_{\overline{\Omega}}|\Delta d(x)|$, let us denote
+\begin{equation*}
+    G = \left[\left(K_1\delta_0+(\alpha+1)\right)^{\alpha+1} - (\alpha+1)^{\alpha+1}\right]\alpha.
+\end{equation*}
+
+\begin{lem}\label{lem:subsln} For each $<\delta < \frac{1}{2}\delta_0$, if $\eta\geq G\varepsilon^{\alpha+1}$, we have
+\begin{equation*}
+    \overline{w}_{\eta,\delta}(x) = \frac{C_\varepsilon+\eta}{(d(x)-\delta)^\alpha} +\frac{M_\varepsilon}{\lambda},\qquad x\in \Omega_\delta, 
 \end{equation*}
 is a supersolution of \eqref{eq:PDEeps} in $\Omega_\delta$ where
-\begin{equation*}
-    M = \max_{\overline{\Omega}} f(x) + 2^{\alpha+1}K\alpha\varepsilon\delta_0^{-(\alpha+1)}.
-\end{equation*}
+\begin{equation}\label{e:M_eps}
+    M_\varepsilon = \max_{\overline{\Omega}} f + 2\left(\frac{2}{\delta_0}\right)^{\alpha+1}K_1(\alpha+1)^{\alpha+1}\varepsilon^{\alpha+2} + \left(\frac{2(\alpha+1)\varepsilon}{\delta_0}\right)^{\alpha+2}\big(2^pK_2^p+2K_2^2\big).
+\end{equation}
 \end{lem}
-\begin{proof} We compute
-\begin{align*}
-    \mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) &= \frac{\lambda(C_\varepsilon + \eta)}{(d(x)-\delta)^\alpha} + M_\eta + \frac{(C_\varepsilon+\eta)^p \alpha^p}{(d(x)-\delta)^{p(\alpha+1)}}|\nabla d(x)|^p - f(x) \\
-    &\qquad\qquad\qquad\qquad\quad\;\,  - \frac{\varepsilon(C_\varepsilon+\eta)\alpha(\alpha+1)}{(d(x)-\delta)^{\alpha+2}}|\nabla d(x)|^2 + \frac{\varepsilon(C_\varepsilon+\eta)\alpha}{(d(x)-\delta)^{\alpha+1}}\Delta d(x).
-\end{align*}
-\textcolor{red}{to be filled in...}
+\noindent The reason why we state this lemma again instead of just citing \cite{Lasry1989} is because we want to show that the constant $M_\varepsilon$ here can be chosen independent of $\eta$ as long as $\eta \geq G\varepsilon^{\alpha+1}$, thus $\{M_\varepsilon\}_{\varepsilon>0}$ is bounded.
+\begin{proof} Recall that $p(\alpha+1) = \alpha+2$, we compute
+\begin{align*}
+    \mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) = \frac{\lambda(C_\varepsilon + \eta)}{(d(x)-\delta)^\alpha} &+ M_\varepsilon + \frac{(C_\varepsilon+\eta)^p \alpha^p}{(d(x)-\delta)^{\alpha+2}}|D d(x)|^p - f(x) \\
+    &- \frac{\varepsilon(C_\varepsilon+\eta)\alpha(\alpha+1)}{(d(x)-\delta)^{\alpha+2}}|D d(x)|^2 + \frac{\varepsilon(C_\varepsilon+\eta)\alpha}{(d(x)-\delta)^{\alpha+1}}\Delta d(x).
+\end{align*}
+Regarding the relation \eqref{e:relation}, we define
+\begin{equation*}
+    1<\nu = \left(\frac{C_\varepsilon+\eta}{C_\varepsilon}\right) \leq 2.
+\end{equation*}
+There are two cases to be considered.
+\begin{itemize}
+    \item In the region where $d(x)\geq \delta_0$ then $d(x)-\delta \geq \frac{1}{2}\delta_0$, therefore 
+    \begin{align*}
+        \mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) = \frac{\lambda(C_\varepsilon + \eta)}{(d(x)-\delta)^\alpha} + M_\varepsilon &+ \frac{\alpha^pC_\varepsilon^p}{(d(x)-\delta)^{\alpha+2}}\left(\nu^{p}|Dd(x)|^p - \nu|Dd(x)|^2\right)\\
+        &+\frac{\nu\varepsilon \alpha C_\varepsilon}{(d(x)-\delta)^{\alpha+1}}\Delta d(x) - f(x).
+    \end{align*}
+Recall that $K_2 = \max_{x\in\overline{\Omega}}|Dd(x)|$ and $1<|\nu|\leq 2$, we have
+\begin{align*}
+    \frac{\alpha^pC_\varepsilon^p}{(d(x)-\delta)^{\alpha+2}}\left|\nu^{p}|Dd(x)|^p - \nu|Dd(x)|^2\right| &\leq \left(\frac{2(\alpha+1)\varepsilon}{\delta_0}\right)^{\alpha+2}\big(2^pK_2^p+2K_2^2\big).
+\end{align*}
+%As $|Dd(x)|\leq 1$, $\nu^p|Dd(x)|^p - \nu|Dd(x)|^2 \geq 0$ since $1<p<2$ and $\nu>1$. Finally
+\begin{equation*}
+    \frac{\nu\varepsilon \alpha C_\varepsilon}{(d(x)-\delta)^{\alpha+1}}|\Delta d(x)| \leq 2\left(\frac{2}{\delta_0}\right)^{\alpha+1}K_1 \alpha\varepsilon C_\varepsilon \leq 2\left(\frac{2}{\delta_0}\right)^{\alpha+1}K_1 (\alpha+1)^{\alpha+1}\varepsilon^{\alpha+2}.
+\end{equation*}
+ From the definition of $M_\varepsilon$ in \eqref{e:M_eps} we deduce that $\mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right]\geq 0$ in this region.
+    \item In the region where $\delta < d(x)\leq \delta_0$, we have $|Dd(x)|=1$, thus
+    \begin{align*}
+         \mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) &= \frac{\lambda(C_\varepsilon + \eta)}{(d(x)-\delta)^\alpha} + M - f(x)\\
+         & + \frac{\alpha^p C_\varepsilon^p}{(d(x)-\delta)^{\alpha+2}}\nu\left(\nu^{p-1} - 1 - \frac{ (d(x)-\delta)\Delta d(x)}{(\alpha+1)}\right).
+    \end{align*}
+    We note that as $0<d(x)\leq \delta_0$, we have
+    \begin{equation*}
+        \left|\frac{(d(x)-\delta)\Delta  d(x)}{(\alpha+1)}\right| \leq \frac{_1\delta_0}{\alpha+1}.
+    \end{equation*}
+    Recall that $\nu = \left(1+\frac{\eta}{C_\varepsilon}\right)$, we want to choose $\eta$ such that
+    \begin{equation*}
+        \left(1+\frac{\eta}{C_\varepsilon}\right)^{p-1} - 1 \geq \frac{K_1\delta_0}{\alpha+1} \qquad\Longrightarrow\qquad \eta \geq C_\varepsilon\left[\left(1+\frac{K_1\delta_0}{\alpha+1}\right)^{\alpha+1}-1\right] = G\varepsilon^{\alpha+1}
+    \end{equation*}
+    where we use $\frac{1}{p-1} = \alpha+1$ again. This will ensure that $\mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) \geq 0$ in this region.
+\end{itemize}
 \end{proof}
 
-\begin{lem}\label{lem:supersln} For each $\eta>0$ there exists $M_\eta > 0$ such that 
-\begin{equation*}
-    \overline{w}_{\eta,\delta}(x) \textcolor{orange}{(\underline{w}_{\eta, \delta})} = \frac{C_\varepsilon-\eta}{(d(x)+\delta)^\alpha} -\frac{M_\eta}{\lambda}, \qquad x\in \Omega^\delta 
-\end{equation*}
-is a supersolution $\textcolor{orange}{(subsolution)}$ of \eqref{eq:PDEeps} in $\Omega^\delta$.
+\begin{lem}\label{lem:supersln} For each $\eta\geq G\varepsilon^{\alpha+1}$ there exists $M_\eta > 0$ such that 
+\begin{equation*}
+    \underline{w}_{\eta, \delta}(x) = \frac{C_\varepsilon-\eta}{(d(x)+\delta)^\alpha} -\frac{M_\varepsilon}{\lambda}, \qquad x\in \Omega^\delta 
+\end{equation*}
+is a subsolution of \eqref{eq:PDEeps} in $\Omega^\delta$.
 \end{lem}
 
-We divide the rest of the proof into 3 steps.
+\begin{proof} The proof for this Lemma should be the same with Lemma \ref{lem:subsln}.
+\end{proof}
+
+\noindent We divide the rest of the proof into 3 steps.
 We first construct a minimal solution, then a maximal solution to \eqref{eq:PDEeps}, and finally show that they are equal to conclude the existence and uniqueness of solution to \eqref{eq:PDEeps}.
@@
     \end{equation}
-    Fix $\eta>0$, as $\delta\to 0$ the value of $\underline{w}_{\eta,\delta}$ blows up on the boundary, therefore by comparison principle we have $\delta_1 \leq  \delta_2$ implies $w_{\eta,\delta_1}\geq  w_{\eta,\delta_2}$ on $\overline{\Omega}$.
-
-    \noindent Since $\underline{w}_{\eta,\delta'}$ is a subsolution in $\overline{\Omega}$ with finite boundary, we obtain that
+    \begin{itemize}
+        \item Fix $\eta>0$ (and $\eta\geq G\varepsilon^{\alpha+1}$ in view of Lemmas \ref{lem:subsln} and \ref{lem:supersln}), as $\delta\to 0$ the value of $\underline{w}_{\eta,\delta}$ blows up on the boundary, therefore by the standard comparison principle for second-order elliptic equation with Dirichlet boundary we have $\delta_1 \leq  \delta_2$ implies $w_{\eta,\delta_1}\geq  w_{\eta,\delta_2}$ on $\overline{\Omega}$.
+        \item For $\delta'>0$, since $\underline{w}_{\eta,\delta'}$ is a subsolution in $\overline{\Omega}$ with finite boundary, we obtain that
             \begin{equation}\label{e:cp_delta1}
@@
             \end{equation}
-    For $\delta' > 0$, since $\overline{w}_{\eta,\delta}$ is a supersolution on $\Omega_{\delta'}$ with infinity value on the boundary $\partial\Omega_{\delta'}$, by comparison principle
+        \item Similarly, since $\overline{w}_{\eta,\delta'}$ is a supersolution on $\Omega_{\delta'}$ with infinity value on the boundary $\partial\Omega_{\delta'}$, by comparison principle
             \begin{equation}\label{e:cp_delta2}
@@
             \end{equation}
-    From \eqref{e:cp_delta1} and \eqref{e:cp_delta2} we have
+    \end{itemize}
+    \noindent From \eqref{e:cp_delta1} and \eqref{e:cp_delta2} we have
     \begin{equation}\label{e:cp_delta3}
@@
     \end{equation}
-    Thus $\{w_{\eta,\delta}\}_{\delta>0}$ is locally bounded in $L^{\infty}_{\mathrm{loc}}(\Omega)$.
-Using the gradient estimate for $w_{\eta,\delta}$ solving \eqref{e:w_def} we deduce that $\{w_{\eta,\delta}\}_{\delta>0}$ is locally bounded in $W^{1,\infty}_{\mathrm{loc}}(\Omega)$.
-Plug it back into the defining equation \eqref{e:w_def} to bound the Laplacian and the second derivative terms, we deduce that $\{w_{\eta,\delta}\}_{\delta>0}$ is locally bounded in $W^{2,r}_{\mathrm{loc}}(\Omega)$ for all $r<\infty$.
-
-    \noindent Local boundedness of $\{u_{\eta,\delta}\}_{\delta>0}$ in $W^{2,r}_{\mathrm{loc}}(\Omega)$ implies weak$^*$ compactnes, that is there exists a function $u\in W^{2,r}(\Omega)$ such that (via subsequence and monotonicity)
-    \begin{equation*}
-    \begin{cases}
-        w_{\eta,\delta} \rup u \qquad\text{weakly in}\;W^{2,r}_{\mathrm{loc}}(\Omega),\vspace{0.2cm}\\
+    Thus $\{w_{\eta,\delta}\}_{\delta>0}$ is locally bounded in $L^{\infty}_{\mathrm{loc}}(\Omega)$ ($\{w_{\eta,\delta}\}_{\delta>0}$ is uniformly bounded from below), thus using the local gradient estimate for $w_{\eta,\delta}$ solving \eqref{e:w_def} we deduce that $\{w_{\eta,\delta}\}_{\delta>0}$ is locally bounded in $W^{1,\infty}_{\mathrm{loc}}(\Omega)$.
+Plug it back into the defining equation \eqref{e:w_def} we deduce that $\{w_{\eta,\delta}\}_{\delta>0}$ is locally bounded in $W^{2,r}_{\mathrm{loc}}(\Omega)$ for all $r<\infty$.
+
+    \noindent Local boundedness of $\{u_{\eta,\delta}\}_{\delta>0}$ in $W^{2,r}_{\mathrm{loc}}(\Omega)$ implies weak$^*$ compactness, that is there exists a function $u\in W^{2,r}(\Omega)$ such that (via subsequence and monotonicity)
+    \begin{equation*}
+        w_{\eta,\delta} \rup u \qquad\text{weakly in}\;W^{2,r}_{\mathrm{loc}}(\Omega),\qquad \text{and}\qquad
         w_{\eta,\delta} \to u \qquad\text{strongly in}\;W^{1,r}_{\mathrm{loc}}(\Omega).
-    \end{cases}
-    \end{equation*}
-    In particular, $w_{\eta,\delta}\to u$ in $\mathrm{C}^1_{\mathrm{loc}}(\Omega)$ thanks to compact embedding.
-Let us rewrite the equation $\mathcal{L}\left[u_{\eta,\delta}\right] = 0$ as $\varepsilon\Delta w_{\eta,\delta}(x) = F[w_{\eta,\delta}](x)$ in $U$ for $U\subset\subset \Omega$ where
+    \end{equation*}
+    In particular, $w_{\eta,\delta}\to u$ in $\mathrm{C}^1_{\mathrm{loc}}(\Omega)$ thanks to Sobolev compact embedding.
+Let us rewrite the equation $\mathcal{L}^\varepsilon\left[u_{\eta,\delta}\right] = 0$ as $\varepsilon\Delta w_{\eta,\delta}(x) = F[w_{\eta,\delta}](x)$ in $U$ for $U\subset\subset \Omega$ where
     \begin{equation*}
@@
     \end{equation*}
-    As $u_{\eta,\delta}\to u$ in $\mathrm{C}^1(U)$ as $\delta\to 0$, we have $F[w_{\eta,\delta}](x) \to F(x)$ uniformly in $U$ where 
+    Since $u_{\eta,\delta}\to u$ in $\mathrm{C}^1(U)$ as $\delta\to 0$, we have $F[w_{\eta,\delta}](x) \to F(x)$ uniformly in $U$ where 
     \begin{equation*}
@@
     \end{equation*}
-    In the limit we see that $u\in L^2$ is a weak solution of $\varepsilon\Delta u = F$ in $U$ where $F$ is continuous, thus $u\in \mathrm{C}^2(\Omega)$ as well and by stability we see that $u$ solves $\mathcal{L}[u] = 0$ in $\Omega$.
+    In the limit as $\delta\to 0$ we obtain that $u\in L^2(U)$ is a weak solution of $\varepsilon\Delta u = F$ in $U$ where $F$ is continuous, thus $u\in \mathrm{C}^2(\Omega)$ and by stability $u$ solves $\mathcal{L}^\varepsilon[u] = 0$ in $\Omega$.
 From \eqref{e:cp_delta3} we also have
@@
 We note that at this point, by construction, $u$ may depend on $\eta$.
-We show that $u$ is the maximal solution of $\mathcal{L}[u] = 0$ in $\Omega$ such that $u = +\infty$ on $\partial\Omega$, and thus consequently showing that $u$ is independent of $\eta$.
-
-    \noindent Let $v\in W^{2,r}(\Omega)$ for all $r<\infty$ solving \eqref{eq:PDEeps}.
-Fix $\delta>0$, then for all $\vartheta>0$ small we see that on $\partial\overline{\Omega}_\vartheta$ the value of $v$ blows up as $\vartheta\to 0$, while $w_{\eta,\delta}$ remains bounded (we fixed $\delta>0$).
-Comparison principle gives us that $v\geq w_{\eta,\delta}$ on $\Omega_{\vartheta}$, thus as $\vartheta\to 0$ we obtain $v\geq w_{\eta,\delta}$ on $\Omega$.
-Let $\delta\to 0$ we deduce that $v\geq u$ on $\Omega$.
-This concludes that $u$ is the minimal solution in $W^{2,r}(\Omega)(\forall\,r<\infty)$ and thus independent of $\eta>0$.
+We show that $u$ is the maximal solution of $\mathcal{L}^\varepsilon[u] = 0$ in $\Omega$ such that $u = +\infty$ on $\partial\Omega$, thus consequently showing that $u$ is independent of $\eta$.
+
+    \noindent Let $v\in W^{2,r}(\Omega)$ for all $r<\infty$ and $v$ solves \eqref{eq:PDEeps}.
+Fix $\delta>0$ then since $v(x)\to \infty$ as $x\to \partial\Omega$ while $w_{\eta,\delta}$ remains bounded on $\partial \Omega$, comparison principle yields
+    \begin{equation*}
+        v\geq w_{\eta,\delta} \qquad\text{in}\Omega.
+    \end{equation*}
+    Let $\delta\to 0$ we deduce that $v\geq u$ on $\Omega$. This concludes that $u$ is the minimal solution in $W^{2,r}(\Omega)(\forall\,r<\infty)$ and thus $u$ is independent of $\eta>0$. 
 \end{proof}
@@
 \end{equation}
-for any $\eta>0$. This extra parameter $\eta$ now enables us to show that $\overline{u} = \underline{u}$ in $\Omega$.
+for any $\eta>0$. This extra parameter $\eta$ now enables us to show that $\overline{u} = \underline{u}$ in $\Omega$. The key ingredient here is the convexity of $\varrho\mapsto H(x,\varrho)$.
 
@@
 \end{prop}
+
 \begin{proof} Let $\theta\in (0,1)$, we cook up a subsolution by convex combination $w_\theta = \theta \overline{u} + (1-\theta)\lambda^{-1}\left(\inf_{\Omega} f\right)$, which if we can use comparison principle then
@@
 \subsection{Convergence result} We show the convergence (qualitatively) of \eqref{eq:PDEeps} to \eqref{eq:PDE0}.
-We first state the following Lemma (\cite{Capuzzo-Dolcetta1990}), which characterizes the state-constraint of first-order equation
+We first state the following Lemma (\cite{Capuzzo-Dolcetta1990}), which characterizes the state-constraint of the first-order equation
 \begin{equation}\label{S_0}
@@
 
-\begin{thm}[Qualitative result]\label{thm:qual} Assume $\mathrm{(A1)}$.
-Let $u^\varepsilon$ be the solution to \eqref{eq:PDEeps}, then there exists $u^0 \in \mathrm{C}(\overline{\Omega})$ such that $u^\varepsilon \rightarrow u^0$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$ and $u^0$ solves \eqref{eq:PDE0}.
-Furthermore
-\begin{equation*}
-    u^0 \leq u^\varepsilon \qquad\text{in}\;\Omega.
-\end{equation*}
+The following Theorem says that the large solution $u^\varepsilon$ converges to $u^0$ locally uniformly on $\Omega$ as $\varepsilon\to 0$.
+We present a simple proof here for the reader's convenience, see also \cite[Theorem VII.3]{Capuzzo-Dolcetta1990}.
+\begin{thm}[Vanishing viscosity - Qualitative result]\label{thm:qual} Assume $\mathrm{(A1)}$.
+Let $u^\varepsilon$ be the solution to \eqref{eq:PDEeps}, then there exists $u^0 \in \mathrm{C}(\overline{\Omega})$ such that $u^\varepsilon \rightarrow u^0$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$, $u^0$ solves \eqref{eq:PDE0} and $u^0 \leq u^\varepsilon$ in $\Omega$.
 \end{thm}
@@
 \end{equation}
+It is well-known that $v^\varepsilon_\delta\to v_\delta$ uniformly on $\overline{\Omega}_\delta$ as $\varepsilon\to 0$.
+
 For all $\delta$ small enough $v_\delta\leq u^\varepsilon$ on $\partial \Omega_\delta$, thus by maximum principle $v^\varepsilon_\delta \leq u^\varepsilon$ on $\overline{\Omega}_\delta$.
@@
 
+\subsection{Rate of convergence for first-order equation on nested domain - revisited}
+For $\lambda>0$, let $u\in \rmC(\overline{\Omega})$ and $u_\delta\in \rmC(\overline{\Omega}_\delta)$, respectively, state-constraint solutions to 
+\begin{equation*}
+    \begin{cases}
+    \lambda u(x)+H(x,Du(x)) \leq 0 \quad\text{in}\;\Omega,\\
+    \lambda u(x)+H(x,Du(x)) \geq 0 \quad\text{on}\;\overline{\Omega},
+    \end{cases}\qquad\text{and}\qquad 
+    \begin{cases}
+    \lambda u_\delta(x)+H(x,Du_\delta(x)) \leq 0 \quad\text{in}\;\Omega_\delta,\\
+    \lambda u_\delta(x)+H(x,Du_\delta(x)) \geq 0 \quad\text{on}\;\overline{\Omega}_\delta.
+    \end{cases}
+\end{equation*} 
+It is well-known that $0\leq u_\delta(x) - u(x) \leq C\delta$ for $x\in\overline{\Omega}_\delta$ and this rate is optimal.
+This can be proved easily by comparison principle when the domain have a scaling structure, i.e., $\Omega_\delta = (1-\delta)\Omega$ (see \cite{kim_state-constraint_2020}).
+In the general case when the scaling structure is not available but $\partial\Omega$ is smooth enough, for example $\partial\Omega$ is of class $\mathrm{C}^2$, one can construct a $\rmC^2$ diffeomorphism $T:\overline{\Omega}_\delta\to \overline{\Omega}$ that maps $\partial\Omega_\delta$ to $\partial\Omega$ and do scaling with
+\begin{equation*}
+ \tilde{u}_\delta(x) = u_\delta\left(T^{-1}(x)\right)   
+\end{equation*}
+defined on $\overline{\Omega}$ (see \cite{Capuzzo-Dolcetta1990}). We present here a simple proof using the doubling variables technique.
+
+\begin{thm}\label{thm:conv_general} Let $\Omega$ be an open, bounded and connected subset $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary. Assume $\mathrm{(H1)}-\mathrm{(H4)}$. 
+Then there exists a constant $C$ such that
+\begin{equation*}
+    0\leq u_\delta(x) - u(x) \leq C\delta \qquad\text{for}\; x\in \overline{\Omega}.
+\end{equation*}
+\end{thm}
+\begin{proof} We use $d(\cdot)$ to denote the extension of the distance function as in \eqref{e:distance_def}. Denote by $C_0$ the constant in the priori estimate
+\begin{equation*}
+    |u_\delta(x)| + |Du_\delta(x)|\leq C_0  \qquad\text{for}\;x\in \overline{\Omega}_\delta.
+\end{equation*}
+We note that this estimate with the same constant $C_0$ holds for $u\in \rmC(\overline{\Omega})$ as well. We will consider $\delta\in (0,1)$ small so that $0<\delta < \delta_1$ where 
+\begin{equation*}
+\delta_1 = \min\left\lbrace \delta_0,\frac{\mathrm{diam}(\Omega)\varepsilon_0}{2(4\tilde{C}_0+1)}\right\rbrace.    
+\end{equation*}
+Without loss of generality, let us assume $x_0\in \Omega$ and $d(x_0)\geq \mathrm{diam}(\Omega)\varepsilon_0\geq \delta$ for some $\varepsilon_0\in (0,1)$. We consider the auxiliary functional
+\begin{equation*}
+    \Phi^{\theta}(x,y) = u_\delta(x) - u(y) - \frac{2\tilde{C}_0\left|x-y\right|^2}{\theta^\beta} - \frac{C_3\theta^\beta}{d(y)}, \qquad(x,y)\in \overline{\Omega}_\delta\times \overline{\Omega}
+\end{equation*}
+where $C_3=2\left(4\tilde{C}_0+1\right)$ for some $\beta < 1$.
+Assume $\Phi^\delta(x,y)$ has a maximum over $\overline{\Omega}_\delta\times \overline{\Omega}$ at $(x_\theta,y_\theta)\in\overline{\Omega}_\delta\times \overline{\Omega}$.
+\begin{itemize}
+    \item $\Phi^\delta(x_\theta,y_\theta) \geq \Phi^\delta(x_0,x_0)$, which gives us
+    \begin{align*}
+        u_\delta(x_\theta) - u(y_\theta) - \frac{2\tilde{C}_0|x_\theta - y_\theta|^2}{\theta^\beta} - \frac{C_3\theta^\beta}{d(y_\theta)} \geq u_\delta(x_0) - u(x_0) - \frac{C_3\delta^\beta}{d(x_0)}. 
+    \end{align*}
+    Therefore, as $C_3 = 2(4\tilde{C}_0+1)$
+    \begin{align}\label{e:d(y)}
+        \frac{C_3\theta^\beta}{d(y_\theta)} \leq 4\tilde{C}_0 + \frac{C_3 \theta^\beta}{d(x_0)}  \leq 4\tilde{C}_0 + 1 \qquad\Longrightarrow\qquad d(y_\delta) \geq 2\theta^\beta \geq 2\delta
+    \end{align}
+    since $\beta < 1$.
+    \item Since $d(y_\theta)\geq 2\delta$, we have $y_\theta\in \Omega_\delta$ and thus $\Phi^\theta(x_\theta,y_\theta) \geq \Phi^\theta(y_\theta,y_\theta)$, which gives us
+    \begin{align*}
+        u_\delta(x_\theta) - u(y_\theta) - \frac{2\tilde{C}_0|x_\theta - y_\theta|^2}{\theta^\beta} - \frac{C_3\theta^\beta}{d(y_\theta)} \geq u_\theta(y_\theta) - u(y_\theta) - \frac{C_3\theta^\beta}{d(y_\theta)}.
+    \end{align*}
+    I.e.,
+    \begin{align*}
+        u_\delta(x_\theta)  - \frac{2\tilde{C}_0|x_\theta- y_\theta|^2}{\theta^\beta} \geq u_\delta(y_\theta) 
+    \end{align*}
+    and thus
+    \begin{equation*}
+        \frac{2\tilde{C}_0|x_\theta-y_\theta|^2}{\theta^\beta} \leq u_\delta(x_\theta) - u_\delta(y_\theta) \leq \tilde{C}_0|x_\theta-y_\theta|
+    \end{equation*}
+    and therefore
+    \begin{equation}\label{e:x-y}
+        |x_\theta-y_\theta|\leq \frac{\theta^\beta}{2}
+    \end{equation}
+    \item From \eqref{e:d(y)} and \eqref{e:x-y} we obtain that, if $z\in \partial\Omega$ then
+    \begin{align*}
+        |x_\delta - z| &= |(x_\delta - y_\delta) - (z - y_\delta)| \\
+        &\geq |z-y_\delta| - |x_\delta - y_\delta| \geq d(y_\delta) - |x_\delta - y_\delta| \geq 2\delta - \frac{\delta}{2} = \frac{3\delta}{2}.
+    \end{align*}
+    Therefore
+    \begin{equation*}
+        d(x_\delta) = \inf_{z\in \partial\Omega} |x_\delta - z|  \geq \frac{3\delta}{2}
+    \end{equation*}
+    and thus $x_\delta\in \Omega_\delta$.
+    \item $x\mapsto \Phi^\delta(x,y_\delta)$ has a maximum at $x_\delta\in \Omega_\delta$, thus
+    \begin{equation*}
+        \lambda u_\delta(x_\delta) + H\left(x_\delta, \frac{4\tilde{C}_0(x_\delta-y_\delta)}{\delta}\right) \leq 0.
+    \end{equation*}
+    \item $y\mapsto \Phi^\delta(x_\delta,y)$ has a maximum at $y_\delta\in \overline{\Omega}$, thus
+    \begin{equation*}
+        \lambda u(y_\delta) + H\left(y_\delta,\frac{4\tilde{C}_0(x_\delta-y_\delta)}{\delta} + C_3\delta^\beta\frac{Dd(y_\delta)}{d(y_\delta)^2} \right) \geq 0.
+    \end{equation*}
+\end{itemize}
+\end{proof}
+
 \section{Rate of convergence via Doubling variables - a toy case}
@@
 \begin{align*}
-    &\lambda u^\varepsilon(x_\sigma) + \left|\frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma} - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\nabla d(x_\sigma )\right|^p - f(x_\sigma)\\
-    &\qquad\qquad\qquad -\varepsilon\left(\frac{2n}{\sigma} + \frac{C_\varepsilon(\alpha+\beta)(\alpha+\beta+1)|\nabla d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+\beta+2}}-\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\Delta d(x_\sigma)\right)  \leq 0.
-\end{align*}
-\paragraph{\textcolor{blue}{\textbf{Step 4.}}} $y\mapsto \Phi^\sigma(x_\sigma,y)$ has a maximum at $y_\sigma\in \overline{\Omega}$, thus 
+    &\lambda u^\varepsilon(x_\sigma) + \left|\frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma} - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma )\right|^p - f(x_\sigma)\\
+    &\qquad\qquad\qquad -\varepsilon\left(\frac{2n}{\sigma} + \frac{C_\varepsilon(\alpha+\beta)(\alpha+\beta+1)|D d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+\beta+2}}-\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\Delta d(x_\sigma)\right)  \leq 0.
+\end{align*}
+\paragraph{\textcolor{blue}{\textbf{Step 4.}}} $y\mapsto \Phi^\sigma(x_\sigma,y)$ has a maximum at $y_\sigma\in \overline{\Omega}_\delta$, thus 
 \begin{equation*}
@@
 \begin{equation*}
-    \xi_\sigma = \frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma} \qquad\text{and}\qquad \zeta_\sigma = - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\nabla d(x_\sigma)
+    \xi_\sigma = \frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma} \qquad\text{and}\qquad \zeta_\sigma = - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma)
 \end{equation*}
@@
 \begin{equation*}
- |\zeta_\sigma|=   \left|\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\nabla d(x_\sigma )\right| \leq \frac{C_\varepsilon(\alpha+\beta)}{\sigma^{\alpha+\beta+1}}\leq \frac{\alpha+\beta}{\alpha} (\alpha+1)^\frac{1}{p-1}\frac{\varepsilon^\frac{1}{p-1}}{\sigma^{\alpha+\beta+1}}.
+ |\zeta_\sigma|=   \left|\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma )\right| \leq \frac{C_\varepsilon(\alpha+\beta)}{\sigma^{\alpha+\beta+1}}\leq \frac{\alpha+\beta}{\alpha} (\alpha+1)^\frac{1}{p-1}\frac{\varepsilon^\frac{1}{p-1}}{\sigma^{\alpha+\beta+1}}.
 \end{equation*}
@@
 \end{equation}
-\paragraph{\textcolor{blue}{\textbf{Step 6.}}} Recall $|\nabla d(x_\sigma)| = 1$, we have
+\paragraph{\textcolor{blue}{\textbf{Step 6.}}} Recall $|D d(x_\sigma)| = 1$, we have
 \begin{align}
-    \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) &\leq \underbrace{\left|\frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma}\right|^p}_{|\xi_\sigma|^p} - \underbrace{ \left|\frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma} - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\nabla d(x_\sigma )\right|^p}_{|\xi_\sigma+\zeta_\sigma|^p} \nonumber\\
+    \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) &\leq \underbrace{\left|\frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma}\right|^p}_{|\xi_\sigma|^p} - \underbrace{ \left|\frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma} - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma )\right|^p}_{|\xi_\sigma+\zeta_\sigma|^p} \nonumber\\
     &+ \underbrace{f(y_\sigma) - f(x_\sigma)}_{\mathfrak{F}|x_\sigma - y_\sigma|} + \varepsilon\left(\frac{2n}{\sigma} + \underbrace{\frac{C_\varepsilon(\alpha+\beta)(\alpha+\beta+1)}{d(x_\sigma)^{\alpha+\beta+2}}}_{\frac{C_\varepsilon (\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta + 1}}.\frac{\alpha+\beta+1}{d(x_\sigma)}}-\underbrace{\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\Delta d(x_\sigma)}_{\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}.\Delta d(x_\sigma)}\right)\nonumber\\

### 2021-04-06 Drafts and notes/Attempts/Old_draft_07.tex
Major change

--- 2021-04-06 Drafts and notes/Attempts/Old_draft_06.tex
@@
 \begin{abstract}
-We investigate qualitatively the convergence of large, or state-constraint solution to nonlinear elliptic equation as the viscosity vanish.
+We investigate qualitatively the convergence of large, or state-constraint solution to nonlinear elliptic equation as the viscosity vanishes.
 \end{abstract}
@@
 \end{itemize}
+    The following assumptions on $\Omega$ will also be used.
+\begin{itemize}    
+    \item[(A2)] There exists a universal pair of positive numbers $(r,h)$ and $\eta\in \mathrm{BUC}(\overline{\Omega};\mathbb{R}^n)$ such that $B(x+t\eta(x), rt)\subset\Omega$ for all $t\in (0,h]$.
+    \item[(A3)] $\Omega$ is a bounded and star-shaped (with respect to the origin) open subset of $\mathbb{R}^n$ such that
+    \begin{equation*}
+        \mathrm{dist}(x,\overline{\Omega}) \geq \kappa r \qquad\text{for all}\; x\in (1+r) \partial\Omega, \;\text{for all}\;r>0,
+    \end{equation*}
+for some $\kappa > 0$.
+\end{itemize}
+Assumption $\mathrm{(A1)}$ follows \cite{Lasry1989}, where the specific structure of the Hamiltonian enables more explicit estimates on the solution of \eqref{eq:PDEeps}.
+Assumptions $\mathrm{(A2)}$ or $\mathrm{(A3)}$ guarantees a comparison principle holds for the state-constraint problem \eqref{eq:PDE0}.
+We note that $\mathrm{(A1)}$ was first studied by M.
+Soner in \cite{Soner1986} (and $\mathrm{(A1)}$ holds for any smooth bounded domain), while $\mathrm{(A2)}$ was posed and studied by I.
+Capuzzo-Dolcetta and P.
+L.
+Lions in \cite{Capuzzo-Dolcetta1990}.
 We list the assumptions on a general Hamiltonian as follow.
@@
 \end{equation}
-We recall that $|D d(x)| = 1$ in the viscosity sense (and thus in classical sense) in $\Omega^{\delta_0}\backslash \Omega_{\delta_0}$.
-Since $x\mapsto \mathrm{dist}(x,\partial \Omega)$ is a viscosity solution to $|Du(x)|=1$ in $\Omega$.
-%we can assume that the extension $d(x)$ as also satisfies $|Dd(x)|\leq 1$ in $\Omega$.
-Let 
+We recall that $|D d(x)| = 1$ in the viscosity sense (and thus in classical sense) in $\Omega^{\delta_0}\backslash \Omega_{\delta_0}$. Let 
 \begin{equation*}
@@
 \end{thm}
-
-\begin{proof} Let $\theta\in (0,1)$ be chosen later, $\varphi\in \mathrm{C}_c^\infty(\Omega)$, $0\leq \varphi\leq 1$, $\mathrm{supp}\;\varphi\subset \Omega$ and $\varphi = 1$ on $\Omega_\delta$ such that
+\noindent We provide a proof for this Theorem in Appendix for the reader's convenience.
+
+\subsection{Well-posedness of large solution for subquaratic case} In this section, with the specific form of the Hamiltonian $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$, we show the existence and uniqueness of solutions to \eqref{eq:PDEeps}.
+We note that the assumption of $f$ can be relaxed to $f\in L^\infty(\Omega)$, but for the clarity of the proof we will assume $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
+
+\begin{thm}\label{thm:wellposed1<p<2} If $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ then there exists a unique solution $u^\varepsilon\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that
+\begin{equation*}
+    %\frac{C_\varepsilon-\eta}{d(x)^\alpha}-\frac{M_\eta}{\lambda} \leq u(x)\leq \frac{C_\varepsilon+\eta}{d(x)^\alpha}+\frac{M_\eta}{\lambda} 
+    \lim_{d(x)\to 0} u^\varepsilon(x) \,d(x)^\alpha = C_\varepsilon 
+\end{equation*}
+where
+\begin{equation*}
+    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^{\alpha+1}\right) \varepsilon^{\alpha+1}.
+\end{equation*}
+\end{thm}
+\noindent This is Theorem I.1 in \cite{Lasry1989}.
+We provide a proof in Appendix with the explicit dependence of $C_\varepsilon$ in terms of $\varepsilon$ for later use, it is useful to note that $\alpha+1 = \frac{1}{p-1}$.
+
+\subsection{Convergence result} We show the convergence (qualitatively) of \eqref{eq:PDEeps} to \eqref{eq:PDE0}.
+We first state the following Lemma (\cite{Capuzzo-Dolcetta1990}), which characterizes the state-constraint of the first-order equation
+\begin{equation}\label{S_0}
+ \lambda u(x) + H(x,Du(x)) = 0\;\qquad\text{in}\;\Omega. \tag{$S_0$}
+\end{equation}
+
+\begin{lem}\label{lem:max} Let $u\in \rmC(\overline{\Omega})$ be a viscosity subsolution of \eqref{S_0} such that, for all viscosity subsolution $v\in \rmC(\overline{\Omega})$ of \eqref{S_0} one has $v\leq u$ in $\overline{\Omega}$, then $u$ is a viscosity supersolution of \eqref{S_0} on $\overline{\Omega}$.
+\end{lem}
+\noindent Lemma \ref{lem:max} is a variation of Perron's method.
+We give a proof in Appendix for the sake of completeness.
+Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ be a solution to \eqref{eq:PDEeps}, we claim that $\{\lambda u^\varepsilon\}_{\varepsilon>0}$ is uniformly bounded from below by a constant independent of $\varepsilon$ and $\lambda$.
+We have
+\begin{equation*}
+    u^\varepsilon(x) = \lim_{m\to \infty} u^{\varepsilon}_m(x), \qquad x\in \Omega,
+\end{equation*}
+ where $u^{\varepsilon,m}\in \mathrm{C}^2(\Omega)\cap \rmC(\overline{\Omega})$ solves the Drichlet problem
+\begin{equation}\label{e:uepsm}
+    \begin{cases}
+    \lambda u(x) + H(x,Du(x)) - \varepsilon \Delta u(x) = 0 &\qquad
+    \text{in}\;\Omega, \vspace{0cm}\\
+    \;\;\quad\quad\qquad\qquad\qquad\qquad u(x) = m &\qquad
+    \text{on}\;\partial\Omega.
+    \end{cases} \tag{PDE$_{\varepsilon,m}$}
+\end{equation}
+If we assume $\mathrm{(H2)}$ then we can take $C_2 = \Vert f\Vert_{L^\infty(\Omega)}$ and take $\varphi(x) \equiv -\lambda^{-1}C_2$ for $x\in \overline{\Omega}$ as a subsolution to \eqref{e:uepsm}, hence by comparison principle for \eqref{e:uepsm} we have $u^{\varepsilon}_m(x)\geq -\lambda^{-1}C_2$ for all $x\in \overline{\Omega}$, thus as $m\to \infty$ we obtain $u^\varepsilon(x) \geq -\lambda^{-1}C_2$ for all $x\in \Omega$.
+
+The following Theorem says that the large solution $u^\varepsilon$ converges to $u^0$ locally uniformly on $\Omega$ as $\varepsilon\to 0$.
+We present a simple proof here for the reader's convenience, see also \cite[Theorem VII.3]{Capuzzo-Dolcetta1990}.
+\begin{thm}[Vanishing viscosity - Qualitative result]\label{thm:qual} Assume $\mathrm{(A1)}$.
+Let $u^\varepsilon$ be the solution to \eqref{eq:PDEeps}, then there exists $u^0 \in \mathrm{C}(\overline{\Omega})$ such that $u^\varepsilon \rightarrow u^0$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$, $u^0$ solves \eqref{eq:PDE0} and $u^0 \leq u^\varepsilon$ in $\Omega$.
+\end{thm}
+
+\begin{proof}[Proof of Theorem \ref{thm:qual}] By a priori estimate (Theorem \ref{thm:grad_1})
+\begin{equation}\label{e:priorie_eps}
+    |u^\varepsilon(x)| + |Du^\varepsilon(x)| \leq C_\delta \qquad\text{for}\;x\in \overline{\Omega}_\delta
+\end{equation}
+we deduce from the Arzel\'a--Ascoli theorem that there exists a subsequence $\varepsilon_j\to 0$ and a function $u^0\in \rmC(\Omega)$ such that $u^{\varepsilon_j}\to u^0$ locally uniformly in $\Omega$.
+By the stability of viscosity solution we easily deduce that
+\begin{equation}\label{eq:u0int}
+   \lambda u^0(x) + H(x,Du^0(x)) = 0 \qquad\text{in}\;\Omega.
+\end{equation}
+Since $\lambda u^\varepsilon(x)\geq -C_2$ for all $x\in \Omega$, we also have $\lambda u^0(x)\geq -C_2$ for all $x\in \Omega$, thus together with \eqref{eq:u0int} we obtain $H(x,\xi) \leq C_2$ for all $\xi\in D^+u^0(x)$ and $x\in \Omega$.
+The coercivity $\mathrm{(H4)}$ implies that there exists $K>0$ such that
+\begin{equation*}
+    |u^0(x) - u^0(y)| \leq K \qquad\text{for all}\;x,y\in \Omega.
+\end{equation*}
+Thus we can extend $u^0$ uniquely to $u^0\in \rmC(\overline{\Omega})$.
+We will use Lemma \ref{lem:max} to show that $u^0$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$.
+It suffices to show that $u^0\geq w$ on $\overline{\Omega}$ where $w\in \rmC(\overline{\Omega})$ is the unique solution to \eqref{eq:PDE0}.
+
+For $\delta>0$, let $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\partial \Omega) > \delta\}$ and $v_\delta\in\rmC(\overline{\Omega}_\delta)$ be the state-constraint viscosity solution to the problem $\lambda u(x) + H(x,Du(x)) = 0$ in $\Omega_\delta$, i.e., $v_\delta$ is the unique viscosity solution to
+\begin{equation}\label{e:v_v}
+    \begin{cases}
+    \lambda v_\delta(x) + H(x,Dv_\delta(x)) \leq 0 &\qquad\text{in}\;\Omega_\delta,\\
+    \lambda v_\delta(x) + H(x,Dv_\delta(x)) \geq 0 &\qquad\text{on}\;\overline{\Omega}_\delta.
+    \end{cases}
+\end{equation}
+As $v_\delta\rightarrow w$ locally uniformly as $\delta\rightarrow 0^+$ (see \cite{kim_state-constraint_2020}) and $w$ is bounded, therefore $\{v_\delta\}_{\delta>0}$ is uniformly bounded.
+Let $v^\varepsilon_\delta\in \rmC^2(\Omega_\delta)\cap \rmC(\overline{\Omega}_\delta)$ be the unique solution to the Dirichlet problem
+\begin{equation}\label{eq:vv_eps}
+\begin{cases}
+    \lambda v_\delta^\varepsilon(x) + |Dv_\delta^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v_\delta^\varepsilon(x) &\qquad\text{in}\;\Omega_\delta,\\
+    \;\;\;\,\quad\qquad\qquad\qquad\qquad v_\delta^\varepsilon = v_\delta &\qquad \text{on}\;\partial\Omega_\delta.
+\end{cases}
+\end{equation}
+It is well-known that $v^\varepsilon_\delta\to v_\delta$ uniformly on $\overline{\Omega}_\delta$ as $\varepsilon\to 0$.
+
+For all $\delta$ small enough $v_\delta\leq u^\varepsilon$ on $\partial \Omega_\delta$, thus by maximum principle $v^\varepsilon_\delta \leq u^\varepsilon$ on $\overline{\Omega}_\delta$.
+Let $\varepsilon\to 0$ we have $v_\delta \leq u^0$ on $\overline{\Omega}_\delta$.
+Let $\delta\rightarrow 0$ we obtain $w\leq u^0$ in $\Omega$, which implies $w\leq u^0$ on $\overline{\Omega}$ since both $w,u^0$ belong to $\rmC(\overline{\Omega})$.
+\end{proof}
+
+\subsection{Rate of convergence for first-order equation on nested domain}
+For $\delta >0$, let $u\in \rmC(\overline{\Omega})$ and $u_\delta\in \rmC(\overline{\Omega}_\delta)$, respectively, be viscosity state-constraint solutions to 
+\begin{equation*}
+    \begin{cases}
+    \lambda u(x)+H(x,Du(x)) \leq 0 \quad\text{in}\;\Omega,\\
+    \lambda u(x)+H(x,Du(x)) \geq 0 \quad\text{on}\;\overline{\Omega},
+    \end{cases}\qquad\text{and}\qquad 
+    \begin{cases}
+    \lambda u_\delta(x)+H(x,Du_\delta(x)) \leq 0 \quad\text{in}\;\Omega_\delta,\\
+    \lambda u_\delta(x)+H(x,Du_\delta(x)) \geq 0 \quad\text{on}\;\overline{\Omega}_\delta.
+    \end{cases}
+\end{equation*} 
+It is well-known that $0\leq u_\delta(x) - u(x) \leq C\delta$ for $x\in\overline{\Omega}_\delta$ and this rate is optimal.
+This can be proved easily by comparison principle when the domain have a scaling structure with $\mathrm{(A3)}$ holds, i.e., $\Omega_\delta = (1-\delta)\Omega$ (see \cite{kim_state-constraint_2020}).
+We have the following theorem for the general smooth domains.
+
+\begin{thm}\cite{Capuzzo-Dolcetta1990}\label{thm:conv_general} Let $\Omega$ be an open, bounded and connected subset $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary. Assume $\mathrm{(H1)}-\mathrm{(H4)}$. 
+Then there exists a constant $C$ independent of $\delta$ such that
+\begin{equation*}
+    0\leq u_\delta(x) - u(x) \leq C\delta \qquad\text{for}\; x\in \overline{\Omega}.
+\end{equation*}
+\end{thm}
+\begin{proof}[Proof of Theorem \ref{thm:conv_general}] Following \cite{Capuzzo-Dolcetta1990}, we construct a $\rmC^2$ diffeomorphism $T:\overline{\Omega}_\delta\to \overline{\Omega}$ that maps $\partial\Omega_\delta$ to $\partial\Omega$ and satisfies
+\begin{equation}\label{e:bound_T}
+    \sup_{x\in \overline{\Omega}_\delta}\Big(|T(x)-x| + |DT(x) - \mathrm{Id}|\Big) \leq C\delta
+\end{equation}
+for some constant $C$ independent of $\delta$.
+Let us define $\tilde{u}_\delta(x) = u_\delta\left(T^{-1}(x)\right)$ for $x\in \overline{\Omega}$.
+Using $\mathrm{(H4)}$ and \eqref{e:bound_T} we obtain that $\tilde{u}_\delta$ is a viscosity subsolution to
+\begin{equation*}
+    \lambda \tilde{u}_\delta(x) + H(x,D\tilde{u}_\delta(x))  = C\delta \qquad\text{in}\;\Omega.
+\end{equation*}
+Therefore by comparison principle $0\leq \tilde{u}_\delta(x) - u(x) \leq C\delta$ on $\overline{\Omega}$, i.e., $0\leq \tilde{u}_\delta(Ty) - u(Ty) \leq C\delta$ on $\overline{\Omega}_\delta$, hence
+\begin{equation*}
+    0 \leq u_\delta(y) - u(y) \leq u_\delta(y) - u(Ty) + u(Ty) - u(y) \leq C\delta
+\end{equation*}
+since $u$ is Lipschitz on $\overline{\Omega}$.
+\end{proof}
+
+\section{Rate of convergence via the doubling variables method}
+\noindent The main result is the following Theorem.
+\begin{thm}\label{thm:rate_doubling1} Let $\Omega$ be an open, bounded and connected subset $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary.
+Assume $\mathrm{(A1)},\mathrm{(H1)}-\mathrm{(H4)}$ and $1<p<2$.
+Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u^0$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that
+\begin{equation*}
+    0\leq u^\varepsilon(x) - u^0(x) \leq C\sqrt{\varepsilon} \qquad\text{for}\;x\in \Omega_{2\sqrt{\varepsilon}}.
+\end{equation*}
+\end{thm}
+
+\begin{proof}[Proof of Theorem \ref{thm:rate_doubling1}] Let $u_\delta\in \mathrm{C}(\overline{\Omega}_\delta)$ be the state-constraint solution to
+\begin{equation}\label{e:PDE_delta}
+    \begin{cases}  
+    \lambda u_\delta(x) + H(x,Du_\delta(x)) \leq 0 \qquad\text{in}\; \Omega_\delta\\
+    \lambda u_\delta(x) + H(x,Du_\delta(x)) \geq 0 \qquad\text{on}\; \overline{\Omega}_\delta.
+    \end{cases} \tag{PDE$_\delta$}
+\end{equation} 
+Let $C_f$ be the Lipschitz constant of $f$ and $\beta,\sigma,\delta \in (0,1)$ to be chosen later.
+Recall the definition of $C_\varepsilon$ from Theorem \ref{thm:wellposed1<p<2}, we define the auxiliary functional
+\begin{align*}
+    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u_\delta(y) - \frac{C_0|x-y - \delta \nabla d(x)|^2}{\sigma}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}_\delta,
+\end{align*}
+where $C_0$ is the Lipschitz constant of $u^0$ (also the Lipschitz constant of $u_\delta$ for $\delta>0$). We split the proof into several steps.
+\begin{enumerate}
+    \item[1.] Since $u^\varepsilon (x)d(x)^\alpha \to C_\varepsilon$ as $d(x)\to 0$, we see that $\Phi^\sigma(x,y)\to -\infty$ as $d(x)\to 0$, therefore for a fixed $\varepsilon>0$, there is $(x_{\sigma},y_\sigma)\in \Omega\times\overline{\Omega}_\delta$ such that
+\begin{equation*}
+    \max_{\overline{\Omega}\times \overline{\Omega}_\delta} \Phi^\sigma = \Phi^\sigma(x_\sigma,y_\sigma).
+\end{equation*}
+We can assume that 
+\begin{equation}\label{e:ass_delta0}
+    d(x_\sigma) < \delta_0
+\end{equation}
+so that $|Dd(x_\sigma)| = 1$. We will mention how the case $d(x_\sigma)\geq \delta_0$ is easily deduced at the end of the proof.
+\item[2.] $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(x_\sigma,x_\sigma)$ gives us that
+    \begin{equation}\label{e:est_sigma2}
+     \frac{C_0|x_\sigma-y_\sigma|^2}{\sigma} \leq u_\delta(x_\sigma) - u_\delta(y_\sigma) \leq C_0|x_\sigma-y_\sigma| \qquad\Longrightarrow\qquad |x_\sigma -y _\sigma|\leq \sigma.
+    \end{equation}
+    This gives us that
+    \begin{equation}\label{e:est_sigma3}
+        d(x_\sigma) \geq d(y_\sigma) - |x_\sigma-y_\sigma|\geq \delta-\sigma.
+    \end{equation}
+    Let $\delta = 2\sigma$, we deduce that $d(x_\sigma)\geq \sigma$.
+    \item[3.] $x\mapsto \Phi^\sigma(x,y_\sigma)$ has a maximum at $x_\sigma\in \Omega$, thus by subsolution test for \eqref{eq:PDEeps} we have
+\begin{align}\label{e:sub1}
+    &\lambda u^\varepsilon(x_\sigma) + \left|\frac{2C_0(x_\sigma-y_\sigma)}{\sigma} - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma )\right|^p - f(x_\sigma)\nonumber\\
+    &\qquad\qquad -\varepsilon\left(\frac{2n}{\sigma} + \frac{C_\varepsilon(\alpha+\beta)(\alpha+\beta+1)|D d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+\beta+2}}-\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\Delta d(x_\sigma)\right)  \leq 0.
+\end{align}
+\item[4.] Let
+\begin{equation}\label{e:est_xi_zeta}
+    \xi_\sigma = \frac{2C_0(x_\sigma-y_\sigma)}{\sigma} \qquad\text{and}\qquad \zeta_\sigma = - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma)
+\end{equation}
+then $|\xi_\sigma|\leq 2C_0$ by \eqref{e:est_sigma2} and furthermore $\xi_\sigma+\zeta_\sigma \in D^-u^\varepsilon(x_\sigma)$, which, by the local gradient estimate, as $x_\sigma\in \Omega_{\sigma}$, $\xi_\sigma+\zeta_\sigma$ is bounded in terms of $\sigma$ and will blow up as $\sigma\to 0$.
+Nevertheless, we can do better as following.
+\begin{align*}
+    |\zeta_\sigma|=\left|\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma )\right| \leq \frac{C_\varepsilon(\alpha+\beta)}{\sigma^{\alpha+\beta+1}} 
+    &\leq \frac{(\alpha+\beta)(\alpha+1)^{\alpha+1}}{\alpha} \frac{\varepsilon^{\alpha+1}}{\sigma^{\alpha+\beta+1}} \\
+    &= \frac{(\alpha+\beta)(\alpha+1)^{\alpha+1}}{\alpha}\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)}
+\end{align*}
+by choosing $\sigma = \varepsilon^\gamma$ where
+\begin{equation*}
+ \displaystyle 0 < \gamma < \frac{\alpha+1}{\alpha+1+\beta}.
+\end{equation*}
+In particular, $|\zeta_\sigma|\leq \mathfrak{C}_\alpha$ where $\mathfrak{C}_\alpha = \alpha^{-1}(\alpha+\beta)(\alpha+1)^{\alpha+1}$.
+\item[5.] $y\mapsto \Phi^\sigma(x_\sigma,y)$ has a maximum at $y_\sigma\in \overline{\Omega}_\delta$, thus by supersolution test for \eqref{e:PDE_delta} we have 
+\begin{equation}\label{e:super1}
+    \lambda u_\delta(y_\sigma) + \left|\frac{2C_0(x_\sigma-y_\sigma)}{\sigma}\right|^p - f(y_\sigma) \geq 0.
+\end{equation}
+\item[6.] Recall that $|D d(x_\sigma)| = 1$, from \eqref{e:sub1}, \eqref{e:super1}, $d(x_\sigma)\geq \sigma$ and $|x_\sigma-y_\sigma|\leq \sigma$ we have
+\begin{align}
+    &\lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) \leq |\xi_\sigma|^p - |\xi_\sigma+\zeta_\sigma|^p + f(y_\sigma) - f(x_\sigma) \nonumber\\
+    &\qquad\qquad\qquad\quad + \varepsilon\left(\frac{2n}{\sigma} + \frac{C_\varepsilon(\alpha+\beta)(\alpha+\beta+1)}{d(x_\sigma)^{\alpha+\beta+2}} - \frac{C_\varepsilon(\alpha+\beta)\Delta d(x_\sigma)}{d(x_\sigma)^{\alpha+\beta +1}}\right)\nonumber \\
+    &\qquad\qquad\qquad\quad\leq |\xi_\sigma|^p - |\xi_\sigma+\zeta_\sigma|^p + C_f\sigma +\varepsilon \left(\frac{2n}{\sigma} + \frac{(\alpha+\beta+1)|\zeta_\sigma|}{\sigma} + K_1|\zeta_\sigma|\right) \label{e:est3}
+\end{align}
+where $K_2 = \max_{x\in \overline{\Omega}}\Delta d(x)$. Using the estimate
+\begin{align*}
+    \left||x+y|^p - |x|^p \right| \leq  p\big(|x|+|y|\big)^{p-1}|y|
+\end{align*}
+with $x = \xi_\sigma$, $y = \zeta_\sigma$ and the fact that $|\zeta_\sigma|\leq \mathfrak{C}_\alpha$ we obtain
+\begin{align}
+    \Big||\xi_\sigma+\zeta_\sigma|^p - |\xi|^p\Big| &\leq p\Big(|\xi_\sigma|+|\zeta_\sigma|\Big)^{p-1}|\zeta_\sigma| \leq K_3\varepsilon ^{\alpha+1  - \gamma(\alpha+1+\beta)}\label{e:est2}
+\end{align}
+where $K_3 = p\mathfrak{C}_\alpha(2C_0+\mathfrak{C}_\alpha)^{p-1}$. From \eqref{e:est3} and \eqref{e:est2} and $\sigma = \varepsilon^\gamma$ we deduce that
+\begin{align*}
+    \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) &\leq   K_3\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)}+ C_f\varepsilon^\gamma + 2n \varepsilon^{1-\gamma}\\
+    & + (\alpha+\beta + 1)\mathfrak{C}_\alpha \varepsilon^{\alpha+2 - \gamma(\alpha+2+\beta)} + K_1\mathfrak{C}_\alpha\varepsilon^{\alpha+2 - \gamma(\alpha+1+\beta)}.
+\end{align*}
+\item[7.] As $p\in (1,2)$, we have $\alpha\in (0,1)$, therefore we can always pick $\beta \in (0,\alpha)$ and $\gamma = \frac{1}{2}$ to deduce that 
+\begin{equation*}
+     \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) \leq K_4 \sqrt{\varepsilon}
+\end{equation*}
+where 
+\begin{equation*}
+    K_4 = \max\big\lbrace K_3,C_f,2n, (\alpha+\beta+1)\mathfrak{C}_\alpha, K_1\mathfrak{C}_\alpha \big\rbrace.   
+\end{equation*}
+\item[8.] We recall that $\delta = 2\sigma = \sqrt{\varepsilon}$. Using $\Phi^\sigma(x_\sigma,y_\sigma)\geq \Phi^\sigma(x,x)$ for all $x\in \overline{\Omega}_\delta$ we have
+\begin{equation*}
+    \lambda u^\varepsilon(x) - \lambda u_\delta(x) - \frac{C_\varepsilon}{d(x)^{\alpha+\beta}} \leq \Phi^\sigma(x_\sigma,y_\sigma) \leq \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) \leq K_4\sqrt{\varepsilon}.
+\end{equation*}
+Therefore, using the fact that $d(x)\geq \delta = 2\sqrt{\varepsilon}$ as $x\in \overline{\Omega}_\delta$ and $\alpha+1 - \frac{\alpha+\beta}{2} > 1$ we have
+\begin{align}
+    \lambda u^\varepsilon(x) - \lambda u_\delta(x) &\leq K_4\sqrt{\varepsilon} + \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}\nonumber \\
+    &\leq K_4\sqrt{\varepsilon} + \frac{(\alpha+1)^{\alpha+1}}{2^{\alpha+\beta}\alpha}\varepsilon^{\alpha+1 - \frac{\alpha+\beta}{2}}\leq K_5 \sqrt{\varepsilon}\label{e:almost}
+\end{align}
+for all $x\in \overline{\Omega}_{2\sqrt{\varepsilon}}$ where
+\begin{equation*}
+    K_5 = \max\left\lbrace K_4, \frac{(\alpha+1)^{\alpha+1}}{2^{\alpha+\beta}\alpha}\right\rbrace.
+\end{equation*}
+\end{enumerate}
+From Theorem \ref{thm:conv_general} we have that
+\begin{equation}\label{e:citepaper}
+    0\leq \lambda u_\delta(x) - \lambda u^0(x)\leq C_H\delta \qquad\text{for all}\; x\in \overline{\Omega}_\delta
+\end{equation}
+where $C_H$ is independent of $\delta$. From \eqref{e:almost} and \eqref{e:citepaper} with $\delta = 2\sqrt{\varepsilon}$, we deduce that
+\begin{align*}
+    0 \leq \lambda u^\varepsilon(x) - \lambda u^0(x) \leq \left(K_5 + 2C_H\right)\sqrt{\varepsilon} \qquad\text{for all}\; x\in \overline{\Omega}_{2\sqrt{\varepsilon}}.
+\end{align*}
+Finally, we mention the case where \eqref{e:ass_delta0} does not hold, i.e., $d(x_\sigma)\geq \delta_0$ instead.
+All the steps carry out the same with some modifications.
+Instead of \eqref{e:est_xi_zeta} we have
+\begin{equation*}
+    |\zeta_\sigma| \leq K_2\mathfrak{C}_\alpha \delta_0^{-(\alpha+\beta+1)} \varepsilon^{\alpha+1}
+\end{equation*}
+and at this point $\sigma$ is still independent of $\varepsilon$. 
+\end{proof}
+
+\section{Rate of convergence via nonlinear adjoint method}
+
+%\nocite{*}
+
+\begin{appendices}
+\section{Proofs of some preliminary results}
+\begin{proof}[Proof of Theorem \ref{thm:grad_1}] Let $\theta\in (0,1)$ be chosen later, $\varphi\in \mathrm{C}_c^\infty(\Omega)$, $0\leq \varphi\leq 1$, $\mathrm{supp}\;\varphi\subset \Omega$ and $\varphi = 1$ on $\Omega_\delta$ such that
 \begin{equation}\label{e:ass_power}
@@
 for $x\in \Omega$ and $C = C(\delta,\theta)$.
-Let $w(x) = |Du(x)|^2$ for $x\in \Omega$, the goal is to derive an equation for $\varphi w$. The equation for $w$ is given by
+Let $w(x) = |Du(x)|^2$ for $x\in \Omega$. The goal is to derive an equation for $\varphi w$. The equation for $w$ is given by
 \begin{equation*}
@@
 \end{align*}
-Assume that $\varphi w$ achieves its maximum over $\overline{\Omega}$ at $x_0\in \Omega$ then we can assume that $x_0\in \mathrm{supp}\;\varphi$, since otherwise the maximum of $\varphi w$ over $\overline{\Omega}$ is zero.
+Assume that $\varphi w$ achieves its maximum over $\overline{\Omega}$ at $x_0\in \Omega$, then we can assume that $x_0\in \mathrm{supp}\;\varphi$, since otherwise the maximum of $\varphi w$ over $\overline{\Omega}$ is zero.
 By the classical maximum principle
@@
 
-\subsection{Well-posedness of large solution for subquaratic case} In this section, with the specific form of the Hamiltonian $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$, we show the existence and uniqueness of solutions to \eqref{eq:PDEeps}.
-We note that the assumption of $f$ can be relaxed to $f\in L^\infty(\Omega)$, but for the clarity of the proof we will assume $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
-
-\begin{thm} If $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ then there exists a unique solution $u^\varepsilon\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that
-\begin{equation*}
-    %\frac{C_\varepsilon-\eta}{d(x)^\alpha}-\frac{M_\eta}{\lambda} \leq u(x)\leq \frac{C_\varepsilon+\eta}{d(x)^\alpha}+\frac{M_\eta}{\lambda} 
-    \lim_{d(x)\to 0} u^\varepsilon(x) \,d(x)^\alpha = C_\varepsilon 
-\end{equation*}
-where
-\begin{equation*}
-    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}\right) \varepsilon^{\frac{1}{p-1}}.
-\end{equation*}
-\end{thm}
-
-\begin{proof}
-
-\noindent To find a candidate for subsolution and supersolution to \eqref{eq:PDEeps}, we use the \emph{ansatz}
+\begin{proof} [Proof of Theorem \ref{thm:wellposed1<p<2}] To find a candidate for subsolution and supersolution to \eqref{eq:PDEeps}, we use the \emph{ansatz}
 \begin{equation}\label{eq:ansatz}
@@
 \end{equation}
-We note that $\alpha+1 = \frac{1}{p-1}$ for convenience later. Recall that $_1 = \max_{\overline{\Omega}}|\Delta d(x)|$, let us denote
+We note that $\alpha+1 = \frac{1}{p-1}$ for convenience later. Recall that $K_1 = \max_{\overline{\Omega}}|\Delta d(x)|$, let us denote
 \begin{equation*}
@@
 \end{lem}
-\noindent The reason why we state this lemma again instead of just citing \cite{Lasry1989} is because we want to show that the constant $M_\varepsilon$ here can be chosen independent of $\eta$ as long as $\eta \geq G\varepsilon^{\alpha+1}$, thus $\{M_\varepsilon\}_{\varepsilon>0}$ is bounded.
+
 \begin{proof} Recall that $p(\alpha+1) = \alpha+2$, we compute
@@
          \mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) &= \frac{\lambda(C_\varepsilon + \eta)}{(d(x)-\delta)^\alpha} + M - f(x)\\
-         & + \frac{\alpha^p C_\varepsilon^p}{(d(x)-\delta)^{\alpha+2}}\nu\left(\nu^{p-1} - 1 - \frac{ (d(x)-\delta)\Delta d(x)}{(\alpha+1)}\right).
+         & + \frac{\alpha^p C_\varepsilon^p\nu }{(d(x)-\delta)^{\alpha+2}}\left(\nu^{p-1} - 1 - \frac{ (d(x)-\delta)\Delta d(x)}{(\alpha+1)}\right).
     \end{align*}
@@
 
-\begin{proof} Let $\theta\in (0,1)$, we cook up a subsolution by convex combination $w_\theta = \theta \overline{u} + (1-\theta)\lambda^{-1}\left(\inf_{\Omega} f\right)$, which if we can use comparison principle then
+\begin{proof} Let $\theta\in (0,1)$. We define
+\begin{equation*}
+    w_\theta = \theta \overline{u} + (1-\theta)\lambda^{-1}\left(\inf_{\Omega} f\right).
+\end{equation*}
+If $w_\theta$ is a subsolution to \eqref{eq:PDEeps}, then we can use comparison principle to obtain that
 \begin{equation*}
@@
 \end{proof}
-\noindent A final remark is that, we can also repeat the proof for $p=2$.
+\noindent This finishes the well-posedness of \eqref{eq:PDEeps} for $1<p<2$.
 \end{proof}
-\subsection{Convergence result} We show the convergence (qualitatively) of \eqref{eq:PDEeps} to \eqref{eq:PDE0}.
-We first state the following Lemma (\cite{Capuzzo-Dolcetta1990}), which characterizes the state-constraint of the first-order equation
-\begin{equation}\label{S_0}
- \lambda u(x) + H(x,Du(x)) = 0\;\qquad\text{in}\;\Omega. \tag{$S_0$}
-\end{equation}
-
-\begin{lem}\label{lem:max} Let $u\in \rmC(\overline{\Omega})$ be a viscosity subsolution of \eqref{S_0} such that, for all viscosity subsolution $v\in \rmC(\overline{\Omega})$ of \eqref{S_0} one has $v\leq u$ in $\overline{\Omega}$, then $u$ is a viscosity supersolution of \eqref{S_0} on $\overline{\Omega}$.
-\end{lem}
-\noindent Lemma \ref{lem:max} is a variation of Perron's method.
-We give a proof in Appendix for the sake of completeness.
-Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ be a solution to \eqref{eq:PDEeps}, we claim that $\{\lambda u^\varepsilon\}_{\varepsilon>0}$ is uniformly bounded from below by a constant independent of $\varepsilon$ and $\lambda$.
-We have
-\begin{equation*}
-    u^\varepsilon(x) = \lim_{m\to \infty} u^{\varepsilon}_m(x), \qquad x\in \Omega,
-\end{equation*}
- where $u^{\varepsilon,m}\in \mathrm{C}^2(\Omega)\cap \rmC(\overline{\Omega})$ solves the Drichlet problem
-\begin{equation}\label{e:uepsm}
-    \begin{cases}
-    \lambda u(x) + H(x,Du(x)) - \varepsilon \Delta u(x) = 0 &\qquad
-    \text{in}\;\Omega, \vspace{0cm}\\
-    \;\;\quad\quad\qquad\qquad\qquad\qquad u(x) = m &\qquad
-    \text{on}\;\partial\Omega.
-    \end{cases} \tag{PDE$_{\varepsilon,m}$}
-\end{equation}
-If we assume $\mathrm{(H2)}$ then we can take $C_2 = \Vert f\Vert_{L^\infty(\Omega)}$ and take $\varphi(x) \equiv -\lambda^{-1}C_2$ for $x\in \overline{\Omega}$ as a subsolution to \eqref{e:uepsm}, hence by comparison principle for \eqref{e:uepsm} we have $u^{\varepsilon}_m(x)\geq -\lambda^{-1}C_2$ for all $x\in \overline{\Omega}$, thus as $m\to \infty$ we obtain $u^\varepsilon(x) \geq -\lambda^{-1}C_2$ for all $x\in \Omega$.
-
-The following Theorem says that the large solution $u^\varepsilon$ converges to $u^0$ locally uniformly on $\Omega$ as $\varepsilon\to 0$.
-We present a simple proof here for the reader's convenience, see also \cite[Theorem VII.3]{Capuzzo-Dolcetta1990}.
-\begin{thm}[Vanishing viscosity - Qualitative result]\label{thm:qual} Assume $\mathrm{(A1)}$.
-Let $u^\varepsilon$ be the solution to \eqref{eq:PDEeps}, then there exists $u^0 \in \mathrm{C}(\overline{\Omega})$ such that $u^\varepsilon \rightarrow u^0$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$, $u^0$ solves \eqref{eq:PDE0} and $u^0 \leq u^\varepsilon$ in $\Omega$.
-\end{thm}
-
-\begin{proof}[Proof of Theorem \ref{thm:qual}] By the priori estimate
-\begin{equation*}
-    |u^\varepsilon(x)| + |Du^\varepsilon(x)| \leq C_\delta \qquad\text{for}\;x\in \overline{\Omega}_\delta
-\end{equation*}
-we deduce from the Arzel\'a--Ascoli theorem that there exists a subsequence $\varepsilon_j\to 0$ and a function $u^0\in \rmC(\Omega)$ such that $u^{\varepsilon_j}\to u^0$ locally uniformly in $\Omega$.
-By the stability of viscosity solution we easily deduce that
-\begin{equation}\label{eq:u0int}
-   \lambda u^0(x) + H(x,Du^0(x)) = 0 \qquad\text{in}\;\Omega.
-\end{equation}
-Since $u^\varepsilon(x)\geq -C_2$ for all $x\in \Omega$ we also have $u^0(x)\geq -C_2$ for all $x\in \Omega$, thus together with \eqref{eq:u0int} we obtain $H(x,\xi) \leq C_2$ for all $\xi\in D^+u^0(x)$ and $x\in \Omega$.
-The coercivity $\mathrm{(H4)}$ implies that there exists $K>0$ such that
-\begin{equation*}
-    |u^0(x) - u^0(y)| \leq K \qquad\text{for all}\;x,y\in \Omega.
-\end{equation*}
-Thus we can extend $u^0$ uniquely to $u^0\in \rmC(\overline{\Omega})$.
-We will use Lemma \ref{lem:max} to show that $u^0$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$.
-It suffices to to show that $u^0\geq w$ on $\overline{\Omega}$ where $w\in \rmC(\overline{\Omega})$ is the unique solution to \eqref{eq:PDE0}.
-
-For $\delta>0$, let $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) < \delta\}$ and $v_\delta\in\rmC(\overline{\Omega}_\delta)$ be the state-constraint viscosity subsolution to the problem $\lambda u(x) + H(x,Du(x)) = 0$ in $\Omega_\delta$.
-As $v_\delta\rightarrow w$ locally uniformly as $\delta\rightarrow 0^+$ (see \cite{kim_state-constraint_2020}) and $w$ is bounded, therefore $\{v_\delta\}_{\delta>0}$ is uniformly bounded.
-Let $v^\varepsilon_\delta\in \rmC^2(\Omega_\delta)\cap \rmC(\overline{\Omega}_\delta)$ be the unique solution to the Dirichlet problem
-\begin{equation}\label{eq:vv_eps}
-\begin{cases}
-    \lambda v_\delta^\varepsilon(x) + |Dv_\delta^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v_\delta^\varepsilon(x) &\qquad\text{in}\;\Omega_\delta,\\
-    \;\;\;\,\quad\qquad\qquad\qquad\qquad v_\delta^\varepsilon = v_\delta &\qquad \text{on}\;\partial\Omega_\delta.
+
+\begin{proof}[Proof of Lemma \ref{lem:max}] The proof is a variation of Perron's method (see \cite{Capuzzo-Dolcetta1990}).
+Let $\varphi\in \rmC(\overline{\Omega})$ and $x_0\in \overline{\Omega}$ such that $u(x_0) = \varphi(x_0)$ and $u-\varphi$ has a global strict minimum over $\overline{\Omega}$ at $x_0$ and that
+\begin{equation}\label{eq:max_a1}
+    \lambda \varphi(x_0) + H(x_0,D\varphi(x_0)) < 0.
+\end{equation}
+Let $\varphi^\varepsilon(x) = \varphi(x) - |x-x_0|^2 + \varepsilon$ for $x\in \overline{\Omega}$. Let $\delta > 0$, we see that for $x\in \partial B(x_0,\delta)\cap \overline{\Omega}$ then
+\begin{equation*}
+    \varphi^\varepsilon(x) = \varphi(x) - \delta^2 +\varepsilon \leq \varphi(x) - \varepsilon
+\end{equation*}
+if $2\varepsilon \leq \delta^2$. We observe that
+\begin{equation*}
+    \begin{split}
+    \varphi^\varepsilon(x) - \varphi(x_0)  &= \varphi(x)-\varphi(x_0) + \varepsilon - |x-x_0|^2 \\
+    D\phi^\varepsilon(x) - D\phi(x_0) &= D\varphi(x) - D\varphi(x_0) - 2(x-x_0)
+    \end{split}
+\end{equation*}
+for $x\in B(x,\delta)\cap \overline{\Omega}$.
+We deduce from \eqref{eq:max_a1}, the continuity of $H(x,p)$ near $(x_0,D\varphi(x_0))$ and the fact that $\varphi\in \rmC^1(\overline{\Omega})$ that if $\delta$ is small enough and $0<2\varepsilon < \delta^2$ then
+\begin{equation}\label{eq:max_a2}
+    \lambda \varphi^\varepsilon(x)+H(x,D\varphi^\varepsilon(x)) < 0 \qquad\text{for}\;x\in B(x_0,\delta)\cap \overline{\Omega}.
+\end{equation}
+We have found $\phi^\varepsilon\in \mathrm{C}^1(\overline{\Omega})$ such that $\varphi^\varepsilon(x_0)>u(x_0)$, $\varphi^\varepsilon<u$ on $\partial B(x_0,\delta)\cap \overline{\Omega}$ and \eqref{eq:max_a2}.
+Let
+\begin{equation*}
+    \tilde{u}(x) = \begin{cases}
+    \max \big\lbrace u(x),\phi^\varepsilon(x) \big\rbrace &x\in B(x_0,\delta)\cap \overline{\Omega},\\
+    u(x)&x\notin B(x_0,\delta)\cap \overline{\Omega},\\
     \end{cases}
-\end{equation}
-It is well-known that $v^\varepsilon_\delta\to v_\delta$ uniformly on $\overline{\Omega}_\delta$ as $\varepsilon\to 0$.
-
-For all $\delta$ small enough $v_\delta\leq u^\varepsilon$ on $\partial \Omega_\delta$, thus by maximum principle $v^\varepsilon_\delta \leq u^\varepsilon$ on $\overline{\Omega}_\delta$.
-Let $\varepsilon\to 0$ we have $v_\delta \leq u^0$ on $\overline{\Omega}_\delta$.
-Let $\delta\rightarrow 0$ we obtain $w\leq u^0$ in $\Omega$, which implies $w\leq u^0$ on $\overline{\Omega}$ since both $w,u^0$ belong to $\rmC(\overline{\Omega})$.
+\end{equation*}
+We see that $\tilde{u}\in \rmC(\overline{\Omega})$ is a subsolution of \eqref{S_0} in $\Omega$ with $\tilde{u}(x_0) > u(x_0)$, which is a contradiction, thus $u$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$.
 \end{proof}
 
-\subsection{Rate of convergence for first-order equation on nested domain - revisited}
-For $\lambda>0$, let $u\in \rmC(\overline{\Omega})$ and $u_\delta\in \rmC(\overline{\Omega}_\delta)$, respectively, state-constraint solutions to 
-\begin{equation*}
-    \begin{cases}
-    \lambda u(x)+H(x,Du(x)) \leq 0 \quad\text{in}\;\Omega,\\
-    \lambda u(x)+H(x,Du(x)) \geq 0 \quad\text{on}\;\overline{\Omega},
-    \end{cases}\qquad\text{and}\qquad 
-    \begin{cases}
-    \lambda u_\delta(x)+H(x,Du_\delta(x)) \leq 0 \quad\text{in}\;\Omega_\delta,\\
-    \lambda u_\delta(x)+H(x,Du_\delta(x)) \geq 0 \quad\text{on}\;\overline{\Omega}_\delta.
-    \end{cases}
-\end{equation*} 
-It is well-known that $0\leq u_\delta(x) - u(x) \leq C\delta$ for $x\in\overline{\Omega}_\delta$ and this rate is optimal.
-This can be proved easily by comparison principle when the domain have a scaling structure, i.e., $\Omega_\delta = (1-\delta)\Omega$ (see \cite{kim_state-constraint_2020}).
-In the general case when the scaling structure is not available but $\partial\Omega$ is smooth enough, for example $\partial\Omega$ is of class $\mathrm{C}^2$, one can construct a $\rmC^2$ diffeomorphism $T:\overline{\Omega}_\delta\to \overline{\Omega}$ that maps $\partial\Omega_\delta$ to $\partial\Omega$ and do scaling with
-\begin{equation*}
- \tilde{u}_\delta(x) = u_\delta\left(T^{-1}(x)\right)   
-\end{equation*}
-defined on $\overline{\Omega}$ (see \cite{Capuzzo-Dolcetta1990}). We present here a simple proof using the doubling variables technique.
-
-\begin{thm}\label{thm:conv_general} Let $\Omega$ be an open, bounded and connected subset $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary. Assume $\mathrm{(H1)}-\mathrm{(H4)}$. 
-Then there exists a constant $C$ such that
-\begin{equation*}
-    0\leq u_\delta(x) - u(x) \leq C\delta \qquad\text{for}\; x\in \overline{\Omega}.
-\end{equation*}
-\end{thm}
-\begin{proof} We use $d(\cdot)$ to denote the extension of the distance function as in \eqref{e:distance_def}. Denote by $C_0$ the constant in the priori estimate
-\begin{equation*}
-    |u_\delta(x)| + |Du_\delta(x)|\leq C_0  \qquad\text{for}\;x\in \overline{\Omega}_\delta.
-\end{equation*}
-We note that this estimate with the same constant $C_0$ holds for $u\in \rmC(\overline{\Omega})$ as well. We will consider $\delta\in (0,1)$ small so that $0<\delta < \delta_1$ where 
-\begin{equation*}
-\delta_1 = \min\left\lbrace \delta_0,\frac{\mathrm{diam}(\Omega)\varepsilon_0}{2(4\tilde{C}_0+1)}\right\rbrace.    
-\end{equation*}
-Without loss of generality, let us assume $x_0\in \Omega$ and $d(x_0)\geq \mathrm{diam}(\Omega)\varepsilon_0\geq \delta$ for some $\varepsilon_0\in (0,1)$. We consider the auxiliary functional
-\begin{equation*}
-    \Phi^{\theta}(x,y) = u_\delta(x) - u(y) - \frac{2\tilde{C}_0\left|x-y\right|^2}{\theta^\beta} - \frac{C_3\theta^\beta}{d(y)}, \qquad(x,y)\in \overline{\Omega}_\delta\times \overline{\Omega}
-\end{equation*}
-where $C_3=2\left(4\tilde{C}_0+1\right)$ for some $\beta < 1$.
-Assume $\Phi^\delta(x,y)$ has a maximum over $\overline{\Omega}_\delta\times \overline{\Omega}$ at $(x_\theta,y_\theta)\in\overline{\Omega}_\delta\times \overline{\Omega}$.
-\begin{itemize}
-    \item $\Phi^\delta(x_\theta,y_\theta) \geq \Phi^\delta(x_0,x_0)$, which gives us
-    \begin{align*}
-        u_\delta(x_\theta) - u(y_\theta) - \frac{2\tilde{C}_0|x_\theta - y_\theta|^2}{\theta^\beta} - \frac{C_3\theta^\beta}{d(y_\theta)} \geq u_\delta(x_0) - u(x_0) - \frac{C_3\delta^\beta}{d(x_0)}. 
-    \end{align*}
-    Therefore, as $C_3 = 2(4\tilde{C}_0+1)$
-    \begin{align}\label{e:d(y)}
-        \frac{C_3\theta^\beta}{d(y_\theta)} \leq 4\tilde{C}_0 + \frac{C_3 \theta^\beta}{d(x_0)}  \leq 4\tilde{C}_0 + 1 \qquad\Longrightarrow\qquad d(y_\delta) \geq 2\theta^\beta \geq 2\delta
-    \end{align}
-    since $\beta < 1$.
-    \item Since $d(y_\theta)\geq 2\delta$, we have $y_\theta\in \Omega_\delta$ and thus $\Phi^\theta(x_\theta,y_\theta) \geq \Phi^\theta(y_\theta,y_\theta)$, which gives us
-    \begin{align*}
-        u_\delta(x_\theta) - u(y_\theta) - \frac{2\tilde{C}_0|x_\theta - y_\theta|^2}{\theta^\beta} - \frac{C_3\theta^\beta}{d(y_\theta)} \geq u_\theta(y_\theta) - u(y_\theta) - \frac{C_3\theta^\beta}{d(y_\theta)}.
-    \end{align*}
-    I.e.,
-    \begin{align*}
-        u_\delta(x_\theta)  - \frac{2\tilde{C}_0|x_\theta- y_\theta|^2}{\theta^\beta} \geq u_\delta(y_\theta) 
-    \end{align*}
-    and thus
-    \begin{equation*}
-        \frac{2\tilde{C}_0|x_\theta-y_\theta|^2}{\theta^\beta} \leq u_\delta(x_\theta) - u_\delta(y_\theta) \leq \tilde{C}_0|x_\theta-y_\theta|
-    \end{equation*}
-    and therefore
-    \begin{equation}\label{e:x-y}
-        |x_\theta-y_\theta|\leq \frac{\theta^\beta}{2}
-    \end{equation}
-    \item From \eqref{e:d(y)} and \eqref{e:x-y} we obtain that, if $z\in \partial\Omega$ then
-    \begin{align*}
-        |x_\delta - z| &= |(x_\delta - y_\delta) - (z - y_\delta)| \\
-        &\geq |z-y_\delta| - |x_\delta - y_\delta| \geq d(y_\delta) - |x_\delta - y_\delta| \geq 2\delta - \frac{\delta}{2} = \frac{3\delta}{2}.
-    \end{align*}
-    Therefore
-    \begin{equation*}
-        d(x_\delta) = \inf_{z\in \partial\Omega} |x_\delta - z|  \geq \frac{3\delta}{2}
-    \end{equation*}
-    and thus $x_\delta\in \Omega_\delta$.
-    \item $x\mapsto \Phi^\delta(x,y_\delta)$ has a maximum at $x_\delta\in \Omega_\delta$, thus
-    \begin{equation*}
-        \lambda u_\delta(x_\delta) + H\left(x_\delta, \frac{4\tilde{C}_0(x_\delta-y_\delta)}{\delta}\right) \leq 0.
-    \end{equation*}
-    \item $y\mapsto \Phi^\delta(x_\delta,y)$ has a maximum at $y_\delta\in \overline{\Omega}$, thus
-    \begin{equation*}
-        \lambda u(y_\delta) + H\left(y_\delta,\frac{4\tilde{C}_0(x_\delta-y_\delta)}{\delta} + C_3\delta^\beta\frac{Dd(y_\delta)}{d(y_\delta)^2} \right) \geq 0.
-    \end{equation*}
-\end{itemize}
-\end{proof}
-
-\section{Rate of convergence via Doubling variables - a toy case}
-\noindent Let $\Omega = B(0,1)$. Let $\beta,\sigma,\delta \in (0,1)$ to be chosen later, let us define
-\begin{align*}
-    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u_\delta(y) - \frac{L_0|x-y|^2}{\sigma}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}_\delta
-\end{align*}
-where $L_0$ is the Lipschitz constant of $u^0$ and $u_\delta\in \mathrm{C}(\overline{\Omega}_\delta)$ is the state-constraint solution to
-\begin{equation*}
-    \begin{cases}  
-    \lambda u_\delta(x) + H(x,Du_\delta(x)) \leq 0 \qquad\text{in}\; \Omega_\delta\\
-    \lambda u_\delta(x) + H(x,Du_\delta(x)) \geq 0 \qquad\text{on}\; \overline{\Omega}_\delta.
-    \end{cases}
-\end{equation*}
-As we are working with the ball, note that $\Omega_\delta = (1-\delta)\Omega$. Let $\mathfrak{F}$ be the Lipschitz constant of $f$.
-\paragraph{\textcolor{blue}{\textbf{Step 1.}}} Since $u^\varepsilon (x)d(x)^\alpha \to C_\varepsilon$ as $d(x)\to 0$, we see that $\Phi^\sigma(x,y)\to -\infty$ as $d(x)\to 0$, therefore for a fixed $\varepsilon>0$, there is $(x_{\sigma},y_\sigma)\in \Omega\times\overline{\Omega}_\delta$ such that
-\begin{equation*}
-    \max_{\overline{\Omega}\times \overline{\Omega}_\delta} \Phi^\sigma = \Phi^\sigma(x_\sigma,y_\sigma).
-\end{equation*}
-\paragraph{\textcolor{blue}{\textbf{Step 2.}}} $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(x_\sigma,x_\sigma)$ gives us that
-    \begin{equation}\label{e:est_sigma2}
-        \mathfrak{C}\frac{|x_\sigma-y_\sigma|^2}{\sigma} \leq u_\delta(x_\sigma) - u_\delta(y_\sigma) \leq \mathfrak{C}|x_\sigma-y_\sigma| \qquad\Longrightarrow\qquad |x_\sigma -y _\sigma|\leq \sigma.
-    \end{equation}
-    This gives us that
-    \begin{equation}\label{e:est_sigma3}
-        |x_\sigma|\leq |y_\sigma|+\sigma \qquad\Longrightarrow\qquad d(x_\sigma) \geq d(y_\sigma) - \sigma\geq \delta-\sigma.
-    \end{equation}
-Let 
-\begin{equation*}
-   \fbox{$\displaystyle \delta = 2\sigma$.}
-\end{equation*}
-then 
-\begin{equation*}
-    \fbox{$d(x_\sigma) \geq \sigma$.}
-\end{equation*}
-\paragraph{\textcolor{blue}{\textbf{Step 3.}}} $x\mapsto \Phi^\sigma(x,y_\sigma)$ has a maximum at $x_\sigma\in \Omega$, thus 
-\begin{align*}
-    &\lambda u^\varepsilon(x_\sigma) + \left|\frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma} - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma )\right|^p - f(x_\sigma)\\
-    &\qquad\qquad\qquad -\varepsilon\left(\frac{2n}{\sigma} + \frac{C_\varepsilon(\alpha+\beta)(\alpha+\beta+1)|D d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+\beta+2}}-\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\Delta d(x_\sigma)\right)  \leq 0.
-\end{align*}
-\paragraph{\textcolor{blue}{\textbf{Step 4.}}} $y\mapsto \Phi^\sigma(x_\sigma,y)$ has a maximum at $y_\sigma\in \overline{\Omega}_\delta$, thus 
-\begin{equation*}
-    \lambda u_\delta(y_\sigma) + \left|\frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma}\right|^p - f(y_\sigma) \geq 0
-\end{equation*}
-\paragraph{\textcolor{blue}{\textbf{Step 5.}}} Gradient estimate, let
-\begin{equation*}
-    \xi_\sigma = \frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma} \qquad\text{and}\qquad \zeta_\sigma = - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma)
-\end{equation*}
-then $|\xi_\sigma|\leq 2\mathfrak{C}$ already and furthermore
-\begin{equation*}
-   \xi_\sigma+\zeta_\sigma \in D^-u^\varepsilon(x_\sigma),
-\end{equation*}
-which, by the local gradient estimate, as $x_\sigma\in \Omega_{\sigma}$, this is bounded in terms of $\sigma$ and will blow up as $\sigma\to 0$. Nevertheless, we can do better as following.
-\begin{equation*}
- |\zeta_\sigma|=   \left|\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma )\right| \leq \frac{C_\varepsilon(\alpha+\beta)}{\sigma^{\alpha+\beta+1}}\leq \frac{\alpha+\beta}{\alpha} (\alpha+1)^\frac{1}{p-1}\frac{\varepsilon^\frac{1}{p-1}}{\sigma^{\alpha+\beta+1}}.
-\end{equation*}
-Thus by choosing $\sigma = \varepsilon^\gamma$ appropriately, we can make this tends to zero as $\varepsilon \to 0$. Indeed, we have
-\begin{equation*}
-    |\zeta_\sigma| \leq \frac{(\alpha+1)^\frac{1}{p-1}}{\alpha} \varepsilon^{\frac{1}{p-1} - \gamma(\alpha+\beta+1)} = \frac{\alpha+\beta}{\alpha}(\alpha+1)^{\alpha+1}\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)},
-\end{equation*}
-where we made use of the fact that $\alpha+1 = \frac{1}{p-1}$. We see that the first condition we want to impose is
-\begin{equation}\label{e:condition_gamma_1}
-    \fbox{\qquad\qquad\qquad$\displaystyle 0 < \gamma < \frac{\alpha+1}{\alpha+1+\beta}$\qquad\qquad\qquad.}
-\end{equation}
-As long as \eqref{e:condition_gamma_1} holds then
-\begin{equation}\label{e:bddp_sigmaq_sigma}
-    |\zeta_\sigma|\leq \mathfrak{C}_\alpha \qquad\text{where}\qquad \mathfrak{C}_\alpha = \frac{\alpha+\beta}{\alpha}(\alpha+1)^{\alpha+1}.
-\end{equation}
-\paragraph{\textcolor{blue}{\textbf{Step 6.}}} Recall $|D d(x_\sigma)| = 1$, we have
-\begin{align}
-    \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) &\leq \underbrace{\left|\frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma}\right|^p}_{|\xi_\sigma|^p} - \underbrace{ \left|\frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma} - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma )\right|^p}_{|\xi_\sigma+\zeta_\sigma|^p} \nonumber\\
-    &+ \underbrace{f(y_\sigma) - f(x_\sigma)}_{\mathfrak{F}|x_\sigma - y_\sigma|} + \varepsilon\left(\frac{2n}{\sigma} + \underbrace{\frac{C_\varepsilon(\alpha+\beta)(\alpha+\beta+1)}{d(x_\sigma)^{\alpha+\beta+2}}}_{\frac{C_\varepsilon (\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta + 1}}.\frac{\alpha+\beta+1}{d(x_\sigma)}}-\underbrace{\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\Delta d(x_\sigma)}_{\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}.\Delta d(x_\sigma)}\right)\nonumber\\
-    &\leq |\xi_\sigma|^p - |\xi_\sigma+\zeta_\sigma|^p + \mathfrak{F}\sigma + \frac{2n\varepsilon}{\sigma} + (\alpha+\beta+1)|\zeta_\sigma|\frac{\varepsilon}{\sigma} + K|\zeta_\sigma|\varepsilon \label{e:est3}
-\end{align}
-where we recall that $K = \max_{x\in \overline{\Omega}}\Delta d(x)$. Let's recall a simple estimate, let $f(t) = (x+ty)^p$ then
-\begin{align*}
-    f(1) - f(0) = \int_ 0^1 f'(s)\;ds = p\int_0^1 (x+sy)^{p-1}y\;ds,
-\end{align*}
-therefore
-\begin{align*}
-    \left||x+y|^p - |x|^p \right| &\leq p \left(\int_0^1 |x+sy|^{p-1}ds\right)|y|\\
-    &\leq p\left(\int_0^1\Big(|x|+s|y|\Big)^{p-1}\;ds\right)|y| \leq  p\Big(|x|+|y|\Big)^{p-1}|y|.
-\end{align*}
-Using this for $x = \xi_\sigma$ and $y = \zeta_\sigma$ we deduce that
-\begin{align}
-    \Big||\xi_\sigma+\zeta_\sigma|^p - |\xi|^p\Big| &\leq p\Big(|\xi_\sigma|+|\zeta_\sigma|\Big)^{p-1}|\zeta_\sigma|\nonumber\\
-    &\leq p\left(2\mathfrak{C} + \frac{(\alpha+1)^{\alpha+1}}{\alpha}\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)}\right)^{p-1}\frac{(\alpha+1)^{\alpha+1}}{\alpha}\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)}\nonumber\\
-    &\leq \underbrace{\left(p\big(2\mathfrak{C} + \mathfrak{C}_\alpha\big)^{p-1} \mathfrak{C}_\alpha \right)}_{\mathfrak{B}}\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)} \label{e:est2}
-\end{align}
-where we make use of \eqref{e:bddp_sigmaq_sigma}.
-\paragraph{\textcolor{blue}{\textbf{Step 7. Combining stuffs.}}} From \eqref{e:est2} and \eqref{e:est3} and $\sigma = \varepsilon^\gamma$ we deduce that
-\begin{align*}
-    \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) &\leq   \mathfrak{B}\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)}+ \mathfrak{F}\varepsilon^\gamma + 2n \varepsilon^{1-\gamma}\\
-    & + (\alpha+\beta + 1)\mathfrak{C}_\alpha \varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)} \varepsilon^{1-\gamma} + K\mathfrak{C}_\alpha\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)} \varepsilon.
-\end{align*}
-Let us denote
-\begin{equation*}
-    \mathfrak{X}:= \max\Big\lbrace \mathfrak{B}, \mathfrak{F},2n, (\alpha+\beta+1)\mathfrak{C}_\alpha, K\mathfrak{C}_\alpha \Big\rbrace
-\end{equation*}
-then
-\begin{equation*}
-    \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) \leq \mathfrak{X}\Big(\varepsilon^{\alpha+1-\gamma(\alpha+1+\beta)}+\varepsilon^\gamma+\varepsilon^{1-\gamma} + \varepsilon^{\alpha+2-\gamma(\alpha+2+\beta)}+\varepsilon^{\alpha+2-\gamma(\alpha+1+\beta)}\Big).
-\end{equation*}
-Take $\gamma = \frac{1}{2}$ to balance $\varepsilon^\gamma \approx \varepsilon^{1-\gamma}$ (\textcolor{blue}{which normally gives the rate $\sqrt{\varepsilon}$ for zero Dirichlet boundary problem}), we have
-\begin{equation*}
-    \begin{cases}
-    \alpha+1 - \frac{1}{2}(\alpha+1+\beta) > \frac{1}{2}\vspace{3pt}\\
-    \alpha+2 - \frac{1}{2}(\alpha+2+\beta) > \frac{1}{2}\vspace{3pt}\\
-    \alpha+2 - \frac{1}{2}(\alpha+1+\beta) > \frac{1}{2}
-    \end{cases} \qquad\Longleftrightarrow\qquad \begin{cases}
-    \alpha+1-\beta > 1\\
-    \alpha+2-\beta > 1\\
-    \alpha+3-\beta > 1
-    \end{cases}
-\end{equation*}
-which is always correct as long as $0 < \beta < \alpha$. We note that as $1<p<2$, we have $\alpha\in (0,\infty)$ and therefore such a choice of $\beta$ is always possible. We conclude that
-\begin{equation}\label{e:crucial}
-    \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) \leq \mathfrak{X}\varepsilon^\frac{1}{2}
-\end{equation}
-where $\sigma = \varepsilon^\frac{1}{2}$. 
-\paragraph{\textcolor{blue}{\textbf{Step 8.
-Deriving the conclusion}.}} Using $\Phi^\sigma(x_\sigma,y_\sigma)\geq \Phi^\sigma(x,x)$ for \textcolor{red}{all} $x\in \overline{\Omega}_\delta =  \overline{\Omega}_{2\sigma}$, we have
-\begin{equation*}
-    \lambda u^\varepsilon(x) - \lambda u_\delta(x) - \frac{C_\varepsilon}{d(x)^{\alpha+\beta}} \leq \Phi^\sigma(x_\sigma,y_\sigma) \leq \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) \leq \mathfrak{X}\varepsilon^\frac{1}{2}.
-\end{equation*}
-Using $d(x)\geq 2\sigma = 2\varepsilon^{\frac{1}{2}}$ we deduce that
-\begin{equation}\label{e:almost}
-    \lambda u^\varepsilon(x) - \lambda u_\delta(x) \leq \mathfrak{X}\varepsilon^\frac{1}{2} + \frac{(\alpha+1)^{\alpha+1}}{2^{\alpha+\beta}\alpha}\varepsilon^{\alpha+1 - \frac{\alpha+\beta}{2}} \leq \tilde{\mathfrak{X}}\varepsilon^\frac{1}{2} \qquad \text{for all}\;x\in \overline{\Omega}_{2\sigma}
-\end{equation}
-where (we see that $\alpha+1 - \frac{\alpha+\beta}{2} = 1+ \frac{\alpha-\beta}{2} > 1$)
-\begin{equation*}
-    \tilde{\mathfrak{X}} = \max \left\lbrace\mathfrak{X}, \frac{(\alpha+1)^{\alpha+1}}{2^{\alpha+\beta}\alpha} \right\rbrace.
-\end{equation*}
-Finally, in the case of the ball, $\Omega_\delta = (1-\delta)\Omega$, by \cite[Theorem 1.5]{kim_state-constraint_2020} we know that, optimally,
-\begin{equation}\label{e:citepaper}
-    0\leq \lambda u_\delta(x) - \lambda u^0(x)\leq C_H\delta \qquad\text{for all}\; x\in \overline{\Omega}_\delta.
-\end{equation}
-From \eqref{e:almost} and \eqref{e:citepaper} and $\delta =2\sigma= 2\varepsilon^\frac{1}{2}$, and $u^\varepsilon \geq u^0$ from Theorem \ref{thm:qual} we deduce that
-\begin{align*}
-    \fbox{ $\displaystyle 0 \leq \lambda u^\varepsilon(x) - \lambda u^0(x) \leq \left(\tilde{\mathfrak{X}} + 2C_H\right)\sqrt{\varepsilon} \qquad\text{for all}\; x\in \overline{\Omega}_{2\sqrt{\varepsilon}}$.}
-\end{align*}
-It appears that the boundary layer is the strip
-\begin{equation*}
-    \Gamma_\varepsilon = \{x\in \Omega: 0<\mathrm\dist(x,\partial\Omega)< 2\sqrt{\varepsilon}\}.
-\end{equation*}
-\color{blue}
-\textcolor{blue}{\textbf{The next questions and tasks:}}
-\begin{enumerate}
-    \item Check all the constants, make sure things are correct!
-    \item It seems that $\sqrt{\varepsilon}$ is the best using this method. Now we can improve this by either:
-    \begin{itemize}
-        \item[(a)] Make the boundary layer to $\sqrt{\varepsilon}$ only, instead of $2\sqrt{\varepsilon}$.
-        \item[(b)] \textcolor{red}{\textbf{Important.}} Generalize this to more general domain, possibly star-shaped domains where we can do scaling is fine (just my guess).
-    \end{itemize}
-    \item Other formulations of the doubling variable method here, for example, in the first step, it seems that making $\Phi^\sigma(x,y)\to  -\infty$ as $x\to \partial\Omega$ is "\emph{too wasteful}".
-One may need only to do something like
-    \begin{equation*}
-        \Phi^\sigma(x,y) < \Phi^\sigma(0,0) \qquad\text{if}\qquad d(x) < \;\text{something close to the boundary}.
-    \end{equation*}
-    Can we improve that to get a better rate?
-My guess is not even if we can improve this, since the dominating term coming from $\varepsilon^\gamma$ and $\varepsilon^{1-\gamma}$ later.
-Nevertheless, it maybe still interesting to see why and how the \emph{wasteful} formulation here can be improved.
-    \item \textcolor{red}{\textbf{Important.}} Using nonlinear adjoint method.
-    \item Now once we have some rate, can we do bootstrap to improve it as we discussed earlier (the simple ideas, ...)?
-    \item \textcolor{red}{\textbf{Important.}} Can we find an example where $|u^\varepsilon - u^0| = \mathcal{O}(1)$ in the strip where $0<\mathrm{dist}(x,\partial\Omega)<2\sqrt{\varepsilon}$?
-Or can we even make more layers inside with more scales, as $|u^\varepsilon - u^0| = \mathcal{O}(1)$ is not possible near the boundary $\partial\Omega$.
-\end{enumerate}
-\color{black}
-
-\newpage
-\section{Rate of convergence via a simple idea}
-\noindent Let $\Omega = B(0,1)$, the scaling and distance near boundary are the same, i.e., $(1-\delta)\Omega = \Omega_\delta$.
-
-\noindent Let $u_\delta\in \rmC(\overline{\Omega}_\delta)$ be the state-constraint solution of the first-order equation, still $H(x,\varrho) = |\varrho|^p - f(x)$,
-\begin{equation*}
-    \begin{cases}
-    \lambda u_\delta(x) + H(x,Du_\delta(x)) \leq 0 &\qquad\text{in}\;(1-\delta)\Omega,\\
-    \lambda u_\delta(x) + H(x,Du_\delta(x)) \geq 0 &\qquad\text{on}\;(1-\delta)\overline{\Omega}.
-    \end{cases}
-\end{equation*}
-We know that the optimal rate of convergence of $u_\delta$ to $u^0$ is given by (\cite{kim_state-constraint_2020})
-\begin{equation*}
-    0\leq u_\delta - u^0 \leq C\delta
-\end{equation*}
-where $C$ depends on $H$ only (\textcolor{red}{check this}).
-
-\noindent Let $g_{\varepsilon,\delta}(x) = u^\varepsilon(x)$ for $x\in \partial\Omega_\delta$ which is finite.
-We have $u_\delta\leq g_{\varepsilon,\delta}$ for all $\varepsilon$ and also for each fixed $\delta>0$ then
-\begin{equation*}
-    \lim_{\varepsilon\to 0} g_{\varepsilon,\delta}(x) = u_\delta(x).
-\end{equation*}
-On the domain $\Omega_\delta$, we consider the problem
-\begin{equation*}
-    \begin{cases}
-    \mathcal{L}[v^\varepsilon] = 0 &\qquad\text{in}\;\Omega_\delta,\\
-    v^\varepsilon = g_{\delta,\varepsilon} &\qquad\text{on}\;\partial\Omega_\delta.
-    \end{cases}
-\end{equation*}
-Question: can we quantify $\Vert v^\varepsilon - u_\delta\Vert_{L^\infty}$ in term of $\varepsilon$?
-
-\section{Rate of convergence via nonlinear adjoint method}
-
-%\nocite{*}
-
-\section{Questions and Ideas}
-\begin{quest} [Jan 12, 2021] Why do we use the distance functions to get boundary estimates? 
-\end{quest}
-
-\begin{quest} [Jan 13, 2021] Maximum principle for sub-quadratic case.
-\end{quest}
-
-\begin{quest}[Jan 20, 2021] Here is an idea to estimate $\Vert u^\varepsilon - u^0\Vert_{L^\infty_{loc}(\Omega)}$. We start first by assuming star-shaped and consider
-\begin{equation}\label{e:S_eta}
-    \begin{cases}
-    \lambda u_\eta^\varepsilon(x) + H(x,Du_\eta^\varepsilon(x)) - \varepsilon \Delta u_\eta^\varepsilon(x) = 0 &\qquad
-    \text{in}\;(1-\eta)\Omega, \vspace{0cm}\\
-    \qquad\qquad\qquad\qquad\qquad\qquad\;\, u^\varepsilon_\eta(x) = +\infty &\qquad
-    \text{on}\;(1-\eta)\partial\Omega.
-    \end{cases} \tag{$S_\eta$}
-\end{equation}
-Can we estimate $0\leq u^\varepsilon_\eta - u^\varepsilon \leq \omega(\varepsilon,\eta)$ and then chose $\eta = \omega'(\varepsilon)$ to conclude?
-One way is to approximate infinity boundary by finite boundary first, it may be too naive, but whatever!
-\begin{equation}\label{e:S_eta_m}
-    \begin{cases}
-    \lambda v_\eta^\varepsilon(x) + H(x,Dv_\eta^\varepsilon(x)) - \varepsilon \Delta v_\eta^\varepsilon(x) = 0 &\qquad
-    \text{in}\;(1-\eta)\Omega, \vspace{0cm}\\
-    \qquad\qquad\qquad\qquad\qquad\qquad\;\, v^\varepsilon_\eta(x) = m &\qquad
-    \text{on}\;(1-\eta)\partial\Omega.
-    \end{cases} \tag{$S_{\eta}^m$}
-\end{equation}
-In contrast, let us consider
-\begin{equation}\label{e:S_0}
-    \begin{cases}
-    \lambda v^\varepsilon(x) + H(x,Dv^\varepsilon(x)) - \varepsilon \Delta v^\varepsilon(x) = 0 &\qquad
-    \text{in}\;\Omega, \vspace{0cm}\\
-    \qquad\qquad\qquad\qquad\qquad\qquad\;\, v^\varepsilon(x) = m &\qquad
-    \text{on}\;\partial\Omega.
-    \end{cases} \tag{$S^m$}
-\end{equation}
-How can we compare $v^\varepsilon$ and $v^\varepsilon_\eta$?
-\end{quest}
-
-\begin{appendices}
-
-\section{Gradient bounds}
-\subsection{Local interior gradient bound for elliptic equation}
-Let $\Omega\subset \R^n$ be an open, bounded, connected set with $\rmC^2$ boundary and $H(x,p):\overline{\Omega}\times \R^n\rightarrow \mathbb{R}$ be a continuously differentiable Hamiltonian satisfying
-\begin{equation}\label{eq:grow}
-\lim_{|p\rightarrow \infty} \left(\frac{1}{2}H(x,p)^2 + D_xH(x,p)\cdot p\right) = +\infty \qquad\text{uniformly in}\;x\in \overline{\Omega}. \tag{H1}
-\end{equation}
-We consider the following equation
-\begin{equation}\label{eq:C_eps}
-    \lambda u^\varepsilon(x) + H(x,Du^\varepsilon(x)) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad\text{in}\;\Omega.
-\end{equation}
-Let $u^\varepsilon\in \rmC^2(\Omega)\cap \mathrm{C}^1(\overline{\Omega})$ be a bounded solution to \eqref{eq:C_eps}, say $|\lambda u^\varepsilon(x)| \leq C_1$ for all $x\in \overline{\Omega}$.
-In this section we show that an interior gradient bound also holds, i.e., if $x\mapsto|Du^\varepsilon(x)|$ has a maximum over $\overline{\Omega}$ at $x_0\in \Omega$ then $|Du^\varepsilon(x_0)| \leq C_2$ for all $x\in \Omega$.
-Here $C_1,C_2$ are independent of $\varepsilon>0$.\\
-
-\noindent We will use the classical Bernstein's argument.
-Let $\varphi(x) = \frac{1}{2}|Du^\varepsilon(x)|^2$ for $x\in \Omega$.
-Differentiate \eqref{eq:C_eps} in $x_i$ then multiply the resulting equation with $u^\varepsilon_{x_i}$ and then sum over $i=1,2,\ldots, n$ we obtain
-\begin{equation*}
-    2\lambda \varphi(x) + D_pH(x,Du^\varepsilon(x))\cdot D\varphi(x) - \varepsilon \Delta \varphi(x) + \Big(\varepsilon |D^2u^\varepsilon(x)| + D_xH(x,Du^\varepsilon(x))\cdot Du^\varepsilon(x)\Big) = 0.
-\end{equation*}
-If $\varphi(x)$ achieves its maximum over $\overline{\Omega}$ at $x_0\in \Omega$, then $D\varphi(x_0) = 0$ and $\Delta \varphi(x_0)\leq 0$, together with $\varepsilon |D^2u^\varepsilon(x)|^2\geq \frac{1}{n\varepsilon}(\varepsilon\Delta u^\varepsilon(x))^2\geq (\varepsilon\Delta u^\varepsilon(x))^2$ if $n\varepsilon < 1$ we deduce that
-\begin{equation*}
-    \lambda |D u^\varepsilon(x_0)|^2 + \Big(\lambda u^\varepsilon(x_0)+H(x_0,Du^\varepsilon(x_0))\Big)^2 + D_xH(x_0,Du^\varepsilon(x_0))\cdot Du^\varepsilon(x_0) \leq 0.
-\end{equation*}
-Assume $|\lambda u^\varepsilon(x_0)|\leq C_1$, using \eqref{eq:grow} we deduce that
-\begin{equation*}
-    \frac{1}{2}H(x_0,Du^\varepsilon(x_0))^2 + D_xH(x_0,Du^\varepsilon(x_0))\cdot Du^\varepsilon(x_0) + \left(\frac{1}{\sqrt{2}}H(x_0,Du^\varepsilon(x_0) - \sqrt{2}C_1\right)^2 - \left(C_1\right)^2\leq 0
-\end{equation*}
-which gives us $|Du^\varepsilon(x_0)|\leq C_2$ for some $C_2$ independent of $\varepsilon$. 
-\begin{rem} Assumption \eqref{eq:grow} is weaker than the combination of $p\mapsto H(x,p)$ is superlinear and $|D_xH(x,p)|\leq C(1+|p|)$.
-\end{rem}
-
 \section{Differentiability with respect to the parameter}
-For the vanishing viscosity problem with the Dirichlet boundary condition,
+\noindent For the vanishing viscosity problem with the Dirichlet boundary condition,
 \begin{equation}
@@
 
- Next we try to bound $\{u\in X : u=\lambda A[u]$ for some $0 \leq  \lambda \leq 1\}$.
- If $u=\lambda A[u]$, the PDE becomes
+\noindent Next we try to bound $\{u\in X : u=\lambda A[u]$ for some $0 \leq  \lambda \leq 1\}$. If $u=\lambda A[u]$, the PDE becomes
 
@@
 
-Calderon-Zygmund estimates tell us that if we have
+\noindent Calderon-Zygmund estimates tell us that if we have
 \begin{equation}
@@
 \end{equation}
-
 and $\Tilde{f} \in {L^p(U)}$ for some $p\in (1, \infty)$, then $v \in W^{2,p}(U)$ and $$\|v\|_{w^{2,p}(U)} \leq C\|\Tilde{f}\|_{L^p(U)}.$$
 
-Apply to \eqref{lamb} and we get
+\noindent Apply to \eqref{lamb} and we get
 
@@
 \end{equation}
-
 Choose $p=2n$ and $\displaystyle \alpha =\frac{1}{2}$. We have $\{\Tilde{u}\in X : \Tilde{u}=\lambda A[\Tilde{u}]$ for some $0 \leq  \lambda \leq 1\}$ is bounded in $X= C^{1, \frac{1}{2}}(
@@
 \end{equation}
-
 From the existence proof, we know $\|u^\epsilon\|_{C^{2,\alpha}(\overline{U})} \leq C$ uniformly in $\epsilon$.
@@
 This implies $w^h \to w^\ast$ in $C^{2, \beta}(\overline{U})$.
-
-\section{Proofs of some Lemmas and Propositions}
-\begin{proof}[Proof of Lemma \ref{lem:max}] The proof is a variation of Perron's method (see \cite{Capuzzo-Dolcetta1990}).
-Let $\varphi\in \rmC(\overline{\Omega})$ and $x_0\in \overline{\Omega}$ such that $u(x_0) = \varphi(x_0)$ and $u-\varphi$ has a global strict minimum over $\overline{\Omega}$ at $x_0$ and that
-\begin{equation}\label{eq:max_a1}
-    \lambda \varphi(x_0) + H(x_0,D\varphi(x_0)) < 0.
-\end{equation}
-Let $\varphi^\varepsilon(x) = \varphi(x) - |x-x_0|^2 + \varepsilon$ for $x\in \overline{\Omega}$. Let $\delta > 0$, we see that for $x\in \partial B(x_0,\delta)\cap \overline{\Omega}$ then
-\begin{equation*}
-    \varphi^\varepsilon(x) = \varphi(x) - \delta^2 +\varepsilon \leq \varphi(x) - \varepsilon
-\end{equation*}
-if $2\varepsilon \leq \delta^2$. We observe that
-\begin{equation*}
-    \begin{split}
-    \varphi^\varepsilon(x) - \varphi(x_0)  &= \varphi(x)-\varphi(x_0) + \varepsilon - |x-x_0|^2 \\
-    D\phi^\varepsilon(x) - D\phi(x_0) &= D\varphi(x) - D\varphi(x_0) - 2(x-x_0)
-    \end{split}
-\end{equation*}
-for $x\in B(x,\delta)\cap \overline{\Omega}$.
-We deduce from \eqref{eq:max_a1}, the continuity of $H(x,p)$ near $(x_0,D\varphi(x_0))$ and the fact that $\varphi\in \rmC^1(\overline{\Omega})$ that if $\delta$ is small enough and $0<2\varepsilon < \delta^2$ then
-\begin{equation}\label{eq:max_a2}
-    \lambda \varphi^\varepsilon(x)+H(x,D\varphi^\varepsilon(x)) < 0 \qquad\text{for}\;x\in B(x_0,\delta)\cap \overline{\Omega}.
-\end{equation}
-We have found $\phi^\varepsilon\in \mathrm{C}^1(\overline{\Omega})$ such that $\varphi^\varepsilon(x_0)>u(x_0)$, $\varphi^\varepsilon<u$ on $\partial B(x_0,\delta)\cap \overline{\Omega}$ and \eqref{eq:max_a2}.
-Let
-\begin{equation*}
-    \tilde{u}(x) = \begin{cases}
-    \max \big\lbrace u(x),\phi^\varepsilon(x) \big\rbrace &x\in B(x_0,\delta)\cap \overline{\Omega},\\
-    u(x)&x\notin B(x_0,\delta)\cap \overline{\Omega},\\
-    \end{cases}
-\end{equation*}
-We see that $\tilde{u}\in \rmC(\overline{\Omega})$ is a subsolution of \eqref{S_0} in $\Omega$ with $\tilde{u}(x_0) > u(x_0)$, which is a contradiction, thus $u$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$.
-\end{proof}
-
 \end{appendices}
 
-%\section*{Acknowledgement}
+\section*{Acknowledgement}
+The authors would like to express their appreciation to Hung V. Tran for his invaluable guidance.
 

### 2021-04-06 Drafts and notes/Attempts/Old_draft_09.tex
Major change

--- 2021-04-06 Drafts and notes/Attempts/Old_draft_07.tex
@@
 \noindent The main result is the following Theorem.
-\begin{thm}\label{thm:rate_doubling1} Let $\Omega$ be an open, bounded and connected subset $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary.
-Assume $\mathrm{(A1)},\mathrm{(H1)}-\mathrm{(H4)}$ and $1<p<2$.
+\begin{thm}\label{thm:rate_doubling1} Let $\Omega = B(0,1)$ be the open unit ball in $\mathbb{R}^n$.
+Assume $\mathrm{(A1)},\mathrm{(H1)}-\mathrm{(H4)}$ and also $1<p<2$.
 Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u^0$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that
@@
 \end{equation} 
-Let $C_f$ be the Lipschitz constant of $f$ and $\beta,\sigma,\delta \in (0,1)$ to be chosen later.
-Recall the definition of $C_\varepsilon$ from Theorem \ref{thm:wellposed1<p<2}, we define the auxiliary functional
-\begin{align*}
-    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u_\delta(y) - \frac{C_0|x-y - \delta \nabla d(x)|^2}{\sigma}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}_\delta,
-\end{align*}
-where $C_0$ is the Lipschitz constant of $u^0$ (also the Lipschitz constant of $u_\delta$ for $\delta>0$). We split the proof into several steps.
+Let $C_f$ be the Lipschitz constant of $f$ and $\beta,\sigma,\delta \in (0,1)$ to be chosen later. Recall the definition of $C_\varepsilon$ from Theorem \ref{thm:wellposed1<p<2} and a priori estimate
+\begin{equation*}
+    \sup_{x\in \overline{\Omega}_\delta} \left(|u_\delta(x)| + |Du_\delta(x)|\right) \leq C_0.
+\end{equation*}
+We define the auxiliary functional
+\begin{align*}
+    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u_\delta(y) - \frac{C_0|x-y+\delta \nabla d(x)|^2}{2\sigma^2}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}_\delta.
+\end{align*}
+We split the proof into several steps.
 \begin{enumerate}
@@
 so that $|Dd(x_\sigma)| = 1$. We will mention how the case $d(x_\sigma)\geq \delta_0$ is easily deduced at the end of the proof.
-\item[2.] $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(x_\sigma,x_\sigma)$ gives us that
+\item[2.] The unit outward normal vector at a point $z\in \partial\Omega$ is given by 
+\begin{equation*}
+    \mathbf{n}(z) = -\nabla d(z).
+\end{equation*}
+The projection of $x_\sigma$ to $\partial\Omega$ is given by
+\begin{equation*}
+    \underline{x}_\sigma = x_\sigma + d(x_\sigma)\mathbf{n}(\underline{x}_\sigma).
+\end{equation*}
+Assume $0<d(x_\sigma) < \delta$, then clearly 
+\begin{equation*}
+    x_\sigma - \delta \mathbf{n}(\underline{x}_\sigma) \in \overline{\Omega}_\delta.
+\end{equation*}
+From $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(x_\sigma,x_\sigma-\delta \mathbf{n}(\underline{x}_\sigma))$ we have
     \begin{equation}\label{e:est_sigma2}
-     \frac{C_0|x_\sigma-y_\sigma|^2}{\sigma} \leq u_\delta(x_\sigma) - u_\delta(y_\sigma) \leq C_0|x_\sigma-y_\sigma| \qquad\Longrightarrow\qquad |x_\sigma -y _\sigma|\leq \sigma.
+     \frac{C_0|x_\sigma-y_\sigma - \delta\nabla d(x_\sigma)|^2}{2\sigma^2} \leq u_\delta(x_\sigma) - u_\delta(y_\sigma) \leq C_0|x_\sigma-y_\sigma| \qquad\Longrightarrow\qquad |x_\sigma -y _\sigma|\leq \sigma.
     \end{equation}

### 2021-04-06 Drafts and notes/Attempts/Old_draft_10.tex
Major change

--- 2021-04-06 Drafts and notes/Attempts/Old_draft_09.tex
@@
 \begin{align*}
-    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u_\delta(y) - \frac{C_0|x-y+\delta \nabla d(x)|^2}{2\sigma^2}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}_\delta.
+    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u_\delta(y) - \frac{C_0|(1+\delta)x-y |^2}{2\sigma^2}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}_\delta.
 \end{align*}
@@
 so that $|Dd(x_\sigma)| = 1$. We will mention how the case $d(x_\sigma)\geq \delta_0$ is easily deduced at the end of the proof.
-\item[2.] The unit outward normal vector at a point $z\in \partial\Omega$ is given by 
-\begin{equation*}
-    \mathbf{n}(z) = -\nabla d(z).
-\end{equation*}
-The projection of $x_\sigma$ to $\partial\Omega$ is given by
-\begin{equation*}
-    \underline{x}_\sigma = x_\sigma + d(x_\sigma)\mathbf{n}(\underline{x}_\sigma).
-\end{equation*}
-Assume $0<d(x_\sigma) < \delta$, then clearly 
-\begin{equation*}
-    x_\sigma - \delta \mathbf{n}(\underline{x}_\sigma) \in \overline{\Omega}_\delta.
-\end{equation*}
-From $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(x_\sigma,x_\sigma-\delta \mathbf{n}(\underline{x}_\sigma))$ we have
+\item[2.] Since $x_\sigma\in \Omega = B(0,1)$, we have $(1-\delta)x_\sigma \in B(0,1-\delta) = \Omega_\delta$ and by convex combination, for any $\eta\in (0,1)$ we have
+\begin{equation*}
+    \eta (1-\delta)x_\sigma + (1-\eta)y_\sigma \in \overline{\Omega}_{\delta}.
+\end{equation*}
+by definition of the maximum of $\Phi^\sigma(x_\sigma,y_\sigma)$ we have
+\begin{equation*}
+    \Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma\Big(x_\sigma, \eta (1-\delta)x_\sigma + (1-\eta)y_\sigma \Big).
+\end{equation*}
+That is
+\begin{align*}
+    &- u_\delta(y_\sigma) - \frac{C_0\big|(1+\delta)x_\sigma - y_\sigma \big|^2}{2\sigma^2} \\
+    &\qquad\qquad\geq  - u_\delta\Big(\eta (1-\delta)x_\sigma + (1-\eta)y_\sigma\Big) - \frac{C_0\big|(1+\delta)x_\sigma - \eta (1-\delta)x_\sigma - (1-\eta)y_\sigma \big|^2}{2\sigma^2}.
+\end{align*}
+Therefore
+\begin{align*}
+    \frac{C_0}{2\sigma^2}\big|(1+\delta)x_\sigma - y_\sigma \big|^2 &\leq u_\delta\Big(\eta (1-\delta)x_\sigma + (1-\eta)y_\sigma\Big) - u_\delta(y_\sigma) \\
+    &\qquad\qquad  + \frac{C_0}{2\sigma^2}\Big|\eta2\delta x_\sigma + (1-\eta)\big((1+\delta)x_\sigma-y_\sigma\big)\Big|^2
+\end{align*}
+
+\item[2.] Since $x_\sigma\in \Omega = B(0,1)$, we have $(1-\delta)x_\sigma \in B(0,1-\delta) = \Omega_\delta$, thus by definition of the maximum of $\Phi^\sigma(x_\sigma,y_\sigma)$ we have
+\begin{equation*}
+    \Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(x_\sigma, (1-\delta) x_\sigma).
+\end{equation*}
+That is
+\begin{align*}
+    &u^\varepsilon(x_\sigma) - u_\delta(y_\sigma) - \frac{C_0\big|(1+\delta)x_\sigma - y_\sigma \big|^2}{2\sigma^2} - \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+\beta}}\\
+    &\qquad\qquad\quad \geq  u^\varepsilon(x_\sigma) - u_\delta((1-\delta)x_\sigma) - \frac{C_0\big|(1+\delta)x_\sigma - (1-\delta)x_\sigma \big|^2}{2\sigma^2} - \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+\beta}}.
+\end{align*}
+Therefore we obtain that
     \begin{equation}\label{e:est_sigma2}
-     \frac{C_0|x_\sigma-y_\sigma - \delta\nabla d(x_\sigma)|^2}{2\sigma^2} \leq u_\delta(x_\sigma) - u_\delta(y_\sigma) \leq C_0|x_\sigma-y_\sigma| \qquad\Longrightarrow\qquad |x_\sigma -y _\sigma|\leq \sigma.
+     \frac{C_0|(1+\delta)x_\sigma-y_\sigma|^2}{2\sigma^2} \leq u_\delta((1-\delta)x_\sigma) - u_\delta(y_\sigma) + \frac{C_0|2\delta x_\sigma|^2}{2\sigma^2}. 
+    \end{equation}
+    Let $\delta = m \sigma^\kappa$, from \eqref{e:est_sigma2} we have
+    \begin{equation}\label{e:est_sigma3n}
+        \frac{C_0|(1+\delta)x_\sigma-y_\sigma|^2}{2\sigma^2}  \leq 2C_0(1+m^2).
     \end{equation}
     This gives us that
-    \begin{equation}\label{e:est_sigma3}
-        d(x_\sigma) \geq d(y_\sigma) - |x_\sigma-y_\sigma|\geq \delta-\sigma.
-    \end{equation}
-    Let $\delta = 2\sigma$, we deduce that $d(x_\sigma)\geq \sigma$.
-    \item[3.] $x\mapsto \Phi^\sigma(x,y_\sigma)$ has a maximum at $x_\sigma\in \Omega$, thus by subsolution test for \eqref{eq:PDEeps} we have
+    \begin{equation}\label{e:est_snow}
+      \big|(1+\delta)x_\sigma - y_\sigma\big|   \leq 2\sigma\sqrt{1+m^2\sigma^{2(\kappa-1)}},
+    \end{equation}
+    therefore
+    \begin{equation}\label{e:e2}
+     |x_\sigma| \leq \frac{1-\delta}{1+\delta} + \frac{2\sigma}{1+\delta}.
+    \end{equation}
+    As $\Omega = B(0,1)$, we have $d(x) = 1-|x|$ for $x\in \Omega$, therefore
+    \begin{equation*}
+        d(x_\sigma) = 1- |x_\sigma| \geq 1 - \left(\frac{1-\delta}{1+\delta} + \frac{2\sigma}{1+\delta}\right) = \frac{2(\delta - \sigma)}{1+\delta}.
+    \end{equation*}
+    Choose 
+    \begin{equation}\label{e:scale_sigma}
+        \sigma = \frac{\delta}{2}
+    \end{equation}
+    we deduce that
+    \begin{equation}\label{e:snow_7}
+    d(x_\sigma)\geq \frac{\delta}{1+\delta} \geq \frac{\delta}{2} = \sigma
+    \end{equation}
+    if we choose only $0<\delta < 1$.
+    \item[3.] $x\mapsto \Phi^\sigma(x,y_\sigma)$ has a maximum at $x_\sigma\in \Omega$, i.e.,
+    \begin{equation*}
+        u^\varepsilon(x) - \left(\frac{C_0|(1+\delta)x-y_\sigma|^2}{2\sigma^2} + \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}\right)
+    \end{equation*}
+    has a maximum at $x_\sigma\in \Omega$. By subsolution test for \eqref{eq:PDEeps} we have
 \begin{align}\label{e:sub1}
-    &\lambda u^\varepsilon(x_\sigma) + \left|\frac{2C_0(x_\sigma-y_\sigma)}{\sigma} - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma )\right|^p - f(x_\sigma)\nonumber\\
-    &\qquad\qquad -\varepsilon\left(\frac{2n}{\sigma} + \frac{C_\varepsilon(\alpha+\beta)(\alpha+\beta+1)|D d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+\beta+2}}-\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\Delta d(x_\sigma)\right)  \leq 0.
+    &\lambda u^\varepsilon(x_\sigma) + \left|\xi_\sigma+\zeta_\sigma\right|^p - f(x_\sigma)\nonumber\\
+    &\quad  -\varepsilon\left(\frac{2n}{\sigma} + \frac{C_\varepsilon(\alpha+\beta)(\alpha+\beta+1)|D d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+\beta+2}}-\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\Delta d(x_\sigma)\right)  \leq 0
 \end{align}
-\item[4.] Let
+where 
 \begin{equation}\label{e:est_xi_zeta}
-    \xi_\sigma = \frac{2C_0(x_\sigma-y_\sigma)}{\sigma} \qquad\text{and}\qquad \zeta_\sigma = - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma)
-\end{equation}
-then $|\xi_\sigma|\leq 2C_0$ by \eqref{e:est_sigma2} and furthermore $\xi_\sigma+\zeta_\sigma \in D^-u^\varepsilon(x_\sigma)$, which, by the local gradient estimate, as $x_\sigma\in \Omega_{\sigma}$, $\xi_\sigma+\zeta_\sigma$ is bounded in terms of $\sigma$ and will blow up as $\sigma\to 0$.
-Nevertheless, we can do better as following.
-\begin{align*}
-    |\zeta_\sigma|=\left|\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma )\right| \leq \frac{C_\varepsilon(\alpha+\beta)}{\sigma^{\alpha+\beta+1}} 
+    \xi_\sigma = \frac{C_0\big((1+\delta)x_\sigma-y_\sigma\big)}{\sigma^2} \qquad\text{and}\qquad \zeta_\sigma = - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma).
+\end{equation}
+We have the following estimates
+\begin{align*}
+    |\zeta_\sigma|=\left|\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma )\right|
+    &\leq \frac{C_\varepsilon(\alpha+\beta)}{\sigma^{\alpha+\beta+1}} \\
     &\leq \frac{(\alpha+\beta)(\alpha+1)^{\alpha+1}}{\alpha} \frac{\varepsilon^{\alpha+1}}{\sigma^{\alpha+\beta+1}} \\
@@
 In particular, $|\zeta_\sigma|\leq \mathfrak{C}_\alpha$ where $\mathfrak{C}_\alpha = \alpha^{-1}(\alpha+\beta)(\alpha+1)^{\alpha+1}$.
+
+\noindent On the other hand, we need to improve the estimate \eqref{e:est_snow} to make sure that $|\xi_\sigma|$ is bounded. From \eqref{e:est_sigma2} we have
+\begin{align*}
+    \frac{C_0\big|(1+\delta)x_\sigma - y_\sigma\big|^2}{2\sigma^2} &\leq u_\delta((1-\delta)x_\sigma) - u_\delta(y_\sigma) \\
+    &\leq C_0\big|(1-\delta)x_\sigma - y_\sigma\big| \leq C_0\Big(|(1+\delta)x_\sigma - y_\sigma| + 2\delta|x_\sigma|\Big)
+\end{align*}
+which implies that 
+\begin{equation*}
+    \big|(1+\delta)x_\sigma - y_\sigma\big|^2 \leq 2\sigma^2 \big|(1+\delta)x_\sigma - y_\sigma\big| + 4\delta \sigma^2 \leq 12\sigma^3 
+\end{equation*}
+since $|x_\sigma|\leq 1$ and \eqref{e:est_snow}. Therefore we have a new estimate for $|\xi_\sigma|$ as follows.
+
 \item[5.] $y\mapsto \Phi^\sigma(x_\sigma,y)$ has a maximum at $y_\sigma\in \overline{\Omega}_\delta$, thus by supersolution test for \eqref{e:PDE_delta} we have 

### 2021-04-06 Drafts and notes/Draft_01.tex
Major change

--- 2021-04-06 Drafts and notes/Attempts/Old_draft_07.tex
@@
 
-%\usepackage[libertine,cmintegrals,cmbraceFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfFunction Analysis - Haim brezis.pdfs,vvarbb]{newtxmath}
+%\usepackage[libertine,cmintegrals,cmbrac,vvarbb]{newtxmath}
 \usepackage{eucal}
@@
 \newcommand{\kap}{\kappa}
-\newcommand{\lam}{\lambda}
+\newcommand{\lam}{ }
 \newcommand{\sig}{\sigma}
@@
 \newcommand{\Gam}{\Gamma}
-\newcommand{\Lam}{\Lambda}
+\newcommand{\Lam}{ }
 \newcommand{\Om}{\Omega}
@@
 \subsection{Motivation} Let $\Omega$ be an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$.
-Let us consider the following Hamiltonian $ H(x,\varrho) = |\varrho|^p-f(x)$ for $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$, $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
-Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ (see \cite{Lasry1989}) be the solution to
+%Let us consider the following Hamiltonian $ H(x,\varrho) = |\varrho|^p-f(x)$ for $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$,
+Let $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$. Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ (see \cite{Lasry1989}) be the solution to 
 \begin{equation}\label{eq:PDEeps}
     \begin{cases}
-    \lambda u^\varepsilon(x) + H(x,Du^\varepsilon(x)) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
+      u^\varepsilon(x) + |Du^\varepsilon(x)|^p - f(x) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
     \text{in}\;\Omega, \vspace{0cm}\\
@@
 \end{equation}
-When $1<p\leq 2$, equation \eqref{eq:PDEeps} describes the (expectation) value function associated with a minimization of a stochastic optimal control problem with state-constraint.
-We are interested in studying the asymptotic behavior of $\{u^\varepsilon\}_{\varepsilon>0}$ as $\varepsilon\rightarrow 0$.
+When $1<p\leq 2$, equation \eqref{eq:PDEeps} describes the value function associated with a minimization of a stochastic optimal control problem with state-constraint.
+We are interested in studying the asymptotic behavior of $\{u^\varepsilon\}_{\varepsilon>0}$ as $\varepsilon\rightarrow 0^+$.
 Heuristically, the state-constraint second-order problem converges to the state-constraint first-order, which is associated with deterministic optimal control, which is described in the framework of viscosity solution as follows:
@@
     \begin{cases}
-     \lambda u(x) + H(x,Du(x)) \leq 0\;\qquad\text{in}\;\Omega,\\
-     \lambda u(x) + H(x,Du(x)) \geq 0\;\qquad\text{on}\;\overline{\Omega}.
+       u(x) + |Du(x)|^p - f(x) \leq 0\;\qquad\text{in}\;\Omega,\\
+       u(x) + |Du(x)|^p - f(x) \geq 0\;\qquad\text{on}\;\overline{\Omega}.
     \end{cases} \tag{PDE$_0$}
@@
 Lions in \cite{Capuzzo-Dolcetta1990}.
-We list the assumptions on a general Hamiltonian as follow.
-\begin{itemize}
-    \item[$\mathrm{(H1)}$] There exists $C_1 > 0$ such that $H(x,p) \geq -C_1$ for all $(x,p)\in \overline{\Omega}\times\mathbb{R}^n$.
-    \item[$\mathrm{(H2)}$] There exists $C_2>0$ such that $|H(x,0)|\,\leq \,C_2$ for all $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$.
-    \item[$\mathrm{(H3)}$] For each $R>0$ there exists a modulus $\omega_{R}[0,\infty)\to [0,\infty)$ such that $\omega_R(0^+) = 0$ and 
-    \begin{equation*}
-        \begin{cases}
-        |H(x,p) - H(y,p)| \leq \omega_R(|x-y|),\\
-        |H(x,p) - H(x,q)| \leq \omega_R(|p-q|),
-        \end{cases} \qquad\text{for all}\;x,y\in \overline{\Omega}, p,q \in \mathbb{R}^n\;\text{with}\;|p|,|q|\leq R.
-    \end{equation*}
-    \item[$\mathrm{(H4)}$] $H(x,p)\rightarrow \infty$ as $|p|\to \infty$ uniformly in $x\in \overline{\Omega}$.
-\end{itemize}
+%We list the assumptions on a general Hamiltonian as follow.
+%\begin{itemize}
+%    \item[$\mathrm{(H1)}$] There exists $C_1 > 0$ such that $H(x,p) \geq -C_1$ for all $(x,p)\in \overline{\Omega}\times\mathbb{R}^n$.
+%    \item[$\mathrm{(H2)}$] There exists $C_2>0$ such that $|H(x,0)|\,\leq \,C_2$ for all $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$.
+%    \item[$\mathrm{(H3)}$] For each $R>0$ there exists a modulus $\omega_{R}[0,\infty)\to [0,\infty)$ such that $\omega_R(0^+) = 0$ and 
+%    \begin{equation*}
+%        \begin{cases}
+%        |H(x,p) - H(y,p)| \leq \omega_R(|x-y|),\\
+%        |H(x,p) - H(x,q)| \leq \omega_R(|p-q|),
+%        \end{cases} \qquad\text{for all}\;x,y\in \overline{\Omega}, p,q \in \mathbb{R}^n\;\text{with}\;|p|,|q|\leq R.
+%    \end{equation*}
+%    \item[$\mathrm{(H4)}$] $H(x,p)\rightarrow \infty$ as $|p|\to \infty$ uniformly in $x\in \overline{\Omega}$.
+%\end{itemize}
 
@@
 
-\noindent Let $\delta_0>0$ be a fixed number such that $x\mapsto \mathrm{dist}(x,\partial\Omega)$ is of class $\mathrm{C}^2$ on $\Omega\backslash \Omega_{\delta_0}$ (see \cite{gilbarg_elliptic_2001}), i.e., in the region where $0<\mathrm{dist}(x,\partial\Omega) \leq \delta_0$.
+\begin{defn} Let us define
+\begin{equation}\label{def:delta_0}
+    \delta_{0,\Omega} = \sup \big\{ \delta > 0: x\mapsto\mathrm{dist}(x,\partial\Omega)\;\text{is}\;\rmC^2\;\text{in}\;\Omega\backslash\overline{\Omega}_{\delta} \big\}.
+\end{equation}
+The distance function is of class $\mathrm{C}^2$ in the region where $0<\mathrm{dist}(x,\partial\Omega) < \delta_0$. We will simply write $\delta_0$ if the underlying domain is understood.
+\end{defn}
+
+We refer the readers to \cite{gilbarg_elliptic_2001} for the regularity of the distance function defined in the above definition.
 We then extend $\mathrm{dist}(x,\partial\Omega)$ to a function $d(x)\in \mathrm{C}^2(\mathbb{R}^n)$ such that
@@
 \begin{equation*}
-    K_1 := \max_{x\in \overline{\Omega}} |\Delta d(x)| \qquad\text{and}\qquad K_2 := \max_{x\in \overline{\Omega}} |D d(x)|.
+   K_0:= \max_{x\in \overline{\Omega}}|d(x)|, \qquad K_1 := \max_{x\in \overline{\Omega}} |\Delta d(x)| \qquad\text{and}\qquad K_2 := \max_{x\in \overline{\Omega}} |D d(x)|.
 \end{equation*}
@@
 \begin{equation*}
-    \mathcal{L}^\varepsilon[u](x) := \lambda u(x) + H(x,Du(x)) - \varepsilon \Delta u(x), \qquad x\in \Omega.
+    \mathcal{L}^\varepsilon[u](x) :=   u(x) + |Du(x)| - f(x) - \varepsilon \Delta u(x), \qquad x\in \Omega.
 \end{equation*}
@@
 The technique being used is the classical Bernstein's method.
-Let $\Omega$ be an open, bounded subset of $\R^n$, $\varepsilon \in (0,1)$ and $\lambda \in [0,1)$.
-We consider the Hamiltonian $H(x,\rho) = |\rho|^p - f(x)$ where $1<p < \infty$.
+Let $\Omega$ be an open, bounded subset of $\R^n$, $\varepsilon \in (0,1)$.
+We consider $p>1$ in this section.
+%We consider the Hamiltonian $H(x,\rho) = |\rho|^p - f(x)$ where $1<p < \infty$.
 
 \begin{thm}\label{thm:grad_1} Let $f\in \rmC(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $u\in \mathrm{C}^2(\Omega)$ be a solution to $\mathcal{L}^\varepsilon[u] = 0$ in $\Omega$.
-Assume that $\lambda u(x)-f(x)\geq -K_0$ in $\Omega$, then for $\delta>0$ there exists $C_\delta = C(K_0,p,\delta, \Vert D f\Vert_{L^\infty(\Omega)})$ such that
+Assume that $  u(x)-f(x)\geq -L$ in $\Omega$, then for $\delta>0$ there exists $C_\delta = C(L,p,\delta, \Vert D f\Vert_{L^\infty(\Omega)})$ such that
 \begin{equation*}
@@
 \begin{equation*}
-    %\frac{C_\varepsilon-\eta}{d(x)^\alpha}-\frac{M_\eta}{\lambda} \leq u(x)\leq \frac{C_\varepsilon+\eta}{d(x)^\alpha}+\frac{M_\eta}{\lambda} 
-    \lim_{d(x)\to 0} u^\varepsilon(x) \,d(x)^\alpha = C_\varepsilon 
+    %\frac{C_\varepsilon-\eta}{d(x)^\alpha}-\frac{M_\eta}{ } \leq u(x)\leq \frac{C_\varepsilon+\eta}{d(x)^\alpha}+\frac{M_\eta}{ } 
+    \lim_{d(x)\to 0} u^\varepsilon(x) \,d(x)^\alpha = C_\alpha \varepsilon^{\alpha+1}
 \end{equation*}
@@
 \begin{equation*}
-    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^{\alpha+1}\right) \varepsilon^{\alpha+1}.
+    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\alpha = \left(\frac{1}{\alpha}(\alpha+1)^{\alpha+1}\right).
 \end{equation*}
@@
 \noindent This is Theorem I.1 in \cite{Lasry1989}.
-We provide a proof in Appendix with the explicit dependence of $C_\varepsilon$ in terms of $\varepsilon$ for later use, it is useful to note that $\alpha+1 = \frac{1}{p-1}$.
-
-\subsection{Convergence result} We show the convergence (qualitatively) of \eqref{eq:PDEeps} to \eqref{eq:PDE0}.
+We provide a proof in Appendix with the explicit constant $C_\alpha\varepsilon^{\alpha+1}$ in terms of $\varepsilon$ for later use, it is useful to note that $\alpha+1 = \frac{1}{p-1}$.
+We also state the following useful results.
+
+\subsection{Convergence result} We show qualitatively the convergence of \eqref{eq:PDEeps} to \eqref{eq:PDE0}.
 We first state the following Lemma (\cite{Capuzzo-Dolcetta1990}), which characterizes the state-constraint of the first-order equation
 \begin{equation}\label{S_0}
- \lambda u(x) + H(x,Du(x)) = 0\;\qquad\text{in}\;\Omega. \tag{$S_0$}
+\begin{cases}
+       u(x) + |Du(x)| - f(x) = 0\;\qquad\text{in}\;\Omega,\\
+       u(x) + |Du(x)| - f(x) \geq 0\;\qquad\text{on}\;\partial\Omega. 
+\end{cases}\tag{$S_0$}   
 \end{equation}
@@
 \end{lem}
-\noindent Lemma \ref{lem:max} is a variation of Perron's method.
-We give a proof in Appendix for the sake of completeness.
-Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ be a solution to \eqref{eq:PDEeps}, we claim that $\{\lambda u^\varepsilon\}_{\varepsilon>0}$ is uniformly bounded from below by a constant independent of $\varepsilon$ and $\lambda$.
-We have
-\begin{equation*}
-    u^\varepsilon(x) = \lim_{m\to \infty} u^{\varepsilon}_m(x), \qquad x\in \Omega,
-\end{equation*}
- where $u^{\varepsilon,m}\in \mathrm{C}^2(\Omega)\cap \rmC(\overline{\Omega})$ solves the Drichlet problem
+\noindent We give a proof of Lemma \ref{lem:max} in Appendix for the sake of completeness.
+
+\begin{lem}\label{lem:lower-bound} Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ be a solution to \eqref{eq:PDEeps}.
+We have $\{  u^\varepsilon\}_{\varepsilon>0}$ is uniformly bounded from below by a constant independent of $\varepsilon$.
+Precisely, we have $  u^\varepsilon \geq \min_\Omega f$ and $  u\geq \min_\Omega f$.
+%\begin{equation}\label{e:lower_bound_u_eps}
+%    \inf_{x\in \Omega}   u^\varepsilon(x) \geq  \inf_{\Omega} f
+%\end{equation}
+%and also
+%\begin{equation}\label{e:lower_bound_u}
+%    \inf_{x\in \Omega}   u(x) \geq  \inf_{\Omega} f
+%\end{equation}
+\end{lem}
+\begin{proof} For $m\in \mathbb{N}$, let $u^{\varepsilon,m}\in \mathrm{C}^2(\Omega)\cap \rmC(\overline{\Omega})$ solves the Drichlet problem
 \begin{equation}\label{e:uepsm}
     \begin{cases}
-    \lambda u(x) + H(x,Du(x)) - \varepsilon \Delta u(x) = 0 &\qquad
+      u(x) + |Du(x)|^p - f(x) - \varepsilon \Delta u(x) = 0 &\qquad
     \text{in}\;\Omega, \vspace{0cm}\\
-    \;\;\quad\quad\qquad\qquad\qquad\qquad u(x) = m &\qquad
+    \;\qquad\quad\qquad\qquad\qquad\qquad u(x) = m &\qquad
     \text{on}\;\partial\Omega.
@@
 \end{equation}
-If we assume $\mathrm{(H2)}$ then we can take $C_2 = \Vert f\Vert_{L^\infty(\Omega)}$ and take $\varphi(x) \equiv -\lambda^{-1}C_2$ for $x\in \overline{\Omega}$ as a subsolution to \eqref{e:uepsm}, hence by comparison principle for \eqref{e:uepsm} we have $u^{\varepsilon}_m(x)\geq -\lambda^{-1}C_2$ for all $x\in \overline{\Omega}$, thus as $m\to \infty$ we obtain $u^\varepsilon(x) \geq -\lambda^{-1}C_2$ for all $x\in \Omega$.
-
-The following Theorem says that the large solution $u^\varepsilon$ converges to $u^0$ locally uniformly on $\Omega$ as $\varepsilon\to 0$.
-We present a simple proof here for the reader's convenience, see also \cite[Theorem VII.3]{Capuzzo-Dolcetta1990}.
-\begin{thm}[Vanishing viscosity - Qualitative result]\label{thm:qual} Assume $\mathrm{(A1)}$.
-Let $u^\varepsilon$ be the solution to \eqref{eq:PDEeps}, then there exists $u^0 \in \mathrm{C}(\overline{\Omega})$ such that $u^\varepsilon \rightarrow u^0$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$, $u^0$ solves \eqref{eq:PDE0} and $u^0 \leq u^\varepsilon$ in $\Omega$.
+We have $u^{\varepsilon}_m(x) \to u^\varepsilon(x)$ as $m\to \infty$ in $\Omega$.
+Let $\varphi(x) \equiv  ^{-1} \inf_{\Omega} f$ for $x\in \overline{\Omega}$ then $\varphi(x)$ is a classical subsolution of \eqref{e:uepsm} in $\Omega$ with
+\begin{equation*}
+    \varphi(x) =   \inf_\Omega f \leq m = u^\varepsilon_m(x) \qquad\text{for}\;x\in \partial\Omega.
+\end{equation*}
+By comparison principle for the uniformly elliptic equation \eqref{e:uepsm} we have
+\begin{equation*}
+     ^{-1}\inf_\Omega f \leq u^{\varepsilon}_m(x) \qquad\text{for all}\;x\in \Omega.
+\end{equation*}
+As $m\to \infty$ we obtain $  u^\varepsilon \geq \min_\Omega f$.
+The inequality $  u\geq \min_{\Omega}f$ follows from the comparison principle of \eqref{eq:PDE0} between supersolution $u$ on $\overline{\Omega}$ and subsolution $\varphi(x)$ in $\Omega$.
+\end{proof}
+
+We present a simple proof of the convergence $u^\varepsilon \to u$ using Lemma \ref{lem:max} for the reader's convenience, see also \cite[Theorem VII.3]{Capuzzo-Dolcetta1990}.
+\begin{thm}[Vanishing viscosity]\label{thm:qual} Assume $\mathrm{(A1)}$.
+Let $u^\varepsilon$ be the solution to \eqref{eq:PDEeps}, then there exists $u \in \mathrm{C}(\overline{\Omega})$ such that $u^\varepsilon \rightarrow u$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$, $u$ solves \eqref{eq:PDE0} in $\Omega$.
 \end{thm}
 
-\begin{proof}[Proof of Theorem \ref{thm:qual}] By a priori estimate (Theorem \ref{thm:grad_1})
+\begin{proof}[Proof of Theorem \ref{thm:qual}] By a priori estimate (Theorem \ref{thm:grad_1}) we have
 \begin{equation}\label{e:priorie_eps}
@@
 \end{equation}
-we deduce from the Arzel\'a--Ascoli theorem that there exists a subsequence $\varepsilon_j\to 0$ and a function $u^0\in \rmC(\Omega)$ such that $u^{\varepsilon_j}\to u^0$ locally uniformly in $\Omega$.
+we deduce from the Arzel\'a--Ascoli theorem that there exists a subsequence $\varepsilon_j\to 0$ and a function $u\in \rmC(\Omega)$ such that $u^{\varepsilon_j}\to u$ locally uniformly in $\Omega$.
 By the stability of viscosity solution we easily deduce that
 \begin{equation}\label{eq:u0int}
-   \lambda u^0(x) + H(x,Du^0(x)) = 0 \qquad\text{in}\;\Omega.
-\end{equation}
-Since $\lambda u^\varepsilon(x)\geq -C_2$ for all $x\in \Omega$, we also have $\lambda u^0(x)\geq -C_2$ for all $x\in \Omega$, thus together with \eqref{eq:u0int} we obtain $H(x,\xi) \leq C_2$ for all $\xi\in D^+u^0(x)$ and $x\in \Omega$.
-The coercivity $\mathrm{(H4)}$ implies that there exists $K>0$ such that
-\begin{equation*}
-    |u^0(x) - u^0(y)| \leq K \qquad\text{for all}\;x,y\in \Omega.
-\end{equation*}
-Thus we can extend $u^0$ uniquely to $u^0\in \rmC(\overline{\Omega})$.
-We will use Lemma \ref{lem:max} to show that $u^0$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$.
-It suffices to show that $u^0\geq w$ on $\overline{\Omega}$ where $w\in \rmC(\overline{\Omega})$ is the unique solution to \eqref{eq:PDE0}.
-
-For $\delta>0$, let $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\partial \Omega) > \delta\}$ and $v_\delta\in\rmC(\overline{\Omega}_\delta)$ be the state-constraint viscosity solution to the problem $\lambda u(x) + H(x,Du(x)) = 0$ in $\Omega_\delta$, i.e., $v_\delta$ is the unique viscosity solution to
+     u(x) + |Du(x)| - f(x) = 0 \qquad\text{in}\;\Omega.
+\end{equation}
+From Lemma \ref{lem:lower-bound} we have $  u^\varepsilon(x)\geq \min_{\Omega} f$ and  $  u(x)\geq \min_{\Omega} f$ for all $x\in \Omega$, together with \eqref{eq:u0int} we obtain $|\xi|\leq \max_\Omega f - \min_\Omega f$ for all $\xi\in D^+u(x)$ and $x\in \Omega$.
+In other words there is a constant $C_0$ such that
+\begin{equation*}
+    |u(x) - u(y)| \leq C_0|x-y| \qquad\text{for all}\;x,y\in \Omega.
+\end{equation*}
+Thus we can extend $u$ uniquely to $u\in \rmC(\overline{\Omega})$.
+We will use Lemma \ref{lem:max} to show that $u$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$.
+It suffices to show that $u\geq w$ on $\overline{\Omega}$ where $w\in \rmC(\overline{\Omega})$ is the unique solution to \eqref{eq:PDE0}.
+
+For $\delta>0$, let $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\partial \Omega) > \delta\}$ and $u_\delta\in\rmC(\overline{\Omega}_\delta)$ be the state-constraint viscosity solution to the problem $  u(x) + |Du(x)| - f(x) = 0$ in $\Omega_\delta$, i.e., $u_\delta$ is the unique viscosity solution to
 \begin{equation}\label{e:v_v}
     \begin{cases}
-    \lambda v_\delta(x) + H(x,Dv_\delta(x)) \leq 0 &\qquad\text{in}\;\Omega_\delta,\\
-    \lambda v_\delta(x) + H(x,Dv_\delta(x)) \geq 0 &\qquad\text{on}\;\overline{\Omega}_\delta.
+      u_\delta(x) + |Du_\delta(x)|-f(x) \leq 0 &\qquad\text{in}\;\Omega_\delta,\\
+      u_\delta(x) + |Du_\delta(x)| - f(x) \geq 0 &\qquad\text{on}\;\overline{\Omega}_\delta.
     \end{cases}
 \end{equation}
-As $v_\delta\rightarrow w$ locally uniformly as $\delta\rightarrow 0^+$ (see \cite{kim_state-constraint_2020}) and $w$ is bounded, therefore $\{v_\delta\}_{\delta>0}$ is uniformly bounded.
+As $u_\delta\rightarrow w$ locally uniformly as $\delta\rightarrow 0^+$ (see \cite{kim_state-constraint_2020}) and $w$ is bounded, therefore $\{u_\delta\}_{\delta>0}$ is uniformly bounded.
 Let $v^\varepsilon_\delta\in \rmC^2(\Omega_\delta)\cap \rmC(\overline{\Omega}_\delta)$ be the unique solution to the Dirichlet problem
@@
 \begin{cases}
-    \lambda v_\delta^\varepsilon(x) + |Dv_\delta^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v_\delta^\varepsilon(x) &\qquad\text{in}\;\Omega_\delta,\\
+      v_\delta^\varepsilon(x) + |Dv_\delta^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v_\delta^\varepsilon(x) &\qquad\text{in}\;\Omega_\delta,\\
     \;\;\;\,\quad\qquad\qquad\qquad\qquad v_\delta^\varepsilon = v_\delta &\qquad \text{on}\;\partial\Omega_\delta.
@@
 For all $\delta$ small enough $v_\delta\leq u^\varepsilon$ on $\partial \Omega_\delta$, thus by maximum principle $v^\varepsilon_\delta \leq u^\varepsilon$ on $\overline{\Omega}_\delta$.
-Let $\varepsilon\to 0$ we have $v_\delta \leq u^0$ on $\overline{\Omega}_\delta$.
-Let $\delta\rightarrow 0$ we obtain $w\leq u^0$ in $\Omega$, which implies $w\leq u^0$ on $\overline{\Omega}$ since both $w,u^0$ belong to $\rmC(\overline{\Omega})$.
-\end{proof}
-
-\subsection{Rate of convergence for first-order equation on nested domain}
-For $\delta >0$, let $u\in \rmC(\overline{\Omega})$ and $u_\delta\in \rmC(\overline{\Omega}_\delta)$, respectively, be viscosity state-constraint solutions to 
+Let $\varepsilon\to 0$ we have $v_\delta \leq u$ on $\overline{\Omega}_\delta$.
+Let $\delta\rightarrow 0$ we obtain $w\leq u$ in $\Omega$, which implies $w\leq u$ on $\overline{\Omega}$ since both $w,u$ belong to $\rmC(\overline{\Omega})$.
+\end{proof}
+
+\section{Rate of convergence via the doubling variables method}
+In this section, we focus on the rate of convergence for the case $f\in \mathrm{C}^1(\overline{\Omega})$.
+By adding a constant to the solution $u^\varepsilon$ of \eqref{eq:PDEeps}, without loss of generality we can assume the \emph{nonnegativity}
+\begin{equation}\label{e:minf}
+    \min_{\overline{\Omega}} f(x) = 0.
+\end{equation}
+As a consequence, $u^\varepsilon(x),u(x)\geq 0$ for $x\in \Omega$ by Lemma \ref{lem:lower-bound}.
+\subsection{Lower bound}
+We start with the lower bound of $u^\varepsilon - u$.
+\begin{thm} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
+Assume \eqref{e:minf} and $H(x,\xi) = |\xi|^p - f(x)$ where $p\in\left(1,2\right]$.
+Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that
+\begin{equation}\label{e:lower1}
+    -C\sqrt{\varepsilon} \leq u^\varepsilon(x) - u(x) \qquad\text{for all}\;x\in \Omega.
+\end{equation} 
+\end{thm}
+\begin{proof} The proof relies on a well-known rate of convergence for vanishing viscosity of viscous Hamilton--Jacobi equation with Dirichlet boundary condition (\textcolor{blue}{citation}).
+As $u\in \mathrm{C}(\overline{\Omega})$, let $g(x) = u(x)$ for $x\in \partial\Omega$ then $g\in \mathrm{C}(\partial\Omega)$.
+Let $v^\varepsilon\in \mathrm{C}^2(\Omega)\cap \mathrm{C}(\overline{\Omega})$ be the unique viscosity solution to
 \begin{equation*}
     \begin{cases}
-    \lambda u(x)+H(x,Du(x)) \leq 0 \quad\text{in}\;\Omega,\\
-    \lambda u(x)+H(x,Du(x)) \geq 0 \quad\text{on}\;\overline{\Omega},
-    \end{cases}\qquad\text{and}\qquad 
+          v^\varepsilon(x) + |Dv^\varepsilon(x)|^p - f(x) - \varepsilon \Delta v^\varepsilon(x) = 0 &\qquad\text{in}\;\Omega,\\
+        \qquad\qquad\qquad\qquad\qquad \qquad\quad v^\varepsilon(x) = g(x) &\qquad\text{on}\;\partial\Omega.
+    \end{cases}
+\end{equation*}
+It is well-known that $v^\varepsilon \to u$ uniformly where $v$ is the viscosity solution to
+\begin{equation*}
 \begin{cases}
-    \lambda u_\delta(x)+H(x,Du_\delta(x)) \leq 0 \quad\text{in}\;\Omega_\delta,\\
-    \lambda u_\delta(x)+H(x,Du_\delta(x)) \geq 0 \quad\text{on}\;\overline{\Omega}_\delta.
+       v(x) + |Dv(x)| - f(x) = 0 &\qquad\text{in}\;\Omega,\\
+     \qquad\qquad\qquad\quad\; v(x) = g(x)&\qquad\text{on}\;\partial\Omega. 
 \end{cases}
 \end{equation*}
-It is well-known that $0\leq u_\delta(x) - u(x) \leq C\delta$ for $x\in\overline{\Omega}_\delta$ and this rate is optimal.
-This can be proved easily by comparison principle when the domain have a scaling structure with $\mathrm{(A3)}$ holds, i.e., $\Omega_\delta = (1-\delta)\Omega$ (see \cite{kim_state-constraint_2020}).
-We have the following theorem for the general smooth domains.
-
-\begin{thm}\cite{Capuzzo-Dolcetta1990}\label{thm:conv_general} Let $\Omega$ be an open, bounded and connected subset $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary. Assume $\mathrm{(H1)}-\mathrm{(H4)}$. 
-Then there exists a constant $C$ independent of $\delta$ such that
-\begin{equation*}
-    0\leq u_\delta(x) - u(x) \leq C\delta \qquad\text{for}\; x\in \overline{\Omega}.
+By comparison principle, it is clear that $v = u$, the solution of \eqref{eq:PDE0}. Furthermore, there exists a positive constant $C$ such that 
+\begin{equation}\label{e:cp1}
+     |v^\varepsilon(x)  - u(x)| \leq C\sqrt{\varepsilon} \qquad\text{for}\;x\in \overline{\Omega}.
+\end{equation}
+By comparison principle for \eqref{eq:PDEeps} we have
+\begin{equation}\label{e:cp2}
+    v^\varepsilon(x)\leq u^\varepsilon(x) \qquad\text{for}\;x\in \Omega.
+\end{equation}
+From \eqref{e:cp1} and \eqref{e:cp2} we obtain the lower bound \eqref{e:lower1}.
+\end{proof}
+
+%We state some observations  regarding the property of the solution $u$ to \eqref{eq:PDE0}.
+
+\begin{lem}\label{lem:f=0} If $f\geq 0$ in $\Omega$ then $u(x) = 0$ whenever $f(x) = 0$. In particular $f \equiv 0$ implies $u \equiv 0$.
+\end{lem}
+\begin{proof} We have $u\geq 0$ in $\overline{\Omega}$. Using the optimal control formula (\cite{Bardi1997,Hung2019}), we have
+\begin{equation}\label{e:foru}
+    u(x) = \inf \left\lbrace \int_0^\infty e^{-  s}\Big(c|\dot{\eta}(s)|^{q} +f(\eta(s))\Big)ds: \eta\in \mathrm{AC}([0,\infty);\overline{\Omega}), \eta(0) = x\right\rbrace
+\end{equation}
+where 
+\begin{equation*}
+    c = \left(pq^{\frac{1}{p-1}}\right)^{-1} \qquad\text{and}\qquad \frac{1}{p} + \frac{1}{q} = 1.
+\end{equation*}
+Assume that $f(x) = 0$, we can choose $\eta(s) = x$ for all $s\in [0,\infty)$ as an admissible path in \eqref{e:foru} to obtain that
+\begin{equation*}
+    u(x) \leq  \int_0^\infty e^{-  s}\Big(c|\dot{\eta}(s)|^{q} +f(\eta(s))\Big)ds = f(x) =  0.
+\end{equation*}
+\end{proof}
+\noindent For simplicity, let us assume $  = 1$ from now on.
+We state the following lemma as a crucial estimate we will be using.
+It is a refined construction of the supersolution for \eqref{eq:PDEeps}.
+\begin{lem}\label{lem:super_refined} There exist positive constants $\nu = \nu(\alpha,\delta_0)$ and $C_\nu$ such that if $0\leq \delta \leq \frac{1}{2}\delta_0$ then
+\begin{equation*}
+    w(x) = \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + \max f + C_\nu \varepsilon^{\alpha+2}, \qquad x\in \Omega_\delta 
+\end{equation*}
+is a supersolution of \eqref{eq:PDEeps} in $\Omega_\delta$. 
+\end{lem}
+
+\begin{proof}
+We have $|\nabla d(x)| = 1$ for all $x\in \Omega_\delta\backslash \Omega_{\delta_0}$.
+Recall from Theorem \ref{thm:wellposed1<p<2} that $C_\alpha^p \alpha^p = C_\alpha \alpha (\alpha+1)$ and $p(\alpha+1) = \alpha+2$, we compute
+\begin{equation*}
+    |\nabla w(x)|^p = \nu^p\frac{(C_\alpha\alpha)^p\varepsilon^{p(\alpha+1)}}{(d(x)-\delta)^{p(\alpha+1)}} = \nu^p\frac{C_\alpha \alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}
+\end{equation*}
+and
+\begin{equation*}
+    \varepsilon\Delta w(x) = \nu\frac{C_\alpha\alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}} - \nu\frac{C_\alpha\alpha\varepsilon^{\alpha+2}\Delta d(x)}{(d(x)-\delta)^{\alpha+1}}.
+\end{equation*}
+We have
+\begin{equation*}
+    \begin{split}
+        \mathcal{L}\left[w_\delta\right] \geq \frac{\nu C_\alpha\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + \frac{C_\alpha \alpha (\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}\left[\nu^p-\nu +\nu\frac{(d(x)-\delta)\Delta d(x)}{\alpha+1}\right].
+    \end{split}
+\end{equation*}
+Recall that $K_2= \Vert \Delta d\Vert_{L^\infty}$, we observe that in the region where $\delta< d(x)\leq \delta_0$ then
+\begin{equation*}
+    \left|\frac{(d(x)-\delta)\Delta d(x)}{\alpha+1}\right| \leq \frac{\delta_0\Vert \Delta d\Vert_{L^\infty}}{\alpha+1} \leq \frac{K_2\delta_0}{\alpha+1}\leq K_2\delta_0.
+\end{equation*}
+Therefore
+\begin{equation}\label{e:choose_nu}
+    \begin{split}
+        \nu^p-\nu +\nu\frac{(d(x)-\delta)\Delta d(x)}{(\alpha+1)} \geq \nu^p - \nu - \nu K_2\delta_0 = \nu\Big(\nu^{p-1} - (1+K_2\delta_0)\Big).
+    \end{split}
+\end{equation}
+We will choose $\nu$ as follows. For $\gamma>1$ we have
+\begin{equation*}
+    \Big||x+y|^\gamma - |x|^\gamma\Big|\leq \gamma\Big(|x|+|y|\Big)^{\gamma-1}|y|
+\end{equation*}
+which implies that
+\begin{equation*}
+     0 \leq (1+K_2\delta_0)^{\alpha+1} - 1 \leq\underbrace{(\alpha+1)\left(1+K_2\delta_0\right)^\alpha K_2}_{C_2}\delta_0.
+\end{equation*}
+which implies that $(1+K_2\delta_0)^{\alpha+1} \leq 1 + C_2\delta_0$, thus
+\begin{equation}\label{e:cru1}
+    (1+K_2\delta_0) \leq (1+C_2\delta_0)^{\frac{1}{\alpha+1}} = (1+C_2\delta_0)^{p-1}
+\end{equation}
+since $\alpha+1 = \frac{1}{p-1}$.
+Choose $\nu = 1+C_2\delta_0$ in \eqref{e:choose_nu} we obtain $\mathcal{L}[w]\geq 0$ in $\{x\in \Omega_\delta: \delta <d(x)\leq \delta_0\}$.
+Recall that $K_0 = \Vert d\Vert_{L^\infty}$ and $K_1 = \Vert \nabla d\Vert_{L^\infty}$.
+In the region where $d(x)\geq \delta_0$ then $d(x)-\delta \geq \frac{1}{2}\delta_0$, we have
+\begin{align*}
+    \mathcal{L}[w] &= \frac{\nu C_\alpha\alpha\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + \max_{\Omega} f - f(x)\\
+    &+  \nu^p\frac{C_\alpha\alpha(\alpha+1)\varepsilon^{\alpha+1}}{(d(x)-\delta)^{\alpha+2}}|\nabla d(x)|^p - \nu \frac{C_\alpha \alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}|\nabla d(x)|^2
+    + \nu \frac{C_\alpha \alpha \varepsilon^{\alpha+2}\Delta d(x)}{(d(x)-\delta)^{\alpha+1}} + C_\nu \varepsilon^{\alpha+2}\\
+    &\geq \frac{C_\alpha \alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}\left(\nu^p|\nabla d(x)|^p - \nu |\nabla d(x)|^2 + \nu \frac{\Delta d(x)(d(x)-\delta)}{\alpha+1}\right) + C_\nu \varepsilon^{\alpha+2}\\
+    &\geq (C_\nu - C_3)\varepsilon^{\alpha+2}
+\end{align*}
+where 
+\begin{equation*}
+    C_3 = \left(\frac{2}{\delta_0}\right)^{\alpha+2} C_\alpha\alpha(\alpha+1) \left(\nu^pK_1^p + \nu K_1^2 + \nu \frac{K_0K_2}{\alpha+1}\right).
+\end{equation*}
+Therefore we can choose $C_\nu = C_3$ to obtain $\mathcal{L}[w]\geq 0$ in this region $\{x\in \Omega_\delta:d(x)\geq \delta_0\}$.
+\end{proof}
+
+\subsection{Zero data}
+\begin{thm}\label{thm:rate_doubling0} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
+Assume that $H(x,\xi) = |\xi|^p - f(x)$ where $p\in\left(1,2\right)$ and $f\equiv 0$ in $\Omega$.
+Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u \equiv 0 $ be the unique solution to \eqref{eq:PDE0}.
+Then there exists a constant $C$ independent of $\varepsilon$ such that
+\begin{equation*}
+ -C \varepsilon^{\frac{1}{2}}\leq  u^\varepsilon(x) - u(x) \leq C\varepsilon \quad  \text{for} \quad x\in \Omega_{\varepsilon}.
 \end{equation*}
 \end{thm}
-\begin{proof}[Proof of Theorem \ref{thm:conv_general}] Following \cite{Capuzzo-Dolcetta1990}, we construct a $\rmC^2$ diffeomorphism $T:\overline{\Omega}_\delta\to \overline{\Omega}$ that maps $\partial\Omega_\delta$ to $\partial\Omega$ and satisfies
-\begin{equation}\label{e:bound_T}
-    \sup_{x\in \overline{\Omega}_\delta}\Big(|T(x)-x| + |DT(x) - \mathrm{Id}|\Big) \leq C\delta
-\end{equation}
-for some constant $C$ independent of $\delta$.
-Let us define $\tilde{u}_\delta(x) = u_\delta\left(T^{-1}(x)\right)$ for $x\in \overline{\Omega}$.
-Using $\mathrm{(H4)}$ and \eqref{e:bound_T} we obtain that $\tilde{u}_\delta$ is a viscosity subsolution to
-\begin{equation*}
-    \lambda \tilde{u}_\delta(x) + H(x,D\tilde{u}_\delta(x))  = C\delta \qquad\text{in}\;\Omega.
-\end{equation*}
-Therefore by comparison principle $0\leq \tilde{u}_\delta(x) - u(x) \leq C\delta$ on $\overline{\Omega}$, i.e., $0\leq \tilde{u}_\delta(Ty) - u(Ty) \leq C\delta$ on $\overline{\Omega}_\delta$, hence
-\begin{equation*}
-    0 \leq u_\delta(y) - u(y) \leq u_\delta(y) - u(Ty) + u(Ty) - u(y) \leq C\delta
-\end{equation*}
-since $u$ is Lipschitz on $\overline{\Omega}$.
-\end{proof}
-
-\section{Rate of convergence via the doubling variables method}
-\noindent The main result is the following Theorem.
-\begin{thm}\label{thm:rate_doubling1} Let $\Omega$ be an open, bounded and connected subset $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary.
-Assume $\mathrm{(A1)},\mathrm{(H1)}-\mathrm{(H4)}$ and $1<p<2$.
-Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u^0$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that
-\begin{equation*}
-    0\leq u^\varepsilon(x) - u^0(x) \leq C\sqrt{\varepsilon} \qquad\text{for}\;x\in \Omega_{2\sqrt{\varepsilon}}.
-\end{equation*}
+
+\begin{proof} From Lemma \ref{lem:super_refined} and comparison principle, we have the estimate
+\begin{equation*}
+    u^\varepsilon(x)\leq \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} + C_\nu\varepsilon^{\alpha+2}, \qquad x\in \Omega.
+\end{equation*}
+Note that in this case $u^\varepsilon \to u \equiv 0$ as $\varepsilon\to 0$. We consider
+\begin{equation*}
+    \Phi(x,y) := u^\varepsilon(x) - u(y) - \frac{C_0|x-y|^2}{\sigma} - (1+\delta^\alpha)\frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}.
+\end{equation*}
+It has a maximum at $(x_\sigma,y_\sigma)\in \Omega\times\overline{\Omega}$. From $\Phi(x_\sigma,y_\sigma)\geq \Phi(x_\sigma,x_\sigma)$ we have
+\begin{equation*}
+    \frac{C_0|x_\sigma-y_\sigma|^2}{\sigma}\leq u(x_\sigma) - u(y_\sigma)\leq C_0|x_\sigma - y_\sigma| \qquad\Longrightarrow\qquad |x_\sigma - y_\sigma|\leq \sigma.
+\end{equation*}
+From $\Phi(x_\sigma,y_\sigma)\geq \Phi(x_0,x_0)$ for a fixed point $x_0 \in \Omega$ that has the largest distance away from the boundary, we have
+\begin{equation*}
+    \delta^\alpha\frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x_{\sigma})^\alpha} \leq u^\varepsilon(x_{\sigma}) - \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x_{\sigma})^\alpha} + C\varepsilon^{\alpha+1} \leq C_{\nu}\varepsilon^{\alpha+2}+ C\varepsilon^{\alpha+1}.
+\end{equation*}
+Thus
+\begin{equation*}
+    d(x_\sigma) \geq C\delta.
+\end{equation*}
+Now the subsolution test of $x\mapsto \Phi(x,y_\sigma)$ gives us
+\begin{equation*}
+\begin{split}
+    u^\varepsilon(x) + &\left|\frac{2C_0(x_\sigma-y_\sigma)}{\sigma}-(1+\delta^\alpha)\frac{\nu C_\alpha\alpha\varepsilon^{\alpha+1}\nabla d(x_\sigma)}{d(x_\sigma)^{\alpha+1}}\right|^p \\
+    &- \varepsilon \left(\frac{2nC_0}{\sigma} - (1+\delta^\alpha)\frac{\nu C_\alpha\alpha(\alpha + 1)\varepsilon^{\alpha+1}|\nabla d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+2}} + (1+\delta^\alpha)\frac{\nu C_\alpha \alpha \varepsilon^{\alpha+1}\Delta d(x_\sigma)}{d(x_\sigma)^{\alpha+1}}\right)\leq 0.
+\end{split}    
+\end{equation*}
+Similarly, the supersolution test of $y\mapsto \Phi(x_\sigma,y)$ gives us
+\begin{equation*}
+    u(y_\sigma) + \left|\frac{2C_0(x_\sigma-y_\sigma)}{\sigma}\right|^p \geq 0.
+\end{equation*}
+Therefore
+\begin{equation}
+\label{doubling}
+\begin{split}
+    u^\varepsilon(x_\sigma) - u(y_\sigma) \leq & p\left|2C_0+(1+\delta^\alpha)\nu C_\alpha \alpha\left( \frac{\varepsilon}{\delta}\right)^{\alpha+1}\right|^{p-1}(1+\delta^\alpha) \nu C_\alpha \alpha \left(\frac{\varepsilon}{\delta}\right)^{\alpha+1} \\
+    &+2nC_0\frac{\varepsilon}{\sigma} + (1+\delta^\alpha)\nu C_\alpha \alpha(\alpha+1)\left(\frac{\varepsilon}{\delta}\right)^{\alpha+2} + (1+\delta^\alpha)\nu C_\alpha \alpha C \left(\frac{\varepsilon}{\delta}\right)^{\alpha+1}\varepsilon\\
+    &\leq C\left(\frac{\varepsilon}{\sigma} + \left(\frac{\varepsilon}{\delta}\right)^{\alpha+1} + \left(\frac{\varepsilon}{\delta}\right)^{\alpha+2} \right).
+\end{split}
+\end{equation}
+Max happens when we choose $\sigma = 1$, and hence
+\begin{equation*}
+    u^\varepsilon(x_\sigma) - u(y_\sigma) \leq C\left( \frac{\varepsilon}{1} + \left(\frac{\varepsilon}{\delta}\right)^{\alpha+1} + \left(\frac{\varepsilon}{\delta}\right)^{\alpha+2}\right).
+\end{equation*}
+Choosing $\delta = \varepsilon^\frac{\alpha}{\alpha+1}$ we obtain 
+\begin{equation*}
+    u^\varepsilon(x_\sigma) - u(y_\sigma) \leq C(\varepsilon + \varepsilon + \varepsilon ^p ) \leq C\varepsilon.
+\end{equation*}
+As a consequence, 
+\begin{equation}
+\label{zerodata}
+   -C \varepsilon^{\frac{1}{2}}\leq  u^\varepsilon(x) - u(x) \leq C\varepsilon + \left(1+\varepsilon^{\frac{\alpha^2}{\alpha+1}}\right)\frac{\nu C_\alpha  \varepsilon^{\alpha+1}}{d(x)^\alpha} 
+\end{equation}
+for every $x\in \Omega$.
+\end{proof}
+
+\begin{rem} \textcolor{blue}{We believe that in case $f\equiv  0$, the lower bound in Theorem \ref{thm:rate_doubling0} can be made to $-C\varepsilon \leq u^\varepsilon - u$ instead of $-C\sqrt{\varepsilon}$.}
+\end{rem}
+
+\subsection{Compactly supported data}
+\begin{thm}\label{thm:rate_doubling0} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
+Assume that $H(x,\xi) = |\xi|^p - f(x)$ where $p\in\left(1,2\right)$ and $f$ is compactly supported in $\Omega$.
+Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
+Then there exists a constant $C$ depends on the support of $f$ such that
+\begin{equation*}
+|u^\varepsilon(x) - u(x)| \leq C\sqrt{\varepsilon} \quad  \text{for} \quad x\in \Omega_{\varepsilon}.
+\end{equation*}
+Furthermore, in the region where $f$ vanishes, the rate of convergence can be improved to $\mathcal{O}(\varepsilon)$ in $\Omega_\varepsilon$.
 \end{thm}
 
-\begin{proof}[Proof of Theorem \ref{thm:rate_doubling1}] Let $u_\delta\in \mathrm{C}(\overline{\Omega}_\delta)$ be the state-constraint solution to
-\begin{equation}\label{e:PDE_delta}
-    \begin{cases}  
-    \lambda u_\delta(x) + H(x,Du_\delta(x)) \leq 0 \qquad\text{in}\; \Omega_\delta\\
-    \lambda u_\delta(x) + H(x,Du_\delta(x)) \geq 0 \qquad\text{on}\; \overline{\Omega}_\delta.
-    \end{cases} \tag{PDE$_\delta$}
-\end{equation} 
-Let $C_f$ be the Lipschitz constant of $f$ and $\beta,\sigma,\delta \in (0,1)$ to be chosen later.
-Recall the definition of $C_\varepsilon$ from Theorem \ref{thm:wellposed1<p<2}, we define the auxiliary functional
+\begin{proof} Without loss of generality, we assume $f$ is compactly supported in $\Omega_{\kappa}$ where $0<\kappa < \frac{1}{2}\delta_0$.
+Let $g_\kappa = u^\varepsilon$ on $\partial\Omega_{\kappa}$, then the solution $u^\varepsilon$ of \eqref{eq:PDEeps} also solves
+\begin{equation*}
+    \left\{
+  \begin{aligned}
+  u^\varepsilon(x) + |Du^\varepsilon(x)|^p-\varepsilon \Delta u^\varepsilon(x) &=0 \;\qquad \text{in } U ,\\
+  u^\varepsilon(x) &= +\infty \quad \text{on } \partial \Omega,\\
+  u^\varepsilon(x) &= g_\kappa \;\quad \text{on } \partial \Omega_{\kappa},
+    \end{aligned}
+\right.
+\end{equation*}
+in the annulus $U_\kappa= \Omega \setminus \overline{\Omega}_{\kappa} = \{x\in \Omega: 0< d(x) < \kappa\}$.
+From Theorem \ref{thm:wellposed1<p<2}, let $\tilde{u}^\varepsilon\in \mathrm{C}^2(U_\kappa)$ be the solution to the following problem in the annulus $U_\kappa= \Omega \setminus \overline{\Omega}_{\kappa}$
+\begin{equation*}
+    \left\{
+        \begin{aligned}
+            \tilde{u}^\varepsilon(x) + |D\tilde{u}^\varepsilon(x)|^p-\varepsilon \Delta \tilde{u}^\varepsilon(x) &=0 \;\qquad \text{in } U_\kappa ,\\
+            \tilde{u}^\varepsilon(x) &= +\infty \quad \text{on } \partial U = \partial \Omega\cup \partial \Omega_{\kappa}.
+        \end{aligned}
+    \right.
+\end{equation*}
+Here the boundary condition is understood as $\tilde{u}^\varepsilon(x)\to \infty$ as $d_\kappa(x)\to 0$ where $d_\kappa(\cdot)$ is the distance function from the boundary of the annulus $U_\kappa$, i.e.,
+\begin{equation*}
+    d_\kappa(x) = \min \big\lbrace \mathrm{dist}(x,\partial \Omega_\kappa),\mathrm{dist}(x)  \big\rbrace \leq d(x) \qquad\text{for}\;x\in U_\kappa.
+\end{equation*}
+Since $f = 0$ in $\overline{U}$, by Lemma \ref{lem:f=0} $u=0$ in $\overline{U}$, thus it is also the unique state-constraint solution to
+\begin{equation*}
+    \left\{
+        \begin{aligned}
+            u(x)+ |Du(x)|^p &=0 \quad \text{in } U_\kappa ,\\
+            u(x)+ |Du(x)|^p &\geq 0 \quad \text{on } \partial U_\kappa = \partial \Omega \cup\partial \Omega_{\kappa}.
+        \end{aligned}
+    \right.
+\end{equation*}
+From \eqref{zerodata} and the fact that $u \equiv 0$ in $U$, there exists a constant $C$ (depends on $\kappa$) such that
+\begin{equation} \label{annulus}
+   \tilde{u}^\varepsilon(x) \leq C\varepsilon + \left(1+\varepsilon^{\frac{\alpha^2}{\alpha+1}}\right)\frac{\nu C_\alpha  \varepsilon^{\alpha+1}}{d_\kappa(x)^\alpha} \qquad\text{for}\;x\in U_\kappa.
+\end{equation}
+%Since $f \equiv 0 $ in $U$, $u (x) = 0$ in $U$, which gives us
+%\begin{equation}\label{annulus}
+%   -C \varepsilon^{\frac{1}{2}}\leq \tilde{u}^\varepsilon(x)  \leq C\varepsilon + \left(1+\varepsilon^{\frac{\alpha^2}{\alpha+1}}\right)\frac{\nu C_\alpha  \varepsilon^{\alpha+1}}{\tilde{d}(x)^\alpha}.
+%\end{equation}
+By comparison principle in $U_\kappa$, $u^\varepsilon \geq 0$ and \eqref{annulus} we have
+\begin{equation}\label{annulus2}
+    0\leq u^\varepsilon(x) \leq \tilde{u}^\varepsilon(x) \leq C\varepsilon + \left(1+\varepsilon^{\frac{\alpha^2}{\alpha+1}}\right)\frac{\nu C_\alpha  \varepsilon^{\alpha+1}}{d_\kappa(x)^\alpha}  \qquad\text{for}\;x\in U_\kappa.
+\end{equation}
+In other words, in the region where $f = 0$ the have an upper bound for $u^\varepsilon - u$.
+We proceed with the doubling variable method.
+Let $\sigma,\delta\in (0,1)$, we consider the auxiliary functional
+\begin{equation*}
+    \Phi(x,y)= u^\varepsilon(x) - u(y) -\frac{C_0|x-y|^2}{\sigma} - (1+\delta^\alpha) \frac{C_\alpha \varepsilon^{\alpha +1}}{d(x)^\alpha}, \qquad (x,y)\in \overline{\Omega}\times \overline{\Omega}.
+\end{equation*}
+Since $\displaystyle d(x)^\alpha u^\varepsilon(x) \to C_\alpha \varepsilon^{\alpha+1}$ as $d(x) \to 0$, we deduce that
+\begin{equation*}
+    \max_{(x,y) \in \overline{\Omega} \times \overline{\Omega}} \Phi(x,y) = \Phi(x_\sigma, y_\sigma) \qquad\text{for some}\;(x_\sigma,y_\sigma) \in \Omega \times \overline{\Omega}.
+\end{equation*}
+Similar to the zero data case, from $\Phi(x_\sigma, y_\sigma) \geq \Phi(x_\sigma, x_\sigma)$, we can deduce that
+\begin{equation*}
+    \left| x_\sigma - y_\sigma \right| \leq \sigma.  
+\end{equation*}
+If $ d(x_\sigma) \geq \frac{1}{2}\kappa$, then by a similar  computation of subsolution test as in \eqref{doubling} we get 
 \begin{align*}
-    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u_\delta(y) - \frac{C_0|x-y - \delta \nabla d(x)|^2}{\sigma}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}_\delta,
+     u^\varepsilon(x_\sigma) - u(y_\sigma) \leq & p\left(2C_0+(1+\delta^\alpha)\nu C_\alpha \alpha\left( \frac{2\varepsilon}{\kappa}\right)^{\alpha+1}\right)^{p-1}(1+\delta^\alpha) \nu C_\alpha \alpha \left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+1} + C\sigma\nonumber\\
+    &+\frac{2nC_0\varepsilon}{\sigma} + (1+\delta^\alpha)\nu C_\alpha \alpha(\alpha+1)\left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+2} + (1+\delta^\alpha)\nu C_\alpha \alpha C \left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+1}\varepsilon\nonumber\\
+    &\leq C\left(\sigma + \frac{\varepsilon}{\sigma} + \left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1} + \left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2} \right).
 \end{align*}
-where $C_0$ is the Lipschitz constant of $u^0$ (also the Lipschitz constant of $u_\delta$ for $\delta>0$). We split the proof into several steps.
-\begin{enumerate}
-    \item[1.] Since $u^\varepsilon (x)d(x)^\alpha \to C_\varepsilon$ as $d(x)\to 0$, we see that $\Phi^\sigma(x,y)\to -\infty$ as $d(x)\to 0$, therefore for a fixed $\varepsilon>0$, there is $(x_{\sigma},y_\sigma)\in \Omega\times\overline{\Omega}_\delta$ such that
-\begin{equation*}
-    \max_{\overline{\Omega}\times \overline{\Omega}_\delta} \Phi^\sigma = \Phi^\sigma(x_\sigma,y_\sigma).
-\end{equation*}
-We can assume that 
-\begin{equation}\label{e:ass_delta0}
-    d(x_\sigma) < \delta_0
-\end{equation}
-so that $|Dd(x_\sigma)| = 1$. We will mention how the case $d(x_\sigma)\geq \delta_0$ is easily deduced at the end of the proof.
-\item[2.] $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(x_\sigma,x_\sigma)$ gives us that
-    \begin{equation}\label{e:est_sigma2}
-     \frac{C_0|x_\sigma-y_\sigma|^2}{\sigma} \leq u_\delta(x_\sigma) - u_\delta(y_\sigma) \leq C_0|x_\sigma-y_\sigma| \qquad\Longrightarrow\qquad |x_\sigma -y _\sigma|\leq \sigma.
-    \end{equation}
-    This gives us that
-    \begin{equation}\label{e:est_sigma3}
-        d(x_\sigma) \geq d(y_\sigma) - |x_\sigma-y_\sigma|\geq \delta-\sigma.
-    \end{equation}
-    Let $\delta = 2\sigma$, we deduce that $d(x_\sigma)\geq \sigma$.
-    \item[3.] $x\mapsto \Phi^\sigma(x,y_\sigma)$ has a maximum at $x_\sigma\in \Omega$, thus by subsolution test for \eqref{eq:PDEeps} we have
-\begin{align}\label{e:sub1}
-    &\lambda u^\varepsilon(x_\sigma) + \left|\frac{2C_0(x_\sigma-y_\sigma)}{\sigma} - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma )\right|^p - f(x_\sigma)\nonumber\\
-    &\qquad\qquad -\varepsilon\left(\frac{2n}{\sigma} + \frac{C_\varepsilon(\alpha+\beta)(\alpha+\beta+1)|D d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+\beta+2}}-\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\Delta d(x_\sigma)\right)  \leq 0.
+Max happens when $\sigma = \sqrt{\varepsilon}$, for example, which gives us  
+\begin{equation}\label{e:final1}
+    \Phi(x_\sigma,y_\sigma) \leq u^\varepsilon(x_\sigma) - u(y_\sigma) \leq C\sqrt{\varepsilon}.
+\end{equation}
+If $d(x_\sigma) < \frac{1}{2}\kappa$ then $x_\sigma \in U_\kappa$ and furthermore $\mathrm{dist}(x_\sigma,\partial \Omega_\kappa) > \frac{1}{2}\kappa$, therefore $d_\kappa(x_\sigma) = d(x_\sigma)$.
+Indeed, for any $y\in\partial\Omega$ and $z\in \partial\Omega_k$, we have
+\begin{equation*}
+    |x_\sigma - z| + |x_\sigma - y| \geq |y-z|.
+\end{equation*}
+Taking the infimum over all $y\in \partial\Omega$ we deduce that
+\begin{equation*}
+    |x_\sigma - z| + d(x_\sigma) \geq \inf_{y\in \partial \Omega}|y-z| = d(z) = \kappa
+\end{equation*}
+since $z\in \partial\Omega_k = \{x\Omega: d(x) = \kappa\}$. Thus we have $|x_\sigma - z| \geq \kappa - d(x_\sigma) > \frac{1}{2}\kappa$ for all $z\in \partial\Omega_k$. We have further that
+\begin{equation*}
+    \mathrm{dist}(x_\sigma,\partial\Omega_\kappa) = \kappa - d(x_\sigma).
+\end{equation*}
+Using \eqref{annulus2} and the fact that $u \geq 0$ we have
+\begin{align}
+    \Phi(x_\sigma, y_\sigma) &\leq u^\varepsilon (x_\sigma)-\left(1+\delta^\alpha\right)\frac{\nu C_\alpha  \varepsilon^{\alpha+1}}{d(x_\sigma)^\alpha}\nonumber\\
+    &= u^\varepsilon (x_\sigma)-\left(1+\varepsilon^{\frac{\alpha^2}{\alpha+1}}\right)\frac{\nu C_\alpha  \varepsilon^{\alpha+1}}{d_\kappa(x_\sigma)^\alpha}
+    \leq C \varepsilon\label{e:final2}
 \end{align}
-\item[4.] Let
-\begin{equation}\label{e:est_xi_zeta}
-    \xi_\sigma = \frac{2C_0(x_\sigma-y_\sigma)}{\sigma} \qquad\text{and}\qquad \zeta_\sigma = - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma)
-\end{equation}
-then $|\xi_\sigma|\leq 2C_0$ by \eqref{e:est_sigma2} and furthermore $\xi_\sigma+\zeta_\sigma \in D^-u^\varepsilon(x_\sigma)$, which, by the local gradient estimate, as $x_\sigma\in \Omega_{\sigma}$, $\xi_\sigma+\zeta_\sigma$ is bounded in terms of $\sigma$ and will blow up as $\sigma\to 0$.
-Nevertheless, we can do better as following.
-\begin{align*}
-    |\zeta_\sigma|=\left|\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma )\right| \leq \frac{C_\varepsilon(\alpha+\beta)}{\sigma^{\alpha+\beta+1}} 
-    &\leq \frac{(\alpha+\beta)(\alpha+1)^{\alpha+1}}{\alpha} \frac{\varepsilon^{\alpha+1}}{\sigma^{\alpha+\beta+1}} \\
-    &= \frac{(\alpha+\beta)(\alpha+1)^{\alpha+1}}{\alpha}\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)}
-\end{align*}
-by choosing $\sigma = \varepsilon^\gamma$ where
-\begin{equation*}
- \displaystyle 0 < \gamma < \frac{\alpha+1}{\alpha+1+\beta}.
-\end{equation*}
-In particular, $|\zeta_\sigma|\leq \mathfrak{C}_\alpha$ where $\mathfrak{C}_\alpha = \alpha^{-1}(\alpha+\beta)(\alpha+1)^{\alpha+1}$.
-\item[5.] $y\mapsto \Phi^\sigma(x_\sigma,y)$ has a maximum at $y_\sigma\in \overline{\Omega}_\delta$, thus by supersolution test for \eqref{e:PDE_delta} we have 
-\begin{equation}\label{e:super1}
-    \lambda u_\delta(y_\sigma) + \left|\frac{2C_0(x_\sigma-y_\sigma)}{\sigma}\right|^p - f(y_\sigma) \geq 0.
-\end{equation}
-\item[6.] Recall that $|D d(x_\sigma)| = 1$, from \eqref{e:sub1}, \eqref{e:super1}, $d(x_\sigma)\geq \sigma$ and $|x_\sigma-y_\sigma|\leq \sigma$ we have
-\begin{align}
-    &\lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) \leq |\xi_\sigma|^p - |\xi_\sigma+\zeta_\sigma|^p + f(y_\sigma) - f(x_\sigma) \nonumber\\
-    &\qquad\qquad\qquad\quad + \varepsilon\left(\frac{2n}{\sigma} + \frac{C_\varepsilon(\alpha+\beta)(\alpha+\beta+1)}{d(x_\sigma)^{\alpha+\beta+2}} - \frac{C_\varepsilon(\alpha+\beta)\Delta d(x_\sigma)}{d(x_\sigma)^{\alpha+\beta +1}}\right)\nonumber \\
-    &\qquad\qquad\qquad\quad\leq |\xi_\sigma|^p - |\xi_\sigma+\zeta_\sigma|^p + C_f\sigma +\varepsilon \left(\frac{2n}{\sigma} + \frac{(\alpha+\beta+1)|\zeta_\sigma|}{\sigma} + K_1|\zeta_\sigma|\right) \label{e:est3}
-\end{align}
-where $K_2 = \max_{x\in \overline{\Omega}}\Delta d(x)$. Using the estimate
-\begin{align*}
-    \left||x+y|^p - |x|^p \right| \leq  p\big(|x|+|y|\big)^{p-1}|y|
-\end{align*}
-with $x = \xi_\sigma$, $y = \zeta_\sigma$ and the fact that $|\zeta_\sigma|\leq \mathfrak{C}_\alpha$ we obtain
-\begin{align}
-    \Big||\xi_\sigma+\zeta_\sigma|^p - |\xi|^p\Big| &\leq p\Big(|\xi_\sigma|+|\zeta_\sigma|\Big)^{p-1}|\zeta_\sigma| \leq K_3\varepsilon ^{\alpha+1  - \gamma(\alpha+1+\beta)}\label{e:est2}
-\end{align}
-where $K_3 = p\mathfrak{C}_\alpha(2C_0+\mathfrak{C}_\alpha)^{p-1}$. From \eqref{e:est3} and \eqref{e:est2} and $\sigma = \varepsilon^\gamma$ we deduce that
-\begin{align*}
-    \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) &\leq   K_3\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)}+ C_f\varepsilon^\gamma + 2n \varepsilon^{1-\gamma}\\
-    & + (\alpha+\beta + 1)\mathfrak{C}_\alpha \varepsilon^{\alpha+2 - \gamma(\alpha+2+\beta)} + K_1\mathfrak{C}_\alpha\varepsilon^{\alpha+2 - \gamma(\alpha+1+\beta)}.
-\end{align*}
-\item[7.] As $p\in (1,2)$, we have $\alpha\in (0,1)$, therefore we can always pick $\beta \in (0,\alpha)$ and $\gamma = \frac{1}{2}$ to deduce that 
-\begin{equation*}
-     \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) \leq K_4 \sqrt{\varepsilon}
-\end{equation*}
-where 
-\begin{equation*}
-    K_4 = \max\big\lbrace K_3,C_f,2n, (\alpha+\beta+1)\mathfrak{C}_\alpha, K_1\mathfrak{C}_\alpha \big\rbrace.   
-\end{equation*}
-\item[8.] We recall that $\delta = 2\sigma = \sqrt{\varepsilon}$. Using $\Phi^\sigma(x_\sigma,y_\sigma)\geq \Phi^\sigma(x,x)$ for all $x\in \overline{\Omega}_\delta$ we have
-\begin{equation*}
-    \lambda u^\varepsilon(x) - \lambda u_\delta(x) - \frac{C_\varepsilon}{d(x)^{\alpha+\beta}} \leq \Phi^\sigma(x_\sigma,y_\sigma) \leq \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) \leq K_4\sqrt{\varepsilon}.
-\end{equation*}
-Therefore, using the fact that $d(x)\geq \delta = 2\sqrt{\varepsilon}$ as $x\in \overline{\Omega}_\delta$ and $\alpha+1 - \frac{\alpha+\beta}{2} > 1$ we have
-\begin{align}
-    \lambda u^\varepsilon(x) - \lambda u_\delta(x) &\leq K_4\sqrt{\varepsilon} + \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}\nonumber \\
-    &\leq K_4\sqrt{\varepsilon} + \frac{(\alpha+1)^{\alpha+1}}{2^{\alpha+\beta}\alpha}\varepsilon^{\alpha+1 - \frac{\alpha+\beta}{2}}\leq K_5 \sqrt{\varepsilon}\label{e:almost}
-\end{align}
-for all $x\in \overline{\Omega}_{2\sqrt{\varepsilon}}$ where
-\begin{equation*}
-    K_5 = \max\left\lbrace K_4, \frac{(\alpha+1)^{\alpha+1}}{2^{\alpha+\beta}\alpha}\right\rbrace.
-\end{equation*}
-\end{enumerate}
-From Theorem \ref{thm:conv_general} we have that
-\begin{equation}\label{e:citepaper}
-    0\leq \lambda u_\delta(x) - \lambda u^0(x)\leq C_H\delta \qquad\text{for all}\; x\in \overline{\Omega}_\delta
-\end{equation}
-where $C_H$ is independent of $\delta$. From \eqref{e:almost} and \eqref{e:citepaper} with $\delta = 2\sqrt{\varepsilon}$, we deduce that
-\begin{align*}
-    0 \leq \lambda u^\varepsilon(x) - \lambda u^0(x) \leq \left(K_5 + 2C_H\right)\sqrt{\varepsilon} \qquad\text{for all}\; x\in \overline{\Omega}_{2\sqrt{\varepsilon}}.
-\end{align*}
-Finally, we mention the case where \eqref{e:ass_delta0} does not hold, i.e., $d(x_\sigma)\geq \delta_0$ instead.
-All the steps carry out the same with some modifications.
-Instead of \eqref{e:est_xi_zeta} we have
-\begin{equation*}
-    |\zeta_\sigma| \leq K_2\mathfrak{C}_\alpha \delta_0^{-(\alpha+\beta+1)} \varepsilon^{\alpha+1}
-\end{equation*}
-and at this point $\sigma$ is still independent of $\varepsilon$. 
-\end{proof}
+where we choose $\delta = \varepsilon^{\frac{\alpha}{\alpha+1}}$. Since $\Phi(x,x) \leq \Phi(x_\sigma,y_\sigma)$ for all $x\in \Omega$, we obtain from \eqref{e:final1} and \eqref{e:final2} that
+\begin{equation*}
+    u^\varepsilon(x)-u(x)-\left(1+\varepsilon^{\frac{\alpha^2}{\alpha+1}}\right)\frac{\nu C_\alpha  \varepsilon^{\alpha+1}}{d(x)^\alpha} \leq C\sqrt{\varepsilon}.
+\end{equation*}
+Therefore,
+\begin{equation}
+   -C \sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x) \leq C\sqrt{\varepsilon} + \left(1+\varepsilon^{\frac{\alpha^2}{\alpha+1}}\right)\frac{\nu C_\alpha  \varepsilon^{\alpha+1}}{d(x)^\alpha} 
+\end{equation}
+for every $x\in \Omega$. The final conclusions follow.
+\end{proof}
+
+\subsection{General bounded data}
+
+We start with the following Lemma, which will be used later.
+\begin{lem} Let $0<\kappa < \delta_0$ and $U_\kappa = \big\{x\in \Omega: 0<\mathrm{dist}(x,\partial\Omega) < \kappa\big\} = \Omega\backslash \overline{\Omega}_\kappa$. There holds
+\begin{equation*}
+    \mathrm{dist}(x,\partial\Omega_\kappa) = \kappa - \mathrm{dist}(x,\partial\Omega) \qquad\text{for all}\;x\in U_\kappa.
+\end{equation*}
+\end{lem}
+
+\begin{proof} By definition of $\delta_0$ we have $d(x) = \mathrm{dist}(x,\partial\Omega)$ is twice continuously differentiable in the region $U_{\delta_0} = \Omega\backslash \overline{\Omega}_{\delta_0}$.
+The proof follows from \textcolor{blue}{\cite{} fill in Trudinger}.
+\end{proof}
+
+\begin{lem} Let $u^\varepsilon\in \mathrm{C}^2(U_\kappa)$ be the unique solution to 
+\begin{equation*}
+    \left\{
+        \begin{aligned}
+            \tilde{u}^\varepsilon(x) + |D\tilde{u}^\varepsilon(x)|^p-\varepsilon \Delta \tilde{u}^\varepsilon(x) &=0 \;\qquad \text{in } U_\kappa ,\\
+            \tilde{u}^\varepsilon(x) &= +\infty \quad \text{on } \partial U_\kappa = \partial \Omega\cup \partial \Omega_{\kappa},
+        \end{aligned}
+    \right.
+\end{equation*}
+and $u \equiv 0 $ be the unique solution to 
+\begin{equation*}
+    \left\{
+        \begin{aligned}
+            u(x)+ |Du(x)|^p &=0 \quad \text{in } U_\kappa ,\\
+            u(x)+ |Du(x)|^p &\geq 0 \quad \text{on } \partial U_\kappa = \partial \Omega \cup\partial \Omega_{\kappa}.
+        \end{aligned}
+    \right.
+\end{equation*}
+Then there exists a constant $C$ independent of $\varepsilon$ such that
+\begin{equation*}
+  |u^\varepsilon(x) - u(x)| \leq C\varepsilon \quad  \text{for} \quad x\in \Omega_{\varepsilon}
+\end{equation*}
+where $C$ is independent of $\kappa$.
+\end{lem}
+\begin{rem} Unlike Theorem \ref{thm:rate_doubling0} where we made use of Lemma \ref{lem:super_refined}, the constant in the rate of convergence blows up as $\delta_{0,U_\kappa} \to 0$.
+\end{rem}
+%\nocite{*}
+
+\clearpage
 
 \section{Rate of convergence via nonlinear adjoint method}
-
-%\nocite{*}
 
@@
 \begin{equation*}
-    -\varepsilon \Delta w + p|D u|^{p-2}D u \cdot D w + 2\lambda w - D f\cdot D u + \varepsilon |D^2u|^2 = 0 \qquad\text{in}\;\Omega.
+    -\varepsilon \Delta w + p|D u|^{p-2}D u \cdot D w + 2  w - D f\cdot D u + \varepsilon |D^2u|^2 = 0 \qquad\text{in}\;\Omega.
 \end{equation*}
@@
 \begin{align*}
-    &-\varepsilon \Delta (\varphi w) + p|D u|^{p-2}D u \cdot D (\varphi w) + 2\lambda (\varphi w) + \varepsilon \varphi|D^2u|^2 + 2\varepsilon \frac{D \varphi}{\varphi}\cdot D (\varphi w) \\
+    &-\varepsilon \Delta (\varphi w) + p|D u|^{p-2}D u \cdot D (\varphi w) + 2  (\varphi w) + \varepsilon \varphi|D^2u|^2 + 2\varepsilon \frac{D \varphi}{\varphi}\cdot D (\varphi w) \\
     &\qquad\qquad\qquad\qquad = \varphi(D f\cdot D u) + p|D u|^{p-2}(D u\cdot D \varphi)w -\varepsilon w \Delta \varphi + 2\varepsilon \frac{|D \varphi|^2}{\varphi}w
@@
 \begin{equation}\label{e:est_for_D^2u_2}
-    \varepsilon |D^2u|^2 \geq \frac{(\varepsilon \Delta u)^2}{n\varepsilon} \geq (\varepsilon \Delta u)^2 = \left(\lambda u + |Du|^p - f\right)^2 \geq |Du|^{2p} - 2C_0|Du|^p \geq \frac{|Du|^{2p}}{2} - 2K_0.
+    \varepsilon |D^2u|^2 \geq \frac{(\varepsilon \Delta u)^2}{n\varepsilon} \geq (\varepsilon \Delta u)^2 = \left(  u + |Du|^p - f\right)^2 \geq |Du|^{2p} - 2C_0|Du|^p \geq \frac{|Du|^{2p}}{2} - 2K_0.
 \end{equation}
@@
 \begin{align*}
-    \lambda u(x) &\approx C_\varepsilon d(x)^{-\alpha},\\
+      u(x) &\approx C_\varepsilon d(x)^{-\alpha},\\
     \frac{\partial u}{\partial x_i}(x) &\approx -\alpha C_\varepsilon d(x)^{-(\alpha+1)} \frac{\partial d}{\partial x_i}(x) \qquad\qquad\qquad \Longrightarrow\qquad |Du (x)|^p \approx \alpha^p C_\varepsilon^p d(x)^{-p(\alpha+1)}|D d(x)|^p,\\
@@
 \end{equation*}
-Setting them to zero, we deduce that
+Setting them to zero, as $\alpha+1 = \frac{1}{p-1}$ we deduce that 
 \begin{equation}\label{e:relation}
@@
 \end{equation}
-We note that $\alpha+1 = \frac{1}{p-1}$ for convenience later. Recall that $K_1 = \max_{\overline{\Omega}}|\Delta d(x)|$, let us denote
+Recall that $K_1 = \max_{\overline{\Omega}}|\Delta d(x)|$, let us denote
 \begin{equation*}
@@
 
-\begin{lem}\label{lem:subsln} For each $<\delta < \frac{1}{2}\delta_0$, if $\eta\geq G\varepsilon^{\alpha+1}$, we have
-\begin{equation*}
-    \overline{w}_{\eta,\delta}(x) = \frac{C_\varepsilon+\eta}{(d(x)-\delta)^\alpha} +\frac{M_\varepsilon}{\lambda},\qquad x\in \Omega_\delta, 
+\begin{lem}\label{lem:subsln} For each $\delta > 0$ such that $0<2\delta < \delta_0$, if $\eta\geq G\varepsilon^{\alpha+1}$ then
+\begin{equation*}
+    \overline{w}_{\eta,\delta}(x) = \frac{C_\varepsilon+\eta}{(d(x)-\delta)^\alpha} +\frac{M_\varepsilon}{ },\qquad x\in \Omega_\delta, 
 \end{equation*}
@@
 \begin{align*}
-    \mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) = \frac{\lambda(C_\varepsilon + \eta)}{(d(x)-\delta)^\alpha} &+ M_\varepsilon + \frac{(C_\varepsilon+\eta)^p \alpha^p}{(d(x)-\delta)^{\alpha+2}}|D d(x)|^p - f(x) \\
+    \mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) = \frac{ (C_\varepsilon + \eta)}{(d(x)-\delta)^\alpha} &+ M_\varepsilon + \frac{(C_\varepsilon+\eta)^p \alpha^p}{(d(x)-\delta)^{\alpha+2}}|D d(x)|^p - f(x) \\
     &- \frac{\varepsilon(C_\varepsilon+\eta)\alpha(\alpha+1)}{(d(x)-\delta)^{\alpha+2}}|D d(x)|^2 + \frac{\varepsilon(C_\varepsilon+\eta)\alpha}{(d(x)-\delta)^{\alpha+1}}\Delta d(x).
@@
     \begin{align*}
-        \mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) = \frac{\lambda(C_\varepsilon + \eta)}{(d(x)-\delta)^\alpha} + M_\varepsilon &+ \frac{\alpha^pC_\varepsilon^p}{(d(x)-\delta)^{\alpha+2}}\left(\nu^{p}|Dd(x)|^p - \nu|Dd(x)|^2\right)\\
+        \mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) = \frac{ (C_\varepsilon + \eta)}{(d(x)-\delta)^\alpha} + M_\varepsilon &+ \frac{\alpha^pC_\varepsilon^p}{(d(x)-\delta)^{\alpha+2}}\left(\nu^{p}|Dd(x)|^p - \nu|Dd(x)|^2\right)\\
         &+\frac{\nu\varepsilon \alpha C_\varepsilon}{(d(x)-\delta)^{\alpha+1}}\Delta d(x) - f(x).
@@
     \begin{align*}
-         \mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) &= \frac{\lambda(C_\varepsilon + \eta)}{(d(x)-\delta)^\alpha} + M - f(x)\\
+         \mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) &= \frac{ (C_\varepsilon + \eta)}{(d(x)-\delta)^\alpha} + M - f(x)\\
          & + \frac{\alpha^p C_\varepsilon^p\nu }{(d(x)-\delta)^{\alpha+2}}\left(\nu^{p-1} - 1 - \frac{ (d(x)-\delta)\Delta d(x)}{(\alpha+1)}\right).
@@
     \begin{equation*}
-        \left|\frac{(d(x)-\delta)\Delta  d(x)}{(\alpha+1)}\right| \leq \frac{_1\delta_0}{\alpha+1}.
+        \left|\frac{(d(x)-\delta)\Delta  d(x)}{(\alpha+1)}\right| \leq {K_1\delta_0}{\alpha+1}.
     \end{equation*}
@@
 \begin{equation*}
-    \underline{w}_{\eta, \delta}(x) = \frac{C_\varepsilon-\eta}{(d(x)+\delta)^\alpha} -\frac{M_\varepsilon}{\lambda}, \qquad x\in \Omega^\delta 
+    \underline{w}_{\eta, \delta}(x) = \frac{C_\varepsilon-\eta}{(d(x)+\delta)^\alpha} -\frac{M_\varepsilon}{ }, \qquad x\in \Omega^\delta 
 \end{equation*}
@@
     \begin{equation*}
-        F[w_{\eta,\delta}](x) =  \lambda w_{\eta,\delta}(x) + H(x,Dw_{\eta,\delta}(x)).
+        F[w_{\eta,\delta}](x) =    w_{\eta,\delta}(x) + H(x,Dw_{\eta,\delta}(x)).
     \end{equation*}
@@
     \begin{equation*}
-        F(x) = \lambda u(x) + H(x,Du(x)).
+        F(x) =   u(x) + H(x,Du(x)).
     \end{equation*}
@@
 \begin{equation*}
-    w_\theta = \theta \overline{u} + (1-\theta)\lambda^{-1}\left(\inf_{\Omega} f\right).
+    w_\theta = \theta \overline{u} + (1-\theta) ^{-1}\left(\inf_{\Omega} f\right).
 \end{equation*}
@@
 \begin{equation*}
-    w_\theta = \theta \overline{u} + (1-\theta)\lambda^{-1}\left(\inf_{\Omega} f\right) \leq \underline{u} \qquad\text{in}\;\Omega.
+    w_\theta = \theta \overline{u} + (1-\theta) ^{-1}\left(\inf_{\Omega} f\right) \leq \underline{u} \qquad\text{in}\;\Omega.
 \end{equation*}
@@
 \begin{equation*}
-    1\leq \frac{\overline{u}(x)}{\underline{u}(x)} \leq \frac{\overline{w}_{\eta,0}(x)}{\underline{w}_{\eta,0}(x)} = \frac{(C_0+\eta)+\lambda^{-1}C_\eta d(x)^\alpha}{(C_0-\eta)-\lambda^{-1}C_\eta d(x)^\alpha} \qquad\text{for}\;x\in \Omega
+    1\leq \frac{\overline{u}(x)}{\underline{u}(x)} \leq \frac{\overline{w}_{\eta,0}(x)}{\underline{w}_{\eta,0}(x)} = \frac{(C_0+\eta)+ ^{-1}C_\eta d(x)^\alpha}{(C_0-\eta)- ^{-1}C_\eta d(x)^\alpha} \qquad\text{for}\;x\in \Omega
 \end{equation*}
@@
 \begin{equation*}
-\frac{\overline{u}(x)}{\underline{u}(x)}\leq (1+\varsigma)     \qquad\Longrightarrow\qquad \frac{1}{1+\varsigma} \overline{u}(x) \leq \underline{u}(x) \qquad\text{in}\; \Omega\backslash \Omega_\delta
-\end{equation*}
-For given $\theta\in (0,1)$, we can always choose $\varsigma$ small enough such that $(1+\varsigma)^{-1} > \theta$ which renders $\underline{u}(x) \geq \theta \overline{u}(x) + (1-\theta)\lambda^{-1}\left(\inf_\Omega f\right)$ for $0< d(x) < \delta' < \delta$.
+\frac{\overline{u}(x)}{\underline{u}(x)}\leq (1+\varsigma)     \qquad\Longrightarrow\qquad \left(\frac{1}{1+\varsigma}\right)\overline{u}(x) \leq \underline{u}(x) \qquad\text{in}\; \Omega\backslash \Omega_\delta
+\end{equation*}
+For given $\theta\in (0,1)$, we can always choose $\varsigma$ small enough such that $(1+\varsigma)^{-1} > \theta$ which renders $\underline{u}(x) \geq \theta \overline{u}(x) + (1-\theta) ^{-1}\left(\inf_\Omega f\right)$ for $0< d(x) < \delta' < \delta$.
 \end{proof}
@@
 \begin{equation}\label{eq:max_a1}
-    \lambda \varphi(x_0) + H(x_0,D\varphi(x_0)) < 0.
+      \varphi(x_0) + H(x_0,D\varphi(x_0)) < 0.
 \end{equation}
@@
 \begin{equation}\label{eq:max_a2}
-    \lambda \varphi^\varepsilon(x)+H(x,D\varphi^\varepsilon(x)) < 0 \qquad\text{for}\;x\in B(x_0,\delta)\cap \overline{\Omega}.
+      \varphi^\varepsilon(x)+H(x,D\varphi^\varepsilon(x)) < 0 \qquad\text{for}\;x\in B(x_0,\delta)\cap \overline{\Omega}.
 \end{equation}
@@
 Let $A:X \to X$ be continuous and compact.
-Assume the set $\{u\in X : u=\lambda A[u]$ for some $0 \leq  \lambda \leq 1\}$ is bounded.
+Assume the set $\{u\in X : u=  A[u]$ for some $0 \leq    \leq 1\}$ is bounded.
 Then $A$ has a fixed point $u =A[u]$.
@@
 
-\noindent Next we try to bound $\{u\in X : u=\lambda A[u]$ for some $0 \leq  \lambda \leq 1\}$. If $u=\lambda A[u]$, the PDE becomes
+\noindent Next we try to bound $\{u\in X : u=  A[u]$ for some $0 \leq    \leq 1\}$. If $u=  A[u]$, the PDE becomes
 
@@
   \begin{aligned}
-   \epsilon \Delta u &= \lambda H(x, Du) \quad \, \text{in } U, \\
+   \epsilon \Delta u &=   H(x, Du) \quad \, \text{in } U, \\
               u &= 0 \qquad \qquad \text{on } \partial U.
@@
 \end{equation}
-Choose $p=2n$ and $\displaystyle \alpha =\frac{1}{2}$. We have $\{\Tilde{u}\in X : \Tilde{u}=\lambda A[\Tilde{u}]$ for some $0 \leq  \lambda \leq 1\}$ is bounded in $X= C^{1, \frac{1}{2}}(
+Choose $p=2n$ and $\displaystyle \alpha =\frac{1}{2}$. We have $\{\Tilde{u}\in X : \Tilde{u}=  A[\Tilde{u}]$ for some $0 \leq    \leq 1\}$ is bounded in $X= C^{1, \frac{1}{2}}(
 \overline{U})$.

### 2021-04-06 Drafts and notes/Notes/Notes.tex
Major change

--- 2021-01-27 Drafts and notes/Draft.tex
@@
 \title[Rate of convergence]
-{\textsc{Second-order state-constraint Hamilton-Jacobi equations}}
+{\textsc{Notes on the project}}
 \thanks{The authors are supported in part by NSF grant DMS-1664424.}
-\begin{abstract}
-We investigate qualitatively the convergence of large, or state-constraint solution to nonlinear elliptic equation as the viscosity vanish.
-\end{abstract}
+%\begin{abstract}
+%We investigate qualitatively the convergence of large, or state-constraint solution to nonlinear elliptic equation as the viscosity vanish.
+%\end{abstract}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \setcounter{tocdepth}{1}
-\tableofcontents
+%\tableofcontents
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}\label{sec:intro}
-\subsection{Motivation} Let $\Omega$ be an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$.
-Let us consider the following Hamiltonian $ H(x,\varrho) = |\varrho|^p-f(x)$ for $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$, $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
-Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ (see \cite{Lasry1989}) be the solution to
-\begin{equation}\label{eq:PDEeps}
-    \begin{cases}
-    \lambda u^\varepsilon(x) + H(x,Du^\varepsilon(x)) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
-    \text{in}\;\Omega, \vspace{0cm}\\
-    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^\varepsilon(x) = +\infty.
-    \end{cases} \tag{PDE$_\varepsilon$}
+
+\section{Doubling variable - Attempt No. 28}
+\noindent (February 14, 2021) \\
+We invoke the following weird stuff, say (good news, it is proved in \cite{alessio_asymptotic_2006})
+\begin{equation*}
+ u^\varepsilon(x) \approx \frac{C_\varepsilon}{d(x)^\alpha} \qquad\text{as}\; x\to \partial\Omega\qquad \Longrightarrow\qquad Du^\varepsilon(x) \approx \frac{C_\varepsilon \alpha \nabla d(x)}{d(x)^{\alpha+1}} \qquad\text{as}\; x\to \partial\Omega.
+\end{equation*}
+Let us still use $\Omega = B(0,1)$, and also assume that $p\in \left(\frac{3}{2},2\right)$ so that $\alpha = \frac{2-p}{p-1} \in (0,1)$. We define
+\begin{equation*}
+    \Phi(x,y) = u^\varepsilon(x) - u_\delta(y) - \frac{C_\varepsilon |x-y|^2}{\sigma} - \frac{C_\varepsilon}{d(x)^{\alpha+1}}, \qquad (x,y)\in \overline{\Omega}\times \overline{\Omega}_\delta.
+\end{equation*}
+Let us start with $\Phi(x_\sigma,y_\sigma)\geq \Phi(0,y_\sigma)$, we have
+\begin{align*}
+    u^\varepsilon(x_\sigma) - u_\delta(y_\sigma) - \frac{C_\varepsilon |x_\sigma-y_\sigma|^2}{\sigma} - \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+1}} \geq u^\varepsilon(0) - u_\delta(y_\sigma) - \frac{C_\varepsilon |y_\sigma|^2}{\sigma} - C_\varepsilon.
+\end{align*}
+Therefore
+\begin{align*}
+    \frac{C_\varepsilon |x_\sigma-y_\sigma|^2}{\sigma} + \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+1}} &\leq C_\varepsilon + u^\varepsilon(x_\sigma) - u^\varepsilon(0) + \frac{C_\varepsilon }{\sigma}\\
+    &\leq C_\varepsilon + \frac{C_\varepsilon}{\sigma} + \frac{C_\varepsilon \alpha|x_\sigma|}{d(x_\sigma)^{\alpha+1}}.
+\end{align*}
+As a consequence, since $\alpha \in (0,1)$ we have
+\begin{equation*}
+    \frac{C_\varepsilon |x_\sigma-y_\sigma|^2}{\sigma} + \frac{C_\varepsilon(1-\alpha)}{d(x_\sigma)^{\alpha+1}} 
+    \leq C_\varepsilon + \frac{C_\varepsilon}{\sigma}.
+\end{equation*}
+Therefore
+\begin{equation*}
+    \frac{|x_\sigma - y_\sigma|^2}{\sigma} + \frac{(1-\alpha)}{d(x_\sigma)^{\alpha+1}} \leq 1 + \frac{1}{\sigma}.
+\end{equation*}
+Thus
+\begin{equation*}
+    \frac{\sigma(1-\alpha)}{d(x_\sigma)^{\alpha+1}} \leq \sigma+1
+\end{equation*}
+Therefore
+\begin{equation*}
+    d(x_\sigma)\geq \left(\left(\frac{1-\alpha}{1+\sigma}\right)\sigma\right)^{\frac{1}{\alpha+1}} 
+\end{equation*}
+Say let us try with $p = \frac{5}{3}$ so that $\alpha = \frac{1}{2}$, we have
+\begin{equation*}
+    d(x_\sigma) \geq \left(\frac{\sigma}{4}\right)^\frac{2}{3}.
+\end{equation*}
+Let $\sigma = 4\delta^\frac{3}{2}$ then $d(x_\sigma)\geq \delta$, therefore $\Phi(x_\sigma,y_\sigma)\geq \Phi(x_\sigma,x_\sigma)$, thus
+\begin{equation*}
+      u^\varepsilon(x_\sigma) - u_\delta(y_\sigma) - \frac{C_\varepsilon |x_\sigma-y_\sigma|^2}{\sigma} - \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+1}} \geq u^\varepsilon(x_\sigma) - u_\delta(x_\sigma) - \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+1}}
+\end{equation*}
+Therefore
+\begin{equation}\label{e:bdd_xi}
+    \frac{C_\varepsilon|x_\sigma - y_\sigma|^2}{\sigma} \leq u_\delta(x_\sigma) - u_\delta(y_\sigma)\leq C_0|x_\sigma - y_\sigma|
 \end{equation}
-When $1<p\leq 2$, equation \eqref{eq:PDEeps} describes the (expectation) value function associated with a minimization of a stochastic optimal control problem with state-constraint.
-We are interested in studying the asymptotic behavior of $\{u^\varepsilon\}_{\varepsilon>0}$ as $\varepsilon\rightarrow 0$.
-Heuristically, the state-constraint second-order problem converges to the state-constraint first-order, which is associated with deterministic optimal control, which is described in the framework of viscosity solution as follows:
-\begin{equation}\label{eq:PDE0}
-    \begin{cases}
-     \lambda u(x) + H(x,Du(x)) \leq 0\;\qquad\text{in}\;\Omega,\\
-     \lambda u(x) + H(x,Du(x)) \geq 0\;\qquad\text{on}\;\overline{\Omega}.
-    \end{cases} \tag{PDE$_0$}
+Therefore
+\begin{equation*}
+    |x_\sigma - y_\sigma|\leq \left(\frac{C_0\alpha}{(\alpha+1)^{\alpha+1}}\right)\frac{\sigma}{\varepsilon^{\alpha+1}}.
+\end{equation*}
+Let $\sigma = \varepsilon^{(\alpha+1)(1+\beta)}$ for some $\beta > 0$. Then
+\begin{equation*}
+    |x_\sigma - y_\sigma|\leq \left(\frac{C_0\alpha}{(\alpha+1)^{\alpha+1}}\right)\varepsilon^{\beta(1+\alpha)} \qquad\text{and}\qquad d(x_\sigma)\geq \left(\frac{1-\alpha}{1+\sigma}\right)\varepsilon^{\beta}.
+\end{equation*}
+For simplicity, let us denote
+\begin{equation*}
+    K_4 = \left(\frac{C_0\alpha}{(\alpha+1)^{\alpha+1}}\right) \qquad\text{then}\qquad |x_\sigma-y_\sigma|\leq K_4\varepsilon^{\beta(1+\alpha)}.
+\end{equation*}
+Now $x\mapsto \Phi(x,y_\sigma)$ has a maximum at $x_\sigma\in \Omega$, i.e.,
+    \begin{equation*}
+        u^\varepsilon(x) - \left(\frac{C_\varepsilon|x-y_\sigma|^2}{\sigma} + \frac{C_\varepsilon}{d(x)^{\alpha+1}}\right)
+    \end{equation*}
+    has a maximum at $x_\sigma\in \Omega$. By subsolution test we have
+\begin{align}\label{e:sub1}
+    &\lambda u^\varepsilon(x_\sigma) + \left|\xi_\sigma+\zeta_\sigma\right|^p - f(x_\sigma)\nonumber\\
+    &\quad  -\varepsilon\left(\frac{2nC_\varepsilon}{\sigma} + \frac{C_\varepsilon(\alpha+1)(\alpha+2)|D d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+3}}-\frac{C_\varepsilon(\alpha+1)}{d(x_\sigma)^{\alpha+2}}\Delta d(x_\sigma)\right)  \leq 0
+\end{align}
+where 
+\begin{equation}\label{e:est_xi_zeta}
+    \xi_\sigma = \frac{2C_\varepsilon\big(x_\sigma-y_\sigma\big)}{\sigma} \qquad\text{and}\qquad \zeta_\sigma = - \frac{C_\varepsilon(\alpha+1)}{d(x_\sigma)^{\alpha+2}}D d(x_\sigma).
 \end{equation}
-Equation \eqref{eq:PDE0} admits a unique viscosity solution in the space $\rmC(\overline{\Omega})$, which is also the maximal viscosity subsolution among all viscosity subsolution $v\in\rmC(\overline{\Omega})$.
-The problem is interesting since in the limit we no longer have blowing up behavior.
-In this paper, we are interested in the rate of convergence of $u^\varepsilon \to u$ as $\varepsilon\to 0$.
-A boundary layer is expected to describe the behavior of convergence near the boundary.
-\subsection{Assumptions} We will always assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary in $\mathbb{R}^n$ and $H:\mathbb{R}^n\times \mathbb{R}^n$ is a continuous Hamiltonian.
-\begin{itemize}
-    \item[$\mathrm{(A1)}$] $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
-\end{itemize}
-We list the assumptions on a general Hamiltonian as follow.
-\begin{itemize}
-    \item[$\mathrm{(H1)}$] There exists $C_1 > 0$ such that $H(x,p) \geq -C_1$ for all $(x,p)\in \overline{\Omega}\times\mathbb{R}^n$.
-    \item[$\mathrm{(H2)}$] There exists $C_2>0$ such that $|H(x,0)|\,\leq \,C_2$ for all $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$.
-    \item[$\mathrm{(H3)}$] For each $R>0$ there exists a modulus $\omega_{R}[0,\infty)\to [0,\infty)$ such that $\omega_R(0^+) = 0$ and 
+We have the following estimates
+\begin{align*}
+    |\zeta_\sigma|=\left|\frac{C_\varepsilon(\alpha+1)}{d(x_\sigma)^{\alpha+2}}D d(x_\sigma )\right|
+    &\leq \frac{C_\varepsilon(\alpha+1)}{\sigma^{\alpha+2}} = \frac{(\alpha+1)^{\alpha+2}}{\alpha}\left(\frac{1+\sigma}{1-\alpha}\right)^{\alpha+2}\left(\frac{\varepsilon^{\alpha+1}}{\varepsilon^{\beta(\alpha+2)}}\right).
+\end{align*}
+We need to choose $\beta$ such that
 \begin{equation*}
-        \begin{cases}
-        |H(x,p) - H(y,p)| \leq \omega_R(|x-y|),\\
-        |H(x,p) - H(x,q)| \leq \omega_R(|p-q|),
-        \end{cases} \qquad\text{for all}\;x,y\in \overline{\Omega}, p,q \in \mathbb{R}^n\;\text{with}\;|p|,|q|\leq R.
+ \displaystyle 0 < \beta < \frac{\alpha+1}{\alpha+2}.
 \end{equation*}
-    \item[$\mathrm{(H4)}$] $H(x,p)\rightarrow \infty$ as $|p|\to \infty$ uniformly in $x\in \overline{\Omega}$.
-\end{itemize}
-
-\section{Preliminaries}\label{sec:prelim}
-\subsection{Gradient estimate}
-
-\subsection{Well-posedness of large solution for subquaratic case}
-
-In this section, with the specific form of the Hamiltonian $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$, we show the existence and uniqueness of solutions to \eqref{eq:PDEeps}.
-We note that the assumption of $f$ can be relaxed to $f\in L^\infty(\Omega)$ only, but for the clarity of the proof we will assume $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
-
-\begin{thm} If $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ then there exists a unique solution $u\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps}.
-\end{thm}
-
-\begin{proof} For $\delta>0$, let us define $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) < \delta\}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$.
-\begin{figure}[ht]
-    \centering
-    %\incfig{Domains}
-    \def\svgwidth{0.47\columnwidth}
-    \import{./figs/}{Domains.pdf_tex}
-    \caption{The domain $\Omega$ variations $\Omega_\delta, \Omega^\delta$.}
-    \label{fig:Domains}
-\end{figure}
-We consider $\delta$ small enough so that the distance function $x\mapsto \mathrm{dist}(x,\partial \Omega)$ is $\mathrm{C}^2$ in the strip $\Omega^\delta\backslash \overline{\Omega}_\delta$, we recall that $|D d(x)| = 1$ in that region.
-We extend the signed distance function into a $\mathrm{C}^2(\mathbb{R}^n)$ function, denoted by $d(x)$ such that
+In particular, we have
 \begin{equation*}
-    \begin{cases}
-    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_\delta,\\
-    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^\delta\backslash \Omega.
-    \end{cases}
+    |\zeta_\sigma|\leq \mathfrak{C}_\alpha \qquad\text{where}\qquad \mathfrak{C}_\alpha =  \frac{(\alpha+1)^{\alpha+2}}{\alpha}\left(\frac{1+\sigma}{1-\alpha}\right)^{\alpha+2}.
 \end{equation*}
-We can choose $d(\cdot)$ so that $\Omega_\delta = \{x\in \mathbb{R}^n: d(x)-\delta >0 \}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: d(x) +\delta>0\}$.
-
-\noindent To find candidate for subsolution and supersolution to \eqref{eq:PDEeps}, we use the ansatz
-\begin{equation}\label{eq:ansatz}
-    u(x) = C_0 d(x)^{-\alpha}, \qquad x\in \Omega
+On the other hand, from \eqref{e:bdd_xi} we have
+\begin{equation*}
+    |\xi_\sigma| = \frac{2C_\varepsilon|x_\sigma - y_\sigma|}{\sigma} \leq C_0 .
+\end{equation*}
+Now $y\mapsto \Phi^\sigma(x_\sigma,y)$ has a maximum at $y_\sigma\in \overline{\Omega}_\delta$, thus by supersolution test we have 
+\begin{equation}\label{e:super1}
+    \lambda u_\delta(y_\sigma) + \left|\xi_\sigma\right|^p - f(y_\sigma) \geq 0.
 \end{equation}
-as we expect it blows up near the boundary like some thing proportionate to inverse of the distance function, due to the structure of $H(x,\varrho) = |\varrho|^p - f(x)$.
-Let us plug \eqref{eq:ansatz} into \eqref{eq:PDEeps} we obtain that the highest order terms are
-\begin{equation*}
-        -C_0 \alpha(\alpha+1)d^{-(\alpha+2)} + C_0^p \alpha^p d^{-(\alpha+1)p}.
-\end{equation*}
-Setting them to zero, we deduce that
-\begin{equation*}
-    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_0 = \frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}.
-\end{equation*}
-We can obtain the following families of supersolution on $\Omega_\delta$ and subsolution on $\Omega^\delta$ as follow.
-\begin{equation*}
-        \overline{w}_{\eta,\delta}(x) = \frac{C_0+\eta}{(d(x)-\delta)^\alpha} +\frac{C_\eta}{\lambda} \quad\text{for}\;x\in \Omega_\delta \qquad\text{and}\qquad \underline{w}_{\eta,\delta}(x) = \frac{C_0-\eta}{(d(x)+\delta)^\alpha} -\frac{C_\eta}{\lambda} \quad\text{for}\;x\in \Omega^\delta.
-\end{equation*}
-We divide the rest of the proof into 3 steps.
-We first construct a minimal solution, then a maximal solution to \eqref{eq:PDEeps}, and finally show that they are equal to conclude the existence and uniqueness of solution to \eqref{eq:PDEeps}.
-
-\begin{prop}\label{pro:minimalsol} There exists a minimal solution $\underline{u}\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that $v\geq \underline{u}$ for any other solution $v\in \mathrm{C}^2(\Omega)$ solving \eqref{eq:PDEeps}.
-\end{prop}
-\begin{proof} Let $w_{\eta,\delta}\in \mathrm{C}^2(\Omega)$ solves
-    \begin{equation}\label{e:w_def}
-    \begin{cases}
-        \mathcal{L}\left[w_{\eta,\delta}\right] = 0 &\qquad\text{in}\;\Omega,\\
-        \qquad w_{\eta,\delta} = \underline{w}_{\eta,\delta} &\qquad\text{on}\;\partial\Omega.
-    \end{cases}
-    \end{equation}
-    Fix $\eta>0$, as $\delta\to 0$ the value of $\underline{w}_{\eta,\delta}$ blows up on the boundary, therefore by comparison principle we have $\delta_1 \leq  \delta_2$ implies $w_{\eta,\delta_1}\leq  w_{\eta,\delta_2}$ on $\overline{\Omega}$.
-
-    \noindent Since $\underline{w}_{\eta,\delta'}$ is a subsolution in $\overline{\Omega}$ with finite boundary, we obtain that
-    \begin{equation}\label{e:cp_delta1}
-        0<\delta \leq \delta'\qquad\Longrightarrow\qquad \underline{w}_{\eta,\delta'} \leq w_{\eta_,\delta'}\leq w_{\eta,\delta} \qquad\text{on}\;\overline{\Omega}.
-    \end{equation}
-    For $\delta' > 0$, since $\overline{w}_{\eta,\delta}$ is a supersolution on $\Omega_{\delta'}$ with infinity value on the boundary $\partial\Omega_{\delta'}$, by comparison principle
-    \begin{equation}\label{e:cp_delta2}
-        w_{\eta,\delta} \leq \overline{w}_{\eta, \delta'} \qquad\text{in}\;\Omega_{\delta'} \qquad\Longrightarrow\qquad w_{\eta,\delta} \leq \overline{w}_{\eta,0} \qquad\text{in}\;\Omega.
-    \end{equation}
-    From \eqref{e:cp_delta1} and \eqref{e:cp_delta2} we have
-    \begin{equation}\label{e:cp_delta3}
-        0<\delta \leq \delta'\qquad\Longrightarrow\qquad \underline{w}_{\eta,\delta'} \leq w_{\eta_,\delta'}\leq w_{\eta,\delta} \leq \overline{w}_{\eta,0} \qquad\text{in}\;\Omega.
-    \end{equation}
-    Thus $\{w_{\eta,\delta}\}_{\delta>0}$ is locally bounded in $L^{\infty}_{\mathrm{loc}}(\Omega)$.
-Using the gradient estimate for $w_{\eta,\delta}$ solving \eqref{e:w_def} we deduce that $\{w_{\eta,\delta}\}_{\delta>0}$ is locally bounded in $W^{1,\infty}_{\mathrm{loc}}(\Omega)$.
-Plug it back into the defining equation \eqref{e:w_def} to bound the Laplacian and the second derivative terms, we deduce that $\{w_{\eta,\delta}\}_{\delta>0}$ is locally bounded in $W^{2,r}_{\mathrm{loc}}(\Omega)$ for all $r<\infty$.
-
-    \noindent Local boundedness of $\{u_{\eta,\delta}\}_{\delta>0}$ in $W^{2,r}_{\mathrm{loc}}(\Omega)$ implies weak$^*$ compactnes, that is there exists a function $u\in W^{2,r}(\Omega)$ such that (via subsequence and monotonicity)
-    \begin{equation*}
-    \begin{cases}
-        w_{\eta,\delta} \rup u \qquad\text{weakly in}\;W^{2,r}_{\mathrm{loc}}(\Omega),\vspace{0.2cm}\\
-        w_{\eta,\delta} \to u \qquad\text{strongly in}\;W^{1,r}_{\mathrm{loc}}(\Omega).
-    \end{cases}
-    \end{equation*}
-    In particular, $w_{\eta,\delta}\to u$ in $\mathrm{C}^1_{\mathrm{loc}}(\Omega)$ thanks to compact embedding.
-Let us rewrite the equation $\mathcal{L}\left[u_{\eta,\delta}\right] = 0$ as $\varepsilon\Delta w_{\eta,\delta}(x) = F[w_{\eta,\delta}](x)$ in $U$ for $U\subset\subset \Omega$ where
-    \begin{equation*}
-        F[w_{\eta,\delta}](x) =  \lambda w_{\eta,\delta}(x) + H(x,Dw_{\eta,\delta}(x)).
-    \end{equation*}
-    As $u_{\eta,\delta}\to u$ in $\mathrm{C}^1(U)$ as $\delta\to 0$, we have $F[w_{\eta,\delta}](x) \to F(x)$ uniformly in $U$ where 
-    \begin{equation*}
-        F(x) = \lambda u(x) + H(x,Du(x)).
-    \end{equation*}
-    In the limit we see that $u\in L^2$ is a weak solution of $\varepsilon\Delta u = F$ in $U$ where $F$ is continuous, thus $u\in \mathrm{C}^2(\Omega)$ as well and by stability we see that $u$ solves $\mathcal{L}[u] = 0$ in $\Omega$.
-From \eqref{e:cp_delta3} we also have
-    \begin{equation*}
-        \underline{w}_{\eta,0} \leq u \leq \overline{w}_{\eta,0} \qquad\text{in}\;\Omega.
-    \end{equation*}
-    It is clear that $u(x)\to \infty$ as $\mathrm{dist}(x,\partial\Omega)\to 0$ with the precise rate like \eqref{eq:ansatz}.
-We note that at this point, by construction, $u$ may depend on $\eta$.
-We show that $u$ is the maximal solution of $\mathcal{L}[u] = 0$ in $\Omega$ such that $u = +\infty$ on $\partial\Omega$, and thus consequently showing that $u$ is independent of $\eta$.
-
-    \noindent Let $v\in W^{2,r}(\Omega)$ for all $r<\infty$ solving \eqref{eq:PDEeps}.
-Fix $\delta>0$, then for all $\vartheta>0$ small we see that on $\partial\overline{\Omega}_\vartheta$ the value of $v$ blows up as $\vartheta\to 0$, while $w_{\eta,\delta}$ remains bounded (we fixed $\delta>0$).
-Comparison principle gives us that $v\geq w_{\eta,\delta}$ on $\Omega_{\vartheta}$, thus as $\vartheta\to 0$ we obtain $v\geq w_{\eta,\delta}$ on $\Omega$.
-Let $\delta\to 0$ we deduce that $v\geq u$ on $\Omega$.
-This concludes that $u$ is the minimal solution in $W^{2,r}(\Omega)(\forall\,r<\infty)$ and thus independent of $\eta>0$.
-\end{proof}
-
-\begin{prop} There exists a maximal solution $\overline{u}\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that $v\leq \overline{u}$ for any other solution $v\in \mathrm{C}^2(\Omega)$ solving \eqref{eq:PDEeps}.
-\end{prop}
-
-\begin{proof} For each $\delta>0$, let us denote $u_\delta\in \mathrm{C}^2(\Omega_\delta)$ be the minimal solution to $\mathcal{L}[u_\delta] = 0$ in $\Omega$ and $u_\delta = +\infty$ on $\partial\Omega_\delta$ according to Proposition \ref{pro:minimalsol}.
-By comparison principle, for every $\eta>0$ there holds
-\begin{equation*}
-    \underline{w}_{\eta,\delta} \leq u_\delta \leq \overline{w}_{\eta,\delta} \qquad\text{in}\;\Omega_\delta,
-\end{equation*}
-and
-\begin{equation*}
-    0<\delta<\delta' \qquad \Longrightarrow\qquad u_\delta \leq u_\delta' \qquad\text{in}\;\Omega_{\delta'}.
-\end{equation*}
-We have the local boundedness of $\{u_\delta\}_{\delta>0}$ in $W^{2,r}(\Omega)$ as well, thus together with monotonicity there exists $u\in W^{2,r}(\Omega)$ for all $r<\infty$ such that $u_\delta\to u$ strongly in $\rmC^1_{\mathrm{loc}}(\Omega)$, therefore using the equation $\mathcal{L}[u_\delta] = 0$ in $\Omega_\delta$ and the regularity of Laplace equation we deduce that $u\in \mathrm{C}^2(\Omega)$ solving \eqref{eq:PDEeps} and
-\begin{equation*}
-    \underline{w}_{\eta,0} \leq u\leq \overline{w}_{\eta,0} \qquad\text{in}\;\Omega
-\end{equation*}
-for all $\eta>0$.
-From the construction, as $u_\delta$ is independent of $\eta$, it is clear that $u$ is also independent of $\eta$.
-We now show that $u$ is the maximal solution of \eqref{eq:PDEeps}.
-Let $v\in\rmC^2(\Omega)$ solves \eqref{eq:PDEeps}, then clearly $v\leq u_\delta$ on $\Omega_\delta$ and therefore as $\delta \to 0$ we have $v\leq u$.
-\end{proof}
-\noindent In conclusion we have found a minimal solution $\underline{u}$ and a maximal solution $\overline{u}$ in $\rmC^2(\Omega)$ such that
-\begin{equation}\label{e:chain}
-    \underline{w}_{\eta,0} \leq \underline{u}\leq \overline{u}\leq \overline{w}_{\eta,0} \qquad\text{in}\;\Omega
-\end{equation}
-for any $\eta>0$. This extra parameter $\eta$ now enables us to show that $\overline{u} = \underline{u}$ in $\Omega$.
-
-\begin{prop}[Uniqueness] We have $\overline{u}\equiv \underline{u}$ in $\Omega$ and therefore solution to \eqref{eq:PDEeps} in $\mathrm{C}^2(\Omega)$ is unique.
-\end{prop}
-\begin{proof} Let $\theta\in (0,1)$, we cook up a subsolution by convex combination $w_\theta = \theta \overline{u} + (1-\theta)\lambda^{-1}\left(\inf_{\Omega} f\right)$, which if we can use comparison principle then
-\begin{equation*}
-    w_\theta = \theta \overline{u} + (1-\theta)\lambda^{-1}\left(\inf_{\Omega} f\right) \leq \underline{u} \qquad\text{in}\;\Omega.
-\end{equation*}
-If that is the case, let $\theta\to 1$ we conclude that $\overline{u} \leq \underline{u}$.
-There is a problem here, as they are both explosive solutions, to use comparison principle we need to show that $w_\theta \leq \underline{u}$ in a neighborhood of $\partial\Omega$.
-From \eqref{e:chain} we see that
-\begin{equation*}
-    1\leq \frac{\overline{u}(x)}{\underline{u}(x)} \leq \frac{\overline{w}_{\eta,0}(x)}{\underline{w}_{\eta,0}(x)} = \frac{(C_0+\eta)+\lambda^{-1}C_\eta d(x)^\alpha}{(C_0-\eta)-\lambda^{-1}C_\eta d(x)^\alpha} \qquad\text{for}\;x\in \Omega
-\end{equation*}
-and therefore
-\begin{equation*}
-   1\leq  \lim_{d(x)\to 0} \left(\frac{\overline{u}(x)}{\underline{u}(x)}\right) \leq \frac{C_0+\eta}{C_0-\eta} \qquad\Longrightarrow\qquad  \lim_{d(x)\to 0} \left(\frac{\overline{u}(x)}{\underline{u}(x)}\right) = 1
-\end{equation*}
-since $\eta>0$ is chosen arbitrary. This means for any $\varsigma\in(0,1)$ we can find $\delta(\varsigma)>0$ small such that on $\Omega\backslash \Omega_\delta$ one has
-\begin{equation*}
-\frac{\overline{u}(x)}{\underline{u}(x)}\leq (1+\varsigma)     \qquad\Longrightarrow\qquad \frac{1}{1+\varsigma} \overline{u}(x) \leq \underline{u}(x) \qquad\text{in}\; \Omega\backslash \Omega_\delta
-\end{equation*}
-For given $\theta\in (0,1)$, we can always choose $\varsigma$ small enough such that $(1+\varsigma)^{-1} > \theta$ which renders $\underline{u}(x) \geq \theta \overline{u}(x) + (1-\theta)\lambda^{-1}\left(\inf_\Omega f\right)$ for $0< d(x) < \delta' < \delta$.
-\end{proof}
-\noindent A final remark is that, we can also repeat the proof for $p=2$.
-\end{proof}
-\subsection{Convergence result} We show the convergence (qualitatively) of \eqref{eq:PDEeps} to \eqref{eq:PDE0}.
-We first state the following Lemma (\cite{Capuzzo-Dolcetta1990}), which characterizes the state-constraint of first-order equation
-\begin{equation}\label{S_0}
- \lambda u(x) + H(x,Du(x)) = 0\;\qquad\text{in}\;\Omega. \tag{$S_0$}
-\end{equation}
-
-\begin{lem}\label{lem:max} Let $u\in \rmC(\overline{\Omega})$ be a viscosity subsolution of \eqref{S_0} such that, for all viscosity subsolution $v\in \rmC(\overline{\Omega})$ of \eqref{S_0} one has $v\leq u$ in $\overline{\Omega}$, then $u$ is a viscosity supersolution of \eqref{S_0} on $\overline{\Omega}$.
-\end{lem}
-\noindent Lemma \ref{lem:max} is a variation of Perron's method.
-We give a proof in Appendix for the sake of completeness.
-Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ be a solution to \eqref{eq:PDEeps}, we claim that $\{\lambda u^\varepsilon\}_{\varepsilon>0}$ is uniformly bounded from below by a constant independent of $\varepsilon$ and $\lambda$.
-We have
-\begin{equation*}
-    u^\varepsilon(x) = \lim_{m\to \infty} u^{\varepsilon}_m(x), \qquad x\in \Omega,
-\end{equation*}
-where $u^{\varepsilon,m}\in \mathrm{C}^2(\Omega)\cap \rmC(\overline{\Omega})$ solves the Drichlet problem
-\begin{equation}\label{e:uepsm}
-    \begin{cases}
-    \lambda u(x) + H(x,Du(x)) - \varepsilon \Delta u(x) = 0 &\qquad
-    \text{in}\;\Omega, \vspace{0cm}\\
-    \;\;\quad\quad\qquad\qquad\qquad\qquad u(x) = m &\qquad
-    \text{on}\;\partial\Omega.
-    \end{cases} \tag{PDE$_{\varepsilon,m}$}
-\end{equation}
-If we assume $\mathrm{(H2)}$ then we can take $C_2 = \Vert f\Vert_{L^\infty(\Omega)}$ and take $\varphi(x) \equiv -\lambda^{-1}C_2$ for $x\in \overline{\Omega}$ as a subsolution to \eqref{e:uepsm}, hence by comparison principle for \eqref{e:uepsm} we have $u^{\varepsilon}_m(x)\geq -\lambda^{-1}C_2$ for all $x\in \overline{\Omega}$, thus as $m\to \infty$ we obtain $u^\varepsilon(x) \geq -\lambda^{-1}C_2$ for all $x\in \Omega$.
-
-\begin{thm}[Qualitative result]\label{thm:qual} Assume $\mathrm{(A1)}$.
-Let $u^\varepsilon$ be the solution to \eqref{eq:PDEeps}, then there exists $u^0 \in \mathrm{C}(\overline{\Omega})$ such that $u^\varepsilon \rightarrow u^0$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$ and $u^0$ solves \eqref{eq:PDE0}.
-Furthermore
-\begin{equation*}
-    u^0 \leq u^\varepsilon \qquad\text{in}\;\Omega.
-\end{equation*}
-\end{thm}
-
-\begin{proof}[Proof of Theorem \ref{thm:qual}] By the priori estimate
-\begin{equation*}
-    |u^\varepsilon(x)| + |Du^\varepsilon(x)| \leq C_\delta \qquad\text{for}\;x\in \overline{\Omega}_\delta
-\end{equation*}
-we deduce from the Arzel\'a--Ascoli theorem that there exists a subsequence $\varepsilon_j\to 0$ and a function $u^0\in \rmC(\Omega)$ such that $u^{\varepsilon_j}\to u^0$ locally uniformly in $\Omega$.
-By the stability of viscosity solution we easily deduce that
-\begin{equation}\label{eq:u0int}
-   \lambda u^0(x) + H(x,Du^0(x)) = 0 \qquad\text{in}\;\Omega.
-\end{equation}
-Since $u^\varepsilon(x)\geq -C_2$ for all $x\in \Omega$ we also have $u^0(x)\geq -C_2$ for all $x\in \Omega$, thus together with \eqref{eq:u0int} we obtain $H(x,\xi) \leq C_2$ for all $\xi\in D^+u^0(x)$ and $x\in \Omega$.
-The coercivity $\mathrm{(H4)}$ implies that there exists $K>0$ such that
-\begin{equation*}
-    |u^0(x) - u^0(y)| \leq K \qquad\text{for all}\;x,y\in \Omega.
-\end{equation*}
-Thus we can extend $u^0$ uniquely to $u^0\in \rmC(\overline{\Omega})$.
-We will use Lemma \ref{lem:max} to show that $u^0$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$.
-It suffices to to show that $u^0\geq w$ on $\overline{\Omega}$ where $w\in \rmC(\overline{\Omega})$ is the unique solution to \eqref{eq:PDE0}.
-
-For $\delta>0$, let $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) < \delta\}$ and $v_\delta\in\rmC(\overline{\Omega}_\delta)$ be the state-constraint viscosity subsolution to the problem $\lambda u(x) + H(x,Du(x)) = 0$ in $\Omega_\delta$.
-As $v_\delta\rightarrow w$ locally uniformly as $\delta\rightarrow 0^+$ (see \cite{kim_state-constraint_2020}) and $w$ is bounded, therefore $\{v_\delta\}_{\delta>0}$ is uniformly bounded.
-Let $v^\varepsilon_\delta\in \rmC^2(\Omega_\delta)\cap \rmC(\overline{\Omega}_\delta)$ be the unique solution to the Dirichlet problem
-\begin{equation}\label{eq:vv_eps}
-\begin{cases}
-    \lambda v_\delta^\varepsilon(x) + |Dv_\delta^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v_\delta^\varepsilon(x) &\qquad\text{in}\;\Omega_\delta,\\
-    \;\;\;\,\quad\qquad\qquad\qquad\qquad v_\delta^\varepsilon = v_\delta &\qquad \text{on}\;\partial\Omega_\delta.
-\end{cases}
-\end{equation}
-For all $\delta$ small enough $v_\delta\leq u^\varepsilon$ on $\partial \Omega_\delta$, thus by maximum principle $v^\varepsilon_\delta \leq u^\varepsilon$ on $\overline{\Omega}_\delta$.
-Let $\varepsilon\to 0$ we have $v_\delta \leq u^0$ on $\overline{\Omega}_\delta$.
-Let $\delta\rightarrow 0$ we obtain $w\leq u^0$ in $\Omega$, which implies $w\leq u^0$ on $\overline{\Omega}$ since both $w,u^0$ belong to $\rmC(\overline{\Omega})$.
-\end{proof}
-
-\section{Rate of convergence via Doubling variables}
-\noindent Let $\Omega = B(0,1)$. Fix $\theta \in (0,1)$ to be chosen later, let us define
+Recall that $|D d(x_\sigma)| = 1$, from \eqref{e:sub1}, \eqref{e:super1}, $d(x_\sigma)\geq \sigma$ we have
+\begin{align}
+    &\lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) \leq |\xi_\sigma|^p - |\xi_\sigma+\zeta_\sigma|^p + f(y_\sigma) - f(x_\sigma) \nonumber\\
+    &\qquad\qquad\qquad\quad + \varepsilon\left(\frac{2nC_\varepsilon}{\sigma} + \frac{C_\varepsilon(\alpha+1)(\alpha+2)}{d(x_\sigma)^{\alpha+3}} - \frac{C_\varepsilon(\alpha+1)\Delta d(x_\sigma)}{d(x_\sigma)^{\alpha+2}}\right)\nonumber \\
+    &\qquad\qquad\qquad\quad\leq |\xi_\sigma|^p - |\xi_\sigma+\zeta_\sigma|^p + C_f|x_\sigma - y_\sigma| +\varepsilon \left(\frac{2n C_\varepsilon}{\sigma} + \frac{(\alpha+2)}{d(x_\sigma)}|\zeta_\sigma| + K_2|\zeta_\sigma|\right) \label{e:est3}
+\end{align}
+where $K_2 = \max_{x\in \overline{\Omega}}\Delta d(x)$. Using the estimate
 \begin{align*}
-    \Psi^{\sigma}(x,y) = \theta u^\varepsilon(x) - u^0(y) - \frac{|x-y|^2}{\sigma}- \frac{C_0}{d(x)^\alpha}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega} 
+    \left||x+y|^p - |x|^p \right| \leq  p\big(|x|+|y|\big)^{p-1}|y|
 \end{align*}
-where $\sigma>0$ to be chosen later.
-
-\section{Rate of convergence via a simple idea}
-\noindent Let $\Omega = B(0,1)$, the scaling and distance near boundary are the same, i.e., $(1-\delta)\Omega = \Omega_\delta$.
-
-\noindent Let $u_\delta\in \rmC(\overline{\Omega}_\delta)$ be the state-constraint solution of the first-order equation, still $H(x,\varrho) = |\varrho|^p - f(x)$,
-\begin{equation*}
-    \begin{cases}
-    \lambda u_\delta(x) + H(x,Du_\delta(x)) \leq 0 &\qquad\text{in}\;(1-\delta)\Omega,\\
-    \lambda u_\delta(x) + H(x,Du_\delta(x)) \geq 0 &\qquad\text{on}\;(1-\delta)\overline{\Omega}.
-    \end{cases}
-\end{equation*}
-We know that the optimal rate of convergence of $u_\delta$ to $u^0$ is given by (\cite{kim_state-constraint_2020})
-\begin{equation*}
-    0\leq u_\delta - u^0 \leq C\delta
-\end{equation*}
-where $C$ depends on $H$ only (\textcolor{red}{check this}).
-
-\noindent Let $g_{\varepsilon,\delta}(x) = u^\varepsilon(x)$ for $x\in \partial\Omega_\delta$ which is finite.
-We have $u_\delta\leq g_{\varepsilon,\delta}$ for all $\varepsilon$ and also for each fixed $\delta>0$ then
-\begin{equation*}
-    \lim_{\varepsilon\to 0} g_{\varepsilon,\delta}(x) = u_\delta(x).
-\end{equation*}
-On the domain $\Omega_\delta$, we consider the problem
-\begin{equation*}
-    \begin{cases}
-    \mathcal{L}[v^\varepsilon] = 0 &\qquad\text{in}\;\Omega_\delta,\\
-    v^\varepsilon = g_{\delta,\varepsilon} &\qquad\text{on}\;\partial\Omega_\delta.
-    \end{cases}
-\end{equation*}
-Question: can we quantify $\Vert v^\varepsilon - u_\delta\Vert_{L^\infty}$ in term of $\varepsilon$?
-
-\section{Rate of convergence via nonlinear adjoint method}
-
-%\nocite{*}
+with $x = \xi_\sigma$, $y = \zeta_\sigma$ and the fact that $|\zeta_\sigma|\leq \mathfrak{C}_\alpha$ we obtain
+\begin{align}
+    \Big||\xi_\sigma+\zeta_\sigma|^p - |\xi|^p\Big| &\leq p\Big(|\xi_\sigma|+|\zeta_\sigma|\Big)^{p-1}|\zeta_\sigma| \nonumber \\
+    &\leq \Big( p(C_0 + \mathfrak{C}_\alpha)^{p-1}\mathfrak{C}_\alpha \Big) \varepsilon^{(\alpha+1) -\beta(\alpha+2)} \leq K_3\varepsilon ^{(\alpha+1)  - \beta(\alpha+2)}\label{e:est2}
+\end{align}
+where $K_3 = p\mathfrak{C}_\alpha(C_0+\mathfrak{C}_\alpha)^{p-1}$. From \eqref{e:est3} and \eqref{e:est2} we deduce that
+\begin{align*}
+    \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) &\leq  K_3 \varepsilon^{(\alpha+1) - \beta(\alpha+2)}  + C_fK_4 \varepsilon^{\beta(1+\alpha)} \\
+    &+ \left(\frac{2n(\alpha+1)^{\alpha+1}}{\alpha}\right)\varepsilon^{(\alpha+2) - (\alpha+1)(\beta+1)}\\
+    &+ \left(\frac{(\alpha+2)(1+\sigma)}{1-\alpha}\mathfrak{C}_\alpha\right)\varepsilon^{(1-\beta) + (\alpha+1) - \beta(\alpha+2)}\\
+    &+ K_2\mathfrak{C}_\alpha \varepsilon^{1+(\alpha+1)-\beta(\alpha+2)}.
+\end{align*}
+We obtain again that the optimal rate is $\mathcal{O}(\sqrt{\varepsilon})$ in this case.
 
@@
 
-\begin{appendices}
+\begin{quest} Let $g_{\varepsilon,\delta}(x) = u^\varepsilon(x)$ for $x\in \partial\Omega_\delta$ which is finite.
+We have $u_\delta\leq g_{\varepsilon,\delta}$ for all $\varepsilon$ and also for each fixed $\delta>0$ then
+\begin{equation*}
+    \lim_{\varepsilon\to 0} g_{\varepsilon,\delta}(x) = u_\delta(x).
+\end{equation*}
+On the domain $\Omega_\delta$, we consider the problem
+\begin{equation*}
+    \begin{cases}
+    \mathcal{L}[v^\varepsilon] = 0 &\qquad\text{in}\;\Omega_\delta,\\
+    v^\varepsilon = g_{\delta,\varepsilon} &\qquad\text{on}\;\partial\Omega_\delta.
+    \end{cases}
+\end{equation*}
+Question: can we quantify $\Vert v^\varepsilon - u_\delta\Vert_{L^\infty}$ in term of $\varepsilon$?
+
+\end{quest}
+
+\color{blue}
+\textcolor{blue}{\textbf{The next questions and tasks:}}
+\begin{enumerate}
+    \item Check all the constants, make sure things are correct!
+    \item It seems that $\sqrt{\varepsilon}$ is the best using this method. Now we can improve this by either:
+    \begin{itemize}
+        \item[(a)] Make the boundary layer to $\sqrt{\varepsilon}$ only, instead of $2\sqrt{\varepsilon}$.
+        \item[(b)] \textcolor{red}{\textbf{Important.}} Generalize this to more general domain, possibly star-shaped domains where we can do scaling is fine (just my guess).
+    \end{itemize}
+    \item Other formulations of the doubling variable method here, for example, in the first step, it seems that making $\Phi^\sigma(x,y)\to  -\infty$ as $x\to \partial\Omega$ is "\emph{too wasteful}".
+One may need only to do something like
+    \begin{equation*}
+        \Phi^\sigma(x,y) < \Phi^\sigma(0,0) \qquad\text{if}\qquad d(x) < \;\text{something close to the boundary}.
+    \end{equation*}
+    Can we improve that to get a better rate?
+My guess is not even if we can improve this, since the dominating term coming from $\varepsilon^\gamma$ and $\varepsilon^{1-\gamma}$ later.
+Nevertheless, it maybe still interesting to see why and how the \emph{wasteful} formulation here can be improved.
+    \item \textcolor{red}{\textbf{Important.}} Using nonlinear adjoint method.
+    \item Now once we have some rate, can we do bootstrap to improve it as we discussed earlier (the simple ideas, ...)?
+    \item \textcolor{red}{\textbf{Important.}} Can we find an example where $|u^\varepsilon - u^0| = \mathcal{O}(1)$ in the strip where $0<\mathrm{dist}(x,\partial\Omega)<2\sqrt{\varepsilon}$?
+Or can we even make more layers inside with more scales, as $|u^\varepsilon - u^0| = \mathcal{O}(1)$ is not possible near the boundary $\partial\Omega$.
+\end{enumerate}
+\color{black}
 
@@
 
-\section{Differentiability with respect to the parameter}
-For the vanishing viscosity problem with the Dirichlet boundary condition,
-\begin{equation}
-\label{dir}
-\left\{
-  \begin{aligned}
-    H(x, Du^\epsilon(x)) &= \epsilon \Delta u^\epsilon \quad \, \text{in } U, \\
-              u^\epsilon &= 0 \quad \qquad \text{on } \partial U,
-  \end{aligned}
-\right.
-\end{equation}
-where  $H(x,p)$ is $C^\infty(\overline{U}\times \mathbb{R}^n)$, $\displaystyle \frac{H(x,p)}{|p|} \to \infty$ uniformly in $x$ as $|p| \to \infty$ and $\displaystyle \sup_{x\in U}|D_xH(x,p)|\leq C(1+|p|)$, we want to show the smooth dependence of $u^\epsilon$ on $\epsilon$.
-Formally, if we differentiate \eqref{dir} with respect to $\epsilon$, we get
-\begin{equation}
-\label{dir_dif}
-\left\{
-  \begin{aligned}
-    D_pH(x, Du^\epsilon(x))\cdot Du^\epsilon_\epsilon &= \epsilon \Delta u^\epsilon_\epsilon +\Delta u^\epsilon \quad \, \text{in } U, \\
-              u^\epsilon_\epsilon &= 0 \quad \qquad  \qquad  \text{on } \partial U.
-  \end{aligned}
-\right.
-\end{equation}
-By Schaefer's fixed point theorem and the maximal principle, $u^\epsilon_\epsilon$ is the unique solution in $C^{2,\alpha}(\overline{U})$ of \eqref{dir_dif}.
+\section{The construction of $C^2$ diffeomorphism from $\overline{\Omega}$ to $\overline{\Omega^\delta}$}
+$\Omega \subset \mathbb{R}^n$ is an open and bounded domain with a smooth boundary.
+For $\delta > 0$, let $\Gamma_\delta = \{x \in \Omega: \mathrm{dist}(x, \partial \Omega) < \delta \}$, $\Gamma^\delta = \{x \in \Omega^c: \mathrm{dist}(x, \Omega^c) < \delta \}$.
+For $\delta$ small enough, we want to construct a diffeomorphism $T_\delta$ that maps from $\overline{\Omega}$ onto $\overline{\Omega^\delta}$and $\partial \Omega$ onto $\partial \Omega^\delta$, and
 
-\noindent The main idea is, we look at the difference quotients $\displaystyle \frac{u^{\epsilon+h}-u^\epsilon}{h}$and prove that as $h \to 0^+$, they converge to a limiting function $w^{\ast}$ in the uniform norm  such that $w^{\ast}$ solves \eqref{dir_dif}.
-Since \eqref{dir_dif} has a unique solution, we have $$u^\epsilon_\epsilon=\lim_{h \to 0^+}\frac{u^{\epsilon+h}-u^\epsilon}{h}.$$
+$$\sup_{x\in \overline{\Omega}}\{|T_\delta(x)-x|+|\nabla T_\delta(x)-I|\} \leq C \delta.$$
 
-\subsection{Solution $u^\epsilon \in C^{2,\alpha}(\overline{U})$ exists} We use Schaufer's fixed point theorem as follows.
+The conditions on $\Omega$ imply that $\partial \Omega$ satisfies a uniform two-sided (interior and exterior) sphere condition.
+That is, at each point $y^0 \in \partial \Omega$, there exists a ball $B_1(r_{y_0}, y_0)$ such that $B_1(r_{y_0}, y_0) \cap (\mathbb{R}^n - \Omega)=\{y_0\}$, and another ball $B_2(r^\prime_{y_0}, y_0)$ such that $B_2(r^\prime_{y_0}, y_0) \cap  \Omega=B_2(r^\prime_{y_0}, y_0)$.
+More importantly, the radii are strictly bounded below by a positive constant, which we take to be $\delta$.
+Note that principal curvatures of $\partial \Omega$ are bounded by $\delta^{-1}$.
 
-\begin{thm} Suppose $X$ is a Banach space.
-Let $A:X \to X$ be continuous and compact.
-Assume the set $\{u\in X : u=\lambda A[u]$ for some $0 \leq  \lambda \leq 1\}$ is bounded.
-Then $A$ has a fixed point $u =A[u]$.
-\end{thm}
-\noindent Fix $0<\alpha<1$. Let $X=C^{1,\alpha}(\overline{U})$. Given $u \in X=C^{1,\alpha}(\overline{U})$, we look at the linear PDE
-\begin{equation}
-\label{fix}
-\left\{
-  \begin{aligned}
-   \epsilon \Delta v &= H(x, Du) \quad \, \text{in } U, \\
-              v &= 0 \qquad \qquad \text{on } \partial U.
-  \end{aligned}
-\right.
-\end{equation}
-\noindent
-Estimate the Holder norm of RHS
-$$\|H(x, Du)\|_{C^{0, \alpha}(\overline{U})}:=\sup_{x\in\overline{U}} |H(x,Du(x))| + \sup_{x, y \in \overline{U}}\frac{|H(x, Du(x))-H(y, Du(y))|}{|x-y|^\alpha}.$$
-Since $Du$ is bounded and H is smooth,
-\begin{equation}
-    \sup_{x\in\overline{U}} |H(x,Du(x))| \leq C.
-\end{equation}
+For each point $z \in \Gamma_\delta$, there is a unique point $y=y(z) \in \partial \Omega$ such that $|y-z|=\mathrm{dist}(z, \partial \Omega)$, and for each point $x \in \Gamma^\delta$, there is a unique point $w=w(x) \in \partial \Omega$ such that $|w-x|= \mathrm{dist}(x, \partial \Omega)$.
+
+Define a smooth increasing function $f: \mathbb{R} \to \mathbb{R}$ by
 
 \begin{equation}
+f(x)=\left\{  
    \begin{aligned}
-  &\sup_{x, y \in \overline{U}}\frac{|H(x, Du(x))-H(y, Du(y))|}{|x-y|^\alpha}\\
-  \leq &  \sup_{x, y \in \overline{U}}\frac{|H(x, Du(x))-H(y, Du(x))|}{|x-y|^\alpha} + \sup_{x, y \in \overline{U}}\frac{|H(y, Du(x))-H(y, Du(y))|}{|x-y|^\alpha} \\
-  =&    \sup_{x, y \in \overline{U}}\frac{|\int_0^1D_xH(y+\theta (x-y), Du(x))d\theta \cdot (x-y)|}{|x-y|^\alpha}\\& +
-     \sup_{x, y \in \overline{U}}\frac{|\int_0^1D_pH(y, Du(y)+\theta (Du(x)-Du(y)))d\theta \cdot (Du(x)-Du(y))|}{|x-y|^\alpha}\\
-  \leq &  C\sup_{x, y \in \overline{U}} (1+|Du(x)|)|x-y|^{1-\alpha} +  C \sup_{x, y \in \overline{U}}\frac{| (Du(x)-Du(y))|}{|x-y|^\alpha}\\
- \leq & C(1 + \|u\|_{C^{1,\alpha}(\overline{U})})
-    \end{aligned}
-\end{equation}
-since $Du$ is bounded on $\overline{U}$, $D_pH \in C^\infty (\overline{U} \times \mathbb{R}^n)$ and
-$\displaystyle \sup_{x\in U}|D_xH(x,p)|\leq C(1+|p|)$. Therefore,
-\begin{equation}
- \|H(x, Du)\|_{C^{0, \alpha}(\overline{U})} \leq C(1 + \|u\|_{C^{1,\alpha}(\overline{U})}).
-\end{equation}
-By Schauder estimates, there exists a unique solution $v \in C^{2,\alpha }(\overline{U})$ such that
-\begin{equation}
-\label{schauder}
-    \|v\|_{C^{2, \alpha}(\overline{U})} \leq C  \|H(x, Du)\|_{C^{0, \alpha}(\overline{U})}. 
-\end{equation}
-\noindent Define operator $A$ on $X := C^{1, \alpha} (\overline{U}) $ by $A[u]=v$. So 
-\begin{equation}
-     \|A[u]\|_{C^{2, \alpha}(\overline{U})} \leq C(1 + \|u\|_{C^{1,\alpha}(\overline{U})}),
-\end{equation}
-\noindent
- and thus $A$ is continuous and compact.
-(i.e., if $\{u_k\}_{k=1}^\infty$ is bounded in $X=C^{1, \alpha}(\overline{U})$, then $\{A[u_k]\}_{k=1}\infty$ is bounded in $C^{2,\alpha} (\overline{U})$, thus precompact in $C^{1, \alpha}(\overline{U})$.
-Lemma 6.36 in Gilbarg and Trudinger.
-)
-
- Next we try to bound $\{u\in X : u=\lambda A[u]$ for some $0 \leq  \lambda \leq 1\}$.
- If $u=\lambda A[u]$, the PDE becomes
-
-\begin{equation}
-\label{lamb}
-\left\{
-  \begin{aligned}
-   \epsilon \Delta u &= \lambda H(x, Du) \quad \, \text{in } U, \\
-              u &= 0 \qquad \qquad \text{on } \partial U.
+   x, \, x \leq -\delta\\
+   \delta, \, \, x=0.
   \end{aligned}
@@
 
-Calderon-Zygmund estimates tell us that if we have
-\begin{equation}
-\label{cald}
-\left\{
-  \begin{aligned}
-  - \Delta v &=\Tilde{f}   \qquad \, \text{in } U, \\
-              v &= 0 \qquad \text{on } \partial U.
-  \end{aligned}
-\right.
-\end{equation}
+Given a point $z_0 \in \Gamma_\delta$, let $y_0= y(z_0)$ and choose a principle coordinate system at $y_0$ for a neighborhood $\mathcal{N}(y_0)$ around $y_0$.
+Let $T(y_0)$ be the tangent hyperplane to $\partial \Omega$ at $y_0$ and $\mathbf{v}(y_0)$ be the inner normal vector to $\partial \Omega$ at $y_0$.
+In $\mathcal{N}(y_0)$ , $\partial \Omega$ is given by $x_n=\phi(x^\prime)$ where $x^\prime=(x_1, x_2, \cdots, x_n)$ for some smooth function $\phi$.
 
-and $\Tilde{f} \in {L^p(U)}$ for some $p\in (1, \infty)$, then $v \in W^{2,p}(U)$ and $$\|v\|_{w^{2,p}(U)} \leq C\|\Tilde{f}\|_{L^p(U)}.$$
+We define a map $g: (T(y_0) \times \mathcal{N}(y_0)) \times \mathbb{R} \to R^n $ by
+$$g(z)=(y(z), \phi (y(z))) + f(|y(z)-z|) \mathbf{v}(y(z))$$
 
-Apply to \eqref{lamb} and we get
-
-\begin{equation}
-    \|u\|_{w^{2,p}(U)} \leq C\|H(x, Du)\|_{L^p(U)}
-\end{equation}
-
-(We want RHS to be bounded by some constant so that later we can choose $p$ larger than $n$ to  conclude $ \|u\|_{C^{1, \alpha}(U)} \leq   C\|u\|_{w^{2,p}(U)} \leq C$ by Morrey's estimate.) By a priori estimate, if we assume the solution of \eqref{dir} $u$ exists, then $\| Du\|_{L^\infty} \leq C_0$ where $C_0$ is independent of $\epsilon$.
-We can modify $H$ to get a new $\Tilde{H}$ so that it is smooth, $\Tilde{H} = H$ for $|p|<C_1$ and $H(x,p)=C_1+1$ for $|p|>C_1+1$ for some constant $C_1$ ($C_1$ is definitely larger than $C^0$).
-Moreover, the same prior estimate is correct for $\Tilde{H}$.
-Namely, if the solution $\Tilde{u}$ to \eqref{dir} with $H$ replaced by $\Tilde{H}$ exists, then $\| D\Tilde{u}\|_{L^\infty} \leq C_0$.
-(The way we choose this $C_1$ is that we work back from the beginning of the proof of a priori estimate for $u$, on both the boundary and interior of $\Omega$, and modify $H$ so that all the proofs go through and the same a priori estimate holds for the equation with $\Tilde{H}$.) Now with $\Tilde{H}$, we go through the same argument of Schaufer's fixed point theorem from the very beginning, and \eqref{cald} reads
-\begin{equation}
-       \|\Tilde{u}\|_{w^{2,p}(U)} \leq C\|\Tilde{H}(x, D\Tilde{u})\|_{L^p(U)} \leq C(1+\|D\Tilde{u}\|_{L^\infty}) \leq C.
-\end{equation}
-
-Choose $p=2n$ and $\displaystyle \alpha =\frac{1}{2}$. We have $\{\Tilde{u}\in X : \Tilde{u}=\lambda A[\Tilde{u}]$ for some $0 \leq  \lambda \leq 1\}$ is bounded in $X= C^{1, \frac{1}{2}}(
-\overline{U})$.
-Thus Schaefer's fixed point theorem implies the equation \eqref{dir} with $H$ replaced by $\Tilde{H}$ has a solution $\Tilde{u} \in C^{2,\alpha} (\overline{\Omega})$.
-Since $\| D\Tilde{u}\|_{L^\infty} \leq C_0$, $\Tilde{u}$ also solves the original equation \eqref{dir}.
-
-\subsection{Uniqueness}
-Let $u$ and $v$ be two solutions to \eqref{dir} and $w := u-v$. Then we have
-\begin{equation}
-\begin{aligned}
-    &-\epsilon \Delta (u-v) = H(x, Dv)-H(x, Du)\\
-    \Rightarrow &-\epsilon \Delta w   =\int_0^1 D_pH(x, tDv+(1-t)Du) \cdot (Dv-Du)dt\\
-    \Rightarrow &-\epsilon \Delta w  +\int_0^1 D_pH(x, tDv+(1-t)Du)dt \cdot Dw = 0.
-\end{aligned}
-\end{equation}
-By the strong maximum principle, $w \equiv 0$.
-
-\subsection{Smooth dependence on $\epsilon$}
-Fix $\epsilon >0$. Let  $$w^h(x):=\frac{u^{\epsilon+h}(x)-u^\epsilon(x)}{h} \in C^{2,\alpha}(\overline{U}).$$
-
-A little computation shows that $w^h$ solves
-
-\begin{equation}
-\label{dir_quo}
-\left\{
-  \begin{aligned}
-   \epsilon \Delta w^h(x) + \frac{\epsilon}{\epsilon + h}\Delta u^\epsilon &= \frac{\epsilon}{\epsilon +h} \int_0^1 D_pH(x, Du^\epsilon+\theta (Du^{\epsilon+h}-Du^\epsilon)) d\theta \cdot Dw^h \quad \, \text{in } U, \\
-              w^h &= 0 \quad \qquad \text{on } \partial U.
-  \end{aligned}
-\right.
-\end{equation}
-
-From the existence proof, we know $\|u^\epsilon\|_{C^{2,\alpha}(\overline{U})} \leq C$ uniformly in $\epsilon$.
-So $\|Du^{\epsilon+h}-Du^\epsilon\|_{C^{0,\alpha}(\overline{U})}$and $\|\Delta u\|_{C^{0,\alpha}(\overline{U})}
-$ is uniformly bounded in $h$.
-
-By Schauder estimates, $\{w^h\}_{h>0} \subset C^{2, \alpha}(\overline{U})$ are bounded, hence is precompact in $ C^{2, \beta}(\overline{U})$ for any $\beta < \alpha$.
-Therefore, there exits a subsequence $\{w^{h_j}\}_{j=1}^\infty$ such that $w^{h_j} \to w^\ast$ for some $w^\ast \in  C^{2, \beta}(\overline{U}) $ and $w^\ast$ solves \eqref{dir_dif}.
-This implies $w^h \to w^\ast$ in $C^{2, \beta}(\overline{U})$.
-
-\section{Proofs of some Lemmas and Propositions}
-\begin{proof}[Proof of Lemma \ref{lem:max}] The proof is a variation of Perron's method (see \cite{Capuzzo-Dolcetta1990}).
-Let $\varphi\in \rmC(\overline{\Omega})$ and $x_0\in \overline{\Omega}$ such that $u(x_0) = \varphi(x_0)$ and $u-\varphi$ has a global strict minimum over $\overline{\Omega}$ at $x_0$ and that
-\begin{equation}\label{eq:max_a1}
-    \lambda \varphi(x_0) + H(x_0,D\varphi(x_0)) < 0.
-\end{equation}
-Let $\varphi^\varepsilon(x) = \varphi(x) - |x-x_0|^2 + \varepsilon$ for $x\in \overline{\Omega}$. Let $\delta > 0$, we see that for $x\in \partial B(x_0,\delta)\cap \overline{\Omega}$ then
-\begin{equation*}
-    \varphi^\varepsilon(x) = \varphi(x) - \delta^2 +\varepsilon \leq \varphi(x) - \varepsilon
-\end{equation*}
-if $2\varepsilon \leq \delta^2$. We observe that
-\begin{equation*}
-    \begin{split}
-    \varphi^\varepsilon(x) - \varphi(x_0)  &= \varphi(x)-\varphi(x_0) + \varepsilon - |x-x_0|^2 \\
-    D\phi^\varepsilon(x) - D\phi(x_0) &= D\varphi(x) - D\varphi(x_0) - 2(x-x_0)
-    \end{split}
-\end{equation*}
-for $x\in B(x,\delta)\cap \overline{\Omega}$.
-We deduce from \eqref{eq:max_a1}, the continuity of $H(x,p)$ near $(x_0,D\varphi(x_0))$ and the fact that $\varphi\in \rmC^1(\overline{\Omega})$ that if $\delta$ is small enough and $0<2\varepsilon < \delta^2$ then
-\begin{equation}\label{eq:max_a2}
-    \lambda \varphi^\varepsilon(x)+H(x,D\varphi^\varepsilon(x)) < 0 \qquad\text{for}\;x\in B(x_0,\delta)\cap \overline{\Omega}.
-\end{equation}
-We have found $\phi^\varepsilon\in \mathrm{C}^1(\overline{\Omega})$ such that $\varphi^\varepsilon(x_0)>u(x_0)$, $\varphi^\varepsilon<u$ on $\partial B(x_0,\delta)\cap \overline{\Omega}$ and \eqref{eq:max_a2}.
-Let
-\begin{equation*}
-    \tilde{u}(x) = \begin{cases}
-    \max \big\lbrace u(x),\phi^\varepsilon(x) \big\rbrace &x\in B(x_0,\delta)\cap \overline{\Omega},\\
-    u(x)&x\notin B(x_0,\delta)\cap \overline{\Omega},\\
-    \end{cases}
-\end{equation*}
-We see that $\tilde{u}\in \rmC(\overline{\Omega})$ is a subsolution of \eqref{S_0} in $\Omega$ with $\tilde{u}(x_0) > u(x_0)$, which is a contradiction, thus $u$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$.
-\end{proof}
-
-\end{appendices}
+Define $\Gamma_\delta : \overline{\Omega} \to \overline{\Omega^\delta}$ by
 

### 2021-04-06 Drafts and notes/Notes/Report-Apr 2.tex
Major change

\documentclass[english,reqno]{amsart}
%\renewcommand{\baselinestretch}{1.2}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\raggedbottom
\usepackage{subfig}
\usepackage{amssymb,amsbsy,amsmath,amsfonts,amssymb,amscd}
\usepackage{comment}
\usepackage{verbatim}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage[numbers]{natbib} % for alphabetically numbered lists
\usepackage{algorithm,algpseudocode}
\usepackage{setspace}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{assum}{Assumption}[section]
\newtheorem{cor}{Corollary}[section]

\title{Progress Report - Arp 2}

\begin{document}

\maketitle
Let $u^\epsilon$ solve the equation
\begin{equation}
\left\{
  \begin{aligned}
    u^\epsilon + |Du^\epsilon|^p -f(x) - \epsilon \Delta u^\epsilon &=0 \quad \, \text{in } \Omega, \\
            u^\epsilon &= \infty \quad \text{on } \partial \Omega,
  \end{aligned}
\right.
\end{equation}

and $u_0$ solve the equation
\begin{equation}
\left\{
  \begin{aligned}
    u_0 + |Du_0|^p -f(x) &\leq 0 \quad \, \text{in } \Omega, \\
             u_0 + |Du_0|^p -f(x) &\geq 0 \quad \text{on } \bar{\Omega}.
  \end{aligned}
\right.
\end{equation}

\begin{itemize}
    \item[1.] Before, we had the conclusion $ u \leq u^\epsilon$, which is in fact false. What we have is only $u \leq u^\epsilon +C\epsilon^\frac{1}{2}$. Let $w^\epsilon$ be the solution of 
    \begin{equation}
\left\{
  \begin{aligned}
     w^\epsilon\ + |Dw^\epsilon|^p -f(x) - \epsilon \Delta w^\epsilon  &=0 \quad \, \text{in } \Omega, \\
   w^\epsilon &= u \quad \text{on } \partial \Omega.
  \end{aligned}
\right.
\end{equation} 
By the estimate of vanishing viscosity problem with Dirichlet boundary condition, we have \begin{equation}
    |w^\epsilon - u| \leq C \epsilon ^\frac{1}{2}.
\end{equation}
Hence, we have 
\begin{equation}
    u \leq C\epsilon^\frac{1}{2}+w^\epsilon\leq C\epsilon^\frac{1}{2} + u^\epsilon
\end{equation}
by comparison principle.

\bigbreak
\bigbreak

\item[2.] Consider
\begin{equation}
\left\{
  \begin{aligned}
    L(\varphi_\alpha) = \varphi_\alpha + |D\varphi_\alpha|^p -f(x) - \alpha \Delta \varphi_\alpha &=0 \quad \, \text{in } \Omega_\epsilon, \\
   \varphi_\alpha &= C\epsilon \quad \text{on } \partial \Omega_\epsilon.
  \end{aligned}
\right.
\end{equation}

It is not clear to us why $\varphi_\epsilon \geq u_\epsilon$. If we fix $\epsilon$, $\displaystyle u_\epsilon \approx \frac{C_\alpha \epsilon^{\alpha+1}}{d(x)^\alpha} +M $ in the interior and we don't quite have $u_\epsilon \leq C\epsilon$ when $d(x)=\epsilon$ because of the constant $M$.

Note that $\varphi_0$ solves
\begin{equation}
\label{vis}
\left\{
  \begin{aligned}
    \varphi_0 + |D\varphi_0|^p -f(x) &=0 \quad \, \text{in } \Omega_\epsilon, \\
             \varphi_0 &= C\epsilon \quad \text{on } \partial \Omega_\epsilon.
  \end{aligned}
\right.
\end{equation}
We are still trying to see what is the relation between $u_0$ and $\varphi_0$ for now.

\bigbreak
\bigbreak

\item[3.]Suppose $f$ has compact support and we try to find the minimum of $u^\epsilon$. Suppose $u^\epsilon$ has min at $x_0$, then $\epsilon \Delta u^\epsilon(x_0) \geq 0$ and $$u^\epsilon(x_0) -f(x_0) - \epsilon \Delta u^\epsilon(x_0) =0 ,$$
which gives us $u^\epsilon(x_0) \geq f(x_0)$. This seems not very useful since we already know $u^\epsilon (x) \geq \min f$. Another attempt is to bound $\epsilon \Delta u^\epsilon(x_0)$ by Bernstein's method. However, this doesn't work out for now. After we get the equation for $\displaystyle w :=\frac{|Du^\epsilon|^2}{2}$, we don't know how to get a bound for $\epsilon \Delta u^\epsilon(x_0)$ from the equation of $\displaystyle w$.

\bigbreak
\bigbreak

    \item[4.] 
Let's assume $f$ is radial symmetric and $n=1$, then $u^\epsilon(x) = v(|x|)$ for some function $v$. Then $v$ solves
\begin{equation}
\left\{
  \begin{aligned}
    v(r) + |v^\prime (r)|^p -f(r) - \epsilon v^{\prime \prime} \left(\frac{n-1}{r}\right) &=0 \quad \, \text{in } (0,1), \\
            v &= \infty \quad \text{at  } x=1,
  \end{aligned}
\right.
\end{equation}

This ODE looks more complicated than the one of $u^\epsilon$.
We tried an example with 
\begin{equation}
f=
\left\{
  \begin{aligned}
     &1-|x| \quad \text{in } (-1,1), \\
          & 0 \quad \text{in  } (-2,2) \setminus (-1, 1),
  \end{aligned}
\right.
\end{equation}
and the boundary condition $u(0)=0$ and $u^\prime(0)=1$ in WolframAlpha. $u^\epsilon$ does blow up at $x=2$ and $x=-2$ according to the pictures. But we didn't manage to find out $u$ by manually computing.

We also tried Bernstein's method for the radial symmetric case but didn't get anything useful for now.

\item[5.] We also looked at the stochastic optimal control problem. We are still confused about the effect of $dB_t$ term on the path $X_t$.

\end{itemize}

\end{document}

### 2021-04-06 Drafts and notes/Notes/old_draft.tex
Major change

--- 2021-04-06 Drafts and notes/Attempts/Old_draft_07.tex
@@
     %\frac{C_\varepsilon-\eta}{d(x)^\alpha}-\frac{M_\eta}{\lambda} \leq u(x)\leq \frac{C_\varepsilon+\eta}{d(x)^\alpha}+\frac{M_\eta}{\lambda} 
-    \lim_{d(x)\to 0} u^\varepsilon(x) \,d(x)^\alpha = C_\varepsilon 
+    \lim_{d(x)\to 0} u^\varepsilon(x) \,d(x)^\alpha = C_\alpha \varepsilon^{\alpha+1}
 \end{equation*}
@@
 \noindent This is Theorem I.1 in \cite{Lasry1989}.
-We provide a proof in Appendix with the explicit dependence of $C_\varepsilon$ in terms of $\varepsilon$ for later use, it is useful to note that $\alpha+1 = \frac{1}{p-1}$.
+We provide a proof in Appendix with the explicit constant $C_\alpha\varepsilon^{\alpha+1}$ in terms of $\varepsilon$ for later use, it is useful to note that $\alpha+1 = \frac{1}{p-1}$.
+We also state the following useful results.
+
+\begin{prop}\cite{Lasry1989}\label{prop:u<} Assume the hypothesises of Theorem \ref{thm:wellposed1<p<2}. If $\frac{3}{2}<p<2$ then there exists some constant $C>0$ such that
+\begin{equation*}
+  \sup_{x\in \Omega} \left|u^\varepsilon(x) - \frac{C_\varepsilon}{d(x)^\alpha}\right| \leq C.
+\end{equation*}
+\end{prop}
+
+\begin{prop}\cite[Theorem B.3]{alessio_asymptotic_2006}\label{prop:grad} Assume the hypothesises of Theorem \ref{thm:wellposed1<p<2}. The gradient of $u^\varepsilon$ satisfies
+\begin{equation*}
+    \lim_{d(x)\to 0} \Big( d(x)^{\alpha+1}\nabla u^\varepsilon(x)\Big) = \left(C_\varepsilon \alpha\right) \mathfrak{n}(x_0)
+\end{equation*}
+where $\mathbf{n}(x_0)$ is the outward unit normal vector to $\Omega$ at $x_0\in \partial\Omega$.
+\end{prop}
 
@@
 \end{lem}
-\noindent Lemma \ref{lem:max} is a variation of Perron's method.
-We give a proof in Appendix for the sake of completeness.
-Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ be a solution to \eqref{eq:PDEeps}, we claim that $\{\lambda u^\varepsilon\}_{\varepsilon>0}$ is uniformly bounded from below by a constant independent of $\varepsilon$ and $\lambda$.
-We have
-\begin{equation*}
-    u^\varepsilon(x) = \lim_{m\to \infty} u^{\varepsilon}_m(x), \qquad x\in \Omega,
-\end{equation*}
- where $u^{\varepsilon,m}\in \mathrm{C}^2(\Omega)\cap \rmC(\overline{\Omega})$ solves the Drichlet problem
+\noindent We give a proof of Lemma \ref{lem:max} in Appendix for the sake of completeness.
+
+\begin{lem}\label{lem:lower-bound} Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ be a solution to \eqref{eq:PDEeps}.
+We have $\{\lambda u^\varepsilon\}_{\varepsilon>0}$ is uniformly bounded from below by a constant independent of $\varepsilon$.
+Precisely, we have
+\begin{equation}\label{e:lower_bound_u_eps}
+    \inf_{x\in \Omega} \lambda u^\varepsilon(x) \geq  \inf_{\Omega} f
+\end{equation}
+and also
+\begin{equation}\label{e:lower_bound_u}
+    \inf_{x\in \Omega} \lambda u(x) \geq  \inf_{\Omega} f
+\end{equation}
+\end{lem}
+\begin{proof} For $m\in \mathbb{N}$, let $u^{\varepsilon,m}\in \mathrm{C}^2(\Omega)\cap \rmC(\overline{\Omega})$ solves the Drichlet problem
 \begin{equation}\label{e:uepsm}
@@
 \end{equation}
-If we assume $\mathrm{(H2)}$ then we can take $C_2 = \Vert f\Vert_{L^\infty(\Omega)}$ and take $\varphi(x) \equiv -\lambda^{-1}C_2$ for $x\in \overline{\Omega}$ as a subsolution to \eqref{e:uepsm}, hence by comparison principle for \eqref{e:uepsm} we have $u^{\varepsilon}_m(x)\geq -\lambda^{-1}C_2$ for all $x\in \overline{\Omega}$, thus as $m\to \infty$ we obtain $u^\varepsilon(x) \geq -\lambda^{-1}C_2$ for all $x\in \Omega$.
-
-The following Theorem says that the large solution $u^\varepsilon$ converges to $u^0$ locally uniformly on $\Omega$ as $\varepsilon\to 0$.
-We present a simple proof here for the reader's convenience, see also \cite[Theorem VII.3]{Capuzzo-Dolcetta1990}.
-\begin{thm}[Vanishing viscosity - Qualitative result]\label{thm:qual} Assume $\mathrm{(A1)}$.
-Let $u^\varepsilon$ be the solution to \eqref{eq:PDEeps}, then there exists $u^0 \in \mathrm{C}(\overline{\Omega})$ such that $u^\varepsilon \rightarrow u^0$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$, $u^0$ solves \eqref{eq:PDE0} and $u^0 \leq u^\varepsilon$ in $\Omega$.
+We have $u^{\varepsilon}_m(x) \to u^\varepsilon(x)$ as $m\to \infty$ in $\Omega$.
+Let $\varphi(x) \equiv \lambda^{-1} \inf_{\Omega} f$ for $x\in \overline{\Omega}$ then $\varphi(x)$ is a classical subsolution of \eqref{e:uepsm} in $\Omega$ with
+\begin{equation*}
+    \varphi(x) = \lambda \inf_\Omega f \leq m = u^\varepsilon_m(x) \qquad\text{for}\;x\in \partial\Omega.
+\end{equation*}
+By comparison principle for the uniformly elliptic equation \eqref{e:uepsm} we have
+\begin{equation*}
+    \lambda^{-1}\inf_\Omega f \leq u^{\varepsilon}_m(x) \qquad\text{for all}\;x\in \Omega.
+\end{equation*}
+As $m\to \infty$ we obtain the conclusion \eqref{e:lower_bound_u_eps}.
+The inequality \eqref{e:lower_bound_u} follows from comparison principle of state-constraint equation \eqref{eq:PDE0} with supersolution $u$ on $\overline{\Omega}$ and subsolution $\varphi(x)$ in $\Omega$.
+\end{proof}
+
+We present a simple proof of the convergence $u^\varepsilon \to u$ using Lemma \ref{lem:max} for the reader's convenience, see also \cite[Theorem VII.3]{Capuzzo-Dolcetta1990}.
+\begin{thm}[Vanishing viscosity]\label{thm:qual} Assume $\mathrm{(A1)}$.
+Let $u^\varepsilon$ be the solution to \eqref{eq:PDEeps}, then there exists $u \in \mathrm{C}(\overline{\Omega})$ such that $u^\varepsilon \rightarrow u$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$, $u$ solves \eqref{eq:PDE0} and $u \leq u^\varepsilon$ in $\Omega$.
 \end{thm}
@@
 \end{equation}
-we deduce from the Arzel\'a--Ascoli theorem that there exists a subsequence $\varepsilon_j\to 0$ and a function $u^0\in \rmC(\Omega)$ such that $u^{\varepsilon_j}\to u^0$ locally uniformly in $\Omega$.
+we deduce from the Arzel\'a--Ascoli theorem that there exists a subsequence $\varepsilon_j\to 0$ and a function $u\in \rmC(\Omega)$ such that $u^{\varepsilon_j}\to u$ locally uniformly in $\Omega$.
 By the stability of viscosity solution we easily deduce that
 \begin{equation}\label{eq:u0int}
-   \lambda u^0(x) + H(x,Du^0(x)) = 0 \qquad\text{in}\;\Omega.
-\end{equation}
-Since $\lambda u^\varepsilon(x)\geq -C_2$ for all $x\in \Omega$, we also have $\lambda u^0(x)\geq -C_2$ for all $x\in \Omega$, thus together with \eqref{eq:u0int} we obtain $H(x,\xi) \leq C_2$ for all $\xi\in D^+u^0(x)$ and $x\in \Omega$.
-The coercivity $\mathrm{(H4)}$ implies that there exists $K>0$ such that
-\begin{equation*}
-    |u^0(x) - u^0(y)| \leq K \qquad\text{for all}\;x,y\in \Omega.
-\end{equation*}
-Thus we can extend $u^0$ uniquely to $u^0\in \rmC(\overline{\Omega})$.
-We will use Lemma \ref{lem:max} to show that $u^0$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$.
-It suffices to show that $u^0\geq w$ on $\overline{\Omega}$ where $w\in \rmC(\overline{\Omega})$ is the unique solution to \eqref{eq:PDE0}.
-
-For $\delta>0$, let $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\partial \Omega) > \delta\}$ and $v_\delta\in\rmC(\overline{\Omega}_\delta)$ be the state-constraint viscosity solution to the problem $\lambda u(x) + H(x,Du(x)) = 0$ in $\Omega_\delta$, i.e., $v_\delta$ is the unique viscosity solution to
+   \lambda u(x) + H(x,Du(x)) = 0 \qquad\text{in}\;\Omega.
+\end{equation}
+Since $\lambda u^\varepsilon(x)\geq -C_2$ for all $x\in \Omega$, we also have $\lambda u(x)\geq -C_2$ for all $x\in \Omega$, thus together with \eqref{eq:u0int} we obtain $H(x,\xi) \leq C_2$ for all $\xi\in D^+u(x)$ and $x\in \Omega$.
+The coercivity $\mathrm{(H4)}$ implies that there exists $C_0>0$ such that
+\begin{equation*}
+    |u(x) - u(y)| \leq C_0|x-y| \qquad\text{for all}\;x,y\in \Omega.
+\end{equation*}
+Thus we can extend $u$ uniquely to $u\in \rmC(\overline{\Omega})$.
+We will use Lemma \ref{lem:max} to show that $u$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$.
+It suffices to show that $u\geq w$ on $\overline{\Omega}$ where $w\in \rmC(\overline{\Omega})$ is the unique solution to \eqref{eq:PDE0}.
+
+For $\delta>0$, let $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\partial \Omega) > \delta\}$ and $u_\delta\in\rmC(\overline{\Omega}_\delta)$ be the state-constraint viscosity solution to the problem $\lambda u(x) + H(x,Du(x)) = 0$ in $\Omega_\delta$, i.e., $u_\delta$ is the unique viscosity solution to
 \begin{equation}\label{e:v_v}
     \begin{cases}
-    \lambda v_\delta(x) + H(x,Dv_\delta(x)) \leq 0 &\qquad\text{in}\;\Omega_\delta,\\
-    \lambda v_\delta(x) + H(x,Dv_\delta(x)) \geq 0 &\qquad\text{on}\;\overline{\Omega}_\delta.
+    \lambda u_\delta(x) + H(x,Du_\delta(x)) \leq 0 &\qquad\text{in}\;\Omega_\delta,\\
+    \lambda u_\delta(x) + H(x,Du_\delta(x)) \geq 0 &\qquad\text{on}\;\overline{\Omega}_\delta.
     \end{cases}
 \end{equation}
-As $v_\delta\rightarrow w$ locally uniformly as $\delta\rightarrow 0^+$ (see \cite{kim_state-constraint_2020}) and $w$ is bounded, therefore $\{v_\delta\}_{\delta>0}$ is uniformly bounded.
+As $u_\delta\rightarrow w$ locally uniformly as $\delta\rightarrow 0^+$ (see \cite{kim_state-constraint_2020}) and $w$ is bounded, therefore $\{u_\delta\}_{\delta>0}$ is uniformly bounded.
 Let $v^\varepsilon_\delta\in \rmC^2(\Omega_\delta)\cap \rmC(\overline{\Omega}_\delta)$ be the unique solution to the Dirichlet problem
@@
 For all $\delta$ small enough $v_\delta\leq u^\varepsilon$ on $\partial \Omega_\delta$, thus by maximum principle $v^\varepsilon_\delta \leq u^\varepsilon$ on $\overline{\Omega}_\delta$.
-Let $\varepsilon\to 0$ we have $v_\delta \leq u^0$ on $\overline{\Omega}_\delta$.
-Let $\delta\rightarrow 0$ we obtain $w\leq u^0$ in $\Omega$, which implies $w\leq u^0$ on $\overline{\Omega}$ since both $w,u^0$ belong to $\rmC(\overline{\Omega})$.
+Let $\varepsilon\to 0$ we have $v_\delta \leq u$ on $\overline{\Omega}_\delta$.
+Let $\delta\rightarrow 0$ we obtain $w\leq u$ in $\Omega$, which implies $w\leq u$ on $\overline{\Omega}$ since both $w,u$ belong to $\rmC(\overline{\Omega})$.
 \end{proof}
@@
 \subsection{Rate of convergence for first-order equation on nested domain}
-For $\delta >0$, let $u\in \rmC(\overline{\Omega})$ and $u_\delta\in \rmC(\overline{\Omega}_\delta)$, respectively, be viscosity state-constraint solutions to 
+For $\delta >0$, we denote $u\in \rmC(\overline{\Omega})$ and $u_\delta\in \rmC(\overline{\Omega}_\delta)$, respectively, viscosity state-constraint solutions to 
 \begin{equation*}
@@
 \begin{equation}\label{e:bound_T}
-    \sup_{x\in \overline{\Omega}_\delta}\Big(|T(x)-x| + |DT(x) - \mathrm{Id}|\Big) \leq C\delta
+    \sup_{x\in \overline{\Omega}_\delta}\Big(|T(x)-x| + \big|DT(x) - \mathrm{Id}_{\overline{\Omega}_\delta}(x)\big|\Big) \leq C\delta
 \end{equation}
@@
 \noindent The main result is the following Theorem.
-\begin{thm}\label{thm:rate_doubling1} Let $\Omega$ be an open, bounded and connected subset $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary.
-Assume $\mathrm{(A1)},\mathrm{(H1)}-\mathrm{(H4)}$ and $1<p<2$.
-Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u^0$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that
-\begin{equation*}
-    0\leq u^\varepsilon(x) - u^0(x) \leq C\sqrt{\varepsilon} \qquad\text{for}\;x\in \Omega_{2\sqrt{\varepsilon}}.
+
+\begin{thm}\label{thm:rate_doubling0} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
+Assume that $H(x,\xi) = |\xi|^p - f(x)$ where $p\in\left(\frac{3}{2},2\right)$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ satisfying $f\geq 0$ in $\Omega$.
+Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that
+\begin{equation*}
+    0\leq u^\varepsilon(x) - u(x) \leq C\sqrt{\varepsilon} \qquad\text{for}\;x\in \Omega_{C\varepsilon^2}.
 \end{equation*}
 \end{thm}
-
-\begin{proof}[Proof of Theorem \ref{thm:rate_doubling1}] Let $u_\delta\in \mathrm{C}(\overline{\Omega}_\delta)$ be the state-constraint solution to
-\begin{equation}\label{e:PDE_delta}
-    \begin{cases}  
-    \lambda u_\delta(x) + H(x,Du_\delta(x)) \leq 0 \qquad\text{in}\; \Omega_\delta\\
-    \lambda u_\delta(x) + H(x,Du_\delta(x)) \geq 0 \qquad\text{on}\; \overline{\Omega}_\delta.
-    \end{cases} \tag{PDE$_\delta$}
-\end{equation} 
-Let $C_f$ be the Lipschitz constant of $f$ and $\beta,\sigma,\delta \in (0,1)$ to be chosen later.
-Recall the definition of $C_\varepsilon$ from Theorem \ref{thm:wellposed1<p<2}, we define the auxiliary functional
-\begin{align*}
-    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u_\delta(y) - \frac{C_0|x-y - \delta \nabla d(x)|^2}{\sigma}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}_\delta,
-\end{align*}
-where $C_0$ is the Lipschitz constant of $u^0$ (also the Lipschitz constant of $u_\delta$ for $\delta>0$). We split the proof into several steps.
+\begin{proof} As $f(x)\geq 0$ on $\Omega$, from Lemma \ref{lem:lower-bound} and Theorem \ref{thm:qual} we have 
+\begin{equation}\label{e:low}
+    u^\varepsilon(x) \geq u(x) \geq 0 \qquad\text{for all}\;x\in \Omega.
+\end{equation}
+From a priori estimate for $u$, we redefine the constant $C_0$ such that
+\begin{equation}\label{e:priori}
+    \sup_{x\in \overline{\Omega}} \left(\left| u(x)\right| + \left|Du(x)\right|\right) + \Vert \nabla f\Vert_{L^\infty(\Omega)} \leq C_0.
+\end{equation}
+We recall that
+\begin{equation}\label{e:behavior_ueps}
+    \lim_{d(x)\to 0^+} u^\varepsilon(x)d(x)^\alpha = C_\alpha \varepsilon^{\alpha+1} \qquad\text{where}\qquad \alpha = \frac{2-p}{p-1} \in (0,1) \quad\text{and}\quad C_\alpha := \frac{1}{\alpha}(\alpha+1)^{\alpha+1}.
+\end{equation}
+Let 
+\begin{equation*}
+    G = \left[\left(1+\frac{K_1\delta_0}{\alpha+1}\right)^{\alpha+1} - 1\right]C_\alpha 
+\end{equation*}
+then for $\eta = G\varepsilon^{\alpha+1}$, we have 
+\begin{equation*}
+    \mathcal{W}(x) = \frac{(C_\alpha+G)\varepsilon}{d(x)^\alpha} + \frac{M_\varepsilon}{\lambda}, \qquad x\in \Omega \qquad\text{where}\qquad M_\varepsilon = \sup_{\Omega} f + C\varepsilon^{\alpha+2}.
+\end{equation*}
+is a supersolution of \eqref{eq:PDEeps} in $\Omega$. Here $C$ depends only on $K,\alpha,\delta_0$. We therefore can assume $M_\varepsilon\leq \lambda M$ independent of $\varepsilon>0$. Let 
+\begin{equation*}
+    G_\alpha = \left(1+\frac{K\delta_0}{\alpha+1}\right)^{\alpha+1}C_\alpha
+\end{equation*}
+then 
+\begin{equation*}
+    u^\varepsilon(x) - \frac{G_\alpha\varepsilon^{\alpha+1}}{d(x)^\alpha} \leq M \qquad\text{for all}\; x\in \Omega.
+\end{equation*}
+As a consequence, for any $\delta>0$ we have
+\begin{equation*}
+    u^\varepsilon(x) - (1+\delta) \frac{G_\alpha \varepsilon^{\alpha+1}}{d(x)^{\alpha}} \leq  M - \delta\frac{G_\alpha \varepsilon^{\alpha+1}}{d(x)^{\alpha}}\leq 0 \qquad\text{if}\qquad d(x)< \left(\frac{\delta G_\alpha\varepsilon^{\alpha+1}}{M}\right)^{\frac{1}{\alpha}}.
+\end{equation*}
+Let $\delta,\theta,\sigma\in (0,1)$ to be chosen later. We define the following auxiliary functional
+\begin{equation*}
+    \Phi(x,y) =  u^\varepsilon(x) - u(y) - \frac{C_0|x-y|^2}{\sigma}- \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x)^{\alpha}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}.
+\end{equation*}
+We split the proof into several steps.
 \begin{enumerate}
-    \item[1.] Since $u^\varepsilon (x)d(x)^\alpha \to C_\varepsilon$ as $d(x)\to 0$, we see that $\Phi^\sigma(x,y)\to -\infty$ as $d(x)\to 0$, therefore for a fixed $\varepsilon>0$, there is $(x_{\sigma},y_\sigma)\in \Omega\times\overline{\Omega}_\delta$ such that
-\begin{equation*}
-    \max_{\overline{\Omega}\times \overline{\Omega}_\delta} \Phi^\sigma = \Phi^\sigma(x_\sigma,y_\sigma).
+    \item[1.] From \eqref{e:blows_up} we see that $\Phi^\sigma(x,y)\to -\infty$ as $d(x)\to 0$, thus for a fixed $\varepsilon>0$, there is $(x_{\sigma},y_\sigma)\in \Omega\times\overline{\Omega}$ such that
+    \begin{equation*}
+        \max_{\overline{\Omega}\times \overline{\Omega}} \Phi = \Phi(x_\sigma,y_\sigma).
     \end{equation*}
@@
     \end{equation}
+    so that $|Dd(x_\sigma)| = 1$. We will mention how the case $d(x_\sigma)\geq \delta_0$ can be easily deduced at the end of the proof.
+    \item[2.] From $\Phi(x_\sigma,y_\sigma)\geq \Phi(x_\sigma,x_\sigma)$ we have
+    \begin{align*}
+        & u^\varepsilon(x_\sigma) - u(y_\sigma) - \frac{C_0|x_\sigma-y_\sigma |^2}{\sigma}- \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}} \\
+        & \qquad\qquad\qquad\qquad \geq u^\varepsilon(x_\sigma) - u(x_\sigma) - \frac{C_0|x_\sigma-x_\sigma |^2}{\sigma}- \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}}.
+    \end{align*}
+    Therefore
+    \begin{equation*}
+        \frac{C_0|x_\sigma - y_\sigma|^2}{\sigma} \leq u(x_\sigma) - u(y_\sigma) \leq C_0|x_\sigma - y_\sigma|.
+    \end{equation*}
+    Thus we obtain that
+    \begin{equation*}
+        |x_\sigma - y_\sigma|\leq \sigma.
+    \end{equation*}
+    \item[3.] For any $z\in \partial\Omega_\theta$, i.e., $d(z) = \theta$ we have $\Phi(x_\sigma,y_\sigma)\geq \Phi(z,z)$, thus
+    \begin{align*}
+          & u^\varepsilon(x_\sigma) - u(y_\sigma) - \frac{C_0|x_\sigma-y_\sigma |^2}{\sigma}- \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}} \\
+        & \qquad\qquad\qquad\qquad \geq u^\varepsilon(z) - u(z) - \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{\theta^{\alpha}}.
+    \end{align*}
+    Using the fact that $u^\varepsilon(z) \geq u(z)$ and $0\geq -u(y_\sigma)$ we deduce that
+    \begin{align*}
+        \delta\left(\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}}\right) \leq \left(u^\varepsilon(x) - \left(1+\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}}\right) + \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{\theta^{\alpha}}.
+    \end{align*}
+\end{enumerate}
+\end{proof}
+
+\begin{thm}\label{thm:rate_doubling0} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
+Assume that $H(x,\xi) = |\xi|^p - f(x)$ where $p\in\left(\frac{3}{2},2\right)$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ satisfying
+\begin{equation*}
+    \inf_{\Omega} f \geq 0.
+\end{equation*}
+Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that
+\begin{equation*}
+    0\leq u^\varepsilon(x) - u(x) \leq C\sqrt{\varepsilon} \qquad\text{for}\;x\in \Omega_{C\varepsilon^2}.
+\end{equation*}
+\end{thm}
+\begin{proof} As $f(x)\geq 0$ on $\Omega$, from Lemma \ref{lem:lower-bound} and Theorem \ref{thm:qual} we have 
+\begin{equation}\label{e:low}
+    u^\varepsilon(x) \geq u(x) \geq 0 \qquad\text{for all}\;x\in \Omega.
+\end{equation}
+From a priori estimate for $u$, we redefine the constant $C_0$ such that
+\begin{equation}\label{e:priori}
+    \sup_{x\in \overline{\Omega}} \left(\left| u(x)\right| + \left|Du(x)\right|\right) + \Vert \nabla f\Vert_{L^\infty(\Omega)} \leq C_0.
+\end{equation}
+We recall from \cite{Lasry1989} that
+\begin{equation}\label{e:behavior_ueps}
+    \lim_{d(x)\to 0^+} u^\varepsilon(x)d(x)^\alpha = C_\alpha \varepsilon^{\alpha+1}.
+\end{equation}
+where 
+\begin{equation*}
+    \alpha = \frac{2-p}{p-1} \in (0,1) \qquad\text{and}\qquad C_\alpha := \frac{1}{\alpha}(\alpha+1)^{\alpha+1}.
+\end{equation*}
+We have $u^\varepsilon (x)d(x)^\alpha \to C_\varepsilon$ as $d(x)\to 0$.
+From \cite[Theorem II.3]{Lasry1989} we know further that when $\frac{3}{2} < p <2$ there exists a constant $M_{\alpha,\varepsilon}$ such that
+\begin{equation}\label{e:blows_up}
+    \sup_{x\in \Omega}\left|u^\varepsilon(x) - \frac{C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha}\right| \leq M_{\alpha,\varepsilon}
+\end{equation}
+As a consequence, for any $\delta>0$ we have
+\begin{equation*}
+    u^\varepsilon(x) - (1+\delta) \frac{C_\alpha \varepsilon^{\alpha+1}}{d(x)^{\alpha}} \leq  M_{\alpha,\varepsilon} - \delta\frac{C_\alpha \varepsilon^{\alpha+1}}{d(x)^{\alpha}}\leq 0 \qquad\text{if}\qquad d(x)< \left(\frac{\delta C_\alpha\varepsilon^{\alpha+1}}{M_{\alpha,\varepsilon}}\right)^{\frac{1}{\alpha}}.
+\end{equation*}
+Let $\delta,\theta,\sigma\in (0,1)$ to be chosen later. We define the following auxiliary functional
+\begin{equation*}
+    \Phi(x,y) =  u^\varepsilon(x) - u(y) - \frac{C_0|x-y|^2}{\sigma}- \left(1+\delta\right)\frac{C_\alpha\varepsilon^{\alpha+1}}{d(x)^{\alpha}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}.
+\end{equation*}
+We split the proof into several steps.
+\begin{enumerate}
+    \item[1.] From \eqref{e:blows_up} we see that $\Phi^\sigma(x,y)\to -\infty$ as $d(x)\to 0$, thus for a fixed $\varepsilon>0$, there is $(x_{\sigma},y_\sigma)\in \Omega\times\overline{\Omega}$ such that
+    \begin{equation*}
+        \max_{\overline{\Omega}\times \overline{\Omega}} \Phi = \Phi(x_\sigma,y_\sigma).
+    \end{equation*}
+    We can assume that 
+    \begin{equation}\label{e:ass_delta0}
+        d(x_\sigma) < \delta_0
+    \end{equation}
+    so that $|Dd(x_\sigma)| = 1$. We will mention how the case $d(x_\sigma)\geq \delta_0$ can be easily deduced at the end of the proof.
+    \item[2.] From $\Phi(x_\sigma,y_\sigma)\geq \Phi(x_\sigma,x_\sigma)$ we have
+    \begin{align*}
+        & u^\varepsilon(x_\sigma) - u(y_\sigma) - \frac{C_0|x_\sigma-y_\sigma |^2}{\sigma}- \left(1+\delta\right)\frac{C_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}} \\
+        & \qquad\qquad\qquad\qquad \geq u^\varepsilon(x_\sigma) - u(x_\sigma) - \frac{C_0|x_\sigma-x_\sigma |^2}{\sigma}- \left(1+\delta\right)\frac{C_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}}.
+    \end{align*}
+    Therefore
+    \begin{equation*}
+        \frac{C_0|x_\sigma - y_\sigma|^2}{\sigma} \leq u(x_\sigma) - u(y_\sigma) \leq C_0|x_\sigma - y_\sigma|.
+    \end{equation*}
+    Thus we obtain that
+    \begin{equation*}
+        |x_\sigma - y_\sigma|\leq \sigma.
+    \end{equation*}
+\end{enumerate}
+\end{proof}
+
+\begin{thm}\label{thm:rate_doubling1} Let $\Omega = B(0,1)$ be the open unit ball in $\mathbb{R}^n$.
+Assume $\mathrm{(A1)},\mathrm{(H1)}-\mathrm{(H4)}$ and also $\frac{3}{2}<p<2$ so that $\alpha = \frac{2-p}{p-1} \in (0,1)$.
+Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that
+\begin{equation*}
+    0\leq u^\varepsilon(x) - u(x) \leq C\sqrt{\varepsilon} \qquad\text{for}\;x\in \Omega_{2\sqrt{\varepsilon}}.
+\end{equation*}
+
+\end{thm}
+
+\begin{proof}[Proof of Theorem \ref{thm:rate_doubling1}] Let $C_f$ be the Lipschitz constant of $f$ and $\beta,\sigma \in (0,1)$ to be chosen later.
+Recall the definition of $C_\varepsilon$ from Theorem \ref{thm:wellposed1<p<2} and a priori estimates
+\begin{equation}\label{e:priori}
+    \sup_{x\in \overline{\Omega}} \left(|u(x)| + |Du(x)|\right) \leq C_0 \qquad\text{and}\qquad |\nabla u^\varepsilon(x)| \leq \frac{\theta C_\varepsilon \alpha}{d(x)^{\alpha+1}} \qquad\text{for all}\;\theta > 1, x\in \Omega.
+\end{equation}
+We define the auxiliary functional
+\begin{align*}
+    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u(y) - \frac{C_\varepsilon|x-y |^2}{\sigma}- \frac{C_\varepsilon}{d(x)^{\alpha+1}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}
+    .
+\end{align*}
+We split the proof into several steps.
+\begin{enumerate}
+    \item[1.] Since $u^\varepsilon (x)d(x)^\alpha \to C_\varepsilon$ as $d(x)\to 0$, we see that $\Phi^\sigma(x,y)\to -\infty$ as $d(x)\to 0$, therefore for a fixed $\varepsilon>0$, there is $(x_{\sigma},y_\sigma)\in \Omega\times\overline{\Omega}$ such that
+    \begin{equation*}
+        \max_{\overline{\Omega}\times \overline{\Omega}} \Phi^\sigma = \Phi^\sigma(x_\sigma,y_\sigma).
+    \end{equation*}
+    We can assume that 
+    \begin{equation}\label{e:ass_delta0}
+        d(x_\sigma) < \delta_0
+    \end{equation}
     so that $|Dd(x_\sigma)| = 1$. We will mention how the case $d(x_\sigma)\geq \delta_0$ is easily deduced at the end of the proof.
-\item[2.] $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(x_\sigma,x_\sigma)$ gives us that
-    \begin{equation}\label{e:est_sigma2}
-     \frac{C_0|x_\sigma-y_\sigma|^2}{\sigma} \leq u_\delta(x_\sigma) - u_\delta(y_\sigma) \leq C_0|x_\sigma-y_\sigma| \qquad\Longrightarrow\qquad |x_\sigma -y _\sigma|\leq \sigma.
-    \end{equation}
-    This gives us that
-    \begin{equation}\label{e:est_sigma3}
-        d(x_\sigma) \geq d(y_\sigma) - |x_\sigma-y_\sigma|\geq \delta-\sigma.
-    \end{equation}
-    Let $\delta = 2\sigma$, we deduce that $d(x_\sigma)\geq \sigma$.
-    \item[3.] $x\mapsto \Phi^\sigma(x,y_\sigma)$ has a maximum at $x_\sigma\in \Omega$, thus by subsolution test for \eqref{eq:PDEeps} we have
+    \item[2.] As $\Phi^\sigma(x_\sigma,y_\sigma)\geq \Phi^\sigma(0,y_\sigma)$, we have
+    \begin{align*}
+        u^\varepsilon(x_\sigma) - u(y_\sigma) - \frac{C_\varepsilon |x_\sigma-y_\sigma|^2}{\sigma} - \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+1}} \geq u^\varepsilon(0) - u(y_\sigma) - \frac{C_\varepsilon |y_\sigma|^2}{\sigma} - C_\varepsilon.
+    \end{align*}
+    Therefore
+    \begin{align*}
+        \frac{C_\varepsilon |x_\sigma-y_\sigma|^2}{\sigma} + \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+1}} 
+        &\leq u^\varepsilon(x_\sigma) - u^\varepsilon(0) + \frac{C_\varepsilon }{\sigma} +C_\varepsilon.
+    \end{align*}
+    Let $\theta>1$ be a constant such that $\theta\alpha < 1$. Using \eqref{e:priori} we have
+    \begin{equation*}
+        \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+1}} \leq  \frac{\theta C_\varepsilon \alpha|x_\sigma|}{d(x_\sigma)^{\alpha+1}} + \frac{C_\varepsilon}{\sigma}+ C_\varepsilon \leq \frac{\theta \alpha C_\varepsilon}{d(x_\sigma)^{\alpha+1}} + \frac{C_\varepsilon}{\sigma} + C_\varepsilon
+    \end{equation*}
+    since $|x_\sigma| < 1$. We deduce that 
+    \begin{align*}
+       \sigma (1-\theta \alpha)\left(\frac{1}{d(x_\sigma)}\right)^{\alpha+1} \leq \sigma + 1
+    \end{align*}
+    and therefore\footnote{We recall again that by definition $\frac{1}{\alpha+1} = p-1 \in \left(\frac{1}{2},1\right)$.}
+    \begin{equation}\label{e:d(x_sigma)}
+        d(x_\sigma) \geq \left[\left(\frac{1-\theta\alpha}{\sigma+1}\right)\sigma\right]^{\frac{1}{\alpha+1}}.
+    \end{equation}
+    \item[3.] As $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(x_\sigma,x_\sigma)$, we have
+    \begin{equation*}
+         u^\varepsilon(x_\sigma) - u(y_\sigma) - \frac{C_\varepsilon |x_\sigma-y_\sigma|^2}{\sigma} - \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+1}} \geq u^\varepsilon(x_\sigma) - u(x_\sigma) - \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+1}}.
+    \end{equation*}
+    Therefore
+    \begin{equation*}
+        \frac{C_\varepsilon |x_\sigma-y_\sigma|^2}{\sigma} \leq u(x_\sigma) - u(y_\sigma) \leq C_0|x_\sigma-y_\sigma|
+    \end{equation*}
+    thus
+    \begin{equation}\label{e:bdd_xi}
+        \frac{2C_\varepsilon|x_\sigma - y_\sigma|}{\sigma} \leq 2C_0
+    \end{equation}
+    and 
+    \begin{equation}\label{e:bd|x-y|}
+        |x_\sigma - y_\sigma| \leq \left(\frac{C_0 \alpha}{(\alpha+1)^{\alpha+1}}\right) \frac{\sigma}{\varepsilon^{\alpha+1}}.
+    \end{equation}
+    \item[3.] Let $\beta > 0$, we let 
+    \begin{equation}\label{e:scale}
+        \sigma = \varepsilon^{(\beta+1)(\alpha+1)}
+    \end{equation}
+    then \eqref{e:d(x_sigma)} and \eqref{e:bd|x-y|} become
+    \begin{equation}
+        d(x_\sigma) \geq \left(\frac{1-\theta\alpha}{\sigma+1}\right)^{p-1}
+    \end{equation}
+    \item[3.] $x\mapsto \Phi^\sigma(x,y_\sigma)$ has a maximum at $x_\sigma\in \Omega$, i.e.,
+    \begin{equation*}
+        u^\varepsilon(x) - \left(\frac{C_0|(1+\delta)x-y_\sigma|^2}{2\sigma^2} + \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}\right)
+    \end{equation*}
+    has a maximum at $x_\sigma\in \Omega$. By subsolution test for \eqref{eq:PDEeps} we have
 \begin{align}\label{e:sub1}
-    &\lambda u^\varepsilon(x_\sigma) + \left|\frac{2C_0(x_\sigma-y_\sigma)}{\sigma} - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma )\right|^p - f(x_\sigma)\nonumber\\
-    &\qquad\qquad -\varepsilon\left(\frac{2n}{\sigma} + \frac{C_\varepsilon(\alpha+\beta)(\alpha+\beta+1)|D d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+\beta+2}}-\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\Delta d(x_\sigma)\right)  \leq 0.
+    &\lambda u^\varepsilon(x_\sigma) + \left|\xi_\sigma+\zeta_\sigma\right|^p - f(x_\sigma)\nonumber\\
+    &\quad  -\varepsilon\left(\frac{2n}{\sigma} + \frac{C_\varepsilon(\alpha+\beta)(\alpha+\beta+1)|D d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+\beta+2}}-\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\Delta d(x_\sigma)\right)  \leq 0
 \end{align}
-\item[4.] Let
+where 
 \begin{equation}\label{e:est_xi_zeta}
-    \xi_\sigma = \frac{2C_0(x_\sigma-y_\sigma)}{\sigma} \qquad\text{and}\qquad \zeta_\sigma = - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma)
-\end{equation}
-then $|\xi_\sigma|\leq 2C_0$ by \eqref{e:est_sigma2} and furthermore $\xi_\sigma+\zeta_\sigma \in D^-u^\varepsilon(x_\sigma)$, which, by the local gradient estimate, as $x_\sigma\in \Omega_{\sigma}$, $\xi_\sigma+\zeta_\sigma$ is bounded in terms of $\sigma$ and will blow up as $\sigma\to 0$.
-Nevertheless, we can do better as following.
-\begin{align*}
-    |\zeta_\sigma|=\left|\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma )\right| \leq \frac{C_\varepsilon(\alpha+\beta)}{\sigma^{\alpha+\beta+1}} 
+    \xi_\sigma = \frac{C_0\big((1+\delta)x_\sigma-y_\sigma\big)}{\sigma^2} \qquad\text{and}\qquad \zeta_\sigma = - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma).
+\end{equation}
+We have the following estimates
+\begin{align*}
+    |\zeta_\sigma|=\left|\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma )\right|
+    &\leq \frac{C_\varepsilon(\alpha+\beta)}{\sigma^{\alpha+\beta+1}} \\
     &\leq \frac{(\alpha+\beta)(\alpha+1)^{\alpha+1}}{\alpha} \frac{\varepsilon^{\alpha+1}}{\sigma^{\alpha+\beta+1}} \\
@@
 \begin{equation}\label{e:citepaper}
-    0\leq \lambda u_\delta(x) - \lambda u^0(x)\leq C_H\delta \qquad\text{for all}\; x\in \overline{\Omega}_\delta
+    0\leq \lambda u_\delta(x) - \lambda u(x)\leq C_H\delta \qquad\text{for all}\; x\in \overline{\Omega}_\delta
 \end{equation}
@@
 \begin{align*}
-    0 \leq \lambda u^\varepsilon(x) - \lambda u^0(x) \leq \left(K_5 + 2C_H\right)\sqrt{\varepsilon} \qquad\text{for all}\; x\in \overline{\Omega}_{2\sqrt{\varepsilon}}.
+    0 \leq \lambda u^\varepsilon(x) - \lambda u(x) \leq \left(K_5 + 2C_H\right)\sqrt{\varepsilon} \qquad\text{for all}\; x\in \overline{\Omega}_{2\sqrt{\varepsilon}}.
 \end{align*}
@@
 
-\begin{lem}\label{lem:subsln} For each $<\delta < \frac{1}{2}\delta_0$, if $\eta\geq G\varepsilon^{\alpha+1}$, we have
+\begin{lem}\label{lem:subsln} For each $\delta > 0$ such that $0<2\delta < \delta_0$, if $\eta\geq G\varepsilon^{\alpha+1}$ then
 \begin{equation*}
@@
 \begin{equation*}
-\frac{\overline{u}(x)}{\underline{u}(x)}\leq (1+\varsigma)     \qquad\Longrightarrow\qquad \frac{1}{1+\varsigma} \overline{u}(x) \leq \underline{u}(x) \qquad\text{in}\; \Omega\backslash \Omega_\delta
+\frac{\overline{u}(x)}{\underline{u}(x)}\leq (1+\varsigma)     \qquad\Longrightarrow\qquad \left(\frac{1}{1+\varsigma}\right)\overline{u}(x) \leq \underline{u}(x) \qquad\text{in}\; \Omega\backslash \Omega_\delta
 \end{equation*}
@@
 \noindent This finishes the well-posedness of \eqref{eq:PDEeps} for $1<p<2$.
+\end{proof}
+
+\begin{thm}[Asymptotic expansions near the boundary] Assume $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
+Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ be the unique solution to \eqref{eq:PDEeps}, then, if $p\in \left(\frac{3}{2},2\right)$ then
+\begin{equation*}
+    \sup_{x\in \Omega}\left|u^\varepsilon(x) - \frac{C_\alpha\varepsilon^{\alpha+1}}{d(x)^\alpha} \right| \leq C.
+\end{equation*}
+\end{thm}
+\begin{proof} Previously, we look for subsolution and supersolution in the form of the ansatz
+\begin{equation*}
+    u(x)\approx \frac{C_\varepsilon}{d(x)^\alpha}
+\end{equation*}
+to find that $C_\varepsilon = C_\alpha\varepsilon^{\alpha+1}$. Now we go further to higher order terms by using the following ansatz
+\begin{equation*}
+    u(x)\approx \frac{C_\varepsilon}{d(x)^\alpha} - C_1(x)d(x)^{1-\alpha}.
+\end{equation*}
+As $p\in \left(\frac{3}{2},2\right)$, we have $\alpha\in (0,1)$. For $\eta > 0$ let us define
+\begin{align*}
+    w^+_{\eta}(x) = \frac{C_\alpha \varepsilon^{\alpha+1}}{d(x)^{\alpha}} - \big(C_1(x)+\eta\big)d(x)^{1-\alpha} + C_\eta, &\qquad x\in \Omega\\
+    w^-_{\eta}(x) = \frac{C_\alpha \varepsilon^{\alpha+1}}{d(x)^{\alpha}} - \big(C_1(x)-\eta\big)d(x)^{1-\alpha} - C_\eta, &\qquad x\in \Omega.
+\end{align*}
+We look for $C_\eta$ so that $w^+_{\eta}(x)$ is a supersolution and $w^-_\eta$ is a subsolution with blowing up boundary of \eqref{eq:PDEeps}.
 \end{proof}

### 2021-04-06 Drafts and notes/Notes/old_draft_2.tex
Major change

--- 2021-04-06 Drafts and notes/Notes/old_draft.tex
@@
 \section{Rate of convergence via the doubling variables method}
-\noindent The main result is the following Theorem.
 
 \begin{thm}\label{thm:rate_doubling0} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
-Assume that $H(x,\xi) = |\xi|^p - f(x)$ where $p\in\left(\frac{3}{2},2\right)$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ satisfying $f\geq 0$ in $\Omega$.
+Assume that $H(x,\xi) = |\xi|^p - f(x)$ where $p\in\left(1,2\right)$ and $f\equiv 0$ in $\Omega$.
 Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that
@@
 \end{thm}
+\color{blue}
+This assumption $f\equiv 0$ effectively renders our theorem useless, since it is radical, it can be reduced to a one dimensional problem (probably uninteresting result).
+\color{black}
 \begin{proof} As $f(x)\geq 0$ on $\Omega$, from Lemma \ref{lem:lower-bound} and Theorem \ref{thm:qual} we have 
@@
 \begin{equation}\label{e:priori}
-    \sup_{x\in \overline{\Omega}} \left(\left| u(x)\right| + \left|Du(x)\right|\right) + \Vert \nabla f\Vert_{L^\infty(\Omega)} \leq C_0.
+    \sup_{x\in \overline{\Omega}} \left(\left| u(x)\right| + \left|Du(x)\right|\right)  \leq C_0.
 \end{equation}
@@
 \begin{equation}\label{e:behavior_ueps}
-    \lim_{d(x)\to 0^+} u^\varepsilon(x)d(x)^\alpha = C_\alpha \varepsilon^{\alpha+1} \qquad\text{where}\qquad \alpha = \frac{2-p}{p-1} \in (0,1) \quad\text{and}\quad C_\alpha := \frac{1}{\alpha}(\alpha+1)^{\alpha+1}.
+    \lim_{d(x)\to 0^+} u^\varepsilon(x)d(x)^\alpha = C_\alpha \varepsilon^{\alpha+1} \qquad\text{where}\qquad \alpha = \frac{2-p}{p-1} \quad\text{and}\quad C_\alpha := \frac{1}{\alpha}(\alpha+1)^{\alpha+1}.
 \end{equation}
@@
 \begin{equation*}
-    G = \left[\left(1+\frac{K_1\delta_0}{\alpha+1}\right)^{\alpha+1} - 1\right]C_\alpha 
-\end{equation*}
-then for $\eta = G\varepsilon^{\alpha+1}$, we have 
-\begin{equation*}
-    \mathcal{W}(x) = \frac{(C_\alpha+G)\varepsilon}{d(x)^\alpha} + \frac{M_\varepsilon}{\lambda}, \qquad x\in \Omega \qquad\text{where}\qquad M_\varepsilon = \sup_{\Omega} f + C\varepsilon^{\alpha+2}.
-\end{equation*}
-is a supersolution of \eqref{eq:PDEeps} in $\Omega$. Here $C$ depends only on $K,\alpha,\delta_0$. We therefore can assume $M_\varepsilon\leq \lambda M$ independent of $\varepsilon>0$. Let 
-\begin{equation*}
     G_\alpha = \left(1+\frac{K\delta_0}{\alpha+1}\right)^{\alpha+1}C_\alpha
 \end{equation*}
-then 
-\begin{equation*}
-    u^\varepsilon(x) - \frac{G_\alpha\varepsilon^{\alpha+1}}{d(x)^\alpha} \leq M \qquad\text{for all}\; x\in \Omega.
+then by Lemma \ref{lem:subsln}
+\begin{equation*}
+    u^\varepsilon(x) - \frac{G_\alpha\varepsilon^{\alpha+1}}{d(x)^\alpha} \leq M_\alpha\varepsilon^{\alpha+2} \qquad\text{for all}\; x\in \Omega.
 \end{equation*}
@@
 \begin{equation*}
-    u^\varepsilon(x) - (1+\delta) \frac{G_\alpha \varepsilon^{\alpha+1}}{d(x)^{\alpha}} \leq  M - \delta\frac{G_\alpha \varepsilon^{\alpha+1}}{d(x)^{\alpha}}\leq 0 \qquad\text{if}\qquad d(x)< \left(\frac{\delta G_\alpha\varepsilon^{\alpha+1}}{M}\right)^{\frac{1}{\alpha}}.
+    u^\varepsilon(x) - (1+\delta) \frac{G_\alpha \varepsilon^{\alpha+1}}{d(x)^{\alpha}} \leq  M_\alpha\varepsilon^{\alpha+2} - \delta\frac{G_\alpha \varepsilon^{\alpha+1}}{d(x)^{\alpha}}\leq 0 \qquad\text{if}\qquad d(x)< \left(\frac{\delta G_\alpha\varepsilon^{\alpha+1}}{M}\right)^{\frac{1}{\alpha}}.
 \end{equation*}
@@
 \begin{equation*}
-    \Phi(x,y) =  u^\varepsilon(x) - u(y) - \frac{C_0|x-y|^2}{\sigma}- \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x)^{\alpha}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}.
+    \Phi(x,y) =  u^\varepsilon(x) - u(y) - \frac{C_0|x-y|^2}{\sigma}- \left(1+\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x)^{\alpha}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}.
 \end{equation*}
@@
     \begin{align*}
-        & u^\varepsilon(x_\sigma) - u(y_\sigma) - \frac{C_0|x_\sigma-y_\sigma |^2}{\sigma}- \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}} \\
-        & \qquad\qquad\qquad\qquad \geq u^\varepsilon(x_\sigma) - u(x_\sigma) - \frac{C_0|x_\sigma-x_\sigma |^2}{\sigma}- \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}}.
+        & u^\varepsilon(x_\sigma) - u(y_\sigma) - \frac{C_0|x_\sigma-y_\sigma |^2}{\sigma}- \left(1+\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}} \\
+        & \qquad\qquad\qquad\qquad \geq u^\varepsilon(x_\sigma) - u(x_\sigma) - \frac{C_0|x_\sigma-x_\sigma |^2}{\sigma}- \left(1+\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}}.
     \end{align*}
@@
     \begin{align*}
-          & u^\varepsilon(x_\sigma) - u(y_\sigma) - \frac{C_0|x_\sigma-y_\sigma |^2}{\sigma}- \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}} \\
-        & \qquad\qquad\qquad\qquad \geq u^\varepsilon(z) - u(z) - \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{\theta^{\alpha}}.
+          & u^\varepsilon(x_\sigma) - u(y_\sigma) - \frac{C_0|x_\sigma-y_\sigma |^2}{\sigma}- \left(1+\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}} \\
+        & \qquad\qquad\qquad\qquad \geq u^\varepsilon(z) - u(z) - \left(1+\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{\theta^{\alpha}}.
     \end{align*}
@@
     \begin{align*}
-        \delta\left(\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}}\right) \leq \left(u^\varepsilon(x) - \left(1+\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}}\right) + \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{\theta^{\alpha}}.
-    \end{align*}
-\end{enumerate}
-\end{proof}
-
-\begin{thm}\label{thm:rate_doubling0} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
-Assume that $H(x,\xi) = |\xi|^p - f(x)$ where $p\in\left(\frac{3}{2},2\right)$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ satisfying
-\begin{equation*}
-    \inf_{\Omega} f \geq 0.
-\end{equation*}
-Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that
-\begin{equation*}
-    0\leq u^\varepsilon(x) - u(x) \leq C\sqrt{\varepsilon} \qquad\text{for}\;x\in \Omega_{C\varepsilon^2}.
-\end{equation*}
-\end{thm}
-\begin{proof} As $f(x)\geq 0$ on $\Omega$, from Lemma \ref{lem:lower-bound} and Theorem \ref{thm:qual} we have 
-\begin{equation}\label{e:low}
-    u^\varepsilon(x) \geq u(x) \geq 0 \qquad\text{for all}\;x\in \Omega.
-\end{equation}
-From a priori estimate for $u$, we redefine the constant $C_0$ such that
-\begin{equation}\label{e:priori}
-    \sup_{x\in \overline{\Omega}} \left(\left| u(x)\right| + \left|Du(x)\right|\right) + \Vert \nabla f\Vert_{L^\infty(\Omega)} \leq C_0.
-\end{equation}
-We recall from \cite{Lasry1989} that
-\begin{equation}\label{e:behavior_ueps}
-    \lim_{d(x)\to 0^+} u^\varepsilon(x)d(x)^\alpha = C_\alpha \varepsilon^{\alpha+1}.
-\end{equation}
-where 
-\begin{equation*}
-    \alpha = \frac{2-p}{p-1} \in (0,1) \qquad\text{and}\qquad C_\alpha := \frac{1}{\alpha}(\alpha+1)^{\alpha+1}.
-\end{equation*}
-We have $u^\varepsilon (x)d(x)^\alpha \to C_\varepsilon$ as $d(x)\to 0$.
-From \cite[Theorem II.3]{Lasry1989} we know further that when $\frac{3}{2} < p <2$ there exists a constant $M_{\alpha,\varepsilon}$ such that
-\begin{equation}\label{e:blows_up}
-    \sup_{x\in \Omega}\left|u^\varepsilon(x) - \frac{C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha}\right| \leq M_{\alpha,\varepsilon}
-\end{equation}
-As a consequence, for any $\delta>0$ we have
-\begin{equation*}
-    u^\varepsilon(x) - (1+\delta) \frac{C_\alpha \varepsilon^{\alpha+1}}{d(x)^{\alpha}} \leq  M_{\alpha,\varepsilon} - \delta\frac{C_\alpha \varepsilon^{\alpha+1}}{d(x)^{\alpha}}\leq 0 \qquad\text{if}\qquad d(x)< \left(\frac{\delta C_\alpha\varepsilon^{\alpha+1}}{M_{\alpha,\varepsilon}}\right)^{\frac{1}{\alpha}}.
-\end{equation*}
-Let $\delta,\theta,\sigma\in (0,1)$ to be chosen later. We define the following auxiliary functional
-\begin{equation*}
-    \Phi(x,y) =  u^\varepsilon(x) - u(y) - \frac{C_0|x-y|^2}{\sigma}- \left(1+\delta\right)\frac{C_\alpha\varepsilon^{\alpha+1}}{d(x)^{\alpha}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}.
-\end{equation*}
-We split the proof into several steps.
-\begin{enumerate}
-    \item[1.] From \eqref{e:blows_up} we see that $\Phi^\sigma(x,y)\to -\infty$ as $d(x)\to 0$, thus for a fixed $\varepsilon>0$, there is $(x_{\sigma},y_\sigma)\in \Omega\times\overline{\Omega}$ such that
-    \begin{equation*}
-        \max_{\overline{\Omega}\times \overline{\Omega}} \Phi = \Phi(x_\sigma,y_\sigma).
-    \end{equation*}
-    We can assume that 
-    \begin{equation}\label{e:ass_delta0}
-        d(x_\sigma) < \delta_0
-    \end{equation}
-    so that $|Dd(x_\sigma)| = 1$. We will mention how the case $d(x_\sigma)\geq \delta_0$ can be easily deduced at the end of the proof.
-    \item[2.] From $\Phi(x_\sigma,y_\sigma)\geq \Phi(x_\sigma,x_\sigma)$ we have
-    \begin{align*}
-        & u^\varepsilon(x_\sigma) - u(y_\sigma) - \frac{C_0|x_\sigma-y_\sigma |^2}{\sigma}- \left(1+\delta\right)\frac{C_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}} \\
-        & \qquad\qquad\qquad\qquad \geq u^\varepsilon(x_\sigma) - u(x_\sigma) - \frac{C_0|x_\sigma-x_\sigma |^2}{\sigma}- \left(1+\delta\right)\frac{C_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}}.
-    \end{align*}
-    Therefore
-    \begin{equation*}
-        \frac{C_0|x_\sigma - y_\sigma|^2}{\sigma} \leq u(x_\sigma) - u(y_\sigma) \leq C_0|x_\sigma - y_\sigma|.
-    \end{equation*}
-    Thus we obtain that
-    \begin{equation*}
-        |x_\sigma - y_\sigma|\leq \sigma.
-    \end{equation*}
-\end{enumerate}
-\end{proof}
-
-\begin{thm}\label{thm:rate_doubling1} Let $\Omega = B(0,1)$ be the open unit ball in $\mathbb{R}^n$.
-Assume $\mathrm{(A1)},\mathrm{(H1)}-\mathrm{(H4)}$ and also $\frac{3}{2}<p<2$ so that $\alpha = \frac{2-p}{p-1} \in (0,1)$.
-Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that
-\begin{equation*}
-    0\leq u^\varepsilon(x) - u(x) \leq C\sqrt{\varepsilon} \qquad\text{for}\;x\in \Omega_{2\sqrt{\varepsilon}}.
-\end{equation*}
-
-\end{thm}
-
-\begin{proof}[Proof of Theorem \ref{thm:rate_doubling1}] Let $C_f$ be the Lipschitz constant of $f$ and $\beta,\sigma \in (0,1)$ to be chosen later.
-Recall the definition of $C_\varepsilon$ from Theorem \ref{thm:wellposed1<p<2} and a priori estimates
-\begin{equation}\label{e:priori}
-    \sup_{x\in \overline{\Omega}} \left(|u(x)| + |Du(x)|\right) \leq C_0 \qquad\text{and}\qquad |\nabla u^\varepsilon(x)| \leq \frac{\theta C_\varepsilon \alpha}{d(x)^{\alpha+1}} \qquad\text{for all}\;\theta > 1, x\in \Omega.
-\end{equation}
-We define the auxiliary functional
-\begin{align*}
-    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u(y) - \frac{C_\varepsilon|x-y |^2}{\sigma}- \frac{C_\varepsilon}{d(x)^{\alpha+1}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}
-    .
-\end{align*}
-We split the proof into several steps.
-\begin{enumerate}
-    \item[1.] Since $u^\varepsilon (x)d(x)^\alpha \to C_\varepsilon$ as $d(x)\to 0$, we see that $\Phi^\sigma(x,y)\to -\infty$ as $d(x)\to 0$, therefore for a fixed $\varepsilon>0$, there is $(x_{\sigma},y_\sigma)\in \Omega\times\overline{\Omega}$ such that
-    \begin{equation*}
-        \max_{\overline{\Omega}\times \overline{\Omega}} \Phi^\sigma = \Phi^\sigma(x_\sigma,y_\sigma).
-    \end{equation*}
-    We can assume that 
-    \begin{equation}\label{e:ass_delta0}
-        d(x_\sigma) < \delta_0
-    \end{equation}
-    so that $|Dd(x_\sigma)| = 1$. We will mention how the case $d(x_\sigma)\geq \delta_0$ is easily deduced at the end of the proof.
-    \item[2.] As $\Phi^\sigma(x_\sigma,y_\sigma)\geq \Phi^\sigma(0,y_\sigma)$, we have
-    \begin{align*}
-        u^\varepsilon(x_\sigma) - u(y_\sigma) - \frac{C_\varepsilon |x_\sigma-y_\sigma|^2}{\sigma} - \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+1}} \geq u^\varepsilon(0) - u(y_\sigma) - \frac{C_\varepsilon |y_\sigma|^2}{\sigma} - C_\varepsilon.
-    \end{align*}
-    Therefore
-    \begin{align*}
-        \frac{C_\varepsilon |x_\sigma-y_\sigma|^2}{\sigma} + \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+1}} 
-        &\leq u^\varepsilon(x_\sigma) - u^\varepsilon(0) + \frac{C_\varepsilon }{\sigma} +C_\varepsilon.
-    \end{align*}
-    Let $\theta>1$ be a constant such that $\theta\alpha < 1$. Using \eqref{e:priori} we have
-    \begin{equation*}
-        \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+1}} \leq  \frac{\theta C_\varepsilon \alpha|x_\sigma|}{d(x_\sigma)^{\alpha+1}} + \frac{C_\varepsilon}{\sigma}+ C_\varepsilon \leq \frac{\theta \alpha C_\varepsilon}{d(x_\sigma)^{\alpha+1}} + \frac{C_\varepsilon}{\sigma} + C_\varepsilon
-    \end{equation*}
-    since $|x_\sigma| < 1$. We deduce that 
-    \begin{align*}
-       \sigma (1-\theta \alpha)\left(\frac{1}{d(x_\sigma)}\right)^{\alpha+1} \leq \sigma + 1
-    \end{align*}
-    and therefore\footnote{We recall again that by definition $\frac{1}{\alpha+1} = p-1 \in \left(\frac{1}{2},1\right)$.}
-    \begin{equation}\label{e:d(x_sigma)}
-        d(x_\sigma) \geq \left[\left(\frac{1-\theta\alpha}{\sigma+1}\right)\sigma\right]^{\frac{1}{\alpha+1}}.
-    \end{equation}
-    \item[3.] As $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(x_\sigma,x_\sigma)$, we have
-    \begin{equation*}
-         u^\varepsilon(x_\sigma) - u(y_\sigma) - \frac{C_\varepsilon |x_\sigma-y_\sigma|^2}{\sigma} - \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+1}} \geq u^\varepsilon(x_\sigma) - u(x_\sigma) - \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+1}}.
-    \end{equation*}
-    Therefore
-    \begin{equation*}
-        \frac{C_\varepsilon |x_\sigma-y_\sigma|^2}{\sigma} \leq u(x_\sigma) - u(y_\sigma) \leq C_0|x_\sigma-y_\sigma|
-    \end{equation*}
-    thus
-    \begin{equation}\label{e:bdd_xi}
-        \frac{2C_\varepsilon|x_\sigma - y_\sigma|}{\sigma} \leq 2C_0
-    \end{equation}
-    and 
-    \begin{equation}\label{e:bd|x-y|}
-        |x_\sigma - y_\sigma| \leq \left(\frac{C_0 \alpha}{(\alpha+1)^{\alpha+1}}\right) \frac{\sigma}{\varepsilon^{\alpha+1}}.
-    \end{equation}
-    \item[3.] Let $\beta > 0$, we let 
-    \begin{equation}\label{e:scale}
-        \sigma = \varepsilon^{(\beta+1)(\alpha+1)}
-    \end{equation}
-    then \eqref{e:d(x_sigma)} and \eqref{e:bd|x-y|} become
-    \begin{equation}
-        d(x_\sigma) \geq \left(\frac{1-\theta\alpha}{\sigma+1}\right)^{p-1}
-    \end{equation}
+        \delta\left(\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}}\right) &\leq \left(u^\varepsilon(x) - \frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}}\right) + \left(1+\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{\theta^{\alpha}}\\
+        &\leq M_\alpha\varepsilon^{\alpha+2} + \left(1+\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{\theta^{\alpha}}.
+    \end{align*}
+    Therefore, using $1+\delta\leq 2$
+    \begin{equation*}
+        \frac{1}{d(x_\sigma)^\alpha}\leq \left(\frac{G_\alpha}{M_\alpha}\right) \frac{\varepsilon}{\delta} + \frac{2G_\alpha}{\delta\theta^\alpha}  .
+    \end{equation*}
+    Choose $\delta = \varepsilon^\beta$ for $0<\beta<1$ then 
+    \begin{equation*}
+        \frac{1}{d(x_\sigma)^\alpha} \leq \frac{C}{\delta\theta^\alpha} \qquad\Longrightarrow\qquad    d(x_\sigma)\geq C\theta \delta^{\frac{1}{\alpha}} = C\theta\varepsilon^{\frac{\beta}{\alpha}}.
+    \end{equation*}
      \item[3.] $x\mapsto \Phi^\sigma(x,y_\sigma)$ has a maximum at $x_\sigma\in \Omega$, i.e.,
@@
 In particular, $|\zeta_\sigma|\leq \mathfrak{C}_\alpha$ where $\mathfrak{C}_\alpha = \alpha^{-1}(\alpha+\beta)(\alpha+1)^{\alpha+1}$.
+\end{enumerate}
+\end{proof}
+
+\begin{thm}\label{thm:rate_doubling0} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
+Assume that $H(x,\xi) = |\xi|^p - f(x)$ where $p\in\left(\frac{3}{2},2\right)$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ satisfying
+\begin{equation*}
+    \inf_{\Omega} f \geq 0.
+\end{equation*}
+Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that
+\begin{equation*}
+    0\leq u^\varepsilon(x) - u(x) \leq C\sqrt{\varepsilon} \qquad\text{for}\;x\in \Omega_{C\varepsilon^2}.
+\end{equation*}
+\end{thm}
+\begin{proof} As $f(x)\geq 0$ on $\Omega$, from Lemma \ref{lem:lower-bound} and Theorem \ref{thm:qual} we have 
+\begin{equation}\label{e:low}
+    u^\varepsilon(x) \geq u(x) \geq 0 \qquad\text{for all}\;x\in \Omega.
+\end{equation}
+From a priori estimate for $u$, we redefine the constant $C_0$ such that
+\begin{equation}\label{e:priori}
+    \sup_{x\in \overline{\Omega}} \left(\left| u(x)\right| + \left|Du(x)\right|\right) + \Vert \nabla f\Vert_{L^\infty(\Omega)} \leq C_0.
+\end{equation}
+We recall from \cite{Lasry1989} that
+\begin{equation}\label{e:behavior_ueps}
+    \lim_{d(x)\to 0^+} u^\varepsilon(x)d(x)^\alpha = C_\alpha \varepsilon^{\alpha+1}.
+\end{equation}
+where 
+\begin{equation*}
+    \alpha = \frac{2-p}{p-1} \in (0,1) \qquad\text{and}\qquad C_\alpha := \frac{1}{\alpha}(\alpha+1)^{\alpha+1}.
+\end{equation*}
+We have $u^\varepsilon (x)d(x)^\alpha \to C_\varepsilon$ as $d(x)\to 0$.
+From \cite[Theorem II.3]{Lasry1989} we know further that when $\frac{3}{2} < p <2$ there exists a constant $M_{\alpha,\varepsilon}$ such that
+\begin{equation}\label{e:blows_up}
+    \sup_{x\in \Omega}\left|u^\varepsilon(x) - \frac{C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha}\right| \leq M_{\alpha,\varepsilon}
+\end{equation}
+As a consequence, for any $\delta>0$ we have
+\begin{equation*}
+    u^\varepsilon(x) - (1+\delta) \frac{C_\alpha \varepsilon^{\alpha+1}}{d(x)^{\alpha}} \leq  M_{\alpha,\varepsilon} - \delta\frac{C_\alpha \varepsilon^{\alpha+1}}{d(x)^{\alpha}}\leq 0 \qquad\text{if}\qquad d(x)< \left(\frac{\delta C_\alpha\varepsilon^{\alpha+1}}{M_{\alpha,\varepsilon}}\right)^{\frac{1}{\alpha}}.
+\end{equation*}
+Let $\delta,\theta,\sigma\in (0,1)$ to be chosen later. We define the following auxiliary functional
+\begin{equation*}
+    \Phi(x,y) =  u^\varepsilon(x) - u(y) - \frac{C_0|x-y|^2}{\sigma}- \left(1+\delta\right)\frac{C_\alpha\varepsilon^{\alpha+1}}{d(x)^{\alpha}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}.
+\end{equation*}
+We split the proof into several steps.
+\begin{enumerate}
+    \item[1.] From \eqref{e:blows_up} we see that $\Phi^\sigma(x,y)\to -\infty$ as $d(x)\to 0$, thus for a fixed $\varepsilon>0$, there is $(x_{\sigma},y_\sigma)\in \Omega\times\overline{\Omega}$ such that
+    \begin{equation*}
+        \max_{\overline{\Omega}\times \overline{\Omega}} \Phi = \Phi(x_\sigma,y_\sigma).
+    \end{equation*}
+    We can assume that 
+    \begin{equation}\label{e:ass_delta0}
+        d(x_\sigma) < \delta_0
+    \end{equation}
+    so that $|Dd(x_\sigma)| = 1$. We will mention how the case $d(x_\sigma)\geq \delta_0$ can be easily deduced at the end of the proof.
+    \item[2.] From $\Phi(x_\sigma,y_\sigma)\geq \Phi(x_\sigma,x_\sigma)$ we have
+    \begin{align*}
+        & u^\varepsilon(x_\sigma) - u(y_\sigma) - \frac{C_0|x_\sigma-y_\sigma |^2}{\sigma}- \left(1+\delta\right)\frac{C_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}} \\
+        & \qquad\qquad\qquad\qquad \geq u^\varepsilon(x_\sigma) - u(x_\sigma) - \frac{C_0|x_\sigma-x_\sigma |^2}{\sigma}- \left(1+\delta\right)\frac{C_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}}.
+    \end{align*}
+    Therefore
+    \begin{equation*}
+        \frac{C_0|x_\sigma - y_\sigma|^2}{\sigma} \leq u(x_\sigma) - u(y_\sigma) \leq C_0|x_\sigma - y_\sigma|.
+    \end{equation*}
+    Thus we obtain that
+    \begin{equation*}
+        |x_\sigma - y_\sigma|\leq \sigma.
+    \end{equation*}
+\end{enumerate}
+\end{proof}
+
+\begin{thm}\label{thm:rate_doubling1} Let $\Omega = B(0,1)$ be the open unit ball in $\mathbb{R}^n$.
+Assume $\mathrm{(A1)},\mathrm{(H1)}-\mathrm{(H4)}$ and also $\frac{3}{2}<p<2$ so that $\alpha = \frac{2-p}{p-1} \in (0,1)$.
+Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that
+\begin{equation*}
+    0\leq u^\varepsilon(x) - u(x) \leq C\sqrt{\varepsilon} \qquad\text{for}\;x\in \Omega_{2\sqrt{\varepsilon}}.
+\end{equation*}
+
+\end{thm}
+
+\begin{proof}[Proof of Theorem \ref{thm:rate_doubling1}] Let $C_f$ be the Lipschitz constant of $f$ and $\beta,\sigma \in (0,1)$ to be chosen later.
+Recall the definition of $C_\varepsilon$ from Theorem \ref{thm:wellposed1<p<2} and a priori estimates
+\begin{equation}\label{e:priori}
+    \sup_{x\in \overline{\Omega}} \left(|u(x)| + |Du(x)|\right) \leq C_0 \qquad\text{and}\qquad |\nabla u^\varepsilon(x)| \leq \frac{\theta C_\varepsilon \alpha}{d(x)^{\alpha+1}} \qquad\text{for all}\;\theta > 1, x\in \Omega.
+\end{equation}
+We define the auxiliary functional
+\begin{align*}
+    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u(y) - \frac{C_\varepsilon|x-y |^2}{\sigma}- \frac{C_\varepsilon}{d(x)^{\alpha+1}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}
+    .
+\end{align*}
+We split the proof into several steps.
+\begin{enumerate}
+    \item[1.] Since $u^\varepsilon (x)d(x)^\alpha \to C_\varepsilon$ as $d(x)\to 0$, we see that $\Phi^\sigma(x,y)\to -\infty$ as $d(x)\to 0$, therefore for a fixed $\varepsilon>0$, there is $(x_{\sigma},y_\sigma)\in \Omega\times\overline{\Omega}$ such that
+    \begin{equation*}
+        \max_{\overline{\Omega}\times \overline{\Omega}} \Phi^\sigma = \Phi^\sigma(x_\sigma,y_\sigma).
+    \end{equation*}
+    We can assume that 
+    \begin{equation}\label{e:ass_delta0}
+        d(x_\sigma) < \delta_0
+    \end{equation}
+    so that $|Dd(x_\sigma)| = 1$. We will mention how the case $d(x_\sigma)\geq \delta_0$ is easily deduced at the end of the proof.
+    \item[2.] As $\Phi^\sigma(x_\sigma,y_\sigma)\geq \Phi^\sigma(0,y_\sigma)$, we have
+    \begin{align*}
+        u^\varepsilon(x_\sigma) - u(y_\sigma) - \frac{C_\varepsilon |x_\sigma-y_\sigma|^2}{\sigma} - \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+1}} \geq u^\varepsilon(0) - u(y_\sigma) - \frac{C_\varepsilon |y_\sigma|^2}{\sigma} - C_\varepsilon.
+    \end{align*}
+    Therefore
+    \begin{align*}
+        \frac{C_\varepsilon |x_\sigma-y_\sigma|^2}{\sigma} + \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+1}} 
+        &\leq u^\varepsilon(x_\sigma) - u^\varepsilon(0) + \frac{C_\varepsilon }{\sigma} +C_\varepsilon.
+    \end{align*}
+    Let $\theta>1$ be a constant such that $\theta\alpha < 1$. Using \eqref{e:priori} we have
+    \begin{equation*}
+        \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+1}} \leq  \frac{\theta C_\varepsilon \alpha|x_\sigma|}{d(x_\sigma)^{\alpha+1}} + \frac{C_\varepsilon}{\sigma}+ C_\varepsilon \leq \frac{\theta \alpha C_\varepsilon}{d(x_\sigma)^{\alpha+1}} + \frac{C_\varepsilon}{\sigma} + C_\varepsilon
+    \end{equation*}
+    since $|x_\sigma| < 1$. We deduce that 
+    \begin{align*}
+       \sigma (1-\theta \alpha)\left(\frac{1}{d(x_\sigma)}\right)^{\alpha+1} \leq \sigma + 1
+    \end{align*}
+    and therefore\footnote{We recall again that by definition $\frac{1}{\alpha+1} = p-1 \in \left(\frac{1}{2},1\right)$.}
+    \begin{equation}\label{e:d(x_sigma)}
+        d(x_\sigma) \geq \left[\left(\frac{1-\theta\alpha}{\sigma+1}\right)\sigma\right]^{\frac{1}{\alpha+1}}.
+    \end{equation}
+    \item[3.] As $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(x_\sigma,x_\sigma)$, we have
+    \begin{equation*}
+         u^\varepsilon(x_\sigma) - u(y_\sigma) - \frac{C_\varepsilon |x_\sigma-y_\sigma|^2}{\sigma} - \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+1}} \geq u^\varepsilon(x_\sigma) - u(x_\sigma) - \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+1}}.
+    \end{equation*}
+    Therefore
+    \begin{equation*}
+        \frac{C_\varepsilon |x_\sigma-y_\sigma|^2}{\sigma} \leq u(x_\sigma) - u(y_\sigma) \leq C_0|x_\sigma-y_\sigma|
+    \end{equation*}
+    thus
+    \begin{equation}\label{e:bdd_xi}
+        \frac{2C_\varepsilon|x_\sigma - y_\sigma|}{\sigma} \leq 2C_0
+    \end{equation}
+    and 
+    \begin{equation}\label{e:bd|x-y|}
+        |x_\sigma - y_\sigma| \leq \left(\frac{C_0 \alpha}{(\alpha+1)^{\alpha+1}}\right) \frac{\sigma}{\varepsilon^{\alpha+1}}.
+    \end{equation}
+    \item[3.] Let $\beta > 0$, we let 
+    \begin{equation}\label{e:scale}
+        \sigma = \varepsilon^{(\beta+1)(\alpha+1)}
+    \end{equation}
+    then \eqref{e:d(x_sigma)} and \eqref{e:bd|x-y|} become
+    \begin{equation}
+        d(x_\sigma) \geq \left(\frac{1-\theta\alpha}{\sigma+1}\right)^{p-1}
+    \end{equation}
+    \item[3.] $x\mapsto \Phi^\sigma(x,y_\sigma)$ has a maximum at $x_\sigma\in \Omega$, i.e.,
+    \begin{equation*}
+        u^\varepsilon(x) - \left(\frac{C_0|(1+\delta)x-y_\sigma|^2}{2\sigma^2} + \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}\right)
+    \end{equation*}
+    has a maximum at $x_\sigma\in \Omega$. By subsolution test for \eqref{eq:PDEeps} we have
+\begin{align}\label{e:sub1}
+    &\lambda u^\varepsilon(x_\sigma) + \left|\xi_\sigma+\zeta_\sigma\right|^p - f(x_\sigma)\nonumber\\
+    &\quad  -\varepsilon\left(\frac{2n}{\sigma} + \frac{C_\varepsilon(\alpha+\beta)(\alpha+\beta+1)|D d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+\beta+2}}-\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\Delta d(x_\sigma)\right)  \leq 0
+\end{align}
+where 
+\begin{equation}\label{e:est_xi_zeta}
+    \xi_\sigma = \frac{C_0\big((1+\delta)x_\sigma-y_\sigma\big)}{\sigma^2} \qquad\text{and}\qquad \zeta_\sigma = - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma).
+\end{equation}
+We have the following estimates
+\begin{align*}
+    |\zeta_\sigma|=\left|\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma )\right|
+    &\leq \frac{C_\varepsilon(\alpha+\beta)}{\sigma^{\alpha+\beta+1}} \\
+    &\leq \frac{(\alpha+\beta)(\alpha+1)^{\alpha+1}}{\alpha} \frac{\varepsilon^{\alpha+1}}{\sigma^{\alpha+\beta+1}} \\
+    &= \frac{(\alpha+\beta)(\alpha+1)^{\alpha+1}}{\alpha}\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)}
+\end{align*}
+by choosing $\sigma = \varepsilon^\gamma$ where
+\begin{equation*}
+ \displaystyle 0 < \gamma < \frac{\alpha+1}{\alpha+1+\beta}.
+\end{equation*}
+In particular, $|\zeta_\sigma|\leq \mathfrak{C}_\alpha$ where $\mathfrak{C}_\alpha = \alpha^{-1}(\alpha+\beta)(\alpha+1)^{\alpha+1}$.
 

### 2021-04-06 Drafts and notes/Things to try.tex
Major change

\documentclass[10pt]{article}
\usepackage[T1]{fontenc}

\usepackage{xcolor}
\usepackage{fullpage}
\usepackage{mathrsfs}
\usepackage{amsmath, amsthm}
%\usepackage[utf8]{vietnam} 
%\usepackage[utf8]{inputenc}
%\usepackage[english,vietnam]{babel}

%\usepackage{fontspec}
%\setmainfont[Ligatures=TeX]{Linux Libertine O}
%\usepackage{polyglossia}
%\setmainlanguage{vietnamese}

%\usepackage[bitstream-charter]{mathdesign}
%\usepackage{eucal}
\usepackage{geometry}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2.5cm,rmargin=2.2cm,headheight=2.5cm}

%\usepackage[tracking]{microtype}
\usepackage[sc,osf]{mathpazo}   % With old-style figures and real %smallcaps.
\linespread{1.025}              % Palatino leads a little more leading
% Euler for math and numbers
\usepackage[euler-digits,small]{eulervm}

\usepackage{frcursive}
\usepackage{calligra}
\newcommand{\setfont}[2]{{\fontfamily{#1}\selectfont #2}}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}
\newtheorem{ass}{Assumption}
\renewcommand{\theass}{}
\newtheorem{defn}{Definition}
\newtheorem{quest}{Question}
\newtheorem{com}{Comment}
\newtheorem{ex}{Example}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{prop}[thm]{Proposition}
\theoremstyle{remark}
\newtheorem{rem}{\bf{Remark}}
%\numberwithin{equation}{section}

\usepackage[framemethod=TikZ]{mdframed}
%\newcounter{theo}[section]\setcounter{theo}{0}

%\newcounter{theo}[]\setcounter{theo}{0}
%\renewcommand{\thetheo}{\arabic{section}.\arabic{theo}}
%\renewcommand{\thetheo}{\arabic{theo}}
\newenvironment{theo}[2][]{%
\refstepcounter{theo}%
\ifstrempty{#1}%
{\mdfsetup{%
frametitle={%
\tikz[baseline=(current bounding box.east),outer sep=0pt]
\node[anchor=east,rectangle,fill=blue!20]
%{\strut Theorem~\thetheo};}}
{\strut Question~\thetheo};}}
}%
{\mdfsetup{%
frametitle={%
\tikz[baseline=(current bounding box.east),outer sep=0pt]
\node[anchor=east,rectangle,fill=blue!20]
{\strut Theorem~\thetheo:~#1};}}%
}%
\mdfsetup{innertopmargin=10pt,linecolor=blue!20,%
linewidth=2pt,topline=true,%
frametitleaboveskip=\dimexpr-\ht\strutbox\relax
}
\begin{mdframed}[]\relax%
\label{#2}}{\end{mdframed}}

\begin{document}

\begin{center}
{\LARGE \textsc{Quasilinear equations}}\\
%{Từ Nguyễn Thái Sơn}\\
%{\setfont{calligra}{Son Nguyen Thai Tu}}\\
%{\setfont{frc}{March 13, 2021}}\\
{\textit{March 24, 2021}}
\end{center}

\begin{center}
--------------------------------------------------------------------------------------------------------------------
\end{center}

\begin{enumerate}
    \item Try the special case $\Omega = B(0,1)$, note that we have $\Delta d(x) = 0$ in one dimension. Question: what is the difference between the rotational case (radial) vs one dimensional? 
    \item Try out the special case $f(x) = f(|x|)$ in $B(0,1)$, in which we can reduce it to one-dimensional setting.
    \item Try out the specific case $f(x) = 1-|x|$ on $(-1,1)$ and $f(x) = 0$ in $1\leq |x|\leq 2$ on the domain $\Omega = (-2,2)$. This is a simple case of the compactly supported data.
    \item Idea for general data: Assume $u^\varepsilon\to u$ as $\varepsilon\to 0$. We compare $u^\varepsilon$ and $v^\varepsilon$ where $1<p\leq 2$ and
\begin{equation}\label{eq:PDEeps}
    \begin{cases}
   \mathcal{L}[u^\varepsilon] =  u^\varepsilon(x) + |Du^\varepsilon(x)|^p - f(x) - \varepsilon \Delta u^\varepsilon(x) = 0 &\qquad
    \text{in}\;\Omega, \vspace{0cm}\\
   u^\varepsilon(x) = +\infty &\qquad
    \text{on}\;\partial\Omega
    \end{cases} \tag{PDE$_\varepsilon$}
\end{equation}
and
\begin{equation}\label{eq:vPDEeps}
    \begin{cases}
   \mathcal{L}[v^\varepsilon] =  v^\varepsilon(x) + |Dv^\varepsilon(x)|^p - f(x) - \varepsilon \Delta v^\varepsilon(x) = 0 &\qquad
    \text{in}\;\Omega, \vspace{0cm}\\
   v^\varepsilon(x) = u(x) &\qquad
    \text{on}\;\partial\Omega.
    \end{cases} 
\end{equation}
We know that $|v^\varepsilon - u|\leq C\sqrt{\varepsilon}$, thus the goal is to compare $u^\varepsilon$ and $v^\varepsilon$. Let $w^\varepsilon(x) = u^\varepsilon(x) - v^\varepsilon(x)$, we have
\begin{equation}\label{eq:wPDEeps}
    \begin{cases}
w^\varepsilon(x) + |Du^\varepsilon(x)|^p  - |Dv^\varepsilon|^p - \varepsilon \Delta w^\varepsilon(x) = 0 &\qquad
    \text{in}\;\Omega, \vspace{0cm}\\
   w^\varepsilon(x) = +\infty &\qquad
    \text{on}\;\partial\Omega.
    \end{cases} 
\end{equation}
The good thing about \eqref{eq:wPDEeps} is, the data $f$ disappears and furthermorethe new data, for example with $p=2$ can be written as
\begin{equation}\label{eq:wwPDEeps}
    \begin{cases}
w^\varepsilon(x) + |Dw^\varepsilon(x)|^2 +\underbrace{2Dw^\varepsilon(x)\cdot Dv^\varepsilon(x)}_{g
(x)} - \varepsilon \Delta w^\varepsilon(x) = 0 &\qquad
    \text{in}\;\Omega, \vspace{0cm}\\
   w^\varepsilon(x) = +\infty &\qquad
    \text{on}\;\partial\Omega.
    \end{cases} 
\end{equation}
and $g(x) \approx \frac{\varepsilon \nabla d(x)\cdot \nabla v^\varepsilon(x)}{d(x)} + |Dv^\varepsilon(x)|^2$, which is small in some sense depends on $\varepsilon$. Question: can we get a rate of convergence $w^\varepsilon(x)\to 0$? What is the behavior of $Dv^\varepsilon(x)$ as $\varepsilon\to 0$? Can we know more besides $|v^\varepsilon - u|\leq C\sqrt{\varepsilon}$?
\item Building a better supersolution for compactly supported data. Using the above $v^\varepsilon$ in \eqref{eq:vPDEeps}, can we somehow show
\begin{equation*}
    u^\varepsilon(x) \leq v^\varepsilon(x) + \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} 
\end{equation*}
in $\Omega$ when we assume $\mathrm{supp}\;f \subset \Omega_{\delta_0}$? 
\item Showing $u^\varepsilon$ is very small in the region where $f = 0$, for example $\mathrm{supp}\;f \subset \Omega_{\delta_0}$, using stochastic control. The idea behind this is, $u(x) = 0$ whenever $f(x) = 0$ (we assume $f\geq 0$) and $u^\varepsilon\to u$, thus $u^\varepsilon$ has to be very small where $f = 0$, thus there is a hope to build a better supersolution, to show that 
\begin{equation*}
       u^\varepsilon(x) \leq \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} 
\end{equation*}
where $x$ in the region where $f(x) = 0$. Specifically, solution $u^\varepsilon$ to \eqref{eq:PDEeps} can be written as
\begin{equation*}
    u^\varepsilon(x) = \inf_{a(\cdot)\in \mathcal{A}}  \mathbb{E}\left[\int_0^\infty e^{-t}\left(\frac{(\alpha+1)^{\alpha+1}}{(\alpha+2)^{\alpha+2}}|a(X_t)|^{\alpha+2} + f(X_t)\right)dt \right]
\end{equation*}
where $q = \alpha+2$ satisfies $\frac{1}{q} + \frac{1}{p} = 1$, where
\begin{equation*}
    \begin{cases}
    dX_t = a(X_t)dt + \varepsilon\sqrt{2} d\mathbb{B}_t\\
    \;\;X_0 = x
    \end{cases}
\end{equation*}
and $\mathcal{A}$ is the set of continuous function $a(\cdot):\Omega \to \mathbb{R}$ such that the state $X_t\in \overline{\Omega}$ with probability 1 for all time $t\geq 0$ and for all initial points $x\in \Omega$. Here $\mathbb{B}_t$ is the standard Brownian motion. The hope is that, the optimal Markovian control is given by
\begin{equation*}
    a_0(x) = p|\nabla u^\varepsilon(x)|^{p-2}\nabla u^\varepsilon(x).
\end{equation*}
Hence, note that
\begin{equation*}
    \frac{1}{qp^{\alpha+1}} = \frac{(\alpha+1)^{\alpha+1}}{(\alpha+2)^{\alpha+2}}
\end{equation*}
we have
\begin{equation*}
   \frac{1}{qp^{\alpha+1}} |a_0(X_t)|^q =  \frac{1}{qp^{\alpha+1}}p^q |\nabla u^\varepsilon(x)|^p = \frac{1}{pq}|\nabla u^\varepsilon(x)|^p \approx \frac{1}{pq}\frac{(C_\alpha \alpha)^p\varepsilon^{\alpha+2}}{d(x)^{\alpha+2}}.
\end{equation*}
In fact, this estimate can be make rigorously from \cite{alessio_asymptotic_2006}, that is there is a constant $C>0$ such that
\begin{equation*}
    |\nabla u ^\varepsilon(x)|\leq \frac{C\varepsilon^{\alpha+1}}{d(x)^{\alpha+1}}
\end{equation*}
for $x\in \Omega$.
\end{enumerate}

%\bibliography{zzzzlibrary}{}
%\bibliographystyle{ieeetr}
%\bibliographystyle{acm}
\end{document}

### 2021-05-03 Drafts and notes/Draft.tex
New Draft with established results

--- 2021-01-17 Drafts and notes/Draft.tex
@@
 \usepackage[toc,page]{appendix}
+%\setcounter{secnumdepth}{4}
+%\setcounter{tocdepth}{3}
 %============%============%============%============%
+%\usepackage{romannum}
 \usepackage{xcolor}
@@
 \usepackage{mathpazo}
-%\usepackage[euler-digits]{eulervm}
 
+%\usepackage[libertine,cmintegrals,cmbrac,vvarbb]{newtxmath}
 \usepackage{eucal}
+%\usepackage[utopia]{mathdesign}
+\usepackage[euler-digits]{eulervm}
 \usepackage[unicode=true]{hyperref}
@@
 }
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
-
 \title[Rate of convergence]
-{\textsc{Second-order state-constraint Hamilton-Jacobi equations}}
-
-\thanks{The authors are supported in part by NSF grant DMS-1664424.}
-
+{\textsc{Remarks on the vanishing viscosity of state-constraint Hamilton--Jacobi equations}}
+\thanks{The authors is supported in part by NSF grant DMS-1664424 and NSF CAREER grant DMS-1843320
+to Hung Vinh Tran. The work of Son N. T. Tu is supported in part by the GSSC Fellowship, University of Wisconsin--Madison.}
 \begin{abstract}
-
+We investigate qualitatively the convergence of large solution (state-constraint solution) to the subquadratic quasilinear elliptic equation as the viscosity vanishes.
+We show by a simple proof that for Lipschitz data that vanish on the boundary, the rate of convergence is at least $\mathcal{O}(\sqrt{\varepsilon})$ with a specific boundary layer.
+The rate can be improved in some region to $\mathcal{O}(\varepsilon)$, for instance, on the whole domain with zero data.
+The proof relies on a domain decomposition technique and classical tools in viscosity solution theory.
 \end{abstract}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \author{Yuxi Han}
@@
 }
+\maketitle
+\setcounter{tocdepth}{1}
+\tableofcontents
 
-\maketitle
-
-%\tableofcontents
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}\label{sec:intro}
-
-Let $\Omega$ be an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$.
-Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$.
-Let $u^\varepsilon$ be the solution to
-\begin{equation}\label{eq:PDE}
+\subsection{Motivation} Let $\Omega$ be an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$, %Let us consider the following Hamiltonian $ H(x,\varrho) = |\varrho|^p-f(x)$ for $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$,
+ $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$, and $u^\varepsilon\in \mathrm{C}^2(\Omega)$ (see \cite{Lasry1989}) be the solution to
+ \begin{equation}\label{eq:PDEepsa}
     \begin{cases}
-    \lambda u^\varepsilon(x) + |Du^\varepsilon(x)|^p - f(x) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
+      u^\varepsilon(x) + H(Du^\varepsilon(x)) - f(x) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
+    \text{in}\;\Omega, \vspace{0cm}\\
+    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^\varepsilon(x) = +\infty
+    \end{cases} 
+\end{equation}
+ where $H:\R^n\to\R^n$ is a continuous Hamiltonian.
+A typical subquadratic Hamiltonian that has been considered in the literature is $H(\xi) = |\xi|^p$ for $\xi\in \R^n$ where $1<p\leq 2$.
+For simplicity of the presentation, we will consider this special case and generalize the result later to all Hamiltonian $H(\xi)$ for which (see \cite{sardarli_ergodic_2021} for a similar generalization)
+ \begin{equation*}
+     \lim_{\delta\to 0}\delta^{\frac{p}{p-1}}H\left(\delta^{-\frac{1}{p-1}}\xi\right) = |\xi|^p \qquad\text{locally uniformly in}\;\xi\in \R^n.
+ \end{equation*}
+ With $H(\xi) = |\xi|^p$, the equation of interest is then becomes
+\begin{equation}\label{eq:PDEeps}
+    \begin{cases}
+      u^\varepsilon(x) + |Du^\varepsilon(x)|^p - f(x) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
     \text{in}\;\Omega, \vspace{0cm}\\
@@
 \end{equation}
-We are interested in studying the asymptotic behavior of $\{u^\varepsilon\}_{\varepsilon>0}$ as the vanishing viscosity happens: $\varepsilon\rightarrow 0$.
+When $1<p\leq 2$, equation \eqref{eq:PDEeps} describes the value function associated with a minimization problem in stochastic optimal control with state constraint.
+We are interested in studying the asymptotic behavior of $\{u^\varepsilon\}_{\varepsilon>0}$ as $\varepsilon\rightarrow 0^+$.
+Heuristically, the solution of the second-order state-constraint problem converges to that of a first-order state-constraint problem which is associated with deterministic optimal control, namely,
+\begin{equation}\label{eq:PDE0}
+    \begin{cases}
+       u(x) + |Du(x)|^p - f(x) \leq 0\;\qquad\text{in}\;\Omega,\\
+       u(x) + |Du(x)|^p - f(x) \geq 0\;\qquad\text{on}\;\overline{\Omega},
+    \end{cases} \tag{PDE$_0$}
+\end{equation}
+as is described in the framework of viscosity solution.
+Equation \eqref{eq:PDE0} admits a unique viscosity solution in the space $\rmC(\overline{\Omega})$, which is also the maximal viscosity subsolution among all the viscosity subsolutions in $\rmC(\overline{\Omega})$.
+The problem is interesting since in the limit we no longer have blowing up behavior.
+In this paper, we are interested in the rate of convergence of $u^\varepsilon \to u$ as $\varepsilon\to 0$.
+A boundary layer is expected to describe the behavior of this convergence near the boundary.
+\subsection{Assumptions} We will always assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary in $\mathbb{R}^n$ satisfying either %$H:\mathbb{R}^n\times \mathbb{R}^n$ is a continuous Hamiltonian.
+%\begin{itemize}
+%    \item[$\mathrm{(A1)}$] $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
+%\end{itemize}
+%    The following assumptions on $\Omega$ will also be used.
+\begin{itemize}    
+    \item[(A1)] There exists a universal pair of positive numbers $(r,h)$ and $\eta\in \mathrm{BUC}(\overline{\Omega};\mathbb{R}^n)$ such that $B(x+t\eta(x), rt)\subset\Omega$ for all $t\in (0,h]$.
+    \item[(A2)] $\Omega$ is a bounded star-shaped (with respect to the origin) open subset of $\mathbb{R}^n$ such that
+    \begin{equation*}
+        \mathrm{dist}(x,\overline{\Omega}) \geq \kappa r \qquad\text{for all}\; x\in (1+r) \partial\Omega, \;\text{for all}\;r>0,
+    \end{equation*}
+for some $\kappa > 0$.
+\end{itemize}
+Equation \eqref{eq:PDEeps} follows the setting of \cite{Lasry1989}, where the specific structure of the Hamiltonian $H(x,\xi) = |\xi|^p - f(x)$ enables more explicit estimates on the solution of \eqref{eq:PDEeps}.
+Assumption $\mathrm{(A1)}$ or $\mathrm{(A2)}$ guarantees that a comparison principle holds for the state-constraint problem \eqref{eq:PDE0}.
+We note that $\mathrm{(A1)}$ was first studied by M.
+Soner in \cite{Soner1986} (and $\mathrm{(A1)}$ holds for any smooth bounded domain), while $\mathrm{(A2)}$ was posed and studied by I.
+Capuzzo-Dolcetta and P.
+L.
+Lions in \cite{Capuzzo-Dolcetta1990}.
+%We list the assumptions on a general Hamiltonian as follow.
+%\begin{itemize}
+%    \item[$\mathrm{(H1)}$] There exists $C_1 > 0$ such that $H(x,p) \geq -C_1$ for all $(x,p)\in \overline{\Omega}\times\mathbb{R}^n$.
+%    \item[$\mathrm{(H2)}$] There exists $C_2>0$ such that $|H(x,0)|\,\leq \,C_2$ for all $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$.
+%    \item[$\mathrm{(H3)}$] For each $R>0$ there exists a modulus $\omega_{R}[0,\infty)\to [0,\infty)$ such that $\omega_R(0^+) = 0$ and 
+%    \begin{equation*}
+%        \begin{cases}
+%        |H(x,p) - H(y,p)| \leq \omega_R(|x-y|),\\
+%        |H(x,p) - H(x,q)| \leq \omega_R(|p-q|),
+%        \end{cases} \qquad\text{for all}\;x,y\in \overline{\Omega}, p,q \in \mathbb{R}^n\;\text{with}\;|p|,|q|\leq R.
+%    \end{equation*}
+%    \item[$\mathrm{(H4)}$] $H(x,p)\rightarrow \infty$ as $|p|\to \infty$ uniformly in $x\in \overline{\Omega}$.
+%\end{itemize}
 
-Paper to read \cite{Ishii2017a} and \cite{Lasry1989}.
+\subsection{Literature} There is a
+vast amount of work in the literature on large solutions and second-order viscosity solution with state constraint.
+The problem \eqref{eq:PDEeps} is first studied in \cite{Lasry1989} and subsequently many works have been done in understanding deeper the properties of solutions.
+We refer the readers to \cite{alessio_asymptotic_2006} and the references therein.
+
+In terms of rate of convergence, up to our knowledge such a question has not been studied in the literature.
+For the case \eqref{eq:PDEeps} is equipped with Dirichlet boundary condition, a rate $\mathcal{O}(\sqrt{\varepsilon})$ is well-known with multiple proofs (see \cite{Hung2019}).
+
+\subsection{Main results} The main result of the paper is the following theorem.
+
+\begin{thm} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
+Assume that $1 < p\leq 2$ and $f$ is Lipschitz such that $f = 0$ on $\partial\Omega$.
+Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
+Then there exists a constant $C$ such that for $x\in \Omega$ there holds
+\begin{align*}
+    &C\sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x)\leq C\sqrt{\varepsilon} + C\varepsilon \left(\frac{\varepsilon}{d(x)}\right)^{\frac{2-p}{p-1}} &\qquad\text{if}\; p < 2,\\
+    &C\sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x)\leq C\sqrt{\varepsilon} + \varepsilon|\log(d(x))| &\qquad\text{if}\; p = 2.
+\end{align*}
+\end{thm}
+
+\begin{rem} The condition $f = 0$ on $\partial\Omega$ can be explained as follows.
+One can see that solution to \eqref{eq:PDEeps} is continuous with respect to data $f$ in the weak$^*$ topology of $L^\infty(\Omega)$ (see \cite{Lasry1989}).
+If $f = 0$ on $\partial\Omega$, we are able to approximate $f$ \emph{uniformly} in $L^\infty(\Omega)$ by a sequence of compactly supported functions, where such a rate is easier to obtained.
+Indeed, using the usual doubling variable technique, it is natural to consider the doubling variable for
+\begin{equation*}
+    u^\varepsilon(x) - \frac{C\varepsilon^{\alpha+1}}{d(x)^{\alpha}}
+\end{equation*}
+and $u(x)$, where $C\varepsilon^{\alpha+1}d(x)^{-\alpha}$ is the leading order term in the asymptotic expansion of $u^\varepsilon(x)$ as $\mathrm{dist}(x,\partial\Omega)\to 0$.
+We can see a \emph{correct scale} heuristically happens around $d(x) \approx \varepsilon$.
+However, to control the extra leading term above, one needs to have $d(x)\approx \varepsilon^\gamma$ for $\gamma < 1$ to make the argument work.
+This major difficulty can be overcome when we decompose the solution into an inside part and an outside part that lies in an annulus, where we have reduced to $f=0$ in this region.
+\end{rem}
 
 \section{Preliminaries}\label{sec:prelim} 
-
-\subsection{Convergence result}
-Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$. Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$.
-
-Let $u^\varepsilon$ be the solution to \eqref{eq:PDE}, we observe that if$u^\varepsilon\rightarrow u^0$ uniformly on compact subsets of $\Omega$, we see that $u(x)\rightarrow +\infty$ as $\mathrm{dist}(x,\partial \Omega)\to 0$ as well, therefore the limiting solution is not the state-constraint solution to a limiting first order equation.
-
-\begin{lem}\label{lem:max} Let $u\in \rmC(\overline{\Omega})$ be a viscosity subsolution of 
-\begin{equation}\label{S_0}
- \lambda u(x) + H(x,Du(x)) = 0\;\qquad\text{in}\;\Omega
-\end{equation}
-such that, for all viscosity subsolution $v\in \rmC(\overline{\Omega})$ of \eqref{S_0} one has $v\leq u\in \overline{\Omega}$, then $u$ is a viscosity supersolution of \eqref{S_0} on $\overline{\Omega}$.
-\end{lem}
-
-\begin{thm}[Qualitative result] Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$.
-Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$.
-Let $u^\varepsilon$ be the solution to \eqref{eq:PDE}, then $u^\varepsilon \rightarrow u$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$ and $u$ solves
-\begin{equation}\label{eq:PDE0}
-    \begin{cases}
-    \lambda u(x) + |Du(x)|^p - f(x) \leq 0 \qquad\text{in}\;\Omega,\\
-    \lambda u(x) + |Du(x)|^p - f(x) \geq 0 \qquad\text{on}\;\overline{\Omega}.
-    \end{cases}\tag{PDE$_0$}   
-\end{equation}
-\end{thm}
-
-\color{blue}
-\begin{proof} (\textit{Added on Jan 16, 2021 - Heuristic idea}) Assume that we can get some sort of equi-continuity of the family $\{u^\varepsilon\}_{\varepsilon>0}$ in a local way, that is, for any compact sub-domain $\Omega'\subset\subset \Omega$ there is a constant $C(\Omega')$ such that
-\begin{equation}\label{eq:bound}
-    \Vert u^\varepsilon\Vert_{L^\infty(\Omega')} +\Vert Du^\varepsilon\Vert_{L^\infty(\Omega')} \leq C(\Omega').
-\end{equation}
-This should be done using Berstein's method (fill in later, and as $u$ blows up on $\partial \Omega$, this bound \eqref{eq:bound} may not be improved).
-Now let us assume via some subsequence $\varepsilon_j\to 0$ we have $u^{\varepsilon_j}\rightarrow u^0$ uniformly on compact subsets of $\Omega$, the interior stability of viscosity solution should yield us that
-\begin{equation*}
-    \lambda u^0(x) + |Du^0(x)|^p - f(x) = 0 \qquad\text{in}\;\Omega.
-\end{equation*}
-The real difficulty is describing what is the behavior of $u^0$ on the boundary. As we expect it to solves \eqref{eq:PDE0}, it should be the maximal subsolution (hence, solution) to 
-\begin{equation}\label{eq:S_lambda}
-    \lambda u(x) + |Du(x)|^p - f(x) = 0 \qquad\text{in}\;\Omega.
-\end{equation}
-Let $v^\varepsilon\in \rmC^2(\Omega)\cap \rmC(\overline{\Omega})$ be the unique solution to the Dirichlet problem
-\begin{equation}\label{eq:v_eps}
-\begin{cases}
-    \lambda v^\varepsilon(x) + |Dv^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v^\varepsilon(x) &\qquad\text{in}\;\Omega,\\
-    \;\;\,\quad\quad\qquad\qquad\qquad\qquad v^\varepsilon = u &\qquad \text{on}\;\partial\Omega.
-\end{cases}
-\end{equation}
-where $u\in \rmC(\overline{\Omega})$ is the unique solution of \eqref{eq:PDE0}. Note that $v^\varepsilon\rightarrow v^0$ solves the corresponding Dirichlet problem
-\begin{equation}\label{eq:v_0}
-\begin{cases}
-    \lambda v^0(x) + |Dv^0(x)|^p - f(x) = 0 &\qquad\text{in}\;\Omega,\\
-    \;\;\,\quad\quad\qquad\qquad\qquad\qquad v^0 = u &\qquad \text{on}\;\partial\Omega.
-\end{cases}
-\end{equation}
-\begin{lem} $v^0\equiv u$ as the unique solution to \eqref{eq:PDE0}.
-\end{lem}
-\begin{proof} We observe that $u$ solves \eqref{eq:PDE0} is the unique solution to the Dirichlet problem \eqref{eq:v_0} as well, thus $v^0 \equiv u$ by comparison principle.
-\end{proof}
-\noindent By comparison principle, we see that
-\begin{equation*}
-    v^\varepsilon(x)\leq u^\varepsilon(x) \qquad\text{for}\;x\in \Omega.
-\end{equation*}
-Let $\varepsilon\to 0$, we deduce that
-\begin{equation*}
-    u(x)\leq u^0(x) \qquad\text{for}\;x\in \Omega.
-\end{equation*}
-\end{proof}
-\color{black}
-
-%\nocite{*}
-
-\section{Questions}
-\begin{quest} [Jan 12, 2021.] Why do we use the distance functions to get boundary estimates? 
-\end{quest}
-
-\begin{quest} [Jan 13, 2021.] Maximum principle for sub-quadratic case.
-\end{quest}
-
-\begin{appendices}
-\section{Construction of solution for sub-quadratic case}
-In this section, with the specific form of the Hamiltonian $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$, we show the existence and uniqueness of solutions to \eqref{eq:PDE}.
-\begin{thm} If $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ then there exists a unique solution $u\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDE}.
-\end{thm}
-
-\begin{proof} For $\delta>0$, let us define $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) < \delta\}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$.
+\subsection{Setting and simplifications} Let $\Omega$ be an open, bounded and connected subset of $\mathbb{R}^n$ with boundary $\partial\Omega$ of class $C^2$.
+For small $\delta>0$, we denote $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) > \delta\}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$.
 \begin{figure}[ht]
@@
 \end{figure}
-We consider $\delta$ small enough so that the distance function $x\mapsto \mathrm{dist}(x,\partial \Omega)$ is $\mathrm{C}^2$ in the strip $\Omega^\delta\backslash \overline{\Omega}_\delta$, we recall that $|D d(x)| = 1$ in that region.
-We extend the signed distance function into a $\mathrm{C}^2(\mathbb{R}^n)$ function, denoted by $d(x)$ such that
+
+\begin{defn} Define
+\begin{equation}\label{def:delta_0}
+    \delta_{0,\Omega} =\frac{1}{2}\sup \big\{ \delta > 0: x\mapsto\mathrm{dist}(x,\partial\Omega)\;\text{is}\;\rmC^2\;\text{in}\;\Omega\backslash\overline{\Omega}_{\delta} \big\}.
+\end{equation}
+%The distance function is of class $\mathrm{C}^2$ in the region where $0<\mathrm{dist}(x,\partial\Omega) < \delta_0$. 
+We will simply write $\delta_0$ instead of $\delta_{0,\Omega}$ if the underlying domain is understood.
+\end{defn}
+
+We refer the readers to \cite{gilbarg_elliptic_2001} for the regularity of the distance function defined in the above definition.
+We then extend $\mathrm{dist}(x,\partial\Omega)$ to a function $d(x)\in \mathrm{C}^2(\mathbb{R}^n)$ such that
+\begin{equation}\label{e:distance_def}
+    \begin{cases}
+    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_{\delta_0},\\
+    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^{\delta_0}\backslash \Omega.
+    \end{cases}
+\end{equation}
+Recall that $|D d(x)| = 1$ in the viscosity sense (and thus in classical sense) in $\Omega^{\delta_0}\backslash \Omega_{\delta_0}$. Let 
+\begin{equation}\label{boundond}
+   K_0:= \max_{x\in \overline{\Omega}}|d(x)|, \qquad K_1 := \max_{x\in \overline{\Omega}} |D d(x)| \qquad\text{and}\qquad K_2 := \max_{x\in \overline{\Omega}} |\Delta d(x)|.
+\end{equation}
+\noindent We denote by $\mathcal{L}^\varepsilon:\rmC^2(\Omega)\to \rmC(\Omega)$ the operator
+\begin{equation*}
+    \mathcal{L}^\varepsilon[u](x) :=   u(x) + |Du(x)|^p - f(x) - \varepsilon \Delta u(x), \qquad x\in \Omega.
+\end{equation*}
+
+\subsection{Local gradient estimate} 
+The following theorem is about the local gradient bound as in \cite[Appendix]{Lasry1989}.
+The technique being used is the classical Bernstein's method.
+Let $\Omega$ be an open, bounded subset of $\R^n$, $\varepsilon \in (0,1)$.
+We consider $p>1$ in this section.
+%We consider the Hamiltonian $H(x,\rho) = |\rho|^p - f(x)$ where $1<p < \infty$.
+
+\begin{thm}\label{thm:grad_1} Let $f\in \rmC(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $u\in \mathrm{C}^2(\Omega)$ be a solution to $\mathcal{L}^\varepsilon[u] = 0$ in $\Omega$.
+Assume that $  u(x)-f(x)\geq -m$ in $\Omega$.
+Then for $\delta>0$, there exists $C_\delta = C(m,p,\delta, \Vert D f\Vert_{L^\infty(\Omega)})$ such that
+\begin{equation*}
+    \sup_{x\in \overline{\Omega}_\delta} \Big(|u(x)|+|Du(x)|\Big) \leq C_\delta.
+\end{equation*}
+\end{thm}
+\noindent We provide a proof for this Theorem in Appendix for the reader's convenience.
+
+\subsection{Well-posedness of large solution for subquaratic case} In this section we recall the existence and uniqueness of solutions to \eqref{eq:PDEeps} for $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
+We note that the assumption of $f$ can be relaxed to $f\in L^\infty(\Omega)$ (\cite{Lasry1989}).
+
+\begin{thm}\label{thm:wellposed1<p<2} Let $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
+There exists a unique solution $u^\varepsilon\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that:
+\begin{itemize}
+    \item[(i)] If $1<p< 2$, then 
+\begin{equation}\label{rate_p<2}
+    %\frac{C_\varepsilon-\eta}{d(x)^\alpha}-\frac{M_\eta}{ } \leq u(x)\leq \frac{C_\varepsilon+\eta}{d(x)^\alpha}+\frac{M_\eta}{ } 
+    \lim_{d(x)\to 0}\left( u^\varepsilon(x) \,d(x)^\alpha \right)= C_\alpha \varepsilon^{\alpha+1}
+\end{equation}
+where $\alpha = (p-1)^{-1}(2-p)$ and $C_\alpha = \alpha^{-1}(\alpha+1)^{\alpha+1}$.
+%\begin{equation*}
+%    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\alpha = \frac{1}{\alpha}(\alpha+1)^{\alpha+1}.
+%\end{equation*}
+\item[(ii)] If $p=2$, then
+\begin{equation}\label{rate_p=2}
+    \lim_{d(x)\to 0} \left(-\frac{u^\varepsilon(x)}{\log(d(x))}\right) = \varepsilon.
+\end{equation}
+\end{itemize}
+Furthermore, $u^\varepsilon$ is the maximal subolution among all subsolution $v\in W^{2,r}(\Omega)$ (for all $r>0$) of \eqref{eq:PDEeps}.
+\end{thm}
+\noindent This is Theorem I.1 in \cite{Lasry1989} with an explicit dependence on $\varepsilon$. We provide a proof in Appendix for later use. It is useful to note that $\alpha+1 = (p-1)^{-1}$.
+
+\subsection{Convergence result} We show qualitatively the convergence of \eqref{eq:PDEeps} to \eqref{eq:PDE0}.
+We first state the following Lemma (\cite{Capuzzo-Dolcetta1990}), which characterizes the solution to the first-order state-constraint  equation
+\begin{equation}\label{S_0}
+\begin{cases}
+       u(x) + |Du(x)|^p - f(x) = 0\;\qquad\text{in}\;\Omega,\\
+       u(x) + |Du(x)|^p - f(x) \geq 0\;\qquad\text{on}\;\partial\Omega. 
+\end{cases}\tag{$S_0$}   
+\end{equation}
+
+\begin{lem}\label{lem:max} Let $u\in \rmC(\overline{\Omega})$ be a viscosity subsolution of \eqref{S_0} such that, for all viscosity subsolution $v\in \rmC(\overline{\Omega})$ of \eqref{S_0} one has $v\leq u$ in $\overline{\Omega}$.
+Then $u$ is a viscosity supersolution of \eqref{S_0} on $\overline{\Omega}$.
+\end{lem}
+\noindent We give a proof of Lemma \ref{lem:max} in Appendix for the sake of completeness.
+
+\begin{lem}\label{lem:lower-bound} Assume $1<p\leq 2$.
+Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ be a solution to \eqref{eq:PDEeps}.
+We have $\{  u^\varepsilon\}_{\varepsilon>0}$ is uniformly bounded from below by a constant independent of $\varepsilon$.
+More precisely, we have $  u^\varepsilon \geq \min_\Omega f$ and $  u\geq \min_\Omega f$.
+%\begin{equation}\label{e:lower_bound_u_eps}
+%    \inf_{x\in \Omega}   u^\varepsilon(x) \geq  \inf_{\Omega} f
+%\end{equation}
+%and also
+%\begin{equation}\label{e:lower_bound_u}
+%    \inf_{x\in \Omega}   u(x) \geq  \inf_{\Omega} f
+%\end{equation}
+\end{lem}
+\begin{proof} For $m\in \mathbb{N}$, let $u^{\varepsilon,m}\in \mathrm{C}^2(\Omega)\cap \rmC(\overline{\Omega})$ solve the Drichlet problem
+\begin{equation}\label{e:uepsm}
+    \begin{cases}
+      u(x) + |Du(x)|^p - f(x) - \varepsilon \Delta u(x) = 0 &\qquad
+    \text{in}\;\Omega, \vspace{0cm}\\
+    \;\qquad\quad\qquad\qquad\qquad\qquad u(x) = m &\qquad
+    \text{on}\;\partial\Omega.
+    \end{cases} \tag{PDE$_{\varepsilon,m}$}
+\end{equation}
+We have $u^{\varepsilon}_m(x) \to u^\varepsilon(x)$ as $m\to \infty$ in $\Omega$.
+Let $\varphi(x) \equiv  \inf_{\Omega} f$ for $x\in \overline{\Omega}$.
+Then $\varphi(x)$ is a classical subsolution of \eqref{e:uepsm} in $\Omega$ with
+\begin{equation*}
+    \varphi(x) =   \inf_\Omega f \leq m = u^\varepsilon_m(x) \qquad\text{for}\;x\in \partial\Omega.
+\end{equation*}
+By comparison principle for the uniformly elliptic equation \eqref{e:uepsm}, we have
+\begin{equation*}
+     \inf_\Omega f \leq u^{\varepsilon}_m(x) \qquad\text{for all}\;x\in \Omega.
+\end{equation*}
+As $m\to \infty$, we obtain $  u^\varepsilon \geq \min_\Omega f$.
+The inequality $  u\geq \min_{\Omega}f$ follows from the comparison principle of \eqref{eq:PDE0} between supersolution $u$ on $\overline{\Omega}$ and subsolution $\varphi(x)$ in $\Omega$.
+\end{proof}
+
+We present a simple proof of the convergence $u^\varepsilon \to u$ using Lemma \ref{lem:max} for the reader's convenience. See also \cite[Theorem VII.3]{Capuzzo-Dolcetta1990}.
+\begin{thm}[Vanishing viscosity]\label{thm:qual} Assume $\mathrm{(A1)}$.
+Let $u^\varepsilon$ be the solution to \eqref{eq:PDEeps}.
+Then there exists $u \in \mathrm{C}(\overline{\Omega})$ such that $u^\varepsilon \rightarrow u$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$, where $u$ solves \eqref{eq:PDE0} in $\Omega$.
+\end{thm}
+
+\begin{proof}[Proof of Theorem \ref{thm:qual}] By a priori estimate (Theorem \ref{thm:grad_1}), we have
+\begin{equation}\label{e:priorie_eps}
+    |u^\varepsilon(x)| + |Du^\varepsilon(x)| \leq C_\delta \qquad\text{for}\;x\in \overline{\Omega}_\delta.
+\end{equation}
+By the Arzel\'a--Ascoli theorem, there exists a subsequence $\varepsilon_j\to 0$ and a function $u\in \rmC(\Omega)$ such that $u^{\varepsilon_j}\to u$ locally uniformly in $\Omega$.
+By the stability of viscosity solution, we easily deduce that
+\begin{equation}\label{eq:u0int}
+     u(x) + |Du(x)| - f(x) = 0 \qquad\text{in}\;\Omega.
+\end{equation}
+From Lemma \ref{lem:lower-bound}, we have $  u^\varepsilon(x)\geq \min_{\Omega} f$ and  $  u(x)\geq \min_{\Omega} f$ for all $x\in \Omega$.
+Together with \eqref{eq:u0int}, we obtain $|\xi|\leq \max_\Omega f - \min_\Omega f$ for all $\xi\in D^+u(x)$ and $x\in \Omega$.
+In other words, there is a constant $C_0$ such that
+\begin{equation}\label{e:C0}
+    |u(x) - u(y)| \leq C_0|x-y| \qquad\text{for all}\;x,y\in \Omega.
+\end{equation}
+Thus, we can extend $u$ uniquely to $u\in \rmC(\overline{\Omega})$.
+We will use Lemma \ref{lem:max} to show that $u$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$.
+It suffices to show that $u\geq w$ on $\overline{\Omega}$, where $w\in \rmC(\overline{\Omega})$ is the unique solution to \eqref{eq:PDE0}.
+
+For $\delta>0$, let $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\partial \Omega) > \delta\}$ and $u_\delta\in\rmC(\overline{\Omega}_\delta)$ be the state-constraint viscosity solution to the problem $  u(x) + |Du(x)| - f(x) = 0$ in $\Omega_\delta$, i.e., $u_\delta$ is the unique viscosity solution to
+\begin{equation}\label{e:v_v}
+    \begin{cases}
+      u_\delta(x) + |Du_\delta(x)|-f(x) \leq 0 &\qquad\text{in}\;\Omega_\delta,\\
+      u_\delta(x) + |Du_\delta(x)| - f(x) \geq 0 &\qquad\text{on}\;\overline{\Omega}_\delta.
+    \end{cases}
+\end{equation}
+Since $u_\delta\rightarrow w$ locally uniformly as $\delta\rightarrow 0^+$ (see \cite{kim_state-constraint_2020}) and $w$ is bounded, $\{u_\delta\}_{\delta>0}$ is uniformly bounded.
+Let $v^\varepsilon_\delta\in \rmC^2(\Omega_\delta)\cap \rmC(\overline{\Omega}_\delta)$ be the unique solution to the Dirichlet problem
+\begin{equation}\label{eq:vv_eps}
+\begin{cases}
+      v_\delta^\varepsilon(x) + |Dv_\delta^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v_\delta^\varepsilon(x) &\qquad\text{in}\;\Omega_\delta,\\
+    \;\;\;\,\quad\qquad\qquad\qquad\qquad v_\delta^\varepsilon = v_\delta &\qquad \text{on}\;\partial\Omega_\delta.
+\end{cases}
+\end{equation}
+It is well-known that $v^\varepsilon_\delta\to v_\delta$ uniformly on $\overline{\Omega}_\delta$ as $\varepsilon\to 0$.
+
+For all $\delta$ small enough, $v_\delta\leq u^\varepsilon$ on $\partial \Omega_\delta$.
+Hence by maximum principle, $v^\varepsilon_\delta \leq u^\varepsilon$ on $\overline{\Omega}_\delta$.
+Let $\varepsilon\to 0$ and we have $v_\delta \leq u$ on $\overline{\Omega}_\delta$.
+Let $\delta\rightarrow 0$ and we obtain $w\leq u$ in $\Omega$, which implies $w\leq u$ on $\overline{\Omega}$ since both $w,u$ belong to $\rmC(\overline{\Omega})$.
+\end{proof}
+
+\section{Rate of convergence via the doubling variables method}
+In this section, we focus on the rate of convergence for the case $f\in \mathrm{W}^{1,\infty}(\Omega)\cap\mathrm{C}(\overline{\Omega})$.
+By adding a constant to the solution $u^\varepsilon$ of \eqref{eq:PDEeps}, without loss of generality we can assume the \emph{nonnegativity}
+\begin{equation}\label{e:minf}
+    \min_{\overline{\Omega}} f(x) = 0.
+\end{equation}
+As a consequence, $u^\varepsilon(x),u(x)\geq 0$ for $x\in \Omega$ by Lemma \ref{lem:lower-bound}. We start with the lower bound of $u^\varepsilon - u$.
+\begin{thm} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
+Assume \eqref{e:minf} and $H(x,\xi) = |\xi|^p - f(x)$ where $p\in\left(1,2\right]$.
+Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
+Then there exists a constant $C$ independent of $\varepsilon$ such that
+\begin{equation}\label{e:lower1}
+    -C\sqrt{\varepsilon} \leq u^\varepsilon(x) - u(x) \qquad\text{for all}\;x\in \Omega.
+\end{equation} 
+\end{thm}
+\begin{proof} The proof relies on a well-known rate of convergence for vanishing viscosity of viscous Hamilton--Jacobi equation with Dirichlet boundary condition (\textcolor{blue}{NEED CITATION}).
+As $u\in \mathrm{C}(\overline{\Omega})$, let $g\in \mathrm{C}(\partial\Omega)$ defined by $g(x) = u(x)$ for $x\in \partial\Omega$.
+Let $v^\varepsilon\in \mathrm{C}^2(\Omega)\cap \mathrm{C}(\overline{\Omega})$ be the unique viscosity solution to
 \begin{equation*}
     \begin{cases}
-    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_\delta,\\
-    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^\delta\backslash \Omega.
+          v^\varepsilon(x) + |Dv^\varepsilon(x)|^p - f(x) - \varepsilon \Delta v^\varepsilon(x) = 0 &\qquad\text{in}\;\Omega,\\
+        \qquad\qquad\qquad\qquad\qquad \qquad\quad v^\varepsilon(x) = g(x) &\qquad\text{on}\;\partial\Omega.
     \end{cases}
 \end{equation*}
-We can choose $d(\cdot)$ so that $\Omega_\delta = \{x\in \mathbb{R}^n: d(x)-\delta >0 \}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: d(x) +\delta>0\}$.
-
-To find candidate for subsolution and supersolution to \eqref{eq:PDE}, we use the ansatz
-\begin{equation}\label{eq:ansatz}
-    u(x) = C_0 d(x)^{-\alpha}, \qquad x\in \Omega
+It is well-known that $v^\varepsilon \to u$ uniformly where $v$ is the viscosity solution to
+\begin{equation*}
+\begin{cases}
+       v(x) + |Dv(x)|^p - f(x) = 0 &\qquad\text{in}\;\Omega,\\
+     \qquad\qquad\qquad\quad\;\;\; v(x) = g(x)&\qquad\text{on}\;\partial\Omega. 
+\end{cases}
+\end{equation*}
+By comparison principle, it is clear that $v = u$, the solution of \eqref{eq:PDE0}. Furthermore, there exists a positive constant $C$ such that 
+\begin{equation}\label{e:cp1}
+     |v^\varepsilon(x)  - u(x)| \leq C\sqrt{\varepsilon} \qquad\text{for}\;x\in \overline{\Omega}.
 \end{equation}
-as we expect it blows up near the boundary like some thing proportionate to inverse of the distance function, due to the structure of $H(x,\varrho) = |\varrho|^p - f(x)$.
-Let us plug \eqref{eq:ansatz} into \eqref{eq:PDE} we obtain that the highest order terms are
-\begin{equation*}
-        -C_0 \alpha(\alpha+1)d^{-(\alpha+2)} + C_0^p \alpha^p d^{-(\alpha+1)p}.
-\end{equation*}
-Setting them to zero, we deduce that
-\begin{equation*}
-    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_0 = \frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}.
-\end{equation*}
-We can obtain the following families of subsolution on $\Omega^\delta$ and supersolution on $\Omega^\delta$ as follow.
-\begin{equation*}
-        \overline{w}_{\eta,\delta}(x) = \frac{C_0+\eta}{(d(x)-\delta)^\alpha} +\frac{C_\eta}{\lambda} \quad\text{for}\;x\in \Omega_\delta \qquad\text{and}\qquad \underline{w}_{\eta,\delta}(x) = \frac{C_0-\eta}{(d(x)+\delta)^\alpha} -\frac{C_\eta}{\lambda} \quad\text{for}\;x\in \Omega^\delta.
-\end{equation*}
-We divide the rest of the proof into 3 steps.
-\begin{itemize}
-    \item Step 1. Building a maximal solution to \eqref{eq:PDE}. 
-\end{itemize}
+By comparison principle for \eqref{eq:PDEeps}, we have
+\begin{equation}\label{e:cp2}
+    v^\varepsilon(x)\leq u^\varepsilon(x) \qquad\text{for}\;x\in \Omega.
+\end{equation}
+From \eqref{e:cp1} and \eqref{e:cp2} we obtain the lower bound \eqref{e:lower1}.
 \end{proof}
 
-\section{Gradient bounds}
-\subsection{Local interior gradient bound for elliptic equation}
-Let $\Omega\subset \R^n$ be an open, bounded, connected set with $\rmC^2$ boundary and $H(x,p):\overline{\Omega}\times \R^n\rightarrow \mathbb{R}$ be a continuously differentiable Hamiltonian satisfying
-\begin{equation}\label{eq:grow}
-\lim_{|p\rightarrow \infty} \left(\frac{1}{2}H(x,p)^2 + D_xH(x,p)\cdot p\right) = +\infty \qquad\text{uniformly in}\;x\in \overline{\Omega}. \tag{H1}
+%We state some observations  regarding the property of the solution $u$ to \eqref{eq:PDE0}.
+
+\begin{lem}\label{lem:f=0} Assume $f\geq 0$ in $\Omega$. Then $u(x) = 0$ whenever $f(x) = 0$. In particular, $f \equiv 0$ implies $u \equiv 0$.
+\end{lem}
+\begin{proof} It is clear that $u\geq 0$ in $\overline{\Omega}$. Using the optimal control formula (see \cite{Bardi1997,Hung2019}), we have
+\begin{equation}\label{e:foru}
+    u(x) = \inf \left\lbrace \int_0^\infty e^{-  s}\Big(c|\dot{\eta}(s)|^{q} +f(\eta(s))\Big)ds: \eta\in \mathrm{AC}([0,\infty);\overline{\Omega}), \eta(0) = x\right\rbrace
 \end{equation}
-We consider the following equation
-\begin{equation}\label{eq:C_eps}
-    \lambda u^\varepsilon(x) + H(x,Du^\varepsilon(x)) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad\text{in}\;\Omega.
+where 
+\begin{equation*}
+    c = \left(pq^{\frac{1}{p-1}}\right)^{-1} \qquad\text{and}\qquad \frac{1}{p} + \frac{1}{q} = 1.
+\end{equation*}
+Let $x\in \overline{\Omega}$ such that $f(x) = 0$. We can choose $\eta(s) = x$ for all $s\in [0,\infty)$ as an admissible path in \eqref{e:foru} to obtain that
+\begin{equation*}
+    u(x) \leq  \int_0^\infty e^{-  s}\Big(c|\dot{\eta}(s)|^{q} +f(\eta(s))\Big)ds = f(x) =  0.
+\end{equation*}
+As a consequence, if $f\equiv 0$, then $u\equiv 0$.
+\end{proof}
+\noindent We state the following lemma as a crucial estimate we will be using. It is a refined construction of the supersolution for \eqref{eq:PDEeps}.
+\begin{lem}\label{lem:super_refined} Let $\delta_0$ be defined as in \eqref{def:delta_0}.
+There exist positive constants $\nu = \nu(\delta_0)> 1$ and $C_\nu =\mathcal{O}\left(\delta_0^{-(\alpha+2)}\right)$ such that
+\begin{equation}\label{e:superwa}
+\begin{split}
+    &w(x) = \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} + \max f + C_\nu \varepsilon^{\alpha+2}, \qquad\;\;\,  p<2,\\
+    &w(x) = \nu \varepsilon \log\left(\frac{1}{d(x)}\right) + \max f+ C_\nu \varepsilon^2, \qquad  p=2,
+\end{split}
 \end{equation}
-Let $u^\varepsilon\in \rmC^2(\Omega)\cap \mathrm{C}^1(\overline{\Omega})$ be a bounded solution to \eqref{eq:C_eps}, say $|\lambda u^\varepsilon(x)| \leq C_1$ for all $x\in \overline{\Omega}$.
-In this section we show that an interior gradient bound also holds, i.e., if $x\mapsto|Du^\varepsilon(x)|$ has a maximum over $\overline{\Omega}$ at $x_0\in \Omega$ then $|Du^\varepsilon(x_0)| \leq C_2$ for all $x\in \Omega$.
-Here $C_1,C_2$ are independent of $\varepsilon>0$.\\
+are supersolutions of \eqref{eq:PDEeps} in $\Omega$. 
+%\item[(ii)] If $x\mapsto \mathrm{dist}(x,\partial\Omega)$ is continuously differentiable with $|\nabla \mathrm{dist}(x,\partial\Omega)| = 1$ everywhere in $\Omega$ then we can take $C_\nu = 0$ in \eqref{e:superwa}.
+\end{lem}
+%\textcolor{orange}{(Why is $\nu \in (1,2)$?
+I think when $\alpha$ is large, it can be larger than 2.
+But $\nu$ is certainly bounded.---Oh, you can choose $\delta_0$ so small that $\nu \in (1,2)$.
+But then $\delta_0$ depends on $\alpha$.)} -  \textcolor{red}{I think dependence on $\alpha$ is fine, as we fix $p$ to start with.} \textcolor{orange}{- Do we include that in the definition of $\delta_0$?} --  \textcolor{red}{I will just write $\nu$ for now, not requiring $\nu \leq 2$ anymore.}
 
-\noindent We will use the classical Bernstein's argument.
-Let $\varphi(x) = \frac{1}{2}|Du^\varepsilon(x)|^2$ for $x\in \Omega$.
-Differentiate \eqref{eq:C_eps} in $x_i$ then multiply the resulting equation with $u^\varepsilon_{x_i}$ and then sum over $i=1,2,\ldots, n$ we obtain
+\begin{proof} Let us first consider $1<p<2$.
+We have $|\nabla d(x)| = 1$ for all $x\in \Omega_\delta\backslash \overline{\Omega}_{\delta_0}$.
+Recall from Theorem \ref{thm:wellposed1<p<2} that $C_\alpha^p \alpha^p = C_\alpha \alpha (\alpha+1)$ and $p(\alpha+1) = \alpha+2$.
+Compute
 \begin{equation*}
-    2\lambda \varphi(x) + D_pH(x,Du^\varepsilon(x))\cdot D\varphi(x) - \varepsilon \Delta \varphi(x) + \Big(\varepsilon |D^2u^\varepsilon(x)| + D_xH(x,Du^\varepsilon(x))\cdot Du^\varepsilon(x)\Big) = 0.
+    |\nabla w(x)|^p = \nu^p\frac{(C_\alpha\alpha)^p\varepsilon^{p(\alpha+1)}}{(d(x)-\delta)^{p(\alpha+1)}} = \nu^p\frac{C_\alpha \alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}
 \end{equation*}
-If $\varphi(x)$ achieves its maximum over $\overline{\Omega}$ at $x_0\in \Omega$, then $D\varphi(x_0) = 0$ and $\Delta \varphi(x_0)\leq 0$, together with $\varepsilon |D^2u^\varepsilon(x)|^2\geq \frac{1}{n\varepsilon}(\varepsilon\Delta u^\varepsilon(x))^2\geq (\varepsilon\Delta u^\varepsilon(x))^2$ if $n\varepsilon < 1$ we deduce that
+and
 \begin{equation*}
-    \lambda |D u^\varepsilon(x_0)|^2 + \Big(\lambda u^\varepsilon(x_0)+H(x_0,Du^\varepsilon(x_0))\Big)^2 + D_xH(x_0,Du^\varepsilon(x_0))\cdot Du^\varepsilon(x_0) \leq 0.
+    \varepsilon\Delta w(x) = \nu\frac{C_\alpha\alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}} - \nu\frac{C_\alpha\alpha\varepsilon^{\alpha+2}\Delta d(x)}{(d(x)-\delta)^{\alpha+1}}.
 \end{equation*}
-Assume $|\lambda u^\varepsilon(x_0)|\leq C_1$, using \eqref{eq:grow} we deduce that
+We have
 \begin{equation*}
-    \frac{1}{2}H(x_0,Du^\varepsilon(x_0))^2 + D_xH(x_0,Du^\varepsilon(x_0))\cdot Du^\varepsilon(x_0) + \left(\frac{1}{\sqrt{2}}H(x_0,Du^\varepsilon(x_0) - \sqrt{2}C_1\right)^2 - \left(C_1\right)^2\leq 0
+    \begin{split}
+        \mathcal{L}^\varepsilon\left[w_\delta\right] \geq \frac{\nu C_\alpha\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + \frac{C_\alpha \alpha (\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}\left[\nu^p-\nu +\nu\frac{(d(x)-\delta)\Delta d(x)}{\alpha+1}\right].
+    \end{split}
 \end{equation*}
-which gives us $|Du^\varepsilon(x_0)|\leq C_2$ for some $C_2$ independent of $\varepsilon$. 
-\begin{rem} Assumption \eqref{eq:grow} is weaker than the combination of $p\mapsto H(x,p)$ is superlinear and $|D_xH(x,p)|\leq C(1+|p|)$.
+Recall that $K_2= \Vert \Delta d\Vert_{L^\infty}$. We observe that in the region where $\delta< d(x)\leq \delta_0$,
+\begin{equation*}
+    \left|\frac{(d(x)-\delta)\Delta d(x)}{\alpha+1}\right| \leq \frac{\delta_0\Vert \Delta d\Vert_{L^\infty}}{\alpha+1} \leq \frac{K_2\delta_0}{\alpha+1}\leq K_2\delta_0.
+\end{equation*}
+Therefore,
+\begin{equation}\label{e:choose_nu}
+    \begin{split}
+        \nu^p-\nu +\nu\frac{(d(x)-\delta)\Delta d(x)}{(\alpha+1)} \geq \nu^p - \nu - \nu K_2\delta_0 = \nu\Big(\nu^{p-1} - (1+K_2\delta_0)\Big).
+    \end{split}
+\end{equation}
+We will choose $\nu$ as follows. For $\gamma>1$, we have the inequality
+\begin{equation}\label{e:ineq}
+    \Big||x+y|^\gamma - |x|^\gamma\Big|\leq \gamma\Big(|x|+|y|\Big)^{\gamma-1}|y|
+\end{equation}
+for $x,y\in \mathbb{R}$, which implies that
+\begin{equation*}
+     0 \leq (1+K_2\delta_0)^{\alpha+1} - 1 \leq\underbrace{(\alpha+1)\left(1+K_2\delta_0\right)^\alpha K_2}_{C_2}\delta_0.
+\end{equation*}
+Hence $(1+K_2\delta_0)^{\alpha+1} \leq 1 + C_2\delta_0$. Since $\alpha+1 = \frac{1}{p-1}$,
+\begin{equation}\label{e:cru1}
+    (1+K_2\delta_0) \leq (1+C_2\delta_0)^{\frac{1}{\alpha+1}} = (1+C_2\delta_0)^{p-1}. 
+\end{equation}
+Choose $\nu = 1+C_2\delta_0$ in \eqref{e:choose_nu}and we obtain $\mathcal{L}[w]\geq 0$ in $\{x\in \Omega_\delta: \delta <d(x)\leq \delta_0\}$.
+Recall that $K_0 = \Vert d\Vert_{L^\infty}$ and $K_1 = \Vert \nabla d\Vert_{L^\infty}$.
+In the region where $d(x)\geq \delta_0$, we have
+\begin{align*}
+    \mathcal{L}[w] &= \frac{\nu C_\alpha\alpha\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + \max_{\Omega} f - f(x)\\
+    &+  \nu^p\frac{C_\alpha\alpha(\alpha+1)\varepsilon^{\alpha+1}}{(d(x)-\delta)^{\alpha+2}}|\nabla d(x)|^p - \nu \frac{C_\alpha \alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}|\nabla d(x)|^2
+    + \nu \frac{C_\alpha \alpha \varepsilon^{\alpha+2}\Delta d(x)}{(d(x)-\delta)^{\alpha+1}} + C_\nu \varepsilon^{\alpha+2}\\
+    &\geq \frac{C_\alpha \alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}\left(\nu^p|\nabla d(x)|^p - \nu |\nabla d(x)|^2 + \nu \frac{\Delta d(x)(d(x)-\delta)}{\alpha+1}\right) + C_\nu \varepsilon^{\alpha+2}\\
+    &\geq \left[C_\nu - C_3\left(\frac{1}{\delta_0}\right)^{\alpha+2}\right]\varepsilon^{\alpha+2}
+\end{align*}
+where 
+\begin{equation*}
+    C_3 = C_\alpha\alpha(\alpha+1) \left(\nu^pK_1^p + \nu K_1^2 + \nu \frac{K_0K_2}{\alpha+1}\right).
+\end{equation*}
+We can choose $C_\nu = C_3\delta_0^{-(\alpha+2)}$ to obtain $\mathcal{L}[w]\geq 0$ in this region $\{x\in \Omega_\delta:d(x)\geq \delta_0\}$. 
+\smallskip
+
+\noindent
+If $p=2$, then $\alpha = 0$. The same calculation holds true with $\nu = 1+K_2\delta_0$ and we choose $C_\nu = \delta_0^{-2}\nu (\nu K_1+K_0K_2)$.
+\end{proof}
+
+We start with a rate of convergence when $f = C_f$ for some constant $C_f$ in $\Omega$.
+%\begin{thm}[Zero data]\label{thm:rate_doubling0} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
+Assume $f\equiv 0$ in $\Omega$.
+Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u \equiv 0 $ be the unique solution to \eqref{eq:PDE0}.
+If $1<p<2$ then there exists a constant $C$ such that
+%    \begin{equation*}
+%    0\leq u^\varepsilon(x)\leq C \left(\frac{ \varepsilon^{\alpha+1}}{d(x)^\alpha} + \frac{\varepsilon^{\alpha+2}}{\delta_{0,\Omega}^{\alpha+2}}\right), \qquad x\in \Omega
+%\end{equation*}
+%where $\delta_{0,\Omega}$ is defined as in \eqref{def:delta_0}.
+In particular $0\leq  u^\varepsilon(x) \leq C\varepsilon$ for $x\in \Omega_\varepsilon$, but $|u^\varepsilon(x)| = \mathcal{O}\left(\varepsilon^{\alpha+1}\right)$ on each compact subset of $\Omega$.
+%\end{thm}
+%\textcolor{orange}{(Did you mean "In particular $0\leq  u^\varepsilon(x) \leq C\varepsilon$ for $x\in \Omega_\varepsilon$" ?)}
+
+\begin{thm}[Constant data]\label{thm:rate_doubling0} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
+Assume $f\equiv C_f$ in $\Omega$.
+Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u \equiv C_f$ be the unique solution to \eqref{eq:PDE0}.
+Then there exists a constant $C$ such that
+    \begin{equation*}
+    \begin{split}
+    &0\leq u^\varepsilon(x) - u(x)\leq C \left(\frac{ \varepsilon^{\alpha+1}}{d(x)^\alpha} + \frac{\varepsilon^{\alpha+2}}{\delta_{0,\Omega}^{\alpha+2}}\right),  \qquad\qquad \;\;\; \text{if}\; 1<p<2,\\
+    &0\leq u^\varepsilon(x) - u(x)\leq C \left(\varepsilon \mathrm{log}\left(\frac{1}{d(x)}\right) + \frac{\varepsilon^{2}}{\delta_{0,\Omega}^{2}}\right),  \qquad \text{if}\; p=2,
+    \end{split}
+\end{equation*}
+for $x\in \Omega$, where $\delta_{0,\Omega}$ is defined as in \eqref{def:delta_0}.
+In particular, for the case that $1<p<2$, $0\leq  u^\varepsilon(x) \leq C\varepsilon$ for $x\in \Omega_\varepsilon$, but $|u^\varepsilon(x)| = \mathcal{O}\left(\varepsilon^{\alpha+1}\right)$ on each compact subset of $\Omega$.
+\end{thm}
+%\textcolor{orange}{(Did you mean "In particular $0\leq  u^\varepsilon(x) \leq C\varepsilon$ for $x\in \Omega_\varepsilon$" ?)}
+\begin{proof} By Lemma \ref{lem:f=0} we have $u \equiv C_f$ in $\Omega$.
+From Lemma \ref{lem:lower-bound} and comparison principle, we have $u^\varepsilon - C_f$ is a solution to \eqref{eq:PDEeps} with data $f = 0$.
+So the conclusions follow from Lemma \ref{lem:super_refined}.
+%\begin{equation*}
+%    0\leq u^\varepsilon(x) - u(x)\leq \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} + C_\nu\varepsilon^{\alpha+2}, \qquad x\in \Omega.
+%\end{equation*}
+\end{proof}
+
+\begin{lem} Let $0<\kappa < \delta_0$ and $U_\kappa = \big\{x\in \Omega: 0<\mathrm{dist}(x,\partial\Omega) < \kappa\big\} = \Omega\backslash \overline{\Omega}_\kappa$. There holds
+\begin{equation*}
+    \mathrm{dist}(x,\partial\Omega_\kappa) = \kappa - \mathrm{dist}(x,\partial\Omega) \qquad\text{for all}\;x\in U_\kappa.
+\end{equation*}
+As a consequence, $x\mapsto \mathrm{dist}(x,\partial U_\kappa) = \min\big\{\mathrm{dist}(x,\partial \Omega_k),\mathrm{dist}(x,\partial \Omega)\big\}$ is twice continuously differentiable for $x\in \Omega\backslash \overline{\Omega}_{\frac{\kappa}{2}}$.
+Hence we can choose
+\begin{equation}\label{e:delta_kappa}
+    \delta_{0,U_\kappa} \geq \frac{\kappa}{4}.
+\end{equation}
+\end{lem}
+%\textcolor{orange}{I feel "...twice continuously differentiable away from $\partial \Omega_\frac{k}{2}$" is a little ambiguous.
+How about "...twice continuoously differentiable for $x \in \Omega \setminus \overline{\Omega}_\frac{\kappa}{2}$"?}
+\begin{proof} By the definition of $\delta_0$, $d(x) = \mathrm{dist}(x,\partial\Omega)$ is twice continuously differentiable in the region $U_{\delta_0} = \Omega\backslash \overline{\Omega}_{\delta_0}$.
+The proof follows from \cite[p.
+355]{gilbarg_elliptic_2001}.
+\end{proof}
+
+Next, we show the rate of convergence for compactly supported data $f$.
+
+\begin{thm}[Compactly supported data]\label{thm:rate_doubling1} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
+Assume that $f$ is Lipschitz and is compactly supported in $\Omega$.
+Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
+Then there exists a constant $C$ depends on the support of $f$ such that
+\begin{equation*}
+|u^\varepsilon(x) - u(x)| \leq C\sqrt{\varepsilon} \quad  \text{for} \quad x\in \Omega_{\varepsilon}.
+\end{equation*}
+Furthermore, on any compact subset $K\subset\Omega\backslash \mathrm{supp}(f)$, $|u^\varepsilon - u| = \mathcal{O}(\varepsilon)$.
+\end{thm}
+
+\begin{proof} Without loss of generality, we can assume that $f$ is supported in $\Omega_\kappa$ where $0<\kappa < \delta_{0}$.
+Let $g_\kappa = u^\varepsilon$ on $\partial\Omega_{\kappa}$. Then the solution $u^\varepsilon$ of \eqref{eq:PDEeps} also solves
+\begin{equation*}
+    \left\{
+  \begin{aligned}
+  u^\varepsilon(x) + |Du^\varepsilon(x)|^p-\varepsilon \Delta u^\varepsilon(x) &=0 \;\qquad \text{in } U_\kappa ,\\
+  u^\varepsilon(x) &= +\infty \quad \text{on } \partial \Omega,\\
+  u^\varepsilon(x) &= g_\kappa \;\;\quad \text{on } \partial \Omega_{\kappa},
+    \end{aligned}
+\right.
+\end{equation*}
+in $U_\kappa= \Omega \setminus \overline{\Omega}_{\kappa} = \{x\in \Omega: 0< d(x) < \kappa\}$.
+Let $\tilde{u}^\varepsilon\in \mathrm{C}^2(U_\kappa)$ be the solution to the following problem in the annulus $U_\kappa= \Omega \setminus \overline{\Omega}_{\kappa}$ (Theorem \ref{thm:wellposed1<p<2})
+\begin{equation*}
+    \left\{
+        \begin{aligned}
+            \tilde{u}^\varepsilon(x) + |D\tilde{u}^\varepsilon(x)|^p-\varepsilon \Delta \tilde{u}^\varepsilon(x) &=0 \;\qquad \text{in } U_\kappa ,\\
+            \tilde{u}^\varepsilon(x) &= +\infty \quad \text{on } \partial U = \partial \Omega\cup \partial \Omega_{\kappa}.
+        \end{aligned}
+    \right.
+\end{equation*}
+Here the boundary condition is understood as $\tilde{u}^\varepsilon(x)\to \infty$ as $d_\kappa(x)\to 0$ where $d_\kappa(\cdot)$ is the distance function from the boundary of the annulus $U_\kappa$, i.e.,
+\begin{equation*}
+    d_\kappa(x) = \min \big\lbrace \mathrm{dist}(x,\partial \Omega_\kappa),\mathrm{dist}(x,\partial\Omega)  \big\rbrace \leq d(x) \qquad\text{for}\;x\in U_\kappa.
+\end{equation*}
+Since $f = 0$ in $\overline{U}_\kappa$, by Lemma \ref{lem:f=0} $u=0$ in $\overline{U}_\kappa$. Hence it is also the unique state-constraint solution to
+\begin{equation*}
+    \left\{
+        \begin{aligned}
+            u(x)+ |Du(x)|^p &=0 \quad \text{in } U_\kappa ,\\
+            u(x)+ |Du(x)|^p &\geq 0 \quad \text{on } \partial U_\kappa = \partial \Omega \cup\partial \Omega_{\kappa}.
+        \end{aligned}
+    \right.
+\end{equation*}
+The vanishing viscosity of $\tilde{u}^\varepsilon \to 0$ in $U_\kappa$ can be quantified by Theorem \ref{thm:rate_doubling0}, which gives us
+\begin{equation*}
+\begin{split}
+    &0\leq \tilde{u}^\varepsilon(x) \leq \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d_\kappa(x)^\alpha}+C_3\left(\frac{\varepsilon}{\delta_{0,U_\kappa}}\right)^{\alpha+2}\qquad\quad\;\text{for}\;p<2,\\
+    &0\leq \tilde{u}^\varepsilon(x) \leq \nu \varepsilon \log\left(\frac{1}{d_\kappa(x)}\right)+C_\nu\left(\frac{\varepsilon}{\delta_{0,U_\kappa}}\right)^{2}\qquad\text{for}\;p=2,
+\end{split}    
+\end{equation*}
+for $x\in U_\kappa$. From \eqref{e:delta_kappa} and the comparison principle in $U_\kappa$, we have
+\begin{align}
+    &0\leq u^\varepsilon(x) \leq \tilde{u}^\varepsilon(x)  \leq \frac{\nu C_\alpha\varepsilon^{\alpha+1}}{d_\kappa(x)^{\alpha}} + C_3\left(\frac{4\varepsilon}{\kappa}\right)^{\alpha+2} \qquad\quad\;\text{for}\;p<2, \qquad \label{annulus2}\\
+    &0\leq u^\varepsilon(x)\leq \tilde{u}^\varepsilon(x) \leq \nu \varepsilon \log\left(\frac{1}{d_\kappa(x)}\right)+C_\nu\left(\frac{4\varepsilon}{\kappa}\right)^{2}\qquad\text{for}\;p=2,\label{annulus2p=2}
+\end{align}
+for $x\in U_\kappa$. We proceed with the doubling variable method. For $p<2$, consider the auxiliary functional 
+\begin{equation*}
+    \Phi(x,y)= u^\varepsilon(x) - u(y) -\frac{C_0|x-y|^2}{\sigma} - \frac{\theta C_\alpha \varepsilon^{\alpha +1}}{d(x)^\alpha}, \qquad (x,y)\in \overline{\Omega}\times \overline{\Omega},
+\end{equation*}
+where $C_0$ is the Lipschitz constant of $u$ from \eqref{e:C0}, $\sigma\in (0,1)$ and $\theta>1$ to be determined.
+The fact that $\displaystyle d(x)^\alpha u^\varepsilon(x) \to C_\alpha \varepsilon^{\alpha+1}$ as $d(x) \to 0$ implies
+\begin{equation*}
+    \max_{(x,y) \in \overline{\Omega} \times \overline{\Omega}} \Phi(x,y) = \Phi(x_\sigma, y_\sigma) \qquad\text{for some}\;(x_\sigma,y_\sigma) \in \Omega \times \overline{\Omega}.
+\end{equation*}
+From $\Phi(x_\sigma, y_\sigma) \geq \Phi(x_\sigma, x_\sigma)$, we can deduce that
+\begin{equation}\label{e:sigma}
+    \left| x_\sigma - y_\sigma \right| \leq \sigma.  
+\end{equation}
+If $ d(x_\sigma) \geq \frac{1}{2}\kappa$, since $x\mapsto \Phi(x,y_\sigma)$ has a maximum over $\Omega$ at $x=x_\sigma$, the subsolution test for $u^\varepsilon(x)$ gives us
+\begin{align}\label{e:subsln}
+    &u^\varepsilon(x_\sigma) + \left|\frac{2C_0(x_\sigma - y_\sigma)}{\sigma} -  \frac{\theta C_\alpha\alpha \varepsilon^{\alpha+1} \nabla d(x_\sigma)}{d(x_\sigma)^{\alpha+1}}\right|^p - f(x_\sigma)\nonumber\\
+    &\qquad -\varepsilon\left(\frac{2nC_0}{\sigma}+ \frac{\theta C_\alpha\alpha(\alpha+1) \varepsilon^{\alpha+1}|\nabla d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+2}} - \frac{\theta C_\alpha\alpha \varepsilon^{\alpha+1}\Delta d(x_\sigma)}{d(x_\sigma)^{\alpha+1}}\right) \leq 0.
+\end{align}
+Since $y\mapsto \Phi(x_\sigma,y)$ has a maximum over $\overline{\Omega}$ at $y = y_\sigma$, the supersolution test for $u(y)$ gives us
+\begin{align}\label{e:supersln}
+    u(y_\sigma) + \left|\frac{2C_0(x_\sigma - y_\sigma)}{\sigma}\right|^p - f(y_\sigma) \geq 0.
+\end{align}
+For simplicity, let us define
+\begin{equation*}
+    \xi_\sigma := \frac{2C_0(x_\sigma - y_\sigma)}{\sigma} \qquad\text{and}\qquad \zeta_\sigma :=- \frac{\theta C_\alpha\alpha \varepsilon^{\alpha+1} \nabla d(x_\sigma)}{d(x_\sigma)^{\alpha+1}}.
+\end{equation*}
+From \eqref{e:sigma} and the fact that we are considering $d(x_\sigma) \geq \frac{1}{2}\kappa$, 
+\begin{equation*}
+    |\xi_\sigma|\leq 2C_0 \qquad\text{and}\qquad |\zeta_\sigma| \leq \theta K_1 C_\alpha\alpha \left(\frac{\varepsilon}{d(x_\sigma)}\right)^{\alpha+1} \leq \theta K_1 C_\alpha \alpha  \left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+1}.
+\end{equation*}
+Using the inequality \eqref{e:ineq} with $\gamma = p > 1$, we deduce that
+\begin{align}\label{e:estia}
+    \Big||\xi_\sigma +\zeta_\sigma|^p - |\xi_\sigma|^p \Big| &\leq p\Big(|\xi_\sigma|+|\zeta_\sigma|\Big)^{p-1}|\zeta_\sigma|\nonumber\\
+    &\leq p\left[2C_0+\theta K_1 C_\alpha\alpha \left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+1}\right]^{p-1}\theta K_1 C_\alpha\alpha \left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+1}.
+\end{align}
+Using \eqref{e:estia} together with \eqref{e:subsln}, \eqref{e:supersln} and $|f(x_\sigma) - f(y_\sigma)|\leq C|x_\sigma - y_\sigma|\leq C\sigma$, we obtain that
+\begin{align*}
+     u^\varepsilon(x_\sigma) - u(y_\sigma) \leq & p\left(2C_0+\theta K_1 C_\alpha \alpha\left( \frac{2\varepsilon}{\kappa}\right)^{\alpha+1}\right)^{p-1}\theta K_1 C_\alpha \alpha \left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+1} + C\sigma\nonumber\\
+    &+2nC_0\left(\frac{\varepsilon}{\sigma}\right) + \theta K_1^2C_\alpha \alpha(\alpha+1)\left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+2} + \theta K_2 C_\alpha \alpha  \left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+1}\varepsilon\nonumber\\
+    &\leq C\left[\sigma + \frac{\varepsilon}{\sigma} + \left(1+\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1}\right)^{p-1}\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1} + \left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2} \right].
+    %&\leq C\sqrt{\varepsilon}
+\end{align*}
+By the fact that if $\gamma\in [0,1]$ then $(1+x)^\gamma \leq 1+x^\gamma$ for $x\in [0,1]$, we can get that, as $0<p-1\leq 1$,
+\begin{equation*}
+    \left(1+\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1}\right)^{p-1} \leq 1+ \left(\frac{\varepsilon}{\kappa}\right).
+\end{equation*}
+Therefore,
+\begin{equation*}
+     u^\varepsilon(x_\sigma) - u(y_\sigma) \leq C\left[\sigma + \frac{\varepsilon}{\sigma} + \left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1} + \left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2}\right]
+\end{equation*}
+where $C$ is independent of $\kappa$ and $\varepsilon$. Choosing $\sigma = \sqrt{\varepsilon}$, we obtain that (with $\kappa$ being fixed)
+\begin{equation}\label{e:final1}
+    \Phi(x_\sigma,y_\sigma) \leq u^\varepsilon(x_\sigma) - u(y_\sigma) \leq C\sqrt{\varepsilon}.
+\end{equation}
+If $d(x_\sigma) < \frac{1}{2}\kappa$, then $x_\sigma \in U_\kappa$ and furthermore $\mathrm{dist}(x_\sigma,\partial \Omega_\kappa) > \frac{1}{2}\kappa$.
+Indeed, for any $y\in\partial\Omega$ and $z\in \partial\Omega_k$, we have $|x_\sigma - z| + |x_\sigma - y| \geq |y-z|$.
+Taking the infimum over all $y\in \partial\Omega$, we deduce that
+\begin{equation*}
+    |x_\sigma - z| + d(x_\sigma) \geq \inf_{y\in \partial \Omega}|y-z| = d(z) = \kappa
+\end{equation*}
+since $z\in \partial\Omega_k = \{x \in \Omega: d(x) = \kappa\}$.
+Thus, we have $|x_\sigma - z| \geq \kappa - d(x_\sigma) > \frac{1}{2}\kappa$ for all $z\in \partial\Omega_k$, which implies that $\mathrm{dist}(x_\sigma,\partial\Omega_k)>\frac{1}{2}\kappa$ and therefore $d_\kappa(x_\sigma) = d(x_\sigma)$.
+By \eqref{annulus2} and the fact that $u \geq 0$, we have
+\begin{align}
+    \Phi(x_\sigma, y_\sigma)\leq u^\varepsilon(x_\sigma) - u(y_\sigma)\leq u^\varepsilon(x_\sigma) \leq  \frac{\nu C_\alpha\varepsilon^{\alpha+1}}{d(x)^{\alpha}} + C_3\left(\frac{4\varepsilon}{\kappa}\right)^{\alpha+2} \label{e:final2}.
+\end{align}
+Since $\Phi(x,x) \leq \Phi(x_\sigma,y_\sigma)$ for all $x\in \Omega$, we obtain from \eqref{e:final1} and \eqref{e:final2} that
+\begin{equation*}
+    u^\varepsilon(x)-u(x)-\frac{\theta C_\alpha  \varepsilon^{\alpha+1}}{d(x)^\alpha} \leq C\sqrt{\varepsilon} + \frac{\nu C_\alpha\varepsilon^{\alpha+1}}{d(x)^\alpha}, \qquad x\in \Omega.
+\end{equation*}
+Therefore,
+\begin{equation*}
+   -C \sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x) \leq C\sqrt{\varepsilon} + \frac{(\nu+\theta) C_\alpha  \varepsilon^{\alpha+1}}{d(x)^\alpha} 
+\end{equation*}
+for every $x\in \Omega$. We can send $\theta \to 1^+$ to simplify the constant further and get that 
+\begin{equation}
+   -C \sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x) \leq C\sqrt{\varepsilon} + \frac{(\nu+1)C_\alpha  \varepsilon^{\alpha+1}}{d(x)^\alpha}, \qquad x\in \Omega
+\end{equation}
+where $C$ depends on $\kappa$. It follows that $|u^\varepsilon(x)-u(x)| \leq C\sqrt{\varepsilon}$ for $x\in \Omega_\varepsilon$. 
+If $x\in U_k$, i.e., $f(x) = 0$, then \eqref{annulus2} gives us a better rate $\mathcal{O}(\varepsilon)$ in any compact set $K$ that is disjoint from $\mathrm{supp}(f)$. \\
+
+\noindent For $p=2$, we consider instead the functional 
+\begin{equation*}
+    \Phi(x,y) = u^\varepsilon(x) - u(y) - \frac{C_0|x-y|^2}{\sigma} - \theta \varepsilon \mathrm{log}\left(\frac{1}{d(x)}\right), \qquad (x,y)\in \overline{\Omega}\times \overline{\Omega}.
+\end{equation*}
+Similar to the previous case where $p<2$, the maximum of $\Phi$ must occur at $(x_\sigma,y_\sigma)\in \Omega\times\overline{\Omega}$ and $|x_\sigma - y_\sigma|\leq \sigma$.
+If $d(x_\sigma)\geq \frac{1}{2}\kappa$, by the subsolution test for $u^\varepsilon(x)$, we have
+\begin{align}\label{e:subslnp=2}
+    u^\varepsilon(x_\sigma)&+ \left|\frac{2C_0(x_\sigma - y_\sigma)}{\sigma} - \theta \varepsilon \frac{\nabla d(x_\sigma)}{d(x_\sigma)}\right|^2  -f(x_\sigma) \nonumber\\
+    &- 2nC_0\left(\frac{\varepsilon}{\sigma}\right) - \theta |\nabla d(x_\sigma)|^2 \left(\frac{\varepsilon}{d(x_\sigma)}\right)^2  + \theta \Delta d(x_\sigma)\left(\frac{\varepsilon^2}{d(x_\sigma)}\right) \leq 0.
+\end{align}
+By the supersolution test for $u(y)$, we have
+\begin{equation}\label{e:superslnp=2}
+    u(y_\sigma) + \left|\frac{2C_0(x_\sigma - y_\sigma)}{\sigma}\right|^2 - f(y_\sigma) \geq 0.
+\end{equation}
+Subtracting \eqref{e:superslnp=2} from \eqref{e:subslnp=2}, we have
+\begin{align*}
+    u^\varepsilon(x_\sigma) - u(y_\sigma) &\leq \left(4C_0+ \theta\varepsilon\frac{\nabla d(x_\sigma)}{d(x_\sigma)}\right)\left(\theta \varepsilon \frac{ \nabla d(x_\sigma)}{d(x_\sigma)}\right) \\
+    &+ C\sigma + 2nC_0 \left(\frac{\varepsilon}{\sigma}\right)+ \theta |\nabla d(x_\sigma)|^2 \left(\frac{\varepsilon}{d(x_\sigma)}\right)^2 + \theta|\Delta d(x_\sigma)| \frac{\varepsilon^2}{d(x_\sigma)}.
+\end{align*}
+Using $d(x_\sigma)\geq \frac{1}{2}\kappa$ and \eqref{boundond}, we see that
+\begin{align}\label{p=2a}
+    \Phi(x_\sigma,y_\sigma)&\leq u^\varepsilon(x_\sigma) - u(y_\sigma)\nonumber \\
+    &\leq 4K_1^2\theta(1+\theta)\left(\frac{\varepsilon}{\kappa}\right)^2 + C\sigma + 2nC_0\left( \frac{\varepsilon}{\sigma}\right) + 2\theta(K_2\varepsilon+4C_0K_1)\left(\frac{\varepsilon}{\kappa}\right)\nonumber\\
+    &\leq C\left(\sigma+\frac{\varepsilon}{\sigma} + \frac{\varepsilon}{\kappa} + \left(\frac{\varepsilon}{\kappa}\right)^2\right) \leq C\sqrt{\varepsilon}
+\end{align}
+where we choose $\sigma = \sqrt{\varepsilon}$.
+If $d(x_\sigma)<\frac{1}{2}\kappa$, then $x_\sigma\in U_\kappa$.
+Similar to the previous argument, we have $d_\kappa(x_\sigma) = d(x_\sigma)$ and from \eqref{annulus2p=2}
+\begin{equation}\label{p=2b}
+    \Phi(x_\sigma,y_\sigma) \leq \nu\varepsilon \log\left(\frac{2}{\kappa}\right) + C_\nu\left(\frac{4\varepsilon}{\kappa}\right)^2 \leq C\left(\varepsilon+\varepsilon\,|\log(\kappa)| + \left(\frac{\varepsilon}{\kappa}\right)^2\right).
+\end{equation}
+Since $\Phi(x,x)\leq \Phi(x_\sigma,y_\sigma)$ for $x\in \Omega$, we obtain from \eqref{p=2a} and \eqref{p=2b} that
+\begin{equation*}
+    u^\varepsilon(x) - u(x) - \theta\varepsilon\log\left(\frac{1}{d(x)}\right) \leq C\sqrt{\varepsilon} +C\varepsilon \left(1+|\log(\kappa)| + \frac{\varepsilon}{\kappa^2}\right).
+\end{equation*}
+Let $\theta\to 1^+$ and we obtain 
+\begin{equation*}
+    -C\sqrt{\varepsilon}\leq u^\varepsilon(x) - u(x) \leq C\sqrt{\varepsilon} +  \varepsilon \log\left(\frac{1}{d(x)}\right), \qquad x\in \Omega.
+\end{equation*}
+Similar to the previous case, in the region where $0< d(x)\leq \varepsilon$, $|u^\varepsilon-u|=\mathcal{O}(\sqrt{\varepsilon})$ since $\varepsilon|\log(\varepsilon)|\leq \sqrt{\varepsilon}$.
+Therefore, the conclusion follows.
+\end{proof}
+
+%\begin{rem} From \cite{Lasry1989} we know that, if $p\in \left(\frac{3}{2},2\right]$ then $u^\varepsilon(x) - \frac{C_\alpha\varepsilon^{\alpha+1}}{d(x)^\alpha}$ is uniformly bounded in $\Omega$.
+Theorem \ref{thm:rate_doubling1} says that, if $f$ is compactly supported in $\Omega$ then
+%\begin{equation*}
+%    u^\varepsilon(x) - (\nu+1)\frac{C_\alpha\varepsilon^{\alpha+1}}{d(x)^\alpha}
+%\end{equation*}
+%is uniformly bounded from above in $\Omega$ for all $p\in (1,2)$.
+Recall that $\nu = 1+C_2\delta_{0,\Omega}$ from Lemma \ref{lem:super_refined}, we can always choose $\delta_0$ small so that roughly $\nu\approx 2^+$.
+%(\textcolor{red}{This sounds really weird.})
+%\end{rem}
+
+%\textcolor{orange}{(I think Theorem \ref{thm:rate_doubling1} only says $u^\epsilon-\frac{3C_\alpha \epsilon^{\alpha+1}}{d(x)^\alpha}$ is uniformly bounded above by some constant $C$.
+It doesn't say $u^\epsilon-\frac{3C_\alpha \epsilon^{\alpha+1}}{d(x)^\alpha}$ is uniformly bounded below.
+)}
+
+\begin{rem} For a general datum Lipschitz $f\in \mathrm{C}(\overline{\Omega})$, it is natural to think about using cutoff function argument.
+Let $\chi_{{\kappa}}\in \mathrm{C}_c^\infty(\Omega)$ such that $0\leq \chi_{\kappa}\leq 1$, $\chi_\kappa = 1$ in $\Omega_{2\kappa}$ and $\mathrm{supp}\;\chi_\kappa\subset\Omega_\kappa$.
+Let $u^\varepsilon_\kappa\in \rmC^2(\Omega)\cap\overline{\Omega}$ solves \eqref{eq:PDEeps} with datum $f\chi_{\kappa}$.
+Then as $u^\varepsilon_\kappa\to u^\varepsilon$ as $\kappa\to 0$ (since $f\chi_\kappa\to f$ in the weak$^*$ topology of $L^\infty(\Omega)$, we have a continuity of solution with respect to data in this topology \cite[Remark II.1]{Lasry1989}).
+However, it is not clear at the moment how to quantify this rate of convergence, since $f\chi_\kappa$ does not converge to $f$ in the uniform norm, unless $f = 0$ on $\partial\Omega$.
 \end{rem}
 
+\begin{thm}[Zero boundary data]\label{thm:rate_doubling2} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
+Assume that $f$ is Lipschitz such that $f = 0$ on $\partial\Omega$.
+Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
+Then there exists a constant $C$ such that
+\begin{equation*}
+|u^\varepsilon(x) - u(x)| \leq C\sqrt{\varepsilon} \quad  \text{for} \quad x\in \Omega_{\varepsilon}.
+\end{equation*}
+\end{thm}
+
+\begin{proof} Let $L = \Vert \nabla f\Vert_{L^\infty(\Omega)}$ be the Lipschitz constant of $f$.
+For $\kappa>0$ small such that $0<\kappa<\delta_0$ and $x\in \Omega\backslash \Omega_\kappa$, let $x_0$ be the projection of $x$ onto $\partial\Omega$.
+We observe that
+\begin{equation}\label{e:bound_aa}
+    f(x) = f(x) - f(x_0) \leq L|x-x_0| = L\kappa.
+\end{equation}
+Define
+\begin{equation*}
+    g_\kappa(x) = 
+    \begin{cases}
+        0           &\qquad\text{if}\;0\leq d(x) \leq \frac{\kappa}{2},\\
+        2L\left(d(x)-\frac{\kappa}{2}\right)       &\qquad\text{if}\;\frac{\kappa}{2}\leq d(x) \leq \kappa.
+    \end{cases}
+\end{equation*}
+
+%\textcolor{orange}{(A question is why we can assume $f\in C^1(\overline{\Omega})$?
+If you smooth $f$ up by mollifier, the support of $f$ might go outside of $\Omega$.
+Another question is I think you want $g_k$ to be $2L(d(x)-\frac{\kappa}{2})$ if $\frac{\kappa}{2} \leq d(x) \leq \kappa $.
+)}
+\noindent
+It is clear that for $x\in \partial\Omega_k$, $g_\kappa(x) = L\kappa \geq f(x)$ since \eqref{e:bound_aa}. Therefore, we can define the following continuous function
+\begin{equation*}
+    f_\kappa(x) = 
+    \begin{cases}
+        0             &\qquad\text{if}\;0\leq d(x) \leq \frac{\kappa}{2},\\
+        \min \left\lbrace g_\kappa(x), f(x) \right\rbrace &\qquad\text{if}\;\frac{\kappa}{2}\leq d(x) \leq \kappa,\\
+        f(x) &\qquad\text{if}\;\kappa \leq d(x).
+    \end{cases}
+\end{equation*}
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.35]{Drafts and notes/fig1.png}
+    \caption{Graph of the function $f_\kappa$.}
+    \label{fig:f_kappa}
+\end{figure}
+A graph of $f_\kappa$ is given in Figure \ref{fig:f_kappa}.
+The continuity at $x\in \partial\Omega_\kappa$ comes from the fact that when $d(x) =\kappa$, we have $g_k(x) = L\kappa \geq f(x)$ by \eqref{e:bound_aa}.
+It is clear that $f_\kappa$ is Lipschitz with $\Vert f_\kappa\Vert_{L^\infty(\Omega)}\leq L$ as well and $f_\kappa\to f$ uniformly as $\kappa\to 0$.
+Indeed, we have $0\leq f_\kappa \leq f$ and
+\begin{equation*}
+    0\leq \max_{x\in \overline{\Omega}} (f(x) - f_\kappa(x)) \leq \max_{x\in \overline{\Omega}\backslash \overline{\Omega}_\kappa} (f(x) - f_\kappa(x)) = \max_{x\in \overline{\Omega}\backslash \overline{\Omega}_\kappa} f(x) \leq L\kappa.
+\end{equation*}
+Let $u^\varepsilon_\kappa\in \rmC^2(\Omega)\cap\overline{\Omega}$ be the solution to \eqref{eq:PDEeps} with datum $f\chi_{\kappa}$ and $u_k\in \mathrm{C}(\overline{\Omega})$ be the corresponding solution to \eqref{eq:PDE0} with datum $f{\chi_\kappa}$.
+By comparison principle (\cite[Corollary II.1]{Lasry1989}) we have
+\begin{equation}\label{e:bound_2aa}
+    0\leq u^\varepsilon(x) - u^\varepsilon_\kappa(x) \leq L\kappa \qquad\text{for}\;x\in \Omega.
+\end{equation}
+By the comparison principle for \eqref{eq:PDE0}, we also have
+\begin{equation}\label{e:bound_2ab}
+    0\leq u(x) - u_\kappa(x) \leq L\kappa \qquad\text{for}\;x\in \Omega.
+\end{equation}
+If $1<p<2$, by Theorem \ref{thm:rate_doubling1}, there exists a constant $C$ independent of $\kappa$ such that
+\begin{equation}\label{e:bound_2ac}
+    -C\sqrt{\varepsilon}\leq u^\varepsilon_\kappa(x) - u_\kappa(x)\leq C\left[\sqrt{\varepsilon} + \left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1} + \left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2} + \frac{\varepsilon^{\alpha+1}}{d(x)^\alpha}\right], \qquad x\in \Omega.
+\end{equation}
+Combining \eqref{e:bound_2aa}, \eqref{e:bound_2ab} and \eqref{e:bound_2ac}, we obtain
+\begin{equation*}
+\begin{split}
+   -C\sqrt{\varepsilon}\leq u^\varepsilon(x) - u(x) &= \Big(u^\varepsilon(x) - u^\varepsilon_\kappa(x)\Big) + \Big(u^\varepsilon_\kappa(x) - u_\kappa(x)\Big) + \Big(u_\kappa(x) - u(x)\Big) \\
+    &\leq L\kappa + C\left[\sqrt{\varepsilon} + \left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1} + \left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2} + \frac{\varepsilon^{\alpha+1}}{d(x)^\alpha}\right], \qquad x\in \Omega.
+\end{split}
+\end{equation*}
+Choose $\kappa = \sqrt{\varepsilon}$. We deduce that
+\begin{equation*}
+    -C\sqrt{\varepsilon}\leq u^\varepsilon(x) - u(x) \leq C\sqrt{\varepsilon} + \frac{C\varepsilon^{\alpha+1}}{d(x)^\alpha}
+\end{equation*}
+for $x\in \Omega$ and the conclusion follows. \\
+
+\noindent If $p=2$, by Theorem \ref{thm:rate_doubling1}, there exists a constant $C$ independent of $\kappa$ such that
+\begin{equation}\label{e:bound_2acp=2}
+    -C\sqrt{\varepsilon}\leq u^\varepsilon_\kappa(x) - u_\kappa(x) \leq C\left[\sqrt{\varepsilon} + \varepsilon + \varepsilon |\log(\kappa)|+\left(\frac{\varepsilon}{\kappa}\right)^2 + \varepsilon\log\left(\frac{1}{d(x)}\right)\right], \qquad x\in \Omega.
+\end{equation}
+Combining \eqref{e:bound_2aa}, \eqref{e:bound_2ab} and \eqref{e:bound_2acp=2}, we obtain
+\begin{equation*}
+\begin{split}
+   -C\sqrt{\varepsilon}\leq u^\varepsilon(x) - u(x) &= \Big(u^\varepsilon(x) - u^\varepsilon_\kappa(x)\Big) + \Big(u^\varepsilon_\kappa(x) - u_\kappa(x)\Big) + \Big(u_\kappa(x) - u(x)\Big) \\
+    &\leq L\kappa + C\left[\sqrt{\varepsilon} + \varepsilon|\log(\kappa)| + \left(\frac{\varepsilon}{\kappa}\right)^{2} + \varepsilon\log\left(\frac{1}{d(x)}\right) \right], \qquad x\in \Omega.
+\end{split}
+\end{equation*}
+Choose $\kappa = \varepsilon$. We deduce that
+\begin{equation*}
+    -C\sqrt{\varepsilon}\leq u^\varepsilon(x) - u(x) \leq C\sqrt{\varepsilon} +\varepsilon\log\left(\frac{1}{d(x)}\right)
+\end{equation*}
+for $x\in \Omega$ and the conclusion follows. 
+\end{proof}
+
+%\begin{thm}[General bounded Lipschitz data]\label{thm:rate_doubling1} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
+Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
+Then there exists a constant $C$ such that
+%\begin{equation*}
+%|u^\varepsilon(x) - u(x)| \leq C\sqrt{\varepsilon} \quad  \text{for} \quad x\in \Omega_{\varepsilon}.
+%\end{equation*}
+%\end{thm}
+
+%\begin{proof} Let $\kappa \in (0,1)$ and $\chi_{\kappa}\in \mathrm{C}_c^\infty(\mathbb{R}^n)$ such that $0\leq \chi_\kappa \leq 1$, $\chi = 1$ in $\Omega_{2\kappa}$ and $\mathrm{supp}(\chi_\kappa)\subset \Omega_\kappa$ and
+%\begin{equation*}
+%    \max_{x\in \overline{\Omega}}|\nabla \chi_\kappa(x)| \leq \frac{C}{\kappa} .
+%\end{equation*}
+%Denote $f_\kappa(x) = f(x)\chi_\kappa(x)$ for $x\in \overline{\Omega}$. It is clear that 
+%\begin{equation*}
+%    \mathrm{Lip}(f_\kappa)\leq \frac{C \max  f}{\kappa} + \mathrm{Lip}(f).
+%\end{equation*}
+%Applying Theorem \ref{thm:rate_doubling1} for
+
+%\end{proof}
+
+%\nocite{*}
+
+%\clearpage
+
+%\section{Rate of convergence via nonlinear adjoint method}
+
+\begin{appendices}
+\section{Proofs of some preliminary results}
+\begin{proof}[Proof of Theorem \ref{thm:grad_1}] Let $\theta\in (0,1)$ be chosen later, $\varphi\in \mathrm{C}_c^\infty(\Omega)$, $0\leq \varphi\leq 1$, $\mathrm{supp}\;\varphi\subset \Omega$ and $\varphi = 1$ on $\Omega_\delta$ such that
+\begin{equation}\label{e:ass_power}
+    |\Delta \varphi(x)| \leq C|\varphi(x)|^\theta \qquad\text{and}\qquad |D \varphi(x)|^2 \leq C\varphi^{1+\theta}
+\end{equation}
+for $x\in \Omega$ and $C = C(\delta,\theta)$.
+Let $w(x) = |Du(x)|^2$ for $x\in \Omega$. The goal is to derive an equation for $\varphi w$. The equation for $w$ is given by
+\begin{equation*}
+    -\varepsilon \Delta w + p|D u|^{p-2}D u \cdot D w + 2  w - D f\cdot D u + \varepsilon |D^2u|^2 = 0 \qquad\text{in}\;\Omega.
+\end{equation*}
+Using that, we can derive an equation for $(\varphi w)$ as follows.
+\begin{align*}
+    &-\varepsilon \Delta (\varphi w) + p|D u|^{p-2}D u \cdot D (\varphi w) + 2  (\varphi w) + \varepsilon \varphi|D^2u|^2 + 2\varepsilon \frac{D \varphi}{\varphi}\cdot D (\varphi w) \\
+    &\qquad\qquad\qquad\qquad = \varphi(D f\cdot D u) + p|D u|^{p-2}(D u\cdot D \varphi)w -\varepsilon w \Delta \varphi + 2\varepsilon \frac{|D \varphi|^2}{\varphi}w
+    \qquad\text{in}\;\mathrm{supp}\;\varphi.
+\end{align*}
+Assume that $\varphi w$ achieves its maximum over $\overline{\Omega}$ at $x_0\in \Omega$.
+Then we can further assume that $x_0\in \mathrm{supp}\;\varphi$, since otherwise the maximum of $\varphi w$ over $\overline{\Omega}$ is zero.
+By the classical maximum principle
+\begin{equation*}
+    -\varepsilon \Delta(\varphi w)(x_0)\geq 0 \qquad\text{and}\qquad |D(\varphi w)(x_0)| = 0.
+\end{equation*}
+Using that in the equation of $\varphi w$ above, we obtain that
+\begin{equation*}
+    \varepsilon \varphi|D^2u|^2 \leq  \varphi (Df\cdot Du)+ p|Du|^{p-1} |D\varphi|w + \varepsilon w |\Delta\varphi|  + 2\varepsilon  w\frac{|D\varphi|^2}{\varphi},
+\end{equation*}
+where all terms are evaluated at $x_0$. Using \eqref{e:ass_power} we have
+\begin{equation}\label{e:est_for_D^2u}
+    \varepsilon \varphi|D^2u|^2 \leq  \varphi |Df|w^{\frac{1}{2}}+ Cp w^{\frac{p-1}{2}+1} \varphi^{\frac{1+\theta}{2}} + C\varepsilon w \varphi^{\theta} + 2C\varepsilon  w\varphi^\theta.
+\end{equation}
+By Cauchy-Schwartz inquality, we have $n|D^2u|^2\geq (\Delta u)^2$, thus if $n\varepsilon < 1$ then
+\begin{equation}\label{e:est_for_D^2u_2}
+    \varepsilon |D^2u|^2 \geq \frac{(\varepsilon \Delta u)^2}{n\varepsilon} \geq (\varepsilon \Delta u)^2 = \left(  u + |Du|^p - f\right)^2 \geq |Du|^{2p} - 2C_0|Du|^p \geq \frac{|Du|^{2p}}{2} - 2K_0.
+\end{equation}
+Using \eqref{e:est_for_D^2u_2} in \eqref{e:est_for_D^2u} we obtain that
+\begin{equation*}
+    \varphi\left(\frac{1}{2}w^p - 2K_0\right) \leq \varphi |Df|w^{\frac{1}{2}}+ Cp w^{\frac{p-1}{2}+1} \varphi^{\frac{1+\theta}{2}} + 3C\varepsilon w \varphi^{\theta}.
+\end{equation*}
+Multiplying both sides by $\varphi^{p-1}$, we deduce that
+\begin{align*}
+    (\varphi w)^p \leq 4K_0\varphi^{p-1} + 2\Vert Df\Vert_{L^\infty}\varphi^p w^{\frac{1}{2}} + 2Cp \varphi^{\frac{2p+\theta - 1}{2}}w^{\frac{p+1}{2}} + 6C\varepsilon \varphi^{p+\theta - 1}w.
+\end{align*}
+Choose $2p+\theta -1 \geq p+1$, i.e., $p+\theta\geq 2$. This is always possible with the requirement $\theta \in (0,1)$, as $1<p <\infty$. We deduce that 
+\begin{equation}\label{e:est_for_D^2u_3}
+    (\varphi w)^p \leq C\left(1+ (\varphi w)^\frac{1}{2} + (\varphi w)^\frac{p+1}{2} +(\varphi w)\right)
+\end{equation}
+As a polynomial in $z = (\varphi w)(x_0)$, this implies that $(\varphi w)(x_0)\leq C$ where $C$ depends on coefficients of the right hand side of \eqref{e:est_for_D^2u_3}, which implies our desired gradient bound since $\overline{\Omega}_\delta\subset \mathrm{supp}\;\varphi$.
+\end{proof}
+
+\begin{proof} [Proof of Theorem \ref{thm:wellposed1<p<2}] If $p\in (1,2)$, we use the ansatz $ u(x) = C_\varepsilon d(x)^{-\alpha}$ to find a solution for \eqref{eq:PDEeps}.
+Plugging it into \eqref{eq:PDEeps}, we obtain that
+\begin{equation*}
+    |Du (x)|^p = \frac{(\alpha C_\varepsilon)^p }{d(x)^{p(\alpha+1)}}|D d(x)|^p \qquad\text{and}\qquad\varepsilon\Delta u(x) = \frac{\varepsilon C_\varepsilon\alpha(\alpha+1)}{d(x)^{\alpha+2}}|D d(x)|^2 - \frac{\varepsilon C_\varepsilon\alpha}{d(x)^{\alpha+1}}\Delta d(x).
+\end{equation*}
+Since $|D d(x)| = 1$ for $x$ near $\partial\Omega$, as $x\to \partial \Omega$, the highest explosive order terms are
+\begin{equation*}
+         C_\varepsilon^p \alpha^p d^{-(\alpha+1)p}  -\varepsilon C_\varepsilon \alpha(\alpha+1)d^{-(\alpha+2)}.
+\end{equation*}
+Setting the above to be zero, we deduce that 
+\begin{equation}\label{e:relation}
+    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}\right) \varepsilon^{\frac{1}{p-1}} = \frac{1}{\alpha}(\alpha+1)^{\alpha+1}\varepsilon^{\alpha+1}.
+\end{equation}
+For $0<\delta < \frac{1}{2}\delta_0$ and $\eta$ small, define
+\begin{equation*}
+\begin{split}
+    \overline{w}_{\eta,\delta}(x) &= \frac{(C_\alpha+\eta)\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + M_\eta, \qquad x\in \Omega_\delta,\\
+    \underline{w}_{\eta,\delta}(x) &= \frac{(C_\alpha-\eta)\varepsilon^{\alpha+1}}{(d(x)+\delta)^\alpha} - M_\eta, \qquad x\in \Omega^\delta,
+\end{split}
+\end{equation*}
+where $C_\alpha = \frac{1}{\alpha} (\alpha+1)^{\alpha+1} $, $M_\eta$ to be chosen.
+We will show that $\overline{w}_{\eta,\delta}$ is a supersolution of \eqref{eq:PDEeps} in $\Omega_\delta$, while $\underline{w}_{\eta,\delta}$ is a subsolution of \eqref{eq:PDEeps} in $\Omega^\delta$.
+We have
+\begin{align*}
+    \mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) &= \frac{ (C_\alpha + \eta)\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + M_\eta + \frac{(C_\alpha+\eta)^p \alpha^p\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}|D d(x)|^p - f(x) \\
+    & \qquad\qquad\qquad\qquad\qquad - \frac{(C_\alpha+\eta)\alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}|D d(x)|^2 + \frac{(C_\alpha+\eta)\alpha \varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+1}}\Delta d(x)\\
+    &\geq M_\eta - f(x) + \underbrace{\frac{\nu C_\alpha\alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}\left[\nu^{p-1}|Dd(x)|^{p-1} - |Dd(x)|^2 + \frac{(d(x)-\delta)\Delta d(x)}{\alpha+1}\right]}_{I}
+\end{align*}
+where we use $(C_\alpha\alpha)^p = C_\alpha\alpha(\alpha+1)$ and $\nu = \frac{C_\alpha+\eta}{C_\alpha} \in (1,2)$ for small $\eta$. Let
+\begin{equation*}
+    \delta_\eta : = \frac{\alpha+1}{K_2}\left[\nu^{p-1}-1\right] \to 0 \qquad\text{as}\qquad \eta \to 0.
+\end{equation*}
+Recall \eqref{boundond} and there are two cases to be considered.
+\begin{itemize}
+    \item If $0< d(x)-\delta <\delta_\eta < \delta_0$ for $\eta$ small, then $|Dd(x)| = 1$, and thus $I\geq 0$.
+Hence $\mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right]\geq 0$ if we choose $M_\eta \geq \max_{\overline{\Omega}} f$.
+
+    \item If $d(x)-\delta\geq \delta_\eta$, then 
+    \begin{equation*}
+        I \leq \left(\frac{1}{\delta_\eta}\right)^{\alpha+2}\nu C_\alpha \alpha(\alpha+1)\left[\nu^{p-1}K_1^{p-1}+K_1^2+K_2K_0\right]\varepsilon^{\alpha+2}.
+    \end{equation*}
+    Therefore, if we choose $M_\eta = \sup_{\overline{\Omega}} f + C\varepsilon^{\alpha+2}$ for $C$ large enough (depending on $\eta$), then $\mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right]\geq 0$.
+\end{itemize}
+Therefore, $\overline{w}_{\eta,\delta}$ is a supersolution in $\Omega_\delta$. Similarly, we have 
+\begin{align*}
+    \mathcal{L}_\varepsilon\left[\underline{w}_{\eta,\delta}\right](x) &= \frac{ (C_\alpha - \eta)\varepsilon^{\alpha+1}}{(d(x)+\delta)^\alpha} - M_\eta + \frac{(C_\alpha-\eta)^p \alpha^p\varepsilon^{\alpha+2}}{(d(x)+\delta)^{\alpha+2}}|D d(x)|^p - f(x) \\
+    & \qquad\qquad\qquad\qquad\qquad - \frac{(C_\alpha-\eta)\alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)+\delta)^{\alpha+2}}|D d(x)|^2 + \frac{(C_\alpha-\eta)\alpha \varepsilon^{\alpha+2}}{(d(x)+\delta)^{\alpha+1}}\Delta d(x)\\
+    &= - M_\eta - f(x) \\
+    &+\underbrace{\frac{\nu C_\alpha\alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)+\delta)^{\alpha+2}}\left[\nu^{p-1}|Dd(x)|^{p-1} - |Dd(x)|^2 + \frac{(d(x)+\delta)\Delta d(x)}{\alpha+1}+\frac{(d(x)+\delta)^2}{\alpha(\alpha+1)\varepsilon}\right]}_{J}
+\end{align*}
+where $\nu = \frac{C_\alpha-\eta}{C_\alpha}\in (0,1)$ for small $\eta$. Let
+\begin{equation*}
+    \delta_\eta := \left(1-\nu^{p-1}\right)\left(\frac{1+K_2\alpha\varepsilon}{\alpha(\alpha+1)\varepsilon}\right) \to 0 \qquad\text{as} \qquad \eta\to 0.
+\end{equation*}
+Recall \eqref{boundond}, and there are two cases.
+\begin{itemize}
+    \item $0<d(x)+\delta<\delta_\eta < \delta_0$ for $\eta$ small, then $|Dd(x)| = 1$ , and thus $J\leq 0$.
+Hence $\mathcal{L}^\varepsilon\left[\underline{w}_{\eta,\delta}\right]\leq 0$ if we choose $M_\eta \geq -\max_{\Omega}f$.
+    \item If $d(x)+\delta\geq \delta_n$, then
+    \begin{equation*}
+        |J|\leq \left(\frac{1}{\delta_n}\right)^{\alpha+2} \nu C_\alpha\alpha(\alpha+1)\left[K_1^{p-1}+K_1^2 + \frac{K_0K_2}{\alpha+1} + \frac{K_0^2}{\alpha(\alpha+1)\varepsilon}\right]\varepsilon^{\alpha+2}
+    \end{equation*}
+     Therefore, if we choose $M_\eta = -\sup_{\overline{\Omega}} f - C\varepsilon^{\alpha+2}$ for $C$ large enough (depending on $\eta$), then $\mathcal{L}^\varepsilon\left[\underline{w}_{\eta,\delta}\right]\leq 0$.
+\end{itemize}
+For $p=2$, we use the ansatz $u(x) = -C_\varepsilon \log(d(x))$ instead. Similarly to the previous case, we find $u(x) = -\varepsilon\log(d(x))$. For $0<\delta<\frac{1}{2}\delta_0$, we define 
+\begin{equation*}
+    \begin{split}
+        &\overline{w}_{\eta,\delta}(x) = -(1+\eta)\varepsilon\log(d(x)-\delta) + M_\eta, \qquad x\in \Omega_\delta,\\
+        &\underline{w}_{\eta,\delta}(x) = -(1-\eta)\varepsilon\log(d(x)-\delta) - M_\eta, \qquad x\in \Omega^\delta,
+    \end{split}
+\end{equation*}
+where $M_\eta$ is to be chosen so that $\overline{w}_{\eta,\delta}(x)$ is a supersolution in $\Omega_\delta$ and $\underline{w}_{\eta,\delta}$ is a subsolution in $\Omega^\delta$.
+We omit the computations, as they are similar to the previous case.
+\smallskip
+
+\noindent We divide the rest of the proof into 3 steps.
+We first construct a minimal solution, then a maximal solution to \eqref{eq:PDEeps}, and finally show that they are equal to conclude the existence and uniqueness of solution to \eqref{eq:PDEeps}.
+\smallskip
+
+\paragraph{\textbf{Step 1.}} There exists a minimal solution $\underline{u}\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that $v\geq \underline{u}$ for any other solution $v\in \mathrm{C}^2(\Omega)$ solving \eqref{eq:PDEeps}.
+
+\begin{proof} Let $w_{\eta,\delta}\in \mathrm{C}^2(\Omega)$ solve
+    \begin{equation}\label{e:w_def}
+    \begin{cases}
+        \mathcal{L}^\varepsilon\left[w_{\eta,\delta}\right] = 0 &\qquad\text{in}\;\Omega,\\
+        \qquad w_{\eta,\delta} = \underline{w}_{\eta,\delta} &\qquad\text{on}\;\partial\Omega.
+    \end{cases}
+    \end{equation}
+    \begin{itemize}
+        \item Fix $\eta>0$.
+As $\delta\to 0$, the value of $\underline{w}_{\eta,\delta}$ blows up on the boundary.
+Therefore, by the standard comparison principle for the second-order elliptic equation with Dirichlet boundary, $\delta_1 \leq  \delta_2$ implies $w_{\eta,\delta_1}\geq  w_{\eta,\delta_2}$ on $\overline{\Omega}$.
+        \item For $\delta'>0$, since $\underline{w}_{\eta,\delta'}$ is a subsolution in $\overline{\Omega}$ with finite boundary, we obtain that
+            \begin{equation}\label{e:cp_delta1}
+                0<\delta \leq \delta'\qquad\Longrightarrow\qquad \underline{w}_{\eta,\delta'} \leq w_{\eta_,\delta'}\leq w_{\eta,\delta} \qquad\text{on}\;\overline{\Omega}.
+            \end{equation}
+        \item Similarly, since $\overline{w}_{\eta,\delta'}$ is a supersolution on $\Omega_{\delta'}$ with infinity value on the boundary $\partial\Omega_{\delta'}$, by comparison principle
+            \begin{equation}\label{e:cp_delta2}
+                w_{\eta,\delta} \leq \overline{w}_{\eta, \delta'} \qquad\text{in}\;\Omega_{\delta'} \qquad\Longrightarrow\qquad w_{\eta,\delta} \leq \overline{w}_{\eta,0} \qquad\text{in}\;\Omega.
+            \end{equation}
+    \end{itemize}
+    \noindent From \eqref{e:cp_delta1} and \eqref{e:cp_delta2}, we have
+    \begin{equation}\label{e:cp_delta3}
+        0<\delta \leq \delta'\qquad\Longrightarrow\qquad \underline{w}_{\eta,\delta'} \leq w_{\eta_,\delta'}\leq w_{\eta,\delta} \leq \overline{w}_{\eta,0} \qquad\text{in}\;\Omega.
+    \end{equation}
+    Thus, $\{w_{\eta,\delta}\}_{\delta>0}$ is locally bounded in $L^{\infty}_{\mathrm{loc}}(\Omega)$ ($\{w_{\eta,\delta}\}_{\delta>0}$ is uniformly bounded from below).
+Using the local gradient estimate for $w_{\eta,\delta}$ solving \eqref{e:w_def}, we deduce that $\{w_{\eta,\delta}\}_{\delta>0}$ is locally bounded in $W^{1,\infty}_{\mathrm{loc}}(\Omega)$.
+Plugging it back into the defining equation \eqref{e:w_def}, we have that $\{w_{\eta,\delta}\}_{\delta>0}$ is locally bounded in $W^{2,r}_{\mathrm{loc}}(\Omega)$ for all $r<\infty$.
+
+    \noindent Local boundedness of $\{w_{\eta,\delta}\}_{\delta>0}$ in $W^{2,r}_{\mathrm{loc}}(\Omega)$ implies weak$^*$ compactness, that is, there exists a function $u\in W^{2,r}_{\mathrm{loc}}(\Omega)$ such that (via subsequence and monotonicity)
+    \begin{equation*}
+        w_{\eta,\delta} \rup u \qquad\text{weakly in}\;W^{2,r}_{\mathrm{loc}}(\Omega),\qquad \text{and}\qquad
+        w_{\eta,\delta} \to u \qquad\text{strongly in}\;W^{1,r}_{\mathrm{loc}}(\Omega).
+    \end{equation*}
+    In particular, $w_{\eta,\delta}\to u$ in $\mathrm{C}^1_{\mathrm{loc}}(\Omega)$ thanks to Sobolev compact embedding.
+Let us rewrite the equation $\mathcal{L}^\varepsilon\left[w_{\eta,\delta}\right] = 0$ as $\varepsilon\Delta w_{\eta,\delta}(x) = F[w_{\eta,\delta}](x)$ in $U$ for $U\subset\subset \Omega$ where
+    \begin{equation*}
+        F[w_{\eta,\delta}](x) =    w_{\eta,\delta}(x) + H(x,Dw_{\eta,\delta}(x)).
+    \end{equation*}
+    Since $w_{\eta,\delta}\to u$ in $\mathrm{C}^1(U)$ as $\delta\to 0$, we have $F[w_{\eta,\delta}](x) \to F(x)$ uniformly in $U$ where 
+    \begin{equation*}
+        F(x) =   u(x) + H(x,Du(x)).
+    \end{equation*}
+    In the limit, as $\delta\to 0$, we obtain that $u\in L^2(U)$ is a weak solution of $\varepsilon\Delta u = F$ in $U$ where $F$ is continuous, thus $u\in \mathrm{C}^2(\Omega)$ and by stability $u$ solves $\mathcal{L}^\varepsilon[u] = 0$ in $\Omega$.
+From \eqref{e:cp_delta3} we also have
+    \begin{equation*}
+        \underline{w}_{\eta,0} \leq u \leq \overline{w}_{\eta,0} \qquad\text{in}\;\Omega.
+    \end{equation*}
+    It is clear that $u(x)\to \infty$ as $\mathrm{dist}(x,\partial\Omega)\to 0$ with the precise rate like \eqref{rate_p<2} or \eqref{rate_p=2}.
+By construction, $u$ may depend on $\eta$.
+Next, we show that $u$ is the minimal solution of $\mathcal{L}^\varepsilon[u] = 0$ in $\Omega$ such that $u = +\infty$ on $\partial\Omega$, thus consequently showing that $u$ is independent of $\eta$.
+
+    \noindent Let $v\in W^{2,r}(\Omega)$ for all $r<\infty$ and $v$ solves \eqref{eq:PDEeps}.
+Fix $\delta>0$.
+Then since $v(x)\to \infty$ as $x\to \partial\Omega$ while $w_{\eta,\delta}$ remains bounded on $\partial \Omega$, comparison principle yields
+    \begin{equation*}
+        v\geq w_{\eta,\delta} \qquad\text{in} \; \Omega.
+    \end{equation*}
+    Let $\delta\to 0$ we deduce that $v\geq u$ on $\Omega$. This concludes that $u$ is the minimal solution in $W^{2,r}(\Omega)(\forall\,r<\infty)$ and thus $u$ is independent of $\eta>0$. 
+\end{proof}
+
+\paragraph{\textbf{Step 2.}} There exists a maximal solution $\overline{u}\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that $v\leq \overline{u}$ for any other solution $v\in \mathrm{C}^2(\Omega)$ solving \eqref{eq:PDEeps}.
+
+\begin{proof} For each $\delta>0$, let us denote $u_\delta\in \mathrm{C}^2(\Omega_\delta)$ to be the minimal solution to $\mathcal{L}[u_\delta] = 0$ in $\Omega_\delta$ and $u_\delta = +\infty$ on $\partial\Omega_\delta$.
+By the comparison principle, for every $\eta>0$, there holds
+\begin{equation*}
+    \underline{w}_{\eta,\delta} \leq u_\delta \leq \overline{w}_{\eta,\delta} \qquad\text{in}\;\Omega_\delta,
+\end{equation*}
+and
+\begin{equation*}
+    0<\delta<\delta' \qquad \Longrightarrow\qquad u_\delta \leq u_\delta' \qquad\text{in}\;\Omega_{\delta'}.
+\end{equation*}
+The monotoniciy, together with the local boundedness of $\{u_\delta\}_{\delta>0}$ in $W^{2,r}(\Omega)$, implies there exists $u\in W^{2,r}(\Omega)$ for all $r<\infty$ such that $u_\delta\to u$ strongly in $\rmC^1_{\mathrm{loc}}(\Omega)$.
+Therefore, using the equation $\mathcal{L}[u_\delta] = 0$ in $\Omega_\delta$ and the regularity of Laplace equation, we deduce that $u\in \mathrm{C}^2(\Omega)$ solves \eqref{eq:PDEeps} and
+\begin{equation*}
+    \underline{w}_{\eta,0} \leq u\leq \overline{w}_{\eta,0} \qquad\text{in}\;\Omega
+\end{equation*}
+for all $\eta>0$.
+From the construction, as $u_\delta$ is independent of $\eta$, it is clear that $u$ is also independent of $\eta$.
+We now show that $u$ is the maximal solution of \eqref{eq:PDEeps}.
+Let $v\in\rmC^2(\Omega)$ solve \eqref{eq:PDEeps}.
+Clearly $v\leq u_\delta$ on $\Omega_\delta$.
+Therefore, as $\delta \to 0$, we have $v\leq u$.
+\end{proof}
+\noindent In conclusion, we have found a minimal solution $\underline{u}$ and a maximal solution $\overline{u}$ in $\rmC^2(\Omega)$ such that
+\begin{equation}\label{e:chain}
+    \underline{w}_{\eta,0} \leq \underline{u}\leq \overline{u}\leq \overline{w}_{\eta,0} \qquad\text{in}\;\Omega
+\end{equation}
+for any $\eta>0$. This extra parameter $\eta$ now enables us to show that $\overline{u} = \underline{u}$ in $\Omega$. The key ingredient here is the convexity in the gradient of the operator.
+\smallskip
+\paragraph{\textbf{Step 3.}} We have $\overline{u}\equiv \underline{u}$ in $\Omega$. Therefore, the solution to \eqref{eq:PDEeps} in $\mathrm{C}^2(\Omega)$ is unique.
+
+\begin{proof} Let $\theta\in (0,1)$.
+Define $w_\theta = \theta \overline{u} + (1-\theta) ^{-1}\inf_{\Omega} f$.
+If $w_\theta$ is a subsolution to \eqref{eq:PDEeps}, then we can use comparison principle to obtain that
+\begin{equation*}
+    w_\theta = \theta \overline{u} + (1-\theta) ^{-1}\inf_{\Omega} f\leq \underline{u} \qquad\text{in}\;\Omega.
+\end{equation*}
+If that is the case, let $\theta\to 1$ we conclude that $\overline{u} \leq \underline{u}$.
+There is a problem here.
+As they are both explosive solutions, to use comparison principle, we need to show that $w_\theta \leq \underline{u}$ in a neighborhood of $\partial\Omega$.
+From \eqref{e:chain}, we see that
+\begin{align*}
+    &1\leq \frac{\overline{u}(x)}{\underline{u}(x)} \leq \frac{\overline{w}_{\eta,0}(x)}{\underline{w}_{\eta,0}(x)} = \frac{(C_\alpha+\eta)+ M_\eta d(x)^\alpha}{(C_\alpha-\eta)- M_\eta d(x)^\alpha},& 1<p<2,\\
+    &1 \leq \frac{\overline{u}(x)}{\underline{u}(x)} \leq \frac{\overline{w}_{\eta,0}(x)}{\underline{w}_{\eta,0}(x)} = \frac{-(1+\eta)\log(d(x)) + M_\eta}{-(1-\eta)\log(d(x))-M_\eta}, & p=2,
+\end{align*}
+for $x\in \Omega$. Hence
+\begin{align*}
+     &1\leq  \lim_{d(x)\to 0} \left(\frac{\overline{u}(x)}{\underline{u}(x)}\right) \leq \frac{C_\alpha+\eta}{C_\alpha-\eta}, & 1< p < 2,\\
+     &1\leq  \lim_{d(x)\to 0} \left(\frac{\overline{u}(x)}{\underline{u}(x)}\right) \leq \frac{-(1+\eta)}{-(1-\eta)}, & p = 2.
+\end{align*}
+Since $\eta>0$ is chosen arbitrary, we obtain
+\begin{equation*}
+     \lim_{d(x)\to 0} \left(\frac{\overline{u}(x)}{\underline{u}(x)}\right) = 1.
+\end{equation*}
+ This means for any $\varsigma\in(0,1)$, we can find $\delta(\varsigma)>0$ small such that on $\Omega\backslash \Omega_\delta$, one has
+\begin{equation*}
+\frac{\overline{u}(x)}{\underline{u}(x)}\leq (1+\varsigma)     \qquad\Longrightarrow\qquad \left(\frac{1}{1+\varsigma}\right)\overline{u}(x) \leq \underline{u}(x) \qquad\text{in}\; \Omega\backslash \Omega_\delta.
+\end{equation*}
+For a given $\theta\in (0,1)$, we can always choose $\varsigma$ small enough such that $(1+\varsigma)^{-1} > \theta$, which will imply that $\underline{u}(x) \geq \theta \overline{u}(x) + (1-\theta) ^{-1}\left(\inf_\Omega f\right)$ for $0< d(x) < \delta' < \delta$.
+\end{proof}
+\noindent This finishes the well-posedness of \eqref{eq:PDEeps} for $1<p\leq2$. 
+\end{proof}
+
+\begin{proof}[Proof of Lemma \ref{lem:max}] The proof is a variation of Perron's method (see \cite{Capuzzo-Dolcetta1990}).
+Let $\varphi\in \rmC(\overline{\Omega})$ and $x_0\in \overline{\Omega}$ such that $u(x_0) = \varphi(x_0)$ and $u-\varphi$ has a global strict minimum over $\overline{\Omega}$ at $x_0$ and that
+\begin{equation}\label{eq:max_a1}
+      \varphi(x_0) + H(x_0,D\varphi(x_0)) < 0.
+\end{equation}
+Let $\varphi^\varepsilon(x) = \varphi(x) - |x-x_0|^2 + \varepsilon$ for $x\in \overline{\Omega}$. Let $\delta > 0$. We see that for $x\in \partial B(x_0,\delta)\cap \overline{\Omega}$,
+\begin{equation*}
+    \varphi^\varepsilon(x) = \varphi(x) - \delta^2 +\varepsilon \leq \varphi(x) - \varepsilon
+\end{equation*}
+if $2\varepsilon \leq \delta^2$. We observe that
+\begin{equation*}
+    \begin{split}
+    \varphi^\varepsilon(x) - \varphi(x_0)  &= \varphi(x)-\varphi(x_0) + \varepsilon - |x-x_0|^2 \\
+    D\phi^\varepsilon(x) - D\phi(x_0) &= D\varphi(x) - D\varphi(x_0) - 2(x-x_0)
+    \end{split}
+\end{equation*}
+for $x\in B(x,\delta)\cap \overline{\Omega}$.
+We deduce from \eqref{eq:max_a1}, the continuity of $H(x,p)$ near $(x_0,D\varphi(x_0))$ and the fact that $\varphi\in \rmC^1(\overline{\Omega})$ that if $\delta$ is small enough and $0<2\varepsilon < \delta^2$, then
+\begin{equation}\label{eq:max_a2}
+      \varphi^\varepsilon(x)+H(x,D\varphi^\varepsilon(x)) < 0 \qquad\text{for}\;x\in B(x_0,\delta)\cap \overline{\Omega}.
+\end{equation}
+We have found $\phi^\varepsilon\in \mathrm{C}^1(\overline{\Omega})$ such that $\varphi^\varepsilon(x_0)>u(x_0)$, $\varphi^\varepsilon<u$ on $\partial B(x_0,\delta)\cap \overline{\Omega}$ and \eqref{eq:max_a2}.
+Let
+\begin{equation*}
+    \tilde{u}(x) = \begin{cases}
+    \max \big\lbrace u(x),\phi^\varepsilon(x) \big\rbrace &x\in B(x_0,\delta)\cap \overline{\Omega},\\
+    u(x)&x\notin B(x_0,\delta)\cap \overline{\Omega}.\\
+    \end{cases}
+\end{equation*}
+We see that $\tilde{u}\in \rmC(\overline{\Omega})$ is a subsolution of \eqref{S_0} in $\Omega$ with $\tilde{u}(x_0) > u(x_0)$, which is a contradiction.
+Thus, $u$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$.
+\end{proof}
+
 \section{Differentiability with respect to the parameter}
-For the vanishing viscosity problem with the Dirichlet boundary condition,
+\noindent For the vanishing viscosity problem with the Dirichlet boundary condition,
 \begin{equation}
@@
 \end{equation}
-By Schaefer's fixed point theorem and the maximal principle, $u^\epsilon_\epsilon$ is the unique solution in $C^2(\overline{U})$ of \eqref{dir_dif} \textcolor{orange}{(needs double check)}.
-The main idea is, we look at the difference quotients $\displaystyle \frac{u^{\epsilon+h}-u^\epsilon}{h}$and prove that as $h \to 0^+$, they converge to a limiting function $w^{\ast}$ in the uniform norm \textcolor{orange}{(maybe weaker convergence is fine)} such that $w^{\ast}$ solves \eqref{dir_dif}.
+By Schaefer's fixed point theorem and the maximal principle, $u^\epsilon_\epsilon$ is the unique solution in $C^{2,\alpha}(\overline{U})$ of \eqref{dir_dif}.
+
+\noindent The main idea is, we look at the difference quotients $\displaystyle \frac{u^{\epsilon+h}-u^\epsilon}{h}$and prove that as $h \to 0^+$, they converge to a limiting function $w^{\ast}$ in the uniform norm  such that $w^{\ast}$ solves \eqref{dir_dif}.
 Since \eqref{dir_dif} has a unique solution, we have $$u^\epsilon_\epsilon=\lim_{h \to 0^+}\frac{u^{\epsilon+h}-u^\epsilon}{h}.$$
 
-Fix $\epsilon >0$. Let $$w^h(x):=\frac{u^{\epsilon+h}(x)-u^\epsilon(x)}{h} \in C^2(\overline{U}).$$
+\subsection{Solution $u^\epsilon \in C^{2,\alpha}(\overline{U})$ exists} We use Schaufer's fixed point theorem as follows.
 
-A little computation will show that $w^h$ solves
+\begin{thm} Suppose $X$ is a Banach space.
+Let $A:X \to X$ be continuous and compact.
+Assume the set $\{u\in X : u=  A[u]$ for some $0 \leq    \leq 1\}$ is bounded.
+Then $A$ has a fixed point $u =A[u]$.
+\end{thm}
+\noindent Fix $0<\alpha<1$. Let $X=C^{1,\alpha}(\overline{U})$. Given $u \in X=C^{1,\alpha}(\overline{U})$, we look at the linear PDE
+\begin{equation}
+\label{fix}
+\left\{
+  \begin{aligned}
+   \epsilon \Delta v &= H(x, Du) \quad \, \text{in } U, \\
+              v &= 0 \qquad \qquad \text{on } \partial U.
+  \end{aligned}
+\right.
+\end{equation}
+\noindent
+Estimate the Holder norm of RHS
+$$\|H(x, Du)\|_{C^{0, \alpha}(\overline{U})}:=\sup_{x\in\overline{U}} |H(x,Du(x))| + \sup_{x, y \in \overline{U}}\frac{|H(x, Du(x))-H(y, Du(y))|}{|x-y|^\alpha}.$$
+Since $Du$ is bounded and H is smooth,
+\begin{equation}
+    \sup_{x\in\overline{U}} |H(x,Du(x))| \leq C.
+\end{equation}
+
+\begin{equation}
+    \begin{aligned}
+  &\sup_{x, y \in \overline{U}}\frac{|H(x, Du(x))-H(y, Du(y))|}{|x-y|^\alpha}\\
+  \leq &  \sup_{x, y \in \overline{U}}\frac{|H(x, Du(x))-H(y, Du(x))|}{|x-y|^\alpha} + \sup_{x, y \in \overline{U}}\frac{|H(y, Du(x))-H(y, Du(y))|}{|x-y|^\alpha} \\
+  =&    \sup_{x, y \in \overline{U}}\frac{|\int_0^1D_xH(y+\theta (x-y), Du(x))d\theta \cdot (x-y)|}{|x-y|^\alpha}\\& +
+     \sup_{x, y \in \overline{U}}\frac{|\int_0^1D_pH(y, Du(y)+\theta (Du(x)-Du(y)))d\theta \cdot (Du(x)-Du(y))|}{|x-y|^\alpha}\\
+  \leq &  C\sup_{x, y \in \overline{U}} (1+|Du(x)|)|x-y|^{1-\alpha} +  C \sup_{x, y \in \overline{U}}\frac{| (Du(x)-Du(y))|}{|x-y|^\alpha}\\
+ \leq & C(1 + \|u\|_{C^{1,\alpha}(\overline{U})})
+    \end{aligned}
+\end{equation}
+since $Du$ is bounded on $\overline{U}$, $D_pH \in C^\infty (\overline{U} \times \mathbb{R}^n)$ and
+$\displaystyle \sup_{x\in U}|D_xH(x,p)|\leq C(1+|p|)$. Therefore,
+\begin{equation}
+ \|H(x, Du)\|_{C^{0, \alpha}(\overline{U})} \leq C(1 + \|u\|_{C^{1,\alpha}(\overline{U})}).
+\end{equation}
+By Schauder estimates, there exists a unique solution $v \in C^{2,\alpha }(\overline{U})$ such that
+\begin{equation}
+\label{schauder}
+    \|v\|_{C^{2, \alpha}(\overline{U})} \leq C  \|H(x, Du)\|_{C^{0, \alpha}(\overline{U})}. 
+\end{equation}
+\noindent Define operator $A$ on $X := C^{1, \alpha} (\overline{U}) $ by $A[u]=v$. So 
+\begin{equation}
+     \|A[u]\|_{C^{2, \alpha}(\overline{U})} \leq C(1 + \|u\|_{C^{1,\alpha}(\overline{U})}),
+\end{equation}
+\noindent
+ and thus $A$ is continuous and compact.
+(i.e., if $\{u_k\}_{k=1}^\infty$ is bounded in $X=C^{1, \alpha}(\overline{U})$, then $\{A[u_k]\}_{k=1}\infty$ is bounded in $C^{2,\alpha} (\overline{U})$, thus precompact in $C^{1, \alpha}(\overline{U})$.
+Lemma 6.36 in Gilbarg and Trudinger.
+)
+
+\noindent Next we try to bound $\{u\in X : u=  A[u]$ for some $0 \leq    \leq 1\}$. If $u=  A[u]$, the PDE becomes
+
+\begin{equation}
+\label{lamb}
+\left\{
+  \begin{aligned}
+   \epsilon \Delta u &=   H(x, Du) \quad \, \text{in } U, \\
+              u &= 0 \qquad \qquad \text{on } \partial U.
+  \end{aligned}
+\right.
+\end{equation}
+
+\noindent Calderon-Zygmund estimates tell us that if we have
+\begin{equation}
+\label{cald}
+\left\{
+  \begin{aligned}
+  - \Delta v &=\Tilde{f}   \qquad \, \text{in } U, \\
+              v &= 0 \qquad \text{on } \partial U.
+  \end{aligned}
+\right.
+\end{equation}
+and $\Tilde{f} \in {L^p(U)}$ for some $p\in (1, \infty)$, then $v \in W^{2,p}(U)$ and $$\|v\|_{w^{2,p}(U)} \leq C\|\Tilde{f}\|_{L^p(U)}.$$
+
+\noindent Apply to \eqref{lamb} and we get
+
+\begin{equation}
+    \|u\|_{w^{2,p}(U)} \leq C\|H(x, Du)\|_{L^p(U)}
+\end{equation}
+
+(We want RHS to be bounded by some constant so that later we can choose $p$ larger than $n$ to  conclude $ \|u\|_{C^{1, \alpha}(U)} \leq   C\|u\|_{w^{2,p}(U)} \leq C$ by Morrey's estimate.) By a priori estimate, if we assume the solution of \eqref{dir} $u$ exists, then $\| Du\|_{L^\infty} \leq C_0$ where $C_0$ is independent of $\epsilon$.
+We can modify $H$ to get a new $\Tilde{H}$ so that it is smooth, $\Tilde{H} = H$ for $|p|<C_1$ and $H(x,p)=C_1+1$ for $|p|>C_1+1$ for some constant $C_1$ ($C_1$ is definitely larger than $C^0$).
+Moreover, the same prior estimate is correct for $\Tilde{H}$.
+Namely, if the solution $\Tilde{u}$ to \eqref{dir} with $H$ replaced by $\Tilde{H}$ exists, then $\| D\Tilde{u}\|_{L^\infty} \leq C_0$.
+(The way we choose this $C_1$ is that we work back from the beginning of the proof of a priori estimate for $u$, on both the boundary and interior of $\Omega$, and modify $H$ so that all the proofs go through and the same a priori estimate holds for the equation with $\Tilde{H}$.) Now with $\Tilde{H}$, we go through the same argument of Schaufer's fixed point theorem from the very beginning, and \eqref{cald} reads
+\begin{equation}
+       \|\Tilde{u}\|_{w^{2,p}(U)} \leq C\|\Tilde{H}(x, D\Tilde{u})\|_{L^p(U)} \leq C(1+\|D\Tilde{u}\|_{L^\infty}) \leq C.
+\end{equation}
+Choose $p=2n$ and $\displaystyle \alpha =\frac{1}{2}$. We have $\{\Tilde{u}\in X : \Tilde{u}=  A[\Tilde{u}]$ for some $0 \leq    \leq 1\}$ is bounded in $X= C^{1, \frac{1}{2}}(
+\overline{U})$.
+Thus Schaefer's fixed point theorem implies the equation \eqref{dir} with $H$ replaced by $\Tilde{H}$ has a solution $\Tilde{u} \in C^{2,\alpha} (\overline{\Omega})$.
+Since $\| D\Tilde{u}\|_{L^\infty} \leq C_0$, $\Tilde{u}$ also solves the original equation \eqref{dir}.
+
+\subsection{Uniqueness}
+Let $u$ and $v$ be two solutions to \eqref{dir} and $w := u-v$. Then we have
+\begin{equation}
+\begin{aligned}
+    &-\epsilon \Delta (u-v) = H(x, Dv)-H(x, Du)\\
+    \Rightarrow &-\epsilon \Delta w   =\int_0^1 D_pH(x, tDv+(1-t)Du) \cdot (Dv-Du)dt\\
+    \Rightarrow &-\epsilon \Delta w  +\int_0^1 D_pH(x, tDv+(1-t)Du)dt \cdot Dw = 0.
+\end{aligned}
+\end{equation}
+By the strong maximum principle, $w \equiv 0$.
+
+\subsection{Smooth dependence on $\epsilon$}
+Fix $\epsilon >0$. Let  $$w^h(x):=\frac{u^{\epsilon+h}(x)-u^\epsilon(x)}{h} \in C^{2,\alpha}(\overline{U}).$$
+
+A little computation shows that $w^h$ solves
 
@@
 \end{equation}
-Heuristically, we see as $h \to 0^+$, \eqref{dir_quo} "converges" to \eqref{dir_dif}.
+From the existence proof, we know $\|u^\epsilon\|_{C^{2,\alpha}(\overline{U})} \leq C$ uniformly in $\epsilon$.
+So $\|Du^{\epsilon+h}-Du^\epsilon\|_{C^{0,\alpha}(\overline{U})}$and $\|\Delta u\|_{C^{0,\alpha}(\overline{U})}
+$ is uniformly bounded in $h$.
 
-\textcolor{orange}{Still thinking about how to show $w^h$ converges uniformly as $h \to 0^+$.
-I am tring to show $\| w^h-w^\ast\|_\infty \to 0$ by looking at the equation solved by $v^h:=w^h-w^\ast$.
-More to fill in...}
-
+By Schauder estimates, $\{w^h\}_{h>0} \subset C^{2, \alpha}(\overline{U})$ are bounded, hence is precompact in $ C^{2, \beta}(\overline{U})$ for any $\beta < \alpha$.
+Therefore, there exits a subsequence $\{w^{h_j}\}_{j=1}^\infty$ such that $w^{h_j} \to w^\ast$ for some $w^\ast \in  C^{2, \beta}(\overline{U}) $ and $w^\ast$ solves \eqref{dir_dif}.
+This implies $w^h \to w^\ast$ in $C^{2, \beta}(\overline{U})$.
 \end{appendices}
 
-%\section*{Acknowledgement}
+\section*{Acknowledgement}
+The authors would like to express their appreciation to Hung V. Tran for his invaluable guidance.
 

### 2021-05-03 Drafts and notes/Draft_02.tex
New Draft with established results

--- 2021-04-06 Drafts and notes/Draft_01.tex
@@
 \usepackage[toc,page]{appendix}
+%\setcounter{secnumdepth}{4}
+%\setcounter{tocdepth}{3}
 %============%============%============%============%
@@
 \begin{equation}\label{def:delta_0}
-    \delta_{0,\Omega} = \sup \big\{ \delta > 0: x\mapsto\mathrm{dist}(x,\partial\Omega)\;\text{is}\;\rmC^2\;\text{in}\;\Omega\backslash\overline{\Omega}_{\delta} \big\}.
-\end{equation}
-The distance function is of class $\mathrm{C}^2$ in the region where $0<\mathrm{dist}(x,\partial\Omega) < \delta_0$. We will simply write $\delta_0$ if the underlying domain is understood.
+    \delta_{0,\Omega} = \frac{1}{2}\sup \big\{ \delta > 0: x\mapsto\mathrm{dist}(x,\partial\Omega)\;\text{is}\;\rmC^2\;\text{in}\;\Omega\backslash\overline{\Omega}_{\delta} \big\}.
+\end{equation}
+%The distance function is of class $\mathrm{C}^2$ in the region where $0<\mathrm{dist}(x,\partial\Omega) < \delta_0$. 
+We will simply write $\delta_0$ instead of $\delta_{0,\Omega}$ if the underlying domain is understood.
 \end{defn}
@@
 We have $u^{\varepsilon}_m(x) \to u^\varepsilon(x)$ as $m\to \infty$ in $\Omega$.
-Let $\varphi(x) \equiv  ^{-1} \inf_{\Omega} f$ for $x\in \overline{\Omega}$ then $\varphi(x)$ is a classical subsolution of \eqref{e:uepsm} in $\Omega$ with
+Let $\varphi(x) \equiv  \inf_{\Omega} f$ for $x\in \overline{\Omega}$ then $\varphi(x)$ is a classical subsolution of \eqref{e:uepsm} in $\Omega$ with
 \begin{equation*}
@@
 \begin{equation*}
-     ^{-1}\inf_\Omega f \leq u^{\varepsilon}_m(x) \qquad\text{for all}\;x\in \Omega.
+     \inf_\Omega f \leq u^{\varepsilon}_m(x) \qquad\text{for all}\;x\in \Omega.
 \end{equation*}
@@
 In other words there is a constant $C_0$ such that
-\begin{equation*}
+\begin{equation}\label{e:C0}
     |u(x) - u(y)| \leq C_0|x-y| \qquad\text{for all}\;x,y\in \Omega.
-\end{equation*}
+\end{equation}
 Thus we can extend $u$ uniquely to $u\in \rmC(\overline{\Omega})$.
@@
 \section{Rate of convergence via the doubling variables method}
-In this section, we focus on the rate of convergence for the case $f\in \mathrm{C}^1(\overline{\Omega})$.
+In this section, we focus on the rate of convergence for the case $f\in \mathrm{Lip}(\Omega)\cap\mathrm{C}^(\overline{\Omega})$.
 By adding a constant to the solution $u^\varepsilon$ of \eqref{eq:PDEeps}, without loss of generality we can assume the \emph{nonnegativity}
@@
 \begin{cases}
-       v(x) + |Dv(x)| - f(x) = 0 &\qquad\text{in}\;\Omega,\\
-     \qquad\qquad\qquad\quad\; v(x) = g(x)&\qquad\text{on}\;\partial\Omega. 
+       v(x) + |Dv(x)|^p - f(x) = 0 &\qquad\text{in}\;\Omega,\\
+     \qquad\qquad\qquad\quad\;\;\; v(x) = g(x)&\qquad\text{on}\;\partial\Omega. 
 \end{cases}
@@
 
-\begin{lem}\label{lem:f=0} If $f\geq 0$ in $\Omega$ then $u(x) = 0$ whenever $f(x) = 0$. In particular $f \equiv 0$ implies $u \equiv 0$.
+\begin{lem}\label{lem:f=0} Assume $f\geq 0$ in $\Omega$ then $u(x) = 0$ whenever $f(x) = 0$. In particular $f \equiv 0$ implies $u \equiv 0$.
 \end{lem}
-\begin{proof} We have $u\geq 0$ in $\overline{\Omega}$. Using the optimal control formula (\cite{Bardi1997,Hung2019}), we have
+\begin{proof} It is clear that $u\geq 0$ in $\overline{\Omega}$. Using the optimal control formula (see \cite{Bardi1997,Hung2019}), we have
 \begin{equation}\label{e:foru}
@@
 \end{equation*}
-Assume that $f(x) = 0$, we can choose $\eta(s) = x$ for all $s\in [0,\infty)$ as an admissible path in \eqref{e:foru} to obtain that
+Let $x\in \overline{\Omega}$ such that $f(x) = 0$, we can choose $\eta(s) = x$ for all $s\in [0,\infty)$ as an admissible path in \eqref{e:foru} to obtain that
 \begin{equation*}
@@
 \end{equation*}
-\end{proof}
-\noindent For simplicity, let us assume $  = 1$ from now on.
-We state the following lemma as a crucial estimate we will be using.
-It is a refined construction of the supersolution for \eqref{eq:PDEeps}.
-\begin{lem}\label{lem:super_refined} There exist positive constants $\nu = \nu(\alpha,\delta_0)$ and $C_\nu$ such that if $0\leq \delta \leq \frac{1}{2}\delta_0$ then
-\begin{equation*}
+As a consequence if $f\equiv 0$ then $u\equiv 0$.
+\end{proof}
+\noindent We state the following lemma as a crucial estimate we will be using. It is a refined construction of the supersolution for \eqref{eq:PDEeps}.
+\begin{lem}\label{lem:super_refined} Let $\delta_0$ be defined as in \eqref{def:delta_0}. 
+\begin{itemize}
+    \item[(i)] There exist positive constants $\nu = \nu(\delta_0) \in (1,2)$ and $C_\nu =\mathcal{O}\left(\delta_0^{-(\alpha+2)}\right)$ such that, if $0\leq \delta <\frac{1}{2}\delta_0$ then
+\begin{equation}\label{e:superwa}
     w(x) = \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + \max f + C_\nu \varepsilon^{\alpha+2}, \qquad x\in \Omega_\delta 
-\end{equation*}
+\end{equation}
 is a supersolution of \eqref{eq:PDEeps} in $\Omega_\delta$. 
+\item[(ii)] If $x\mapsto \mathrm{dist}(x,\partial\Omega)$ is continuously differentiable with $|\nabla \mathrm{dist}(x,\partial\Omega)| = 1$ everywhere in $\Omega$ then we can take $C_\nu = 0$ in \eqref{e:superwa}.
+\end{itemize}
 \end{lem}
 
-\begin{proof}
-We have $|\nabla d(x)| = 1$ for all $x\in \Omega_\delta\backslash \Omega_{\delta_0}$.
+\begin{proof} We have $|\nabla d(x)| = 1$ for all $x\in \Omega_\delta\backslash \overline{\Omega}_{\delta_0}$.
 Recall from Theorem \ref{thm:wellposed1<p<2} that $C_\alpha^p \alpha^p = C_\alpha \alpha (\alpha+1)$ and $p(\alpha+1) = \alpha+2$, we compute
@@
     \begin{split}
-        \mathcal{L}\left[w_\delta\right] \geq \frac{\nu C_\alpha\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + \frac{C_\alpha \alpha (\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}\left[\nu^p-\nu +\nu\frac{(d(x)-\delta)\Delta d(x)}{\alpha+1}\right].
+        \mathcal{L}^\varepsilon\left[w_\delta\right] \geq \frac{\nu C_\alpha\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + \frac{C_\alpha \alpha (\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}\left[\nu^p-\nu +\nu\frac{(d(x)-\delta)\Delta d(x)}{\alpha+1}\right].
     \end{split}
@@
 \end{equation}
-We will choose $\nu$ as follows. For $\gamma>1$ we have
+We will choose $\nu$ as follows. For $\gamma>1$ we have the inequality
 \begin{equation*}
@@
 \end{equation*}
-which implies that
+for $x,y\in \mathbb{R}$, which implies that
 \begin{equation*}
@@
 Therefore we can choose $C_\nu = C_3$ to obtain $\mathcal{L}[w]\geq 0$ in this region $\{x\in \Omega_\delta:d(x)\geq \delta_0\}$.
+
+For (ii), we have $d(x) = \mathrm{dist}(x,\partial\Omega)$ (without any smooth mollification away from the boundary) then $|\nabla d(x)| = 1$ for all $x\in \Omega_\delta$, therefore the above proof carries out the same as in \eqref{e:choose_nu} without the need to consider $x$ away from the boundary.
 \end{proof}
@@
 \begin{thm}\label{thm:rate_doubling0} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
-Assume that $H(x,\xi) = |\xi|^p - f(x)$ where $p\in\left(1,2\right)$ and $f\equiv 0$ in $\Omega$.
+Assume $f\equiv 0$ in $\Omega$.
 Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u \equiv 0 $ be the unique solution to \eqref{eq:PDE0}.
-Then there exists a constant $C$ independent of $\varepsilon$ such that
-\begin{equation*}
- -C \varepsilon^{\frac{1}{2}}\leq  u^\varepsilon(x) - u(x) \leq C\varepsilon \quad  \text{for} \quad x\in \Omega_{\varepsilon}.
-\end{equation*}
+\begin{itemize}
+    \item[(i)] In general there exists a constant $C$ such that
+    \begin{equation*}
+    0\leq u^\varepsilon(x)\leq C \left(\frac{ \varepsilon^{\alpha+1}}{d(x)^\alpha} + \frac{\varepsilon^{\alpha+2}}{\delta_{0,\Omega}^{\alpha+2}}\right), \qquad x\in \Omega
+\end{equation*}
+where $\delta_{0,\Omega}$ is defined as in \eqref{def:delta_0}.
+    \item[(ii)] If $x\mapsto \mathrm{dist}(x,\partial\Omega)$ is continuously differentiable with $|\nabla \mathrm{dist}(x,\partial\Omega)| = 1$ everywhere in $\Omega$ then 
+    \begin{equation*}
+        0\leq u^\varepsilon(x)\leq \frac{2C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha}, \qquad x\in \Omega.
+    \end{equation*}
+\end{itemize}
+In particular $0\leq  u^\varepsilon(x) \leq C\varepsilon$ for $x\in \Omega$, but $|u^\varepsilon(x)| = \mathcal{O}\left(\varepsilon^{\alpha+1}\right)$ on each compact subset of $\Omega$.
 \end{thm}
 
-\begin{proof} From Lemma \ref{lem:super_refined} and comparison principle, we have the estimate
-\begin{equation*}
-    u^\varepsilon(x)\leq \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} + C_\nu\varepsilon^{\alpha+2}, \qquad x\in \Omega.
-\end{equation*}
-Note that in this case $u^\varepsilon \to u \equiv 0$ as $\varepsilon\to 0$. We consider
-\begin{equation*}
-    \Phi(x,y) := u^\varepsilon(x) - u(y) - \frac{C_0|x-y|^2}{\sigma} - (1+\delta^\alpha)\frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}.
-\end{equation*}
-It has a maximum at $(x_\sigma,y_\sigma)\in \Omega\times\overline{\Omega}$. From $\Phi(x_\sigma,y_\sigma)\geq \Phi(x_\sigma,x_\sigma)$ we have
-\begin{equation*}
-    \frac{C_0|x_\sigma-y_\sigma|^2}{\sigma}\leq u(x_\sigma) - u(y_\sigma)\leq C_0|x_\sigma - y_\sigma| \qquad\Longrightarrow\qquad |x_\sigma - y_\sigma|\leq \sigma.
-\end{equation*}
-From $\Phi(x_\sigma,y_\sigma)\geq \Phi(x_0,x_0)$ for a fixed point $x_0 \in \Omega$ that has the largest distance away from the boundary, we have
-\begin{equation*}
-    \delta^\alpha\frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x_{\sigma})^\alpha} \leq u^\varepsilon(x_{\sigma}) - \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x_{\sigma})^\alpha} + C\varepsilon^{\alpha+1} \leq C_{\nu}\varepsilon^{\alpha+2}+ C\varepsilon^{\alpha+1}.
-\end{equation*}
-Thus
-\begin{equation*}
-    d(x_\sigma) \geq C\delta.
-\end{equation*}
-Now the subsolution test of $x\mapsto \Phi(x,y_\sigma)$ gives us
-\begin{equation*}
-\begin{split}
-    u^\varepsilon(x) + &\left|\frac{2C_0(x_\sigma-y_\sigma)}{\sigma}-(1+\delta^\alpha)\frac{\nu C_\alpha\alpha\varepsilon^{\alpha+1}\nabla d(x_\sigma)}{d(x_\sigma)^{\alpha+1}}\right|^p \\
-    &- \varepsilon \left(\frac{2nC_0}{\sigma} - (1+\delta^\alpha)\frac{\nu C_\alpha\alpha(\alpha + 1)\varepsilon^{\alpha+1}|\nabla d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+2}} + (1+\delta^\alpha)\frac{\nu C_\alpha \alpha \varepsilon^{\alpha+1}\Delta d(x_\sigma)}{d(x_\sigma)^{\alpha+1}}\right)\leq 0.
-\end{split}    
-\end{equation*}
-Similarly, the supersolution test of $y\mapsto \Phi(x_\sigma,y)$ gives us
-\begin{equation*}
-    u(y_\sigma) + \left|\frac{2C_0(x_\sigma-y_\sigma)}{\sigma}\right|^p \geq 0.
-\end{equation*}
-Therefore
-\begin{equation}
-\label{doubling}
-\begin{split}
-    u^\varepsilon(x_\sigma) - u(y_\sigma) \leq & p\left|2C_0+(1+\delta^\alpha)\nu C_\alpha \alpha\left( \frac{\varepsilon}{\delta}\right)^{\alpha+1}\right|^{p-1}(1+\delta^\alpha) \nu C_\alpha \alpha \left(\frac{\varepsilon}{\delta}\right)^{\alpha+1} \\
-    &+2nC_0\frac{\varepsilon}{\sigma} + (1+\delta^\alpha)\nu C_\alpha \alpha(\alpha+1)\left(\frac{\varepsilon}{\delta}\right)^{\alpha+2} + (1+\delta^\alpha)\nu C_\alpha \alpha C \left(\frac{\varepsilon}{\delta}\right)^{\alpha+1}\varepsilon\\
-    &\leq C\left(\frac{\varepsilon}{\sigma} + \left(\frac{\varepsilon}{\delta}\right)^{\alpha+1} + \left(\frac{\varepsilon}{\delta}\right)^{\alpha+2} \right).
-\end{split}
-\end{equation}
-Max happens when we choose $\sigma = 1$, and hence
-\begin{equation*}
-    u^\varepsilon(x_\sigma) - u(y_\sigma) \leq C\left( \frac{\varepsilon}{1} + \left(\frac{\varepsilon}{\delta}\right)^{\alpha+1} + \left(\frac{\varepsilon}{\delta}\right)^{\alpha+2}\right).
-\end{equation*}
-Choosing $\delta = \varepsilon^\frac{\alpha}{\alpha+1}$ we obtain 
-\begin{equation*}
-    u^\varepsilon(x_\sigma) - u(y_\sigma) \leq C(\varepsilon + \varepsilon + \varepsilon ^p ) \leq C\varepsilon.
-\end{equation*}
-As a consequence, 
-\begin{equation}
-\label{zerodata}
-   -C \varepsilon^{\frac{1}{2}}\leq  u^\varepsilon(x) - u(x) \leq C\varepsilon + \left(1+\varepsilon^{\frac{\alpha^2}{\alpha+1}}\right)\frac{\nu C_\alpha  \varepsilon^{\alpha+1}}{d(x)^\alpha} 
-\end{equation}
-for every $x\in \Omega$.
-\end{proof}
-
-\begin{rem} \textcolor{blue}{We believe that in case $f\equiv  0$, the lower bound in Theorem \ref{thm:rate_doubling0} can be made to $-C\varepsilon \leq u^\varepsilon - u$ instead of $-C\sqrt{\varepsilon}$.}
+\begin{proof} By Lemma \ref{lem:f=0} we have $u \equiv 0$ in $\Omega$. From Lemma \ref{lem:super_refined}, Lemma \ref{lem:lower-bound} and comparison principle, we have the estimate
+\begin{equation*}
+    0\leq u^\varepsilon(x)\leq \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} + C_\nu\varepsilon^{\alpha+2}, \qquad x\in \Omega.
+\end{equation*}
+The conclusions follow from Lemma \ref{lem:super_refined}.
+\end{proof}
+
+\begin{rem} The significance of (ii) in Theorem \ref{thm:rate_doubling0} is that, as the constant $C_\nu$ can be chosen to be zero, the constant in the rate of convergence does not blows up as $\delta_{0,\Omega} \to 0$.
+This is particularly useful in the following situation, where given a bounded continuous function $f$, we do a smooth cutoff to make $f = 0$ in $U_\kappa = \Omega\backslash \Omega_\kappa$.
+In this new region clearly $\delta_{0,U_\kappa} \to 0$ as $\kappa \to 0$, which creates a problem if we apply the estimate (i) in Theorem \ref{thm:rate_doubling0}.
 \end{rem}
@@
 \subsection{Compactly supported data}
+
+We start with the following Lemma, which will be used later.
+\begin{lem} Let $0<\kappa < \delta_0$ and $U_\kappa = \big\{x\in \Omega: 0<\mathrm{dist}(x,\partial\Omega) < \kappa\big\} = \Omega\backslash \overline{\Omega}_\kappa$. There holds
+\begin{equation*}
+    \mathrm{dist}(x,\partial\Omega_\kappa) = \kappa - \mathrm{dist}(x,\partial\Omega) \qquad\text{for all}\;x\in U_\kappa.
+\end{equation*}
+As a consequence, $x\mapsto \mathrm{dist}(x,\partial U_\kappa) = \min$ 
+\end{lem}
+
+\begin{proof} By definition of $\delta_0$ we have $d(x) = \mathrm{dist}(x,\partial\Omega)$ is twice continuously differentiable in the region $U_{\delta_0} = \Omega\backslash \overline{\Omega}_{\delta_0}$.
+The proof follows from \textcolor{blue}{\cite[p.
+355]{gilbarg_elliptic_2001}}.
+\end{proof}
+
 \begin{thm}\label{thm:rate_doubling0} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
-Assume that $H(x,\xi) = |\xi|^p - f(x)$ where $p\in\left(1,2\right)$ and $f$ is compactly supported in $\Omega$.
+Assume that $f$ is compactly supported in $\Omega_\kappa$ where $0<\kappa < \frac{1}{2}\delta_{0}$.
 Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
@@
 
-\begin{proof} Without loss of generality, we assume $f$ is compactly supported in $\Omega_{\kappa}$ where $0<\kappa < \frac{1}{2}\delta_0$.
-Let $g_\kappa = u^\varepsilon$ on $\partial\Omega_{\kappa}$, then the solution $u^\varepsilon$ of \eqref{eq:PDEeps} also solves
+\begin{proof} Let $g_\kappa = u^\varepsilon$ on $\partial\Omega_{\kappa}$, then the solution $u^\varepsilon$ of \eqref{eq:PDEeps} also solves
 \begin{equation*}
@@
   \begin{aligned}
-  u^\varepsilon(x) + |Du^\varepsilon(x)|^p-\varepsilon \Delta u^\varepsilon(x) &=0 \;\qquad \text{in } U ,\\
+  u^\varepsilon(x) + |Du^\varepsilon(x)|^p-\varepsilon \Delta u^\varepsilon(x) &=0 \;\qquad \text{in } U_\kappa ,\\
   u^\varepsilon(x) &= +\infty \quad \text{on } \partial \Omega,\\
-  u^\varepsilon(x) &= g_\kappa \;\quad \text{on } \partial \Omega_{\kappa},
+  u^\varepsilon(x) &= g_\kappa \;\;\quad \text{on } \partial \Omega_{\kappa},
     \end{aligned}
@@
 in the annulus $U_\kappa= \Omega \setminus \overline{\Omega}_{\kappa} = \{x\in \Omega: 0< d(x) < \kappa\}$.
-From Theorem \ref{thm:wellposed1<p<2}, let $\tilde{u}^\varepsilon\in \mathrm{C}^2(U_\kappa)$ be the solution to the following problem in the annulus $U_\kappa= \Omega \setminus \overline{\Omega}_{\kappa}$
+Let $\tilde{u}^\varepsilon\in \mathrm{C}^2(U_\kappa)$ be the solution to the following problem in the annulus $U_\kappa= \Omega \setminus \overline{\Omega}_{\kappa}$ (Theorem \ref{thm:wellposed1<p<2})
 \begin{equation*}
@@
 \end{equation*}
-Since $f = 0$ in $\overline{U}$, by Lemma \ref{lem:f=0} $u=0$ in $\overline{U}$, thus it is also the unique state-constraint solution to
+Since $f = 0$ in $\overline{U}_\kappa$, by Lemma \ref{lem:f=0} $u=0$ in $\overline{U}_\kappa$, thus it is also the unique state-constraint solution to
 \begin{equation*}
@@
 \end{equation*}
-From \eqref{zerodata} and the fact that $u \equiv 0$ in $U$, there exists a constant $C$ (depends on $\kappa$) such that
-\begin{equation} \label{annulus}
-   \tilde{u}^\varepsilon(x) \leq C\varepsilon + \left(1+\varepsilon^{\frac{\alpha^2}{\alpha+1}}\right)\frac{\nu C_\alpha  \varepsilon^{\alpha+1}}{d_\kappa(x)^\alpha} \qquad\text{for}\;x\in U_\kappa.
-\end{equation}
-%Since $f \equiv 0 $ in $U$, $u (x) = 0$ in $U$, which gives us
-%\begin{equation}\label{annulus}
-%   -C \varepsilon^{\frac{1}{2}}\leq \tilde{u}^\varepsilon(x)  \leq C\varepsilon + \left(1+\varepsilon^{\frac{\alpha^2}{\alpha+1}}\right)\frac{\nu C_\alpha  \varepsilon^{\alpha+1}}{\tilde{d}(x)^\alpha}.
-%\end{equation}
-By comparison principle in $U_\kappa$, $u^\varepsilon \geq 0$ and \eqref{annulus} we have
+We claim that the conclusion of (ii)
+
+Recall that $u^\varepsilon\geq 0$, by Theorem \ref{thm:rate_doubling0} comparison principle in $U_\kappa$ and  we have
 \begin{equation}\label{annulus2}
-    0\leq u^\varepsilon(x) \leq \tilde{u}^\varepsilon(x) \leq C\varepsilon + \left(1+\varepsilon^{\frac{\alpha^2}{\alpha+1}}\right)\frac{\nu C_\alpha  \varepsilon^{\alpha+1}}{d_\kappa(x)^\alpha}  \qquad\text{for}\;x\in U_\kappa.
-\end{equation}
-In other words, in the region where $f = 0$ the have an upper bound for $u^\varepsilon - u$.
-We proceed with the doubling variable method.
-Let $\sigma,\delta\in (0,1)$, we consider the auxiliary functional
+    0\leq u^\varepsilon(x) \leq \tilde{u}^\varepsilon(x)  \leq \frac{2C_\alpha\varepsilon^{\alpha+1}}{d(x)^{\alpha}} \qquad\text{for}\;x\in U_\kappa.
+\end{equation}
+We proceed with the doubling variable method. Let $\sigma,\delta\in (0,1)$, we consider the auxiliary functional 
 \begin{equation*}
@@
 \end{equation*}
-since $z\in \partial\Omega_k = \{x\Omega: d(x) = \kappa\}$. Thus we have $|x_\sigma - z| \geq \kappa - d(x_\sigma) > \frac{1}{2}\kappa$ for all $z\in \partial\Omega_k$. We have further that
+since $z\in \partial\Omega_k = \{x \in \Omega: d(x) = \kappa\}$. Thus we have $|x_\sigma - z| \geq \kappa - d(x_\sigma) > \frac{1}{2}\kappa$ for all $z\in \partial\Omega_k$. We have further that
 \begin{equation*}
@@
 
-We start with the following Lemma, which will be used later.
-\begin{lem} Let $0<\kappa < \delta_0$ and $U_\kappa = \big\{x\in \Omega: 0<\mathrm{dist}(x,\partial\Omega) < \kappa\big\} = \Omega\backslash \overline{\Omega}_\kappa$. There holds
-\begin{equation*}
-    \mathrm{dist}(x,\partial\Omega_\kappa) = \kappa - \mathrm{dist}(x,\partial\Omega) \qquad\text{for all}\;x\in U_\kappa.
-\end{equation*}
-\end{lem}
-
-\begin{proof} By definition of $\delta_0$ we have $d(x) = \mathrm{dist}(x,\partial\Omega)$ is twice continuously differentiable in the region $U_{\delta_0} = \Omega\backslash \overline{\Omega}_{\delta_0}$.
-The proof follows from \textcolor{blue}{\cite{} fill in Trudinger}.
-\end{proof}
-
 \begin{lem} Let $u^\varepsilon\in \mathrm{C}^2(U_\kappa)$ be the unique solution to 
@@
 \end{lem}
-\begin{rem} Unlike Theorem \ref{thm:rate_doubling0} where we made use of Lemma \ref{lem:super_refined}, the constant in the rate of convergence blows up as $\delta_{0,U_\kappa} \to 0$.
-\end{rem}
+
 %\nocite{*}

### 2021-05-03 Drafts and notes/Notes/Special_data.tex
New Draft with established results

--- 2021-04-06 Drafts and notes/Things to try.tex
@@
 \begin{center}
-{\LARGE \textsc{Quasilinear equations}}\\
+{\LARGE \textsc{Special data}}\\
 %{Từ Nguyễn Thái Sơn}\\
@@
 %{\setfont{frc}{March 13, 2021}}\\
-{\textit{March 24, 2021}}
+{\textit{April 09, 2021}}
 \end{center}
@@
 
-\begin{enumerate}
-    \item Try the special case $\Omega = B(0,1)$, note that we have $\Delta d(x) = 0$ in one dimension. Question: what is the difference between the rotational case (radial) vs one dimensional? 
-    \item Try out the special case $f(x) = f(|x|)$ in $B(0,1)$, in which we can reduce it to one-dimensional setting.
-    \item Try out the specific case $f(x) = 1-|x|$ on $(-1,1)$ and $f(x) = 0$ in $1\leq |x|\leq 2$ on the domain $\Omega = (-2,2)$. This is a simple case of the compactly supported data.
-    \item Idea for general data: Assume $u^\varepsilon\to u$ as $\varepsilon\to 0$. We compare $u^\varepsilon$ and $v^\varepsilon$ where $1<p\leq 2$ and
+\section{General case}
+Let us consider $p = 2$ and $\delta_0>0$ such that $d(x) = \mathrm{dist}(x,\partial\Omega)$ for $x$ near the boundary such that $0<d(x)<\delta_0$.
+We extend $d(\cdot)\in \mathrm{C}^2(\mathbb{R}^n)$.
+We consider the equation:
 \begin{equation}\label{eq:PDEeps}
     \begin{cases}
-   \mathcal{L}[u^\varepsilon] =  u^\varepsilon(x) + |Du^\varepsilon(x)|^p - f(x) - \varepsilon \Delta u^\varepsilon(x) = 0 &\qquad
+   \mathcal{L}[u^\varepsilon] =  u^\varepsilon(x) + |Du^\varepsilon(x)|^2 - f(x) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
     \text{in}\;\Omega, \vspace{0cm}\\
-   u^\varepsilon(x) = +\infty &\qquad
-    \text{on}\;\partial\Omega
+    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^\varepsilon(x) = +\infty.
     \end{cases} \tag{PDE$_\varepsilon$}
 \end{equation}
-and
-\begin{equation}\label{eq:vPDEeps}
-    \begin{cases}
-   \mathcal{L}[v^\varepsilon] =  v^\varepsilon(x) + |Dv^\varepsilon(x)|^p - f(x) - \varepsilon \Delta v^\varepsilon(x) = 0 &\qquad
-    \text{in}\;\Omega, \vspace{0cm}\\
-   v^\varepsilon(x) = u(x) &\qquad
-    \text{on}\;\partial\Omega.
-    \end{cases} 
+Let $K_0 = \Vert d\Vert_{L^\infty}, K_1 = \Vert\nabla d\Vert_{L^\infty}$ and $K_2 = \Vert \Delta d\Vert_{L^\infty}$.
+We summarize some results from \cite{Lasry1989} in a clearer manner here for convenience.
+Let us without loss of generality assume $f\geq 0$ a.e.
+in $\Omega$ (\textit{positivity}).
+\begin{enumerate}
+    \item If $f = 0$, we are good to go, as 
+    \begin{equation}\label{e:spirit}
+        u(x) = \frac{\nu C_\alpha\varepsilon^{\alpha+1}}{d(x)^\alpha} + \left(\frac{C\varepsilon^{\alpha+2}}{\delta_{0,\Omega}^{\alpha+2}}\right)
     \end{equation}
-We know that $|v^\varepsilon - u|\leq C\sqrt{\varepsilon}$, thus the goal is to compare $u^\varepsilon$ and $v^\varepsilon$. Let $w^\varepsilon(x) = u^\varepsilon(x) - v^\varepsilon(x)$, we have
-\begin{equation}\label{eq:wPDEeps}
-    \begin{cases}
-w^\varepsilon(x) + |Du^\varepsilon(x)|^p  - |Dv^\varepsilon|^p - \varepsilon \Delta w^\varepsilon(x) = 0 &\qquad
-    \text{in}\;\Omega, \vspace{0cm}\\
-   w^\varepsilon(x) = +\infty &\qquad
-    \text{on}\;\partial\Omega.
-    \end{cases} 
-\end{equation}
-The good thing about \eqref{eq:wPDEeps} is, the data $f$ disappears and furthermorethe new data, for example with $p=2$ can be written as
-\begin{equation}\label{eq:wwPDEeps}
-    \begin{cases}
-w^\varepsilon(x) + |Dw^\varepsilon(x)|^2 +\underbrace{2Dw^\varepsilon(x)\cdot Dv^\varepsilon(x)}_{g
-(x)} - \varepsilon \Delta w^\varepsilon(x) = 0 &\qquad
-    \text{in}\;\Omega, \vspace{0cm}\\
-   w^\varepsilon(x) = +\infty &\qquad
-    \text{on}\;\partial\Omega.
-    \end{cases} 
-\end{equation}
-and $g(x) \approx \frac{\varepsilon \nabla d(x)\cdot \nabla v^\varepsilon(x)}{d(x)} + |Dv^\varepsilon(x)|^2$, which is small in some sense depends on $\varepsilon$.
-Question: can we get a rate of convergence $w^\varepsilon(x)\to 0$?
-What is the behavior of $Dv^\varepsilon(x)$ as $\varepsilon\to 0$?
-Can we know more besides $|v^\varepsilon - u|\leq C\sqrt{\varepsilon}$?
-\item Building a better supersolution for compactly supported data. Using the above $v^\varepsilon$ in \eqref{eq:vPDEeps}, can we somehow show
+    is a supersolution. 
+    \item If $f$ is compactly supported in $\Omega_\kappa$ we are good to go as well.
+    \item Instead, if $f$ is a constant we should be able to do the same. Can we improve the result to the case that $f$ is constant in the strip $\Omega\backslash \overline{\Omega}_\kappa$?
+    \item Now here is the deal, in the spirit of \eqref{e:spirit} above, we see that when we plug in the solution $u$ from \eqref{e:spirit} into the equation, we simply ignore the contribution of the monotone term $u(x)$, even though it is positive.
+That leads to the following observation, if we choose
     \begin{equation*}
-    u^\varepsilon(x) \leq v^\varepsilon(x) + \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} 
+        f(x) =  \frac{\theta C_\alpha\varepsilon^{\alpha+1}}{d(x)^\alpha}, \qquad x\in \Omega
     \end{equation*}
-in $\Omega$ when we assume $\mathrm{supp}\;f \subset \Omega_{\delta_0}$? 
-\item Showing $u^\varepsilon$ is very small in the region where $f = 0$, for example $\mathrm{supp}\;f \subset \Omega_{\delta_0}$, using stochastic control.
-The idea behind this is, $u(x) = 0$ whenever $f(x) = 0$ (we assume $f\geq 0$) and $u^\varepsilon\to u$, thus $u^\varepsilon$ has to be very small where $f = 0$, thus there is a hope to build a better supersolution, to show that
+    for any $\theta > 1$ then clearly
     \begin{equation*}
-       u^\varepsilon(x) \leq \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} 
+        \mathcal{L}^\varepsilon[\theta u] \geq 0
     \end{equation*}
-where $x$ in the region where $f(x) = 0$. Specifically, solution $u^\varepsilon$ to \eqref{eq:PDEeps} can be written as
+    therefore $\theta u$ from \eqref{e:spirit} is still a supersolution. While if $\theta\leq 1$, we simply use $u$ as a supersolution. Furthermore, if 
     \begin{equation*}
-    u^\varepsilon(x) = \inf_{a(\cdot)\in \mathcal{A}}  \mathbb{E}\left[\int_0^\infty e^{-t}\left(\frac{(\alpha+1)^{\alpha+1}}{(\alpha+2)^{\alpha+2}}|a(X_t)|^{\alpha+2} + f(X_t)\right)dt \right]
+    \fbox{$\displaystyle    f(x) = \frac{\theta C_\alpha\varepsilon^{\alpha+1}}{d(x)^\beta} $}
     \end{equation*}
-where $q = \alpha+2$ satisfies $\frac{1}{q} + \frac{1}{p} = 1$, where
-\begin{equation*}
-    \begin{cases}
-    dX_t = a(X_t)dt + \varepsilon\sqrt{2} d\mathbb{B}_t\\
-    \;\;X_0 = x
-    \end{cases}
-\end{equation*}
-and $\mathcal{A}$ is the set of continuous function $a(\cdot):\Omega \to \mathbb{R}$ such that the state $X_t\in \overline{\Omega}$ with probability 1 for all time $t\geq 0$ and for all initial points $x\in \Omega$.
-Here $\mathbb{B}_t$ is the standard Brownian motion.
-The hope is that, the optimal Markovian control is given by
-\begin{equation*}
-    a_0(x) = p|\nabla u^\varepsilon(x)|^{p-2}\nabla u^\varepsilon(x).
-\end{equation*}
-Hence, note that
-\begin{equation*}
-    \frac{1}{qp^{\alpha+1}} = \frac{(\alpha+1)^{\alpha+1}}{(\alpha+2)^{\alpha+2}}
-\end{equation*}
-we have
-\begin{equation*}
-   \frac{1}{qp^{\alpha+1}} |a_0(X_t)|^q =  \frac{1}{qp^{\alpha+1}}p^q |\nabla u^\varepsilon(x)|^p = \frac{1}{pq}|\nabla u^\varepsilon(x)|^p \approx \frac{1}{pq}\frac{(C_\alpha \alpha)^p\varepsilon^{\alpha+2}}{d(x)^{\alpha+2}}.
-\end{equation*}
-In fact, this estimate can be make rigorously from \cite{alessio_asymptotic_2006}, that is there is a constant $C>0$ such that
-\begin{equation*}
-    |\nabla u ^\varepsilon(x)|\leq \frac{C\varepsilon^{\alpha+1}}{d(x)^{\alpha+1}}
-\end{equation*}
-for $x\in \Omega$.
+    for any $0<\beta\leq \alpha$ this argument still works. Can we still have a rate of convergence?
 \end{enumerate}
 
-%\bibliography{zzzzlibrary}{}
+\bibliography{zzzzlibrary}{}
 %\bibliographystyle{ieeetr}
-%\bibliographystyle{acm}
+\bibliographystyle{acm}
 \end{document}

### 2021-05-03 Drafts and notes/Things to try.tex
New Draft with established results

@@
 for $x\in \Omega$.
+\item Idea to bound point-wise $u^\varepsilon(x)$ without using stochastic formula.
+If $x\in \Omega$ such that we can find $r>0$ such that $B(x,r)\subset \{f = 0\}$ then by consider an explosive solution $w^\varepsilon$ in $B(x,r)$, then as $w^\varepsilon\to 0$ in $B(x,r)$ and $u^\varepsilon \leq w^\varepsilon$ in $B(x,r)$, one can get a rate locally for $u^\varepsilon$ if we can control the radius $r$, provided we know the support of $f$.
+\textcolor{red}{This idea is clear, probably no more explanation needed or further investigation, maybe?}
+\item Difficulty for the general case of bounded data $f$, after cutting off $f_\kappa = f\chi_\kappa$ such that $\mathrm{supp}(f_\kappa)\subset \Omega_\kappa$, the solution of the corresponding problem is $u^\varepsilon_\kappa$ which is not exactly $u^\varepsilon$, eventhough $u^\varepsilon_\kappa\to u^\varepsilon$ as $\kappa \to 0$.
+However the rate exploded when $\kappa \to 0$ unless we choose a scale $\kappa = \varepsilon^\gamma$ for $\gamma < 1$, but then in the equation $u^\varepsilon_\kappa\to u^\varepsilon$ we loose the term $\varepsilon$ here.
+\begin{itemize}
+    \item An idea to try: bound in the interior only. Write
+    \begin{equation*}
+        f = \frac{1}{2}\left( \underbrace{\qquad\qquad 2f\chi_\kappa\qquad\qquad}_{f_1 \longrightarrow u^\varepsilon_1} +  \underbrace{\qquad\qquad 2f(1-\chi_\kappa)\qquad\qquad}_{f_2 \longrightarrow u^\varepsilon_2}\right).
+    \end{equation*}
+    We know $u_1^\varepsilon\to 0$ with a rate everywhere, while $u_2^\varepsilon \to 0$ in $\Omega_\kappa$ with a rate, thus by convex combination we maybe able to control a rate for $u^\varepsilon$ in $\Omega_\kappa$.
+\textcolor{red}{Seems wrong!
+As we only have subsolution, not supersolution.}
+\end{itemize}
 \end{enumerate}
 
-%\bibliography{zzzzlibrary}{}
+\begin{center}
+--------------------------------------------------------------------------------------------------------------------
+\end{center}
+\begin{enumerate}
+    \item \textcolor{blue}{Log April 03, 2021.} Figured out the annulus bound enables a proof for compactly supported data.
+\end{enumerate}
+
+\bibliography{zzzzlibrary}{}
 %\bibliographystyle{ieeetr}
-%\bibliographystyle{acm}
+\bibliographystyle{acm}
 \end{document}

### 2021-07-15 Drafts and notes/Draft_03.tex
Almost final

--- 2021-05-03 Drafts and notes/Draft.tex
@@
 The rate can be improved in some region to $\mathcal{O}(\varepsilon)$, for instance, on the whole domain with zero data.
-The proof relies on a domain decomposition technique and classical tools in viscosity solution theory.
+The proof relies on a domain decomposition technique and classical tools in the viscosity solution theory.
 \end{abstract}
@@
 \section{Introduction}\label{sec:intro}
-\subsection{Motivation} Let $\Omega$ be an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$, %Let us consider the following Hamiltonian $ H(x,\varrho) = |\varrho|^p-f(x)$ for $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$,
+\subsection{Motivation} Let $\Omega$ be an open, bounded and connected domain of $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary, %Let us consider the following Hamiltonian $ H(x,\varrho) = |\varrho|^p-f(x)$ for $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$,
  $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$, and $u^\varepsilon\in \mathrm{C}^2(\Omega)$ (see \cite{Lasry1989}) be the solution to
@@
 A typical subquadratic Hamiltonian that has been considered in the literature is $H(\xi) = |\xi|^p$ for $\xi\in \R^n$ where $1<p\leq 2$.
-For simplicity of the presentation, we will consider this special case and generalize the result later to all Hamiltonian $H(\xi)$ for which (see \cite{sardarli_ergodic_2021} for a similar generalization)
- \begin{equation*}
-     \lim_{\delta\to 0}\delta^{\frac{p}{p-1}}H\left(\delta^{-\frac{1}{p-1}}\xi\right) = |\xi|^p \qquad\text{locally uniformly in}\;\xi\in \R^n.
- \end{equation*}
- With $H(\xi) = |\xi|^p$, the equation of interest is then becomes
+For simplicity of the presentation, we will consider this special case.
+
+ %and generalize the result later to all Hamiltonian $H(\xi)$ for which (see \cite{sardarli_ergodic_2021} for a similar generalization)
+ %\begin{equation*}
+ %    \lim_{\delta\to 0}\delta^{\frac{p}{p-1}}H\left(\delta^{-\frac{1}{p-1}}\xi\right) = |\xi|^p \qquad\text{locally uniformly in}\;\xi\in \R^n.
+ %\end{equation*}
+ \noindent 
+ With $H(\xi) = |\xi|^p$, the equation of interest then becomes
 \begin{equation}\label{eq:PDEeps}
@@
 We are interested in studying the asymptotic behavior of $\{u^\varepsilon\}_{\varepsilon>0}$ as $\varepsilon\rightarrow 0^+$.
-Heuristically, the solution of the second-order state-constraint problem converges to that of a first-order state-constraint problem which is associated with deterministic optimal control, namely,
+Heuristically, the solution of the second-order state-constraint problem converges to that of a first-order state-constraint problem associated with deterministic optimal control, namely,
 \begin{equation}\label{eq:PDE0}
@@
 The problem is interesting since in the limit we no longer have blowing up behavior.
-In this paper, we are interested in the rate of convergence of $u^\varepsilon \to u$ as $\varepsilon\to 0$.
+In this paper, we investigate the rate of convergence of $u^\varepsilon \to u$ as $\varepsilon\to 0^+$.
 A boundary layer is expected to describe the behavior of this convergence near the boundary.
-\subsection{Assumptions} We will always assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary in $\mathbb{R}^n$ satisfying either %$H:\mathbb{R}^n\times \mathbb{R}^n$ is a continuous Hamiltonian.
+\subsection{Assumptions} We will always assume $\Omega$ is an open, bounded and connected domain in $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary satisfying either %$H:\mathbb{R}^n\times \mathbb{R}^n$ is a continuous Hamiltonian.
 %\begin{itemize}
@@
 \subsection{Literature} There is a
-vast amount of work in the literature on large solutions and second-order viscosity solution with state constraint.
+vast amount of work in the literature on large solutions and second-order viscosity solutions with state constraints.
 The problem \eqref{eq:PDEeps} is first studied in \cite{Lasry1989} and subsequently many works have been done in understanding deeper the properties of solutions.
@@
 In terms of rate of convergence, up to our knowledge such a question has not been studied in the literature.
-For the case \eqref{eq:PDEeps} is equipped with Dirichlet boundary condition, a rate $\mathcal{O}(\sqrt{\varepsilon})$ is well-known with multiple proofs (see \cite{Hung2019}).
+For the case \eqref{eq:PDEeps} is equipped with Dirichlet boundary condition, a rate $\mathcal{O}(\sqrt{\varepsilon})$ is well known with multiple proofs (see \cite{tran_hamilton-jacobi_2021}).
 
@@
 \begin{thm} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
-Assume that $1 < p\leq 2$ and $f$ is Lipschitz such that $f = 0$ on $\partial\Omega$.
+Assume that $1 < p\leq 2$ and $f$ is Lipschitz with the condition $f = 0$ on $\partial\Omega$.
 Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
-Then there exists a constant $C$ such that for $x\in \Omega$ there holds
+Then there exists a constant $C$ such that for $x\in \Omega$,
 \begin{align*}
@@
 \begin{rem} The condition $f = 0$ on $\partial\Omega$ can be explained as follows.
-One can see that solution to \eqref{eq:PDEeps} is continuous with respect to data $f$ in the weak$^*$ topology of $L^\infty(\Omega)$ (see \cite{Lasry1989}).
-If $f = 0$ on $\partial\Omega$, we are able to approximate $f$ \emph{uniformly} in $L^\infty(\Omega)$ by a sequence of compactly supported functions, where such a rate is easier to obtained.
+One can see that the solution to \eqref{eq:PDEeps} is continuous with respect to data $f$ in the weak$^*$ topology of $L^\infty(\Omega)$ (see \cite{Lasry1989}).
+If $f = 0$ on $\partial\Omega$, we are able to approximate $f$ \emph{uniformly} in $L^\infty(\Omega)$ by a sequence of compactly supported functions, where a rate of $u^\varepsilon-u$ is easier to obtained.
 Indeed, using the usual doubling variable technique, it is natural to consider the doubling variable for
@@
 However, to control the extra leading term above, one needs to have $d(x)\approx \varepsilon^\gamma$ for $\gamma < 1$ to make the argument work.
-This major difficulty can be overcome when we decompose the solution into an inside part and an outside part that lies in an annulus, where we have reduced to $f=0$ in this region.
+This major difficulty can be overcome when we decompose the solution into an inside part and an outside part that lies in an annulus, where we have reduced to the case of $f=0$.
 \end{rem}
@@
 
-\begin{thm}\label{thm:grad_1} Let $f\in \rmC(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $u\in \mathrm{C}^2(\Omega)$ be a solution to $\mathcal{L}^\varepsilon[u] = 0$ in $\Omega$.
-Assume that $  u(x)-f(x)\geq -m$ in $\Omega$.
+\begin{thm}\label{thm:grad_1} Let $f\in \rmC(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $u^\varepsilon \in \mathrm{C}^2(\Omega)$ be a solution to $\mathcal{L}^\varepsilon[u^\varepsilon] = 0$ in $\Omega$.
+Assume that $  u^\varepsilon(x)-f(x)\geq -m$ in $\Omega$.
 Then for $\delta>0$, there exists $C_\delta = C(m,p,\delta, \Vert D f\Vert_{L^\infty(\Omega)})$ such that
 \begin{equation*}
-    \sup_{x\in \overline{\Omega}_\delta} \Big(|u(x)|+|Du(x)|\Big) \leq C_\delta.
+    \sup_{x\in \overline{\Omega}_\delta} \Big(|u^\varepsilon(x)|+|Du^\varepsilon(x)|\Big) \leq C_\delta.
 \end{equation*}
 \end{thm}
-\noindent We provide a proof for this Theorem in Appendix for the reader's convenience.
+\noindent We provide a proof for this theorem in Appendix for the reader's convenience.
 
@@
     \text{in}\;\Omega, \vspace{0cm}\\
-    \;\qquad\quad\qquad\qquad\qquad\qquad u(x) = m &\qquad
+    \quad \qquad\quad\qquad\qquad\qquad\qquad u(x) = m &\qquad
     \text{on}\;\partial\Omega.
@@
 \end{equation}
-Thus, we can extend $u$ uniquely to $u\in \rmC(\overline{\Omega})$.
-We will use Lemma \ref{lem:max} to show that $u$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$.
+Thus, we can extend $u$ uniquely to $u\in \rmC(\overline{\Omega})$. We will use Lemma \ref{lem:max} to show that $u$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$.
+
 It suffices to show that $u\geq w$ on $\overline{\Omega}$, where $w\in \rmC(\overline{\Omega})$ is the unique solution to \eqref{eq:PDE0}.
-
-For $\delta>0$, let $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\partial \Omega) > \delta\}$ and $u_\delta\in\rmC(\overline{\Omega}_\delta)$ be the state-constraint viscosity solution to the problem $  u(x) + |Du(x)| - f(x) = 0$ in $\Omega_\delta$, i.e., $u_\delta$ is the unique viscosity solution to
+For $\delta>0$, let $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\partial \Omega) > \delta\}$ and $u_\delta\in\rmC(\overline{\Omega}_\delta)$ be the  unique viscosity solution to
 \begin{equation}\label{e:v_v}
@@
 \end{thm}
-\begin{proof} The proof relies on a well-known rate of convergence for vanishing viscosity of viscous Hamilton--Jacobi equation with Dirichlet boundary condition (\textcolor{blue}{NEED CITATION}).
+\begin{proof} The proof relies on a well-known rate of convergence for vanishing viscosity of viscous Hamilton--Jacobi equation with Dirichlet boundary condition (see \cite{Calder2021,crandall_two_1984,evans_adjoint_2010,fleming_convergence_1961,Tran2011}).
 As $u\in \mathrm{C}(\overline{\Omega})$, let $g\in \mathrm{C}(\partial\Omega)$ defined by $g(x) = u(x)$ for $x\in \partial\Omega$.
@@
 \end{lem}
-\begin{proof} It is clear that $u\geq 0$ in $\overline{\Omega}$. Using the optimal control formula (see \cite{Bardi1997,Hung2019}), we have
+\begin{proof} It is clear that $u\geq 0$ in $\overline{\Omega}$. Using the optimal control formula (see \cite{Bardi1997,tran_hamilton-jacobi_2021}), we have
 \begin{equation}\label{e:foru}
@@
 \begin{equation*}
-    c = \left(pq^{\frac{1}{p-1}}\right)^{-1} \qquad\text{and}\qquad \frac{1}{p} + \frac{1}{q} = 1.
-\end{equation*}
+    c = \left(qp^\frac{1}{p-1}\right)^{-1} \qquad\text{and}\qquad \frac{1}{p} + \frac{1}{q} = 1.
+\end{equation*}
+%\textcolor{red}{(Here, the constant $c=\frac{1}{qp^\frac{1}{p-1}}$? )}
+
 Let $x\in \overline{\Omega}$ such that $f(x) = 0$. We can choose $\eta(s) = x$ for all $s\in [0,\infty)$ as an admissible path in \eqref{e:foru} to obtain that
@@
 \begin{equation}\label{e:superwa}
-\begin{split}
-    &w(x) = \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} + \max f + C_\nu \varepsilon^{\alpha+2}, \qquad\;\;\,  p<2,\\
-    &w(x) = \nu \varepsilon \log\left(\frac{1}{d(x)}\right) + \max f+ C_\nu \varepsilon^2, \qquad  p=2,
-\end{split}
-\end{equation}
-are supersolutions of \eqref{eq:PDEeps} in $\Omega$. 
+w(x) = \begin{cases}
+    \displaystyle\frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} + \max f + C_\nu \varepsilon^{\alpha+2}, \qquad\;\;\,  p<2,\vspace{0.2cm}\\
+    \displaystyle\nu \varepsilon \log\left(\frac{1}{d(x)}\right) + \max f+ C_\nu \varepsilon^2, \qquad  p=2,
+\end{cases}
+\end{equation}
+is a supersolution of \eqref{eq:PDEeps} in $\Omega$. 
 %\item[(ii)] If $x\mapsto \mathrm{dist}(x,\partial\Omega)$ is continuously differentiable with $|\nabla \mathrm{dist}(x,\partial\Omega)| = 1$ everywhere in $\Omega$ then we can take $C_\nu = 0$ in \eqref{e:superwa}.
@@
 \end{equation*}
-We have
+Recall that $K_2= \Vert \Delta d\Vert_{L^\infty}$, we have
 \begin{equation*}
     \begin{split}
-        \mathcal{L}^\varepsilon\left[w_\delta\right] \geq \frac{\nu C_\alpha\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + \frac{C_\alpha \alpha (\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}\left[\nu^p-\nu +\nu\frac{(d(x)-\delta)\Delta d(x)}{\alpha+1}\right].
+        \mathcal{L}^\varepsilon\left[w_\delta\right] =  \frac{\nu C_\alpha\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + \max f - f(x) + C_\nu \varepsilon^{\alpha+2} + \frac{C_\alpha \alpha (\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}\left[\nu^p-\nu +\nu\frac{(d(x)-\delta)\Delta d(x)}{\alpha+1}\right] .
     \end{split}
 \end{equation*}
-Recall that $K_2= \Vert \Delta d\Vert_{L^\infty}$. We observe that in the region where $\delta< d(x)\leq \delta_0$,
+\paragraph{\textbf{Case 1.}} If $\delta< d(x)\leq \delta_0$, we observe that
 \begin{equation*}
@@
 Choose $\nu = 1+C_2\delta_0$ in \eqref{e:choose_nu}and we obtain $\mathcal{L}[w]\geq 0$ in $\{x\in \Omega_\delta: \delta <d(x)\leq \delta_0\}$.
-Recall that $K_0 = \Vert d\Vert_{L^\infty}$ and $K_1 = \Vert \nabla d\Vert_{L^\infty}$.
-In the region where $d(x)\geq \delta_0$, we have
+
+\paragraph{\textbf{Case 2.}} If $d(x)\geq \delta_0$, recall that $K_0 = \Vert d\Vert_{L^\infty}$ and $K_1 = \Vert \nabla d\Vert_{L^\infty}$, we have
 \begin{align*}
@@
 \noindent
-If $p=2$, then $\alpha = 0$. The same calculation holds true with $\nu = 1+K_2\delta_0$ and we choose $C_\nu = \delta_0^{-2}\nu (\nu K_1+K_0K_2)$.
+If $p=2$, then $\alpha = 0$. We can easily see that the same calculation holds true with $\nu = 1+K_2\delta_0$ and we choose $C_\nu = \delta_0^{-2}\nu (\nu K_1+K_0K_2)$.
 \end{proof}
@@
 for $x\in \Omega$, where $\delta_{0,\Omega}$ is defined as in \eqref{def:delta_0}.
-In particular, for the case that $1<p<2$, $0\leq  u^\varepsilon(x) \leq C\varepsilon$ for $x\in \Omega_\varepsilon$, but $|u^\varepsilon(x)| = \mathcal{O}\left(\varepsilon^{\alpha+1}\right)$ on each compact subset of $\Omega$.
+In particular if $1<p<2$ we have $C_f\leq u^\varepsilon(x)\leq C_f + C\varepsilon$ for $x\in \Omega_\varepsilon$, but $|u^\varepsilon(x)| = \mathcal{O}\left(\varepsilon^{\alpha+1}\right)$ on each compact subset of $\Omega$.
 \end{thm}
@@
 How about "...twice continuoously differentiable for $x \in \Omega \setminus \overline{\Omega}_\frac{\kappa}{2}$"?}
-\begin{proof} By the definition of $\delta_0$, $d(x) = \mathrm{dist}(x,\partial\Omega)$ is twice continuously differentiable in the region $U_{\delta_0} = \Omega\backslash \overline{\Omega}_{\delta_0}$.
+\begin{proof} By the definition of $\delta_0 = \delta_{0,\Omega}$, we have $d(x) = \mathrm{dist}(x,\partial\Omega)$ is twice continuously differentiable in the region $U_{\delta_0} = \Omega\backslash \overline{\Omega}_{\delta_0}$.
 The proof follows from \cite[p.
@@
 \begin{equation*}
-    \Phi(x,y)= u^\varepsilon(x) - u(y) -\frac{C_0|x-y|^2}{\sigma} - \frac{\theta C_\alpha \varepsilon^{\alpha +1}}{d(x)^\alpha}, \qquad (x,y)\in \overline{\Omega}\times \overline{\Omega},
-\end{equation*}
-where $C_0$ is the Lipschitz constant of $u$ from \eqref{e:C0}, $\sigma\in (0,1)$ and $\theta>1$ to be determined.
+    \Phi(x,y)= u^\varepsilon(x) - u(y) -\frac{C_0|x-y|^2}{\sigma} - \frac{\nu C_\alpha \varepsilon^{\alpha +1}}{d(x)^\alpha}, \qquad (x,y)\in \overline{\Omega}\times \overline{\Omega},
+\end{equation*}
+where $C_0$ is the Lipschitz constant of $u$ from \eqref{e:C0}, $\sigma\in (0,1)$.
 The fact that $\displaystyle d(x)^\alpha u^\varepsilon(x) \to C_\alpha \varepsilon^{\alpha+1}$ as $d(x) \to 0$ implies
@@
 \begin{align}\label{e:subsln}
-    &u^\varepsilon(x_\sigma) + \left|\frac{2C_0(x_\sigma - y_\sigma)}{\sigma} -  \frac{\theta C_\alpha\alpha \varepsilon^{\alpha+1} \nabla d(x_\sigma)}{d(x_\sigma)^{\alpha+1}}\right|^p - f(x_\sigma)\nonumber\\
-    &\qquad -\varepsilon\left(\frac{2nC_0}{\sigma}+ \frac{\theta C_\alpha\alpha(\alpha+1) \varepsilon^{\alpha+1}|\nabla d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+2}} - \frac{\theta C_\alpha\alpha \varepsilon^{\alpha+1}\Delta d(x_\sigma)}{d(x_\sigma)^{\alpha+1}}\right) \leq 0.
+    &u^\varepsilon(x_\sigma) + \left|\frac{2C_0(x_\sigma - y_\sigma)}{\sigma} -  \frac{\nu C_\alpha\alpha \varepsilon^{\alpha+1} \nabla d(x_\sigma)}{d(x_\sigma)^{\alpha+1}}\right|^p - f(x_\sigma)\nonumber\\
+    &\qquad -\varepsilon\left(\frac{2nC_0}{\sigma}+ \frac{\nu C_\alpha\alpha(\alpha+1) \varepsilon^{\alpha+1}|\nabla d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+2}} - \frac{\nu C_\alpha\alpha \varepsilon^{\alpha+1}\Delta d(x_\sigma)}{d(x_\sigma)^{\alpha+1}}\right) \leq 0.
 \end{align}
@@
 \begin{equation*}
-    \xi_\sigma := \frac{2C_0(x_\sigma - y_\sigma)}{\sigma} \qquad\text{and}\qquad \zeta_\sigma :=- \frac{\theta C_\alpha\alpha \varepsilon^{\alpha+1} \nabla d(x_\sigma)}{d(x_\sigma)^{\alpha+1}}.
+    \xi_\sigma := \frac{2C_0(x_\sigma - y_\sigma)}{\sigma} \qquad\text{and}\qquad \zeta_\sigma :=- \frac{\nu C_\alpha\alpha \varepsilon^{\alpha+1} \nabla d(x_\sigma)}{d(x_\sigma)^{\alpha+1}}.
 \end{equation*}
@@
 \begin{equation*}
-    |\xi_\sigma|\leq 2C_0 \qquad\text{and}\qquad |\zeta_\sigma| \leq \theta K_1 C_\alpha\alpha \left(\frac{\varepsilon}{d(x_\sigma)}\right)^{\alpha+1} \leq \theta K_1 C_\alpha \alpha  \left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+1}.
+    |\xi_\sigma|\leq 2C_0 \qquad\text{and}\qquad |\zeta_\sigma| \leq \nu K_1 C_\alpha\alpha \left(\frac{\varepsilon}{d(x_\sigma)}\right)^{\alpha+1} \leq \nu K_1 C_\alpha \alpha  \left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+1}.
 \end{equation*}
@@
     \Big||\xi_\sigma +\zeta_\sigma|^p - |\xi_\sigma|^p \Big| &\leq p\Big(|\xi_\sigma|+|\zeta_\sigma|\Big)^{p-1}|\zeta_\sigma|\nonumber\\
-    &\leq p\left[2C_0+\theta K_1 C_\alpha\alpha \left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+1}\right]^{p-1}\theta K_1 C_\alpha\alpha \left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+1}.
+    &\leq p\left[2C_0+\nu K_1 C_\alpha\alpha \left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+1}\right]^{p-1}\nu K_1 C_\alpha\alpha \left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+1}.
 \end{align}
@@
 \begin{align*}
-     u^\varepsilon(x_\sigma) - u(y_\sigma) \leq & p\left(2C_0+\theta K_1 C_\alpha \alpha\left( \frac{2\varepsilon}{\kappa}\right)^{\alpha+1}\right)^{p-1}\theta K_1 C_\alpha \alpha \left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+1} + C\sigma\nonumber\\
-    &+2nC_0\left(\frac{\varepsilon}{\sigma}\right) + \theta K_1^2C_\alpha \alpha(\alpha+1)\left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+2} + \theta K_2 C_\alpha \alpha  \left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+1}\varepsilon\nonumber\\
+     u^\varepsilon(x_\sigma) - u(y_\sigma) \leq & p\left(2C_0+\nu K_1 C_\alpha \alpha\left( \frac{2\varepsilon}{\kappa}\right)^{\alpha+1}\right)^{p-1}\nu K_1 C_\alpha \alpha \left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+1} + C\sigma\nonumber\\
+    &+2nC_0\left(\frac{\varepsilon}{\sigma}\right) + \nu K_1^2C_\alpha \alpha(\alpha+1)\left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+2} + \nu K_2 C_\alpha \alpha  \left(\frac{2\varepsilon}{\kappa}\right)^{\alpha+1}\varepsilon\nonumber\\
     &\leq C\left[\sigma + \frac{\varepsilon}{\sigma} + \left(1+\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1}\right)^{p-1}\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1} + \left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2} \right].
@@
 \begin{align}
-    \Phi(x_\sigma, y_\sigma)\leq u^\varepsilon(x_\sigma) - u(y_\sigma)\leq u^\varepsilon(x_\sigma) \leq  \frac{\nu C_\alpha\varepsilon^{\alpha+1}}{d(x)^{\alpha}} + C_3\left(\frac{4\varepsilon}{\kappa}\right)^{\alpha+2} \label{e:final2}.
+    \Phi(x_\sigma, y_\sigma)\leq u^\varepsilon(x_\sigma) - \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x_\sigma)^\alpha} \leq C_3\left(\frac{4\varepsilon}{\kappa}\right)^{\alpha+2} \label{e:final2}.
 \end{align}
+%\textcolor{red}{(I just read this one more time and feel confused here as the RHS should be $\frac{\nu C_\alpha \epsilon^{\alpha + 1}}{d(x_\sigma)}+C_3(\frac{4\epsilon}{\kappa})^{\alpha+2}$.
+But then the following arguement doesn't make sense.
+I think the inequality should be something like
+%\begin{equation*}
+%\begin{aligned}
+%    \Phi(x_\sigma, y_\sigma) &\leq u^\varepsilon (x_\sigma)- \frac{\theta  C_\alpha  \varepsilon^{\alpha+1}}{d(x_\sigma)^\alpha}\nonumber\\
+ %   &= u^\varepsilon (x_\sigma)-\frac{\nu C_\alpha  \varepsilon^{\alpha+1}}{d_\kappa(x_\sigma)^\alpha}
+ %   \leq C_3\left(\frac{4\varepsilon}{\kappa}\right)^{\alpha+2}
+%\end{aligned}   
+%\end{equation*} 
+%where we choose $\theta = \nu$, similar to the proof in draft01. The conclusion isn't much more different.)}
+\noindent
 Since $\Phi(x,x) \leq \Phi(x_\sigma,y_\sigma)$ for all $x\in \Omega$, we obtain from \eqref{e:final1} and \eqref{e:final2} that
 \begin{equation*}
-    u^\varepsilon(x)-u(x)-\frac{\theta C_\alpha  \varepsilon^{\alpha+1}}{d(x)^\alpha} \leq C\sqrt{\varepsilon} + \frac{\nu C_\alpha\varepsilon^{\alpha+1}}{d(x)^\alpha}, \qquad x\in \Omega.
-\end{equation*}
-Therefore,
-\begin{equation*}
-   -C \sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x) \leq C\sqrt{\varepsilon} + \frac{(\nu+\theta) C_\alpha  \varepsilon^{\alpha+1}}{d(x)^\alpha} 
-\end{equation*}
-for every $x\in \Omega$. We can send $\theta \to 1^+$ to simplify the constant further and get that 
-\begin{equation}
-   -C \sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x) \leq C\sqrt{\varepsilon} + \frac{(\nu+1)C_\alpha  \varepsilon^{\alpha+1}}{d(x)^\alpha}, \qquad x\in \Omega
-\end{equation}
-where $C$ depends on $\kappa$. It follows that $|u^\varepsilon(x)-u(x)| \leq C\sqrt{\varepsilon}$ for $x\in \Omega_\varepsilon$. 
+    u^\varepsilon(x)-u(x)-\frac{\nu C_\alpha  \varepsilon^{\alpha+1}}{d(x)^\alpha} \leq C\sqrt{\varepsilon} +C_3\left(\frac{4\varepsilon}{\kappa}\right)^{\alpha+2}.
+\end{equation*}
+Therefore
+\begin{equation*}
+   -C \sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x) \leq C\left(\sqrt{\varepsilon}+\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2}\right) + \frac{\nu C_\alpha  \varepsilon^{\alpha+1}}{d(x)^\alpha}
+\end{equation*}
+for every $x\in \Omega$. It follows that $|u^\varepsilon(x)-u(x)| \leq C\sqrt{\varepsilon}$ for $x\in \Omega_\varepsilon$. 
 If $x\in U_k$, i.e., $f(x) = 0$, then \eqref{annulus2} gives us a better rate $\mathcal{O}(\varepsilon)$ in any compact set $K$ that is disjoint from $\mathrm{supp}(f)$. \\
@@
 \begin{equation*}
-    \Phi(x,y) = u^\varepsilon(x) - u(y) - \frac{C_0|x-y|^2}{\sigma} - \theta \varepsilon \mathrm{log}\left(\frac{1}{d(x)}\right), \qquad (x,y)\in \overline{\Omega}\times \overline{\Omega}.
-\end{equation*}
+    \Phi(x,y) = u^\varepsilon(x) - u(y) - \frac{C_0|x-y|^2}{\sigma} - \theta \varepsilon \mathrm{log}\left(\frac{1}{d(x)}\right), \qquad (x,y)\in \overline{\Omega}\times \overline{\Omega}
+\end{equation*}
+for some $\theta>1$.
 Similar to the previous case where $p<2$, the maximum of $\Phi$ must occur at $(x_\sigma,y_\sigma)\in \Omega\times\overline{\Omega}$ and $|x_\sigma - y_\sigma|\leq \sigma$.
@@
 \end{align*}
-Using $d(x_\sigma)\geq \frac{1}{2}\kappa$ and \eqref{boundond}, we see that
+Using $d(x_\sigma)\geq \frac{1}{2}\kappa$ and bounds on $d(x)$ as in \eqref{boundond}, we see that
 \begin{align}\label{p=2a}
@@
 where we choose $\sigma = \sqrt{\varepsilon}$.
-If $d(x_\sigma)<\frac{1}{2}\kappa$, then $x_\sigma\in U_\kappa$.
-Similar to the previous argument, we have $d_\kappa(x_\sigma) = d(x_\sigma)$ and from \eqref{annulus2p=2}
+
+\noindent
+If $d(x_\sigma)<\frac{1}{2}\kappa$, then $x_\sigma\in U_\kappa$. Similar to the previous argument, we have $d_\kappa(x_\sigma) = d(x_\sigma)$ and from \eqref{annulus2p=2}
 \begin{equation}\label{p=2b}
@@
 \begin{equation*}
-    -C\sqrt{\varepsilon}\leq u^\varepsilon(x) - u(x) \leq C\sqrt{\varepsilon} +  \varepsilon \log\left(\frac{1}{d(x)}\right), \qquad x\in \Omega.
+    -C\sqrt{\varepsilon}\leq u^\varepsilon(x) - u(x) \leq C \left(\sqrt{\varepsilon}+\varepsilon+\varepsilon|\log(\kappa)| + \left(\frac{\varepsilon}{\kappa}\right)^2\right) +  \varepsilon \log\left(\frac{1}{d(x)}\right), \qquad x\in \Omega.
 \end{equation*}
 Similar to the previous case, in the region where $0< d(x)\leq \varepsilon$, $|u^\varepsilon-u|=\mathcal{O}(\sqrt{\varepsilon})$ since $\varepsilon|\log(\varepsilon)|\leq \sqrt{\varepsilon}$.
-Therefore, the conclusion follows.
+Thus the conclusion follows.
 \end{proof}
@@
 
-\begin{rem} For a general datum Lipschitz $f\in \mathrm{C}(\overline{\Omega})$, it is natural to think about using cutoff function argument.
+\begin{rem} For general data Lipschitz $f\in \mathrm{C}(\overline{\Omega})$, it is natural to think about using cutoff function argument.
 Let $\chi_{{\kappa}}\in \mathrm{C}_c^\infty(\Omega)$ such that $0\leq \chi_{\kappa}\leq 1$, $\chi_\kappa = 1$ in $\Omega_{2\kappa}$ and $\mathrm{supp}\;\chi_\kappa\subset\Omega_\kappa$.
@@
 \end{rem}
+
+\subsection{A rate for zero boundary data}
 
@@
 \end{proof}
+
+\subsection{A generalization to some unbounded data} The approach we use allow us to apply to the situation where the data $f_\varepsilon$ blows up with some certain rates near the boundary such that $f_\varepsilon\to f$ in $L^1(\Omega)$.
+To simplify the presentation, we will assume $f\in \mathrm{C}^1(\Omega)$ and $f$ is bounded from below satisfying
+\begin{equation*}
+    f(x) = g(x) + \frac{\gamma \varepsilon^{\alpha+2}}{d(x)^{\alpha+2}}
+\end{equation*}
+where $g\in \mathrm{C}^1(\overline{\Omega})$with $g = 0$ on $\partial\Omega$ and $g\geq 0$ in $\Omega$.
 

### 2021-07-15 Drafts and notes/Draft_04.tex
Almost final

--- 2021-07-15 Drafts and notes/Draft_03.tex
@@
-\documentclass[11pt,reqno]{amsart}
+\documentclass[12pt,reqno]{amsart}
 %============%============%============%============%
@@
 \usepackage[toc,page]{appendix}
+\newcommand{\stoptocwriting}{%
+  \addtocontents{toc}{\protect\setcounter{tocdepth}{-5}}}
+\newcommand{\resumetocwriting}{%
+  \addtocontents{toc}{\protect\setcounter{tocdepth}{\arabic{tocdepth}}}}
+
 %\setcounter{secnumdepth}{4}
@@
 \title[Rate of convergence]
-{\textsc{Remarks on the vanishing viscosity of state-constraint Hamilton--Jacobi equations}}
-\thanks{The authors is supported in part by NSF grant DMS-1664424 and NSF CAREER grant DMS-1843320
-to Hung Vinh Tran. The work of Son N. T. Tu is supported in part by the GSSC Fellowship, University of Wisconsin--Madison.}
+{\textsc{Remarks on the vanishing viscosity process of state-constraint Hamilton--Jacobi equations}}
+\thanks{The authors are supported in part by NSF grant DMS-1664424 and NSF CAREER grant DMS-1843320.
+The work of Son N.
+T.
+Tu is supported in part by the GSSC Fellowship, University of Wisconsin--Madison.}
 \begin{abstract}
-We investigate qualitatively the convergence of large solution (state-constraint solution) to the subquadratic quasilinear elliptic equation as the viscosity vanishes.
-We show by a simple proof that for Lipschitz data that vanish on the boundary, the rate of convergence is at least $\mathcal{O}(\sqrt{\varepsilon})$ with a specific boundary layer.
-The rate can be improved in some region to $\mathcal{O}(\varepsilon)$, for instance, on the whole domain with zero data.
-The proof relies on a domain decomposition technique and classical tools in the viscosity solution theory.
+We investigate the convergence rate in the vanishing viscosity process of  the solution to the state-constraint Hamilton-Jacobi equation.
+We show by a simple proof that for Lipschitz data that vanish on the boundary, the rate of convergence is $\mathcal{O}(\sqrt{\varepsilon})$ with a specific boundary layer.
+Moreover, the rate can be improved to $\mathcal{O}(\varepsilon)$ in the region with zero data.
+The proof relies on the doubling variable method and the construction of a specific barrier.
 \end{abstract}
@@
 \date{\today}
-\keywords{first-order Hamilton--Jacobi equations; state-constraint problems; optimal control theory; rate of convergence; viscosity solutions.}
+\keywords{first-order Hamilton--Jacobi equations; second-order Hamilton--Jacobi equations; state-constraint problems; optimal control theory; rate of convergence; viscosity solutions.}
 \subjclass[2010]{
@@
 \setcounter{tocdepth}{1}
-\tableofcontents
+%\tableofcontents
 
@@
 \section{Introduction}\label{sec:intro}
-\subsection{Motivation} Let $\Omega$ be an open, bounded and connected domain of $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary, %Let us consider the following Hamiltonian $ H(x,\varrho) = |\varrho|^p-f(x)$ for $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$,
- $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$, and $u^\varepsilon\in \mathrm{C}^2(\Omega)$ (see \cite{Lasry1989}) be the solution to
+\subsection{Settings} Let $\Omega$ be an open, bounded and connected domain in $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary, $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
+Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ (see \cite{Lasry1989}) be the solution to
  \begin{equation}\label{eq:PDEepsa}
@@
  where $H:\R^n\to\R^n$ is a continuous Hamiltonian.
+Solution that blows up uniformly on the boundary is also called \emph{large solution}.
 A typical subquadratic Hamiltonian that has been considered in the literature is $H(\xi) = |\xi|^p$ for $\xi\in \R^n$ where $1<p\leq 2$.
-For simplicity of the presentation, we will consider this special case.
-
- %and generalize the result later to all Hamiltonian $H(\xi)$ for which (see \cite{sardarli_ergodic_2021} for a similar generalization)
- %\begin{equation*}
- %    \lim_{\delta\to 0}\delta^{\frac{p}{p-1}}H\left(\delta^{-\frac{1}{p-1}}\xi\right) = |\xi|^p \qquad\text{locally uniformly in}\;\xi\in \R^n.
- %\end{equation*}
- \noindent 
- With $H(\xi) = |\xi|^p$, the equation of interest then becomes
+We focus on this Hamiltonian in our paper, and the equation of interest becomes
 \begin{equation}\label{eq:PDEeps}
@@
 \end{equation}
-When $1<p\leq 2$, equation \eqref{eq:PDEeps} describes the value function associated with a minimization problem in stochastic optimal control with state constraint.
+When $1<p\leq 2$, equation \eqref{eq:PDEeps} describes the value function associated with a minimization problem in stochastic optimal control with state constraint (\cite{Lasry1989}).
 We are interested in studying the asymptotic behavior of $\{u^\varepsilon\}_{\varepsilon>0}$ as $\varepsilon\rightarrow 0^+$.
-Heuristically, the solution of the second-order state-constraint problem converges to that of a first-order state-constraint problem associated with deterministic optimal control, namely,
+Heuristically, the solution of the second-order state-constraint problem converges to that of a first-order state-constraint problem associated with the deterministic optimal control, namely,
 \begin{equation}\label{eq:PDE0}
@@
 as is described in the framework of viscosity solution.
-Equation \eqref{eq:PDE0} admits a unique viscosity solution in the space $\rmC(\overline{\Omega})$, which is also the maximal viscosity subsolution among all the viscosity subsolutions in $\rmC(\overline{\Omega})$.
+Equation \eqref{eq:PDE0} admits a unique viscosity solution in the space $\rmC(\overline{\Omega})$, which is also the maximal viscosity subsolution among all the viscosity subsolutions in $\rmC(\overline{\Omega})$(see \cite{Capuzzo-Dolcetta1990,Soner1986}).
 The problem is interesting since in the limit we no longer have blowing up behavior.
 In this paper, we investigate the rate of convergence of $u^\varepsilon \to u$ as $\varepsilon\to 0^+$.
-A boundary layer is expected to describe the behavior of this convergence near the boundary.
+What is intriguing and delicate here is the narrow boundary layer behavior near $\partial \Omega$.
 \subsection{Assumptions} We will always assume $\Omega$ is an open, bounded and connected domain in $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary satisfying either %$H:\mathbb{R}^n\times \mathbb{R}^n$ is a continuous Hamiltonian.
@@
 \begin{itemize}    
-    \item[(A1)] There exists a universal pair of positive numbers $(r,h)$ and $\eta\in \mathrm{BUC}(\overline{\Omega};\mathbb{R}^n)$ such that $B(x+t\eta(x), rt)\subset\Omega$ for all $t\in (0,h]$.
-    \item[(A2)] $\Omega$ is a bounded star-shaped (with respect to the origin) open subset of $\mathbb{R}^n$ such that
-    \begin{equation*}
-        \mathrm{dist}(x,\overline{\Omega}) \geq \kappa r \qquad\text{for all}\; x\in (1+r) \partial\Omega, \;\text{for all}\;r>0,
-    \end{equation*}
-for some $\kappa > 0$.
+    \item[(A1)] There exists a universal pair of positive numbers $(r,h)$ and $\eta\in \mathrm{BUC}(\overline{\Omega};\mathbb{R}^n)$ such that $B(x+t\eta(x), rt)\subset\Omega$ for all $t\in (0,h]$,
     \end{itemize}
-Equation \eqref{eq:PDEeps} follows the setting of \cite{Lasry1989}, where the specific structure of the Hamiltonian $H(x,\xi) = |\xi|^p - f(x)$ enables more explicit estimates on the solution of \eqref{eq:PDEeps}.
+    or
+    \begin{itemize}
+    \item[(A2)] $\Omega$ is a bounded star-shaped (with respect to the origin) open subset of $\mathbb{R}^n$ such that for some $\kappa > 0$,
+    \begin{equation*}
+        \mathrm{dist}(x,\overline{\Omega}) \geq \kappa r \qquad\text{for all}\; x\in (1+r) \partial\Omega, \;\text{for all}\;r>0.
+    \end{equation*}
+\end{itemize}
+Equation \eqref{eq:PDEeps} follows the setting of \cite{Lasry1989}, where the specific structure of the Hamiltonian $H(x,\xi) = |\xi|^p - f(x)$ enables more explicit estimates for the solution of \eqref{eq:PDEeps}.
 Assumption $\mathrm{(A1)}$ or $\mathrm{(A2)}$ guarantees that a comparison principle holds for the state-constraint problem \eqref{eq:PDE0}.
-We note that $\mathrm{(A1)}$ was first studied by M.
-Soner in \cite{Soner1986} (and $\mathrm{(A1)}$ holds for any smooth bounded domain), while $\mathrm{(A2)}$ was posed and studied by I.
-Capuzzo-Dolcetta and P.
-L.
-Lions in \cite{Capuzzo-Dolcetta1990}.
+Assumption $\mathrm{(A1)}$, which holds for any smooth bounded domain, was first studied in \cite{Soner1986}.
+Assumption $\mathrm{(A2)}$ was posed and studied in \cite{Capuzzo-Dolcetta1990}.
 %We list the assumptions on a general Hamiltonian as follow.
@@
 
-\subsection{Literature} There is a
+\subsection{Relevant literature} There is a
 vast amount of work in the literature on large solutions and second-order viscosity solutions with state constraints.
 The problem \eqref{eq:PDEeps} is first studied in \cite{Lasry1989} and subsequently many works have been done in understanding deeper the properties of solutions.
-We refer the readers to \cite{alessio_asymptotic_2006} and the references therein.
+%For instance, \textcolor{red}{(more references here.)}.
+We refer the readers to \cite{ Porretta_a,alessio_asymptotic_2006,Bandle_1994, marcus_existence_2003} and the references therein.
+The time-dependent version of \eqref{eq:PDEepsa} is also studied by many works, for instance \cite{barles_generalized_2004,barles_large_2010,leonori_local_2011,moll_large_2012} and the references therein.
 
 In terms of rate of convergence, up to our knowledge such a question has not been studied in the literature.
-For the case \eqref{eq:PDEeps} is equipped with Dirichlet boundary condition, a rate $\mathcal{O}(\sqrt{\varepsilon})$ is well known with multiple proofs (see \cite{tran_hamilton-jacobi_2021}).
+For the case \eqref{eq:PDEeps} is equipped with the Dirichlet boundary condition, a rate $\mathcal{O}(\sqrt{\varepsilon})$ is well known with multiple proofs (see \cite{Bardi1997,crandall1984, tran_hamilton-jacobi_2021}).
+We believe part of the reason why the problem is intriguing is that the blowing up behavior of the solution is complicated and deserves further investigation.
 
@@
 
-\begin{thm} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
-Assume that $1 < p\leq 2$ and $f$ is Lipschitz with the condition $f = 0$ on $\partial\Omega$.
+\begin{thm}\label{main_thm1} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
+Assume that $1 < p\leq 2$ and $f$ is Lipschitz with $f = 0$ on $\partial\Omega$.
 Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
@@
 \begin{align*}
-    &C\sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x)\leq C\sqrt{\varepsilon} + C\varepsilon \left(\frac{\varepsilon}{d(x)}\right)^{\frac{2-p}{p-1}} &\qquad\text{if}\; p < 2,\\
-    &C\sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x)\leq C\sqrt{\varepsilon} + \varepsilon|\log(d(x))| &\qquad\text{if}\; p = 2.
+    &-C\sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x)\leq C\sqrt{\varepsilon} + C\varepsilon \left(\frac{\varepsilon}{d(x)}\right)^{\frac{2-p}{p-1}} &\qquad\text{if}\; p < 2,\\
+    &-C\sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x)\leq C\sqrt{\varepsilon} + \varepsilon|\log(d(x))| &\qquad\text{if}\; p = 2.
 \end{align*}
@@
 
-\begin{rem} The condition $f = 0$ on $\partial\Omega$ can be explained as follows.
+\begin{rem} To the best of our knowledge, this theorem is new in the literature.
+We don't know if the order of $\varepsilon$ on the right hand side of the inequalities above is optimal or not near the boundary and this deserves further investigation.
+The condition $f = 0$ on $\partial\Omega$ is a little bit restrictive but can be explained as follows.
 One can see that the solution to \eqref{eq:PDEeps} is continuous with respect to data $f$ in the weak$^*$ topology of $L^\infty(\Omega)$ (see \cite{Lasry1989}).
-If $f = 0$ on $\partial\Omega$, we are able to approximate $f$ \emph{uniformly} in $L^\infty(\Omega)$ by a sequence of compactly supported functions, where a rate of $u^\varepsilon-u$ is easier to obtained.
+If $f = 0$ on $\partial\Omega$, we are able to approximate $f$ \emph{uniformly} in $L^\infty(\Omega)$ by a sequence of compactly supported functions, where a convergence rate of $u^\varepsilon-u$ is easier to obtain.
 Indeed, using the usual doubling variable technique, it is natural to consider the doubling variable for
-\begin{equation*}
+\begin{equation}\label{heur1}
     u^\varepsilon(x) - \frac{C\varepsilon^{\alpha+1}}{d(x)^{\alpha}}
-\end{equation*}
+\end{equation}
 and $u(x)$, where $C\varepsilon^{\alpha+1}d(x)^{-\alpha}$ is the leading order term in the asymptotic expansion of $u^\varepsilon(x)$ as $\mathrm{dist}(x,\partial\Omega)\to 0$.
-We can see a \emph{correct scale} heuristically happens around $d(x) \approx \varepsilon$.
-However, to control the extra leading term above, one needs to have $d(x)\approx \varepsilon^\gamma$ for $\gamma < 1$ to make the argument work.
-This major difficulty can be overcome when we decompose the solution into an inside part and an outside part that lies in an annulus, where we have reduced to the case of $f=0$.
+After taking derivative, heuristically, \eqref{heur1} becomes
+\begin{equation}\label{heur2}
+    Du^\varepsilon(x) + C\alpha \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}Dd(x).
+\end{equation}
+This suggests that $Du^\varepsilon \approx \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}$. We show that this is indeed true (Lemma \ref{lem:boundDu^eps}).
+
+\textcolor{blue}{
+However, to get a useful estimate by the doubling variable, at the maximum point $x_0$ of $u^\varepsilon(x) - u(x)$, we must have $d(x_0)\approx \varepsilon^{\gamma}$ for $\gamma<1$ so that the latter term in \eqref{heur2} vanishes as $\varepsilon\to 0$.
+It turns out that such an estimate is quite delicate.
+We overcome this difficulty by decomposing the solution into an inside part and an outside part near the boundary, where we have reduced to the case of $f=0$.}
 \end{rem}
+
+Using the convexity of $|\xi|^p$, we can avoid the doubling variable route to get a better one-sided estimate.
+Such an one-sided rate is well-known for the case of vanishing discount with zero Dirichlet boundary condition (see \textcolor{blue}{NEED CITATION}).
+
+\begin{thm}\label{main_thm2} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
+Assume that $1 < p\leq 2$ and $f$ is Lipschitz with $f = 0$ on $\partial\Omega$.
+Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
+Then there exists a constant $C$ such that for $x\in \Omega$,
+\begin{align*}
+    &-C\sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x)\leq  C\varepsilon \left(\frac{\varepsilon}{d(x)}\right)^{\frac{2-p}{p-1}} &\qquad\text{if}\; p < 2,\\
+    &-C\sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x)\leq  \varepsilon|\log(d(x))| &\qquad\text{if}\; p = 2.
+\end{align*}
+\end{thm}
+
+\subsection*{Organization of the paper} In Section 2, we state some preliminary results.
+In Section 3, we prove the main result on the rate of convergence.
+The proofs of some lemmas are presented in Appendix.
 
@@
     %\incfig{Domains}
-    \def\svgwidth{0.47\columnwidth}
+    \def\svgwidth{0.35\columnwidth}
     \import{./figs/}{Domains.pdf_tex}
-    \caption{The domain $\Omega$ variations $\Omega_\delta, \Omega^\delta$.}
+    \caption{The domain $\Omega$ and its variations $\Omega_\delta, \Omega^\delta$.}
     \label{fig:Domains}
@@
 
-We refer the readers to \cite{gilbarg_elliptic_2001} for the regularity of the distance function defined in the above definition.
+We refer the reader to \cite{gilbarg_elliptic_2001} for the regularity of the distance function defined in the definition above.
 We then extend $\mathrm{dist}(x,\partial\Omega)$ to a function $d(x)\in \mathrm{C}^2(\mathbb{R}^n)$ such that
@@
 \end{equation}
-Recall that $|D d(x)| = 1$ in the viscosity sense (and thus in classical sense) in $\Omega^{\delta_0}\backslash \Omega_{\delta_0}$. Let 
+Note that $|D d(x)| = 1$ in the viscosity sense (and thus in classical sense) in $\Omega^{\delta_0}\backslash \Omega_{\delta_0}$. Let 
 \begin{equation}\label{boundond}
@@
 \end{equation}
-\noindent We denote by $\mathcal{L}^\varepsilon:\rmC^2(\Omega)\to \rmC(\Omega)$ the operator
+\noindent Denote by $\mathcal{L}^\varepsilon:\rmC^2(\Omega)\to \rmC(\Omega)$ the operator
 \begin{equation*}
@@
 The following theorem is about the local gradient bound as in \cite[Appendix]{Lasry1989}.
-The technique being used is the classical Bernstein's method.
-Let $\Omega$ be an open, bounded subset of $\R^n$, $\varepsilon \in (0,1)$.
-We consider $p>1$ in this section.
-%We consider the Hamiltonian $H(x,\rho) = |\rho|^p - f(x)$ where $1<p < \infty$.
+The technique being used is the classical Bernstein method.
+Let $\Omega$ be an open, bounded subset of $\R^n$, $\varepsilon \in (0,1)$ and $p>1$.
 
 \begin{thm}\label{thm:grad_1} Let $f\in \rmC(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $u^\varepsilon \in \mathrm{C}^2(\Omega)$ be a solution to $\mathcal{L}^\varepsilon[u^\varepsilon] = 0$ in $\Omega$.
-Assume that $  u^\varepsilon(x)-f(x)\geq -m$ in $\Omega$.
+Let $m:= \max_{\overline{\Omega}}f(x)$.
 Then for $\delta>0$, there exists $C_\delta = C(m,p,\delta, \Vert D f\Vert_{L^\infty(\Omega)})$ such that
 \begin{equation*}
-    \sup_{x\in \overline{\Omega}_\delta} \Big(|u^\varepsilon(x)|+|Du^\varepsilon(x)|\Big) \leq C_\delta.
-\end{equation*}
+    \sup_{x\in \overline{\Omega}_\delta} \Big(|u^\varepsilon(x)|+|Du^\varepsilon(x)|\Big) \leq C_\delta
+\end{equation*}
+for $\varepsilon$ small enough.
 \end{thm}
-\noindent We provide a proof for this theorem in Appendix for the reader's convenience.
-
-\subsection{Well-posedness of large solution for subquaratic case} In this section we recall the existence and uniqueness of solutions to \eqref{eq:PDEeps} for $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
-We note that the assumption of $f$ can be relaxed to $f\in L^\infty(\Omega)$ (\cite{Lasry1989}).
+%\textcolor{orange}{(I think here we want to add for $\varepsilon$ small enough?)}
+
+\noindent A proof of this theorem is provided in Appendix for the reader's convenience.
+
+\subsection{Well-posedness of large solution} In this section, we recall the existence and the uniqueness of solutions to \eqref{eq:PDEeps} for $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
+In fact, the assumption of $f$ can be relaxed to $f\in L^\infty(\Omega)$ (\cite{Lasry1989}).
 
@@
 \end{itemize}
-Furthermore, $u^\varepsilon$ is the maximal subolution among all subsolution $v\in W^{2,r}(\Omega)$ (for all $r>0$) of \eqref{eq:PDEeps}.
+Furthermore, $u^\varepsilon$ is the maximal subsolution among all the subsolutions $v\in W^{2,r}(\Omega)$ (for all $r>0$) of \eqref{eq:PDEeps}.
 \end{thm}
-\noindent This is Theorem I.1 in \cite{Lasry1989} with an explicit dependence on $\varepsilon$. We provide a proof in Appendix for later use. It is useful to note that $\alpha+1 = (p-1)^{-1}$.
-
-\subsection{Convergence result} We show qualitatively the convergence of \eqref{eq:PDEeps} to \eqref{eq:PDE0}.
-We first state the following Lemma (\cite{Capuzzo-Dolcetta1990}), which characterizes the solution to the first-order state-constraint  equation
-\begin{equation}\label{S_0}
-\begin{cases}
-       u(x) + |Du(x)|^p - f(x) = 0\;\qquad\text{in}\;\Omega,\\
-       u(x) + |Du(x)|^p - f(x) \geq 0\;\qquad\text{on}\;\partial\Omega. 
-\end{cases}\tag{$S_0$}   
-\end{equation}
-
-\begin{lem}\label{lem:max} Let $u\in \rmC(\overline{\Omega})$ be a viscosity subsolution of \eqref{S_0} such that, for all viscosity subsolution $v\in \rmC(\overline{\Omega})$ of \eqref{S_0} one has $v\leq u$ in $\overline{\Omega}$.
-Then $u$ is a viscosity supersolution of \eqref{S_0} on $\overline{\Omega}$.
+\noindent This is Theorem I.1 in \cite{Lasry1989} with an explicit dependence on $\varepsilon$.
+A proof of this theorem is carried out explicitly in Appendix for later use.
+Also, it is useful to note that $\alpha+1 = (p-1)^{-1}$.
+More results on the behavior of the gradient of $u^\varepsilon$ can be found in \cite{alessio_asymptotic_2006}.
+
+\subsection{Convergence result} We first state the following Lemma (\cite{Capuzzo-Dolcetta1990}), which characterizes the solution to the first-order state-constraint  equation \eqref{eq:PDE0}.
+\begin{lem}\label{lem:max} Let $u\in \rmC(\overline{\Omega})$ be a viscosity subsolution of \eqref{eq:PDE0} such that, for any viscosity subsolution $v\in \rmC(\overline{\Omega})$ of \eqref{eq:PDE0} one has $v\leq u$ on $\overline{\Omega}$.
+Then $u$ is a viscosity supersolution of \eqref{eq:PDE0} on $\overline{\Omega}$.
 \end{lem}
-\noindent We give a proof of Lemma \ref{lem:max} in Appendix for the sake of completeness.
+\noindent A proof of Lemma \ref{lem:max} is given in Appendix for the readers' convenience.
 
 \begin{lem}\label{lem:lower-bound} Assume $1<p\leq 2$.
-Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ be a solution to \eqref{eq:PDEeps}.
+Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ be the solution to \eqref{eq:PDEeps}.
 We have $\{  u^\varepsilon\}_{\varepsilon>0}$ is uniformly bounded from below by a constant independent of $\varepsilon$.
-More precisely, we have $  u^\varepsilon \geq \min_\Omega f$ and $  u\geq \min_\Omega f$.
+More precisely, $  u^\varepsilon \geq \min_\Omega f$ and $  u\geq \min_\Omega f$.
 %\begin{equation}\label{e:lower_bound_u_eps}
@@
 \end{equation}
-We have $u^{\varepsilon}_m(x) \to u^\varepsilon(x)$ as $m\to \infty$ in $\Omega$.
+We have $u^{\varepsilon}_m(x) \to u^\varepsilon(x)$ in $\Omega$ as $m\to \infty$.
 Let $\varphi(x) \equiv  \inf_{\Omega} f$ for $x\in \overline{\Omega}$.
@@
 \begin{equation*}
-    \varphi(x) =   \inf_\Omega f \leq m = u^\varepsilon_m(x) \qquad\text{for}\;x\in \partial\Omega.
-\end{equation*}
-By comparison principle for the uniformly elliptic equation \eqref{e:uepsm}, we have
+    \varphi(x) =   \inf_\Omega f \leq m = u^\varepsilon_m(x) \qquad \text{on } \partial \Omega,
+\end{equation*}
+for $m$ large enough.
+By the comparison principle of the uniformly elliptic equation \eqref{e:uepsm},
 \begin{equation*}
@@
 As $m\to \infty$, we obtain $  u^\varepsilon \geq \min_\Omega f$.
-The inequality $  u\geq \min_{\Omega}f$ follows from the comparison principle of \eqref{eq:PDE0} between supersolution $u$ on $\overline{\Omega}$ and subsolution $\varphi(x)$ in $\Omega$.
+The inequality $  u\geq \min_{\Omega}f$ follows from the comparison principle of \eqref{eq:PDE0} applied to the supersolution $u$ on $\overline{\Omega}$ and the subsolution $\varphi(x)$ in $\Omega$.
 \end{proof}
@@
 We present a simple proof of the convergence $u^\varepsilon \to u$ using Lemma \ref{lem:max} for the reader's convenience. See also \cite[Theorem VII.3]{Capuzzo-Dolcetta1990}.
-\begin{thm}[Vanishing viscosity]\label{thm:qual} Assume $\mathrm{(A1)}$.
+\begin{thm}[Vanishing viscosity]\label{thm:qual} Assume $\mathrm{(A1)}$ or $\mathrm{(A2)}$.
 Let $u^\varepsilon$ be the solution to \eqref{eq:PDEeps}.
-Then there exists $u \in \mathrm{C}(\overline{\Omega})$ such that $u^\varepsilon \rightarrow u$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$, where $u$ solves \eqref{eq:PDE0} in $\Omega$.
+Then there exists $u \in \mathrm{C}(\overline{\Omega})$ such that $u^\varepsilon \rightarrow u$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$ and $u$ solves \eqref{eq:PDE0}.
 \end{thm}
 
-\begin{proof}[Proof of Theorem \ref{thm:qual}] By a priori estimate (Theorem \ref{thm:grad_1}), we have
+\begin{proof}[Proof of Theorem \ref{thm:qual}] By a priori estimate (Theorem \ref{thm:grad_1}), 
 \begin{equation}\label{e:priorie_eps}
@@
 \begin{equation}\label{eq:u0int}
-     u(x) + |Du(x)| - f(x) = 0 \qquad\text{in}\;\Omega.
-\end{equation}
-From Lemma \ref{lem:lower-bound}, we have $  u^\varepsilon(x)\geq \min_{\Omega} f$ and  $  u(x)\geq \min_{\Omega} f$ for all $x\in \Omega$.
+     u(x) + |Du(x)|^p - f(x) = 0 \qquad\text{in}\;\Omega.
+\end{equation}
+From Lemma \ref{lem:lower-bound}, $  u^\varepsilon(x)\geq \min_{\Omega} f$ and  $  u(x)\geq \min_{\Omega} f$ for all $x\in \Omega$.
 Together with \eqref{eq:u0int}, we obtain $|\xi|\leq \max_\Omega f - \min_\Omega f$ for all $\xi\in D^+u(x)$ and $x\in \Omega$.
-In other words, there is a constant $C_0$ such that
+This implies there exits a constant $C_0$ such that
 \begin{equation}\label{e:C0}
@@
 \end{equation}
-Thus, we can extend $u$ uniquely to $u\in \rmC(\overline{\Omega})$. We will use Lemma \ref{lem:max} to show that $u$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$.
+Thus, we can extend $u$ uniquely to $u\in \rmC(\overline{\Omega})$. We will use Lemma \ref{lem:max} to show that $u$ is a supersolution of \eqref{eq:PDE0} on $\overline{\Omega}$.
 
 It suffices to show that $u\geq w$ on $\overline{\Omega}$, where $w\in \rmC(\overline{\Omega})$ is the unique solution to \eqref{eq:PDE0}.
-For $\delta>0$, let $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\partial \Omega) > \delta\}$ and $u_\delta\in\rmC(\overline{\Omega}_\delta)$ be the  unique viscosity solution to
+For $\delta>0$, let $u_\delta\in\rmC(\overline{\Omega}_\delta)$ be the  unique viscosity solution to
 \begin{equation}\label{e:v_v}
     \begin{cases}
-      u_\delta(x) + |Du_\delta(x)|-f(x) \leq 0 &\qquad\text{in}\;\Omega_\delta,\\
-      u_\delta(x) + |Du_\delta(x)| - f(x) \geq 0 &\qquad\text{on}\;\overline{\Omega}_\delta.
+      u_\delta(x) + |Du_\delta(x)|^p-f(x) \leq 0 &\qquad\text{in}\;\Omega_\delta,\\
+      u_\delta(x) + |Du_\delta(x)|^p - f(x) \geq 0 &\qquad\text{on}\;\overline{\Omega}_\delta.
     \end{cases}
@@
       v_\delta^\varepsilon(x) + |Dv_\delta^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v_\delta^\varepsilon(x) &\qquad\text{in}\;\Omega_\delta,\\
-    \;\;\;\,\quad\qquad\qquad\qquad\qquad v_\delta^\varepsilon = v_\delta &\qquad \text{on}\;\partial\Omega_\delta.
+    \;\;\;\,\quad\qquad\qquad\qquad\qquad v_\delta^\varepsilon = u_\delta &\qquad \text{on}\;\partial\Omega_\delta.
 \end{cases}
 \end{equation}
-It is well-known that $v^\varepsilon_\delta\to v_\delta$ uniformly on $\overline{\Omega}_\delta$ as $\varepsilon\to 0$.
-
-For all $\delta$ small enough, $v_\delta\leq u^\varepsilon$ on $\partial \Omega_\delta$.
-Hence by maximum principle, $v^\varepsilon_\delta \leq u^\varepsilon$ on $\overline{\Omega}_\delta$.
-Let $\varepsilon\to 0$ and we have $v_\delta \leq u$ on $\overline{\Omega}_\delta$.
-Let $\delta\rightarrow 0$ and we obtain $w\leq u$ in $\Omega$, which implies $w\leq u$ on $\overline{\Omega}$ since both $w,u$ belong to $\rmC(\overline{\Omega})$.
-\end{proof}
-
-\section{Rate of convergence via the doubling variables method}
-In this section, we focus on the rate of convergence for the case $f\in \mathrm{W}^{1,\infty}(\Omega)\cap\mathrm{C}(\overline{\Omega})$.
-By adding a constant to the solution $u^\varepsilon$ of \eqref{eq:PDEeps}, without loss of generality we can assume the \emph{nonnegativity}
+It is well-known that $v^\varepsilon_\delta\to u_\delta$ uniformly on $\overline{\Omega}_\delta$ as $\varepsilon\to 0$.
+
+For $\delta$ small enough, $u_\delta\leq u^\varepsilon$ on $\partial \Omega_\delta$.
+Hence by the maximum principle, $v^\varepsilon_\delta \leq u^\varepsilon$ on $\overline{\Omega}_\delta$.
+Now we first let $\varepsilon\to 0$ to obtain $u_\delta \leq u$ on $\overline{\Omega}_\delta$.
+Then let $\delta\rightarrow 0$ to get $w\leq u$ in $\Omega$, which implies $w\leq u$ on $\overline{\Omega}$ since both $w,u$ belong to $\rmC(\overline{\Omega})$.
+\end{proof}
+
+\section{Rate of convergence}
+In this section, we focus on the rate of convergence for the case $f\in \mathrm{W}^{1,\infty}(\Omega)\cap\mathrm{C}(\overline{\Omega})$ with an extra assumption to be described.
+By adding a constant to the solution $u^\varepsilon$ of \eqref{eq:PDEeps}, without loss of generality, we can assume the \emph{nonnegativity} of $f$, i.e.,
 \begin{equation}\label{e:minf}
@@
 \end{equation}
-As a consequence, $u^\varepsilon(x),u(x)\geq 0$ for $x\in \Omega$ by Lemma \ref{lem:lower-bound}. We start with the lower bound of $u^\varepsilon - u$.
-\begin{thm} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
-Assume \eqref{e:minf} and $H(x,\xi) = |\xi|^p - f(x)$ where $p\in\left(1,2\right]$.
-Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
-Then there exists a constant $C$ independent of $\varepsilon$ such that
+As a consequence, $u^\varepsilon(x),u(x)\geq 0$ for $x\in \Omega$ by Lemma \ref{lem:lower-bound}.
+Before we show any result about the rate of convergence, we would like to mention a lower bound of $u^\varepsilon - u$ and some properties of $u$ from its optimal control formula.
+\begin{thm} Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}. Then there exists a constant $C$ independent of $\varepsilon$ such that
 \begin{equation}\label{e:lower1}
@@
 \end{thm}
-\begin{proof} The proof relies on a well-known rate of convergence for vanishing viscosity of viscous Hamilton--Jacobi equation with Dirichlet boundary condition (see \cite{Calder2021,crandall_two_1984,evans_adjoint_2010,fleming_convergence_1961,Tran2011}).
-As $u\in \mathrm{C}(\overline{\Omega})$, let $g\in \mathrm{C}(\partial\Omega)$ defined by $g(x) = u(x)$ for $x\in \partial\Omega$.
+\begin{proof} The proof relies on a well-known rate of convergence for vanishing viscosity of the viscous Hamilton--Jacobi equation with the Dirichlet boundary condition (see \cite{crandall1984,evans_adjoint_2010,fleming_convergence_1961,Tran2011}).
+Let $g(x) = u(x)$ for $x\in \partial\Omega$.
 Let $v^\varepsilon\in \mathrm{C}^2(\Omega)\cap \mathrm{C}(\overline{\Omega})$ be the unique viscosity solution to
@@
 \end{equation*}
-It is well-known that $v^\varepsilon \to u$ uniformly where $v$ is the viscosity solution to
-\begin{equation*}
-\begin{cases}
-       v(x) + |Dv(x)|^p - f(x) = 0 &\qquad\text{in}\;\Omega,\\
-     \qquad\qquad\qquad\quad\;\;\; v(x) = g(x)&\qquad\text{on}\;\partial\Omega. 
-\end{cases}
-\end{equation*}
-By comparison principle, it is clear that $v = u$, the solution of \eqref{eq:PDE0}. Furthermore, there exists a positive constant $C$ such that 
+It is well-known that $v^\varepsilon \to u$. Furthermore, there exists a positive constant $C$ such that 
 \begin{equation}\label{e:cp1}
@@
 \end{equation}
-By comparison principle for \eqref{eq:PDEeps}, we have
+By the comparison principle for \eqref{eq:PDEeps}, we have
 \begin{equation}\label{e:cp2}
@@
 \end{equation}
-From \eqref{e:cp1} and \eqref{e:cp2} we obtain the lower bound \eqref{e:lower1}.
+From \eqref{e:cp1} and \eqref{e:cp2}, we obtain the lower bound \eqref{e:lower1}.
 \end{proof}
@@
 
-\begin{lem}\label{lem:f=0} Assume $f\geq 0$ in $\Omega$. Then $u(x) = 0$ whenever $f(x) = 0$. In particular, $f \equiv 0$ implies $u \equiv 0$.
+\begin{lem}\label{lem:f=0} Assume $f\geq 0$ in $\Omega$. Then $u(x) = 0$ if and only if $f(x) = 0$. In particular, $f \equiv 0$ implies $u \equiv 0$.
 \end{lem}
-\begin{proof} It is clear that $u\geq 0$ in $\overline{\Omega}$. Using the optimal control formula (see \cite{Bardi1997,tran_hamilton-jacobi_2021}), we have
+\begin{proof} From Lemma \ref{lem:lower-bound}, we know $u\geq 0$ in $\overline{\Omega}$.
+The optimal control formula for the solution $u$ to \eqref{eq:PDE0} is (see \cite{Bardi1997,tran_hamilton-jacobi_2021})
 \begin{equation}\label{e:foru}
@@
 \end{equation*}
-As a consequence, if $f\equiv 0$, then $u\equiv 0$.
-\end{proof}
-\noindent We state the following lemma as a crucial estimate we will be using. It is a refined construction of the supersolution for \eqref{eq:PDEeps}.
+As a consequence, $f\equiv 0$ implies $u\equiv 0$.
+
+It is not hard to prove the converse by contradiction.
+Suppose $u(x_0) =0$ and $f(x_0)>0$.
+Then there exists $\varepsilon$, $\delta >0$ such that $f(x) > \varepsilon$ for all $x \in B_{\delta} (x_0)$.
+Let $\eta \in AC([0,\infty);\overline{\Omega})$ such that $\eta(0)=x_0$ and t be the time that $\eta$ first hits $\partial B_{\delta}(x_0)$.
+Note that $t$ could be $+\infty$.
+Then
+\begin{equation*}
+    \begin{aligned}
+        \int_0^\infty e^{-s} \left(|\dot{\eta}(s)|^q +f(s )\right) ds &\geq \int_0^t e^{-s} \left(|\dot{\eta}(s)|^q +f(s )\right) ds\\
+        &\geq  \frac{1}{e^t t^{q-1}}\left| \int_0^t \dot{\eta} (s) ds\right|^q+ \varepsilon \left(1-e^{-t} \right)\\
+        &\geq \frac{\delta^q}{e^t t^{q-1}}+\varepsilon \left(1-e^{-t} \right),
+    \end{aligned}
+\end{equation*}
+where we used Jensen's inequality in the second line.
+This implies $u(x_0)>0$ since $q \geq 2$, which is a contradiction.
+\end{proof}
+\noindent The following lemma is about a crucial estimate that will be used. It is a refined construction of a supersolution for \eqref{eq:PDEeps}.
 \begin{lem}\label{lem:super_refined} Let $\delta_0$ be defined as in \eqref{def:delta_0}.
@@
 is a supersolution of \eqref{eq:PDEeps} in $\Omega$. 
-%\item[(ii)] If $x\mapsto \mathrm{dist}(x,\partial\Omega)$ is continuously differentiable with $|\nabla \mathrm{dist}(x,\partial\Omega)| = 1$ everywhere in $\Omega$ then we can take $C_\nu = 0$ in \eqref{e:superwa}.
+%\item[(ii)] If $x\mapsto \mathrm{dist}(x,\partial\Omega)$ is continuously differentiable with $|D \mathrm{dist}(x,\partial\Omega)| = 1$ everywhere in $\Omega$ then we can take $C_\nu = 0$ in \eqref{e:superwa}.
 \end{lem}
@@
 
-\begin{proof} Let us first consider $1<p<2$.
-We have $|\nabla d(x)| = 1$ for all $x\in \Omega_\delta\backslash \overline{\Omega}_{\delta_0}$.
-Recall from Theorem \ref{thm:wellposed1<p<2} that $C_\alpha^p \alpha^p = C_\alpha \alpha (\alpha+1)$ and $p(\alpha+1) = \alpha+2$.
-Compute
-\begin{equation*}
-    |\nabla w(x)|^p = \nu^p\frac{(C_\alpha\alpha)^p\varepsilon^{p(\alpha+1)}}{(d(x)-\delta)^{p(\alpha+1)}} = \nu^p\frac{C_\alpha \alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}
+\begin{proof} Let us first consider $1<p<2$. Recall from Theorem \ref{thm:wellposed1<p<2} that $C_\alpha^p \alpha^p = C_\alpha \alpha (\alpha+1)$ and $p(\alpha+1) = \alpha+2$. Compute 
+\begin{equation*}
+    |D w(x)|^p = \nu^p\frac{(C_\alpha\alpha)^p\varepsilon^{p(\alpha+1)}}{d(x)^{p(\alpha+1)}} \left| Dd(x) \right|^p= \nu^p\frac{C_\alpha \alpha(\alpha+1)\varepsilon^{\alpha+2}}{d(x)^{\alpha+2}}  \left| Dd(x) \right|^p
 \end{equation*}
@@
 \begin{equation*}
-    \varepsilon\Delta w(x) = \nu\frac{C_\alpha\alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}} - \nu\frac{C_\alpha\alpha\varepsilon^{\alpha+2}\Delta d(x)}{(d(x)-\delta)^{\alpha+1}}.
-\end{equation*}
-Recall that $K_2= \Vert \Delta d\Vert_{L^\infty}$, we have
-\begin{equation*}
-    \begin{split}
-        \mathcal{L}^\varepsilon\left[w_\delta\right] =  \frac{\nu C_\alpha\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + \max f - f(x) + C_\nu \varepsilon^{\alpha+2} + \frac{C_\alpha \alpha (\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}\left[\nu^p-\nu +\nu\frac{(d(x)-\delta)\Delta d(x)}{\alpha+1}\right] .
-    \end{split}
-\end{equation*}
-\paragraph{\textbf{Case 1.}} If $\delta< d(x)\leq \delta_0$, we observe that
-\begin{equation*}
-    \left|\frac{(d(x)-\delta)\Delta d(x)}{\alpha+1}\right| \leq \frac{\delta_0\Vert \Delta d\Vert_{L^\infty}}{\alpha+1} \leq \frac{K_2\delta_0}{\alpha+1}\leq K_2\delta_0.
+    \varepsilon\Delta w(x) = \nu\frac{C_\alpha\alpha(\alpha+1)\varepsilon^{\alpha+2}}{d(x)^{\alpha+2}} \left| Dd(x)\right|^2- \nu\frac{C_\alpha\alpha\varepsilon^{\alpha+2}\Delta d(x)}{d(x)^{\alpha+1}}.
+\end{equation*}
+We have
+\begin{equation*}
+    \begin{aligned}
+        \mathcal{L}^\varepsilon\left[ w \right] =  &\frac{\nu C_\alpha\varepsilon^{\alpha+1}}{d(x)^\alpha} + \max f - f(x) + C_\nu \varepsilon^{\alpha+2} \\&+ \frac{C_\alpha \alpha (\alpha+1)\varepsilon^{\alpha+2}}{d(x)^{\alpha+2}}\left[\nu^p\left| Dd(x) \right|^p-\nu \left| Dd(x)\right|^2+\nu\frac{d(x)\Delta d(x)}{\alpha+1}\right] .
+    \end{aligned}
+\end{equation*}
+\paragraph{\textbf{Case 1.}} If $\delta< d(x)\leq \delta_0$, we have $|D d(x)| = 1$. Recall that $K_2= \Vert \Delta d\Vert_{L^\infty}$ and observe
+\begin{equation*}
+    \left|\frac{d(x)\Delta d(x)}{\alpha+1}\right| \leq \frac{\delta_0\Vert \Delta d\Vert_{L^\infty}}{\alpha+1} \leq \frac{K_2\delta_0}{\alpha+1}\leq K_2\delta_0.
 \end{equation*}
@@
     \begin{split}
-        \nu^p-\nu +\nu\frac{(d(x)-\delta)\Delta d(x)}{(\alpha+1)} \geq \nu^p - \nu - \nu K_2\delta_0 = \nu\Big(\nu^{p-1} - (1+K_2\delta_0)\Big).
+        \nu^p-\nu +\nu\frac{d(x) \Delta d(x)}{(\alpha+1)} \geq \nu^p - \nu - \nu K_2\delta_0 = \nu\Big(\nu^{p-1} - (1+K_2\delta_0)\Big).
     \end{split}
@@
 \end{equation}
-Choose $\nu = 1+C_2\delta_0$ in \eqref{e:choose_nu}and we obtain $\mathcal{L}[w]\geq 0$ in $\{x\in \Omega_\delta: \delta <d(x)\leq \delta_0\}$.
-
-\paragraph{\textbf{Case 2.}} If $d(x)\geq \delta_0$, recall that $K_0 = \Vert d\Vert_{L^\infty}$ and $K_1 = \Vert \nabla d\Vert_{L^\infty}$, we have
+Choose $\nu = 1+C_2\delta_0$ in \eqref{e:choose_nu} and we obtain $\mathcal{L}[w]\geq 0$ in $\{x\in \Omega_\delta: \delta <d(x)\leq \delta_0\}$. \\
+
+\paragraph{\textbf{Case 2.}} If $d(x)\geq \delta_0$, recall that $K_0 = \Vert d\Vert_{L^\infty}$ and $K_1 = \Vert D d\Vert_{L^\infty}$, and we have
 \begin{align*}
-    \mathcal{L}[w] &= \frac{\nu C_\alpha\alpha\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + \max_{\Omega} f - f(x)\\
-    &+  \nu^p\frac{C_\alpha\alpha(\alpha+1)\varepsilon^{\alpha+1}}{(d(x)-\delta)^{\alpha+2}}|\nabla d(x)|^p - \nu \frac{C_\alpha \alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}|\nabla d(x)|^2
-    + \nu \frac{C_\alpha \alpha \varepsilon^{\alpha+2}\Delta d(x)}{(d(x)-\delta)^{\alpha+1}} + C_\nu \varepsilon^{\alpha+2}\\
-    &\geq \frac{C_\alpha \alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}\left(\nu^p|\nabla d(x)|^p - \nu |\nabla d(x)|^2 + \nu \frac{\Delta d(x)(d(x)-\delta)}{\alpha+1}\right) + C_\nu \varepsilon^{\alpha+2}\\
+    \mathcal{L}[w] &= \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} + \max_{\Omega} f - f(x)\\
+    &+  \nu^p\frac{C_\alpha\alpha(\alpha+1)\varepsilon^{\alpha+2}}{d(x)^{\alpha+2}}|D d(x)|^p - \nu \frac{C_\alpha \alpha(\alpha+1)\varepsilon^{\alpha+2}}{d(x)^{\alpha+2}}|D d(x)|^2 
+    + \nu \frac{C_\alpha \alpha \varepsilon^{\alpha+2}\Delta d(x)}{d(x)^{\alpha+1}} + C_\nu \varepsilon^{\alpha+2}\\
+    &\geq \frac{C_\alpha \alpha(\alpha+1)\varepsilon^{\alpha+2}}{d(x)^{\alpha+2}}\left(\nu^p|D d(x)|^p - \nu |D d(x)|^2 + \nu \frac{d(x) \Delta d(x)}{\alpha+1}\right) + C_\nu \varepsilon^{\alpha+2}\\
     &\geq \left[C_\nu - C_3\left(\frac{1}{\delta_0}\right)^{\alpha+2}\right]\varepsilon^{\alpha+2}
@@
 \noindent
-If $p=2$, then $\alpha = 0$. We can easily see that the same calculation holds true with $\nu = 1+K_2\delta_0$ and we choose $C_\nu = \delta_0^{-2}\nu (\nu K_1+K_0K_2)$.
-\end{proof}
-
-We start with a rate of convergence when $f = C_f$ for some constant $C_f$ in $\Omega$.
+If $p=2$, then $\alpha = 0$. We can easily see that the same calculation holds true with $\nu = 1+K_2\delta_0$ and $C_\nu = \delta_0^{-2}\nu (\nu K_1^2 + K_1^2+ K_0K_2)$.
+\end{proof}
+
+Now we begin to present the rate of convergence for the special case where $f = C_f$ for some constant $C_f$ in $\Omega$.
 %\begin{thm}[Zero data]\label{thm:rate_doubling0} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
@@
 
-\begin{thm}[Constant data]\label{thm:rate_doubling0} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
-Assume $f\equiv C_f$ in $\Omega$.
+\begin{thm}[Constant data]\label{thm:rate_doubling0} Assume $f\equiv C_f$ in $\Omega$.
 Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u \equiv C_f$ be the unique solution to \eqref{eq:PDE0}.
@@
 \end{equation*}
-for $x\in \Omega$, where $\delta_{0,\Omega}$ is defined as in \eqref{def:delta_0}.
-In particular if $1<p<2$ we have $C_f\leq u^\varepsilon(x)\leq C_f + C\varepsilon$ for $x\in \Omega_\varepsilon$, but $|u^\varepsilon(x)| = \mathcal{O}\left(\varepsilon^{\alpha+1}\right)$ on each compact subset of $\Omega$.
+for $x\in \Omega$, where $\delta_{0,\Omega}$ is defined as in \eqref{def:delta_0}. In particular, if $1<p<2$ then
+\begin{equation*}
+    C_f\leq u^\varepsilon(x)\leq C_f + C\varepsilon, \qquad x\in \Omega_\varepsilon.
+\end{equation*}
+Furthermore, for all $1<p\leq 2$ there holds $|u^\varepsilon-C_f| = \mathcal{O}\left(\varepsilon^{\alpha+1}\right)$ on each compact subset of $\Omega$.
 \end{thm}
 %\textcolor{orange}{(Did you mean "In particular $0\leq  u^\varepsilon(x) \leq C\varepsilon$ for $x\in \Omega_\varepsilon$" ?)}
-\begin{proof} By Lemma \ref{lem:f=0} we have $u \equiv C_f$ in $\Omega$.
-From Lemma \ref{lem:lower-bound} and comparison principle, we have $u^\varepsilon - C_f$ is a solution to \eqref{eq:PDEeps} with data $f = 0$.
-So the conclusions follow from Lemma \ref{lem:super_refined}.
-%\begin{equation*}
-%    0\leq u^\varepsilon(x) - u(x)\leq \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} + C_\nu\varepsilon^{\alpha+2}, \qquad x\in \Omega.
-%\end{equation*}
+\begin{proof} Lemma \ref{lem:f=0} implies $u \equiv C_f$ in $\Omega$.
+And Lemma \ref{lem:lower-bound} tells us $u^\varepsilon-u=u^\varepsilon-C_f \geq 0$.By the comparison principle of \eqref{eq:PDEeps} and Lemma \ref{lem:super_refined}, the conclusion follows.
 \end{proof}
@@
 As a consequence, $x\mapsto \mathrm{dist}(x,\partial U_\kappa) = \min\big\{\mathrm{dist}(x,\partial \Omega_k),\mathrm{dist}(x,\partial \Omega)\big\}$ is twice continuously differentiable for $x\in \Omega\backslash \overline{\Omega}_{\frac{\kappa}{2}}$.
-Hence we can choose
+Hence, we can choose
 \begin{equation}\label{e:delta_kappa}
@@
 
-Next, we show the rate of convergence for compactly supported data $f$.
-
-\begin{thm}[Compactly supported data]\label{thm:rate_doubling1} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
-Assume that $f$ is Lipschitz and is compactly supported in $\Omega$.
+Next, we obtain a rate of convergence for the case where $f$ is compactly supported in $\Omega$.
+
+\begin{thm}[Compactly supported data]\label{thm:rate_doubling1} Assume that $f$ is Lipschitz and is compactly supported in $\Omega$.
 Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
-Then there exists a constant $C$ depends on the support of $f$ such that
+Then there exists a constant $C$ depending on the support of $f$ such that
 \begin{equation*}
@@
 
-\begin{proof} Without loss of generality, we can assume that $f$ is supported in $\Omega_\kappa$ where $0<\kappa < \delta_{0}$.
+\begin{proof} Without loss of generality, assume that $f$ is supported in $\Omega_\kappa$ where $0<\kappa < \delta_{0}$.
 Let $g_\kappa = u^\varepsilon$ on $\partial\Omega_{\kappa}$. Then the solution $u^\varepsilon$ of \eqref{eq:PDEeps} also solves
@@
 \end{equation*}
-in $U_\kappa= \Omega \setminus \overline{\Omega}_{\kappa} = \{x\in \Omega: 0< d(x) < \kappa\}$.
-Let $\tilde{u}^\varepsilon\in \mathrm{C}^2(U_\kappa)$ be the solution to the following problem in the annulus $U_\kappa= \Omega \setminus \overline{\Omega}_{\kappa}$ (Theorem \ref{thm:wellposed1<p<2})
+in the annulus $U_\kappa= \Omega \setminus \overline{\Omega}_{\kappa} = \{x\in \Omega: 0< d(x) < \kappa\}$.
+Let $\tilde{u}^\varepsilon\in \mathrm{C}^2(U_\kappa)$ be the solution to the following problem
 \begin{equation*}
@@
             \tilde{u}^\varepsilon(x) + |D\tilde{u}^\varepsilon(x)|^p-\varepsilon \Delta \tilde{u}^\varepsilon(x) &=0 \;\qquad \text{in } U_\kappa ,\\
-            \tilde{u}^\varepsilon(x) &= +\infty \quad \text{on } \partial U = \partial \Omega\cup \partial \Omega_{\kappa}.
+            \tilde{u}^\varepsilon(x) &= +\infty \quad \text{on } \partial U = \partial \Omega\cup \partial \Omega_{\kappa},
         \end{aligned}
@@
 \end{equation*}
-Here the boundary condition is understood as $\tilde{u}^\varepsilon(x)\to \infty$ as $d_\kappa(x)\to 0$ where $d_\kappa(\cdot)$ is the distance function from the boundary of the annulus $U_\kappa$, i.e.,
+whose existence is guaranteed by Theorem \ref{thm:wellposed1<p<2}.
+Here the boundary condition is understood in the sense that $\tilde{u}^\varepsilon(x)\to \infty$ as $d_\kappa(x)\to 0$, where $d_\kappa(\cdot)$ is the distance function from the boundary of the annulus $U_\kappa$, i.e.,
 \begin{equation*}
@@
 \end{equation*}
-Since $f = 0$ in $\overline{U}_\kappa$, by Lemma \ref{lem:f=0} $u=0$ in $\overline{U}_\kappa$. Hence it is also the unique state-constraint solution to
+Since $f = 0$ in $\overline{U}_\kappa$, by Lemma \ref{lem:f=0} $u=0$ in $\overline{U}_\kappa$. Hence, $u$ is also the unique state-constraint solution to
 \begin{equation*}
@@
     &0\leq \tilde{u}^\varepsilon(x) \leq \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d_\kappa(x)^\alpha}+C_3\left(\frac{\varepsilon}{\delta_{0,U_\kappa}}\right)^{\alpha+2}\qquad\quad\;\text{for}\;p<2,\\
-    &0\leq \tilde{u}^\varepsilon(x) \leq \nu \varepsilon \log\left(\frac{1}{d_\kappa(x)}\right)+C_\nu\left(\frac{\varepsilon}{\delta_{0,U_\kappa}}\right)^{2}\qquad\text{for}\;p=2,
+    &0\leq \tilde{u}^\varepsilon(x) \leq \nu \varepsilon \log\left(\frac{1}{d_\kappa(x)}\right)+C\left(\frac{\varepsilon}{\delta_{0,U_\kappa}}\right)^{2}\qquad\text{for}\;p=2,
 \end{split}    
@@
     &0\leq u^\varepsilon(x) \leq \tilde{u}^\varepsilon(x)  \leq \frac{\nu C_\alpha\varepsilon^{\alpha+1}}{d_\kappa(x)^{\alpha}} + C_3\left(\frac{4\varepsilon}{\kappa}\right)^{\alpha+2} \qquad\quad\;\text{for}\;p<2, \qquad \label{annulus2}\\
-    &0\leq u^\varepsilon(x)\leq \tilde{u}^\varepsilon(x) \leq \nu \varepsilon \log\left(\frac{1}{d_\kappa(x)}\right)+C_\nu\left(\frac{4\varepsilon}{\kappa}\right)^{2}\qquad\text{for}\;p=2,\label{annulus2p=2}
+    &0\leq u^\varepsilon(x)\leq \tilde{u}^\varepsilon(x) \leq \nu \varepsilon \log\left(\frac{1}{d_\kappa(x)}\right)+C\left(\frac{4\varepsilon}{\kappa}\right)^{2}\qquad\text{for}\;p=2,\label{annulus2p=2}
 \end{align}
@@
 \begin{align}\label{e:subsln}
-    &u^\varepsilon(x_\sigma) + \left|\frac{2C_0(x_\sigma - y_\sigma)}{\sigma} -  \frac{\nu C_\alpha\alpha \varepsilon^{\alpha+1} \nabla d(x_\sigma)}{d(x_\sigma)^{\alpha+1}}\right|^p - f(x_\sigma)\nonumber\\
-    &\qquad -\varepsilon\left(\frac{2nC_0}{\sigma}+ \frac{\nu C_\alpha\alpha(\alpha+1) \varepsilon^{\alpha+1}|\nabla d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+2}} - \frac{\nu C_\alpha\alpha \varepsilon^{\alpha+1}\Delta d(x_\sigma)}{d(x_\sigma)^{\alpha+1}}\right) \leq 0.
+    &u^\varepsilon(x_\sigma) + \left|\frac{2C_0(x_\sigma - y_\sigma)}{\sigma} -  \frac{\nu C_\alpha\alpha \varepsilon^{\alpha+1} D d(x_\sigma)}{d(x_\sigma)^{\alpha+1}}\right|^p - f(x_\sigma)\nonumber\\
+    &\qquad -\varepsilon\left(\frac{2nC_0}{\sigma}+ \frac{\nu C_\alpha\alpha(\alpha+1) \varepsilon^{\alpha+1}|D d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+2}} - \frac{\nu C_\alpha\alpha \varepsilon^{\alpha+1}\Delta d(x_\sigma)}{d(x_\sigma)^{\alpha+1}}\right) \leq 0.
 \end{align}
@@
 \begin{equation*}
-    \xi_\sigma := \frac{2C_0(x_\sigma - y_\sigma)}{\sigma} \qquad\text{and}\qquad \zeta_\sigma :=- \frac{\nu C_\alpha\alpha \varepsilon^{\alpha+1} \nabla d(x_\sigma)}{d(x_\sigma)^{\alpha+1}}.
+    \xi_\sigma := \frac{2C_0(x_\sigma - y_\sigma)}{\sigma} \qquad\text{and}\qquad \zeta_\sigma :=- \frac{\nu C_\alpha\alpha \varepsilon^{\alpha+1} D d(x_\sigma)}{d(x_\sigma)^{\alpha+1}}.
 \end{equation*}
@@
 \end{equation*}
-where $C$ is independent of $\kappa$ and $\varepsilon$. Choosing $\sigma = \sqrt{\varepsilon}$, we obtain that (with $\kappa$ being fixed)
+where $C$ is independent of $\kappa$ and $\varepsilon$. Choosing $\sigma = \sqrt{\varepsilon}$, we obtain that (with $\kappa$ fixed)
 \begin{equation}\label{e:final1}
@@
 since $z\in \partial\Omega_k = \{x \in \Omega: d(x) = \kappa\}$.
-Thus, we have $|x_\sigma - z| \geq \kappa - d(x_\sigma) > \frac{1}{2}\kappa$ for all $z\in \partial\Omega_k$, which implies that $\mathrm{dist}(x_\sigma,\partial\Omega_k)>\frac{1}{2}\kappa$ and therefore $d_\kappa(x_\sigma) = d(x_\sigma)$.
+Thus, $|x_\sigma - z| \geq \kappa - d(x_\sigma) > \frac{1}{2}\kappa$ for all $z\in \partial\Omega_k$, which implies that $\mathrm{dist}(x_\sigma,\partial\Omega_k)>\frac{1}{2}\kappa$ and therefore $d_\kappa(x_\sigma) = d(x_\sigma)$.
 By \eqref{annulus2} and the fact that $u \geq 0$, we have
@@
 \begin{align}\label{e:subslnp=2}
-    u^\varepsilon(x_\sigma)&+ \left|\frac{2C_0(x_\sigma - y_\sigma)}{\sigma} - \theta \varepsilon \frac{\nabla d(x_\sigma)}{d(x_\sigma)}\right|^2  -f(x_\sigma) \nonumber\\
-    &- 2nC_0\left(\frac{\varepsilon}{\sigma}\right) - \theta |\nabla d(x_\sigma)|^2 \left(\frac{\varepsilon}{d(x_\sigma)}\right)^2  + \theta \Delta d(x_\sigma)\left(\frac{\varepsilon^2}{d(x_\sigma)}\right) \leq 0.
+    u^\varepsilon(x_\sigma)&+ \left|\frac{2C_0(x_\sigma - y_\sigma)}{\sigma} - \theta \varepsilon \frac{D d(x_\sigma)}{d(x_\sigma)}\right|^2  -f(x_\sigma) \nonumber\\
+    &- 2nC_0\left(\frac{\varepsilon}{\sigma}\right) - \theta |D d(x_\sigma)|^2 \left(\frac{\varepsilon}{d(x_\sigma)}\right)^2  + \theta \Delta d(x_\sigma)\left(\frac{\varepsilon^2}{d(x_\sigma)}\right) \leq 0.
 \end{align}
@@
 \begin{align*}
-    u^\varepsilon(x_\sigma) - u(y_\sigma) &\leq \left(4C_0+ \theta\varepsilon\frac{\nabla d(x_\sigma)}{d(x_\sigma)}\right)\left(\theta \varepsilon \frac{ \nabla d(x_\sigma)}{d(x_\sigma)}\right) \\
-    &+ C\sigma + 2nC_0 \left(\frac{\varepsilon}{\sigma}\right)+ \theta |\nabla d(x_\sigma)|^2 \left(\frac{\varepsilon}{d(x_\sigma)}\right)^2 + \theta|\Delta d(x_\sigma)| \frac{\varepsilon^2}{d(x_\sigma)}.
+    u^\varepsilon(x_\sigma) - u(y_\sigma) &\leq \left(4C_0+ \theta\varepsilon\frac{D d(x_\sigma)}{d(x_\sigma)}\right)\left(\theta \varepsilon \frac{ D d(x_\sigma)}{d(x_\sigma)}\right) \\
+    &+ C\sigma + 2nC_0 \left(\frac{\varepsilon}{\sigma}\right)+ \theta |D d(x_\sigma)|^2 \left(\frac{\varepsilon}{d(x_\sigma)}\right)^2 + \theta|\Delta d(x_\sigma)| \frac{\varepsilon^2}{d(x_\sigma)}.
 \end{align*}
@@
 
-\begin{rem} For general data Lipschitz $f\in \mathrm{C}(\overline{\Omega})$, it is natural to think about using cutoff function argument.
+\begin{rem} For general Lipschitz data $f\in \mathrm{C}(\overline{\Omega})$, it is natural to think about using cutoff function argument.
 Let $\chi_{{\kappa}}\in \mathrm{C}_c^\infty(\Omega)$ such that $0\leq \chi_{\kappa}\leq 1$, $\chi_\kappa = 1$ in $\Omega_{2\kappa}$ and $\mathrm{supp}\;\chi_\kappa\subset\Omega_\kappa$.
-Let $u^\varepsilon_\kappa\in \rmC^2(\Omega)\cap\overline{\Omega}$ solves \eqref{eq:PDEeps} with datum $f\chi_{\kappa}$.
+Let $u^\varepsilon_\kappa\in \rmC^2(\Omega)\cap\rmC(\overline{\Omega})$ solves \eqref{eq:PDEeps} with datum $f\chi_{\kappa}$.
 Then as $u^\varepsilon_\kappa\to u^\varepsilon$ as $\kappa\to 0$ (since $f\chi_\kappa\to f$ in the weak$^*$ topology of $L^\infty(\Omega)$, we have a continuity of solution with respect to data in this topology \cite[Remark II.1]{Lasry1989}).
@@
 
-\begin{thm}[Zero boundary data]\label{thm:rate_doubling2} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
-Assume that $f$ is Lipschitz such that $f = 0$ on $\partial\Omega$.
-Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
-Then there exists a constant $C$ such that
-\begin{equation*}
-|u^\varepsilon(x) - u(x)| \leq C\sqrt{\varepsilon} \quad  \text{for} \quad x\in \Omega_{\varepsilon}.
-\end{equation*}
-\end{thm}
-
-\begin{proof} Let $L = \Vert \nabla f\Vert_{L^\infty(\Omega)}$ be the Lipschitz constant of $f$.
+We prove the rate of convergence for the case $f=0$ on $\partial \Omega$.
+
+\begin{proof}[Proof of Theorem \ref{main_thm1}] Let $L = \Vert D f\Vert_{L^\infty(\Omega)}$ be the Lipschitz constant of $f$.
 For $\kappa>0$ small such that $0<\kappa<\delta_0$ and $x\in \Omega\backslash \Omega_\kappa$, let $x_0$ be the projection of $x$ onto $\partial\Omega$.
@@
     \centering
-    \includegraphics[scale=0.35]{Drafts and notes/fig1.png}
+    \includegraphics[scale=0.40]{Drafts and notes/fig1.png}
     \caption{Graph of the function $f_\kappa$.}
@@
 \end{equation*}
-Let $u^\varepsilon_\kappa\in \rmC^2(\Omega)\cap\overline{\Omega}$ be the solution to \eqref{eq:PDEeps} with datum $f\chi_{\kappa}$ and $u_k\in \mathrm{C}(\overline{\Omega})$ be the corresponding solution to \eqref{eq:PDE0} with datum $f{\chi_\kappa}$.
+Let $u^\varepsilon_\kappa\in \rmC^2(\Omega)\cap\rmC(\overline{\Omega})$ be the solution to \eqref{eq:PDEeps} with datum $f\chi_{\kappa}$ and $u_k\in \mathrm{C}(\overline{\Omega})$ be the corresponding solution to \eqref{eq:PDE0} with datum $f{\chi_\kappa}$.
 By comparison principle (\cite[Corollary II.1]{Lasry1989}) we have
@@
 
-\subsection{A generalization to some unbounded data} The approach we use allow us to apply to the situation where the data $f_\varepsilon$ blows up with some certain rates near the boundary such that $f_\varepsilon\to f$ in $L^1(\Omega)$.
-To simplify the presentation, we will assume $f\in \mathrm{C}^1(\Omega)$ and $f$ is bounded from below satisfying
-\begin{equation*}
-    f(x) = g(x) + \frac{\gamma \varepsilon^{\alpha+2}}{d(x)^{\alpha+2}}
-\end{equation*}
-where $g\in \mathrm{C}^1(\overline{\Omega})$with $g = 0$ on $\partial\Omega$ and $g\geq 0$ in $\Omega$.
-
-%\begin{thm}[General bounded Lipschitz data]\label{thm:rate_doubling1} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
+\subsection{An improved one-sided rate of convergence}
+We still assume $f = 0$ on $\partial\Omega$ and $f\geq 0$ such that $f\in \rmC^2(\overline{\Omega})$. From Lemma \ref{lem:f=0} we have $u = 0$ on $\partial\Omega$. Extent $u$ to $\R^n$ by setting 
+\begin{equation*}
+    \tilde{u}(x) = \begin{cases}
+      u(x) &\qquad\text{if}\;x\in \overline{\Omega},\\
+      0 &\qquad\text{if}\;x\notin \overline{\Omega}.
+    \end{cases}
+\end{equation*}
+
+\begin{lem} If $f = 0$ on $\partial\Omega$ then the extension $\tilde{u}$ is a viscosity solution to
+\begin{equation*}
+    \tilde{u}(x)+|D\tilde{u}(x)|^p - f(x) = 0 \qquad\text{in}\;\R^n.
+\end{equation*}
+As a consequence (Theorem \ref{convex}) $-D^2\tilde{u} \succ -c\;\mathbb{I}_n$ in $\R^n$ if $f\in \mathrm{C}_c^2(\R^n)$ and 
+\begin{equation}\label{def_c}
+    c = \max \big\lbrace  D_{\xi\xi}f(x): |\xi|=1, x\in \overline{\Omega} \big\rbrace\geq 0.
+\end{equation}
+\end{lem}
+\begin{proof} We only need to check that the viscosity solution test hold for $\tilde{u}$ as $x\in \partial\Omega$.
+The supersolution test holds trivially since $f = \tilde{u} = 0$ on $\partial\Omega$.
+If $\varphi\in \mathrm{C}^1(\R^n)$ such that $\tilde{u} - \varphi$ has a local maximum at $x\in \partial\Omega$, then $\tilde{u}(y) - \tilde{u}(y) \leq - \tilde{u}(x)$ for all $y\in \R^n$.
+Since $u\geq 0$, we deduce that $\varphi$ has a local minimum at $x\in \partial\Omega$, therefore $\tilde{u}(x)+|D\varphi(x)|^p - f(x) = 0$ and thus the viscosity subsolution test is satisfied.
+\end{proof}
+
+\begin{thm}[Compactly supported data]\label{thm:rate_doubling2} Assume that $f\in \mathrm{C}^2_c(\Omega)$ such that $\mathrm{supp}(f)\subset\Omega_\kappa$ where $0<\kappa < \delta_{0}$.
 Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
-Then there exists a constant $C$ such that
-%\begin{equation*}
-%|u^\varepsilon(x) - u(x)| \leq C\sqrt{\varepsilon} \quad  \text{for} \quad x\in \Omega_{\varepsilon}.
-%\end{equation*}
-%\end{thm}
-
-%\begin{proof} Let $\kappa \in (0,1)$ and $\chi_{\kappa}\in \mathrm{C}_c^\infty(\mathbb{R}^n)$ such that $0\leq \chi_\kappa \leq 1$, $\chi = 1$ in $\Omega_{2\kappa}$ and $\mathrm{supp}(\chi_\kappa)\subset \Omega_\kappa$ and
-%\begin{equation*}
-%    \max_{x\in \overline{\Omega}}|\nabla \chi_\kappa(x)| \leq \frac{C}{\kappa} .
-%\end{equation*}
-%Denote $f_\kappa(x) = f(x)\chi_\kappa(x)$ for $x\in \overline{\Omega}$. It is clear that 
-%\begin{equation*}
-%    \mathrm{Lip}(f_\kappa)\leq \frac{C \max  f}{\kappa} + \mathrm{Lip}(f).
-%\end{equation*}
-%Applying Theorem \ref{thm:rate_doubling1} for
-
-%\end{proof}
-
-%\nocite{*}
+Then there exists a constant $C$ independent of $\varepsilon$ and $\kappa$ such that
+\begin{equation*}
+\begin{aligned}
+    u^\varepsilon(x) - u(x) &\leq\frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} + CC_\frac{\kappa}{2} \left(\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1}+\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2}\right) + nc\varepsilon, \quad \text{if} \quad 1 < p <2, \\
+    u^\varepsilon(x) - u(x) & \leq \nu \varepsilon \log\left( \frac{1}{d(x)}\right)+C C_\frac{\kappa}{2}\left(\frac{\varepsilon}{\kappa}\right) +C\left( \frac{\varepsilon}{\kappa}\right)^2 + nc \varepsilon, \quad \text{if} \quad p=2,
+\end{aligned}
+\end{equation*}
+where $c$ is defined as in \eqref{def_c} and $C_\frac{\kappa}{2}$ is the gradient bound of $u^\varepsilon$ on $\overline{\Omega}_\frac{\kappa}{2}$ as in \eqref{e:priorie_eps}.
+\end{thm}
+
+\begin{proof} For $1<p<2$, we proceed as in the proof of Theorem \ref{thm:rate_doubling1} to obtain 
+\begin{align}
+    &0\leq u^\varepsilon(x) \leq \tilde{u}^\varepsilon(x)  \leq \frac{\nu C_\alpha\varepsilon^{\alpha+1}}{d_\kappa(x)^{\alpha}} + C_3\left(\frac{4\varepsilon}{\kappa}\right)^{\alpha+2} \label{annulus2a}
+    %&0\leq u^\varepsilon(x)\leq \tilde{u}^\varepsilon(x) \leq \nu \varepsilon \log\left(\frac{1}{d_\kappa(x)}\right)+C_\nu\left(\frac{4\varepsilon}{\kappa}\right)^{2}\qquad\text{for}\;p=2,\label{annulus2p=2a}
+\end{align}
+for $x\in U_\kappa$. Let
+\begin{equation*}
+    \psi^\varepsilon(x) := u^\varepsilon(x) - \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha}, \qquad x\in \Omega
+\end{equation*}
+where $\nu > 1$ is chosen as in Lemma \ref{lem:super_refined}.
+It is clear that $u-\psi^\varepsilon$ has a local minimum at some point $x_0\in \Omega$ since $\psi^\varepsilon(x)\to -\infty$ as $x\to \partial\Omega$.
+The normal derivative test gives us
+\begin{equation*}
+    D\psi^\varepsilon(x_0) = Du^\varepsilon(x_0) + \nu C_\alpha\alpha \left(\frac{\varepsilon}{d(x_0)}\right)^{\alpha+1} D d(x_0) \in D^-u(x_0).
+\end{equation*}
+There are two cases to consider:
+\begin{itemize}
+    \item If $\displaystyle d(x_0)< \frac{1}{2}\kappa$, then as in the proof of Theorem \ref{thm:rate_doubling1}, $x_0\in U_\kappa$ and $d_\kappa(x_0) = d(x_0)$.
+By the definition of $x_0$, for any $x\in \Omega$, there holds
+    \begin{align*}
+        u(x) - \left(u^\varepsilon(x) - \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha}\right) \geq u(x_0) - \left(u^\varepsilon(x_0) - \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x_0)^\alpha}\right).
+    \end{align*}
+    Therefore,
+    \begin{equation*}
+    \begin{split}
+        u^\varepsilon(x) - u(x) - \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} &\leq  \left(u^\varepsilon(x_0) - \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x_0)^\alpha}\right) - u(x_0) \leq C_3 \left(\frac{4\varepsilon}{\kappa}\right)^{\alpha+2}
+    \end{split}
+    \end{equation*}
+    thanks to \eqref{annulus2a}. Thus, in this case
+    \begin{equation*}
+        u^\varepsilon(x) - u(x) \leq \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} + C_3 \left(\frac{4\varepsilon}{\kappa}\right)^{\alpha+2}, \qquad x\in \Omega.
+    \end{equation*}
+    \item If $\displaystyle d(x_0) \geq \frac{1}{2}\kappa$, from the fact that $u$ is semiconcave in $\Omega$, 
+\begin{equation*}
+    D^2\psi^\varepsilon(x_0) \prec c\;\mathbb{I}_n
+\end{equation*}
+which implies that
+\begin{equation*}
+    \Delta \psi^\varepsilon(x_0) \leq nc.
+\end{equation*}
+In other words, we have
+\begin{equation*}
+    \varepsilon\Delta u^\varepsilon (x_0) - \frac{\nu C_\alpha \alpha(\alpha+1)\varepsilon^{\alpha+2}}{d(x_0)^{\alpha+2}}| Dd(x_0)|^2 + \frac{\nu C_\alpha \alpha \varepsilon^{\alpha+2}}{d(x_0)^{\alpha+1}}\Delta d(x_0) \leq nc\varepsilon.
+\end{equation*}
+Since $d(x_0)\geq \frac{1}{2}\kappa$, we can further deduce that
+\begin{equation}\label{delta_psi}
+    \varepsilon\Delta u^\varepsilon(x_0) \leq nc\varepsilon + \frac{C\varepsilon^{\alpha+2}}{d(x_0)^{\alpha+2}} \leq nc\varepsilon +  C\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2}
+\end{equation}
+where $C$ is independent of $\varepsilon$. Since $\psi^\varepsilon\in \rmC^2(\Omega)$, the viscosity supersolution test for $u$ gives us
+\begin{equation}\label{convex1}
+    u(x_0) + \left|Du^\varepsilon(x_0) + \frac{\nu C_\alpha \alpha \varepsilon^{\alpha+1}}{d(x_0)^{\alpha+1}}D d(x_0)\right|^p - f(x_0) \geq 0.
+\end{equation}
+On the other hand, $u^\varepsilon$ solves
+\begin{equation}\label{convex2}
+    u^\varepsilon(x_0) + |Du^\varepsilon(x_0)|^p - f(x_0) - \varepsilon \Delta u^\varepsilon(x_0) = 0.
+\end{equation}
+Combine \eqref{convex1} and \eqref{convex2} to obtain that
+\begin{align}\label{convex3}
+    u^\varepsilon(x_0) - u(x_0) &\leq \left|Du^\varepsilon(x_0) + \frac{\nu C_\alpha \alpha \varepsilon^{\alpha+1}}{d(x_0)^{\alpha+1}}D d(x_0)\right|^p - |Du^\varepsilon(x_0)|^p + \varepsilon\Delta u^\varepsilon(x_0).
+\end{align}
+Now we estimate the gradient terms on the right hand side of \eqref{convex3}, i.e., 
+\begin{align}\label{convex4}
+    &\left|Du^\varepsilon(x_0) + \frac{\nu C_\alpha \alpha \varepsilon^{\alpha+1}}{d(x_0)^{\alpha+1}}D d(x_0)\right|^p - |Du^\varepsilon(x_0)|^p\nonumber \\
+    &\qquad \qquad \leq p\left(|Du^\varepsilon(x_0)| + \frac{\nu C_\alpha \alpha \varepsilon^{\alpha+1}}{d(x_0)^{\alpha+1}}\left|D d(x_0)\right|\right)^{p-1} \frac{\nu C_\alpha \alpha \varepsilon^{\alpha+1}}{d(x_0)^{\alpha+1}}|D d(x_0)|\nonumber\\
+    &\qquad \qquad \leq p\left(C_\frac{\kappa}{2} + C\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1}\right)^{p-1} C\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1}\nonumber\\
+    &\qquad\qquad\leq CC_\frac{\kappa}{2}\left(1+\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1}\right)^{p-1} \left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1} \leq CC_\frac{\kappa}{2} \left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1}\left(1+ \left(\frac{\varepsilon}{\kappa}\right)\right)
+\end{align}
+where $C_\frac{\kappa}{2}$ is the upper bound of $Du^\varepsilon$ in $\Omega_\frac{\kappa}{2}$, as is given in the a priori estimate (Theorem \ref{thm:grad_1}) and $C$ is a constant that depends only on $\nu$, $\alpha$, and bounds on $d,Dd$ and $\Delta d$.
+Using \eqref{delta_psi} and \eqref{convex4} in \eqref{convex3}, we get
+\begin{equation*}
+    u^\varepsilon(x_0) - u(x_0) \leq nc\varepsilon + CC_\frac{\kappa}{2} \left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1}\left(1+ \left(\frac{\varepsilon}{\kappa}\right)\right) + C\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2}.
+\end{equation*}
+%\textcolor{orange}{(I feel you missed some terms when estimating $\epsilon \Delta u^\epsilon$, because $\Delta \psi \neq \Delta u^\epsilon$. But it won't affect the result.)}
+
+Therefore, in this case 
+\begin{equation*}
+    u^\varepsilon(x) - u(x) \leq \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} + CC_\frac{\kappa}{2} \left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1}\left(1+ \left(\frac{\varepsilon}{\kappa}\right)\right) + nc\varepsilon, \qquad x\in \Omega.
+\end{equation*}
+\end{itemize}
+From the two cases, the conclusion follows.
+
+For $p = 2$, the argument is similar.
+We take $\psi^\varepsilon(x):=u^\varepsilon(x)-\nu \varepsilon \log \left(\frac{1}{d(x)}\right)$ instead and still $u-\psi^\varepsilon$ attains a local minimum at some point $x_0 \in \Omega$.
+Carrying out the similar computations as in the case of $1 < p < 2$, we have:
+\begin{itemize}
+    \item If $\displaystyle d(x_0) < \frac{1}{2} \kappa$, then
+    \begin{equation*}
+        u^\varepsilon(x)-u(x) \leq \nu \varepsilon \log \left( \frac{1}{d(x)} \right) + C\left( \frac{4\varepsilon}{\kappa}\right)^2, \quad x \in \Omega.
+    \end{equation*}
+    \item If $\displaystyle d(x_0) \geq \frac{1}{2} \kappa$, then
+    \begin{equation*}
+        u^\varepsilon(x)-u(x) \leq \nu \varepsilon \log\left(\frac{1}{d(x)}\right) + 
+        C C_\frac{\kappa}{2} \left( \frac{\varepsilon}{\kappa} \right) + C \left( \frac{\varepsilon}{\kappa} \right)^2 + nc\varepsilon, \quad x \in \Omega.
+    \end{equation*}
+\end{itemize}
+Therefore, the conclusion follows.
+\end{proof}
+
+\begin{rem} Using our approach, in order to relax the assumption $\mathrm{supp}(f)\subset\subset\Omega$ to $f = 0$ on $\partial\Omega$ as in Theorem \ref{main_thm1}, we need to know more about the blow up rate $C_\kappa$ in $|Du^\varepsilon(x)|\leq C_\kappa$ as $\kappa\to 0$.
+We will use the result in
+
+\end{rem}
+
+\begin{cor} Assume $f = 0$ on $\partial\Omega$.
+Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
+Let $K$ be a compact subset of $\Omega$, then there exists a constant $C_K$ such that
+\begin{equation*}
+    \sup_{x\in K} \big(u^\varepsilon(x) -u(x)\big) \leq C_K\varepsilon.
+\end{equation*}
+\end{cor}
+\begin{proof} We can find $\kappa\in \left(0,\delta_0\right)$ such that $K\subset\subset \Omega_{\kappa}$.
+Define $f_\kappa$ as in the proof of Theorem \ref{main_thm1}, where $\mathrm{supp}(f_\kappa)\subset\Omega_{\frac{\kappa}{2}}$ and
+\begin{equation*}
+    0\leq f - f_\kappa \leq L\kappa
+\end{equation*}
+where $L$ is the Lipschitz constant of $f$.
+Let $u^\varepsilon_\kappa\in \rmC^2(\Omega)\cap \rmC(\overline{\Omega})$ be the solution to \eqref{eq:PDEeps} with datum $f_k$ and $u_k$ be the solution to \eqref{eq:PDE0} with datum $f_k$, then
+\begin{equation*}
+  0\leq u^\varepsilon(x) - u^\varepsilon_\kappa(x)\leq L\kappa \qquad\text{for}\;x\in \Omega
+\end{equation*}
+and
+\begin{equation*}
+    0\leq u(x) - u_\kappa(x)\leq L\kappa \qquad\text{for}\;x\in \Omega.
+\end{equation*}
+Therefore
+\begin{equation*}
+    u^\varepsilon(x)-u(x)\leq 2L\kappa + \big(u^\varepsilon_\kappa - u_\kappa\big) \leq 2L\kappa+C_{\kappa}\varepsilon
+\end{equation*}
+where we use the rate $\mathcal{O}(\varepsilon)$ from Theorem \ref{thm:rate_doubling2} as $f_\kappa$ is compactly supported. 
+\end{proof}
+
+\begin{rem} It is clear from the proof that $C_K$ blows up as $K$ approaching $\Omega$ and we do not have any boundary layer yet, since the bound $|Du^\varepsilon(x)|\leq C_\kappa$ for $x\in \Omega_\kappa$ is not an explicit bound.
+We refer the readers to \cite{alessio_asymptotic_2006} for an explicit behavior of $Du^\varepsilon(x)$ as $x\to \partial \Omega$.
+Of course, using this explicit behavior of $Du^\varepsilon$ we can obtain a boundary layer from this proof, which we omit it here.
+\end{rem}
+
+\begin{proof}[Proof of Theorem \ref{main_thm2}] Define
+
+\end{proof}
 
@@
 
-\begin{appendices}
-\section{Proofs of some preliminary results}
-\begin{proof}[Proof of Theorem \ref{thm:grad_1}] Let $\theta\in (0,1)$ be chosen later, $\varphi\in \mathrm{C}_c^\infty(\Omega)$, $0\leq \varphi\leq 1$, $\mathrm{supp}\;\varphi\subset \Omega$ and $\varphi = 1$ on $\Omega_\delta$ such that
+%\begin{appendices}
+\section*{Appendix}
+\subsection*{Estimates on solutions}
+We present here a proof for the gradient bound of solution to \eqref{eq:PDEeps} using the Bernstein method (see also \cite{Lasry1989,lions_quelques_1985}).
+Another proof using a different technique is given in \cite{Armstrong2015a}.
+
+\begin{proof}[Proof of Theorem \ref{thm:grad_1}] Let $\theta\in (0,1)$ be chosen later, $\varphi\in \mathrm{C}_c^\infty(\Omega)$, $0\leq \varphi\leq 1$, $\mathrm{supp}\;\varphi\subset \Omega$ and $\varphi = 1$ on $\Omega_\delta$ such that there exists $C = C(\delta,\theta)$,
 \begin{equation}\label{e:ass_power}
-    |\Delta \varphi(x)| \leq C|\varphi(x)|^\theta \qquad\text{and}\qquad |D \varphi(x)|^2 \leq C\varphi^{1+\theta}
-\end{equation}
-for $x\in \Omega$ and $C = C(\delta,\theta)$.
-Let $w(x) = |Du(x)|^2$ for $x\in \Omega$. The goal is to derive an equation for $\varphi w$. The equation for $w$ is given by
-\begin{equation*}
-    -\varepsilon \Delta w + p|D u|^{p-2}D u \cdot D w + 2  w - D f\cdot D u + \varepsilon |D^2u|^2 = 0 \qquad\text{in}\;\Omega.
-\end{equation*}
-Using that, we can derive an equation for $(\varphi w)$ as follows.
+    |\Delta \varphi(x)| \leq C\varphi^\theta \qquad\text{and}\qquad |D \varphi(x)|^2 \leq C\varphi^{1+\theta}
+\end{equation}
+for all $x\in \Omega$.
+Define $w(x) := |Du(x)|^2$ for $x \in \Omega$. The equation for $w$ is given by
+\begin{equation*}
+    -\varepsilon \Delta w + 2 p|D u|^{p-2}D u \cdot D w + 2  w - 2 D f\cdot D u + 2 \varepsilon |D^2u|^2 = 0 \qquad\text{in}\;\Omega.
+\end{equation*}
+%\textcolor{orange}{(I think the coefficients here are not correct. I put the corrected ones in orange. Originally, all the coefficients were 1 except for the term 2w.)}
+
+Then an equation for $(\varphi w)$ can be derived as follows.
 \begin{align*}
-    &-\varepsilon \Delta (\varphi w) + p|D u|^{p-2}D u \cdot D (\varphi w) + 2  (\varphi w) + \varepsilon \varphi|D^2u|^2 + 2\varepsilon \frac{D \varphi}{\varphi}\cdot D (\varphi w) \\
-    &\qquad\qquad\qquad\qquad = \varphi(D f\cdot D u) + p|D u|^{p-2}(D u\cdot D \varphi)w -\varepsilon w \Delta \varphi + 2\varepsilon \frac{|D \varphi|^2}{\varphi}w
+    &-\varepsilon \Delta (\varphi w) + 2 p|D u|^{p-2}D u \cdot D (\varphi w) + 2  (\varphi w) + 2 \varepsilon \varphi|D^2u|^2 + 2\varepsilon \frac{D \varphi}{\varphi}\cdot D (\varphi w) \\
+    &\qquad\qquad\qquad\qquad = \varphi(D f\cdot D u) + 2 p|D u|^{p-2}(D u\cdot D \varphi)w -\varepsilon w \Delta \varphi + 2\varepsilon \frac{|D \varphi|^2}{\varphi}w
     \qquad\text{in}\;\mathrm{supp}\;\varphi.
@@
 Assume that $\varphi w$ achieves its maximum over $\overline{\Omega}$ at $x_0\in \Omega$.
-Then we can further assume that $x_0\in \mathrm{supp}\;\varphi$, since otherwise the maximum of $\varphi w$ over $\overline{\Omega}$ is zero.
-By the classical maximum principle
+And we can further assume that $x_0\in \mathrm{supp}\;\varphi$, since otherwise the maximum of $\varphi w$ over $\overline{\Omega}$ is zero.
+By the classical maximum principle,
 \begin{equation*}
@@
 \end{equation*}
-Using that in the equation of $\varphi w$ above, we obtain that
-\begin{equation*}
-    \varepsilon \varphi|D^2u|^2 \leq  \varphi (Df\cdot Du)+ p|Du|^{p-1} |D\varphi|w + \varepsilon w |\Delta\varphi|  + 2\varepsilon  w\frac{|D\varphi|^2}{\varphi},
-\end{equation*}
- where all terms are evaluated at $x_0$. Using \eqref{e:ass_power} we have
+Use this in the equation of $\varphi w$ above to obtain
+\begin{equation*}
+    \varepsilon \varphi|D^2u|^2 \leq  \varphi (Df\cdot Du)+ 2 p|Du|^{p-1} |D\varphi|w + \varepsilon w |\Delta\varphi|  + 2\varepsilon  w\frac{|D\varphi|^2}{\varphi},
+\end{equation*}
+ where all terms are evaluated at $x_0$. From \eqref{e:ass_power}, we have
 \begin{equation}\label{e:est_for_D^2u}
-    \varepsilon \varphi|D^2u|^2 \leq  \varphi |Df|w^{\frac{1}{2}}+ Cp w^{\frac{p-1}{2}+1} \varphi^{\frac{1+\theta}{2}} + C\varepsilon w \varphi^{\theta} + 2C\varepsilon  w\varphi^\theta.
-\end{equation}
-By Cauchy-Schwartz inquality, we have $n|D^2u|^2\geq (\Delta u)^2$, thus if $n\varepsilon < 1$ then
+    \varepsilon \varphi|D^2u|^2 \leq  \varphi |Df|w^{\frac{1}{2}}+ 2 Cp w^{\frac{p-1}{2}+1} \varphi^{\frac{1+\theta}{2}} + C\varepsilon w \varphi^{\theta} + 2C\varepsilon  w\varphi^\theta.
+\end{equation}
+By Cauchy-Schwartz inquality, $n|D^2u|^2\geq (\Delta u)^2$. Thus, if $n\varepsilon < 1$, then
 \begin{equation}\label{e:est_for_D^2u_2}
-    \varepsilon |D^2u|^2 \geq \frac{(\varepsilon \Delta u)^2}{n\varepsilon} \geq (\varepsilon \Delta u)^2 = \left(  u + |Du|^p - f\right)^2 \geq |Du|^{2p} - 2C_0|Du|^p \geq \frac{|Du|^{2p}}{2} - 2K_0.
-\end{equation}
-Using \eqref{e:est_for_D^2u_2} in \eqref{e:est_for_D^2u} we obtain that
-\begin{equation*}
-    \varphi\left(\frac{1}{2}w^p - 2K_0\right) \leq \varphi |Df|w^{\frac{1}{2}}+ Cp w^{\frac{p-1}{2}+1} \varphi^{\frac{1+\theta}{2}} + 3C\varepsilon w \varphi^{\theta}.
-\end{equation*}
-Multiplying both sides by $\varphi^{p-1}$, we deduce that
+    \varepsilon |D^2u|^2 \geq \frac{(\varepsilon \Delta u)^2}{n\varepsilon} \geq (\varepsilon \Delta u)^2 = \left(  u + |Du|^p - f\right)^2 \geq |Du|^{2p} - 2C|Du|^p \geq \frac{|Du|^{2p}}{2} - 2C
+\end{equation}
+where $C$ depends on $\max_{\overline{\Omega}}f$ only. Using \eqref{e:est_for_D^2u_2} in \eqref{e:est_for_D^2u}, we obtain that
+\begin{equation*}
+    \varphi\left(\frac{1}{2}w^p - 2C\right) \leq \varphi |Df|w^{\frac{1}{2}}+ 2 Cp w^{\frac{p-1}{2}+1} \varphi^{\frac{1+\theta}{2}} + 3C\varepsilon w \varphi^{\theta}.
+\end{equation*}
+Multiply both sides by $\varphi^{p-1}$ to deduce that
 \begin{align*}
-    (\varphi w)^p \leq 4K_0\varphi^{p-1} + 2\Vert Df\Vert_{L^\infty}\varphi^p w^{\frac{1}{2}} + 2Cp \varphi^{\frac{2p+\theta - 1}{2}}w^{\frac{p+1}{2}} + 6C\varepsilon \varphi^{p+\theta - 1}w.
+    (\varphi w)^p \leq 4C\varphi^{p-1} + 2\Vert Df\Vert_{L^\infty}\varphi^p w^{\frac{1}{2}} + 4Cp \varphi^{\frac{2p+\theta - 1}{2}}w^{\frac{p+1}{2}} + 6C\varepsilon \varphi^{p+\theta - 1}w.
 \end{align*}
-Choose $2p+\theta -1 \geq p+1$, i.e., $p+\theta\geq 2$. This is always possible with the requirement $\theta \in (0,1)$, as $1<p <\infty$. We deduce that 
+Choose $2p+\theta -1 \geq p+1$, i.e., $p+\theta\geq 2$. This is always possible with the requirement $\theta \in (0,1)$, as $1<p <\infty$. Then we get
 \begin{equation}\label{e:est_for_D^2u_3}
-    (\varphi w)^p \leq C\left(1+ (\varphi w)^\frac{1}{2} + (\varphi w)^\frac{p+1}{2} +(\varphi w)\right)
-\end{equation}
-As a polynomial in $z = (\varphi w)(x_0)$, this implies that $(\varphi w)(x_0)\leq C$ where $C$ depends on coefficients of the right hand side of \eqref{e:est_for_D^2u_3}, which implies our desired gradient bound since $\overline{\Omega}_\delta\subset \mathrm{supp}\;\varphi$.
-\end{proof}
-
+    (\varphi w)^p \leq C\left(1+ (\varphi w)^\frac{1}{2} + (\varphi w)^\frac{p+1}{2} +(\varphi w)\right).
+\end{equation}
+As a polynomial in $z = (\varphi w)(x_0)$, this implies that $(\varphi w)(x_0)\leq C$ where $C$ depends on coefficients of the right hand side of \eqref{e:est_for_D^2u_3}, which gives our desired gradient bound since $\overline{\Omega}_\delta\subset \mathrm{supp}\;\varphi$.
+\end{proof}
+
+\subsection*{Asymptotic behavior of derivatives}
+We denote by $\nu(x)$ the outward unit normal vector at any point $x\in \partial{\Omega}$ and $\tau(x)$ the unitary tangent vector defined on $\partial{\Omega}$, i.e., $\nu(x)\cdot\tau(x) = 0$.
+We start by considering the case $p=2$.
+\begin{equation*}
+    \begin{cases}
+    -\Delta u 
+    \end{cases}
+\end{equation*}
+
+\subsection*{Existence and wellposedness of solution}
 \begin{proof} [Proof of Theorem \ref{thm:wellposed1<p<2}] If $p\in (1,2)$, we use the ansatz $ u(x) = C_\varepsilon d(x)^{-\alpha}$ to find a solution for \eqref{eq:PDEeps}.
-Plugging it into \eqref{eq:PDEeps}, we obtain that
+Plug the ansatz into \eqref{eq:PDEeps} and compute
 \begin{equation*}
@@
 \end{equation*}
-Since $|D d(x)| = 1$ for $x$ near $\partial\Omega$, as $x\to \partial \Omega$, the highest explosive order terms are
+Since $|D d(x)| = 1$ for $x$ near $\partial\Omega$, as $x\to \partial \Omega$, the explosive terms of the highest order are
 \begin{equation*}
@@
 \end{equation*}
-Setting the above to be zero, we deduce that 
+Set the above to be zero to obtain that
 \begin{equation}\label{e:relation}
@@
 \begin{split}
-    \overline{w}_{\eta,\delta}(x) &= \frac{(C_\alpha+\eta)\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + M_\eta, \qquad x\in \Omega_\delta,\\
-    \underline{w}_{\eta,\delta}(x) &= \frac{(C_\alpha-\eta)\varepsilon^{\alpha+1}}{(d(x)+\delta)^\alpha} - M_\eta, \qquad x\in \Omega^\delta,
+    \overline{w}_{\eta,\delta}(x) &:= \frac{(C_\alpha+\eta)\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + M_\eta, \qquad x\in \Omega_\delta,\\
+    \underline{w}_{\eta,\delta}(x) &:= \frac{(C_\alpha-\eta)\varepsilon^{\alpha+1}}{(d(x)+\delta)^\alpha} - M_\eta, \qquad x\in \Omega^\delta,
 \end{split}
 \end{equation*}
-where $C_\alpha = \frac{1}{\alpha} (\alpha+1)^{\alpha+1} $, $M_\eta$ to be chosen.
+where $C_\alpha := \frac{1}{\alpha} (\alpha+1)^{\alpha+1} $, $M_\eta$ to be chosen.
 We will show that $\overline{w}_{\eta,\delta}$ is a supersolution of \eqref{eq:PDEeps} in $\Omega_\delta$, while $\underline{w}_{\eta,\delta}$ is a subsolution of \eqref{eq:PDEeps} in $\Omega^\delta$.
-We have
+Compute
 \begin{align*}
@@
     & \qquad\qquad\qquad\qquad\qquad - \frac{(C_\alpha+\eta)\alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}|D d(x)|^2 + \frac{(C_\alpha+\eta)\alpha \varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+1}}\Delta d(x)\\
-    &\geq M_\eta - f(x) + \underbrace{\frac{\nu C_\alpha\alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}\left[\nu^{p-1}|Dd(x)|^{p-1} - |Dd(x)|^2 + \frac{(d(x)-\delta)\Delta d(x)}{\alpha+1}\right]}_{I}
+    &\geq M_\eta - f(x) + \underbrace{\frac{\nu C_\alpha\alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}\left[\nu^{p-1}|Dd(x)|^{p} - |Dd(x)|^2 + \frac{(d(x)-\delta)\Delta d(x)}{\alpha+1}\right]}_{I}
 \end{align*}
+%\textcolor{orange}{(In the parenthesis of I, I think the first term should be $\nu^{p-1}|Dd(x)|^p$ instead of $\nu^{p-1}|Dd(x)|^{p-1}$.)}
 where we use $(C_\alpha\alpha)^p = C_\alpha\alpha(\alpha+1)$ and $\nu = \frac{C_\alpha+\eta}{C_\alpha} \in (1,2)$ for small $\eta$. Let
 \begin{equation*}
-    \delta_\eta : = \frac{\alpha+1}{K_2}\left[\nu^{p-1}-1\right] \to 0 \qquad\text{as}\qquad \eta \to 0.
-\end{equation*}
-Recall \eqref{boundond} and there are two cases to be considered.
+    \delta_\eta : = \frac{\alpha+1}{K_2}\left[\nu^{p-1}-1\right]
+\end{equation*}
+and $\delta_\eta \to 0$ as $\eta \to 0$.
+Recall the definitions in \eqref{boundond}. To get  $\mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right]\geq 0$, there are two cases to consider, depending on how large $d(x)-\delta$ is.
 \begin{itemize}
-    \item If $0< d(x)-\delta <\delta_\eta < \delta_0$ for $\eta$ small, then $|Dd(x)| = 1$, and thus $I\geq 0$.
+    \item If $0< d(x)-\delta <\delta_\eta < \delta_0$ for $\eta$ small and fixed, then $|Dd(x)| = 1$, and thus $I\geq 0$.
 Hence $\mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right]\geq 0$ if we choose $M_\eta \geq \max_{\overline{\Omega}} f$.
-
+    %\textcolor{orange}{(Question: Here, $\eta$ is fixed right?)}
     \item If $d(x)-\delta\geq \delta_\eta$, then 
     \begin{equation*}
-        I \leq \left(\frac{1}{\delta_\eta}\right)^{\alpha+2}\nu C_\alpha \alpha(\alpha+1)\left[\nu^{p-1}K_1^{p-1}+K_1^2+K_2K_0\right]\varepsilon^{\alpha+2}.
-    \end{equation*}
-    Therefore, if we choose $M_\eta = \sup_{\overline{\Omega}} f + C\varepsilon^{\alpha+2}$ for $C$ large enough (depending on $\eta$), then $\mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right]\geq 0$.
+        I \leq \left(\frac{1}{\delta_\eta}\right)^{\alpha+2}\nu C_\alpha \alpha(\alpha+1)\left[\nu^{p-1}K_1^{p}+K_1^2+K_2K_0\right]\varepsilon^{\alpha+2}.
+    \end{equation*}
+    %\textcolor{orange}{(The first term in the bracket should be $\nu^{p-1}K_1^p$ instead of $\nu^{p-1}K_1^{p-1}$.)}
+
+    Thus, we can choose $M_\eta = \max_{\overline{\Omega}} f + C\varepsilon^{\alpha+2}$ for $C$ large enough (depending on $\eta$) so that  $\mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right]\geq 0$.
 \end{itemize}
-Therefore, $\overline{w}_{\eta,\delta}$ is a supersolution in $\Omega_\delta$. Similarly, we have 
+Therefore, $\overline{w}_{\eta,\delta}$ is a supersolution in $\Omega_\delta$.
+
+Similarly, we have 
 \begin{align*}
@@
     &= - M_\eta - f(x) \\
-    &+\underbrace{\frac{\nu C_\alpha\alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)+\delta)^{\alpha+2}}\left[\nu^{p-1}|Dd(x)|^{p-1} - |Dd(x)|^2 + \frac{(d(x)+\delta)\Delta d(x)}{\alpha+1}+\frac{(d(x)+\delta)^2}{\alpha(\alpha+1)\varepsilon}\right]}_{J}
+    &+\underbrace{\frac{\nu C_\alpha\alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)+\delta)^{\alpha+2}}\left[\nu^{p-1}|Dd(x)|^{p} - |Dd(x)|^2 + \frac{(d(x)+\delta)\Delta d(x)}{\alpha+1}+\frac{(d(x)+\delta)^2}{\alpha(\alpha+1)\varepsilon}\right]}_{J}
 \end{align*}
+%\textcolor{orange}{(In the parenthesis of J, the first term should be $\nu^{p-1}|Dd(x)|^p$ instead of $\nu^{p-1}|Dd(x)|^{p-1}$.)}
+
 where $\nu = \frac{C_\alpha-\eta}{C_\alpha}\in (0,1)$ for small $\eta$. Let
 \begin{equation*}
-    \delta_\eta := \left(1-\nu^{p-1}\right)\left(\frac{1+K_2\alpha\varepsilon}{\alpha(\alpha+1)\varepsilon}\right) \to 0 \qquad\text{as} \qquad \eta\to 0.
-\end{equation*}
-Recall \eqref{boundond}, and there are two cases.
+    \delta_\eta := \left(1-\nu^{p-1}\right)\left(\frac{\alpha(\alpha+1)\varepsilon}{1+K_2\alpha\varepsilon}\right) 
+\end{equation*}
+%\textcolor{orange}{( $\delta_\eta := \left(1-\nu^{p-1}\right)\left(\frac{\alpha(\alpha+1)\varepsilon}{1+K_2\alpha\varepsilon}\right)$)}
+
+and $\delta_\eta \to 0$ as $ \eta \to 0$.
+To obtain $\mathcal{L}^\varepsilon\left[\underline{w}_{\eta,\delta}\right]\leq 0$, there are two cases to consider depending on how large $d(x)+\delta$ is.
 \begin{itemize}
-    \item $0<d(x)+\delta<\delta_\eta < \delta_0$ for $\eta$ small, then $|Dd(x)| = 1$ , and thus $J\leq 0$.
+    \item If $0<d(x)+\delta<\delta_\eta < \delta_0$ for $\eta$ small and fixed, then $|Dd(x)| = 1$ , and thus $J\leq 0$.
 Hence $\mathcal{L}^\varepsilon\left[\underline{w}_{\eta,\delta}\right]\leq 0$ if we choose $M_\eta \geq -\max_{\Omega}f$.
-    \item If $d(x)+\delta\geq \delta_n$, then
-    \begin{equation*}
-        |J|\leq \left(\frac{1}{\delta_n}\right)^{\alpha+2} \nu C_\alpha\alpha(\alpha+1)\left[K_1^{p-1}+K_1^2 + \frac{K_0K_2}{\alpha+1} + \frac{K_0^2}{\alpha(\alpha+1)\varepsilon}\right]\varepsilon^{\alpha+2}
-    \end{equation*}
-     Therefore, if we choose $M_\eta = -\sup_{\overline{\Omega}} f - C\varepsilon^{\alpha+2}$ for $C$ large enough (depending on $\eta$), then $\mathcal{L}^\varepsilon\left[\underline{w}_{\eta,\delta}\right]\leq 0$.
+    \item If $d(x)+\delta\geq \delta_\eta$, then
+    \begin{equation*}
+        |J|\leq \left(\frac{1}{\delta_\eta}\right)^{\alpha+2} \nu C_\alpha\alpha(\alpha+1)\left[\nu^{p-1}K_1^{p}+K_1^2 + \frac{(K_0+1)K_2}{\alpha+1} + \frac{(K_0+1)^2}{\alpha(\alpha+1)\varepsilon}\right]\varepsilon^{\alpha+2}
+    \end{equation*}
+    %\textcolor{orange}{($|J|\leq \left(\frac{1}{\delta_\eta}\right)^{\alpha+2} \nu C_\alpha\alpha(\alpha+1)\left[K_1^{p}+K_1^2 + \frac{(K_0+\delta)K_2}{\alpha+1} + \frac{(K_0+\delta)^2}{\alpha(\alpha+1)\varepsilon}\right]\varepsilon^{\alpha+2}$)}
+
+     Thus, we can choose $M_\eta = -\max_{\overline{\Omega}} f - C\varepsilon^{\alpha+2}$ for $C$ large enough (depending on $\eta$) so that $\mathcal{L}^\varepsilon\left[\underline{w}_{\eta,\delta}\right]\leq 0$.
 \end{itemize}
-For $p=2$, we use the ansatz $u(x) = -C_\varepsilon \log(d(x))$ instead. Similarly to the previous case, we find $u(x) = -\varepsilon\log(d(x))$. For $0<\delta<\frac{1}{2}\delta_0$, we define 
+Therefore, $\underline{w}_{\eta,\delta}$ is a subsolution in $\Omega^\delta$.
+
+For $p=2$, we use the ansatz $u(x) = -C_\varepsilon \log(d(x))$ instead. Similar to the previous case, one can find $u(x) = -\varepsilon\log(d(x))$. For $0<\delta<\frac{1}{2}\delta_0$,  define 
 \begin{equation*}
@@
         &\overline{w}_{\eta,\delta}(x) = -(1+\eta)\varepsilon\log(d(x)-\delta) + M_\eta, \qquad x\in \Omega_\delta,\\
-        &\underline{w}_{\eta,\delta}(x) = -(1-\eta)\varepsilon\log(d(x)-\delta) - M_\eta, \qquad x\in \Omega^\delta,
+        &\underline{w}_{\eta,\delta}(x) = -(1-\eta)\varepsilon\log(d(x)+\delta) - M_\eta, \qquad x\in \Omega^\delta,
     \end{split}
@@
 where $M_\eta$ is to be chosen so that $\overline{w}_{\eta,\delta}(x)$ is a supersolution in $\Omega_\delta$ and $\underline{w}_{\eta,\delta}$ is a subsolution in $\Omega^\delta$.
-We omit the computations, as they are similar to the previous case.
+The computations are omitted here, as they are similar to the previous case.
 \smallskip
@@
 \noindent We divide the rest of the proof into 3 steps.
-We first construct a minimal solution, then a maximal solution to \eqref{eq:PDEeps}, and finally show that they are equal to conclude the existence and uniqueness of solution to \eqref{eq:PDEeps}.
+We first construct a minimal solution, then a maximal solution to \eqref{eq:PDEeps}, and finally show that they are equal to conclude the existence and the uniqueness of the solution to \eqref{eq:PDEeps}.
 \smallskip
@@
 Therefore, by the standard comparison principle for the second-order elliptic equation with Dirichlet boundary, $\delta_1 \leq  \delta_2$ implies $w_{\eta,\delta_1}\geq  w_{\eta,\delta_2}$ on $\overline{\Omega}$.
-        \item For $\delta'>0$, since $\underline{w}_{\eta,\delta'}$ is a subsolution in $\overline{\Omega}$ with finite boundary, we obtain that
+        \item For $\delta'>0$, since $\underline{w}_{\eta,\delta'}$ is a subsolution in $\overline{\Omega}$ with finite boundary, 
             \begin{equation}\label{e:cp_delta1}
@@
             \end{equation}
-        \item Similarly, since $\overline{w}_{\eta,\delta'}$ is a supersolution on $\Omega_{\delta'}$ with infinity value on the boundary $\partial\Omega_{\delta'}$, by comparison principle
+        \item Similarly, since $\overline{w}_{\eta,\delta'}$ is a supersolution on $\Omega_{\delta'}$ with infinity value on the boundary $\partial\Omega_{\delta'}$, by comparison principle,
             \begin{equation}\label{e:cp_delta2}
@@
 Using the local gradient estimate for $w_{\eta,\delta}$ solving \eqref{e:w_def}, we deduce that $\{w_{\eta,\delta}\}_{\delta>0}$ is locally bounded in $W^{1,\infty}_{\mathrm{loc}}(\Omega)$.
-Plugging it back into the defining equation \eqref{e:w_def}, we have that $\{w_{\eta,\delta}\}_{\delta>0}$ is locally bounded in $W^{2,r}_{\mathrm{loc}}(\Omega)$ for all $r<\infty$.
+Since $w_{\eta,\delta}$ solves \eqref{e:w_def}, we further have that $\{w_{\eta,\delta}\}_{\delta>0}$ is locally bounded in $W^{2,r}_{\mathrm{loc}}(\Omega)$ for all $r<\infty$ by Calderon-Zygmund estimates.
 
@@
     In particular, $w_{\eta,\delta}\to u$ in $\mathrm{C}^1_{\mathrm{loc}}(\Omega)$ thanks to Sobolev compact embedding.
-Let us rewrite the equation $\mathcal{L}^\varepsilon\left[w_{\eta,\delta}\right] = 0$ as $\varepsilon\Delta w_{\eta,\delta}(x) = F[w_{\eta,\delta}](x)$ in $U$ for $U\subset\subset \Omega$ where
+Let us rewrite the equation $\mathcal{L}^\varepsilon\left[w_{\eta,\delta}\right] = 0$ as $\varepsilon\Delta w_{\eta,\delta}(x) = F[w_{\eta,\delta}](x)$ for $x \in U\subset\subset \Omega$, where
     \begin{equation*}
@@
     \end{equation*}
-    Since $w_{\eta,\delta}\to u$ in $\mathrm{C}^1(U)$ as $\delta\to 0$, we have $F[w_{\eta,\delta}](x) \to F(x)$ uniformly in $U$ where 
+    Since $w_{\eta,\delta}\to u$ in $\mathrm{C}^1(U)$ as $\delta \to 0$, we have $F[w_{\eta,\delta}](x) \to F(x)$ uniformly in $U$ as $\delta \to 0$,  where 
     \begin{equation*}
@@
     \end{equation*}
-    In the limit, as $\delta\to 0$, we obtain that $u\in L^2(U)$ is a weak solution of $\varepsilon\Delta u = F$ in $U$ where $F$ is continuous, thus $u\in \mathrm{C}^2(\Omega)$ and by stability $u$ solves $\mathcal{L}^\varepsilon[u] = 0$ in $\Omega$.
-From \eqref{e:cp_delta3} we also have
+    In the limit, we obtain that $u\in L^2(U)$ is a weak solution of $\varepsilon\Delta u = F$ in $U$ where $F$ is continuous.
+Thus, $u\in \mathrm{C}^2(\Omega)$ and by stability, $u$ solves $\mathcal{L}^\varepsilon[u] = 0$ in $\Omega$.
+From \eqref{e:cp_delta3}, we also have
     \begin{equation*}
@@
     \end{equation*}
-    It is clear that $u(x)\to \infty$ as $\mathrm{dist}(x,\partial\Omega)\to 0$ with the precise rate like \eqref{rate_p<2} or \eqref{rate_p=2}.
-By construction, $u$ may depend on $\eta$.
-Next, we show that $u$ is the minimal solution of $\mathcal{L}^\varepsilon[u] = 0$ in $\Omega$ such that $u = +\infty$ on $\partial\Omega$, thus consequently showing that $u$ is independent of $\eta$.
-
-    \noindent Let $v\in W^{2,r}(\Omega)$ for all $r<\infty$ and $v$ solves \eqref{eq:PDEeps}.
+    Moreover, $u(x)\to \infty$ as $\mathrm{dist}(x,\partial\Omega)\to 0$ with the precise rate like \eqref{rate_p<2} or \eqref{rate_p=2}.
+Note that by construction, $u$ may depend on $\eta$.
+But next, we will show that $u$ is independent of $\eta$, by proving $u$ is the unique minimal solution of $\mathcal{L}^\varepsilon[u] = 0$ in $\Omega$ with $u = +\infty$ on $\partial\Omega$.
+
+    \noindent Let $v\in \rmC^{2}(\Omega)$ be a solution to \eqref{eq:PDEeps}.
 Fix $\delta>0$.
-Then since $v(x)\to \infty$ as $x\to \partial\Omega$ while $w_{\eta,\delta}$ remains bounded on $\partial \Omega$, comparison principle yields
+Since $v(x)\to \infty$ as $x\to \partial\Omega$ while $w_{\eta,\delta}$ remains bounded on $\partial \Omega$, the comparison principle yields
     \begin{equation*}
@@
     \end{equation*}
-    Let $\delta\to 0$ we deduce that $v\geq u$ on $\Omega$. This concludes that $u$ is the minimal solution in $W^{2,r}(\Omega)(\forall\,r<\infty)$ and thus $u$ is independent of $\eta>0$. 
+    Let $\delta\to 0$ and we deduce that $v\geq u$ in $\Omega$. This concludes that $u$ is the minimal solution in $\mathrm{C}^2(\Omega)(\forall\,r<\infty)$ and thus $u$ is independent of $\eta$. 
 \end{proof}
@@
 
-\begin{proof} For each $\delta>0$, let us denote $u_\delta\in \mathrm{C}^2(\Omega_\delta)$ to be the minimal solution to $\mathcal{L}[u_\delta] = 0$ in $\Omega_\delta$ and $u_\delta = +\infty$ on $\partial\Omega_\delta$.
+\begin{proof} For each $\delta>0$, let $u_\delta\in \mathrm{C}^2(\Omega_\delta)$ be the minimal solution to $\mathcal{L}^\varepsilon[u_\delta] = 0$ in $\Omega_\delta$ with $u_\delta = +\infty$ on $\partial\Omega_\delta$.
 By the comparison principle, for every $\eta>0$, there holds
@@
 \end{equation*}
-The monotoniciy, together with the local boundedness of $\{u_\delta\}_{\delta>0}$ in $W^{2,r}(\Omega)$, implies there exists $u\in W^{2,r}(\Omega)$ for all $r<\infty$ such that $u_\delta\to u$ strongly in $\rmC^1_{\mathrm{loc}}(\Omega)$.
-Therefore, using the equation $\mathcal{L}[u_\delta] = 0$ in $\Omega_\delta$ and the regularity of Laplace equation, we deduce that $u\in \mathrm{C}^2(\Omega)$ solves \eqref{eq:PDEeps} and
+The monotoniciy, together with the local boundedness of $\{u_\delta\}_{\delta>0}$ in $W^{2,r}_{\mathrm{loc}}(\Omega)$, implies that there exists $u\in W^{2,r}_{\mathrm{loc}}(\Omega)$ for all $r<\infty$ such that $u_\delta\to u$ strongly in $\rmC^1_{\mathrm{loc}}(\Omega)$.
+Using the equation $\mathcal{L}^\varepsilon [u_\delta] = 0$ in $\Omega_\delta$ and the regularity of Laplace's equation, we can further deduce that $u\in \mathrm{C}^2(\Omega)$ solves \eqref{eq:PDEeps} and
 \begin{equation*}
@@
 for all $\eta>0$.
-From the construction, as $u_\delta$ is independent of $\eta$, it is clear that $u$ is also independent of $\eta$.
-We now show that $u$ is the maximal solution of \eqref{eq:PDEeps}.
+As $u_\delta$ is independent of $\eta$ by the previous argument in Step 1, it is clear that $u$ is also independent of $\eta$.
+Now we show that $u$ is the maximal solution of \eqref{eq:PDEeps}.
 Let $v\in\rmC^2(\Omega)$ solve \eqref{eq:PDEeps}.
@@
 \end{equation}
-for any $\eta>0$. This extra parameter $\eta$ now enables us to show that $\overline{u} = \underline{u}$ in $\Omega$. The key ingredient here is the convexity in the gradient of the operator.
+for any $\eta>0$. This extra parameter $\eta$ now enables us to show that $\overline{u} = \underline{u}$ in $\Omega$. The key ingredient here is the convexity in the gradient slot of the operator.
 \smallskip
@@
 \begin{proof} Let $\theta\in (0,1)$.
-Define $w_\theta = \theta \overline{u} + (1-\theta) ^{-1}\inf_{\Omega} f$.
-If $w_\theta$ is a subsolution to \eqref{eq:PDEeps}, then we can use comparison principle to obtain that
-\begin{equation*}
-    w_\theta = \theta \overline{u} + (1-\theta) ^{-1}\inf_{\Omega} f\leq \underline{u} \qquad\text{in}\;\Omega.
-\end{equation*}
-If that is the case, let $\theta\to 1$ we conclude that $\overline{u} \leq \underline{u}$.
-There is a problem here.
-As they are both explosive solutions, to use comparison principle, we need to show that $w_\theta \leq \underline{u}$ in a neighborhood of $\partial\Omega$.
+Define $w_\theta = \theta \overline{u} + (1-\theta) \inf_{\Omega} f$.
+It can be verified that $w_\theta$ is a subsolution to \eqref{eq:PDEeps}.
+Then one may argue that by the comparison principle,
+\begin{equation*}
+    w_\theta = \theta \overline{u} + (1-\theta)\inf_{\Omega} f\leq \underline{u} \qquad\text{in}\;\Omega,
+\end{equation*}
+and conclude that $\overline{u} \leq \underline{u}$ by letting $\theta\to 1$.
+But we have to be careful here.
+As they are both explosive solutions, to use the comparison principle, we need to show that $w_\theta \leq \underline{u}$ in a neighborhood of $\partial\Omega$.
 From \eqref{e:chain}, we see that
@@
 \end{equation*}
- This means for any $\varsigma\in(0,1)$, we can find $\delta(\varsigma)>0$ small such that on $\Omega\backslash \Omega_\delta$, one has
-\begin{equation*}
-\frac{\overline{u}(x)}{\underline{u}(x)}\leq (1+\varsigma)     \qquad\Longrightarrow\qquad \left(\frac{1}{1+\varsigma}\right)\overline{u}(x) \leq \underline{u}(x) \qquad\text{in}\; \Omega\backslash \Omega_\delta.
-\end{equation*}
-For a given $\theta\in (0,1)$, we can always choose $\varsigma$ small enough such that $(1+\varsigma)^{-1} > \theta$, which will imply that $\underline{u}(x) \geq \theta \overline{u}(x) + (1-\theta) ^{-1}\left(\inf_\Omega f\right)$ for $0< d(x) < \delta' < \delta$.
-\end{proof}
-\noindent This finishes the well-posedness of \eqref{eq:PDEeps} for $1<p\leq2$. 
-\end{proof}
-
-\begin{proof}[Proof of Lemma \ref{lem:max}] The proof is a variation of Perron's method (see \cite{Capuzzo-Dolcetta1990}).
-Let $\varphi\in \rmC(\overline{\Omega})$ and $x_0\in \overline{\Omega}$ such that $u(x_0) = \varphi(x_0)$ and $u-\varphi$ has a global strict minimum over $\overline{\Omega}$ at $x_0$ and that
+ This means for any $\varsigma\in(0,1)$, there exists $\delta(\varsigma)>0$ small such that 
+\begin{equation*}
+\frac{\overline{u}(x)}{\underline{u}(x)}\leq (1+\varsigma)     \qquad \text{, i.e.,}\qquad \left(\frac{1}{1+\varsigma}\right)\overline{u}(x) \leq \underline{u}(x) \qquad\text{in}\; \Omega\backslash \Omega_\delta.
+\end{equation*}
+For a given $\theta\in (0,1)$, one can always choose $\varsigma$ small enough such that $(1+\varsigma)^{-1} > \theta$.
+Now we just choose $\theta$ close to $1$ so that $\underline{u}(x) \geq \theta \overline{u}(x) + (1-\theta)\left(\inf_\Omega f\right)$ for $x \in \Omega \setminus \Omega_\delta$ for some $\delta$ depending on $\theta$.
+\end{proof}
+
+\noindent This finishes the proof of the well-posedness of \eqref{eq:PDEeps} for $1<p\leq2$. 
+\end{proof}
+
+\begin{proof}[Proof of Lemma \ref{lem:max}] The proof is a variation of Perron's method (see \cite{Capuzzo-Dolcetta1990}) and we proceed by contradiction.
+Let $\varphi\in \rmC(\overline{\Omega})$ and $x_0\in \overline{\Omega}$ such that $u(x_0) = \varphi(x_0)$ and $u-\varphi$ has a global strict minimum over $\overline{\Omega}$ at $x_0$ with
 \begin{equation}\label{eq:max_a1}
@@
     \varphi^\varepsilon(x) - \varphi(x_0)  &= \varphi(x)-\varphi(x_0) + \varepsilon - |x-x_0|^2 \\
-    D\phi^\varepsilon(x) - D\phi(x_0) &= D\varphi(x) - D\varphi(x_0) - 2(x-x_0)
+    D\varphi^\varepsilon(x) - D\varphi(x_0) &= D\varphi(x) - D\varphi(x_0) - 2(x-x_0)
     \end{split}
@@
 for $x\in B(x,\delta)\cap \overline{\Omega}$.
-We deduce from \eqref{eq:max_a1}, the continuity of $H(x,p)$ near $(x_0,D\varphi(x_0))$ and the fact that $\varphi\in \rmC^1(\overline{\Omega})$ that if $\delta$ is small enough and $0<2\varepsilon < \delta^2$, then
+By the continuity of $H(x,p)$ near $(x_0,D\varphi(x_0))$ and the fact that $\varphi\in \rmC^1(\overline{\Omega})$, we can deduce from \eqref{eq:max_a1} that if $\delta$ is small enough and $0<2\varepsilon < \delta^2$, then
 \begin{equation}\label{eq:max_a2}
@@
 \end{equation}
-We have found $\phi^\varepsilon\in \mathrm{C}^1(\overline{\Omega})$ such that $\varphi^\varepsilon(x_0)>u(x_0)$, $\varphi^\varepsilon<u$ on $\partial B(x_0,\delta)\cap \overline{\Omega}$ and \eqref{eq:max_a2}.
+We have found $\varphi^\varepsilon\in \mathrm{C}^1(\overline{\Omega})$ such that $\varphi^\varepsilon(x_0)>u(x_0)$, $\varphi^\varepsilon<u$ on $\partial B(x_0,\delta)\cap \overline{\Omega}$ and \eqref{eq:max_a2}.
 Let
@@
     \tilde{u}(x) = \begin{cases}
-    \max \big\lbrace u(x),\phi^\varepsilon(x) \big\rbrace &x\in B(x_0,\delta)\cap \overline{\Omega},\\
+    \max \big\lbrace u(x),\varphi^\varepsilon(x) \big\rbrace &x\in B(x_0,\delta)\cap \overline{\Omega},\\
     u(x)&x\notin B(x_0,\delta)\cap \overline{\Omega}.\\
@@
 \end{equation*}
-We see that $\tilde{u}\in \rmC(\overline{\Omega})$ is a subsolution of \eqref{S_0} in $\Omega$ with $\tilde{u}(x_0) > u(x_0)$, which is a contradiction.
-Thus, $u$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$.
-\end{proof}
-
-\section{Differentiability with respect to the parameter}
-\noindent For the vanishing viscosity problem with the Dirichlet boundary condition,
-\begin{equation}
-\label{dir}
-\left\{
-  \begin{aligned}
-    H(x, Du^\epsilon(x)) &= \epsilon \Delta u^\epsilon \quad \, \text{in } U, \\
-              u^\epsilon &= 0 \quad \qquad \text{on } \partial U,
-  \end{aligned}
-\right.
-\end{equation}
-where  $H(x,p)$ is $C^\infty(\overline{U}\times \mathbb{R}^n)$, $\displaystyle \frac{H(x,p)}{|p|} \to \infty$ uniformly in $x$ as $|p| \to \infty$ and $\displaystyle \sup_{x\in U}|D_xH(x,p)|\leq C(1+|p|)$, we want to show the smooth dependence of $u^\epsilon$ on $\epsilon$.
-Formally, if we differentiate \eqref{dir} with respect to $\epsilon$, we get
-\begin{equation}
-\label{dir_dif}
-\left\{
-  \begin{aligned}
-    D_pH(x, Du^\epsilon(x))\cdot Du^\epsilon_\epsilon &= \epsilon \Delta u^\epsilon_\epsilon +\Delta u^\epsilon \quad \, \text{in } U, \\
-              u^\epsilon_\epsilon &= 0 \quad \qquad  \qquad  \text{on } \partial U.
-  \end{aligned}
-\right.
-\end{equation}
-By Schaefer's fixed point theorem and the maximal principle, $u^\epsilon_\epsilon$ is the unique solution in $C^{2,\alpha}(\overline{U})$ of \eqref{dir_dif}.
-
-\noindent The main idea is, we look at the difference quotients $\displaystyle \frac{u^{\epsilon+h}-u^\epsilon}{h}$and prove that as $h \to 0^+$, they converge to a limiting function $w^{\ast}$ in the uniform norm  such that $w^{\ast}$ solves \eqref{dir_dif}.
-Since \eqref{dir_dif} has a unique solution, we have $$u^\epsilon_\epsilon=\lim_{h \to 0^+}\frac{u^{\epsilon+h}-u^\epsilon}{h}.$$
-
-\subsection{Solution $u^\epsilon \in C^{2,\alpha}(\overline{U})$ exists} We use Schaufer's fixed point theorem as follows.
-
-\begin{thm} Suppose $X$ is a Banach space.
-Let $A:X \to X$ be continuous and compact.
-Assume the set $\{u\in X : u=  A[u]$ for some $0 \leq    \leq 1\}$ is bounded.
-Then $A$ has a fixed point $u =A[u]$.
+We see that $\tilde{u}\in \rmC(\overline{\Omega})$ is a subsolution of \eqref{eq:PDE0} in $\Omega$ with $\tilde{u}(x_0) > u(x_0)$, which is a contradiction.
+Thus, $u$ is a supersolution of \eqref{eq:PDE0} on $\overline{\Omega}$.
+\end{proof}
+
+\begin{thm}\label{convex} Let $H(x,p) = G(p)-f(x)$ where $G\geq 0$ with $G(0) = 0$ is a convex function from $\R^n\to\R^n$ and $f\in \mathrm{C}^2_c(\R^n)$.
+Let $u\in \mathrm{C}_c(\R^n)$ be a viscosity solution to $u+H(x,Du) = 0$ in $\R^n$.
+Then $u$ is semiconcave, i.e, $u$ is a viscosity solution of  $-D^2u \succ -c\;\mathbb{I}_n$ in $\R^n$ where
+\begin{equation*}
+    c = \max \big\lbrace  D_{\xi\xi}f(x): |\xi|=1, x\in \overline{\Omega} \big\rbrace\geq 0.
+\end{equation*}
 \end{thm}
-\noindent Fix $0<\alpha<1$. Let $X=C^{1,\alpha}(\overline{U})$. Given $u \in X=C^{1,\alpha}(\overline{U})$, we look at the linear PDE
-\begin{equation}
-\label{fix}
-\left\{
-  \begin{aligned}
-   \epsilon \Delta v &= H(x, Du) \quad \, \text{in } U, \\
-              v &= 0 \qquad \qquad \text{on } \partial U.
-  \end{aligned}
-\right.
-\end{equation}
-\noindent
-Estimate the Holder norm of RHS
-$$\|H(x, Du)\|_{C^{0, \alpha}(\overline{U})}:=\sup_{x\in\overline{U}} |H(x,Du(x))| + \sup_{x, y \in \overline{U}}\frac{|H(x, Du(x))-H(y, Du(y))|}{|x-y|^\alpha}.$$
-Since $Du$ is bounded and H is smooth,
-\begin{equation}
-    \sup_{x\in\overline{U}} |H(x,Du(x))| \leq C.
-\end{equation}
-
-\begin{equation}
-    \begin{aligned}
-  &\sup_{x, y \in \overline{U}}\frac{|H(x, Du(x))-H(y, Du(y))|}{|x-y|^\alpha}\\
-  \leq &  \sup_{x, y \in \overline{U}}\frac{|H(x, Du(x))-H(y, Du(x))|}{|x-y|^\alpha} + \sup_{x, y \in \overline{U}}\frac{|H(y, Du(x))-H(y, Du(y))|}{|x-y|^\alpha} \\
-  =&    \sup_{x, y \in \overline{U}}\frac{|\int_0^1D_xH(y+\theta (x-y), Du(x))d\theta \cdot (x-y)|}{|x-y|^\alpha}\\& +
-     \sup_{x, y \in \overline{U}}\frac{|\int_0^1D_pH(y, Du(y)+\theta (Du(x)-Du(y)))d\theta \cdot (Du(x)-Du(y))|}{|x-y|^\alpha}\\
-  \leq &  C\sup_{x, y \in \overline{U}} (1+|Du(x)|)|x-y|^{1-\alpha} +  C \sup_{x, y \in \overline{U}}\frac{| (Du(x)-Du(y))|}{|x-y|^\alpha}\\
- \leq & C(1 + \|u\|_{C^{1,\alpha}(\overline{U})})
-    \end{aligned}
-\end{equation}
-since $Du$ is bounded on $\overline{U}$, $D_pH \in C^\infty (\overline{U} \times \mathbb{R}^n)$ and
-$\displaystyle \sup_{x\in U}|D_xH(x,p)|\leq C(1+|p|)$. Therefore,
-\begin{equation}
- \|H(x, Du)\|_{C^{0, \alpha}(\overline{U})} \leq C(1 + \|u\|_{C^{1,\alpha}(\overline{U})}).
-\end{equation}
-By Schauder estimates, there exists a unique solution $v \in C^{2,\alpha }(\overline{U})$ such that
-\begin{equation}
-\label{schauder}
-    \|v\|_{C^{2, \alpha}(\overline{U})} \leq C  \|H(x, Du)\|_{C^{0, \alpha}(\overline{U})}. 
-\end{equation}
-\noindent Define operator $A$ on $X := C^{1, \alpha} (\overline{U}) $ by $A[u]=v$. So 
-\begin{equation}
-     \|A[u]\|_{C^{2, \alpha}(\overline{U})} \leq C(1 + \|u\|_{C^{1,\alpha}(\overline{U})}),
-\end{equation}
-\noindent
- and thus $A$ is continuous and compact.
-(i.e., if $\{u_k\}_{k=1}^\infty$ is bounded in $X=C^{1, \alpha}(\overline{U})$, then $\{A[u_k]\}_{k=1}\infty$ is bounded in $C^{2,\alpha} (\overline{U})$, thus precompact in $C^{1, \alpha}(\overline{U})$.
-Lemma 6.36 in Gilbarg and Trudinger.
-)
-
-\noindent Next we try to bound $\{u\in X : u=  A[u]$ for some $0 \leq    \leq 1\}$. If $u=  A[u]$, the PDE becomes
-
-\begin{equation}
-\label{lamb}
-\left\{
-  \begin{aligned}
-   \epsilon \Delta u &=   H(x, Du) \quad \, \text{in } U, \\
-              u &= 0 \qquad \qquad \text{on } \partial U.
-  \end{aligned}
-\right.
-\end{equation}
-
-\noindent Calderon-Zygmund estimates tell us that if we have
-\begin{equation}
-\label{cald}
-\left\{
-  \begin{aligned}
-  - \Delta v &=\Tilde{f}   \qquad \, \text{in } U, \\
-              v &= 0 \qquad \text{on } \partial U.
-  \end{aligned}
-\right.
-\end{equation}
-and $\Tilde{f} \in {L^p(U)}$ for some $p\in (1, \infty)$, then $v \in W^{2,p}(U)$ and $$\|v\|_{w^{2,p}(U)} \leq C\|\Tilde{f}\|_{L^p(U)}.$$
-
-\noindent Apply to \eqref{lamb} and we get
-
-\begin{equation}
-    \|u\|_{w^{2,p}(U)} \leq C\|H(x, Du)\|_{L^p(U)}
-\end{equation}
-
-(We want RHS to be bounded by some constant so that later we can choose $p$ larger than $n$ to  conclude $ \|u\|_{C^{1, \alpha}(U)} \leq   C\|u\|_{w^{2,p}(U)} \leq C$ by Morrey's estimate.) By a priori estimate, if we assume the solution of \eqref{dir} $u$ exists, then $\| Du\|_{L^\infty} \leq C_0$ where $C_0$ is independent of $\epsilon$.
-We can modify $H$ to get a new $\Tilde{H}$ so that it is smooth, $\Tilde{H} = H$ for $|p|<C_1$ and $H(x,p)=C_1+1$ for $|p|>C_1+1$ for some constant $C_1$ ($C_1$ is definitely larger than $C^0$).
-Moreover, the same prior estimate is correct for $\Tilde{H}$.
-Namely, if the solution $\Tilde{u}$ to \eqref{dir} with $H$ replaced by $\Tilde{H}$ exists, then $\| D\Tilde{u}\|_{L^\infty} \leq C_0$.
-(The way we choose this $C_1$ is that we work back from the beginning of the proof of a priori estimate for $u$, on both the boundary and interior of $\Omega$, and modify $H$ so that all the proofs go through and the same a priori estimate holds for the equation with $\Tilde{H}$.) Now with $\Tilde{H}$, we go through the same argument of Schaufer's fixed point theorem from the very beginning, and \eqref{cald} reads
-\begin{equation}
-       \|\Tilde{u}\|_{w^{2,p}(U)} \leq C\|\Tilde{H}(x, D\Tilde{u})\|_{L^p(U)} \leq C(1+\|D\Tilde{u}\|_{L^\infty}) \leq C.
-\end{equation}
-Choose $p=2n$ and $\displaystyle \alpha =\frac{1}{2}$. We have $\{\Tilde{u}\in X : \Tilde{u}=  A[\Tilde{u}]$ for some $0 \leq    \leq 1\}$ is bounded in $X= C^{1, \frac{1}{2}}(
-\overline{U})$.
-Thus Schaefer's fixed point theorem implies the equation \eqref{dir} with $H$ replaced by $\Tilde{H}$ has a solution $\Tilde{u} \in C^{2,\alpha} (\overline{\Omega})$.
-Since $\| D\Tilde{u}\|_{L^\infty} \leq C_0$, $\Tilde{u}$ also solves the original equation \eqref{dir}.
-
-\subsection{Uniqueness}
-Let $u$ and $v$ be two solutions to \eqref{dir} and $w := u-v$. Then we have
-\begin{equation}
-\begin{aligned}
-    &-\epsilon \Delta (u-v) = H(x, Dv)-H(x, Du)\\
-    \Rightarrow &-\epsilon \Delta w   =\int_0^1 D_pH(x, tDv+(1-t)Du) \cdot (Dv-Du)dt\\
-    \Rightarrow &-\epsilon \Delta w  +\int_0^1 D_pH(x, tDv+(1-t)Du)dt \cdot Dw = 0.
-\end{aligned}
-\end{equation}
-By the strong maximum principle, $w \equiv 0$.
-
-\subsection{Smooth dependence on $\epsilon$}
-Fix $\epsilon >0$. Let  $$w^h(x):=\frac{u^{\epsilon+h}(x)-u^\epsilon(x)}{h} \in C^{2,\alpha}(\overline{U}).$$
-
-A little computation shows that $w^h$ solves
-
-\begin{equation}
-\label{dir_quo}
-\left\{
-  \begin{aligned}
-   \epsilon \Delta w^h(x) + \frac{\epsilon}{\epsilon + h}\Delta u^\epsilon &= \frac{\epsilon}{\epsilon +h} \int_0^1 D_pH(x, Du^\epsilon+\theta (Du^{\epsilon+h}-Du^\epsilon)) d\theta \cdot Dw^h \quad \, \text{in } U, \\
-              w^h &= 0 \quad \qquad \text{on } \partial U.
-  \end{aligned}
-\right.
-\end{equation}
-From the existence proof, we know $\|u^\epsilon\|_{C^{2,\alpha}(\overline{U})} \leq C$ uniformly in $\epsilon$.
-So $\|Du^{\epsilon+h}-Du^\epsilon\|_{C^{0,\alpha}(\overline{U})}$and $\|\Delta u\|_{C^{0,\alpha}(\overline{U})}
-$ is uniformly bounded in $h$.
-
-By Schauder estimates, $\{w^h\}_{h>0} \subset C^{2, \alpha}(\overline{U})$ are bounded, hence is precompact in $ C^{2, \beta}(\overline{U})$ for any $\beta < \alpha$.
-Therefore, there exits a subsequence $\{w^{h_j}\}_{j=1}^\infty$ such that $w^{h_j} \to w^\ast$ for some $w^\ast \in  C^{2, \beta}(\overline{U}) $ and $w^\ast$ solves \eqref{dir_dif}.
-This implies $w^h \to w^\ast$ in $C^{2, \beta}(\overline{U})$.
-\end{appendices}
-
+\begin{proof} Let us consider the auxiliary functional
+\begin{equation*}
+    \Phi(x,y,z) = u(x)-2u(y)+u(z) - \frac{\alpha}{2}|x-2y+z|^2 - \frac{c}{2}|y-x|^2-\frac{c}{2}|y-z|^2
+\end{equation*}
+for $(x,y,z)\in \R^n\times\R^n\times\R^n$.
+By a priori estimate, $u$ is bounded and Lipschitz, thus we can assume $\Phi$ achieves its maximum over $\R^n\times\R^n\times \R^n$ at $(x_\alpha,y_\alpha,z_\alpha)$.
+The viscosity solutions tests give us
+\begin{align*}
+    &u(x_\alpha) + G\big(p_\alpha+c(x_\alpha-y_\alpha)\big) \leq f(x_\alpha)\\
+    &u(z_\alpha) + G\big(p_\alpha+c(z_\alpha-y_\alpha)\big) \leq f(z_\alpha)\\
+    &u(y_\alpha) + G\left(p_\alpha+\frac{c}{2}(x_\alpha-y_\alpha) + \frac{c}{2}(z_\alpha-y_\alpha)\right) \geq f(y_\alpha),
+\end{align*}
+where $p_\alpha = \alpha(x_\alpha-2y_\alpha+z_\alpha)$. Using the convexity of $G$ we have
+\begin{equation*}
+    2G\left(p_\alpha+\frac{c}{2}(x_\alpha-y_\alpha) + \frac{c}{2}(z_\alpha-y_\alpha)\right) \leq G\big(p_\alpha+c(x_\alpha-y_\alpha)\big)  + G\big(p_\alpha+c(z_\alpha-y_\alpha)\big)
+\end{equation*}
+therefore
+\begin{equation*}
+    u(x_\alpha) - 2u(y_\alpha) + u(z_\alpha) \leq f(x_\alpha) - 2f(y_\alpha) + f(z_\alpha).
+\end{equation*}
+\begin{itemize}
+    \item $\Phi(x_\alpha,y_\alpha,z_\alpha)\geq \Phi(0,0,0)$ gives us
+    \begin{equation*}
+        \frac{\alpha}{2}|x-2y+z|^2 + \frac{c}{2}|y-x|^2+\frac{c}{2}|y-z|^2 \leq C.
+    \end{equation*}
+    Thus we can assume $(x_\alpha-y_\alpha)\to h_0$ and $(y_\alpha-z_\alpha)\to h_0$ as $\alpha\to \infty$.
+    \item $\Phi(x_\alpha,y_\alpha,z_\alpha )\geq \Phi(y_\alpha+h_0,y_\alpha,y_\alpha-h_0)$ gives us
+    \begin{align*}
+        u(x_\alpha)-2u(y_\alpha) + u(z_\alpha) - \frac{\alpha}{2}|x_\alpha - 2y_\alpha+z_\alpha|^2 - \frac{c}{2}|x_\alpha-y_\alpha|^2 - \frac{c}{2}|y_\alpha-z_\alpha|^2 \\
+        \geq u(y_\alpha+h_0) - 2u(y_\alpha) + u(y_\alpha-h_0) - c|h_0|^2.
+    \end{align*}
+    Therefore, using the fact that $u$ is Lipschitz, we have
+    \begin{equation*}
+    \begin{split}
+        \frac{\alpha}{2}|x_\alpha - 2y_\alpha+z_\alpha|^2 
+        &\leq c\left(\frac{2|h_0|^2 - |x_\alpha-y_\alpha|^2 - |y_\alpha-z_\alpha|^2}{2}\right) \\
+        &+ C\Big(|(x_\alpha-y_\alpha) - h_0| + |(z_\alpha - y_\alpha) + h_0|\Big) \to 0
+    \end{split}
+    \end{equation*}
+    as $\alpha\to \infty$.
+\end{itemize}
+For any $x\in \R^n$, we have $\Phi(x_\alpha,y_\alpha,z_\alpha) \geq \Phi(x+h,x,x-h)$, thus
+\begin{align*}
+    u(x+h)-2u(x)+u(x-h)-c|h|^2 &\leq f(x_\alpha)-2f(y_\alpha) + f(z_\alpha) \\
+    &- \frac{\alpha}{2}|x_\alpha - 2y_\alpha+z_\alpha|^2-\frac{c}{2}|y_\alpha-x_\alpha|^2-\frac{c}{2}|y_\alpha-z_\alpha|^2.
+\end{align*}
+If $\{y_\alpha\}$ is unbounded as $\alpha\to \infty$ then since $f\in \mathrm{C}_c^2(\R^n)$, we have $f(y_\alpha)\to 0$ as $\alpha\to \infty$.
+As a consequence, $x_\alpha,z_\alpha \to \infty$ as well and thus $f(x_\alpha)-2f(y_\alpha) + f(z_\alpha)\to 0$ as $\alpha\to \infty$.
+Therefore
+\begin{equation*}
+    u(x+h)-2u(x)+u(x-h)-c|h|^2 \leq 0.
+\end{equation*}
+If $\{y_\alpha\}$ is bounded, then $y_\alpha\to y_0$ as $\alpha\to \infty$, thus
+\begin{equation*}
+     u(x+h)-2u(x)+u(x-h)-c|h|^2 \leq f(y_0+h_0) - 2f(y_0) + f(y_0-h_0) -c|h_0|^2.
+\end{equation*}
+Let $\xi = h_0$, we have
+\begin{equation*}
+    \begin{cases}
+      f(y_0+h_0) - f(y_0) = \int_0^1 D_\xi f(y_0 + t\xi)\cdot \xi dt\\
+      f(y_0) - f(y_0-h_0)  = \int_0^1 D_\xi f(y_0 - t\xi)\cdot \xi dt.
+    \end{cases}
+\end{equation*}
+Therefore
+\begin{equation*}
+\begin{split}
+     f(y_0+h_0) - 2f(y_0) + f(y_0-h_0) &= \int_0^1 \Big(D_\xi f(y_0 + t\xi) - D_\xi f(y_0 - t\xi) \Big)\cdot \xi dt\\
+     &= \int_0^1 \int_0^1 D^2_{\xi\xi} \xi \cdot f(y_0+st \xi)\cdot \xi\;dtds.
+\end{split}
+\end{equation*}
+Therefore
+\begin{equation*}
+    |f(y_0+h_0) - 2f(y_0) + f(y_0-h_0)| \leq \left(\max_{|\xi|=1}D_{\xi\xi} f\right)|\xi|^2.
+\end{equation*}
+Hence
+\begin{equation*}
+    u(x+h)-2u(x)+u(x-h)-c|h|^2 \leq 0
+\end{equation*}
+and thus $u$ is semiconcave. It is easy to see that if $\varphi$ is smooth and $u-\varphi$ has a local min at $x$ then $D^2\varphi(x)\prec c\;\mathbb{I}$, thus $-D^2\varphi(x)\geq -c\;\mathbb{I}$.
+\end{proof}
+%\textcolor{orange}{(I double checked the proof of Jeff and I think his proof is fine.
+Actually we can choose $y_\alpha$ so that $\{y_\alpha\}$ is bounded, only using the fact that $u$ is bounded.
+But your proof is good too.)}
+
+%\end{appendices}
+\stoptocwriting
 \section*{Acknowledgement}
 The authors would like to express their appreciation to Hung V. Tran for his invaluable guidance.
+\resumetocwriting
 

### 2021-07-15 Drafts and notes/Draft_05.tex
Almost final

--- 2021-07-15 Drafts and notes/Draft_04.tex
@@
 \end{equation}
-This suggests that $Du^\varepsilon \approx \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}$. We show that this is indeed true (Lemma \ref{lem:boundDu^eps}).
-
 \textcolor{blue}{
-However, to get a useful estimate by the doubling variable, at the maximum point $x_0$ of $u^\varepsilon(x) - u(x)$, we must have $d(x_0)\approx \varepsilon^{\gamma}$ for $\gamma<1$ so that the latter term in \eqref{heur2} vanishes as $\varepsilon\to 0$.
+To get a useful estimate by the doubling variable, at the maximum point $x_0$ of $u^\varepsilon(x) - u(x)$, we must have $d(x_0)\approx \varepsilon^{\gamma}$ for $\gamma<1$ so that the latter term in \eqref{heur2} vanishes as $\varepsilon\to 0$.
 It turns out that such an estimate is quite delicate.
@@
 
-\subsection{Local gradient estimate} 
-The following theorem is about the local gradient bound as in \cite[Appendix]{Lasry1989}.
-The technique being used is the classical Bernstein method.
-Let $\Omega$ be an open, bounded subset of $\R^n$, $\varepsilon \in (0,1)$ and $p>1$.
+\subsection{Local gradient estimate} Let $\Omega$ be an open, bounded subset of $\R^n$, $\varepsilon \in (0,1)$ and $p>1$.
+We state a priori estimate for $\rmC^2$ solutions of \eqref{eq:PDEeps} (\cite[Appendix]{Lasry1989}).
+Since we are working with nice solutions, the proof is relatively simple using the classical Bernstein method (\cite{bernstein_sur_1910}).
+We provide a proof in Appendix for the readers' convenience.
 
@@
 \end{thm}
+
 %\textcolor{orange}{(I think here we want to add for $\varepsilon$ small enough?)}
-
-\noindent A proof of this theorem is provided in Appendix for the reader's convenience.
 
@@
 \end{equation*}
-for $x\in \Omega$, where $\delta_{0,\Omega}$ is defined as in \eqref{def:delta_0}. In particular, if $1<p<2$ then
-\begin{equation*}
-    C_f\leq u^\varepsilon(x)\leq C_f + C\varepsilon, \qquad x\in \Omega_\varepsilon.
-\end{equation*}
-Furthermore, for all $1<p\leq 2$ there holds $|u^\varepsilon-C_f| = \mathcal{O}\left(\varepsilon^{\alpha+1}\right)$ on each compact subset of $\Omega$.
+for $x\in \Omega$, where $\delta_{0,\Omega}$ is defined as in \eqref{def:delta_0}.
+In particular, if $1<p<2$, we have $C_f\leq u^\varepsilon(x)\leq C_f + C\varepsilon$ for $x\in \Omega_\varepsilon$ and $|u^\varepsilon(x)| = \mathcal{O}\left(\varepsilon^{\alpha+1}\right)$ on each compact subset of $\Omega$.
 \end{thm}
@@
 \end{align}
-where $C_\frac{\kappa}{2}$ is the upper bound of $Du^\varepsilon$ in $\Omega_\frac{\kappa}{2}$, as is given in the a priori estimate (Theorem \ref{thm:grad_1}) and $C$ is a constant that depends only on $\nu$, $\alpha$, and bounds on $d,Dd$ and $\Delta d$.
-Using \eqref{delta_psi} and \eqref{convex4} in \eqref{convex3}, we get
+where, as is given in the a priori estimate (Theorem \ref{thm:grad_1}),
+\begin{equation}\label{est_Ckappa}
+    |Du^\varepsilon(x)|\leq C_{\frac{\kappa}{2}}, \qquad \;x\in \Omega_{\frac{\kappa}{2}},
+\end{equation}
+and $C$ is a constant that depends only on $\nu$, $\alpha$, and bounds on $d,Dd$ and $\Delta d$. Using \eqref{delta_psi} and \eqref{convex4} in \eqref{convex3}, we get
 \begin{equation*}
@@
 
+\begin{rem} Using our approach, in order to relax the assumption $\mathrm{supp}(f)\subset\subset\Omega$ to $f = 0$ on $\partial\Omega$ as in Theorem \ref{main_thm1}, it is necessary to know explicitly how the constant $C_\kappa$ in \eqref{est_Ckappa} blows up as $\kappa\to 0$.
+Fortunately, such a refined version of the local gradient bound is available, for instance \cite[Theorem 3.1]{Armstrong2015} where the authors use Bernstein's method inside a doubling variables argument and explicitly keeping track of all dependencies.
+We refer the readers to \cite{armstrong_stochastic_2012, barles_weak_1991,capuzzo_dolcetta_holder_2010} and the references therein for related versions of the gradient bound.
+\end{rem}
+
+\begin{lem} There exists a constant $C$ independent of $\varepsilon$ such that
+\begin{equation*}
+|Du^\varepsilon(x)| \leq C\left( 1 + \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}\right) \qquad\text{for}\;x\in \Omega.
+\end{equation*}
+\end{lem}
+
 \begin{rem} Using our approach, in order to relax the assumption $\mathrm{supp}(f)\subset\subset\Omega$ to $f = 0$ on $\partial\Omega$ as in Theorem \ref{main_thm1}, we need to know more about the blow up rate $C_\kappa$ in $|Du^\varepsilon(x)|\leq C_\kappa$ as $\kappa\to 0$.
-We will use the result in
-
+Here are some results in the literature: if $u$ solves ($f\in \mathrm{C}^1(\overline{\Omega}), f\geq 0$)
+\begin{equation*}
+\begin{cases}
+    \lambda u + |Du|^p - f(x) - \Delta u = 0&\qquad\text{in}\;\Omega,\\
+    u = +\infty&\qquad\text{on}\;\partial\Omega
+\end{cases}
+\end{equation*}
+then we can have a better bound in a priori estimate (\cite{lions_quelques_1985}) 
+\begin{equation*}
+    |Du(x)| \leq \frac{C}{d(x)^{\alpha+1}}, \qquad x\in \Omega
+\end{equation*}
+where $\alpha = \frac{2-p}{p-1}$, while (\cite{alessio_asymptotic_2006}) gives an asymptotic behavior
+\begin{equation*}
+    \lim_{d(x)\to 0} \Big(Du(x)\cdot Dd(x)\Big)d(x)^{\alpha+1} = (\alpha+1)^{\alpha+1}\mathfrak{n}(x_0).
+\end{equation*}
+Here $\underline{x}$ is the unique projection of $x$ (near the boundary) onto $\partial\Omega$ and $\mathfrak{n}(x_0)$ is the unit outward normal vector of $\Omega$ at $x_0$. 
+\paragraph{\textbf{Our version with $\varepsilon$}}
+In our version, the problem with $\varepsilon$, we have 
+\begin{equation*}
+\begin{cases}
+    \lambda u^\varepsilon + |Du^\varepsilon|^p - f(x) - \varepsilon\Delta u^\varepsilon = 0&\qquad\text{in}\;\Omega,\\
+    u^\varepsilon = +\infty&\qquad\text{on}\;\partial\Omega
+\end{cases}
+\end{equation*}
+we can obtain that
+\begin{equation}\label{eq:yy}
+    |Du^\varepsilon(x)| \leq \frac{C}{d(x)^{\alpha+1}}, \qquad x\in \Omega
+\end{equation}
+and 
+\begin{equation}\label{eq:xx}
+    \lim_{d(x)\to 0} \Big(Du^\varepsilon(x)\cdot Dd(x)\Big)d(x)^{\alpha+1} = (\alpha+1)^{\alpha+1}\mathfrak{n}(x_0)\varepsilon^{\alpha+1}.
+\end{equation}
+
+\paragraph{\textbf{The result that we need for Theorem \ref{main_thm2}}} The ideal estimate we are expecting is, there exists a constant $C$ independent of $\varepsilon$ such that
+\begin{equation*}
+|Du^\varepsilon(x)| \leq C + \frac{C\varepsilon^{\alpha+1}}{d(x)^{\alpha+1}} \qquad\text{for}\;x\in \Omega.
+\end{equation*}
+This estimate can be proven following from a priori estimate $|Du^\varepsilon(x)|\leq C_\delta$ for $x\in \Omega_\delta$ and \eqref{eq:xx} if the limit in \eqref{eq:xx} is uniform in $\varepsilon$.
+
+\paragraph{\textbf{Difficulty}} However, \eqref{eq:xx} is not uniform in $\varepsilon$ (at least from the method the authors Porretta and Veron use in \cite{alessio_asymptotic_2006}).
 \end{rem}
 
-\begin{cor} Assume $f = 0$ on $\partial\Omega$.
-Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
-Let $K$ be a compact subset of $\Omega$, then there exists a constant $C_K$ such that
-\begin{equation*}
-    \sup_{x\in K} \big(u^\varepsilon(x) -u(x)\big) \leq C_K\varepsilon.
-\end{equation*}
-\end{cor}
-\begin{proof} We can find $\kappa\in \left(0,\delta_0\right)$ such that $K\subset\subset \Omega_{\kappa}$.
-Define $f_\kappa$ as in the proof of Theorem \ref{main_thm1}, where $\mathrm{supp}(f_\kappa)\subset\Omega_{\frac{\kappa}{2}}$ and
-\begin{equation*}
-    0\leq f - f_\kappa \leq L\kappa
-\end{equation*}
-where $L$ is the Lipschitz constant of $f$.
-Let $u^\varepsilon_\kappa\in \rmC^2(\Omega)\cap \rmC(\overline{\Omega})$ be the solution to \eqref{eq:PDEeps} with datum $f_k$ and $u_k$ be the solution to \eqref{eq:PDE0} with datum $f_k$, then
-\begin{equation*}
-  0\leq u^\varepsilon(x) - u^\varepsilon_\kappa(x)\leq L\kappa \qquad\text{for}\;x\in \Omega
-\end{equation*}
-and
-\begin{equation*}
-    0\leq u(x) - u_\kappa(x)\leq L\kappa \qquad\text{for}\;x\in \Omega.
-\end{equation*}
-Therefore
-\begin{equation*}
-    u^\varepsilon(x)-u(x)\leq 2L\kappa + \big(u^\varepsilon_\kappa - u_\kappa\big) \leq 2L\kappa+C_{\kappa}\varepsilon
-\end{equation*}
-where we use the rate $\mathcal{O}(\varepsilon)$ from Theorem \ref{thm:rate_doubling2} as $f_\kappa$ is compactly supported. 
-\end{proof}
-
-\begin{rem} It is clear from the proof that $C_K$ blows up as $K$ approaching $\Omega$ and we do not have any boundary layer yet, since the bound $|Du^\varepsilon(x)|\leq C_\kappa$ for $x\in \Omega_\kappa$ is not an explicit bound.
-We refer the readers to \cite{alessio_asymptotic_2006} for an explicit behavior of $Du^\varepsilon(x)$ as $x\to \partial \Omega$.
-Of course, using this explicit behavior of $Du^\varepsilon$ we can obtain a boundary layer from this proof, which we omit it here.
-\end{rem}
-
-\begin{proof}[Proof of Theorem \ref{main_thm2}] Define
-
-\end{proof}
+%\begin{proof}[Proof of Theorem \ref{main_thm2}] Define
+
+%\end{proof}
 

### 2021-07-15 Drafts and notes/Draft_06.tex
Almost final

--- 2021-07-15 Drafts and notes/Draft_05.tex
@@
 \end{equation}
+We show in Lemma \ref{lem:boundDu^eps} that \eqref{heur2} gives the correct behavior of $Du^\varepsilon$ where $\alpha = \frac{2-p}{p-1}$. \\
+\noindent
 \textcolor{blue}{
@@
 
-Using the convexity of $|\xi|^p$, we can avoid the doubling variable route to get a better one-sided estimate.
+Using the convexity of $|\xi|^p$, we can avoid the doubling variable route to get a better one-sided estimate for compactly supported $f$.
 Such an one-sided rate is well-known for the case of vanishing discount with zero Dirichlet boundary condition (see \textcolor{blue}{NEED CITATION}).
@@
 \begin{thm}\label{main_thm2} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
-Assume that $1 < p\leq 2$ and $f$ is Lipschitz with $f = 0$ on $\partial\Omega$.
+Assume that $1 < p\leq 2$ and $f$ is a compactly supported Lipschitz function defined on $\overline{\Omega}$.
 Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
@@
 Also, it is useful to note that $\alpha+1 = (p-1)^{-1}$.
-More results on the behavior of the gradient of $u^\varepsilon$ can be found in \cite{alessio_asymptotic_2006}.
+More results on the behavior of the gradient of $u^\varepsilon$ can be found in \cite{alessio_asymptotic_2006} and Lemma \ref{lem:boundDu^eps}, where we show $|Du^\varepsilon|\leq C + C\left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}$.
 
@@
 \begin{rem} Using our approach, in order to relax the assumption $\mathrm{supp}(f)\subset\subset\Omega$ to $f = 0$ on $\partial\Omega$ as in Theorem \ref{main_thm1}, it is necessary to know explicitly how the constant $C_\kappa$ in \eqref{est_Ckappa} blows up as $\kappa\to 0$.
-Fortunately, such a refined version of the local gradient bound is available, for instance \cite[Theorem 3.1]{Armstrong2015} where the authors use Bernstein's method inside a doubling variables argument and explicitly keeping track of all dependencies.
+Fortunately, such a refined version of the local gradient bound is available, for instance \cite[Theorem 3.1]{Armstrong2015} where the authors use Bernstein's method inside a doubling variables argument and explicitly keep track of all dependencies.
 We refer the readers to \cite{armstrong_stochastic_2012, barles_weak_1991,capuzzo_dolcetta_holder_2010} and the references therein for related versions of the gradient bound.
@@
 
-\begin{lem} There exists a constant $C$ independent of $\varepsilon$ such that
-\begin{equation*}
+\begin{lem}\label{lem:boundDu^eps} For all $\varepsilon$ small enough, there exists a constant $C$ independent of $\varepsilon$ such that
+\begin{equation}\label{eq:es_final}
 |Du^\varepsilon(x)| \leq C\left( 1 + \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}\right) \qquad\text{for}\;x\in \Omega.
-\end{equation*}
+\end{equation}
 \end{lem}
 
-\begin{rem} Using our approach, in order to relax the assumption $\mathrm{supp}(f)\subset\subset\Omega$ to $f = 0$ on $\partial\Omega$ as in Theorem \ref{main_thm1}, we need to know more about the blow up rate $C_\kappa$ in $|Du^\varepsilon(x)|\leq C_\kappa$ as $\kappa\to 0$.
-Here are some results in the literature: if $u$ solves ($f\in \mathrm{C}^1(\overline{\Omega}), f\geq 0$)
-\begin{equation*}
-\begin{cases}
-    \lambda u + |Du|^p - f(x) - \Delta u = 0&\qquad\text{in}\;\Omega,\\
-    u = +\infty&\qquad\text{on}\;\partial\Omega
-\end{cases}
-\end{equation*}
-then we can have a better bound in a priori estimate (\cite{lions_quelques_1985}) 
-\begin{equation*}
-    |Du(x)| \leq \frac{C}{d(x)^{\alpha+1}}, \qquad x\in \Omega
-\end{equation*}
-where $\alpha = \frac{2-p}{p-1}$, while (\cite{alessio_asymptotic_2006}) gives an asymptotic behavior
-\begin{equation*}
-    \lim_{d(x)\to 0} \Big(Du(x)\cdot Dd(x)\Big)d(x)^{\alpha+1} = (\alpha+1)^{\alpha+1}\mathfrak{n}(x_0).
-\end{equation*}
-Here $\underline{x}$ is the unique projection of $x$ (near the boundary) onto $\partial\Omega$ and $\mathfrak{n}(x_0)$ is the unit outward normal vector of $\Omega$ at $x_0$. 
-\paragraph{\textbf{Our version with $\varepsilon$}}
-In our version, the problem with $\varepsilon$, we have 
-\begin{equation*}
-\begin{cases}
-    \lambda u^\varepsilon + |Du^\varepsilon|^p - f(x) - \varepsilon\Delta u^\varepsilon = 0&\qquad\text{in}\;\Omega,\\
-    u^\varepsilon = +\infty&\qquad\text{on}\;\partial\Omega
-\end{cases}
-\end{equation*}
-we can obtain that
-\begin{equation}\label{eq:yy}
-    |Du^\varepsilon(x)| \leq \frac{C}{d(x)^{\alpha+1}}, \qquad x\in \Omega
-\end{equation}
+\begin{proof}[Proof of Lemma \ref{lem:boundDu^eps}] %Let us consider $0<\varepsilon < \min\{4\delta_0,1\}$. 
+Let us fix $x_0 \in \Omega\backslash \Omega_{\delta_0}$ and let $\delta = \frac{1}{4}d(x_0)$. Let 
+\begin{equation*}
+    v(x) = \frac{1}{\delta}u^\varepsilon(x_0+\delta x), \qquad x\in B(0,2).   
+\end{equation*}
+We have $Dv(x) = Du^\varepsilon(x_0+\delta x)$ and $\Delta v(x) = \delta \Delta u^\varepsilon(x_0+\delta x)$ for $x\in B(0,2)$. The equation for $v$ is given by
+\begin{equation*}
+    \delta v(x) + |Dv(x)|^p - \tilde{f}(x) - \frac{\varepsilon}{\delta}\Delta v(x) = 0 \qquad\text{in}\;B(0,2),
+\end{equation*}
+where $\tilde{f}(x) = f(x_0+\delta x)$ defined on $\overline{B(0,2)}$. We note that $\Vert \tilde{f}\Vert_{L^\infty}\leq \Vert f\Vert_{L^\infty}$ and 
+\begin{equation*}
+    B(x_0,2\delta)\subset \Omega_{2\delta}\subset\subset\Omega.
+\end{equation*}
+By Lemma \ref{lem:super_refined}, there is a constant $C$ independent of $\delta,\varepsilon$ such that 
+\begin{equation*}
+     \delta\Vert v\Vert_{L^\infty\left(B\left(0,\frac{3}{2}\right)\right)} \leq \Vert u^\varepsilon\Vert_{L^\infty(\Omega_{2\delta}))} \leq C\left(1 + \frac{\varepsilon^{\alpha+1}}{\delta^\alpha}\right).
+\end{equation*}
+Note that $p = \frac{\alpha+2}{\alpha+1}$ and $\alpha+1 = \frac{1}{p-1}$, we apply Theorem 3.1 in \cite{Armstrong2015} to obtain 
+\begin{equation*}
+\begin{split}
+    \sup_{x\in B(0,1)}|Dv(x)| &\leq C\left[\left(\frac{\varepsilon}{\delta}\right)^{\frac{1}{p-1}} + \left(\Vert f\Vert_{L^\infty}+\delta \Vert v\Vert_{L^\infty\left(B\left(0,\frac{3}{2}\right)\right)}\right)^{\frac{1}{p}}\right] \\
+    &\leq C\left[\left(\frac{\varepsilon}{\delta}\right)^{\alpha+1} + \left(1+\frac{\varepsilon^{\alpha+1}}{\delta^\alpha}\right)^{\frac{\alpha+1}{\alpha+2}}\right]\leq C \left(1+\left(\frac{\varepsilon}{\delta}\right)^{\alpha+1}\right).
+    %&\leq C\left[\left(\frac{\varepsilon}{\delta}\right)^{\alpha+1} + \left(1+\left(\frac{\alpha+1}{\alpha+2}\right)\frac{\varepsilon^{\alpha+1}}{\delta^\alpha}\right)\right] \leq C\left[1+2\left(\frac{\varepsilon}{\delta}\right)^{\alpha+1} \right]
+\end{split}
+\end{equation*}
+%where we use Bernoulli's inequality and the fact that $\delta \leq 1$. 
+Replace $\delta = \frac{1}{4}d(x_0)$ we obtain
+\begin{equation*}
+    |Du^\varepsilon(x_0)| = |Dv(0)| \leq C\left(1+ \left(\frac{\varepsilon}{d(x_0)}\right)^{\alpha+1}\right).
+\end{equation*}
+In other words, we obtain \eqref{eq:es_final} for all $x\in \Omega\backslash\Omega_{\delta_0}$.
+From Theorem \ref{thm:grad_1} there exists a constant $C$ independent of $\varepsilon$ such that $|Du^\varepsilon(x)|\leq C$ for all $x\in \Omega_{\delta_0}$ and thus the proof is complete.
+\end{proof}
+
+\begin{rem} As a consequence, the constant $C_{\frac{\kappa}{2}}$ in Theorem \ref{thm:rate_doubling2} satisfies
+\begin{equation*}
+    C_{\frac{\kappa}{2}} \leq C\left(1+\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1}\right)
+\end{equation*}
+where $C$ is a constant independent of $\varepsilon$ and $\kappa$.
+\end{rem}
+
+\begin{proof}[Proof of Theorem \ref{main_thm2}] Let $L$ be the Lipschitz constant of $f$.
+For $0 < \kappa <\delta_0$ we define $f_\kappa$ as in the proof of Theorem \ref{main_thm1}, where $\mathrm{supp}(f_\kappa)\subset\Omega_{\frac{\kappa}{2}}$ and
+\begin{equation*}
+    0\leq f - f_\kappa \leq L\kappa.
+\end{equation*}
+Let $u^\varepsilon_\kappa\in \rmC^2(\Omega)\cap \rmC(\overline{\Omega})$ be the solution to \eqref{eq:PDEeps} and $u_k$ be the solution to \eqref{eq:PDE0} with $f$ being replaced by $f_k$, respectively.
+By the same argument as in the proof of Theorem \ref{main_thm1}, we have
+\begin{equation*}
+  0\leq u^\varepsilon(x) - u^\varepsilon_\kappa(x)\leq L\kappa \qquad\text{for}\;x\in \Omega
+\end{equation*}
 and
-\begin{equation}\label{eq:xx}
-    \lim_{d(x)\to 0} \Big(Du^\varepsilon(x)\cdot Dd(x)\Big)d(x)^{\alpha+1} = (\alpha+1)^{\alpha+1}\mathfrak{n}(x_0)\varepsilon^{\alpha+1}.
-\end{equation}
-
-\paragraph{\textbf{The result that we need for Theorem \ref{main_thm2}}} The ideal estimate we are expecting is, there exists a constant $C$ independent of $\varepsilon$ such that
-\begin{equation*}
-|Du^\varepsilon(x)| \leq C + \frac{C\varepsilon^{\alpha+1}}{d(x)^{\alpha+1}} \qquad\text{for}\;x\in \Omega.
-\end{equation*}
-This estimate can be proven following from a priori estimate $|Du^\varepsilon(x)|\leq C_\delta$ for $x\in \Omega_\delta$ and \eqref{eq:xx} if the limit in \eqref{eq:xx} is uniform in $\varepsilon$.
-
-\paragraph{\textbf{Difficulty}} However, \eqref{eq:xx} is not uniform in $\varepsilon$ (at least from the method the authors Porretta and Veron use in \cite{alessio_asymptotic_2006}).
-\end{rem}
-
-%\begin{proof}[Proof of Theorem \ref{main_thm2}] Define
-
-%\end{proof}
+\begin{equation*}
+    0\leq u(x) - u_\kappa(x)\leq L\kappa \qquad\text{for}\;x\in \Omega.
+\end{equation*}
+By Theorem \ref{thm:rate_doubling2} and Lemma \ref{lem:boundDu^eps} we have 
+\begin{equation*}
+\begin{aligned}
+    u_\kappa^\varepsilon(x) - u_\kappa(x) &\leq\frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} + C\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1} \left(1+ \left(\frac{\varepsilon}{\kappa}\right) +\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1} +\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2}\right) + nc\varepsilon,  &\quad p <2, \\
+    u_\kappa^\varepsilon(x) - u_\kappa(x) & \leq \nu \varepsilon \log\left( \frac{1}{d(x)}\right)+C\left(\frac{\varepsilon}{\kappa}\right) \left(1+\frac{\varepsilon}{\kappa}\right)+ nc \varepsilon, &\quad p=2.
+\end{aligned}
+\end{equation*}
+Therefore
+\begin{equation*}
+    u^\varepsilon(x)-u(x)\leq 2L\kappa + \Big(u^\varepsilon_\kappa(x) - u_\kappa(x)\Big) \leq 2L\kappa+C_{\kappa}\varepsilon
+\end{equation*}
+where we use the rate $\mathcal{O}(\varepsilon)$ from Theorem \ref{thm:rate_doubling2} as $f_\kappa$ is compactly supported.
+
+\end{proof}
 
@@
 
-\subsection*{Asymptotic behavior of derivatives}
-We denote by $\nu(x)$ the outward unit normal vector at any point $x\in \partial{\Omega}$ and $\tau(x)$ the unitary tangent vector defined on $\partial{\Omega}$, i.e., $\nu(x)\cdot\tau(x) = 0$.
-We start by considering the case $p=2$.
-\begin{equation*}
-    \begin{cases}
-    -\Delta u 
-    \end{cases}
-\end{equation*}
-
 \subsection*{Existence and wellposedness of solution}
@@
 \begin{equation*}
-    |Du (x)|^p = \frac{(\alpha C_\varepsilon)^p }{d(x)^{p(\alpha+1)}}|D d(x)|^p \qquad\text{and}\qquad\varepsilon\Delta u(x) = \frac{\varepsilon C_\varepsilon\alpha(\alpha+1)}{d(x)^{\alpha+2}}|D d(x)|^2 - \frac{\varepsilon C_\varepsilon\alpha}{d(x)^{\alpha+1}}\Delta d(x).
+\begin{split}
+    |Du (x)|^p &= \frac{(\alpha C_\varepsilon)^p }{d(x)^{p(\alpha+1)}}|D d(x)|^p,\\
+    \varepsilon\Delta u(x) &= \frac{\varepsilon C_\varepsilon\alpha(\alpha+1)}{d(x)^{\alpha+2}}|D d(x)|^2 - \frac{\varepsilon C_\varepsilon\alpha}{d(x)^{\alpha+1}}\Delta d(x).
+\end{split}
 \end{equation*}

### 2021-07-15 Drafts and notes/Draft_07.tex
Almost final

--- 2021-07-15 Drafts and notes/Draft_06.tex
@@
 \begin{abstract}
-We investigate the convergence rate in the vanishing viscosity process of  the solution to the state-constraint Hamilton-Jacobi equation.
-We show by a simple proof that for Lipschitz data that vanish on the boundary, the rate of convergence is $\mathcal{O}(\sqrt{\varepsilon})$ with a specific boundary layer.
-Moreover, the rate can be improved to $\mathcal{O}(\varepsilon)$ in the region with zero data.
-The proof relies on the doubling variable method and the construction of a specific barrier.
+We investigate the convergence rate in the vanishing viscosity process of the solutions to the state-constraint Hamilton-Jacobi equations.
+We give two different proofs of the fact that, for Lipschitz data that vanish on the boundary, the rate of convergence is $\mathcal{O}(\sqrt{\varepsilon})$ in the interior.
+Moreover, the one-sided rate can be improved to $\mathcal{O}(\varepsilon)$ for compactly supported data.
+Our approach relies on deep understanding of the blow-up behavior near the boundary and semiconcavity of the solutions.
 \end{abstract}
@@
 \date{\today}
-\keywords{first-order Hamilton--Jacobi equations; second-order Hamilton--Jacobi equations; state-constraint problems; optimal control theory; rate of convergence; viscosity solutions.}
+\keywords{first-order Hamilton--Jacobi equations; second-order Hamilton--Jacobi equations; state-constraint problems; optimal control theory; rate of convergence; viscosity solutions; semiconcavity; boundary layer.}
 \subjclass[2010]{
@@
 \subsection{Settings} Let $\Omega$ be an open, bounded and connected domain in $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary, $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
-Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ (see \cite{Lasry1989}) be the solution to
+For $\varepsilon>0$, let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ (see \cite{Lasry1989}) be the solution to
  \begin{equation}\label{eq:PDEepsa}
@@
 \end{equation}
- where $H:\R^n\to\R^n$ is a continuous Hamiltonian.
-Solution that blows up uniformly on the boundary is also called \emph{large solution}.
+ where $H:\R^n\to\R^n$ is a given continuous Hamiltonian.
+The solution that blows up uniformly on the boundary is also called a \emph{large solution}.
 A typical subquadratic Hamiltonian that has been considered in the literature is $H(\xi) = |\xi|^p$ for $\xi\in \R^n$ where $1<p\leq 2$.
@@
 \end{equation}
-When $1<p\leq 2$, equation \eqref{eq:PDEeps} describes the value function associated with a minimization problem in stochastic optimal control with state constraint (\cite{Lasry1989}).
+When $1<p\leq 2$, equation \eqref{eq:PDEeps} describes the value function associated with a minimization problem in stochastic optimal control with state constraint (\cite{fabbri_stochastic_2017, Lasry1989}.
 We are interested in studying the asymptotic behavior of $\{u^\varepsilon\}_{\varepsilon>0}$ as $\varepsilon\rightarrow 0^+$.
@@
 \end{equation}
-as is described in the framework of viscosity solution.
+as is described in the framework of the theory of viscosity solutions.
 Equation \eqref{eq:PDE0} admits a unique viscosity solution in the space $\rmC(\overline{\Omega})$, which is also the maximal viscosity subsolution among all the viscosity subsolutions in $\rmC(\overline{\Omega})$(see \cite{Capuzzo-Dolcetta1990,Soner1986}).
@@
 In this paper, we investigate the rate of convergence of $u^\varepsilon \to u$ as $\varepsilon\to 0^+$.
-What is intriguing and delicate here is the narrow boundary layer behavior near $\partial \Omega$.
-\subsection{Assumptions} We will always assume $\Omega$ is an open, bounded and connected domain in $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary satisfying either %$H:\mathbb{R}^n\times \mathbb{R}^n$ is a continuous Hamiltonian.
+What is intriguing and delicate here is the blow-up behavior of $u^\varepsilon$ in a narrow strip near $\partial \Omega$ as $\varepsilon\to 0^+$.
+This is often called the boundary layer theory in the literature.
+
+Note that a comparison principle holds for \eqref{eq:PDE0} since we always assume $\Omega$ is an open, bounded and connected domain in $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary (\cite{Capuzzo-Dolcetta1990,Soner1986}).
+Equation \eqref{eq:PDEeps} follows the setting of \cite{Lasry1989}, where the specific structure of the Hamiltonian $H(x,\xi) = |\xi|^p - f(x)$ enables more explicit estimates for the solution of \eqref{eq:PDEeps}.
+
+%\subsection{Assumptions} We will always assume $\Omega$ is an open, bounded and connected domain in $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary.
+Essentially the domain is assumed so that a comparison principle holds for \eqref{eq:PDE0}.
+
 %\begin{itemize}    
-%    \item[$\mathrm{(A1)}$] $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
+%    \item[(A1)] There exists a universal pair of positive numbers $(r,h)$ and $\eta\in \mathrm{BUC}(\overline{\Omega};\mathbb{R}^n)$ such that $B(x+t\eta(x), rt)\subset\Omega$ for all $t\in (0,h]$,
+%    \end{itemize}
+%    or
+%    \begin{itemize}
+%    \item[(A2)] $\Omega$ is a bounded star-shaped (with respect to the origin) open subset of $\mathbb{R}^n$ such that for some $\kappa > 0$,
+%    \begin{equation*}
+%        \mathrm{dist}(x,\overline{\Omega}) \geq \kappa r \qquad\text{for all}\; x\in (1+r) \partial\Omega, \;\text{for all}\;r>0.
+%    \end{equation*}
 %\end{itemize}
-%    The following assumptions on $\Omega$ will also be used.
-\begin{itemize}    
-    \item[(A1)] There exists a universal pair of positive numbers $(r,h)$ and $\eta\in \mathrm{BUC}(\overline{\Omega};\mathbb{R}^n)$ such that $B(x+t\eta(x), rt)\subset\Omega$ for all $t\in (0,h]$,
-    \end{itemize}
-    or
-    \begin{itemize}
-    \item[(A2)] $\Omega$ is a bounded star-shaped (with respect to the origin) open subset of $\mathbb{R}^n$ such that for some $\kappa > 0$,
-    \begin{equation*}
-        \mathrm{dist}(x,\overline{\Omega}) \geq \kappa r \qquad\text{for all}\; x\in (1+r) \partial\Omega, \;\text{for all}\;r>0.
-    \end{equation*}
-\end{itemize}
-Equation \eqref{eq:PDEeps} follows the setting of \cite{Lasry1989}, where the specific structure of the Hamiltonian $H(x,\xi) = |\xi|^p - f(x)$ enables more explicit estimates for the solution of \eqref{eq:PDEeps}.
-Assumption $\mathrm{(A1)}$ or $\mathrm{(A2)}$ guarantees that a comparison principle holds for the state-constraint problem \eqref{eq:PDE0}.
+
+ %Assumption $\mathrm{(A1)}$ or $\mathrm{(A2)}$ guarantees that a comparison principle holds for the state-constraint problem \eqref{eq:PDE0}.
 Assumption $\mathrm{(A1)}$, which holds for any smooth bounded domain, was first studied in \cite{Soner1986}.
-Assumption $\mathrm{(A2)}$ was posed and studied in \cite{Capuzzo-Dolcetta1990}.
+Assumption $\mathrm{(A2)}$ was posed and studied in \cite{Capuzzo-Dolcetta1990} and the references therein.
 %We list the assumptions on a general Hamiltonian as follow.
@@
 \subsection{Relevant literature} There is a
-vast amount of work in the literature on large solutions and second-order viscosity solutions with state constraints.
-The problem \eqref{eq:PDEeps} is first studied in \cite{Lasry1989} and subsequently many works have been done in understanding deeper the properties of solutions.
-%For instance, \textcolor{red}{(more references here.)}.
-We refer the readers to \cite{ Porretta_a,alessio_asymptotic_2006,Bandle_1994, marcus_existence_2003} and the references therein.
-The time-dependent version of \eqref{eq:PDEepsa} is also studied by many works, for instance \cite{barles_generalized_2004,barles_large_2010,leonori_local_2011,moll_large_2012} and the references therein.
-
-In terms of rate of convergence, up to our knowledge such a question has not been studied in the literature.
-For the case \eqref{eq:PDEeps} is equipped with the Dirichlet boundary condition, a rate $\mathcal{O}(\sqrt{\varepsilon})$ is well known with multiple proofs (see \cite{Bardi1997,crandall1984, tran_hamilton-jacobi_2021}).
-We believe part of the reason why the problem is intriguing is that the blowing up behavior of the solution is complicated and deserves further investigation.
-
-\subsection{Main results} The main result of the paper is the following theorem.
+vast amount of work in the literature on viscosity solutions with state constraints and large solutions.
+We would like to first mention that the problem \eqref{eq:PDE0} with general Hamiltonian is a huge subject of research interest, started with the pioneer work \cite{Soner1986} (see also \cite{ishii_new_1996,ishii_class_2002}).
+Some of the recent work related to the asymptotic behavior of solutions of \eqref{eq:PDE0} can be found in \cite{ishii_vanishing_2017,kim_state-constraint_2020,mitake_asymptotic_2008,tu2021vanishing}.
+The problem \eqref{eq:PDEeps} is first studied in \cite{Lasry1989} and subsequently many works have been done in understanding deeper the properties of solutions (see \cite{ Porretta_a,alessio_asymptotic_2006,Bandle_1994, marcus_existence_2003} and the references therein).
+The time-dependent version of \eqref{eq:PDEepsa} is also studied by many works, for instance, \cite{barles_generalized_2004,barles_large_2010,leonori_local_2011,moll_large_2012} and the references therein.
+%For deterministic and stochastic optimal control problems with state constraints, we refer the read to [\textcolor{blue}{NEED CITATION (Ishii, \cite{}}] and the references therein.
+
+In terms of rate of convergence, that is, the convergence rate of $u^\varepsilon\to u$ as $\varepsilon\to 0^+$, to the best of our knowledge, such a question has not been studied in the literature.
+For the case where \eqref{eq:PDEeps} is equipped with the Dirichlet boundary condition, a rate $\mathcal{O}(\sqrt{\varepsilon})$ is well known with multiple proofs (see \cite{Bardi1997,crandall1984, tran_hamilton-jacobi_2021}).
+We believe part of the reason why the problem is intriguing is that the blow-up behavior of the solutions near the boundary of $\Omega$ is complicated and deserves further investigation.
+
+\subsection{Main results} The main results of the paper are the following theorems.
 
@@
 Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
-Then there exists a constant $C$ such that for $x\in \Omega$,
+Then there exists a constant $C$ independent of $\varepsilon\in (0,1)$ such that for $x\in \Omega$,
 \begin{align*}
@@
 If $f = 0$ on $\partial\Omega$, we are able to approximate $f$ \emph{uniformly} in $L^\infty(\Omega)$ by a sequence of compactly supported functions, where a convergence rate of $u^\varepsilon-u$ is easier to obtain.
-Indeed, using the usual doubling variable technique, it is natural to consider the doubling variable for
+Indeed, it is natural to consider the doubling variable method with
 \begin{equation}\label{heur1}
-    u^\varepsilon(x) - \frac{C\varepsilon^{\alpha+1}}{d(x)^{\alpha}}
-\end{equation}
-and $u(x)$, where $C\varepsilon^{\alpha+1}d(x)^{-\alpha}$ is the leading order term in the asymptotic expansion of $u^\varepsilon(x)$ as $\mathrm{dist}(x,\partial\Omega)\to 0$.
-After taking derivative, heuristically, \eqref{heur1} becomes
+    \psi^\varepsilon(x) =  u^\varepsilon(x) - \frac{C_\alpha\varepsilon^{\alpha+1}}{d(x)^{\alpha}}
+\end{equation}
+and $u(x)$, where $d(x)$ is a $\mathrm{C}^2$ extension of the distance function $\mathrm{dist}(x,\partial\Omega)$, $\alpha = (2-p)/(p-1)$ and $C_\alpha\varepsilon^{\alpha+1}d(x)^{-\alpha}$ is the leading order term in the asymptotic expansion of $u^\varepsilon(x)$ as $d(x) \to 0^{+}$.
+If we take the derivative of \eqref{heur1} formally, it becomes
 \begin{equation}\label{heur2}
-    Du^\varepsilon(x) + C\alpha \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}Dd(x).
-\end{equation}
-We show in Lemma \ref{lem:boundDu^eps} that \eqref{heur2} gives the correct behavior of $Du^\varepsilon$ where $\alpha = \frac{2-p}{p-1}$. \\
-\noindent
-\textcolor{blue}{
-To get a useful estimate by the doubling variable, at the maximum point $x_0$ of $u^\varepsilon(x) - u(x)$, we must have $d(x_0)\approx \varepsilon^{\gamma}$ for $\gamma<1$ so that the latter term in \eqref{heur2} vanishes as $\varepsilon\to 0$.
-It turns out that such an estimate is quite delicate.
-We overcome this difficulty by decomposing the solution into an inside part and an outside part near the boundary, where we have reduced to the case of $f=0$.}
+    D\psi^\varepsilon(x) =  Du^\varepsilon(x) + C_\alpha\alpha \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}Dd(x).
+\end{equation}
+We will see that $D\psi^\varepsilon(x)$ is uniformly bounded if $d(x)\geq \varepsilon$ (Lemma \ref{lem:boundDu^eps}). Indeed, 
+\begin{equation*}
+    -C_\alpha \alpha \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}Dd(x)    
+\end{equation*}
+is more or less the leading order term in the asymptotic expansion of $Du^\varepsilon$ near $\partial\Omega$.
+Heuristically, this means that the boundary layer is $\mathcal{O}(\varepsilon)$ from the boundary.
+
+However, to get a useful estimate by the doubling variable, at the maximum point $x_0$ of $\psi^\varepsilon(x) - u(x)$, we need to have $d(x_0)\geq \varepsilon^{\gamma}$ for $\gamma<1$ so that the latter term in \eqref{heur2} vanishes as $\varepsilon\to 0^+$.
+In the other case where $d(x_0) < \varepsilon^{\gamma}$, we introduce a new localization idea, that is, we construct a blow-up solution in the ball of radius $\varepsilon^\gamma$ from the boundary.
+Finally, a technical (and common for the doubling variable) computation leads to $\gamma = 1/2$.
+
+%Essentially we avoid the boundary layer here.
+
+%In the complicated case that $x_0$ is in the boundary layer, we introduce a new localization idea, that is, we construct a blow-up solution in the ball of radius $\varepsilon$.
+%\textcolor{red}{(Actually, I am thinking should it be the ball of radius $\sqrt{\varepsilon}$ from the boundary? Since we choose $\kappa=\sqrt{\varepsilon}$.)}
 \end{rem}
 
-Using the convexity of $|\xi|^p$, we can avoid the doubling variable route to get a better one-sided estimate for compactly supported $f$.
-Such an one-sided rate is well-known for the case of vanishing discount with zero Dirichlet boundary condition (see \textcolor{blue}{NEED CITATION}).
-
-\begin{thm}\label{main_thm2} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
-Assume that $1 < p\leq 2$ and $f$ is a compactly supported Lipschitz function defined on $\overline{\Omega}$.
+As a different approach, the convexity of $|\xi|^p$ and the semiconcavity of the solution to \eqref{eq:PDE0} give us a better one-sided $\mathcal{O}(\varepsilon)$ estimate for compactly supported $f$.
+Such an one-sided $\mathcal{O}(\varepsilon)$ rate is well known for the case of the Dirichlet boundary problem (see \cite{Bardi1997,tran_hamilton-jacobi_2021}).
+Moreover, this approach provides us with a new proof of the $\mathcal{O}(\sqrt{\varepsilon})$ rate in Theorem \ref{main_thm1} without using the doubling variable method.
+
+%As a different approach, if we utilize the convexity of $|\xi|^p$ and the semiconcavity of the solution to \eqref{eq:PDE0} then we have a proof of the $\mathcal{O}(\sqrt{\varepsilon})$ rate without using the doubling variable method.
+More importantly, this approach gives a better one-sided $\mathcal{O}(\varepsilon)$ estimate for compactly supported $f$.
+Such an one-sided $\mathcal{O}(\varepsilon)$ rate is well known for the case of Dirichlet boundary problem (see \cite{Bardi1997,tran_hamilton-jacobi_2021}).
+
+\begin{thm}[One-sided $\mathcal{O}(\varepsilon)$ rate for compactly supported data]\label{thm:rate_doubling2} Assume that $f\in \mathrm{C}^2_c(\Omega)$ such that $\mathrm{supp}(f)\subset\Omega_\kappa$ where  $\Omega_\kappa := \{x\in \Omega: \mathrm{dist}(x,\Omega) > \kappa\}$ for some fixed $\kappa \in (0, \delta_{0})$.
 Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
-Then there exists a constant $C$ such that for $x\in \Omega$,
-\begin{align*}
-    &-C\sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x)\leq  C\varepsilon \left(\frac{\varepsilon}{d(x)}\right)^{\frac{2-p}{p-1}} &\qquad\text{if}\; p < 2,\\
-    &-C\sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x)\leq  \varepsilon|\log(d(x))| &\qquad\text{if}\; p = 2.
-\end{align*}
+Then there exists a constant $C$ independent of $\varepsilon$ and $\kappa$ such that
+\begin{equation*}
+\begin{aligned}
+    u^\varepsilon(x) - u(x) &\leq\frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} + C\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1} \left(1+ \left(\frac{\varepsilon}{\kappa}\right) +\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1} +\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2}\right) + nc\varepsilon,  &\quad p <2, \\
+    u^\varepsilon(x) - u(x) & \leq \nu \varepsilon \log\left( \frac{1}{d(x)}\right)+C\left(\frac{\varepsilon}{\kappa}\right) \left(1+\frac{\varepsilon}{\kappa}\right)+ nc \varepsilon, &\quad p=2.
+\end{aligned}
+\end{equation*}
+where $c = \max \big\lbrace  D_{\xi\xi}f(x): |\xi|=1, x\in \overline{\Omega} \big\rbrace\geq 0$.
 \end{thm}
 
-\subsection*{Organization of the paper} In Section 2, we state some preliminary results.
-In Section 3, we prove the main result on the rate of convergence.
-The proofs of some lemmas are presented in Appendix.
+\begin{rem} As mentioned, Theorem \ref{thm:rate_doubling2} implies Theorem \ref{main_thm1}.
+While the second approach looks more powerful, we need to know more about the gradient bound $Du^\varepsilon$ (Lemma \ref{lem:boundDu^eps}).
+On the other hand, the first approach using doubling variable is relatively simple and does not require any explicit asymptotic behavior of $Du^\varepsilon$ except the fact that it is locally bounded.
+At this moment, we do not know how to generalize to the more general case where $f = 0$ on $\partial\Omega$ in Theorem \ref{thm:rate_doubling2}.
+\end{rem}
+
+\subsection*{Organization of the paper} Section 2 contains some preliminary results.
+The proof of Theorem \ref{main_thm1} is given in Section 3.
+Then in Section 4, we give the proof of Theorem \ref{thm:rate_doubling2} and how Theorem \ref{main_thm1} follows from Theorem \ref{thm:rate_doubling2}.
+Finally, the proofs of some useful lemmas are presented in Appendix.
 
 \section{Preliminaries}\label{sec:prelim} 
-\subsection{Setting and simplifications} Let $\Omega$ be an open, bounded and connected subset of $\mathbb{R}^n$ with boundary $\partial\Omega$ of class $C^2$.
+Let $\Omega$ be an open, bounded and connected subset of $\mathbb{R}^n$ with boundary $\partial\Omega$ of class $C^2$.
 For small $\delta>0$, we denote $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) > \delta\}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$.
@@
 %The distance function is of class $\mathrm{C}^2$ in the region where $0<\mathrm{dist}(x,\partial\Omega) < \delta_0$. 
-We will simply write $\delta_0$ instead of $\delta_{0,\Omega}$ if the underlying domain is understood.
+We will simply write $\delta_0$ instead of $\delta_{0,\Omega}$ when the underlying domain is understood.
 \end{defn}
@@
 \end{equation}
-Note that $|D d(x)| = 1$ in the viscosity sense (and thus in classical sense) in $\Omega^{\delta_0}\backslash \Omega_{\delta_0}$. Let 
+Note that $d(x) = \mathrm{dist}(x,\partial\Omega)$ and $|D d(x)| = 1$ in the classical sense in $\Omega^{\delta_0}\backslash \Omega_{\delta_0}$. Let 
 \begin{equation}\label{boundond}
@@
 
-\subsection{Local gradient estimate} Let $\Omega$ be an open, bounded subset of $\R^n$, $\varepsilon \in (0,1)$ and $p>1$.
-We state a priori estimate for $\rmC^2$ solutions of \eqref{eq:PDEeps} (\cite[Appendix]{Lasry1989}).
+\subsection{Local gradient estimate} For $\varepsilon \in (0,1)$ and $p>1$, we state a priori estimate for $\rmC^2$ solutions to \eqref{eq:PDEeps} (\cite[Appendix]{Lasry1989}).
 Since we are working with nice solutions, the proof is relatively simple using the classical Bernstein method (\cite{bernstein_sur_1910}).
-We provide a proof in Appendix for the readers' convenience.
+We provide a proof in Appendix for the reader's convenience.
 
@@
 
-\subsection{Well-posedness of large solution} In this section, we recall the existence and the uniqueness of solutions to \eqref{eq:PDEeps} for $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
+\subsection{Well-posedness of \eqref{eq:PDEeps}} In this section, we recall the existence and the uniqueness of solutions to \eqref{eq:PDEeps} for $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
 In fact, the assumption of $f$ can be relaxed to $f\in L^\infty(\Omega)$ (\cite{Lasry1989}).
@@
 \end{itemize}
-Furthermore, $u^\varepsilon$ is the maximal subsolution among all the subsolutions $v\in W^{2,r}(\Omega)$ (for all $r>0$) of \eqref{eq:PDEeps}.
+Furthermore, $u^\varepsilon$ is the maximal subsolution among all the subsolutions $v\in W^{2,r}_{\mathrm{loc}}(\Omega)$ for all $r\in [1,\infty)$ of \eqref{eq:PDEeps}.
 \end{thm}
@@
 More results on the behavior of the gradient of $u^\varepsilon$ can be found in \cite{alessio_asymptotic_2006} and Lemma \ref{lem:boundDu^eps}, where we show $|Du^\varepsilon|\leq C + C\left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}$.
-
-\subsection{Convergence result} We first state the following Lemma (\cite{Capuzzo-Dolcetta1990}), which characterizes the solution to the first-order state-constraint  equation \eqref{eq:PDE0}.
-\begin{lem}\label{lem:max} Let $u\in \rmC(\overline{\Omega})$ be a viscosity subsolution of \eqref{eq:PDE0} such that, for any viscosity subsolution $v\in \rmC(\overline{\Omega})$ of \eqref{eq:PDE0} one has $v\leq u$ on $\overline{\Omega}$.
+We believe Lemma \ref{lem:boundDu^eps} is new in the literature.
+
+\subsection{Convergence results} We first state the following Lemma (\cite{Capuzzo-Dolcetta1990}), which characterizes the solution to the first-order state-constraint  equation \eqref{eq:PDE0}.
+\begin{lem}\label{lem:max} Let $u\in \rmC(\overline{\Omega})$ be a viscosity subsolution of \eqref{eq:PDE0} such that, for any viscosity subsolution $v\in \rmC(\overline{\Omega})$ of \eqref{eq:PDE0}, one has $v\leq u$ on $\overline{\Omega}$.
 Then $u$ is a viscosity supersolution of \eqref{eq:PDE0} on $\overline{\Omega}$.
 \end{lem}
-\noindent A proof of Lemma \ref{lem:max} is given in Appendix for the readers' convenience.
+\noindent Again, a proof of Lemma \ref{lem:max} is given in Appendix for the reader's convenience.
 
@@
 As $m\to \infty$, we obtain $  u^\varepsilon \geq \min_\Omega f$.
-The inequality $  u\geq \min_{\Omega}f$ follows from the comparison principle of \eqref{eq:PDE0} applied to the supersolution $u$ on $\overline{\Omega}$ and the subsolution $\varphi(x)$ in $\Omega$.
-\end{proof}
-
-We present a simple proof of the convergence $u^\varepsilon \to u$ using Lemma \ref{lem:max} for the reader's convenience. See also \cite[Theorem VII.3]{Capuzzo-Dolcetta1990}.
-\begin{thm}[Vanishing viscosity]\label{thm:qual} Assume $\mathrm{(A1)}$ or $\mathrm{(A2)}$.
+The inequality $  u\geq \min_{\Omega}f$ follows from the comparison principle of \eqref{eq:PDE0} applied to the supersolution $u$ on $\overline{\Omega}$ and the subsolution $\varphi$ in $\Omega$.
+\end{proof}
+
+We present here a simple proof of the convergence $u^\varepsilon \to u$ using Lemma \ref{lem:max}. See also \cite[Theorem VII.3]{Capuzzo-Dolcetta1990}.
+\begin{thm}[Vanishing viscosity]\label{thm:qual}.
 Let $u^\varepsilon$ be the solution to \eqref{eq:PDEeps}.
@@
 \end{equation}
-By the Arzel\'a--Ascoli theorem, there exists a subsequence $\varepsilon_j\to 0$ and a function $u\in \rmC(\Omega)$ such that $u^{\varepsilon_j}\to u$ locally uniformly in $\Omega$.
-By the stability of viscosity solution, we easily deduce that
+By the Arzel\`a--Ascoli theorem, there exists a subsequence $\varepsilon_j\to 0$ and a function $u\in \rmC(\Omega)$ such that $u^{\varepsilon_j}\to u$ locally uniformly in $\Omega$.
+By the stability of viscosity solutions, we easily deduce that
 \begin{equation}\label{eq:u0int}
@@
 \end{equation}
-Thus, we can extend $u$ uniquely to $u\in \rmC(\overline{\Omega})$. We will use Lemma \ref{lem:max} to show that $u$ is a supersolution of \eqref{eq:PDE0} on $\overline{\Omega}$.
+Thus, we can extend $u$ uniquely to $u\in \rmC(\overline{\Omega})$. We use Lemma \ref{lem:max} to show that $u$ is a supersolution of \eqref{eq:PDE0} on $\overline{\Omega}$.
 
@@
       v_\delta^\varepsilon(x) + |Dv_\delta^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v_\delta^\varepsilon(x) &\qquad\text{in}\;\Omega_\delta,\\
-    \;\;\;\,\quad\qquad\qquad\qquad\qquad v_\delta^\varepsilon = u_\delta &\qquad \text{on}\;\partial\Omega_\delta.
+    \;\quad\qquad\qquad\qquad\qquad v_\delta^\varepsilon = u_\delta &\qquad \text{on}\;\partial\Omega_\delta.
 \end{cases}
@@
 \section{Rate of convergence}
-In this section, we focus on the rate of convergence for the case $f\in \mathrm{W}^{1,\infty}(\Omega)\cap\mathrm{C}(\overline{\Omega})$ with an extra assumption to be described.
+In this section, we focus on the rate of convergence for the case where $f\in \mathrm{W}^{1,\infty}(\Omega)\cap\mathrm{C}(\overline{\Omega})$ with an extra assumption to be described.
 By adding a constant to the solution $u^\varepsilon$ of \eqref{eq:PDEeps}, without loss of generality, we can assume the \emph{nonnegativity} of $f$, i.e.,
@@
 As a consequence, $u^\varepsilon(x),u(x)\geq 0$ for $x\in \Omega$ by Lemma \ref{lem:lower-bound}.
-Before we show any result about the rate of convergence, we would like to mention a lower bound of $u^\varepsilon - u$ and some properties of $u$ from its optimal control formula.
+Before we show any result about the rate of convergence, we would like to mention a lower bound of $u^\varepsilon - u$ and some properties of $u$ from its optimal control formulation.
 \begin{thm} Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}. Then there exists a constant $C$ independent of $\varepsilon$ such that
@@
 \end{equation*}
-It is well-known that $v^\varepsilon \to u$. Furthermore, there exists a positive constant $C$ such that 
+It is well-known that $v^\varepsilon \to u$. Furthermore, there exists a positive constant $C$ independent of $\varepsilon\in (0,1)$ such that 
 \begin{equation}\label{e:cp1}
@@
 \end{equation*}
-We can choose $C_\nu = C_3\delta_0^{-(\alpha+2)}$ to obtain $\mathcal{L}[w]\geq 0$ in this region $\{x\in \Omega_\delta:d(x)\geq \delta_0\}$. 
+We can choose $C_\nu = C_3\delta_0^{-(\alpha+2)}$ to obtain $\mathcal{L}[w]\geq 0$ in $\{x\in \Omega_\delta:d(x)\geq \delta_0\}$. 
 \smallskip
@@
 \noindent
-If $p=2$, then $\alpha = 0$. We can easily see that the same calculation holds true with $\nu = 1+K_2\delta_0$ and $C_\nu = \delta_0^{-2}\nu (\nu K_1^2 + K_1^2+ K_0K_2)$.
-\end{proof}
-
-Now we begin to present the rate of convergence for the special case where $f = C_f$ for some constant $C_f$ in $\Omega$.
-%\begin{thm}[Zero data]\label{thm:rate_doubling0} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary.
-Assume $f\equiv 0$ in $\Omega$.
-Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u \equiv 0 $ be the unique solution to \eqref{eq:PDE0}.
-If $1<p<2$ then there exists a constant $C$ such that
-%    \begin{equation*}
-%    0\leq u^\varepsilon(x)\leq C \left(\frac{ \varepsilon^{\alpha+1}}{d(x)^\alpha} + \frac{\varepsilon^{\alpha+2}}{\delta_{0,\Omega}^{\alpha+2}}\right), \qquad x\in \Omega
-%\end{equation*}
-%where $\delta_{0,\Omega}$ is defined as in \eqref{def:delta_0}.
-In particular $0\leq  u^\varepsilon(x) \leq C\varepsilon$ for $x\in \Omega_\varepsilon$, but $|u^\varepsilon(x)| = \mathcal{O}\left(\varepsilon^{\alpha+1}\right)$ on each compact subset of $\Omega$.
-%\end{thm}
-%\textcolor{orange}{(Did you mean "In particular $0\leq  u^\varepsilon(x) \leq C\varepsilon$ for $x\in \Omega_\varepsilon$" ?)}
+If $p=2$, then $\alpha = 0$. We can easily see that the similar calculation holds true with $\nu := 1+K_2\delta_0$ and $C_\nu := \delta_0^{-2}\nu (\nu K_1^2 + K_1^2+ K_0K_2)$.
+\end{proof}
+
+Now we begin to present the rate of convergence for the special case where $f = C_f$ in $\Omega$ for some constant $C_f$.
 
@@
 Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u \equiv C_f$ be the unique solution to \eqref{eq:PDE0}.
-Then there exists a constant $C$ such that
+Then there exists a constant $C$ independent of $\varepsilon\in(0,1)$ such that
     \begin{equation*}
@@
 \end{equation*}
-for $x\in \Omega$, where $\delta_{0,\Omega}$ is defined as in \eqref{def:delta_0}.
-In particular, if $1<p<2$, we have $C_f\leq u^\varepsilon(x)\leq C_f + C\varepsilon$ for $x\in \Omega_\varepsilon$ and $|u^\varepsilon(x)| = \mathcal{O}\left(\varepsilon^{\alpha+1}\right)$ on each compact subset of $\Omega$.
+for $x\in \Omega$, where $\delta_{0,\Omega}$ is defined as in \eqref{def:delta_0}. In particular, 
+\begin{itemize}
+    \item[(i)] if $1<p<2$, we have $C_f\leq u^\varepsilon(x)\leq C_f + C\varepsilon$ for $x\in \Omega_\varepsilon = \{x\in \Omega: \mathrm{dist}(x,\partial\Omega) \geq \varepsilon\}$, and
+    \item[(ii)] for any $K\subset\subset \Omega$ there hols $\Vert u^\varepsilon - u\Vert_{L^\infty(K)} \leq C\varepsilon^{\alpha+1}$ .
+\end{itemize}
 \end{thm}
-%\textcolor{orange}{(Did you mean "In particular $0\leq  u^\varepsilon(x) \leq C\varepsilon$ for $x\in \Omega_\varepsilon$" ?)}
+
 \begin{proof} Lemma \ref{lem:f=0} implies $u \equiv C_f$ in $\Omega$.
@@
 \end{proof}
+Even this special case (Theorem \ref{thm:rate_doubling0}) is new in the literate.
+As an immediate consequence, we obtain the rate of convergence on any compact subset that is disjoint from the support of $f$.
+
+\begin{cor} Assume $f$ is Lipschitz with compact support and $K$ is a connected compact subset of $\Omega$ that is disjoint from $\mathrm{supp}(f)$.
+Then there exists a constant $C = C(K)$ independent of $\varepsilon\in (0,1)$ such that
+\begin{equation*}
+     \Vert u^\varepsilon - u\Vert_{L^\infty(K)} \leq C\varepsilon^{\alpha+1}.
+\end{equation*}
+\end{cor}
+\begin{proof} We can choose an open, bounded and connected set $U$ such that $\partial U$ is $\rmC^2$ and 
+\begin{equation*}
+    K\subset\subset U \subset\subset \Omega.    
+\end{equation*}
+Let $w^\varepsilon$ be the solution to \eqref{eq:PDEeps} with $\Omega$ replaced by $U$. Then by Theorem \ref{thm:rate_doubling0}, we have
+\begin{equation*}
+    0\leq w^\varepsilon(x)\leq C\left(\varepsilon^{\alpha+1} + \varepsilon^{\alpha+2}\right), \qquad x\in K
+\end{equation*}
+where $C$ depends on $\mathrm{dist}(K, \partial U)$ and $U$.
+Recall that $u = 0$ outside the support of $f$.
+By the comparison principle in $U$, we see that $u^\varepsilon \leq w^\varepsilon$ and thus the conclusion follows.
+\end{proof}
+
+For the general case, we have the following theorem.
+
+\begin{thm}[Compactly supported data]\label{thm:rate_doubling1} Assume that $f$ is Lipschitz and is compactly supported in $\Omega_{\kappa}$.
+Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
+Then there exists a constant $C$ independent of $\varepsilon\in(0,1)$ and $\kappa$ such that
+\begin{align}
+   &-C \sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x) \leq C\left(\sqrt{\varepsilon}+\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2}\right) + \frac{\nu C_\alpha  \varepsilon^{\alpha+1}}{d(x)^\alpha}, \quad\; \qquad p<2,\label{eq:cp1}\\
+   &-C\sqrt{\varepsilon}\leq u^\varepsilon(x) - u(x) \leq C \left(\sqrt{\varepsilon}+ \left(\frac{\varepsilon}{\kappa}\right)^2\right) +  \nu \varepsilon \log\left(\frac{1}{d(x)}\right), \qquad p=2, \label{eq:cp2}
+\end{align}
+for any $x\in \Omega$. As a consequence $|u^\varepsilon(x)-u(x)|\leq C\sqrt{\varepsilon}$ for all $x\in \Omega$ with $d(x)\geq \varepsilon$.
+%Furthermore, on any compact subset $K\subset\Omega\backslash \mathrm{supp}(f)$, $|u^\varepsilon - u| = \mathcal{O}(\varepsilon)$.
+\end{thm}
+
+We state the following Lemma as a preparation.
 
@@
 \begin{equation}\label{e:delta_kappa}
-    \delta_{0,U_\kappa} \geq \frac{\kappa}{4}.
-\end{equation}
+    \delta_{0,U_\kappa} \geq \frac{\kappa}{4}
+\end{equation}
+where $\delta_{0,\Omega}$ is defined as in \eqref{def:delta_0}.
 \end{lem}
-%\textcolor{orange}{I feel "...twice continuously differentiable away from $\partial \Omega_\frac{k}{2}$" is a little ambiguous.
-How about "...twice continuoously differentiable for $x \in \Omega \setminus \overline{\Omega}_\frac{\kappa}{2}$"?}
+
 \begin{proof} By the definition of $\delta_0 = \delta_{0,\Omega}$, we have $d(x) = \mathrm{dist}(x,\partial\Omega)$ is twice continuously differentiable in the region $U_{\delta_0} = \Omega\backslash \overline{\Omega}_{\delta_0}$.
@@
 
-Next, we obtain a rate of convergence for the case where $f$ is compactly supported in $\Omega$.
-
-\begin{thm}[Compactly supported data]\label{thm:rate_doubling1} Assume that $f$ is Lipschitz and is compactly supported in $\Omega$.
-Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
-Then there exists a constant $C$ depending on the support of $f$ such that
-\begin{equation*}
-|u^\varepsilon(x) - u(x)| \leq C\sqrt{\varepsilon} \quad  \text{for} \quad x\in \Omega_{\varepsilon}.
-\end{equation*}
-Furthermore, on any compact subset $K\subset\Omega\backslash \mathrm{supp}(f)$, $|u^\varepsilon - u| = \mathcal{O}(\varepsilon)$.
-\end{thm}
-
-\begin{proof} Without loss of generality, assume that $f$ is supported in $\Omega_\kappa$ where $0<\kappa < \delta_{0}$.
+%\textcolor{red}{"Furthermore, on any compact subset $K\subset\Omega\backslash \mathrm{supp}(f)$, $|u^\varepsilon - u| = \mathcal{O}(\varepsilon)$."--It sounds like the constant inside $O(\varepsilon)$ is uniform in $K$, and do we require anything about the support of $f$?...(I will send a picture.)}
+
+\begin{proof}[Proof of Theorem \ref{thm:rate_doubling1}] Without loss of generality, assume that $f$ is supported in $\Omega_\kappa$ where $0<\kappa < \delta_{0}$.
 Let $g_\kappa = u^\varepsilon$ on $\partial\Omega_{\kappa}$. Then the solution $u^\varepsilon$ of \eqref{eq:PDEeps} also solves
@@
 \end{align}
-For simplicity, let us define
+For simplicity, define
 \begin{equation*}
@@
 \end{equation*}
-From \eqref{e:sigma} and the fact that we are considering $d(x_\sigma) \geq \frac{1}{2}\kappa$, 
+From \eqref{e:sigma} and $d(x_\sigma) \geq \frac{1}{2}\kappa$, 
 \begin{equation*}
@@
 \end{align}
-Using \eqref{e:estia} together with \eqref{e:subsln}, \eqref{e:supersln} and $|f(x_\sigma) - f(y_\sigma)|\leq C|x_\sigma - y_\sigma|\leq C\sigma$, we obtain that
+Combine \eqref{e:estia} together with \eqref{e:subsln}, \eqref{e:supersln} and $|f(x_\sigma) - f(y_\sigma)|\leq C|x_\sigma - y_\sigma|\leq C\sigma$ to obtain
 \begin{align*}
@@
 \end{align*}
-By the fact that if $\gamma\in [0,1]$ then $(1+x)^\gamma \leq 1+x^\gamma$ for $x\in [0,1]$, we can get that, as $0<p-1\leq 1$,
-\begin{equation*}
-    \left(1+\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1}\right)^{p-1} \leq 1+ \left(\frac{\varepsilon}{\kappa}\right).
-\end{equation*}
+By the fact that $(1+x)^\gamma \leq 1+x^\gamma$ for $x\in [0,1]$ and $\gamma\in [0,1]$, we know
+\begin{equation*}
+    \left(1+\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1}\right)^{p-1} \leq 1+ \left(\frac{\varepsilon}{\kappa}\right),
+\end{equation*}
+as $0<p-1\leq 1$.
 Therefore,
@@
 \end{equation*}
-where $C$ is independent of $\kappa$ and $\varepsilon$. Choosing $\sigma = \sqrt{\varepsilon}$, we obtain that (with $\kappa$ fixed)
+where $C$ is independent of $\kappa$ and $\varepsilon$. Now choose $\sigma = \sqrt{\varepsilon}$ to get (with $\kappa$ fixed)
 \begin{equation}\label{e:final1}
@@
 since $z\in \partial\Omega_k = \{x \in \Omega: d(x) = \kappa\}$.
-Thus, $|x_\sigma - z| \geq \kappa - d(x_\sigma) > \frac{1}{2}\kappa$ for all $z\in \partial\Omega_k$, which implies that $\mathrm{dist}(x_\sigma,\partial\Omega_k)>\frac{1}{2}\kappa$ and therefore $d_\kappa(x_\sigma) = d(x_\sigma)$.
+Thus, $|x_\sigma - z| \geq \kappa - d(x_\sigma) > \frac{1}{2}\kappa$ for all $z\in \partial\Omega_k$, which implies that $\mathrm{dist}(x_\sigma,\partial\Omega_k)>\frac{1}{2}\kappa$ and hence $d_\kappa(x_\sigma) = d(x_\sigma)$.
 By \eqref{annulus2} and the fact that $u \geq 0$, we have
@@
 \begin{equation*}
-    u^\varepsilon(x)-u(x)-\frac{\nu C_\alpha  \varepsilon^{\alpha+1}}{d(x)^\alpha} \leq C\sqrt{\varepsilon} +C_3\left(\frac{4\varepsilon}{\kappa}\right)^{\alpha+2}.
-\end{equation*}
-Therefore
-\begin{equation*}
-   -C \sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x) \leq C\left(\sqrt{\varepsilon}+\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2}\right) + \frac{\nu C_\alpha  \varepsilon^{\alpha+1}}{d(x)^\alpha}
-\end{equation*}
-for every $x\in \Omega$. It follows that $|u^\varepsilon(x)-u(x)| \leq C\sqrt{\varepsilon}$ for $x\in \Omega_\varepsilon$. 
-If $x\in U_k$, i.e., $f(x) = 0$, then \eqref{annulus2} gives us a better rate $\mathcal{O}(\varepsilon)$ in any compact set $K$ that is disjoint from $\mathrm{supp}(f)$. \\
+    u^\varepsilon(x)-u(x)-\frac{\nu C_\alpha  \varepsilon^{\alpha+1}}{d(x)^\alpha} \leq C\sqrt{\varepsilon} +C_3\left(\frac{4\varepsilon}{\kappa}\right)^{\alpha+2}
+\end{equation*}
+and thus \eqref{eq:cp1} follows.
 
@@
 \begin{equation*}
-    \Phi(x,y) = u^\varepsilon(x) - u(y) - \frac{C_0|x-y|^2}{\sigma} - \theta \varepsilon \mathrm{log}\left(\frac{1}{d(x)}\right), \qquad (x,y)\in \overline{\Omega}\times \overline{\Omega}
-\end{equation*}
-for some $\theta>1$.
-Similar to the previous case where $p<2$, the maximum of $\Phi$ must occur at $(x_\sigma,y_\sigma)\in \Omega\times\overline{\Omega}$ and $|x_\sigma - y_\sigma|\leq \sigma$.
+    \Phi(x,y) = u^\varepsilon(x) - u(y) - \frac{C_0|x-y|^2}{\sigma} - \nu \varepsilon \mathrm{log}\left(\frac{1}{d(x)}\right), \qquad (x,y)\in \overline{\Omega}\times \overline{\Omega}.
+\end{equation*}
+Similar to the previous case where $1<p<2$, the maximum of $\Phi$ must occur at $(x_\sigma,y_\sigma)\in \Omega\times\overline{\Omega}$ and $|x_\sigma - y_\sigma|\leq \sigma$.
 If $d(x_\sigma)\geq \frac{1}{2}\kappa$, by the subsolution test for $u^\varepsilon(x)$, we have
 \begin{align}\label{e:subslnp=2}
-    u^\varepsilon(x_\sigma)&+ \left|\frac{2C_0(x_\sigma - y_\sigma)}{\sigma} - \theta \varepsilon \frac{D d(x_\sigma)}{d(x_\sigma)}\right|^2  -f(x_\sigma) \nonumber\\
-    &- 2nC_0\left(\frac{\varepsilon}{\sigma}\right) - \theta |D d(x_\sigma)|^2 \left(\frac{\varepsilon}{d(x_\sigma)}\right)^2  + \theta \Delta d(x_\sigma)\left(\frac{\varepsilon^2}{d(x_\sigma)}\right) \leq 0.
+    u^\varepsilon(x_\sigma)&+ \left|\frac{2C_0(x_\sigma - y_\sigma)}{\sigma} - \nu \varepsilon \frac{D d(x_\sigma)}{d(x_\sigma)}\right|^2  -f(x_\sigma) \nonumber\\
+    &- 2nC_0\left(\frac{\varepsilon}{\sigma}\right) - \nu |D d(x_\sigma)|^2 \left(\frac{\varepsilon}{d(x_\sigma)}\right)^2  + \nu \Delta d(x_\sigma)\left(\frac{\varepsilon^2}{d(x_\sigma)}\right) \leq 0.
 \end{align}
@@
 \end{equation}
-Subtracting \eqref{e:superslnp=2} from \eqref{e:subslnp=2}, we have
+Subtract \eqref{e:superslnp=2} from \eqref{e:subslnp=2} to get
 \begin{align*}
-    u^\varepsilon(x_\sigma) - u(y_\sigma) &\leq \left(4C_0+ \theta\varepsilon\frac{D d(x_\sigma)}{d(x_\sigma)}\right)\left(\theta \varepsilon \frac{ D d(x_\sigma)}{d(x_\sigma)}\right) \\
-    &+ C\sigma + 2nC_0 \left(\frac{\varepsilon}{\sigma}\right)+ \theta |D d(x_\sigma)|^2 \left(\frac{\varepsilon}{d(x_\sigma)}\right)^2 + \theta|\Delta d(x_\sigma)| \frac{\varepsilon^2}{d(x_\sigma)}.
+    u^\varepsilon(x_\sigma) - u(y_\sigma) &\leq \left(4C_0+ \nu\varepsilon\frac{D d(x_\sigma)}{d(x_\sigma)}\right)\left(\nu \varepsilon \frac{ D d(x_\sigma)}{d(x_\sigma)}\right) \\
+    &+ C\sigma + 2nC_0 \left(\frac{\varepsilon}{\sigma}\right)+ \nu |D d(x_\sigma)|^2 \left(\frac{\varepsilon}{d(x_\sigma)}\right)^2 + \nu|\Delta d(x_\sigma)| \frac{\varepsilon^2}{d(x_\sigma)}.
 \end{align*}
-Using $d(x_\sigma)\geq \frac{1}{2}\kappa$ and bounds on $d(x)$ as in \eqref{boundond}, we see that
+Using $d(x_\sigma)\geq \frac{1}{2}\kappa$ and bounds on $d(x)$ in \eqref{boundond}, we see that
 \begin{align}\label{p=2a}
     \Phi(x_\sigma,y_\sigma)&\leq u^\varepsilon(x_\sigma) - u(y_\sigma)\nonumber \\
-    &\leq 4K_1^2\theta(1+\theta)\left(\frac{\varepsilon}{\kappa}\right)^2 + C\sigma + 2nC_0\left( \frac{\varepsilon}{\sigma}\right) + 2\theta(K_2\varepsilon+4C_0K_1)\left(\frac{\varepsilon}{\kappa}\right)\nonumber\\
+    &\leq 4K_1^2\nu(1+\nu)\left(\frac{\varepsilon}{\kappa}\right)^2 + C\sigma + 2nC_0\left( \frac{\varepsilon}{\sigma}\right) + 2\nu(K_2\varepsilon+4C_0K_1)\left(\frac{\varepsilon}{\kappa}\right)\nonumber\\
     &\leq C\left(\sigma+\frac{\varepsilon}{\sigma} + \frac{\varepsilon}{\kappa} + \left(\frac{\varepsilon}{\kappa}\right)^2\right) \leq C\sqrt{\varepsilon}
 \end{align}
-where we choose $\sigma = \sqrt{\varepsilon}$.
+if we choose $\sigma = \sqrt{\varepsilon}$.
 
 \noindent
-If $d(x_\sigma)<\frac{1}{2}\kappa$, then $x_\sigma\in U_\kappa$. Similar to the previous argument, we have $d_\kappa(x_\sigma) = d(x_\sigma)$ and from \eqref{annulus2p=2}
+If $d(x_\sigma)<\frac{1}{2}\kappa$, then $x_\sigma\in U_\kappa$. Again, we have $d_\kappa(x_\sigma) = d(x_\sigma)$ and from \eqref{annulus2p=2}
 \begin{equation}\label{p=2b}
-    \Phi(x_\sigma,y_\sigma) \leq \nu\varepsilon \log\left(\frac{2}{\kappa}\right) + C_\nu\left(\frac{4\varepsilon}{\kappa}\right)^2 \leq C\left(\varepsilon+\varepsilon\,|\log(\kappa)| + \left(\frac{\varepsilon}{\kappa}\right)^2\right).
+    \Phi(x_\sigma,y_\sigma) \leq u^\varepsilon(x_\sigma) - \nu \varepsilon \log\left(\frac{1}{d(x_\sigma)}\right) \leq  C\left(\frac{4\varepsilon}{\kappa}\right)^2.
+%\leq C\left(\varepsilon+\varepsilon\,|\log(\kappa)| + \left(\frac{\varepsilon}{\kappa}\right)^2\right).
 \end{equation}
@@
 \begin{equation*}
-    u^\varepsilon(x) - u(x) - \theta\varepsilon\log\left(\frac{1}{d(x)}\right) \leq C\sqrt{\varepsilon} +C\varepsilon \left(1+|\log(\kappa)| + \frac{\varepsilon}{\kappa^2}\right).
-\end{equation*}
-Let $\theta\to 1^+$ and we obtain 
-\begin{equation*}
-    -C\sqrt{\varepsilon}\leq u^\varepsilon(x) - u(x) \leq C \left(\sqrt{\varepsilon}+\varepsilon+\varepsilon|\log(\kappa)| + \left(\frac{\varepsilon}{\kappa}\right)^2\right) +  \varepsilon \log\left(\frac{1}{d(x)}\right), \qquad x\in \Omega.
-\end{equation*}
-Similar to the previous case, in the region where $0< d(x)\leq \varepsilon$, $|u^\varepsilon-u|=\mathcal{O}(\sqrt{\varepsilon})$ since $\varepsilon|\log(\varepsilon)|\leq \sqrt{\varepsilon}$.
-Thus the conclusion follows.
+    u^\varepsilon(x) - u(x) - \nu\varepsilon\log\left(\frac{1}{d(x)}\right) \leq C\sqrt{\varepsilon} +C\left(\frac{4\varepsilon}{\kappa}\right)^2
+\end{equation*}
+and thus \eqref{eq:cp2} follows.
+%Similar to the case where $1<p<2$, \eqref{annulus2p=2} gives us a better rate $\mathcal{O}(\varepsilon)$ in any compact set $K$ that is disjoint from $\mathrm{supp}(f)$. Thus, the conclusion follows.
 \end{proof}
@@
 
-\begin{rem} For general Lipschitz data $f\in \mathrm{C}(\overline{\Omega})$, it is natural to think about using cutoff function argument.
+\begin{rem} For general Lipschitz data $f\in \mathrm{C}(\overline{\Omega})$, it is natural to try a cutoff function argument.
 Let $\chi_{{\kappa}}\in \mathrm{C}_c^\infty(\Omega)$ such that $0\leq \chi_{\kappa}\leq 1$, $\chi_\kappa = 1$ in $\Omega_{2\kappa}$ and $\mathrm{supp}\;\chi_\kappa\subset\Omega_\kappa$.
-Let $u^\varepsilon_\kappa\in \rmC^2(\Omega)\cap\rmC(\overline{\Omega})$ solves \eqref{eq:PDEeps} with datum $f\chi_{\kappa}$.
-Then as $u^\varepsilon_\kappa\to u^\varepsilon$ as $\kappa\to 0$ (since $f\chi_\kappa\to f$ in the weak$^*$ topology of $L^\infty(\Omega)$, we have a continuity of solution with respect to data in this topology \cite[Remark II.1]{Lasry1989}).
+Let $u^\varepsilon_\kappa\in \rmC^2(\Omega)\cap\rmC(\overline{\Omega})$ solve \eqref{eq:PDEeps} with data $f\chi_{\kappa}$.
+Then $u^\varepsilon_\kappa\to u^\varepsilon$ as $\kappa\to 0$ (since $f\chi_\kappa\to f$ in the weak$^*$ topology of $L^\infty(\Omega)$ and we have the continuity of the solution to \eqref{eq:PDEeps} with respect to data in this topology \cite[Remark II.1]{Lasry1989}).
 However, it is not clear at the moment how to quantify this rate of convergence, since $f\chi_\kappa$ does not converge to $f$ in the uniform norm, unless $f = 0$ on $\partial\Omega$.
@@
 It is clear that for $x\in \partial\Omega_k$, $g_\kappa(x) = L\kappa \geq f(x)$ since \eqref{e:bound_aa}. Therefore, we can define the following continuous function
-\begin{equation*}
+\begin{equation}\label{def_f_kappa}
     f_\kappa(x) = 
@@
     \end{cases}
-\end{equation*}
+\end{equation}
 \begin{figure}[h]
@@
 \end{equation*}
-Let $u^\varepsilon_\kappa\in \rmC^2(\Omega)\cap\rmC(\overline{\Omega})$ be the solution to \eqref{eq:PDEeps} with datum $f\chi_{\kappa}$ and $u_k\in \mathrm{C}(\overline{\Omega})$ be the corresponding solution to \eqref{eq:PDE0} with datum $f{\chi_\kappa}$.
-By comparison principle (\cite[Corollary II.1]{Lasry1989}) we have
+Let $u^\varepsilon_\kappa\in \rmC^2(\Omega)\cap\rmC(\overline{\Omega})$ be the solution to \eqref{eq:PDEeps} with data $f\chi_{\kappa}$ and $u_k\in \mathrm{C}(\overline{\Omega})$ be the corresponding solution to \eqref{eq:PDE0} with data $f{\chi_\kappa}$.
+By the comparison principle (\cite[Corollary II.1]{Lasry1989}), we have
 \begin{equation}\label{e:bound_2aa}
@@
 \begin{equation}\label{e:bound_2ac}
-    -C\sqrt{\varepsilon}\leq u^\varepsilon_\kappa(x) - u_\kappa(x)\leq C\left[\sqrt{\varepsilon} + \left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1} + \left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2} + \frac{\varepsilon^{\alpha+1}}{d(x)^\alpha}\right], \qquad x\in \Omega.
+    -C\sqrt{\varepsilon}\leq u^\varepsilon_\kappa(x) - u_\kappa(x)\leq C\left[\sqrt{\varepsilon} + \left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2} + \frac{\varepsilon^{\alpha+1}}{d(x)^\alpha}\right], \qquad x\in \Omega.
 \end{equation}
@@
    -C\sqrt{\varepsilon}\leq u^\varepsilon(x) - u(x) &= \Big(u^\varepsilon(x) - u^\varepsilon_\kappa(x)\Big) + \Big(u^\varepsilon_\kappa(x) - u_\kappa(x)\Big) + \Big(u_\kappa(x) - u(x)\Big) \\
-    &\leq L\kappa + C\left[\sqrt{\varepsilon} + \left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1} + \left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2} + \frac{\varepsilon^{\alpha+1}}{d(x)^\alpha}\right], \qquad x\in \Omega.
+    &\leq L\kappa + C\left[\sqrt{\varepsilon}  + \left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2} + \frac{\varepsilon^{\alpha+1}}{d(x)^\alpha}\right], \qquad x\in \Omega.
 \end{split}
 \end{equation*}
-Choose $\kappa = \sqrt{\varepsilon}$. We deduce that
+Choose $\kappa = \sqrt{\varepsilon}$ and we deduce that
 \begin{equation*}
@@
 \begin{equation}\label{e:bound_2acp=2}
-    -C\sqrt{\varepsilon}\leq u^\varepsilon_\kappa(x) - u_\kappa(x) \leq C\left[\sqrt{\varepsilon} + \varepsilon + \varepsilon |\log(\kappa)|+\left(\frac{\varepsilon}{\kappa}\right)^2 + \varepsilon\log\left(\frac{1}{d(x)}\right)\right], \qquad x\in \Omega.
+    -C\sqrt{\varepsilon}\leq u^\varepsilon_\kappa(x) - u_\kappa(x) \leq C\left[\sqrt{\varepsilon} + \left(\frac{\varepsilon}{\kappa}\right)^2 + \varepsilon\log\left(\frac{1}{d(x)}\right)\right], \qquad x\in \Omega.
 \end{equation}
@@
    -C\sqrt{\varepsilon}\leq u^\varepsilon(x) - u(x) &= \Big(u^\varepsilon(x) - u^\varepsilon_\kappa(x)\Big) + \Big(u^\varepsilon_\kappa(x) - u_\kappa(x)\Big) + \Big(u_\kappa(x) - u(x)\Big) \\
-    &\leq L\kappa + C\left[\sqrt{\varepsilon} + \varepsilon|\log(\kappa)| + \left(\frac{\varepsilon}{\kappa}\right)^{2} + \varepsilon\log\left(\frac{1}{d(x)}\right) \right], \qquad x\in \Omega.
+    &\leq L\kappa + C\left[\sqrt{\varepsilon} +  \left(\frac{\varepsilon}{\kappa}\right)^{2} + \varepsilon\log\left(\frac{1}{d(x)}\right) \right], \qquad x\in \Omega.
 \end{split}
 \end{equation*}
-Choose $\kappa = \varepsilon$. We deduce that
+Choose $\kappa = \varepsilon$ and we deduce that
 \begin{equation*}
@@
 
-\subsection{An improved one-sided rate of convergence}
-We still assume $f = 0$ on $\partial\Omega$ and $f\geq 0$ such that $f\in \rmC^2(\overline{\Omega})$. From Lemma \ref{lem:f=0} we have $u = 0$ on $\partial\Omega$. Extent $u$ to $\R^n$ by setting 
+\section{Improved one-sided rate of convergence for compactly supported data}
+We still assume $f = 0$ on $\partial\Omega$ and $f\geq 0$ such that $f\in \rmC^2(\overline{\Omega})$. From Lemma \ref{lem:f=0}, we have $u = 0$ on $\partial\Omega$. Extent $u$ to $\R^n$ by setting 
 \begin{equation*}
@@
 \end{equation*}
+By abuse of notion, we still denote the extension of $f$ on $\R^n$ by itself.
 
@@
 
-\begin{thm}[Compactly supported data]\label{thm:rate_doubling2} Assume that $f\in \mathrm{C}^2_c(\Omega)$ such that $\mathrm{supp}(f)\subset\Omega_\kappa$ where $0<\kappa < \delta_{0}$.
-Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}.
-Then there exists a constant $C$ independent of $\varepsilon$ and $\kappa$ such that
-\begin{equation*}
-\begin{aligned}
-    u^\varepsilon(x) - u(x) &\leq\frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} + CC_\frac{\kappa}{2} \left(\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1}+\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2}\right) + nc\varepsilon, \quad \text{if} \quad 1 < p <2, \\
-    u^\varepsilon(x) - u(x) & \leq \nu \varepsilon \log\left( \frac{1}{d(x)}\right)+C C_\frac{\kappa}{2}\left(\frac{\varepsilon}{\kappa}\right) +C\left( \frac{\varepsilon}{\kappa}\right)^2 + nc \varepsilon, \quad \text{if} \quad p=2,
-\end{aligned}
-\end{equation*}
-where $c$ is defined as in \eqref{def_c} and $C_\frac{\kappa}{2}$ is the gradient bound of $u^\varepsilon$ on $\overline{\Omega}_\frac{\kappa}{2}$ as in \eqref{e:priorie_eps}.
-\end{thm}
-
-\begin{proof} For $1<p<2$, we proceed as in the proof of Theorem \ref{thm:rate_doubling1} to obtain 
+The following Lemma is a refined version of the local gradient bound in Theorem \ref{thm:grad_1}.
+We follows \cite[Theorem 3.1]{Armstrong2015a} where the authors use Bernstein's method inside a doubling variables argument and explicitly keep track of all dependencies.
+We refer the readers to \cite{barles_weak_1991,capuzzo_dolcetta_holder_2010} and the references therein for related versions of the gradient bound.
+We believe this result is new in the literature since it is uniform in $\varepsilon$.
+It also indicates that the boundary layer is the strip of size $\mathcal{O}(\varepsilon)$ from the boundary.
+
+\begin{lem}\label{lem:boundDu^eps} For all $\varepsilon$ small enough, there exists a constant $C$ independent of $\varepsilon$ such that
+\begin{equation}\label{eq:es_final}
+|Du^\varepsilon(x)| \leq C\left( 1 + \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}\right) \qquad\text{for}\;x\in \Omega.
+\end{equation}
+\end{lem}
+
+\begin{proof}[Proof of Lemma \ref{lem:boundDu^eps}] %Let us consider $0<\varepsilon < \min\{4\delta_0,1\}$. 
+Let us fix $x_0 \in \Omega\backslash \Omega_{\delta_0}$ and let $\delta = \frac{1}{4}d(x_0)$. Let 
+\begin{equation*}
+    v(x) = \frac{1}{\delta}u^\varepsilon(x_0+\delta x), \qquad x\in B(0,2).   
+\end{equation*}
+We have $Dv(x) = Du^\varepsilon(x_0+\delta x)$ and $\Delta v(x) = \delta \Delta u^\varepsilon(x_0+\delta x)$ for $x\in B(0,2)$. The equation for $v$ is given by
+\begin{equation*}
+    \delta v(x) + |Dv(x)|^p - \tilde{f}(x) - \frac{\varepsilon}{\delta}\Delta v(x) = 0 \qquad\text{in}\;B(0,2),
+\end{equation*}
+where $\tilde{f}(x) = f(x_0+\delta x)$ defined on $\overline{B(0,2)}$. We note that $\Vert \tilde{f}\Vert_{L^\infty}\leq \Vert f\Vert_{L^\infty}$ and 
+\begin{equation*}
+    B(x_0,2\delta)\subset \Omega_{2\delta}\subset\subset\Omega.
+\end{equation*}
+By Lemma \ref{lem:super_refined}, there is a constant $C$ independent of $\delta,\varepsilon$ such that 
+\begin{equation*}
+     \delta\Vert v\Vert_{L^\infty\left(B\left(0,\frac{3}{2}\right)\right)} \leq \Vert u^\varepsilon\Vert_{L^\infty(\Omega_{2\delta}))} \leq C\left(1 + \frac{\varepsilon^{\alpha+1}}{\delta^\alpha}\right).
+\end{equation*}
+Note that $p = \frac{\alpha+2}{\alpha+1}$ and $\alpha+1 = \frac{1}{p-1}$, we apply Theorem 3.1 in \cite{Armstrong2015a} to obtain 
+\begin{equation*}
+\begin{split}
+    \sup_{x\in B(0,1)}|Dv(x)| &\leq C\left[\left(\frac{\varepsilon}{\delta}\right)^{\frac{1}{p-1}} + \left(\Vert f\Vert_{L^\infty}+\delta \Vert v\Vert_{L^\infty\left(B\left(0,\frac{3}{2}\right)\right)}\right)^{\frac{1}{p}}\right] \\
+    &\leq C\left[\left(\frac{\varepsilon}{\delta}\right)^{\alpha+1} + \left(1+\frac{\varepsilon^{\alpha+1}}{\delta^\alpha}\right)^{\frac{\alpha+1}{\alpha+2}}\right]\leq C \left(1+\left(\frac{\varepsilon}{\delta}\right)^{\alpha+1}\right).
+    %&\leq C\left[\left(\frac{\varepsilon}{\delta}\right)^{\alpha+1} + \left(1+\left(\frac{\alpha+1}{\alpha+2}\right)\frac{\varepsilon^{\alpha+1}}{\delta^\alpha}\right)\right] \leq C\left[1+2\left(\frac{\varepsilon}{\delta}\right)^{\alpha+1} \right]
+\end{split}
+\end{equation*}
+%where we use Bernoulli's inequality and the fact that $\delta \leq 1$. 
+Replace $\delta = \frac{1}{4}d(x_0)$ we obtain
+\begin{equation*}
+    |Du^\varepsilon(x_0)| = |Dv(0)| \leq C\left(1+ \left(\frac{\varepsilon}{d(x_0)}\right)^{\alpha+1}\right).
+\end{equation*}
+In other words, we obtain \eqref{eq:es_final} for all $x\in \Omega\backslash\Omega_{\delta_0}$.
+From Theorem \ref{thm:grad_1} there exists a constant $C$ independent of $\varepsilon$ such that $|Du^\varepsilon(x)|\leq C$ for all $x\in \Omega_{\delta_0}$ and the proof is complete.
+\end{proof}
+
+\begin{proof}[Proof of Theorem \ref{thm:rate_doubling2}] For $1<p<2$, we proceed as in the proof of Theorem \ref{thm:rate_doubling1} to obtain 
 \begin{align}
@@
     D\psi^\varepsilon(x_0) = Du^\varepsilon(x_0) + \nu C_\alpha\alpha \left(\frac{\varepsilon}{d(x_0)}\right)^{\alpha+1} D d(x_0) \in D^-u(x_0).
+\end{equation*}
+We note that $x_0$ depends on $\nu$. 
+As $u$ is Lipschitz with constant $C_0$, we deduce that
+\begin{equation*}
+    |D\psi^\varepsilon(x_0)| = \left|Du^\varepsilon(x_0) + \nu C_\alpha\alpha \left(\frac{\varepsilon}{d(x_0)}\right)^{\alpha+1} D d(x_0) \right| \leq C_0.
 \end{equation*}
@@
 \end{itemize}
-From the two cases, the conclusion follows.
+%From the two cases, the conclusion follows.
 
@@
 \end{itemize}
-Therefore, the conclusion follows.
-\end{proof}
-
-\begin{rem} Using our approach, in order to relax the assumption $\mathrm{supp}(f)\subset\subset\Omega$ to $f = 0$ on $\partial\Omega$ as in Theorem \ref{main_thm1}, it is necessary to know explicitly how the constant $C_\kappa$ in \eqref{est_Ckappa} blows up as $\kappa\to 0$.
-Fortunately, such a refined version of the local gradient bound is available, for instance \cite[Theorem 3.1]{Armstrong2015} where the authors use Bernstein's method inside a doubling variables argument and explicitly keep track of all dependencies.
-We refer the readers to \cite{armstrong_stochastic_2012, barles_weak_1991,capuzzo_dolcetta_holder_2010} and the references therein for related versions of the gradient bound.
-\end{rem}
-
-\begin{lem}\label{lem:boundDu^eps} For all $\varepsilon$ small enough, there exists a constant $C$ independent of $\varepsilon$ such that
-\begin{equation}\label{eq:es_final}
-|Du^\varepsilon(x)| \leq C\left( 1 + \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}\right) \qquad\text{for}\;x\in \Omega.
-\end{equation}
-\end{lem}
-
-\begin{proof}[Proof of Lemma \ref{lem:boundDu^eps}] %Let us consider $0<\varepsilon < \min\{4\delta_0,1\}$. 
-Let us fix $x_0 \in \Omega\backslash \Omega_{\delta_0}$ and let $\delta = \frac{1}{4}d(x_0)$. Let 
-\begin{equation*}
-    v(x) = \frac{1}{\delta}u^\varepsilon(x_0+\delta x), \qquad x\in B(0,2).   
-\end{equation*}
-We have $Dv(x) = Du^\varepsilon(x_0+\delta x)$ and $\Delta v(x) = \delta \Delta u^\varepsilon(x_0+\delta x)$ for $x\in B(0,2)$. The equation for $v$ is given by
-\begin{equation*}
-    \delta v(x) + |Dv(x)|^p - \tilde{f}(x) - \frac{\varepsilon}{\delta}\Delta v(x) = 0 \qquad\text{in}\;B(0,2),
-\end{equation*}
-where $\tilde{f}(x) = f(x_0+\delta x)$ defined on $\overline{B(0,2)}$. We note that $\Vert \tilde{f}\Vert_{L^\infty}\leq \Vert f\Vert_{L^\infty}$ and 
-\begin{equation*}
-    B(x_0,2\delta)\subset \Omega_{2\delta}\subset\subset\Omega.
-\end{equation*}
-By Lemma \ref{lem:super_refined}, there is a constant $C$ independent of $\delta,\varepsilon$ such that 
-\begin{equation*}
-     \delta\Vert v\Vert_{L^\infty\left(B\left(0,\frac{3}{2}\right)\right)} \leq \Vert u^\varepsilon\Vert_{L^\infty(\Omega_{2\delta}))} \leq C\left(1 + \frac{\varepsilon^{\alpha+1}}{\delta^\alpha}\right).
-\end{equation*}
-Note that $p = \frac{\alpha+2}{\alpha+1}$ and $\alpha+1 = \frac{1}{p-1}$, we apply Theorem 3.1 in \cite{Armstrong2015} to obtain 
-\begin{equation*}
-\begin{split}
-    \sup_{x\in B(0,1)}|Dv(x)| &\leq C\left[\left(\frac{\varepsilon}{\delta}\right)^{\frac{1}{p-1}} + \left(\Vert f\Vert_{L^\infty}+\delta \Vert v\Vert_{L^\infty\left(B\left(0,\frac{3}{2}\right)\right)}\right)^{\frac{1}{p}}\right] \\
-    &\leq C\left[\left(\frac{\varepsilon}{\delta}\right)^{\alpha+1} + \left(1+\frac{\varepsilon^{\alpha+1}}{\delta^\alpha}\right)^{\frac{\alpha+1}{\alpha+2}}\right]\leq C \left(1+\left(\frac{\varepsilon}{\delta}\right)^{\alpha+1}\right).
-    %&\leq C\left[\left(\frac{\varepsilon}{\delta}\right)^{\alpha+1} + \left(1+\left(\frac{\alpha+1}{\alpha+2}\right)\frac{\varepsilon^{\alpha+1}}{\delta^\alpha}\right)\right] \leq C\left[1+2\left(\frac{\varepsilon}{\delta}\right)^{\alpha+1} \right]
-\end{split}
-\end{equation*}
-%where we use Bernoulli's inequality and the fact that $\delta \leq 1$. 
-Replace $\delta = \frac{1}{4}d(x_0)$ we obtain
-\begin{equation*}
-    |Du^\varepsilon(x_0)| = |Dv(0)| \leq C\left(1+ \left(\frac{\varepsilon}{d(x_0)}\right)^{\alpha+1}\right).
-\end{equation*}
-In other words, we obtain \eqref{eq:es_final} for all $x\in \Omega\backslash\Omega_{\delta_0}$.
-From Theorem \ref{thm:grad_1} there exists a constant $C$ independent of $\varepsilon$ such that $|Du^\varepsilon(x)|\leq C$ for all $x\in \Omega_{\delta_0}$ and thus the proof is complete.
-\end{proof}
-
-\begin{rem} As a consequence, the constant $C_{\frac{\kappa}{2}}$ in Theorem \ref{thm:rate_doubling2} satisfies
-\begin{equation*}
-    C_{\frac{\kappa}{2}} \leq C\left(1+\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1}\right)
-\end{equation*}
-where $C$ is a constant independent of $\varepsilon$ and $\kappa$.
-\end{rem}
-
-\begin{proof}[Proof of Theorem \ref{main_thm2}] Let $L$ be the Lipschitz constant of $f$.
-For $0 < \kappa <\delta_0$ we define $f_\kappa$ as in the proof of Theorem \ref{main_thm1}, where $\mathrm{supp}(f_\kappa)\subset\Omega_{\frac{\kappa}{2}}$ and
-\begin{equation*}
-    0\leq f - f_\kappa \leq L\kappa.
-\end{equation*}
+Finally, applying Lemma \ref{lem:boundDu^eps} to get rid of the constant $C_{\frac{\kappa}{2}}$ we obtain the conclusion.
+\end{proof}
+
+\begin{proof}[A different proof of Theorem \ref{main_thm1}] Let $L$ be the Lipschitz constant of $f$.
+For $0 < \kappa <\delta_0$ we define $f_\kappa$ as in \eqref{def_f_kappa}.
+We have $\mathrm{supp}(f_\kappa)\subset\Omega_{\frac{\kappa}{2}}$ and $0\leq f - f_\kappa \leq L\kappa$.
 Let $u^\varepsilon_\kappa\in \rmC^2(\Omega)\cap \rmC(\overline{\Omega})$ be the solution to \eqref{eq:PDEeps} and $u_k$ be the solution to \eqref{eq:PDE0} with $f$ being replaced by $f_k$, respectively.
-By the same argument as in the proof of Theorem \ref{main_thm1}, we have
+It is clear that
 \begin{equation*}
@@
 \end{equation*}
-By Theorem \ref{thm:rate_doubling2} and Lemma \ref{lem:boundDu^eps} we have 
+By Theorem \ref{thm:rate_doubling2} we have 
 \begin{equation*}
@@
 \begin{equation*}
-    u^\varepsilon(x)-u(x)\leq 2L\kappa + \Big(u^\varepsilon_\kappa(x) - u_\kappa(x)\Big) \leq 2L\kappa+C_{\kappa}\varepsilon
-\end{equation*}
-where we use the rate $\mathcal{O}(\varepsilon)$ from Theorem \ref{thm:rate_doubling2} as $f_\kappa$ is compactly supported.
-
-\end{proof}
+    u^\varepsilon(x)-u(x)\leq 2L\kappa + \Big(u^\varepsilon_\kappa(x) - u_\kappa(x)\Big).
+\end{equation*} 
+Choose $\kappa = \sqrt{\varepsilon}$ we obtain the conclusion.
+\end{proof}
+
+\section{Something new}
+Assume $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ with $f = 0$ in $\overline{\Omega}_{2\kappa}$ for $0<\kappa \ll \delta_0$. By doing so we can assume that
+\begin{equation*}
+    \delta_{0,\Omega_{2\kappa}} = \frac{1}{2}\delta_{0,\Omega}.
+\end{equation*}
+Let $1<p<2$ and $d_\kappa(x) = \mathrm{dist}(x,\partial\Omega_\kappa)$ for $x\in \Omega_\kappa$. By Theorem \ref{thm:rate_doubling0} we obtain that
+\begin{equation*}
+    0\leq u^\varepsilon(x)\leq C \left(\frac{\varepsilon^{\alpha+1}}{d_\kappa(x)^{\alpha}} + \frac{\varepsilon^{\alpha+2}}{\delta_{0,\Omega_{\kappa}}^{\alpha+2}}\right)
+\end{equation*}
+for some constant $C$ independent of $\varepsilon\in (0,1)$ and $\kappa$.
 
@@
 
-%\begin{appendices}
-\section*{Appendix}
+\begin{appendices}
+%\section*{Appendix}
 \subsection*{Estimates on solutions}
@@
 
-\subsection*{Existence and wellposedness of solution}
+\subsection*{Wellposedness of solutions}
 \begin{proof} [Proof of Theorem \ref{thm:wellposed1<p<2}] If $p\in (1,2)$, we use the ansatz $ u(x) = C_\varepsilon d(x)^{-\alpha}$ to find a solution for \eqref{eq:PDEeps}.
@@
 
-%\end{appendices}
+\end{appendices}
+
 \stoptocwriting

### 2021-07-15 Drafts and notes/Notes/Notes-May 5.tex
Almost final

\documentclass[english,reqno]{amsart}
%\renewcommand{\baselinestretch}{1.2}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\raggedbottom
\usepackage{subfig}
\usepackage{amssymb,amsbsy,amsmath,amsfonts,amssymb,amscd}
\usepackage{comment}
\usepackage{verbatim}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage[numbers]{natbib} % for alphabetically numbered lists
\usepackage{algorithm,algpseudocode}
\usepackage{setspace}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{assum}{Assumption}[section]
\newtheorem{cor}{Corollary}[section]
\newenvironment{solution}
  {\renewcommand\qedsymbol{$\blacksquare$}\begin{proof}[Solution]}
  {\end{proof}}
\title{Quick Notes}

\begin{document}

\maketitle
\date{May 5, 2021}
\section{New things to think about}
\begin{enumerate}[label=\arabic*)]
    \item Work out the details of the following example in $n=1$.
    Let u be the solution to
    \begin{equation}
    \label{example}
        \left\{
  \begin{aligned}
   u(x) + \frac{1}{2}|u^\prime(x)|^2 -f(x) &\leq 0 \, \quad \qquad \text{in } (-1, 1), \\
              u(x) + \frac{1}{2}|u^\prime (x)|^2 -f(x) &\geq 0 \qquad  \quad \text{for } x=-1, 1,
  \end{aligned}
\right.
    \end{equation}
    with an easier $f$, using deterministic optimal control formula and Euler-Lagrange equation. For instance, $f=0$ in $[-\frac{1}{2}, \frac{1}{2}]$. And then try to look into the solution to the equation with $\epsilon \Delta u^\epsilon$.

 \begin{solution}
\textbf{STEP 1. Find the Euler-Lagrange equation.}

According to the optimal control formula for the state-constraint problem,
\begin{equation}
\label{ocf}
    u(x)=\inf \left\{ \left.I[\eta]: =\int_0^\infty e^{-s} \left( \frac{\left( \dot{\eta}(s) \right)^2}{2} + f(\eta (s)) \right)ds \right| \eta \in \mathrm{AC}([0, \infty); [-1,1]), \eta(0)=x \right\}.
\end{equation}

Suppose a minimizer of \eqref{ocf} with initial data $x_0$ exits and call it $\gamma$. Fix $b >0$ and define $$\displaystyle I_b[\eta] := \int_0^b e^{-s} \left( \frac{\left( \dot{\eta}(s) \right)^2}{2} + f(\eta (s)) \right)ds.$$
Since $\gamma$ is a minimizer of \eqref{ocf}, $\gamma$ is also a minimizer of the problem
\begin{equation}
    \min \left\{ I_b [\eta] ; \eta \in \mathrm{AC}\left([0, b]; [-1,1]\right) , \eta(0) = x_0, \eta(b) =\gamma(b) \right\}.
\end{equation}
Let $\tau \in \mathrm{AC}\left([0, b]; [-1,1]\right)$ with $ \tau(0) = 0, \tau(b) =0$. Assume $\gamma(s) +t \tau(s) \in \bar{\Omega}$, $ \forall s \in [0,b]$, for $t$ small enough. By calculus of variation, 
\begin{equation*}
\begin{aligned}
    \left.  0=\frac{d}{dt}\left( I[\gamma +t \tau]\right) \right|_{t=0} &=\int_0^b e^{-s} \left(\dot{\gamma}(s)  \dot{\tau}(s) + f^\prime(\gamma(s)) \tau(s) \right)ds\\
    &=\int_0^b -\left( e^{-s} \dot{\gamma}(s) \right)^\prime \tau(s) + e^{-s} f^\prime(\gamma(s)) \tau(s)ds\\
    &=\int_0^b \left( \dot{\gamma} -\Ddot{\gamma} +f^\prime (\gamma)\right)\tau e^{-s}ds.
\end{aligned}
\end{equation*}
Therefore, if $\gamma$ is a minimizer of \eqref{ocf}, then 
\begin{equation}
\label{EL}
\left\{
\begin{aligned}
     \Ddot{\gamma}(s)&=\dot{\gamma}(s) + f^\prime (\gamma(s)), s\in (0,b),\\
     \gamma(0)&=x_0.
\end{aligned}
\right.
\end{equation}
\textcolor{red}{(We don't have any info about initial velocity here.)}

We will instead consider \eqref{EL} with the initial position $x_0$ and the initial velocity $y_0$ (to be determined), i.e,
\begin{equation}
\label{EL2}
\left\{
\begin{aligned}
     \Ddot{\gamma}(s)&=\dot{\gamma}(s) + f^\prime (\gamma(s)), s\in (0,b),\\
     \gamma(0)&=x_0,\\
     \dot{\gamma}(0)&=y_0.
\end{aligned}
\right.
\end{equation}
Change notations a little bit by letting $x(s)= \gamma(s)$ and $y(s)=\dot{\gamma}(s)$. Then \eqref{EL2} becomes
\begin{equation}
\label{ode}
\left\{
\begin{aligned}
\dot{x}(s)&=y(s),\\
     \dot{y}(s)&=y(s) + f^\prime (x(s)),\\
     x(0)&=x_0,\\
     y(0)&=y_0.
\end{aligned}
\right.
\end{equation}

\textbf{STEP 2. Solve the Euler-Lagrange equation to get the formula for $\gamma$ and compute the cost function value for $\gamma$.}

\begin{itemize}
    \item \textbf{Example 1}
    Consider \eqref{ode} with $f$ defined by
\begin{equation*}
        f(x) := \left\{
  \begin{aligned}
  -x -\frac{1}{2}   \, \quad \qquad &\text{in } [-1, -\frac{1}{2}], \\
   0 \, \quad \qquad &\text{in } (-\frac{1}{2}, \frac{1}{2}), \\
              x-\frac{1}{2}  \qquad  \quad &\text{in } [\frac{1}{2}, 1],
  \end{aligned}
\right.
    \end{equation*}

    \begin{enumerate}
        \item Suppose $x_0 \in [-\frac{1}{2}, \frac{1}{2}]$. We can choose $\gamma (s) \equiv x_0$. Then $I[\gamma]=0$ and hence $\gamma \equiv x_0$ is a minimizer. Hence, $u(x)=0$ for $x \in [-\frac{1}{2}, \frac{1}{2}]$.
        \item Suppose $x_0 \in (\frac{1}{2}, 1]$. We need to solve the Euler-Lagrange equation.

        If $x(s) \in (\frac{1}{2}, 1)$, we have
        \begin{equation*}
        \begin{aligned}
        &\left\{
        \begin{aligned}
        \dot{x}(s)&=y(s),\\
        \dot{y}(s)&=y(s) + 1,\\
         x(0)&=x_0,\\
         y(0)&=y_0,
        \end{aligned}
        \right.\\
        \Longrightarrow &
        \left\{
        \begin{aligned}
         	& x(s)=(1+y_0)(e^s-1)-s+x_0,\\
         	& y(s)=(1+y_0)e^s-1.
        \end{aligned}
        \right.\\
        \end{aligned}
        \end{equation*}

        \begin{enumerate}
    \item Suppose $\displaystyle x\left(t_\frac{1}{2}\right)=\frac{1}{2}$ for a finite time $t_{\frac{1}{2}} >0$. We will make $x(s)=\frac{1}{2}$, $\forall s>t_\frac{1}{2}$ to minimize the cost function. 
    Set $\displaystyle x \left(t_{\frac{1}{2}} \right)=\frac{1}{2}$ and we can solve for the initial velocity $y_0$ in terms of $t_\frac{1}{2}$:
    \begin{equation*}
        \begin{aligned}
         &(1+y_0)(e^{t_{\frac{1}{2}}}-1)-t_{\frac{1}{2}}+x_0 =\frac{1}{2},\\
         	\Longrightarrow \quad & y_0= \frac{\frac{1}{2} + t_\frac{1}{2} - x_0}{e^{t_\frac{1}{2}}-1}-1.
        \end{aligned}
    \end{equation*}
    Compute the cost function
    \begin{equation*}
    \begin{aligned}
     I[\gamma]&= \int_0^{t_\frac{1}{2}} e^{-s}\left(\frac{y^2}{2} + x(s)-\frac{1}{2}\right)ds\\
     &= \int_0^{t_\frac{1}{2}} e^{-s}\left(\frac{(e^s(1+y_0)-1)^2}{2} + (1+y_0)(e^s-1)-s+x_0-\frac{1}{2}\right)ds\\
     &=\int_0^{t_\frac{1}{2}}\left( e^s \frac{(1+y_0)^2}{2}  -(1+y_0) +\frac{1}{2} e^{-s} -e^{-s}s +(1-e^{-s})(y_0+1) + \left(x_0-\frac{1}{2}\right)e^{-s}\right)ds\\
     &=\frac{(1+y_0)^2}{2}\left(e^{t_{\frac{1}{2}}}-1\right)+t_{\frac{1}{2}}e^{t_{\frac{1}{2}}}+\left(1-e^{t_{\frac{1}{2}}}\right)(x_0-2-y_0)\\
     &= \frac{\left(\frac{1}{2}+t_\frac{1}{2}-x_0\right)^2}{2 \left(e^{t_\frac{1}{2}}-1\right)}+t_{\frac{1}{2}}e^{t_\frac{1}{2}}+(1-x_0)e^{t_\frac{1}{2}}+t_\frac{1}{2}-\frac{1}{2}\\
     \Longrightarrow \frac{\partial I[\gamma]}{\partial t_\frac{1}{2}} &=\frac{4\left( \frac{1}{2} + t_\frac{1}{2} -x_0\right)-2e^{t_\frac{1}{2}}\left(\frac{1}{2}+t_\frac{1}{2}-x_0 \right)^2}{4\left(e^{t_\frac{1}{2}}-1\right)^2}+e^{t_\frac{1}{2}}+t_{\frac{1}{2}}e^{t_\frac{1}{2}}+(1-x_0)e^{t_\frac{1}{2}}+1
    \end{aligned}
    \end{equation*}
    \textcolor{red}{...}

    \item Suppose $\displaystyle x(s)\neq \frac{1}{2}$, $\forall s \geq 0$.
    \end{enumerate}
    \end{enumerate}

    \item \textbf{Example 2}
    Consider \eqref{ode} with $f$ defined by
\begin{equation*}
        f(x) := \left\{
  \begin{aligned}
  &\left(x+\frac{1}{2}\right)^2   \, \quad \qquad \text{in } \left[-1, -\frac{1}{2}\right], \\
   &0 \, \qquad \qquad \qquad \quad \text{in } \left(-\frac{1}{2}, \frac{1}{2}\right), \\
              &\left(x-\frac{1}{2}\right)^2  \qquad  \quad \text{in } \left[\frac{1}{2}, 1\right].
  \end{aligned}
\right.
    \end{equation*}

\begin{enumerate}
    \item Suppose $x_0 \in [-\frac{1}{2}, \frac{1}{2}]$. We can choose $\gamma (s) \equiv x_0$. Then $I[\gamma]=0$ and hence $\gamma \equiv x_0$ is a minimizer. Thus, $u(x)=0$ for $x \in [-\frac{1}{2}, \frac{1}{2}]$.
    \item Suppose $x_0 \in (\frac{1}{2}, 1]$. We need to solve the Euler-Lagrange equation.

If $x(s) \in \left[\frac{1}{2}, 1\right]$, we have
\begin{equation*}
\begin{aligned}
 &\left\{
\begin{aligned}
\dot{x}(s)&=y(s),\\
     \dot{y}(s)&=y(s) + 2\left(x(s)-\frac{1}{2}\right),\\
     x(0)&=x_0,\\
     y(0)&=y_0,
\end{aligned}
\right.\\
\Longrightarrow &
\left\{
    \begin{aligned}
         	& x(s)=\frac{1}{2}+\left(\frac{x_0}{3}+\frac{y_0}{3}-\frac{1}{6}\right)e^{2t} + \left( \frac{2}{3}x_0-\frac{1}{3}y_0-\frac{1}{3}\right) e^{-t},\\
         	& y(s)=2\left(\frac{x_0}{3}+\frac{y_0}{3}-\frac{1}{6}\right)e^{2t} - \left( \frac{2}{3}x_0-\frac{1}{3}y_0-\frac{1}{3}\right) e^{-t}.
    \end{aligned}
\right.\\
\end{aligned}
\end{equation*}
To simplify the expression, we let 
\begin{equation*}
\begin{aligned}
     A &:=\frac{x_0}{3}+\frac{y_0}{3}-\frac{1}{6},\\
    B &:= \frac{2}{3}x_0-\frac{1}{3}y_0-\frac{1}{3},\\
\end{aligned}
\end{equation*}
and then
\begin{equation}
    \left\{
    \begin{aligned}
         	& x(s)=\frac{1}{2}+Ae^{2t} + B e^{-t},\\
         	& y(s)=2Ae^{2t} - B e^{-t}.
    \end{aligned}
\right.
\end{equation}
Set $\displaystyle x(t)=\frac{1}{2}$ and we can try to solve for the time $t_\frac{1}{2}$ when the position is at $x=\frac{1}{2}$:
\begin{equation*}
        \begin{aligned}
         &\frac{1}{2}+Ae^{2t} + B e^{-t} =\frac{1}{2},\\
         	\Longrightarrow \quad & t_\frac{1}{2}=\frac{1}{3} \log \left(-\frac{B}{A}\right).\\
    \end{aligned}
\end{equation*}

\textcolor{red}{$t_{\frac{1}{2}}$ may or may not exist, depending on whether $\displaystyle -\frac{B}{A}$ is positive or not. We break into four cases according to the initial velocity $y_0$ as follows.} 
\begin{enumerate}
    \item Suppose $t_\frac{1}{2}$ exists. $\displaystyle -\frac{B}{A} > 0 , y_0 <0 \Rightarrow A<0 \Rightarrow y_0 < \frac{1-2x_0}{2}$. In this case, after the curve reaches $x=\frac{1}{2}$, we will let the curve stay at $x=\frac{1}{2}$ to minimize the cost.
    \begin{equation*}
    \begin{aligned}
        I[\gamma]&= \int_0^\infty e^{-s}\left( \frac{y(s)^2}{2} +(x(s)-\frac{1}{2})^2\right)ds\\
        &=\int_0^\infty e^{-s}\left( \frac{(2Ae^{2s}-Be^{-s})^2}{2} +(Ae^{2s}+Be^{-s})^2\right)ds\\
        &=\int_0^{t_\frac{1}{2}} 3A^2e^{3s}+\frac{3}{2}B^2e^{-3s}ds\\
        &=\left. A^2e^{3s}-\frac{B^2}{2}e^{-3s} \right|^{\frac{1}{3}\log \left(-\frac{B}{A}\right)}_0 \\
        &=-\frac{x_0y_0}{2}+\frac{1}{4}y_0\\
        \Longrightarrow \frac{\partial I[\gamma]}{\partial y_0} &= -\frac{x_0}{2}+\frac{1}{4}<0.\\
    \end{aligned}
    \end{equation*}
    Therefore, $I[\gamma]$ is decreasing with respect to $y_0$ when $\displaystyle y_0 < \frac{1-2x_0}{2}$.

    \item Suppose $A=0$, i.e., $\displaystyle y_0=\frac{1-2x_0}{2}$. We have
    \begin{equation*}
     \left\{
        \begin{aligned}
        x(s)&=\frac{1}{2}+\left(x_0-\frac{1}{2}\right)e^{-s},\\
        y(s)&=-\left(x_0-\frac{1}{2}\right)e^{-s}.
        \end{aligned}
    \right.
    \end{equation*}
    As we can see here, the curve never reaches $x=\frac{1}{2}$. Compute the cost function
    \begin{equation*}
        \begin{aligned}
         I[\gamma] &= \int_0^\infty e^{-s}\left( \frac{(x_0-\frac{1}{2})^2e^{-2s}}{2} +(x_0-\frac{1}{2})^2e^{-2s}\right)ds\\
          &=\frac{1}{2}x_0^2-\frac{1}{2}x_0+\frac{1}{8}.\\
        \end{aligned}
    \end{equation*}

    \item Suppose $A >0, B \geq 0$, i.e., $\displaystyle \frac{1-2x_0}{2} < y_0 \leq 2x_0-1$. We claim that in this case we can always find a curve $\eta$ that $I[\eta] < I[\gamma]$.

    If we start at $x_0 \in (\frac{1}{2}, 1)$ and evolve according to the Euler-Lagrange equation, the velocity $\dot{\gamma}(s) = y(s)$ may change sign as time goes, for instance, from negative to positive. We can consider another curve $\eta(s)$ such that $\eta(0)=x_0$ and $\dot{\eta}(s)=-|\dot{\gamma}(s)|$ for $s\in \left\{s \in [0, \infty) :\gamma(s)=x(s)<1\right\}$ and stay at $x=\frac{1}{2}$ once the curve $\eta(s)=\frac{1}{2}$. If $\gamma$ arrives at $1$ before $\eta$ hits $\frac{1}{2}$, there are two possibilities for $\gamma$ afterwards. The first possibility is that $\gamma$ can stay at $1$. Then we can choose $\eta$ so that $\displaystyle \frac{\dot{\eta}(s)^2}{2}+\left(\eta(s)-\frac{1}{2}\right)^2<f(1)$ to make $I[\eta] < I[\gamma]$. The second possibility is that $\gamma$ can move away from $1$. Then the strategy is like before, namely that we choose $\dot{\eta}(s)=-|\dot{\gamma}(s)|$ to get $I[\eta] < I[\gamma]$.

    If we start at $x_0=1$, we can choose to stay at $x=1$, i.e., $\eta (s) \equiv 1$. Then $\displaystyle I[\eta]=\frac{1}{4}$. If we choose $\displaystyle y_0=\frac{1-2x_0}{2}$ as in case (b), $\displaystyle I[\gamma]=\frac{1}{8}$.
    \item Suppose $y_0 > 2x_0-1$. In this case, $A >0, B <0$, and $y(s) = 2Ae^{2s}- Be^{-s} >0$. Hence, the curve $\gamma$ will run towards $x=1$. Again, the strategy is to make $\dot{\eta}(s)=-\dot{\gamma}(s)$ and the argument is similar to that in case (c).
\end{enumerate}
In summary, the minimizer is $\displaystyle \gamma (s) = \frac{1}{2}+\left( x_0 -\frac{1}{2}\right) e^{-s}$, which is the solution to the Euler-Lagrange equation with the initial velocity $\displaystyle y_0=\frac{1-2x_0}{2}$. Hence, $\displaystyle u(x)= \frac{1}{2}x^2-\frac{1}{2}x+\frac{1}{8}$ for $x \in (\frac{1}{2}, 1]$.
    \item Suppose $x_0 \in \left[-1, -\frac{1}{2}\right]$.
    If $x(s) \in \left[-1, -\frac{1}{2}\right]$, we have

\begin{equation*}
\begin{aligned}
 &\left\{
\begin{aligned}
\dot{x}(s)&=y(s),\\
     \dot{y}(s)&=y(s) + 2\left(x(s)+\frac{1}{2}\right),\\
     x(0)&=x_0,\\
     y(0)&=y_0,
\end{aligned}
\right.\\
\Longrightarrow &
\left\{
    \begin{aligned}
         	& x(s)=-\frac{1}{2}+\left(\frac{x_0}{3}+\frac{y_0}{3}+\frac{1}{6}\right)e^{2t} + \left( \frac{2}{3}x_0-\frac{1}{3}y_0+\frac{1}{3}\right) e^{-t},\\
         	& y(s)=2\left(\frac{x_0}{3}+\frac{y_0}{3}+\frac{1}{6}\right)e^{2t} - \left( \frac{2}{3}x_0-\frac{1}{3}y_0+\frac{1}{3}\right) e^{-t}.
    \end{aligned}
\right.\\
\end{aligned}
\end{equation*}
Similarly, we can show the minimizer is $\displaystyle \gamma(s)=-\frac{1}{2}+\left(x_0+\frac{1}{2}\right)e^{-s}$ and $\displaystyle u(x)=\frac{1}{2}x^2+\frac{1}{2}x+\frac{1}{8}$ for $x \in \left[-1, -\frac{1}{2}\right]$.
\end{enumerate}
Therefore, 
\begin{equation*}
u(x)=\left\{
    \begin{aligned}
      &\frac{1}{2}\left(x+\frac{1}{2}\right)^2  \quad \qquad \text{if }x \in \left[-1, -\frac{1}{2}\right],\\
     &0 \qquad \qquad \qquad \qquad \text{if } x \in \left[-\frac{1}{2}, \frac{1}{2}\right],\\
   &\frac{1}{2}\left(x-\frac{1}{2}\right)^2 \quad \qquad \text{if } x \in \left[\frac{1}{2}, 1\right].
    \end{aligned}
\right.
\end{equation*}

\vspace{2em}

Next, we look into the second order equation
 \begin{equation}
    \label{sec}
        \left\{
  \begin{aligned}
   u^\epsilon(x) + \frac{1}{2}|\dot{u}^\epsilon(x)|^2 -f(x)-\epsilon \Ddot{u}^\epsilon (x) &= 0 \, \quad \qquad \text{in } (-1, 1), \\
              u^\epsilon &= +\infty \qquad   \text{for } x=-1, 1.
  \end{aligned}
\right.
    \end{equation}
First, we can verify $\displaystyle w(x):=-2\epsilon \log(1-|x|)+2\epsilon \log \left(\frac{1}{4}-\sqrt{\frac{1}{16}-\epsilon}\right)+\left(\frac{1}{4} + \sqrt{\frac{1}{16}-\epsilon}\right)^2$ is a supersolution of \eqref{sec} at least on $\left(-1, -\frac{1}{2}\right)\cup \left(\frac{1}{2}, 1\right)$. $\displaystyle 2 \epsilon \log \left(\frac{1}{4}-\sqrt{\frac{1}{16}-\epsilon}\right)+\left(\frac{1}{4} + \sqrt{\frac{1}{16}-\epsilon}\right)^2$ is the optimal constant $C$ we can choose in order to make $-2\epsilon \log(1-|x|)+C$ a supersolution. And
\begin{equation*}
    \lim_{\epsilon \to 0^+}2 \epsilon \log \left(\frac{1}{4}-\sqrt{\frac{1}{16}-\epsilon}\right)+\left(\frac{1}{4} + \sqrt{\frac{1}{16}-\epsilon}\right)^2 =\frac{1}{4}.
\end{equation*}
\end{itemize}
\end{solution}

    \vspace{1em}

    \item Consider the general $H(p)$ with $C_1 |\xi|^p \leq H(\xi) \leq C_2 |\xi|^p$, and $\displaystyle \lim_{\delta \to 0} \delta^\frac{p}{p-1} H(\delta^{-\frac{1}{p-1}}x) = |x|^p$.
\end{enumerate}

\vspace{3em}

\section{Ideas}
\begin{enumerate}[label=\arabic*)]
    \item We already proved the convergence rate for $f$ with $f|_{\partial \Omega} =0$. For general $f$, let $u^\epsilon$ be the solution to
\begin{equation}
\left\{
  \begin{aligned}
   u^\epsilon + |Du^\epsilon|^p -f(x) - \epsilon \Delta u^\epsilon &=0 \, \quad \qquad \text{in } \Omega, \\
              u^\epsilon &= +\infty \qquad  \text{on } \partial \Omega,
  \end{aligned}
\right.
\end{equation}

and u be the solution to 
\begin{equation}
\left\{
  \begin{aligned}
   u + |Du|^p -f(x) & \leq 0 \quad \qquad \text{in } \Omega, \\
              u + |Du|^p -f(x) & \geq 0 \quad \qquad \text{on } \partial \Omega.
  \end{aligned}
\right.
\end{equation}
The idea is to extend $f: \Omega \to \mathbb{R}$ to $f_\lambda: (1+\lambda) \Omega \to \mathbb{R}$ with $f_\lambda|_{\partial (1+\lambda)\Omega}=0$. Consider the solution to
\begin{equation}
\left\{
  \begin{aligned}
   v^\epsilon + |Dv^\epsilon|^p -f_\lambda(x) - \epsilon \Delta v^\epsilon &=0 \, \quad \qquad \text{in } (1+\lambda)\Omega, \\
              v^\epsilon &= +\infty \qquad  \text{on } \partial [(1+\lambda)\Omega],
  \end{aligned}
\right.
\end{equation}
and the solution to 
\begin{equation}
\left\{
  \begin{aligned}
   v + |Dv|^p -f_\lambda(x) & \leq 0 \quad \qquad \text{in } (1+\lambda)\Omega, \\
              v + |Dv|^p -f_\lambda(x) & \geq 0 \quad \qquad \text{on } \partial [(1+\lambda)\Omega].
  \end{aligned}
\right.
\end{equation}
We know $\bar{v^\epsilon} \to v$ with the rate $\sqrt{\epsilon}$ except the boundary layer. We can try to scale $v^\epsilon$ to be $\bar{v^\epsilon}: \Omega \to \mathbb{R}$ such that $\bar{v^\epsilon} = v^\epsilon$ in $(1-\delta)\Omega$. (Here, $\delta$ can depend on $\epsilon$.) In $(1-\delta)\Omega$, $\bar{v^\epsilon} \to v=u$ with the rate $\sqrt{\epsilon}$, since $f =f_\lambda$ there.

Some forms of scaling to try:
\begin{itemize}
    \item $\bar{v^\epsilon} := \alpha(x) v^\epsilon \left(\beta(x) x \right)$
    \item $v^\epsilon:= \left\{
  \begin{aligned}
   &v^\epsilon(x) + v^\epsilon \left((1+\lambda)x \right)e^{-\displaystyle \frac{1}{|x|^2-|1-\delta|^2}} \, \quad \qquad \text{in } \Omega \setminus \Omega_\delta, \\
              &v^\epsilon(x) \qquad \qquad \qquad \qquad \qquad \qquad \quad \qquad \qquad  \text{on } \Omega_\delta.
  \end{aligned}
\right.$
\end{itemize}
\item The desired convergence rate is true not only for $f$ with $f|_{\partial \Omega} = 0$, but also for $\displaystyle f(x) = g(x) + \frac{\sigma \epsilon^{\alpha + 1}}{d(x)^\alpha}$ where $g=0$ on $\partial \Omega$. We can use this to scale $\bar{v^\epsilon}$ in (1).

\item Compare $u^\varepsilon$ and $v^\varepsilon$ where $1<p\leq 2$ and
\begin{equation}\label{eq:PDEeps}
    \begin{cases}
   \mathcal{L}[u^\varepsilon] =  u^\varepsilon(x) + |Du^\varepsilon(x)|^p - f(x) - \varepsilon \Delta u^\varepsilon(x) = 0 &\qquad
    \text{in}\;\Omega, \vspace{0cm}\\
   u^\varepsilon(x) = +\infty &\qquad
    \text{on}\;\partial\Omega
    \end{cases} \tag{PDE$_\varepsilon$}
\end{equation}
and
\begin{equation}\label{eq:vPDEeps}
    \begin{cases}
   \mathcal{L}[v^\varepsilon] =  v^\varepsilon(x) + |Dv^\varepsilon(x)|^p - f(x) - \varepsilon \Delta v^\varepsilon(x) = 0 &\qquad
    \text{in}\;\Omega, \vspace{0cm}\\
   v^\varepsilon(x) = u(x) &\qquad
    \text{on}\;\partial\Omega.
    \end{cases} 
\end{equation}
We know that $|v^\varepsilon - u|\leq C\sqrt{\varepsilon}$, thus the goal is to compare $u^\varepsilon$ and $v^\varepsilon$. Let $w^\varepsilon(x) = u^\varepsilon(x) - v^\varepsilon(x)$, we have
\begin{equation}\label{eq:wPDEeps}
    \begin{cases}
w^\varepsilon(x) + |Du^\varepsilon(x)|^p  - |Dv^\varepsilon|^p - \varepsilon \Delta w^\varepsilon(x) = 0 &\qquad
    \text{in}\;\Omega, \vspace{0cm}\\
   w^\varepsilon(x) = +\infty &\qquad
    \text{on}\;\partial\Omega.
    \end{cases} 
\end{equation}
The good thing about \eqref{eq:wPDEeps} is, the data $f$ disappears and furthermorethe new data, for example with $p=2$ can be written as
\begin{equation}\label{eq:wwPDEeps}
    \begin{cases}
w^\varepsilon(x) + |Dw^\varepsilon(x)|^2 +\underbrace{2Dw^\varepsilon(x)\cdot Dv^\varepsilon(x)}_{g
(x)} - \varepsilon \Delta w^\varepsilon(x) = 0 &\qquad
    \text{in}\;\Omega, \vspace{0cm}\\
   w^\varepsilon(x) = +\infty &\qquad
    \text{on}\;\partial\Omega.
    \end{cases} 
\end{equation}
and $g(x) \approx \frac{\varepsilon \nabla d(x)\cdot \nabla v^\varepsilon(x)}{d(x)} + |Dv^\varepsilon(x)|^2$, which is small in some sense depends on $\varepsilon$. Question: can we get a rate of convergence $w^\varepsilon(x)\to 0$? What is the behavior of $Dv^\varepsilon(x)$ as $\varepsilon\to 0$? Can we know more besides $|v^\varepsilon - u|\leq C\sqrt{\varepsilon}$?
\end{enumerate}

\end{document}

### 2021-07-15 Drafts and notes/Notes/Notes-May18.tex
Almost final

\documentclass[english,reqno]{amsart}
%\renewcommand{\baselinestretch}{1.2}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\raggedbottom
\usepackage{subfig}
\usepackage{amssymb,amsbsy,amsmath,amsfonts,amssymb,amscd}
\usepackage{comment}
\usepackage{verbatim}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage[numbers]{natbib} % for alphabetically numbered lists
\usepackage{algorithm,algpseudocode}
\usepackage{setspace}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{assum}{Assumption}[section]
\newtheorem{cor}{Corollary}[section]
\newenvironment{solution}
  {\renewcommand\qedsymbol{$\blacksquare$}\begin{proof}[Solution]}
  {\end{proof}}
\title{Classical mechanics Hamiltonian}

\begin{document}

\maketitle
\date{May 18, 2021}
\section{The first-order equation}\noindent
Work out the details of the following example in $n=1$. Let u be the solution to
    \begin{equation}
    \label{example}
        \left\{
  \begin{aligned}
   u(x) + \frac{1}{2}|u^\prime(x)|^2 -f(x) &\leq 0 \, \quad \qquad \text{in } (-1, 1), \\
              u(x) + \frac{1}{2}|u^\prime (x)|^2 -f(x) &\geq 0 \qquad  \quad \text{on } [-1,1],
  \end{aligned}
\right.
    \end{equation}
with an easier $f$, using deterministic optimal control formula and Euler-Lagrange equation. For instance, $f=0$ in $[-\frac{1}{2}, \frac{1}{2}]$ and $f(x) = x-\frac{1}{2}$ on $[\frac{1}{2},1]$ and $f(x) = -\frac{1}{2} - x$ on $[-1,-\frac{1}{2}]$.
And then try to look into the solution to the equation with $\epsilon \Delta u^\epsilon$.

\paragraph{\textbf{Optimal control formula}}
\noindent Solution is given by
\begin{equation*}
    u(x_0) = \inf_{\gamma(0)=x_0} \int_0^\infty e^{-s}\left(\frac{|\dot{\gamma}(s)|^2}{2} + f(\gamma(s))\right)ds
\end{equation*}
where the admissible set are absolutely continuous curves $\gamma$ such that $\gamma(s)\in \overline{\Omega}$ for all $s\geq 0$ and $\gamma(0)=x_0$.

\paragraph{\textbf{Euler-Lagrange equation}}    
\begin{equation}
\label{EL}
\left\{
\begin{aligned}
     \Ddot{\gamma}(s)&=\dot{\gamma}(s) + f^\prime (\gamma(s)), \qquad s\in (0,\infty)\\
     \gamma(0)&=x_0.
\end{aligned}
\right.
\end{equation}
\paragraph{\textbf{Gradient bound}} Since $u\equiv 1$ is a supersolution and $u\equiv 0$ is a subsolution, we have $0\leq u\leq 1$, thus
\begin{equation*}
    \frac{1}{2}|u'(x)|^2 \leq f(x) - u(x) \leq 1
\end{equation*}
and thus (in viscosity sense)
\begin{equation*}
    |u'(x)| \leq 2.
\end{equation*}
\paragraph{\textbf{An identity (analog of conservation of energy)}} 
\begin{equation*}
    \frac{d}{ds}\left(\frac{|\dot{\gamma}(s)|^2}{2} - f(\gamma(s))\right) = |\dot{\gamma}(s)|^2.
\end{equation*}

\paragraph{\textbf{Observations}}
\begin{itemize}
    \item If $x_0\in [-\frac{1}{2},\frac{1}{2}$ then obviously the minimizer is $\gamma(s) \equiv x_0$ for all $s\geq 0$, which resulted in $u(x_0) = 0$.
    \item We are interested in solving for $u(x_0)$ if $x_0\notin [-\frac{1}{2},\frac{1}{2}]$. For example let us consider $x_0 \in [\frac{1}{2},1]$, then heuristically a minimizing path has to traverses to the left to reach $\frac{1}{2}$ so that the potential term
    \begin{equation*}
        f(\gamma(s))    
    \end{equation*}
    in the cost function decreases, while also try to move not too fast so that the kinetic term
    \begin{equation*}
        \frac{1}{2}|\dot{\gamma}(s)|^2
    \end{equation*} 
    does not contribute too much. So we have a game of balancing between the kinetic energy and potential energy.
    \item Now we see that, it could be the case that it takes an infinite amount of time to reach $\frac{1}{2}$. Let us denote $t_0$ the fist time $\gamma$ reaches $\frac{1}{2}$.
\end{itemize}
\subsection{The case $t_0$ is finite} From the dynamic programming principle we have
\begin{equation*}
    u(x_0) = \int_0^{t_0}e^{-s}\left(\frac{|\dot{\gamma}(s)|^2}{2} + f(\gamma(s))\right)ds + \underbrace{u(\gamma\left(t_0\right))}_{u(1/2) = 0}
\end{equation*}
On $[0,t_0]$, the Euler-Lagrange equation reads 
\begin{equation*}
    \ddot{\gamma}(s) = \dot{\gamma}(s)+1, \qquad s\in (0,t_0)
\end{equation*}
thus we can solve for $\dot{\gamma}$, assuming the initial velocity $\dot{\gamma}(0) = \xi_0$. We have
\begin{equation*}
    \dot{\gamma}(s) = (\xi_0+1)e^{s} - 1, \qquad s\in (0,t_0).
\end{equation*}
Thus
\begin{equation*}
    \gamma(s) = (\xi_0+1)(e^s-1) - s + x_0, \qquad s\in (0,t_0).
\end{equation*}
Set $\gamma(t_0) = \frac{1}{2}$ we have
\begin{equation*}
    (\xi_0+1)(e^{t_0}-1) - t_0 + x_0 = \frac{1}{2}.
\end{equation*}
We compute (should be with a minimizer)
\begin{equation*}
\begin{split}
    u(x_0) &= \int_0^{t_0}e^{-s}\left(\frac{1}{2}\Big((\xi_0+1)e^{s}-1\Big)^2 +\left[ (\xi_0+1)(e^{s}-1)-s+x_0 - \frac{1}{2}\right]\right)ds\\
    &=\int_0^{t_0}\left[\frac{1}{2}(\xi_0+1)^2e^{s}+\frac{e^{-s}}{2} - (\xi_0+1) \right]ds + \int_0^{t_0}\left((\xi_0+1)(1-e^{-s})-se^{-s} + e^{-s}\left(x_0-\frac{1}{2}\right)\right)ds.
\end{split}
\end{equation*}
We have
\begin{align*}
    &\int_0^{t_0}\left[\frac{1}{2}(\xi_0+1)^2e^{s}+\frac{e^{-s}}{2} - (\xi_0+1) \right]ds = \frac{(\xi_0+1)^2(e^{t_0}-1)}{2} + \frac{1-e^{-t_0}}{2} - (\xi_0+1)t_0 \\
    &\int_0^{t_0} (\xi_0+1)(1-e^{-s}) ds = (\xi_0+1)t_0 - (\xi_0+1)(1-e^{-t_0})\\
    &\int_0^{t_0} -se^{-s}ds = t_0e^{-t_0} + (1-e^{-t_0})\\
    &\int_0^{t_0} e^{-s}\left(x_0-\frac{1}{2}\right)ds = \left(x_0-\frac{1}{2}\right)(1-e^{-t_0}).
\end{align*}
Therefore
\begin{equation*}
\begin{split}
    u(x_0) &= \frac{(\xi_0+1)^2(e^{t_0}-1)}{2} +t_0e^{-t_0} + (1-e^{-t_0})\Bigg(\frac{1}{2}-\xi_0-1 +1+x_0-\frac{1}{2} \Bigg)\\
    &= \frac{(\xi_0+1)^2(e^{t_0}-1)}{2} + t_0e^{-t_0} + (1-e^{-t_0})(x_0-\xi_0)
\end{split}
\end{equation*}
Now given a time $t_0\in (0,\infty)$ from the equation
\begin{equation*}
    (\xi_0+1)(e^{t_0}-1) - t_0 + x_0 = \frac{1}{2}
\end{equation*}
we can uniquely solve for $\xi_0 = \xi_0(t_0)$ as a function (smooth, obviously). Thus we can try to optimize the function
\begin{equation*}
    \mathcal{G}(t_0) =\frac{(\xi_0+1)^2(e^{t_0}-1)}{2} + t_0e^{-t_0} + (1-e^{-t_0})(x_0-\xi_0).
\end{equation*}
Taking derivative

\subsection{A different potential}
Now using 
\begin{equation*}
    f(x) = \begin{cases}
    0 & |x|\leq \frac{1}{2}\\
    \left(|x|-\frac{1}{2}\right)^2 & |x|\in \left[\frac{1}{2},1\right].
    \end{cases}
\end{equation*}
We can use the fact that for a minimizer $\gamma$ starting at $x_0\in \left[\frac{1}{2},1\right]$ then $\gamma(t_0) = \frac{1}{2}$ implies $\dot{\gamma}(t_0) = 0$. We have
\begin{equation*}
    \displaystyle \gamma (s) = \frac{1}{2}+\left( x_0 -\frac{1}{2}\right) e^{-s},\qquad s\geq 0.
\end{equation*}
We deduce that for $|x|\geq \frac{1}{2}$ then
\begin{equation*}
    u(x) = \frac{3}{2}\int_0^\infty  \left(x-\frac{1}{2}\right)^2e^{
    -3s}ds = \frac{1}{2}\left(x-\frac{1}{2}\right)^2.
\end{equation*}

\end{document}
